### 2021-10-04 preregistration/preregistration_analyses.Rmd
reformat task folders

---
title: "preregistration_analyses"
author: "Stefan Vermeent"
date: "9/29/2021"
output: pdf_document
---

```{r libraries, include=FALSE}
library(tidyverse)
```

### 2021-10-18 preregistration/preregistration_analyses.Rmd
intermediate update prereg

@@
 ---
-title: "preregistration_analyses"
-author: "Stefan Vermeent"
-date: "9/29/2021"
-output: pdf_document
+bibliography: references.bib
+csl: apa.csl
+output:
+  pdf_document: default
+  officedown::rdocx_document:
+    reference_docx: reference-doc.docx
+    page_margins:
+      bottom: 1
+      top: 1
+      right: 1
+      left: 1
+      header: 0.5
+      footer: 0
+      gutter: 0
+    plots:
+      align: center
+      caption:
+        style: Image Caption
+        pre: 'Figure '
+        sep: '. '
+    tables:
+      caption:
+        style: Table Caption
+        pre: 'Table '
+        sep: '. '
 ---
@@
 ```
+
+# Methods {#methods}
+
+# Participants {#participants}
+
+Participants will be XXX US-based individuals between the ages of 18 and 30.
+We decided for this age cut-off to limit the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 (@salthouse_selective_2010).
+
+# Procedure {#procedure}
+
+## Measures {#measures}
+
+This is the measures section.
+
+### Attention tasks {#tasks}
+
+This is the section featuring all the attention tasks.
+
+### Questionnaires {#questionnaires}
+
+This is the section featuring all the questionnaires.
+
+## Data analyses {#analyses}
+
+lorem ipsum
+
+### preprocessing {#preprocessing}
+
+lorem ipsum
+
+### Reaction Times {#rt}
+
+lorem ipsum
+
+### Drift Diffusion Models {#ddm}
+
+lorem ipsum

### 2021-10-19 preregistration/preregistration_analyses.Rmd
initial commit of methods preregistration

--- 2021-10-04 preregistration/preregistration_analyses.Rmd
@@
 ---
-title: "preregistration_analyses"
-author: "Stefan Vermeent"
-date: "9/29/2021"
-output: pdf_document
+bibliography: references.bib
+csl: apa.csl
+output:
+  word_document: default
+  pdf_document: default
+  officedown::rdocx_document:
+    page_margins:
+      bottom: 1
+      footer: 0
+      gutter: 0
+      header: 0.5
+      left: 1
+      right: 1
+      top: 1
+    plots:
+      align: center
+      caption:
+        pre: 'Figure '
+        sep: '. '
+        style: Image Caption
+    reference_docx: reference-doc.docx
+    tables:
+      caption:
+        pre: 'Table '
+        sep: '. '
+        style: Table Caption
 ---
 
-```{r libraries, include=FALSE}
-library(tidyverse)
-```
+# Introduction and hypotheses
+
+Childhood adversity outcomes are commonly viewed from a deficit perspective, emphasizing the detrimental effects of adversity on a range of cognitive and behavioral outcomes.
+Recent years have seen the development of the complimentary hidden talents approach, which stresses that people cognitively adapt to their environment and might therefore develop specific cognitive skills that are ecologically advantageous.
+However, it remains largely unclear which mechanisms drive specific enhancements and impairments of cognitive abilities.
+In this pilot study, we test the idea that people who grow up in adversity tend to develop a present-focused attention style, with features that benefit performance on some cognitive tasks but hurt performance on others.
+
+In line with previous theorizing [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013], we expect stress-adapted cognitive styles to be characterized by a strong focus on the present.
+By cognitive style we mean a collection of relatively stable information processing tendencies (e.g., speed of processing, focus of attention, goal-directed behavior) that together determine how people interact with their environment.
+We expect that cognitive styles are best understood at the level of more basic cognitive processes.
+Higher-level processes that are typically targeted in hidden talents studies (e.g., working memory, task-switching) are not fully dissociable processes but instead involve many of the same more basic processes [@conway_2021; @kovacs_2019; @verbruggen_2014].
+This overlap means that impairment and enhancement patterns across tasks could be driven by the same underlying process.
+For example, an attention style that is strongly focused on the here-and-now would be beneficial for basic processing speed and information updating tasks, but might harm performance if in tasks with a lot of distracting stimuli.
+Thus, common cognitive tasks can be categorized in terms of how they align with certain (aspects of) cognitive styles, and could be experimentally manipulated to increase or decrease their fit to a person’s style.
+
+we focus on two aspects of external attention [i.e., attention pointed at the external environment; @chun_2011] that we expect to develop in harsh and unpredictable environments: 1) A relatively wider scope of attention and 2) an increased sensitivity to subtle changes in the environment.
+When might these attention styles develop in adverse environments?
+Attention is involved in information processing on a timescale of seconds to minutes; Focusing attention for longer periods on a single stimulus is impossible for most people [@warm_2008].
+Thus, stable attention styles are most useful in response to environmental features that unfold on the same timescale.
+Factors such as changes in adult household members or frequently moving homes, which are often used as proxies for unpredictability, are unlikely to shape stable attentional styles as they unfold over days or weeks.
+In addition, any threats that are spatially or temporally predictable (e.g., a specific part of the neighborhood that is known to be dangerous or might be especially dangerous at night) are more likely to lead to signal- or cue-based changes in cognitive processing.
+Instead, a cognitive style that systematically favors external attention over internal attention should develop when threats are frequent and the environment is chaotic, such that past states of the environment are not predictive of the current state [@emond_2020; @young_2020].
+In such an environment, threats might arise at any time and the occasional reward might be fleeting [@ellis_2009; @frankenhuis_2016].
+In the absence of reliable cues, a person would benefit from having their attention fixated broadly on the external environment, so that threats and opportunities can be anticipated and dealt with as soon as they appear.
+
+The current pilot study had two primary aims: First, we tested whether people from harsh and unpredictable environments would perform better on attention tasks favor a broad attention scope and a sensitivity to subtle changes.
+To this end, participants completed three attention tasks that differed in the extent to which they would favor or punish these attention features.
+Second,
+we investigated the link between adversity and attention both in a traditional analysis of reaction times, as well as by using the Drift Diffusion Model [DDM; @forstmann_2016; @ratcliff_2015; @ratcliff_2008] to more precisely disentangle the underlying cognitive processes.
+
+Our confirmatory hypotheses were as follows:
+1)
+
+In addition, the pilot study had two secondary aims: First, we investigated whether the link between measures of adversity and attention would be contingent on the timescale of the adversity items.
+More specifically, we expected stable attention styles to be better predicted by items of momentary unpredictability (e.g., "things were often chaotic in my house") than by items of temporally extended unpredictability ("At least one of my parents changed jobs frequently").
+Second, we conducted exploratory correlation analyses between measures of adversity, attention, and measures of temporal orientation (i.e., impulsivity and future orientation).
+
+# Methods {#methods}
+
+## Participants {#participants}
+
+Participants were XXX US-based individuals between the ages of 18 and 30 (*M* = `r #TBD`, *SD* = `r #TBD`).
+We decided for this age cut-off to limit the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 (@salthouse_2010).
+Recruitment took place through Prolific.
+Participants were eligible for for the study if they were between 18 and 30 years old, if English was their primary language, if they were currently residing in the United States, if they did not have a history of brain injury, if they did not have color blindness, and if they had normal or corrected-to-normal eyesight.
+
+## Exclusion criteria {#exclusion}
+
+We applied several exclusion criteria prior to inspecting or testing any of the relationships between independent and dependent variables.
+First, we excluded participants with incomplete data on any of the attention tasks (*N* = `r #TBD `).
+Second, we excluded participants who did not have normal or corrected-to-normal vision (*N* = `r #TBD `).
+Third, we analyzed responses to the attention checks and reversed coded items in the questionnaire part of the experiment.
+We excluded participants if they missed both attention check items or if they had suspicious response patterns (e.g., consistently endorsing high response options even when some items were reversed coded) (*N* = `r #TBD `).
+
+In addition, we screened the reaction times on each of the three attention tasks.
+For the Drift Diffusion analyses, it is important that each response is generated by a diffusion process (as opposed to, for example, guessing).
+To this end, trials with reaction times < 250ms  or longer than 3500ms (@ratcliff_2015) were excluded from the analyses (*N* = `r #TBD `).
+Participants for whom more than 10 trials were removed were excluded from the analyses (N = `r #TBD `).
+
+## Procedure {#procedure}
+
+The experiment was completed on the participants' own laptop or desktop computer and consisted of three parts: written consent, attention task battery, questionnaire battery, brief demographics form, and final checks and the opportunity to give feedback on the experiment.
+The demographics questions asked about the participant's age, sex at birth, gender, ethnicity, social class, education level, occupation, and household income.
+In addition, we checked whether participants had color blindness and whether they had normal or corrected-to-normal vision.
+At the end of the experiment, participants were asked whether they ever got up and left during the study and whether they were ever interrupted during the study (answers on these questions did not affect compensation).
+
+After providing written consent, participants started with the three attention tasks.
+They were asked to complete the attention tasks in a quiet room in the house where they would be least likely to be distracted by other people or outside noises.
+The order of the tasks was counterbalanced between subjects.
+At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs.
+The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych.
+Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the creditcard.
+The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants.
+After succesfully resizing the screen, participants completed all three tasks.
+Whenever participants had to respond by use of their keyboard, the cursor was hidden from the screen to minimize distractions.
+
+## Measures {#measures}
+
+### Attention tasks {#tasks}
+
+The attention tasks were programmed in JsPsych version 3.6.1 (@deLeeuw_2015).
+
+#### Cued attention task {#cued_attention}
+
+The cued attention task is an adaptation of the Posner task (@posner_1980).
+On each trial, a left- or right-pointing arrow is presented in one of eight random locations at a distance of 300 pixels from the center of the screen (see Figure 1B).
+Participants have to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard.
+On 50% of the trials, the arrow is preceded by a cue ("\*") in the exact same location (i.e., cued trials).
+On the other 50% of the trials, the cue ("\*") is presented at the center of the screen (i.e., neutral trials).
+Thus, on the cued trials, the location of the cue deterministically predicts the location of the arrow, whereas on the neutral trials the arrow will always appear in a different location.
+
+Each trial starts with a fixation cross presented at the center of the screen for 1000ms.
+Then, the cue is presented for 250ms either at the center of the screen or in the location where the arrow will appear.
+Finally, the arrow is presented until a response is given by the participant.
+The cued attention task begins with eight practice trials (four cued and four neutral trials) in which participants receive performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
+After finishing the practice round, participants complete a single test block consisting of a total of 64 trials (two repetitions of all parameter combinations: arrow location (top center vs.
+top left vs.
+center left vs.
+bottom left vs.
+bottom center vs.
+bottom right vs.
+center right vs.
+top right) X arrow direction (left vs.
+right) X condition (cued vs.
+neutral)).
+
+The average reaction time for each participant was calculated separately for cued and neutral trials based on correct trials only.
+If necessary for meeting model assumptions, reaction times were log-transformed.
+We did not plan on conducting analyses on the proportion of errors as error rates are generally very low on similar Cued Attention Tasks (i.e., < 5% of trials).
+
+#### Flanker task {#flanker}
+
+On each trial of the Flanker task (@eriksen_1974), participants are presented with a set of five arrows pointing either left or right.
+Their job is to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right (see Figure 1A).
+On 50% of the trials, the flanking arrows point in the same direction as the central arrow (i.e., congruent trials), and on the other 50% of the trials they point in the opposite direction (i.e., incongruent trials).
+The arrows are randomly presented in the top-half or bottom-half of the screen.
+This is done to prevent participants from being able to fixate on the center of the screen, which would reduce the interfering effect of the flanking arrows.
+
+Each trial starts with a fixation cross presented at the center of the screen.
+After a variable delay (randomly sampled from a uniform distribution from 800ms to 1200 ms with time steps of 50ms), the arrows are presented either in the top- or bottom-half of the screen.
+Participants have 2000ms to indicate the direction of the center arrow.
+The Flanker task begins with eight practice trials in which participants receive performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
+After finishing the practice round, participants complete a single test block consisting of a total of 64 trials (eight repetitions of all parameter combinations: arrow location (top vs.
+bottom) X central arrow direction (left vs.
+right) X condition: (congruent vs.
+incongruent)).
+Participants do not receive performance feedback during the test block.
+
+The average reaction time for each participant was calculated separately for congruent and incongruent trials based on correct trials only.
+If necessary for meeting model assumptions, reaction times were log-transformed.
+We did not plan on conducting analyses on the proportion of errors as error rates are generally very low on the Flanker task, especially on the congruent trials (i.e., < 5% of trials).
+
+The DDM analysis of the Flanker task was done using an adaptation of the standard DDM that was specifically developed to account for Flanker data: The Spotlight Drift Diffusion Model (SDDM; @grange_2016; @white_2018a; @white_2018b, @white_2011).
+The standard DDM model assumes a stable drift rate over time within trials (i.e., the rate of information accumulation does not change over time).
+However, on the Flanker Task, reaction time patterns indicate that the drift rate increases over time, thus violating the basic assumption of the standard DDM (@white_2011).
+The SDDM assumes that attention on the Flanker task works like a spotlight that starts relatively broad, and then gradually narrows down to the central arrow over time.
+Each arrow provides perceptual input *p*.
+If the flanking arrows are congruent, all flankers take a positive value for *p*; if the flanking arrows are incongruent, they take a negative value for *p* while the central arrow takes a positive value.
+The drift rate (*v*) at each time point is the function of the strength of perceptual input *p* multiplied by the amount of attention focused on each arrow.
+Attention is operationalized by two additional parameters: the initial width of the attentional spotlight (*SD~a~*) and the shrinking rate of the attentional spotlight (*rd*).
+The attentional spotlight is assumed to be normally distributed over the arrows, with relatively more attention paid to the arrows at the center and relatively less attention paid to the peripheral arrows.
+Over time, this normal distribution (*SD~a~*) narrows down to the central arrow at the rate specified by *rd*, thereby gradually decreasing the interfering effect of the flanking arrows.
+Note that the SDDM is based on a combined analysis of congruent and incongruent trials.
+See Figure 1B for a visualization of the SDDM.
+
+Previous research has shown that it is not useful to interpret both *SD~a~* and *rd* since they trade-off against each other (i.e., a wide initial spotlight combined with a large shrinking rate leads to similar patterns as a narrow initial spotlight combined with a low shrinking rate; @white_2018a; @white_2011).
+Most previous studies have fixed *SD~a~* and only estimated *rd*, or calculated a *SD~a~*/*rd* ratio, which serves as a measure of interference.
+However, our primary interest lies in the initial width of the attentional spotlight, which we hypothesize to be wider for people from harsh and unpredictable environments compared to people from safe and predictable environments.
+In this pilot study, we fit several SDDM models either estimating both attention parameters or fixing *rd* to see how it affected model fit (more details below).
+
+#### Change detection task {#change}
+
+On each trial of the change detection task, participants are presented with five colored circles against a grey background, each with a radius of 15 pixels (see Figure 1C).
+Each circle is located in a random location within a pre-specified area of 50 by 50 pixels to prevent overlap.
+Participants have 1000ms to memorize the locations of the five circles around the fixation cross.
+After 1000ms, the circles briefly disappear for 500ms and then reappear again.
+On 50% of the trials, one of the circles has moved to another location for a fixed total of 40 pixels in a 360 degree direction.
+On the other 50% of the trials, all circles are still in the same location as the initial memory display.
+Participants have to indicate whether they think one of the circles changed location (by pressing the left-arrow key) or whether they think all circles are still in the same location (by pressing the right-arrow key).
+Note that the only potential difference between the memory and probe display is the displacement of **one** circle; the remaining circles are always in the same place and circles never change color within a trial.
+
+The change detection task starts with five practice trials in which participants receive performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
+After finishing the practice round, participants complete two test blocks consisting of 25 trials each (50 trials in total).
+The design is fully counterbalanced so that on each "movement" trial, each of the five circles changes five times per block for each of the five colors.
+Participants do not receive performance feedback during the two test blocks.
+
+### State anxiety {#state}
+
+We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory (STAI-S; @spielberger_1999).
+The STAI-S contains 20 short items measuring current anxiety rated on a scale of 1 (not al all) to 4 (very much so): 1) "I feel calm" (reversed); 2) "I feel secure" (reversed); 3) "I feel tense"; 4) "I feel strained"; 5) "I feel at ease" (reversed); 6) "I feel upset"; 7) "I am presently worrying over possible misfortunes"; 8) "I feel satisfied" (reversed); 9) "I feel frightened"; 10) "I feel comfortable" (reversed); 11) "I feel self-confident" (reversed); 12) "I feel nervous"; 13) "I am jittery"; 14) "I feel indecisive"; 15) "I am relaxed" (reversed); 16) "I feel content" (reversed); 17) "I am worried"; 18) "I feel confused"; 19) "I feel steady" (reversed); 20) "I feel pleasant" (reversed).
+
+An overall state anxiety variable was computed by averaging the 20 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+
+### Adversity {#adversity}
+
+All adversity questionnaires focused on experiences before age 13, which was defined as the "experiences during preschool, kindergarten, elementary school, and the start of middle school".
+
+#### Violence exposure{#violence}
+
+Violence exposure is measured using the Neighborhood Violence Scale (NVS; Frankenhuis & Bijlstra, 2018; Frankenhuis, de Vries, Bianchi, & Ellis, 2020) and two items assessing exposure to physical fights.
+The NVS contains seven items rated on a scale from 1 (never true) to 5 (very often true): 1) "I grew up in a safe neighborhood"; 2) "Crime was common in the neighborhood where I grew up"; 3) "In the neighborhood where I grew up, people had plenty of money" (reversed); 4) "In the neighborhood where I grew up, physical fights were common"; 5) "In the neighborhood where I grew up, shootings or stabbings occurred"; 6) "In the neighborhood where I grew up, most people felt unsafe walking alone after dark"; 7) "Where I grew up, it was important to be able to defend yourself against physical harm".
+The physical fighting items assessed witnessing fights: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
+
+An overall violence exposure variable was computed by separately standardizing the NVS (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `) and physical fighting items and averaging them together (*r* = `r #TBD `).
+
+#### Unpredictability {#unpred}
+
+Unpredictability was measured using two different scales: A scale of perceived childhood unpredictability used in previous research (@mittal_2015; @young_2018) and the Questionnaire of Unpredictability in Childhood (QUIC; @glynn_2019).
+The scale of perceived childhood unpredictability contains eight items rated on a scale of 1 (never true) to 5 (very often true): 1) "My family life was generally inconsistent and unpredictable from day-to-day"; 2) "My parent(s) frequently had arguments or fights with each other or other people in my childhood", 3) My parents had a difficult divorce or separation during this time"; 4) "People often moved in and out of my house on a pretty random basis"; 5) "When I woke up, I often didn't know what could happen in my house that day"; 6) "My family environment was often tense and "on edge""; 7) Things were often chaotic in my house"; 8) "I had a hard time knowing what my parent(s) or other people in my house were going to say".
+
+We included the QUIC because it captures several dimensions of environmental and household unpredictability with a better (but not perfect) distinction between items capturing more short-term unpredictability (i.e., on the level of seconds to minutes) and more long-term unpredictability (i.e., on the level of days to months (or longer)).
+Note that the scale of perceived childhood unpredictability combines items on a short-term scale (e.g., item 1) with items measured on a long-term scale (e.g., item 3) which might have different effects on the development of specific attention styles.
+the QUIC consists of 38 items across five subscales.
+Parental monitoring and involvement: 1) "I had a set morning routine on school days (i.e., I usually did the same thing each day to get ready)"; 2) "My parents kept track of what I ate (e.g., made sure that I didn’t skip meals or tried to make sure I ate healthy food)" (reversed); 3) "My family ate a meal together most days" (reversed); 4) "My parents tried to make sure I got a good night’s sleep (e.g., I had a regular bedtime, my parents checked to make sure I went to sleep)" (reversed); 5) "I had a bedtime routine (e.g, my parents tucked me in, my parents read me a book, I took a bath)" (reversed); 6) "In my afterschool or free time hours at least one of my parents knew what I was doing" (reversed); 7) "At least one of my parents regularly checked that I did my homework" (reversed); 8) "At least one of my parents regularly kept track of my school progress" (reversed); 9) "At least one parent made time each day to see how I was doing".
+Parental predictability: 1) "My parents were often very late to pick me up (e.g., from school, aftercare or sports)"; 2) "I usually knew when my parents were going to be home" (reversed); 3) "At least one of my parents had punishments that were unpredictable"; 4) "I often wondered whether or not one of my parents would come home at the end of the day"; 5) "My family planned activities to do together" (reversed); 6) "At least one of my parents would plan something for the family, but then not follow through with the plan"; 7) "My family had holiday traditions that we did every year (e.g., cooking a special food at a particular time of year/decorate the house the same way)" (reversed).
+8) "At least one of my parents was disorganized"; 9) "At least one of my parents was unpredictable"; 10) "For at least one of my parents, when they were upset I did not know how they would act"; 11) "One of my parents could go from calm to furious in an instant"; 12) "One of my parents could go from calm to stressed or nervous in an instant".
+Parental environment: 1) "There was a long period of time when I didn’t see one of my parents (e.g., military deployment, jail time, custody arrangements)"; 2) "I experienced changes in my custody arrangement"; 3) "At least one of my parents changed jobs frequently"; 4) "There were times when one of my parents was unemployed and couldn’t find a job even though he/she wanted one"; 5) "My parents had a stable relationship with each other" (reversed); 6) "My parents got divorced"; 7) "At least one of my parents had many romantic partners".
+Physical environment: 1) "There were often people coming and going in my house that I did not expect to be there"; 2) "I moved frequently"; 3) "I changed schools frequently"; 4) "I changed schools mid-year"; 5) "I lived in a clean house" (reversed); 6) I lived in a cluttered house (e.g., piles of stuff everywhere); 7) "In my house things I needed were often misplaced so that I could not find them".
+Safety and security: 1) "There was a period of time when I often worried that I was not going to have enough food to eat."; 2) "There was a period of time when I often worried that my family would not have enough money to pay for necessities like clothing or bills"; 3) "There was a period of time when I did not feel safe in my home".
+All items were endorsed as either "yes" or "no".
+
+We computed several unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overal QUIC variable as the sum of all 38 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales as the sum of their sub-items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `).
+
+#### Household chaos {#chaos}
+
+We assessed household chaos using the Confusion, Hubbub, and Order Scale (CHAOS; @matheny_1995).
+The CHAOS consists of 15 items rated on a scale of 1 (Never true) to 5 (Very often true).
+(Note that the original scale consists of binary "true" or "false" response options).
+The items were: 1) "There was very little commotion in our home", 2) "We could usually find things when we needed them"; 3) "We almost always seemed to be rushed"; 4) "We were usually able to stay on top of things"; 5) "No matter how hard we tried, we always seemed to be running late"; 6) "It was a real zoo in our home"; 7) "At home we could talk to each other without being interrupted"; 8) "There was often a fuss going on at our home"; 9) "No matter what our family planned, it usually didn't seem to work out"; 10) "You couldn't hear yourself think in our home"; 11) "I often got drawn into other people's arguments at home"; 12) "Our home was a good place to relax"; 13) "The telephone took up a lot of our time at home"; 14) "The atmosphere in our home was calm"; 15) "First thing in the day, we had a regular routine at home".
+
+An overall household chaos variable was computed by averaging the 15 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+
+### Temporal orientation {#temp_orientation}
+
+#### Impulsivity {#impulsivity}
+
+We assessed general impulsivity with the Motor Impulsivity subscale of the (Barrett Impulsivity Scale (BIS); @patton_1995; @spinella_2007).
+The Motor Impulsivity subscale of the BIS consists of five items rated on a scale of 1 (never true) to 5 (very often true): 1) "I do things without thinking"; 2) "I say things without thinking"; 3) "I act on the spur of the moment"; 4) "I buy things on impulse"; 5) "I act on impulse".
+
+An overall motor impulsivity variable was computed by averaging the 5 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+
+#### Future Orientation {#future_orientation}
+
+We assessed future orientation with an adapted version of the Future Orientation Scale (FOS; @steinberg_2009).
+The original scale consists of 15 sets of opposing items separated by "BUT" (e.g., "Some people like to plan things out one step at a time BUT other people like to jump right into things without planning them out beforehand").
+Participants first choose the item that best matches their general preference, and then indicate whether the statement is "really true" or "somewhat true".
+We adapted this format to a single statement per item (by picking each statement in the original right-hand column) presented in a first-person format in an attempt to reduce the cognitive load of the items.
+We were worried that people with less formal education or who were sitting in a noisier environment would struggle with the original items.
+The 15 adapted items were rated on a scale of 1 (never true) to 5 (very often true): 1) "I jump right into things without planning them beforehand"; 2) "I spend a lot of time thinking about how things might be in the future" (reversed); 3) "I don't think about every little possibility before making a decision"; 4) "When I act, I don't think about the consequences"; 5) "I give up my happiness now to get what I want in the future" (reversed); 6) "Making lists of things to do is a waste of time"; 7) "I usually make plans before going ahead with my decision" (reversed); 8) "I'd rather spend money right away than save it for a rainy day"; 9) "I am pretty good at seeing in advance how one thing can lead to another" (reversed); 10) "I think a lot about how my decisions will affect others" (reversed); 11) "I don't try to imagine what my life will be like in 10 years"; 12) "Things work out better if they are planned out in advance" (reversed); 13) "Breaking big projects down into small steps isn't really necessary"; 14) "I am always thinking about what tomorrow will bring" (reversed); 15) "It is best not to worry about things you can't predict".
+
+An overall future orientation variable was computed by averaging the 15 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+In addition, we calculated subscales for "Planning ahead" (items 1, 6, 7, 12 and 13), "Time Perspective" (items 2, 5, 8, 11 and 14) and "Anticipation of Future Consequences" (items 3, 4, 9, 10 and 15).
+
+### Psychopathology {#psychopathology}
+
+We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale (CESD; @radloff_1977).
+The scale consists of 20 items rated from 1 (rarely or none of the time (less than 1 day)) to 4 (most or all of the time (5-7 days)): 1) "I was bothered by things that usually don't bother me"; 2) "I did not feel like eating; my appetite was poor"; 3) "I felt that I could not shake off the blues even with help from my family and friends"; 4) "I felt that I was just as good as other people" (reversed); 5) "I had trouble keeping my mind on what I was doing"; 6) "I felt depressed"; 7) "I felt that everything I did was an effort"; 8) "I felt hopeful about the future" (reversed); 9) "I thought my life had been a failure"; 10) "I felt fearful"; 11) "My sleep was restless"; 12) I was happy" (reversed); 13) "I talked less than usual"; 14) "I felt lonely"; 15) "People were unfriendly"; 16) "I enjoyed life" (reversed); 17) "I had crying spells"; 18) "I felt sad"; 19) "I felt that people dislike me"; 20) "I could not get 'going'".

### 2021-10-20 preregistration/preregistration_analyses.Rmd
update to preregistration

@@
 output:
-  word_document: default
-  pdf_document: default
   officedown::rdocx_document:
@@
         style: Table Caption
+  pdf_document: default
+  word_document: default
 ---
+
+(Note: This document doubles as a preregistration of the pilot study.
+It was written as a dynamic document with analysis code prior to data collection.
+For a full history of this document, see the [Open Science Framework (OSF) link](https://osf.io/gfpnr/) to this project).
+See also the [github link](https://github.com/StefanVermeent/attention_pilot) embedded in the OSF project for a full history of the document)
 
@@
 
-we focus on two aspects of external attention [i.e., attention pointed at the external environment; @chun_2011] that we expect to develop in harsh and unpredictable environments: 1) A relatively wider scope of attention and 2) an increased sensitivity to subtle changes in the environment.
+We focus on two aspects of external attention [i.e., attention pointed at the external environment; @chun_2011] that we expect to develop in harsh and unpredictable environments: 1) A relatively wider scope of attention and 2) an increased sensitivity to subtle changes in the environment.
 When might these attention styles develop in adverse environments?
@@
 
-The current pilot study had two primary aims: First, we tested whether people from harsh and unpredictable environments would perform better on attention tasks favor a broad attention scope and a sensitivity to subtle changes.
+The current pilot study had two primary aims: First, we tested whether people from harsh and unpredictable environments would perform better on attention tasks that favor a broad attention scope and a sensitivity to subtle changes.
 To this end, participants completed three attention tasks that differed in the extent to which they would favor or punish these attention features.
-Second,
-we investigated the link between adversity and attention both in a traditional analysis of reaction times, as well as by using the Drift Diffusion Model [DDM; @forstmann_2016; @ratcliff_2015; @ratcliff_2008] to more precisely disentangle the underlying cognitive processes.
+Second, we investigated the link between adversity and attention both in a traditional analysis of reaction times, as well as by using the Drift Diffusion Model [DDM; @forstmann_2016; @ratcliff_2015; @ratcliff_2008] to more precisely disentangle the underlying cognitive processes (for more details on the DDM analysis, see the [analyses](#analyses) section).
 
-Our confirmatory hypotheses were as follows:
-1)
+Our primary hypotheses were as follows:
 
-In addition, the pilot study had two secondary aims: First, we investigated whether the link between measures of adversity and attention would be contingent on the timescale of the adversity items.
-More specifically, we expected stable attention styles to be better predicted by items of momentary unpredictability (e.g., "things were often chaotic in my house") than by items of temporally extended unpredictability ("At least one of my parents changed jobs frequently").
+1) People with more exposure to violence and environmental unpredictability during childhood will show enhanced or equal performance compared to people from safe environments on tasks that require quickly detecting peripheral stimuli and detecting subtle changes (i.e., the Cued Attention Task and Change Detection Task).
+This effect is at least partly explained by an increased drift rate in the DDM analysis
+
+2) People with more exposure to violence and environmental unpredictability during childhood will perform worse on tasks that require ignoring distracting peripheral stimuli (i.e., the Flanker Task).
+This effect is at least partly explained by a wider initial attentional focus, as quantified by an SDDM analysis.
+
+In addition, the pilot study had a number secondary aims: First, we investigated whether the link between measures of adversity and attention would be contingent on the timescale of the adversity items.
+More specifically, we explored whether stable attention styles might be better predicted by items of momentary unpredictability (e.g., "things were often chaotic in my house") than by items of temporally extended unpredictability ("At least one of my parents changed jobs frequently").
 Second, we conducted exploratory correlation analyses between measures of adversity, attention, and measures of temporal orientation (i.e., impulsivity and future orientation).
+Third, we explored whether potential effects of adversity on task performance might be moderated by current states of anxiety, hunger, or sleep deprivation.
+Fourth, we explored the extent to which our retrospective measures of adversity correlate with current depressive symptoms, which could be a potential confound [@nivison_2021].
 
@@
 Participants were XXX US-based individuals between the ages of 18 and 30 (*M* = `r #TBD`, *SD* = `r #TBD`).
-We decided for this age cut-off to limit the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 (@salthouse_2010).
+We decided for this age cut-off to limit the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 [@salthouse_2010].
 Recruitment took place through Prolific.
 Participants were eligible for for the study if they were between 18 and 30 years old, if English was their primary language, if they were currently residing in the United States, if they did not have a history of brain injury, if they did not have color blindness, and if they had normal or corrected-to-normal eyesight.
+
+The sample size was determined by a [preregistered power analysis](https://osf.io/gfpnr/))).
+[...]
 
@@
 For the Drift Diffusion analyses, it is important that each response is generated by a diffusion process (as opposed to, for example, guessing).
-To this end, trials with reaction times < 250ms  or longer than 3500ms (@ratcliff_2015) were excluded from the analyses (*N* = `r #TBD `).
+To this end, trials with reaction times < 250ms or longer than 3500ms [@ratcliff_2015] were excluded from the analyses (*N* = `r #TBD `).
 Participants for whom more than 10 trials were removed were excluded from the analyses (N = `r #TBD `).
@@
 
-### Attention tasks {#tasks}
+The attention tasks were programmed in JsPsych version 3.6.1 [@deLeeuw_2015].
 
-The attention tasks were programmed in JsPsych version 3.6.1 (@deLeeuw_2015).
+### Cued attention task {#cued_attention}
 
-#### Cued attention task {#cued_attention}
-
-The cued attention task is an adaptation of the Posner task (@posner_1980).
+The cued attention task is an adaptation of the Posner task [@posner_1980].
 On each trial, a left- or right-pointing arrow is presented in one of eight random locations at a distance of 300 pixels from the center of the screen (see Figure 1B).
@@
 
-The average reaction time for each participant was calculated separately for cued and neutral trials based on correct trials only.
-If necessary for meeting model assumptions, reaction times were log-transformed.
-We did not plan on conducting analyses on the proportion of errors as error rates are generally very low on similar Cued Attention Tasks (i.e., < 5% of trials).
+### Flanker task {#flanker}
 
-#### Flanker task {#flanker}
-
-On each trial of the Flanker task (@eriksen_1974), participants are presented with a set of five arrows pointing either left or right.
+On each trial of the Flanker task [@eriksen_1974], participants are presented with a set of five arrows pointing either left or right.
 Their job is to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right (see Figure 1A).
@@
 
-The average reaction time for each participant was calculated separately for congruent and incongruent trials based on correct trials only.
-If necessary for meeting model assumptions, reaction times were log-transformed.
-We did not plan on conducting analyses on the proportion of errors as error rates are generally very low on the Flanker task, especially on the congruent trials (i.e., < 5% of trials).
-
-The DDM analysis of the Flanker task was done using an adaptation of the standard DDM that was specifically developed to account for Flanker data: The Spotlight Drift Diffusion Model (SDDM; @grange_2016; @white_2018a; @white_2018b, @white_2011).
-The standard DDM model assumes a stable drift rate over time within trials (i.e., the rate of information accumulation does not change over time).
-However, on the Flanker Task, reaction time patterns indicate that the drift rate increases over time, thus violating the basic assumption of the standard DDM (@white_2011).
-The SDDM assumes that attention on the Flanker task works like a spotlight that starts relatively broad, and then gradually narrows down to the central arrow over time.
-Each arrow provides perceptual input *p*.
-If the flanking arrows are congruent, all flankers take a positive value for *p*; if the flanking arrows are incongruent, they take a negative value for *p* while the central arrow takes a positive value.
-The drift rate (*v*) at each time point is the function of the strength of perceptual input *p* multiplied by the amount of attention focused on each arrow.
-Attention is operationalized by two additional parameters: the initial width of the attentional spotlight (*SD~a~*) and the shrinking rate of the attentional spotlight (*rd*).
-The attentional spotlight is assumed to be normally distributed over the arrows, with relatively more attention paid to the arrows at the center and relatively less attention paid to the peripheral arrows.
-Over time, this normal distribution (*SD~a~*) narrows down to the central arrow at the rate specified by *rd*, thereby gradually decreasing the interfering effect of the flanking arrows.
-Note that the SDDM is based on a combined analysis of congruent and incongruent trials.
-See Figure 1B for a visualization of the SDDM.
-
-Previous research has shown that it is not useful to interpret both *SD~a~* and *rd* since they trade-off against each other (i.e., a wide initial spotlight combined with a large shrinking rate leads to similar patterns as a narrow initial spotlight combined with a low shrinking rate; @white_2018a; @white_2011).
-Most previous studies have fixed *SD~a~* and only estimated *rd*, or calculated a *SD~a~*/*rd* ratio, which serves as a measure of interference.
-However, our primary interest lies in the initial width of the attentional spotlight, which we hypothesize to be wider for people from harsh and unpredictable environments compared to people from safe and predictable environments.
-In this pilot study, we fit several SDDM models either estimating both attention parameters or fixing *rd* to see how it affected model fit (more details below).
-
-#### Change detection task {#change}
+### Change detection task {#change}
 
@@
 
-We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory (STAI-S; @spielberger_1999).
+We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [STAI-S; @spielberger_1999].
 The STAI-S contains 20 short items measuring current anxiety rated on a scale of 1 (not al all) to 4 (very much so): 1) "I feel calm" (reversed); 2) "I feel secure" (reversed); 3) "I feel tense"; 4) "I feel strained"; 5) "I feel at ease" (reversed); 6) "I feel upset"; 7) "I am presently worrying over possible misfortunes"; 8) "I feel satisfied" (reversed); 9) "I feel frightened"; 10) "I feel comfortable" (reversed); 11) "I feel self-confident" (reversed); 12) "I feel nervous"; 13) "I am jittery"; 14) "I feel indecisive"; 15) "I am relaxed" (reversed); 16) "I feel content" (reversed); 17) "I am worried"; 18) "I feel confused"; 19) "I feel steady" (reversed); 20) "I feel pleasant" (reversed).
@@
 
-### Adversity {#adversity}
+### Violence exposure {#violence}
 
-All adversity questionnaires focused on experiences before age 13, which was defined as the "experiences during preschool, kindergarten, elementary school, and the start of middle school".
-
-#### Violence exposure{#violence}
-
-Violence exposure is measured using the Neighborhood Violence Scale (NVS; Frankenhuis & Bijlstra, 2018; Frankenhuis, de Vries, Bianchi, & Ellis, 2020) and two items assessing exposure to physical fights.
+Violence exposure was measured using the Neighborhood Violence Scale [NVS; Frankenhuis & Bijlstra, 2018; Frankenhuis, de Vries, Bianchi, & Ellis, 2020] and two items assessing exposure to physical fights before age 13.
 The NVS contains seven items rated on a scale from 1 (never true) to 5 (very often true): 1) "I grew up in a safe neighborhood"; 2) "Crime was common in the neighborhood where I grew up"; 3) "In the neighborhood where I grew up, people had plenty of money" (reversed); 4) "In the neighborhood where I grew up, physical fights were common"; 5) "In the neighborhood where I grew up, shootings or stabbings occurred"; 6) "In the neighborhood where I grew up, most people felt unsafe walking alone after dark"; 7) "Where I grew up, it was important to be able to defend yourself against physical harm".
@@
 
-#### Unpredictability {#unpred}
+### Unpredictability {#unpred}
 
-Unpredictability was measured using two different scales: A scale of perceived childhood unpredictability used in previous research (@mittal_2015; @young_2018) and the Questionnaire of Unpredictability in Childhood (QUIC; @glynn_2019).
+Unpredictability before age 13 was measured using two different scales: A scale of perceived childhood unpredictability used in previous research [@mittal_2015; @young_2018] and the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019].
 The scale of perceived childhood unpredictability contains eight items rated on a scale of 1 (never true) to 5 (very often true): 1) "My family life was generally inconsistent and unpredictable from day-to-day"; 2) "My parent(s) frequently had arguments or fights with each other or other people in my childhood", 3) My parents had a difficult divorce or separation during this time"; 4) "People often moved in and out of my house on a pretty random basis"; 5) "When I woke up, I often didn't know what could happen in my house that day"; 6) "My family environment was often tense and "on edge""; 7) Things were often chaotic in my house"; 8) "I had a hard time knowing what my parent(s) or other people in my house were going to say".
@@
 
-#### Household chaos {#chaos}
+### Household chaos {#chaos}
 
-We assessed household chaos using the Confusion, Hubbub, and Order Scale (CHAOS; @matheny_1995).
+We assessed household chaos before age 13 using the Confusion, Hubbub, and Order Scale [CHAOS; @matheny_1995].
 The CHAOS consists of 15 items rated on a scale of 1 (Never true) to 5 (Very often true).
@@
 
-### Temporal orientation {#temp_orientation}
+### Impulsivity {#impulsivity}
 
-#### Impulsivity {#impulsivity}
-
-We assessed general impulsivity with the Motor Impulsivity subscale of the (Barrett Impulsivity Scale (BIS); @patton_1995; @spinella_2007).
+We assessed general impulsivity with the Motor Impulsivity subscale of the [Barrett Impulsivity Scale (BIS); @patton_1995; @spinella_2007].
 The Motor Impulsivity subscale of the BIS consists of five items rated on a scale of 1 (never true) to 5 (very often true): 1) "I do things without thinking"; 2) "I say things without thinking"; 3) "I act on the spur of the moment"; 4) "I buy things on impulse"; 5) "I act on impulse".
@@
 
-#### Future Orientation {#future_orientation}
+### Future Orientation {#future_orientation}
 
-We assessed future orientation with an adapted version of the Future Orientation Scale (FOS; @steinberg_2009).
+We assessed future orientation with an adapted version of the Future Orientation Scale [FOS; @steinberg_2009].
 The original scale consists of 15 sets of opposing items separated by "BUT" (e.g., "Some people like to plan things out one step at a time BUT other people like to jump right into things without planning them out beforehand").
@@
 
-### Psychopathology {#psychopathology}
+### Depressive symptoms {#depression}
 
-We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale (CESD; @radloff_1977).
+We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD; @radloff_1977].
 The scale consists of 20 items rated from 1 (rarely or none of the time (less than 1 day)) to 4 (most or all of the time (5-7 days)): 1) "I was bothered by things that usually don't bother me"; 2) "I did not feel like eating; my appetite was poor"; 3) "I felt that I could not shake off the blues even with help from my family and friends"; 4) "I felt that I was just as good as other people" (reversed); 5) "I had trouble keeping my mind on what I was doing"; 6) "I felt depressed"; 7) "I felt that everything I did was an effort"; 8) "I felt hopeful about the future" (reversed); 9) "I thought my life had been a failure"; 10) "I felt fearful"; 11) "My sleep was restless"; 12) I was happy" (reversed); 13) "I talked less than usual"; 14) "I felt lonely"; 15) "People were unfriendly"; 16) "I enjoyed life" (reversed); 17) "I had crying spells"; 18) "I felt sad"; 19) "I felt that people dislike me"; 20) "I could not get 'going'".
+
+## Data analyses
+
+### Reaction Times
+
+For the Cued Attention Task and Flanker Task, average reaction times per participant were calculated separately for each condition (cued/neutral trials and incongruent/congruent trials, respectively).
+For the change detection task, we calculated an average reaction time across all trials.
+If necessary for meeting model assumptions, reaction times were log-transformed.
+We did not plan on conducting analyses on the proportion of errors as error rates are generally very low on similar Cued Attention and Flanker tasks (i.e., < 5% of trials).
+Note that the DDM analysis provides a full breakdown of performance both in terms of reaction times and accuracy.
+
+For the Cued Attention Task and Flanker Task, we performed a set of linear mixed effects analyses to test adversity X condition interactions on mean RTs.
+All models included a random intercept for participants.
+Across separate models, adversity was operationalized as childhood violence exposure and childhood unpredictability.
+For violence exposure, we used aggregated violence exposure variable.
+For unpredictability, we used the
+
+The effect of different dimensions of adversity on mean RTs was assessed both using linear mixed effects models (for the Cued Attention Task and the Flanker Task) and linear regressions (Change Detection Task).
+
+For the Cued Attention Task and the Flanker Task, we performed a set of linear mixed effects analyses separately for different measures of adversity and task condition (cued vs.
+neutral) as well their interaction.
+For
+
+The models included a random intercept for participants. The adversity measures included as independent variables were
+
+### Drift Diffusion Model
+
+The Drift Diffusion Model (DDM; @ratcliff_2008; @ratcliff_2015) is a cognitive model that accounts for the fundamental cognitive processes underlying two-alternative forced-choice paradigms (2-AFC; see Figure XXX).
+The model assumes that the decision-making process constitutes a noisy information accumulation process that continues until one of two decision boundaries (corresponding to one of two response options) is reached.
+As soon as the accumulation process reaches a decision boundary, the process terminates and a motor response is initiated.
+The DDM computes four parameters that map onto distinct cognitive processes [@voss_2004].
+The accumulation process is modeled as a drift rate (*v*), reflecting basic cognitive speed.
+large values of *v* reflect more efficient processing (faster and more accurate).
+Unless people are biased to favor one response over the other (e.g., due to a skewed reward structure), the starting point (*z*) of the accumulation process is usually fixed to be equidistant from both decision boundaries (*a*).
+larger values of *a* reflect more conservative responses (slower but more accurate) while smaller values of *a* reflect more liberal responses (faster but less accurate).
+The fourth and final parameter is the non-decision time (*Ter*), which includes a collection of processes that are not related to the decision process (e.g., initial stimulus encoding and initiating the motor response).
+Importantly, the DDM parameters account for the full pattern of correct RTs, incorrect RTs, and proportion of errors.
+
+The DDM is fit separately to the data of each participant.
+For the data of the Change Detection Task and the Cued Attention Task, the DDM was fit using Fast-dm [@voss_2007].
+We used Maximum Likelihood estimation as it has been shown to provide reliable estimates with relatively few trials [@lerche_2017; see also our power simulations on [OSF](https://osf.io/gfpnr/)].
+*a*, *v* and *Ter* were freely estimated and *z* was fixed to 0.5 (the midpoint).
+In addition, all inter-trial variability parameters were fixed to 0 to increase model parsimony.
+For the Cued Attention Task, the DDM was fit separately to data of the cued and neutral condition.
+For the Change Detection task, the DDM was fit to all trials.
+
+The DDM analysis of the Flanker task was done using an adaptation of the standard DDM that was specifically developed to account for Flanker data: The Spotlight Drift Diffusion Model [SDDM; @grange_2016; @white_2018a; @white_2018b, @white_2011].
+The standard DDM model assumes a stable drift rate over time within trials (i.e., the rate of information accumulation does not change over time).
+However, on the Flanker Task, reaction time patterns indicate that the drift rate increases over time, thus violating the basic assumption of the standard DDM [@white_2011].
+The SDDM explains this pattern by assuming that attention on the Flanker task works like a spotlight that starts relatively broad, and then gradually narrows down to the central arrow over time.
+Each arrow provides perceptual input *p*.
+If the flanking arrows are congruent, all flankers take a positive value for *p*; if the flanking arrows are incongruent, they take a negative value for *p* while the central arrow takes a positive value.
+The drift rate (*v*) at each time point is the function of the strength of perceptual input *p* multiplied by the amount of attention focused on each arrow.
+Attention is operationalized by two additional parameters: the initial width of the attentional spotlight (*SD~a~*) and the shrinking rate of the attentional spotlight (*rd*).
+The attentional spotlight is assumed to be normally distributed over the arrows, with relatively more attention paid to the arrows at the center and relatively less attention paid to the peripheral arrows.
+Over time, this normal distribution (*SD~a~*) narrows down to the central arrow at the rate specified by *rd*, thereby gradually decreasing the interfering effect of the flanking arrows.
+Note that the SDDM is based on a combined analysis of congruent and incongruent trials.
+See Figure 1B for a visualization of the SDDM.
+
+Previous research has shown that it is not useful to interpret both *SD~a~* and *rd* since they trade-off against each other [i.e., a wide initial spotlight combined with a large shrinking rate leads to similar patterns as a narrow initial spotlight combined with a low shrinking rate; @white_2018a; @white_2011].
+Most previous studies have fixed *SD~a~* and only estimated *rd*, or calculated a *SD~a~*/*rd* ratio, which serves as a measure of interference.
+However, our primary interest lies in the initial width of the attentional spotlight, which we hypothesize to be wider for people from harsh and unpredictable environments compared to people from safe and predictable environments.
+In this pilot study, we fitted several SDDM models either estimating both attention parameters or fixing *rd* to see how it affected model fit (more details below).
+Model fit was done using the `flankr` package in R [@grange_2016].
+
+### Effect of adversity on task performance
+
+The effect of different dimensions of adversity on attention task performance was assessed both using linear mixed effects models (for the Cued Attention Task) and linear regressions (for the Flanker Task and the Change Detection Task).
+Dependent variables were mean RTs and DDM parameters.
+While our hypotheses were specific to DDM parameters *v* (for the Flanker Task and the Change Detection Task) and *SD~a~*, we repeated the analyses using DDM parameters *a* and *Ter* (but not *z*), and SDDM parameters *a*, *p*, *Ter* and *SD~a~*/*rd* (but not *rd*).
+
+For the Cued Attention Task, we performed a set of linear mixed effects analyses separately for different measures of adversity and task condition (cued vs. neutral) as well their interaction. For
+
+The models included a random intercept for participants. The adversity measures included as independent variables were
+
+### Secondary analyses
+
+We computed Pearson correlations between all adversity measures, temporal orientation measures, state measures, and attention tasks..

### 2021-10-20 tasks/attention_cueing/1_attention_cueing_instructions.js

@@ -12,17 +12,33 @@ var cueing_welcome = {
   data: {variable: 'welcome', task: "cueing"}
 };
 
-
 //-------------------- Instructions
 var cueing_instructions1 = {
   type: 'instructions',
   pages: [
-    "<p style = 'text-align: left; padding: 0 20% 0 20%;'>"+ 
-      "You will be playing the <strong>Arrow Detection</strong> game.<br><br>" + 
-      "In this game, a left arrow (<) or right arrow (>) will be presented in one of nine locations around the center of the screen.<br>" +
-      "Your job is to indicate the direction of the arrow.<br>" +
-      "If the arrow points left, press the (&larr;) arrow on your keyboard. If the arrow points right, press the (&rarr;) arrow.<br><br><br>" +
-      "Click the 'continue' button for the next page of instructions.</p>"
+    "<p style = 'text-align: center;'>" + 
+      "In this game, an arrow will appear somewhere on the screen.<br><br>" +
+      "Your job is to figure out in which direction the arrow is pointing.<br><br><br>",
+      
+    "<p style = 'text-align: center;'>" + 
+      "Each round has three parts.<br><br><br>" +
+      "<img width = 600 src = 'img/instructions1.png'></img><br><br>",
+    
+    "<p style = 'text-align: center;'>" +   
+      "Sometimes the * will appear in the middle.<br><br>" +
+      "Other times it will appear <strong>in the same place as the arrow.</strong><br><br><br>" +
+      "<img width = 490 src = 'img/instructions2.png'></img><br><br><br>",
+      
+    "<p style = 'text-align: center;'>" + 
+      "When the arrow appears, press the arrow key that matches its direction.<br><br>" +
+      "<div style = 'float: left;'>If it points LEFT<br>press the LEFT (<) key.</div>" +
+      "<div style = 'float: right;'>If it points RIGHT<br>press the RIGHT (>) key.</div><br><br><br><br>" + 
+      "For example, you would press the left key for the arrow below.<br><br><br>" + 
+      "<img width = 160 src = 'img/instructions3.png'></img><br><br><br>",
+      
+   "<p style = 'text-align: center;'>" +    
+      "Click the 'continue' button to practice the<br><strong>Arrow Detection</strong> game.",
+      
   ],
   show_clickable_nav: true,
   allow_backward: true,

### 2021-10-20 tasks/flanker/1_flanker_instructions.js

@@ -2,7 +2,7 @@
 var flanker_welcome = {
   type: 'instructions',
   pages: [
-    "Welcome to the <b>Flanker</b> game!"
+    "Welcome to the <b>Arrow</b> game!"
   ],
   show_clickable_nav: true,
   allow_backward: true,
@@ -16,15 +16,33 @@ var flanker_welcome = {
 var flanker_instructions = {
   type: 'instructions',
   pages: [
-    "<p style = 'text-align: left; padding: 0 20% 0 20%;'>"+ 
-      "You will be playing the <strong>Flanker</strong> game.<br><br>" + 
-      "In this game you will see groups of five arrows pointing left or right (e.g., &larr;&larr;&larr;&larr;&larr;, or &rarr;&rarr;&rarr;&rarr;&rarr;).<br>" +
-      "Your job is to indicate the direction of the <strong>central</strong> arrow, while ignoring the others.<br><br>" +
-      "On some rounds, the surrounding arrows will point in the same direction as the central arrow. On other rounds, they will point in the opposite direction.<br><br>" +
-      "If the central arrow points left, press the (&larr;) arrow. If the central arrow points right, press the (&rarr;) arrow.<br><br>" +
-      "Please try to respond as quickly and accurately as possible.<br><br>"+
+    "<p style = 'text-align: center;'>"+ 
+      "In this game, you will see five arrows like the ones below.<br><br><br>" +
+      "<div style = 'font-size: 30px'>&larr;&larr;&larr;&larr;&larr;</div><br><br><br>" +
+      "Your job is to figure out which direction the <strong>central arrow</strong> is pointing.<br><br><br>",
       
-      "Click the 'continue' button to practice the <strong>Flanker</strong> game.<br></p>"
+     "<p style = 'text-align: center;'>"+ 
+      "Sometimes all the arrows point in the <strong>same</strong> direction.<br><br><br>" +
+      "<div style = 'font-size: 30px'>&larr;&larr;&larr;&larr;&larr;</div><br><br><br>",
+      
+     "<p style = 'text-align: center;'>"+ 
+      "Other times the arrows point in the <strong>different</strong> direction.<br><br><br>" +
+      "<div style = 'font-size: 30px'>&larr;&larr;&rarr;&larr;&larr;</div><br><br><br>",  
+      
+      "<p style = 'text-align: center;'>"+ 
[…]

### 2021-10-20 tasks/flanker/2_flanker_procedure.js

@@ -18,7 +18,7 @@ var flanker_present_arrows = {
     }
   }
   }
-}
+};
 
 
 var flanker_test_procedure = {

### 2021-10-26 manuscript/preregistration.Rmd
#prereg updated intermediate version of prereg

---
bibliography: references.bib
csl: apa.csl
output:
  officedown::rdocx_document:
    page_margins:
      bottom: 1
      footer: 0
      gutter: 0
      header: 0.5
      left: 1
      right: 1
      top: 1
    plots:
      align: center
      caption:
        pre: 'Figure '
        sep: '. '
        style: Image Caption
    reference_docx: reference-doc.docx
    tables:
      caption:
        pre: 'Table '
        sep: '. '
        style: Table Caption
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}

# Load libraries
library(tidyverse)
library(officer)
library(flextable)
library(here)

## Custom function to restart numbering at the start of each new chapter.
new_chapter <- function(){
  if(!exists("chapter_count")) chapter_count <<- 0 
  chapter_count <<- chapter_count + 1
  }

# set up chunk options
knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "!t", 
  out.extra = "",
  fig.show = "asis",
  message = FALSE,
  warning = FALSE
)

# set up flextable for tables
set_flextable_defaults(
  font.family = "Times", 
  font.size = 10,
  font.color = "black",
  line_spacing = 1,
  padding.bottom = 1, 
  padding.top = 1,
  padding.left = 1,
  padding.right = 1
)

# Source necessary objects
codebook = read_csv(here("data", "1_pilot_data", "clean", "pilot_self_report_codebook.csv"))
pilot_self_report = read_csv(here("data", "1_pilot_data", "clean", "pilot_self_report.csv"))
```

(Note: This document was written as a dynamic R Markdown document. The current version was submitted as a time-stamped **Preregistration** of the pilot study on <DATE>. In later versions in time, it will be extended to incorporate the results and discussion based on the pilot data, as well as potential deviations from the current preregistration and additional preregistrations. For an overview of all major versions of the document (e.g., from preregistration to (potential) deviations from the preregistration to final manuscript version), see the [overview of preregistrations and milestones on github](https://github.com/StefanVermeent/attention_pilot/Preregistrations_and_Milestones.xlsx)).

# Introduction and hypotheses

Experiencing childhood adversity is widely thought to have detrimental effects on a range of cognitive and behavioral outcomes. Findings in line with this deficit model have been extensively documented (). Recent years have seen the development of the complimentary hidden talents approach, which emphasizes the specific skills that people might develop in harsh environments through cognitive adaptations. However, it remains largely unclear which mechanisms drive specific enhancements and impairments of cognitive abilities. In this pilot study, we test the idea that people who grow up in adversity tend to develop a present-focused attention style, with features that benefit performance on some cognitive tasks but hurt performance on others.

In line with previous theorizing [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013], we expect stress-adapted cognitive styles to be characterized by a strong focus on the present. By cognitive style we mean a collection of relatively stable information processing tendencies (e.g., speed of processing, focus of attention, goal-directed behavior) that together determine how people interact with their environment. Over time, a tendency to focus on the here-and-now might lead to a stable external attention style [i.e., attention pointed at the external environment; @chun_2011], while less attention is paid to internal processes (e.g., goal-directed behavior, memory retrieval). Previous studies focusing on attentional processes in people from adversity suggest that adversity exposure impairs attention (.., but see ..). However, most of these studies measure attention either indirectly through subjective parent reports, or using "executive attention" tasks which involve executive processes such as inhibiting responses and actively maintaining a complex task goal. Conversely, studies focusing on more basic processes tend to focus on attention for and processing of threatening stimuli such as angry faces [e.g., @pollak_2002; @thompson_2021]. Therefore, it remains largely unclear whether adversity shapes more basic and stable (i.e., context-independent) attention styles.

Here, we focus on two aspects of external attention that we expect to develop in harsh and unpredictable environments: 1) A relatively wider scope of attention and 2) an increased sensitivity to subtle changes in the environment. When might these attention styles develop in adverse environments? Attention is involved in information processing on a timescale of seconds to minutes; Focusing attention for longer periods on a single stimulus is impossible for most people [@warm_2008]. Thus, stable attention styles are most useful in response to environmental features that unfold on the same timescale. Factors such as changes in adult household members or frequently moving homes, which are often used as proxies for unpredictability, are unlikely to shape stable attentional styles as they unfold over days or weeks. In addition, any threats that are spatially or temporally predictable (e.g., a specific part of the neighborhood that is known to be dangerous or might be especially dangerous at night) are more likely to lead to signal- or cue-based changes in cognitive processing. Instead, a cognitive style that systematically favors external attention over internal attention should develop when threats are frequent and the environment is chaotic, such that past states of the environment are not predictive of the current state [@emond_2020; @young_2020]. In such an environment, threats might arise at any time and the occasional reward might be fleeting [@ellis_2009; @frankenhuis_2016]. In the absence of reliable cues, a person would benefit from having their attention fixated broadly on the external environment, so that threats and opportunities can be anticipated and dealt with as soon as they appear.

The current pilot study had two primary aims: First, we tested whether people from harsh and unpredictable environments would perform better on attention tasks that favor a broad attention scope and a sensitivity to subtle changes. To this end, participants completed three attention tasks that differed in the extent to which they would favor or punish these attention features. Second, we investigated the link between adversity and attention both in a traditional analysis of reaction times, as well as by using the Drift Diffusion Model [DDM; @forstmann_2016; @ratcliff_2015; @ratcliff_2008] to more precisely disentangle the underlying cognitive processes (for more details on the DDM analysis, see the [Data analyses]{#ddm_plan} section).

Our primary hypotheses were as follows:

1) People with more exposure to violence and environmental unpredictability during childhood will show enhanced or equal performance compared to people from safe environments on tasks that require quickly detecting peripheral stimuli and detecting subtle changes (i.e., the Cued Attention Task and Change Detection Task). This effect is at least partly explained by the speed of information uptake (operationalized through the drift rate parameter of the DDM).

2) People with more exposure to violence and environmental unpredictability during childhood will perform worse on tasks that require ignoring distracting peripheral stimuli (i.e., the Flanker Task). This effect is at least partly explained by a wider initial attentional focus, (operationalized through the attentional width parameter of the Spotlight DDM (SDDM) analysis).

In addition, the pilot study had a number of secondary aims: First, we investigated whether the link between measures of adversity and attention would be contingent on the timescale of the adversity items. More specifically, we explored whether stable attention styles might be better predicted by items of momentary unpredictability (e.g., "things were often chaotic in my house") than by items of temporally extended unpredictability ("At least one of my parents changed jobs frequently"). Second, we conducted exploratory correlation analyses between measures of adversity, attention, and measures of temporal orientation (i.e., impulsivity and future orientation). Third, we explored whether potential effects of adversity on task performance might be moderated by current states of anxiety, hunger, or sleep deprivation. Fourth, we explored the extent to which our retrospective measures of adversity correlate with current depressive symptoms, which might reflect a retrospective negativity bias driven by current psychopathological symptoms [@nivison_2021].

# Methods {#methods}

## Participants {#participants}

Participants were XXX US-based individuals between the ages of 18 and 30 (*M* = `r #TBD`, *SD* = `r #TBD`). We decided for this age cut-off to limit the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 [@salthouse_2010]. Recruitment took place through Prolific. Participants were eligible for for the study if they were between 18 and 30 years old, if they were currently residing in the United States, if they did not have a history of brain injury, and if they had normal or corrected-to-normal eyesight.

The sample size was determined by a [preregistered power analysis](https://osf.io/gfpnr/))).
[...]

## Exclusion criteria {#exclusion}

We applied several exclusion criteria prior to analyzing the data. First, we excluded participants with incomplete data on any of the attention tasks (*N* = `r #TBD `). Second, we analyzed responses to the attention checks and reversed coded items in the questionnaire part of the experiment. We excluded participants if they missed both attention check items or if they had suspicious response patterns (e.g., consistently endorsing high response options even when some items were reversed coded) (*N* = `r #TBD `).

In addition, we screened the reaction times on each of the three attention tasks. For the Drift Diffusion analyses, it is important that each response is generated by a process of active information accumulation (i.e., a diffusion process, as opposed to guessing). To this end, trials with reaction times < 250ms or longer than 3500ms [@ratcliff_2015] were excluded from the analyses (*N* = `r #TBD `). Participants with more than 10 removed trials were excluded from the analyses (N = `r #TBD `).

## Procedure {#procedure}

The experiment was completed on the participants' own laptop or desktop computer and consisted of four parts: written consent, attention task battery, questionnaire battery, brief demographics form, and final checks and the opportunity to give feedback on the experiment. [something on ethical approval].

After providing consent, participants started with the three attention tasks. They were asked to complete the attention tasks in a quiet room in the house where they would be least likely to be distracted by other people or outside noises. The order of the tasks was counterbalanced between subjects. At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs. The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych. Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the creditcard. The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants. After succesfully resizing the screen, participants completed all three tasks. Whenever participants had to respond by use of their keyboard, the cursor was hidden from the screen to minimize distractions. Code for the three tasks can be found on [Github](https://github.com/StefanVermeent/attention_pilot/tree/main/tasks).

After completing the attention tasks, participants completed the questionnaire battery in the following fixed order: 1) Current state (state anxiety and separate questions relating to specific states); 2) Childhood adversity (perceived unpredictability, perceived socio-economic status, exposure to violence and physical fights, household chaos); 3) Temporal orientation (impulsivity, future orientation); 4) Depressive symptoms.

Finally, the demographics questions asked about the participant's age, weight, height, physical activity, sex at birth, gender, ethnicity, social class (current and during childhood), education level (one's own as well as parents' education level), occupation, and household income. At the end of the experiment, we asked participants if they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.

## Measures {#measures}

The attention tasks were programmed in JsPsych version 3.6.1 [@deLeeuw_2015].

### Cued attention task {#cued_attention}

The cued attention task was an adaptation of the Posner task [@posner_1980]. On each trial, a left- or right-pointing arrow is presented in one of eight random locations at a distance of 300 pixels from the center of the screen (see Figure 1B). Participants had to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard. On 50% of the trials, the arrow was preceded by a cue ("\*") in the exact same location (i.e., cued trials). On the other 50% of the trials, the cue ("\*") was presented at the center of the screen (i.e., neutral trials). Thus, on the cued trials, the location of the cue deterministically predicted the location of the arrow, whereas on the neutral trials the arrow always appeared in a different location.

Each trial started with a fixation cross presented at the center of the screen for 1000ms. Then, the cue was presented for 250ms either at the center of the screen or in the location where the arrow would appear next. Finally, the arrow was presented 250ms after the onset of the cue and shown until a response was given. The cued attention task began with eight practice trials (four cued and four neutral trials) in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red). After finishing the practice round, participants completed a single test block consisting of a total of 64 trials (two repetitions of all parameter combinations: arrow location (top center vs. top left vs. center left vs. bottom left vs. bottom center vs. bottom right vs. center right vs. top right) X arrow direction (left vs. right) X condition (cued vs. neutral)).

### Flanker task {#flanker}

On each trial of the Flanker task [@eriksen_1974], participants were presented with a set of five arrows pointing either left or right. Their job was to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right (see Figure 1A). On 50% of the trials, the flanking arrows pointed in the same direction as the central arrow (i.e., congruent trials), and on the other 50% of the trials they pointed in the opposite direction (i.e., incongruent trials). The arrows were randomly presented in the top-half or bottom-half of the screen. This was done to prevent participants from rigidly fixating on the center of the screen, which would reduce the interfering effect of the flanking arrows.

Each trial started with a fixation cross presented at the center of the screen. After a delay of 1000ms, the arrows are presented either in the top- or bottom-half of the screen. Participants were given 2000ms to indicate the direction of the center arrow. The Flanker task began with eight practice trials in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red). After finishing the practice round, participants completed a single test block consisting of a total of 64 trials (eight repetitions of all parameter combinations: arrow location (top vs. bottom) X central arrow direction (left vs. right) X condition: (congruent vs. incongruent)). Participants did not receive performance feedback during the test block.

### Change detection task {#change}

On each trial of the change detection task, participants were presented with five colored circles against a grey background, each with a radius of 15 pixels (see Figure 1C). Each circle was located in a random location within a pre-specified area of 50 by 50 pixels to prevent overlap. Participants had 1000ms to memorize the locations of the five circles around the fixation cross. After 1000ms, the circles briefly disappeared for 500ms and then reappeared again. On 50% of the trials, one of the circles had moved to another location with a fixed displacement of 40 pixels in a 360 degree direction. On the other 50% of the trials, all circles were still in the same location as the initial memory display. Participants have to indicate whether they thought one of the circles changed location (by pressing the left-arrow key) or whether they thought all circles were still in the same location (by pressing the right-arrow key). Note that the only potential difference between the memory and probe display was the displacement of **one** circle; the remaining circles were always in the same place and circles never changed color within a trial.

The change detection task started with five practice trials in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red). After finishing the practice round, participants completed two test blocks consisting of 25 trials each (50 trials in total). The design was fully counterbalanced so that on each "movement" trial, each of the five circles changes five times per block for each of the five colors. Participants did not receive performance feedback during the two test blocks.

### Current state {#state}

We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [STAI-S; @spielberger_1999]. The STAI-S contains 20 short items measuring current anxiety (e.g., "I feel tense"; See [Table S1](#appendix) for an overview of all items). Participants rated each item on a scale of 1 (not at all) to 4 (very much so).

Scores were recoded to range from 0 (not at all) to 3 (very much so). An overall state anxiety variable was computed by summing the 20 items (*M* = `rr #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).

In addition, participants answered five questions relating to specific states: "Are you currently sick?" (rated as yes or no); "Have you eaten a full meal today?" (rated as yes or no); "How hungry do you feel right now?" (rated from 1 (not at all) to 5 (very hungry)); "How well did you sleep last night?" (rated from 1 (very poorly) to 5 (very well)); "How rested or refreshed did you feel when you woke up this morning?" (rated from 1 (not at all) to 5 (very rested)).

### Violence exposure {#violence}

Violence exposure was measured using the Neighborhood Violence Scale [NVS; Frankenhuis & Bijlstra, 2018; Frankenhuis, de Vries, Bianchi, & Ellis, 2020] and two items assessing exposure to physical fights before age 13. The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up"; See [Table S2](#appendix) for an overview of all items). Participants rated each on a scale from 1 (never true) to 5 (very often true). The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).

The items of the NVS were averaged together (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `). Similarly, we averaged the scores on the two fighting items together. Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and averaging them together (*r* = `r #TBD `).

### Unpredictability {#unpred}

Perceived unpredictability before age 13 was measured using two different scales: A scale of perceived childhood unpredictability used in previous research [@mittal_2015; @young_2018] and an adaptation of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019]. The perceived childhood unpredictability scale contained eight items measuring perceived unpredictability before age 13 (e.g, "My family life was generally inconsistent and unpredictable from day-to-day"; See [Table S2](#appendix) for an overview of all items). Participants rated each on a scale from 1 (never true) to 5 (very often true).

We included the QUIC because it captures several dimensions of environmental and household unpredictability with a better (but not perfect) distinction between items capturing more short-term unpredictability (i.e., on the level of seconds to minutes) and more long-term unpredictability (i.e., on the level of days to months). Note that the scale of perceived childhood unpredictability combines items on a short-term scale (e.g., item 1) with items measured on a long-term scale (e.g., item 3) which might have different effects on the development of specific attention styles.

the QUIC consists of 38 items across five subscales: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 5) Safety and security (See [Table S4](#appendix) for an overview of all items). We made two changes to the original scale as described in @glynn_2019: First, While the original QUIC items refer to perceived unpredictability either before age 12 or age 18, we adapted all items to refer to participants' experiences before age 13. This was done to reduce cognitive load from having to mentally switch timescales between items and different scales and because the youngest eligible participants were 18 years old. Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format. This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.

We computed several unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overal QUIC variable as the sum of all 38 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales as the sum of their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `).

### Household chaos {#chaos}

We assessed household chaos before age 13 using an adaptation of the Confusion, Hubbub, and Order Scale [CHAOS; @matheny_1995]. The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late"; See [Table S5](#appendix) for an overview of all items). We made two changes to the original scale as described in @matheny_1995: First, all items were converted from the present tense to the past tense, and were endorsed as applying to partipants' life before age 13. Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format. This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.

An overall household chaos variable was computed by averaging the 15 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).

### Perceived socioeconomic status {#ses}

Perceived socioeconomic status before age 13 was measured using 7 items (e.g., "Your family had enough money to afford the kind of **home** you all needed"; See [Table S6](#appendix) for an overview of all items). Participants rated each on a scale from 1 (never true) to 5 (very often true).

The items were averaged together to create a composite scale (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).

### Impulsivity {#impulsivity}

We assessed impulsivity with the Motor Impulsivity subscale of the [Barrett Impulsivity Scale (BIS; short form); @patton_1995; @spinella_2007]. The Motor Impulsivity subscale of the BIS (short form) consists of five items (e.g., "I do things without thinking"; See [Table S7](#appendix) for an overview of all items). We did not include the Non-planning subscale because it overlapped substantially with the Future Orientation Scale described below. In addition, we did not include the Attention impulsivity subscale because it included items which we deemed to be mostly irrelevant for our target population (e.g., "I 'squirm' at plays or lectures"). We changed the original 4-point rating scale (rarely/never to almost always) to a 5-point rating scale ranging from 1 (never true) to 5 (very often true).

An overall impulsivity variable was computed by averaging the 5 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).

### Future Orientation {#future_orientation}

We assessed future orientation with an adapted version of the Future Orientation Scale [FOS; @steinberg_2009]. The original scale consists of 15 sets of opposing items separated by "BUT" (e.g., "Some people like to plan things out one step at a time BUT other people like to jump right into things without planning them out beforehand"). Participants first choose the item that best matches their general preference, and then indicate whether the statement is "really true" or "somewhat true". We adapted this format in a couple of ways: First, we converted the two statements per item to a single statement by picking the statements in the original right-hand column. Second, we adapted the 15 statements from a third-person to a first-person format. These changes were made in an attempt to reduce the cognitive load of the items. We worried that people with less formal education or who were sitting in a noisier environment would struggle with the length of the original items. In addition, item 8 of the original scale ("[...] other people would rather spend their money right away on something fun than save it for a rainy day") was changed to "I'd rather spend money right away than save it for a rainy day" (i.e., dropping the phrase "on something fun") to make it more general with regard to the thing that money is spent on. For people from adversity, spending money right now instead of saving it for the future might often be born out of necessity (e.g., having just enough food for food and shelter; being in debt) instead of a failure to delay gratification. See [Table S8](#appendix) for an overview of all adapted items). Finally, the rating scale was adapted from the original 4-point scale (ranging from really true for the left-hand statement to really true for the right-hand statement) to a 5-point scale ranging from 1 (never true) to 5 (very often true).

An overall future orientation variable was computed by averaging the 15 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `). In addition, we calculated subscales for "Planning ahead" (items 1, 6, 7, 12 and 13), "Time Perspective" (items 2, 5, 8, 11 and 14) and "Anticipation of Future Consequences" (items 3, 4, 9, 10 and 15).

### Depressive symptoms {#depression}

We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD; @radloff_1977]. The scale consists of 20 items (e.g., "I do things without thinking"; See [Table S9](#appendix) for an overview of all items). Participants rate each item on a scale of 1 (rarely or none of the time (less than 1 day)) to 4 (most or all of the time (5-7 days)).

Scores were recoded to range from 0 (rarely or none of the time (less than 1 day)) to 3 (most or all of the time (5-7 days)). An overall depression variable was computed by summing the 20 items (*M* = `rr #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).

## Primary data analyses {analysis_plan}

### Reaction Times {rt_plan}

For the Cued Attention Task and Flanker Task, average reaction times per participant were calculated separately for each condition (cued/neutral trials and incongruent/congruent trials, respectively). For the change detection task, we calculated an average reaction time across all trials. If necessary for meeting model assumptions, reaction times were log-transformed. We only planned on performing analyses on the proportion of errors if the average error rate was at least 5% of trials. Note that the DDM analysis described below provides a full breakdown of performance both in terms of reaction times and accuracy. For the Cued Attention Task and Flanker Task, we performed a set of linear mixed effects analyses to test adversity X condition interactions on mean RTs and accuracy (if possible). All models included a random intercept for participants. For the Change Detection Task, we performed linear regression to test the main effect of adversity on mean RTs and accuracy (if possible). Across separate models, adversity was operationalized as the composite measures of violence exposure, SES, perceived childhood unpredictability, household chaos, and the QUIC subscales (unless they correlated >.80, in which case QUIC subscales were merged together). Significant interaction effects were unpacked using simple slopes analysis.

### Drift Diffusion Model {#ddm_plan}

The Drift Diffusion Model (DDM; @ratcliff_2008; @ratcliff_2015) is a cognitive model that accounts for the fundamental cognitive processes underlying two-alternative forced-choice decision-making processes (2-AFC; see Figure XXX). The model assumes that the decision-making process constitutes a noisy information accumulation process that continues until one of two decision boundaries (corresponding to one of two response options) is reached. As soon as the accumulation process reaches a decision boundary, the process terminates and a motor response is initiated. The DDM recovers four parameters that map onto distinct cognitive processes [@voss_2004]. The accumulation process is modeled as a drift rate (*v*), reflecting basic cognitive speed/speed of information uptake. large values of *v* reflect more efficient processing (faster and more accurate). The starting point (*z*) reflects the starting position of the accumulation process relative to the two decision boundaries. Unless people are biased to favor one response over the other (e.g., due to a skewed reward structure), (*z*) is usually fixed to be equidistant from both decision boundaries (*a*). larger values of *a* indicate that the boundaries are further removed from each other, leading to more conservative responses (slower but more accurate) while smaller values of *a* reflect more liberal responses (faster but less accurate). Thus, *a* reflects the speed-accuracy trade-off made by an indidual. The fourth and final parameter is the non-decision time (*Ter*), which includes processes that are not related to the decision process (e.g., initial stimulus encoding and initiating the motor response). Importantly, the DDM parameters account for the full pattern of correct RTs, incorrect RTs, and proportion of errors.

The DDM was fit separately to the data of each participant. For the data of the Change Detection Task and the Cued Attention Task, the DDM was fit using Fast-dm [@voss_2007]. We used Maximum Likelihood estimation as it has been shown to provide reliable estimates with relatively few trials [@lerche_2017]; (see also our power simulations on [Github](https://github.com/StefanVermeent/attention_pilot/tree/main/scripts)). *a*, *v* and *Ter* were freely estimated and *z* was fixed to 0.5 (the midpoint, indicating no response bias). In addition, all inter-trial variability parameters were fixed to 0 to increase model parsimony. The DDM is fit separately to the data of each individual and to separate conditions. Thus, for the Cued Attention Task, the DDM was fit separately to data of the cued and neutral condition. For the Change Detection task, the DDM was fit to all trials.

The DDM analysis of the Flanker task was done using an adaptation of the standard DDM that was specifically developed to account for Flanker data: The Spotlight Drift Diffusion Model [SDDM; @grange_2016; @white_2018a; @white_2018b, @white_2011]. The standard DDM model assumes a stable drift rate over time within trials (i.e., the rate of information accumulation does not change over time). However, on the Flanker Task, reaction time patterns indicate that the drift rate increases over time, thus violating the basic assumption of the standard DDM [@white_2011]. The SDDM explains this pattern by assuming that attention on the Flanker task works like a spotlight that starts relatively broad, and then gradually narrows down to the central arrow over time. Each arrow provides perceptual input *p*. If the flanking arrows are congruent, all flankers take a positive value for *p*; if the flanking arrows are incongruent, they take a negative value for *p* while the central arrow takes a positive value. The drift rate (*v*) at each time point is the function of the strength of perceptual input *p* multiplied by the amount of attention focused on each arrow. Attention is operationalized by two additional parameters: the initial width of the attentional spotlight (*SD~a~*) and the shrinking rate of the attentional spotlight (*rd*). The attentional spotlight is assumed to be normally distributed over the arrows, with relatively more attention paid to the arrows at the center and relatively less attention paid to the peripheral arrows. Over time, this normal distribution (*SD~a~*) narrows down to the central arrow at the rate specified by *rd*, thereby gradually decreasing the interfering effect of the flanking arrows. Note that the SDDM is based on a combined analysis of congruent and incongruent trials. See Figure 1B for a visualization of the SDDM.

Previous research has shown that it is not useful to interpret both *SD~a~* and *rd* since they trade-off against each other [i.e., a wide initial spotlight combined with a large shrinking rate leads to similar patterns as a narrow initial spotlight combined with a low shrinking rate; @white_2018a; @white_2011]. Most previous studies have fixed *SD~a~* and only estimated *rd*, or calculated a *SD~a~*/*rd* ratio, which serves as a measure of interference. However, our primary interest lies in the initial width of the attentional spotlight, which we hypothesize to be wider for people from harsh and unpredictable environments compared to people from safe and predictable environments. In this pilot study, we fitted several SDDM models either estimating both attention parameters or fixing *rd* to see how it affected model fit (more details below). Model fit was done using the `flankr` package in R [@grange_2016].

DDM parameters *v*, *a* and *Ter* (as well as *p*, *SD~a~* and *SD~a~*/*rd* for the Flanker Task) were used as dependent variables in the analyses for each attention task. For the Flanker Task and Change Detection Task, DDM parameters were submitted to a series of linear regression models with adversity as the independent variable. For the Cued Attention Task, DDM parameters were submitted to linear mixed effects models to test for adversity X condition interactions. All models included a random intercept for participants. Independent adversity variables were identical to the RT/accuracy analyses. Significant interaction effects were unpacked using simple slopes analysis.

\pagebreak

# References {#refs}

<div id="refs"></div>

\pagebreak

# Appendix

```{r}
new_chapter()
```

Go back to [Methods](#state)

```{r supp_table1, tab.id="tableS2", tab.cap.style="Table Caption", tab.cap="Items of the State-Trait Anxiety Inventory (state subscale; STAI-S)"}
codebook %>%
  filter(str_detect(Variable, "stai_s(\\d\\d|_\\d\\d)")) %>% 
  mutate(Item = 1:n()) %>%
  select(Item, Label) %>%
  add_column(.after = 1, "empty1" = "") %>%
  mutate(Label = ifelse(Item %in% c(1,2,5,8,10,11,15,16,19,20), str_c(Label, "*"), Label)) %>%
  flextable(cwidth = c(0.75, .2, 5)) %>%
  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
  add_footer_row(values = " ", colwidths = 3) %>%
  compose(
    i = 1, j = 1,
    as_paragraph(as_i("Note: "), "Reverse scored items."),
    part = 'footer')
```

\pagebreak

Go back to [Methods](#violence)

```{r tableS2, tab.id="tableS2", tab.cap.style="Table Caption", tab.cap="Items of the Neighborhood Violence Scale (NVS)"}
codebook %>%
  filter(str_detect(Variable, "violence\\d\\d")) %>% 
  mutate(Item = 1:n()) %>%
  select(Item, Label) %>%
  add_column(.after = 1, "empty1" = "") %>%
  mutate(Label = ifelse(Item %in% c(1,3), str_c(Label, "*"), Label)) %>%
  flextable(cwidth = c(0.75, .2, 5)) %>%
  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
  add_footer_row(values = " ", colwidths = 3) %>%
  compose(
    i = 1, j = 1,
    as_paragraph(as_i("Note: "), "Reverse scored items."),
    part = 'footer')
```

\pagebreak

Go back to [Methods](#unpred)

```{r tableS3, tab.id="tableS3", tab.cap.style="Table Caption", tab.cap="Items of the Perceived Childhood Unpredictability scale"}
codebook %>%
  filter(str_detect(Variable, "unp\\d\\d")) %>% 
  mutate(Item = 1:n()) %>%
  select(Item, Label) %>%
  add_column(.after = 1, "empty1" = "") %>%
  flextable(cwidth = c(0.75, .2, 5)) %>%
  set_header_labels(Item = "Item", empty1 = "", Label = "Description")
```

\pagebreak

Go back to [Methods](#unpred)

```{r tableS4, tab.id="tableS4", tab.cap.style="Table Caption", tab.cap="Items of the Questionnaire of Unpredictability in Childhood (QUIC)"}
codebook %>%
  filter(str_detect(Variable, "quic\\d\\d")) %>% 
  mutate(Item = 1:n()) %>%
  select(Item, Label) %>%
  add_column(.after = 1, "empty1" = "") %>%
  add_row(.before = 1, "Label" = "Parental monitoring and involvement") %>%
  add_row(.after = 10, "Label" = "Parental predictability") %>%
  add_row(.after = 23, "Label" = "Parental environment") %>%
  add_row(.after = 31, "Label" = "Physical environment") %>%
  add_row(.after = 39, "Label" = "Safety and security") %>%
  mutate(Label = ifelse(Item %in% c(1,2,3,4,5,6,7,8,9,11,14,16,26,33), str_c(Label, "*"), Label)) %>%
  flextable(cwidth = c(0.75, .2, 5)) %>%
  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
  merge_h_range(i = c(1,11,24,32,40)) %>%
  bold(i = c(1,11,24,32,40)) %>%
  add_footer_row(values = " ", colwidths = 3) %>%
  compose(
    i = 1, j = 1,
    as_paragraph(as_i("Note: "), "Reverse scored items."),
    part = 'footer')
```

\pagebreak

Go back to [Methods](#chaos)

```{r tableS5, tab.id="tableS5", tab.cap.style="Table Caption", tab.cap="Items of the Confusion, Hubbub, and Order Scale (CHAOS)"}
codebook %>%
  filter(str_detect(Variable, "chaos\\d\\d")) %>% 
  mutate(Item = 1:n()) %>%
  select(Item, Label) %>%
  add_column(.after = 1, "empty1" = "") %>%
  mutate(Label = ifelse(Item %in% c(1,2,7,12,14,15), str_c(Label, "*"), Label)) %>%
  flextable(cwidth = c(0.75, .2, 5)) %>%
  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
  add_footer_row(values = " ", colwidths = 3) %>%
  compose(
    i = 1, j = 1,
    as_paragraph(as_i("Note: "), "Reverse scored items."),
    part = 'footer')
```

\pagebreak

Go back to [Methods](#ses)

```{r tableS6, tab.id="tableS6", tab.cap.style="Table Caption", tab.cap="Items of the perceived socio-economic status scale"}
codebook %>%
  filter(str_detect(Variable, "ses\\d\\d")) %>% 
  mutate(Item = 1:n()) %>%
  select(Item, Label) %>%
  add_column(.after = 1, "empty1" = "") %>%
  mutate(Label = ifelse(Item %in% c(7), str_c(Label, "*"), Label)) %>%
  flextable(cwidth = c(0.75, .2, 5)) %>%
  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
  add_footer_row(values = " ", colwidths = 3) %>%
  compose(
    i = 1, j = 1,
    as_paragraph(as_i("Note: "), "Reverse scored items."),
    part = 'footer')
```

\pagebreak

Go back to [Methods](#impulsivity)

```{r tableS7, tab.id="tableS7", tab.cap.style="Table Caption", tab.cap="Items of the Barrett Impulsivity Scale (BIS) - motor impulsivity subscale"}
codebook %>%
  filter(str_detect(Variable, "impuls\\d\\d")) %>% 
  mutate(Item = 1:n()) %>%
  select(Item, Label) %>%
  add_column(.after = 1, "empty1" = "") %>%
  flextable(cwidth = c(0.75, .2, 5)) %>%
  set_header_labels(Item = "Item", empty1 = "", Label = "Description")
```

\pagebreak

Go back to [Methods](#future_orientation)

```{r tableS8, tab.id="tableS8", tab.cap.style="Table Caption", tab.cap="Items of the Future Orientation Scale (FOS)"}
codebook %>%
  filter(str_detect(Variable, "fos\\d\\d")) %>% 
  slice(match(c("fos01","fos06","fos07","fos12","fos13", "fos02","fos05","fos08","fos11","fos14", "fos03","fos04","fos09","fos10","fos15"), Variable)) %>%
  mutate(Item = 1:n()) %>%
  select(Item, Label) %>%
  add_column(.after = 1, "empty1" = "") %>%
  add_row(.before = 1, "Label" = "Planning ahead") %>%
  add_row(.after = 6, "Label" = "Time perspective") %>%
  add_row(.after = 12, "Label" = "Anticipation of future consequences") %>%
  mutate(Label = ifelse(Item %in% c(1,2,5,8,9,11,12,15), str_c(Label, "*"), Label)) %>%
  flextable(cwidth = c(0.75, .2, 5)) %>%
  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
  merge_h_range(i = c(1,7,13)) %>%
  bold(i = c(1,7,13)) %>%
  add_footer_row(values = " ", colwidths = 3) %>%
  compose(
    i = 1, j = 1,
    as_paragraph(as_i("Note: "), "Reverse scored items."),
    part = 'footer')
```

\pagebreak

Go back to [Methods](#depression)

```{r tableS9, tab.id="tableS9", tab.cap.style="Table Caption", tab.cap="Items of the Epidemiologic Studies Depression Scale (CESD)"}
codebook %>%
  filter(str_detect(Variable, "depression\\d\\d")) %>% 
  mutate(Item = 1:n()) %>%
  select(Item, Label) %>%
  add_column(.after = 1, "empty1" = "") %>%
  mutate(Label = ifelse(Item %in% c(4,8,12,16), str_c(Label, "*"), Label)) %>%
  flextable(cwidth = c(0.75, .2, 5)) %>%
  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
  add_footer_row(values = " ", colwidths = 3) %>%
  compose(
    i = 1, j = 1,
    as_paragraph(as_i("Note: "), "Reverse scored items."),
    part = 'footer')
```

### 2021-10-28 preregistrations/1_pilot/preregistration.Rmd
major change to project structure

--- 2021-10-26 manuscript/preregistration.Rmd
@@
   word_document: default
+keep_md: true
 ---
@@
 library(here)
+library(pwr)
 
@@
 
-(Note: This document was written as a dynamic R Markdown document.
-The current version was submitted as a time-stamped **Preregistration** of the pilot study on <DATE>.
-In later versions in time, it will be extended to incorporate the results and discussion based on the pilot data, as well as potential deviations from the current preregistration and additional preregistrations.
-For an overview of all major versions of the document (e.g., from preregistration to (potential) deviations from the preregistration to final manuscript version), see the [overview of preregistrations and milestones on github](https://github.com/StefanVermeent/attention_pilot/Preregistrations_and_Milestones.xlsx)).
+*NOTE: This document serves as a time-stamped Preregistration of the pilot study.
+For each study/data collection, we will complete one preregistration.
+Each preregistration is written as a dynamic document in manuscript form.
+After data collection, the preregistration document will be extended to incorporate the analyses results and discussion.
+For each study/data collection, the document will go through a couple of milestones: 1) Preregistration; 2) Potential deviations from the preregistration; 3) Final manuscript.
+Each of these milestones will be time-stamped and tagged on [Github](https://github.com/StefanVermeent/attention_pilot) for easy referencing.*
 
-# Introduction and hypotheses
+\linebreak
 
-Experiencing childhood adversity is widely thought to have detrimental effects on a range of cognitive and behavioral outcomes.
-Findings in line with this deficit model have been extensively documented ().
-Recent years have seen the development of the complimentary hidden talents approach, which emphasizes the specific skills that people might develop in harsh environments through cognitive adaptations.
-However, it remains largely unclear which mechanisms drive specific enhancements and impairments of cognitive abilities.
-In this pilot study, we test the idea that people who grow up in adversity tend to develop a present-focused attention style, with features that benefit performance on some cognitive tasks but hurt performance on others.
+# Introduction
 
-In line with previous theorizing [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013], we expect stress-adapted cognitive styles to be characterized by a strong focus on the present.
-By cognitive style we mean a collection of relatively stable information processing tendencies (e.g., speed of processing, focus of attention, goal-directed behavior) that together determine how people interact with their environment.
-Over time, a tendency to focus on the here-and-now might lead to a stable external attention style [i.e., attention pointed at the external environment; @chun_2011], while less attention is paid to internal processes (e.g., goal-directed behavior, memory retrieval).
-Previous studies focusing on attentional processes in people from adversity suggest that adversity exposure impairs attention (.., but see ..).
-However, most of these studies measure attention either indirectly through subjective parent reports, or using "executive attention" tasks which involve executive processes such as inhibiting responses and actively maintaining a complex task goal.
-Conversely, studies focusing on more basic processes tend to focus on attention for and processing of threatening stimuli such as angry faces [e.g., @pollak_2002; @thompson_2021].
-Therefore, it remains largely unclear whether adversity shapes more basic and stable (i.e., context-independent) attention styles.
+Experiencing childhood adversity can have detrimental effects on cognitive outcomes [@hackman_2010; @ursache_2016].
+However, the hidden talents approach suggests that people living in adversity might develop specific skills that help them navigate harsh and unpredictable environments.
+For example, recent work shows that growing up in stressful environments can enhance working memory updating, at least under certain conditions [@young_2018].
+However, the cognitive mechanisms responsible for lowered (impairments) and improved (enhancements) performance on various tests remain poorly understood.
+Some studies suggest that specific types of adversity lead to specific abilities independent of the current context [@fields_2021].
+Others only find enhancement effects when testing conditions are made more ecologically relevant [@young_2018, submitted for publication].
 
-Here, we focus on two aspects of external attention that we expect to develop in harsh and unpredictable environments: 1) A relatively wider scope of attention and 2) an increased sensitivity to subtle changes in the environment.
-When might these attention styles develop in adverse environments?
-Attention is involved in information processing on a timescale of seconds to minutes; Focusing attention for longer periods on a single stimulus is impossible for most people [@warm_2008].
-Thus, stable attention styles are most useful in response to environmental features that unfold on the same timescale.
-Factors such as changes in adult household members or frequently moving homes, which are often used as proxies for unpredictability, are unlikely to shape stable attentional styles as they unfold over days or weeks.
-In addition, any threats that are spatially or temporally predictable (e.g., a specific part of the neighborhood that is known to be dangerous or might be especially dangerous at night) are more likely to lead to signal- or cue-based changes in cognitive processing.
-Instead, a cognitive style that systematically favors external attention over internal attention should develop when threats are frequent and the environment is chaotic, such that past states of the environment are not predictive of the current state [@emond_2020; @young_2020].
-In such an environment, threats might arise at any time and the occasional reward might be fleeting [@ellis_2009; @frankenhuis_2016].
-In the absence of reliable cues, a person would benefit from having their attention fixated broadly on the external environment, so that threats and opportunities can be anticipated and dealt with as soon as they appear.
+Further progress depends on addressing two related questions: First, to what extent are patterns of impairment and enhancement independent?
+Cognitive processes that are typically targeted in hidden talents studies (e.g., working memory, task-switching) are complex processes that share many of the same more basic processes [@conway_2021, @kovacs_2019; @verbruggen_2014].
+This overlap means that impairment and enhancement patterns across tasks could be driven by the same underlying process.
+Second, which *cognitive* mechanisms are responsible for performance differences?
+Performance measures such as reaction times (RTs) or error rates are coarse indicators of performance.
+RTs on cognitive tasks are thought to reflect a number of sequentially unfolding processes.
+When the effect of adversity exposure on cognitive performance is measured by looking at RTs, enhancements or impairments might be driven by any of these subprocesses.
+Formal cognitive models such as the Drift Diffusion Model [DDM; @ratcliff_2008; @ratcliff_2015] might provide inside into the exact processes that are impaired or enhanced by adversity.
+In this pilot study, we leverage the DDM to better understand the processes involved in performance differences.
 
-The current pilot study had two primary aims: First, we tested whether people from harsh and unpredictable environments would perform better on attention tasks that favor a broad attention scope and a sensitivity to subtle changes.
-To this end, participants completed three attention tasks that differed in the extent to which they would favor or punish these attention features.
-Second, we investigated the link between adversity and attention both in a traditional analysis of reaction times, as well as by using the Drift Diffusion Model [DDM; @forstmann_2016; @ratcliff_2015; @ratcliff_2008] to more precisely disentangle the underlying cognitive processes (for more details on the DDM analysis, see the [Data analyses]{#ddm_plan} section).
+The DDM accounts for the fundamental cognitive processes underlying relatively simple, binary decision-making processes (2-AFC).
+The model assumes that the decision-making process constitutes a noisy information accumulation process that continues until one of two decision boundaries (corresponding to the response options) is reached.
+As soon as the accumulation process reaches a decision boundary, the process terminates and a motor response is initiated (e.g, pressing a a key on the keyboard).
+The DDM accounts for the full pattern of correct RTs, incorrect RTs, and proportion of errors.
+In doing so, it recovers four parameters that map onto distinct cognitive processes ([@voss_2004]; see Figure XXX).
+The accumulation process is modeled as a drift rate (*v*), reflecting basic cognitive speed/speed of information uptake.
+large values of *v* reflect more efficient processing (faster and more accurate).
+The starting point (*z*) reflects the starting position of the accumulation process relative to the two decision boundaries.
+Unless people are biased to favor one response over the other (e.g., due to a skewed reward structure), (*z*) is usually fixed to be equidistant from both decision boundaries (*a*).
+larger values of *a* indicate that the boundaries are further removed from each other, leading to more conservative responses (slower but more accurate) while smaller values of *a* reflect more liberal responses (faster but less accurate).
+Thus, *a* reflects the speed-accuracy trade-off made by an indidual.
+The fourth and final parameter is the non-decision time (*Ter*), which includes processes that are not related to the decision process (e.g., initial stimulus encoding and initiating the motor response).
+
+The current study aims to address these questions using an incremental preregistration approach.
+In the current preregistered pilot study, we measured various forms of adversity with a focus on unpredictability on different time scales.
+In addition, Participants completed three attention tasks that differed in the extent to which they would favor or punish a broad, externally focused attention style.
+We applied the DDM to the RT and accuracy data to decompose performance.
+If people from adversity develop specialized attention skills, this should be reflected in DDM parameters.
+First and foremost, more attention on the relevant stimuli should be reflected in a higher drift rate *v*.
+Second, enhanced initial detection of peripheral stimuli should be reflected in a lower non-decision time (*Ter*) since this would allow the decision process to initiate sooner in time.
+Beyond attention skills, people from adversity might have a smaller boundary separation *a*, reflecting more impulsive responses.
+
+# Hypotheses
 
@@
 1) People with more exposure to violence and environmental unpredictability during childhood will show enhanced or equal performance compared to people from safe environments on tasks that require quickly detecting peripheral stimuli and detecting subtle changes (i.e., the Cued Attention Task and Change Detection Task).
-This effect is at least partly explained by the speed of information uptake (operationalized through the drift rate parameter of the DDM).
+This effect is explained by at least one of two DDM parameters: the speed of information uptake *v* and non-decision time *Ter*.
 
 2) People with more exposure to violence and environmental unpredictability during childhood will perform worse on tasks that require ignoring distracting peripheral stimuli (i.e., the Flanker Task).
-This effect is at least partly explained by a wider initial attentional focus, (operationalized through the attentional width parameter of the Spotlight DDM (SDDM) analysis).
+This effect is at least partly explained by a wider initial attentional focus, (operationalized through the attentional width parameter of a special adaptation of the original DDM; see [data analyses](#ddm_plan) for more details).
 
@@
 Second, we conducted exploratory correlation analyses between measures of adversity, attention, and measures of temporal orientation (i.e., impulsivity and future orientation).
-Third, we explored whether potential effects of adversity on task performance might be moderated by current states of anxiety, hunger, or sleep deprivation.
-Fourth, we explored the extent to which our retrospective measures of adversity correlate with current depressive symptoms, which might reflect a retrospective negativity bias driven by current psychopathological symptoms [@nivison_2021].
+Third, we explored whether potential effects of adversity on task performance might be moderated by current anxiety.
+Fourth, we explored effects of hunger and sleep deprivation on performance.
+Finally, we explored the extent to which our retrospective measures of adversity correlate with current depressive symptoms, which might reflect a retrospective negativity bias driven by current psychopathological symptoms [@nivison_2021].
 
@@
 
-Participants were XXX US-based individuals between the ages of 18 and 30 (*M* = `r #TBD`, *SD* = `r #TBD`).
+Participants were 450 US-based individuals between the ages of 18 and 30 (*M* = `r #TBD`, *SD* = `r #TBD`).
 We decided for this age cut-off to limit the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 [@salthouse_2010].
@@
 
-The sample size was determined by a [preregistered power analysis](https://osf.io/gfpnr/))).
-[...]
+The sample size was determined based on a power analysis for detecting a standardized effect of 0.1 and 90% power. [preregistered power analysis](https://osf.io/gfpnr/))).
+[TO BE FILLED IN]
 
@@
 
+The exclusion criteria listed above are our best *a-priori* guesses. We expect to develop new criteria empirically after collecting the data.
+
 ## Procedure {#procedure}
 
-The experiment was completed on the participants' own laptop or desktop computer and consisted of four parts: written consent, attention task battery, questionnaire battery, brief demographics form, and final checks and the opportunity to give feedback on the experiment.
+The experiment was completed on the participants' own laptop or desktop computer and consisted of four parts: consent, attention task battery, questionnaire battery, brief demographics form, and final checks and the opportunity to give feedback on the experiment.
 [something on ethical approval].
@@
 At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs.
-The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych.
+The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deLeeuw_2015].
 Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the creditcard.
 The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants.
-After succesfully resizing the screen, participants completed all three tasks.
+After successfully resizing the screen, participants completed all three tasks.
 Whenever participants had to respond by use of their keyboard, the cursor was hidden from the screen to minimize distractions.
@@
 
-### Cued attention task {#cued_attention}
+### Cued Attention Task {#cued_attention}
 
-The cued attention task was an adaptation of the Posner task [@posner_1980].
+The cued attention task was an adaptation of the Posner task [@posner_1980] which measures basic spatial attention speed.
 On each trial, a left- or right-pointing arrow is presented in one of eight random locations at a distance of 300 pixels from the center of the screen (see Figure 1B).
@@
 neutral)).
+The main performance measures are RTs and accuracy for each condition.
 
@@
 
+The Flanker Task measures selective attention and response inhibition.
 On each trial of the Flanker task [@eriksen_1974], participants were presented with a set of five arrows pointing either left or right.
@@
 Participants did not receive performance feedback during the test block.
+The main performance measures are RTs and accuracy for each condition.
 
@@
 
+The Change Detection Task measures the ability to detect subtle spatial changes.
 On each trial of the change detection task, participants were presented with five colored circles against a grey background, each with a radius of 15 pixels (see Figure 1C).
@@
 Participants did not receive performance feedback during the two test blocks.
+The main performance measures are RTs and accuracy across all trials.
 
@@
 Participants rated each item on a scale of 1 (not at all) to 4 (very much so).
-
-Scores were recoded to range from 0 (not at all) to 3 (very much so). An overall state anxiety variable was computed by summing the 20 items (*M* = `rr #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+An overall state anxiety variable was computed by averaging across the 20 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
 
@@
 
+We computed an overall sleep deprivation composite by standardizing and averaging across the two sleep-related items (*M* = `r #TBD `, *SD* = `r #TBD `).
+The first hunger item (i.e., "have you eaten a full meal today?") was recoded as half a standard-deviation above or below the mean (standardized).
+People who had not eaten a full meal were coded as -0.5, and those who had eaten a full meal were coded as 0.5.
+A hunger composite was calculated by averaging the recoded meal item and the hunger item (*M* = `r #TBD `, *SD* = `r #TBD `).
+
 ### Violence exposure {#violence}
 
-Violence exposure was measured using the Neighborhood Violence Scale [NVS; Frankenhuis & Bijlstra, 2018; Frankenhuis, de Vries, Bianchi, & Ellis, 2020] and two items assessing exposure to physical fights before age 13.
+Violence exposure was measured using the Neighborhood Violence Scale [NVS; @frankenhuis_2018; @frankenhuis_deVries_2020] and two items assessing exposure to physical fights before age 13.
 The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up"; See [Table S2](#appendix) for an overview of all items).
@@
 The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
-
 The items of the NVS were averaged together (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
@@
 
-the QUIC consists of 38 items across five subscales: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 5) Safety and security (See [Table S4](#appendix) for an overview of all items).
-We made two changes to the original scale as described in @glynn_2019: First, While the original QUIC items refer to perceived unpredictability either before age 12 or age 18, we adapted all items to refer to participants' experiences before age 13.
+The QUIC consists of 38 items across five subscales: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 5) Safety and security (See [Table S4](#appendix) for an overview of all items).
+We made two changes to the original scale as described in @glynn_2019: First, while the original QUIC items refer to perceived unpredictability either before age 12 or age 18, we adapted all items to refer to participants' experiences before age 13.
 This was done to reduce cognitive load from having to mentally switch timescales between items and different scales and because the youngest eligible participants were 18 years old.
@@
 
-We computed several unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overal QUIC variable as the sum of all 38 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales as the sum of their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `).
+We computed several unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overal QUIC variable by averaging all 38 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `).
 
@@
 This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
-
 An overall household chaos variable was computed by averaging the 15 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
 
-### Perceived socioeconomic status {#ses}
+### Poverty exposure {#ses}
 
-Perceived socioeconomic status before age 13 was measured using 7 items (e.g., "Your family had enough money to afford the kind of **home** you all needed"; See [Table S6](#appendix) for an overview of all items).
+Participants' perceived level of resource scarcity before age 13 was measured using 7 items (e.g., "Your family had enough money to afford the kind of **home** you all needed"; See [Table S6](#appendix) for an overview of all items).
 Participants rated each on a scale from 1 (never true) to 5 (very often true).
+Scores for the first six items were reversed so that higher scores indicated more perceived resource scarcity.
+The items were averaged together to create a composite scale (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
 
-The items were averaged together to create a composite scale (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+In addition, we measured several indicators of objective SES before age 13.
+First, participants separately indicated the highest education of their mother and father on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'.
+The mother and father education level were averaged to create an overall parental education composite (*M* = `r #TBD `, *SD* = `r #TBD `).
+
+In addition, participants indicated their family's household income before age 13 on a 6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'.
+Scores were reversed so that higher scores indicated higher levels of poverty.
+
+We created a composite score of poverty exposure before age 13 by averaging together the standardized scores of perceived level of resource scarcity, overall parental education, and household income.
 
@@
 
-Scores were recoded to range from 0 (rarely or none of the time (less than 1 day)) to 3 (most or all of the time (5-7 days)).
-An overall depression variable was computed by summing the 20 items (*M* = `rr #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+An overall depression variable was computed by averaging the 20 items (*M* = `rr #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
 
-## Primary data analyses {analysis_plan}
+## Primary data analyses {#analysis_plan}
 
-### Reaction Times {rt_plan}
+### Reaction Times {#rt_plan}
 
@@
 
-The Drift Diffusion Model (DDM; @ratcliff_2008; @ratcliff_2015) is a cognitive model that accounts for the fundamental cognitive processes underlying two-alternative forced-choice decision-making processes (2-AFC; see Figure XXX).
-The model assumes that the decision-making process constitutes a noisy information accumulation process that continues until one of two decision boundaries (corresponding to one of two response options) is reached.
-As soon as the accumulation process reaches a decision boundary, the process terminates and a motor response is initiated.
-The DDM recovers four parameters that map onto distinct cognitive processes [@voss_2004].
-The accumulation process is modeled as a drift rate (*v*), reflecting basic cognitive speed/speed of information uptake.
-large values of *v* reflect more efficient processing (faster and more accurate).
-The starting point (*z*) reflects the starting position of the accumulation process relative to the two decision boundaries.
-Unless people are biased to favor one response over the other (e.g., due to a skewed reward structure), (*z*) is usually fixed to be equidistant from both decision boundaries (*a*).
-larger values of *a* indicate that the boundaries are further removed from each other, leading to more conservative responses (slower but more accurate) while smaller values of *a* reflect more liberal responses (faster but less accurate).
-Thus, *a* reflects the speed-accuracy trade-off made by an indidual.
-The fourth and final parameter is the non-decision time (*Ter*), which includes processes that are not related to the decision process (e.g., initial stimulus encoding and initiating the motor response).
-Importantly, the DDM parameters account for the full pattern of correct RTs, incorrect RTs, and proportion of errors.
+DDM models were fit separately to the data of each participant. 
+(see also our power simulations on [Github](https://github.com/StefanVermeent/attention_pilot/tree/main/scripts), which indicated that recovered drift rate and boundary separation parameters generally correlated highly (*r* = .80-.95) with the true data-generating parameters even with 30 trials).
 
@@
 For the data of the Change Detection Task and the Cued Attention Task, the DDM was fit using Fast-dm [@voss_2007].
-We used Maximum Likelihood estimation as it has been shown to provide reliable estimates with relatively few trials [@lerche_2017]; (see also our power simulations on [Github](https://github.com/StefanVermeent/attention_pilot/tree/main/scripts)).
+We used Maximum Likelihood estimation as it has been shown to provide reliable estimates with relatively few trials [@lerche_2017]; (see also our power simulations on [Github](https://github.com/StefanVermeent/attention_pilot/tree/main/scripts), which indicated that recovered drift rate and boundary separation parameters generally correlated highly (*r* = .80-.95) with the true data-generating parameters even with 30 trials).
 *a*, *v* and *Ter* were freely estimated and *z* was fixed to 0.5 (the midpoint, indicating no response bias).
 In addition, all inter-trial variability parameters were fixed to 0 to increase model parsimony.
-The DDM is fit separately to the data of each individual and to separate conditions.
-Thus, for the Cued Attention Task, the DDM was fit separately to data of the cued and neutral condition.
-For the Change Detection task, the DDM was fit to all trials.
+For the Cued Attention Task, the DDM was fit separately to data of the two conditions (cued vs neutral).
+For the Change Detection task, we had no *a-priori* expectations about performance differences between the change and no-change trials.
+Prior to fitting the DDM models, we ran paired-sample t-tests on the RTs and proportion of errors.
+If either model showed significant mean differences, the DDM was fit separately to data of the change and no-change trials.
+If there were no differences, the DDM models were fit to all trials simultaneously.
 
@@
 The drift rate (*v*) at each time point is the function of the strength of perceptual input *p* multiplied by the amount of attention focused on each arrow.
+
 Attention is operationalized by two additional parameters: the initial width of the attentional spotlight (*SD~a~*) and the shrinking rate of the attentional spotlight (*rd*).
@@
 # Appendix
-
-```{r}
-new_chapter()
-```
 
@@
 
-```{r tableS6, tab.id="tableS6", tab.cap.style="Table Caption", tab.cap="Items of the perceived socio-economic status scale"}
+```{r tableS6, tab.id="tableS6", tab.cap.style="Table Caption", tab.cap="Items of the perceived resource scarcity scale"}
 codebook %>%
@@
   add_column(.after = 1, "empty1" = "") %>%
-  mutate(Label = ifelse(Item %in% c(7), str_c(Label, "*"), Label)) %>%
+  mutate(Label = ifelse(!Item %in% c(7), str_c(Label, "*"), Label)) %>%
   flextable(cwidth = c(0.75, .2, 5)) %>%

### 2021-10-28 preregistrations/1_pilot/scripts/0_power_analysis.R

@@ -248,7 +248,7 @@ simulation_data <-
         adversity = rnorm(n(), 0, 1),
         intercept = rnorm(n(), 0, 2),
         sigma = rnorm(n(), 0, sigma_sd),
-        drift_rate_true = intercept + (fixed_effect * adversity) + sigma,
+        drift_rate_true = 0 + (fixed_effect * adversity) + sigma,
         drift_rate_recov = rnorm_pre(drift_rate_true, mu = mean(drift_rate_true), sd = sd(drift_rate_true), r = DDM_recovery_correlation, empirical = TRUE),
         n_sim = n_sim,
         r = DDM_recovery_correlation,

### 2021-10-28 preregistrations/1_pilot/scripts/1_create-scales.R

@@ -1,0 +1,262 @@
+# Packages ----------------------------------------------------------------
+library(tidyverse)
+library(qualtRics)
+library(jsonlite)
+library(here)
+
+# Functions ---------------------------------------------------------------
+source("scripts/custom_functions/create_codebook.R")
+
+# Data --------------------------------------------------------------------
+pilot_data <- 
+  fetch_survey(
+    surveyID = "SV_2tsChV0wnzp0LH0", 
+    verbose  = T,
+    force_request = T,
+    label = F,
+    convert = F,
+    add_var_labels = F
+  ) %>% 
+  rename_with(tolower) %>% 
+  mutate(id = 1:n()) %>% 
+  sjlabelled::var_labels(
+    id = "Blinded participant ID"
+  ) 
+
+# meta data ---------------------------------------------------------------
+vars01_meta <- 
+  pilot_data %>% 
+  rename(
+    meta_duration = `duration (in seconds)`,
+    meta_start    = startdate,
+    meta_end      = enddate,
+    meta_recorded = recordeddate,
+    meta_finished = finished,
+    meta_captcha  = q_recaptchascore,
+  ) %>% 
+  select(id, starts_with("meta_"))
+
+
+# Current state -----------------------------------------------------------
+
+vars02_state <- 
+  pilot_data %>%
+  select(id, starts_with('stai_s'), sick, meal, hungry, sleep, rested) %>%
+  mutate(
+    stai_s_sum = across(matches("stai_s")) %>% psych::reverse.code(keys = c(-1,-1,1,1,-1,1,1,-1,1,-1,-1,1,1,1,-1,-1,1,1,-1,-1), items = ., mini = 0, maxi = 3) %>% rowSums(., na.rm = T)
+  )
+
+# Unpredictability --------------------------------------------------------
+vars03_unp <- 
+  pilot_data %>% 
+  select(id,starts_with(c("chaos", "unp", "quic"))) %>% 
+  mutate(
+    unp_mean                 = across(matches("unp\\d\\d")) %>% rowMeans(., na.rm = T),
+    unp_missing              = across(matches("unp\\d\\d")) %>% is.na() %>% rowSums(., na.rm = T),
+    
[…]

### 2021-10-28 preregistrations/1_pilot/scripts/custom_functions/create_codebook.R

@@ -47,9 +47,7 @@ create_codebook <- function (data) {
     message("---------The following variables have no value labels:---------\n", 
             paste(no_values %>% dplyr::pull(Variable), collapse = "\n"))
   }
-  
-  codebook %<>%
-    separate(col = Label, into = c("Preface", "Label"), sep = "-")
-  
+  codebook
+      
   
 }

### 2021-10-28 preregistrations/1_pilot/tasks/attention_cueing/1_attention_cueing_instructions.js

@@ -31,8 +31,8 @@ var cueing_instructions = {
       
     "<p style = 'text-align: center;'>" + 
       "When the arrow appears, press the arrow key that matches the way it points.<br><br>" +
-      "<div style = 'float: left;'>If it points LEFT<br>press the LEFT (<) key.</div>" +
-      "<div style = 'float: right;'>If it points RIGHT<br>press the RIGHT (>) key.</div><br><br><br><br>" + 
+      "<div style = 'float: left;'>If it points LEFT<br>press the LEFT (&larr;) key.</div>" +
+      "<div style = 'float: right;'>If it points RIGHT<br>press the RIGHT (&rarr;) key.</div><br><br><br><br>" + 
       "In the example below, you would press the left key.<br><br><br>" + 
       "<img width = 160 src = 'img/cueing_instructions3.png'></img><br><br><br>",
       
@@ -56,7 +56,7 @@ var cueing_practice_start = {
   type: 'html-keyboard-response',
   stimulus:    "<p style = 'text-align: center;'>" +
       "You will practice the game <strong>8 times</strong>.<br><br>" +
-      "Place your fingers on the left (<) and right (>) arrow keys.<br><br>" +
+      "Place your fingers on the left (&larr;) and right (&rarr;) arrow keys.<br><br>" +
       "When you are ready to practice, press any key to start.",
   choices: jsPsych.ALL_KEYS,
   data: {variable: "practice_start", task: "cueing"}

### 2021-10-28 preregistrations/1_pilot/tasks/change_detection/1_spatial_change_instructions.js

@@ -32,8 +32,8 @@ var change_instructions = {
       
     "<p style = 'text-align: center;'>" + 
       "Your job is to figure out if the places of the circles are the SAME or DIFFERENT.<br><br>" +
-      "<div style = 'float: left;'>If the SAME<br>press the LEFT (<) key.</div>" +
-      "<div style = 'float: right;'>If DIFFERENT<br>press the RIGHT (>) key.</div><br><br><br><br>",
+      "<div style = 'float: left;'>If the SAME<br>press the LEFT (&larr;) key.</div>" +
+      "<div style = 'float: right;'>If DIFFERENT<br>press the RIGHT (&rarr;) key.</div><br><br><br><br>",
       
     "<p style = 'text-align: center;'>" +
       "The words 'SAME' and 'DIFFERENT' will always be at the bottom<br>" +
@@ -56,7 +56,7 @@ var change_practice_start = {
   type: 'html-keyboard-response',
   stimulus:    "<p style = 'text-align: center;'>" +
       "You will practice the game <strong>5 times</strong>.<br><br>" +
-      "Place your fingers on the left (<) and right (>) arrow keys.<br><br>" +
+      "Place your fingers on the left (&larr;) and right (&rarr;) arrow keys.<br><br>" +
       "When you are ready to practice, press any key to start.",
   choices: jsPsych.ALL_KEYS,
   data: {variable: "practice_start", task: "change"}
@@ -91,7 +91,9 @@ var change_practice1 = {
       },
       ],
       data: {
-        type: jsPsych.timelineVariable('type'),
+        variable: 'practice',
+        task: 'change',
+        condition: jsPsych.timelineVariable('type'),
         mem_stim1_x: jsPsych.timelineVariable('mem_stim1_x'),
         mem_stim2_x: jsPsych.timelineVariable('mem_stim2_x'),
         mem_stim3_x: jsPsych.timelineVariable('mem_stim3_x'),
@@ -162,7 +164,9 @@ var change_practice2 = {
       },
       ],
       data: {
-        type: jsPsych.timelineVariable('type'),
+        variable: 'practice',
+        task: 'change',
+        condition: jsPsych.timelineVariable('type'),
         mem_stim1_x: jsPsych.timelineVariable('mem_stim1_x'),
         mem_stim2_x: jsPsych.timelineVariable('mem_stim2_x'),
[…]

### 2021-10-28 preregistrations/1_pilot/tasks/change_detection/2_spatial_change_procedure.js

@@ -26,7 +26,8 @@ var change_trial_block1 = {
       data: {
         variable: 'test_block1',
         task: 'change',
-        type: jsPsych.timelineVariable('type'),
+        condition: jsPsych.timelineVariable('type'),
+        correct_response: jsPsych.timelineVariable('correct_response'),
         mem_stim1_x: jsPsych.timelineVariable('mem_stim1_x'),
         mem_stim2_x: jsPsych.timelineVariable('mem_stim2_x'),
         mem_stim3_x: jsPsych.timelineVariable('mem_stim3_x'),
@@ -245,7 +246,8 @@ stim1_color: '#0457A0', stim2_color: '#25D9E4', stim3_color: '#D40E0E', stim4_co
       data: {
         variable: 'test_block2',
         task: 'change',
-        type: jsPsych.timelineVariable('type'),
+        condition: jsPsych.timelineVariable('type'),
+        correct_response: jsPsych.timelineVariable('correct_response'),
         mem_stim1_x: jsPsych.timelineVariable('mem_stim1_x'),
         mem_stim2_x: jsPsych.timelineVariable('mem_stim2_x'),
         mem_stim3_x: jsPsych.timelineVariable('mem_stim3_x'),

### 2021-10-28 preregistrations/1_pilot/tasks/flanker/0_flanker_setup.js

@@ -52,8 +52,7 @@ var location_stim = function(up, down){
   type: 'html-keyboard-response',
   stimulus: '<div style="font-size:60px;">+</div>',
   choices: jsPsych.NO_KEYS,
-  trial_duration: function(){
-    return jsPsych.randomization.sampleWithoutReplacement([800, 850, 900, 950, 1000, 1050, 1100, 1150, 1200], 1)[0]},
+  trial_duration: 1000,
   data: {
     variable: 'fixation'
   }

### 2021-10-28 preregistrations/1_pilot/tasks/flanker/1_flanker_instructions.js

@@ -32,8 +32,8 @@ var flanker_instructions = {
       "<p style = 'text-align: center;'>"+ 
       "You should <i>always</i> look at the <strong>middle arrow</strong> and ignore the others.<br><br>" +
       
-      "<div style = 'float: left;'>If it points LEFT<br>press the LEFT (<) key.</div>" +
-      "<div style = 'float: right;'>If it points RIGHT<br>press the RIGHT (>) key.</div><br><br><br><br>" + 
+      "<div style = 'float: left;'>If it points LEFT<br>press the LEFT (&larr;) key.</div>" +
+      "<div style = 'float: right;'>If it points RIGHT<br>press the RIGHT (&rarr;) key.</div><br><br><br><br>" + 
       
       "In the example below, the middle arrow points left,<br>" +
       "so you would press the left key.<br><br>" +
@@ -58,7 +58,7 @@ var flanker_practice_start = {
   type: 'html-keyboard-response',
   stimulus:    "<p style = 'text-align: center;'>" +
       "You will practice the game <strong>8 times</strong>.<br><br>" +
-      "Place your fingers on the left (<) and right (>) arrow keys.<br><br>" +
+      "Place your fingers on the left (&larr;) and right (&rarr;) arrow keys.<br><br>" +
       "When you are ready to practice, press any key to start.",
   choices: jsPsych.ALL_KEYS,
   data: {variable: "practice_start", task: "flanker"}

### 2021-10-28 preregistrations/1_pilot/tasks/global_variables.js

@@ -12,7 +12,9 @@ var resize_screen = {
   "Then, click and drag the lower right corner of the box until the box is the same size as the credit card when held up to the screen." +
   "</p>",
   button_label: ['Continue'],
-  pixels_per_unit: 100
+  pixels_per_unit: 100,
+  data: {
+    task: 'resize',
 };
 
 var fullscreenmode = {

### 2021-10-28 scripts/1_create-scales.R

@@ -1,232 +1,0 @@
-# Packages ----------------------------------------------------------------
-library(tidyverse)
-library(qualtRics)
-library(jsonlite)
-
-# Functions ---------------------------------------------------------------
-source("scripts/functions-create_codebook.R")
-
-# Data --------------------------------------------------------------------
-pilot_data <- 
-  fetch_survey(
-    surveyID = "SV_2tsChV0wnzp0LH0", 
-    verbose  = T,
-    force_request = T,
-    label = F,
-    convert = F
-  ) %>% 
-  rename_with(tolower) %>% 
-  mutate(id = 1:n()) %>% 
-  sjlabelled::var_labels(
-    id = "Blinded participant ID"
-  ) 
-
-# meta data ---------------------------------------------------------------
-vars01_meta <- 
-  pilot_data %>% 
-  rename(
-    meta_duration = `duration (in seconds)`,
-    meta_start    = startdate,
-    meta_end      = enddate,
-    meta_recorded = recordeddate,
-    meta_finished = finished,
-    meta_captcha  = q_recaptchascore,
-  ) %>% 
-  select(id, starts_with("meta_"))
-
-
-# Current state -----------------------------------------------------------
-
-vars02_state <- 
-  pilot_data %>%
-  select(id, starts_with('stai_s'), sick, meal, hungry, sleep, rested) %>%
-  mutate(
-    stai_s_mean = across(matches("stai_s")) %>% psych::reverse.code(keys = c(-1,-1,1,1,-1,1,1,-1,1,-1,-1,1,1,1,-1,-1,1,1,-1,-1), items = ., mini = 1, maxi = 4) %>% rowSums(., na.rm = T)
-  )
-
-# Unpredictability --------------------------------------------------------
-vars03_unp <- 
-  pilot_data %>% 
-  select(id,starts_with(c("chaos", "unp", "quic"))) %>% 
-  mutate(
-    unp_mean                 = across(matches("unp\\d\\d")) %>% rowMeans(., na.rm = T),
-    unp_missing              = across(matches("unp\\d\\d")) %>% is.na() %>% rowSums(., na.rm = T),
-    
[…]

### 2021-10-28 scripts/custom_functions/update_gitlog.R

@@ -1,78 +1,0 @@
-update_gitlog <- function(repo_url) {
-  
-  library(tidyverse)
-  library(openxlsx)
-  
-  
-  # Create Updated Git log
-  log_format_options <- c(datetime = "cd", commit = "h", author = "an", subject = "s")
-  option_delim <- "\t"
-  log_format   <- glue("%{log_format_options}") %>% glue_collapse(option_delim)
-  log_options  <- glue('--pretty=format:"{log_format}" --date=format:"%Y-%m-%d %H:%M:%S"')
-  log_cmd      <- glue(str_c('git -C ', here(), ' log {log_options}'))
-  log_cmd
-  
-  gitlog <- system(log_cmd, intern = TRUE) %>%
-    str_split_fixed(option_delim, length(log_format_options)) %>%
-    as_tibble() %>%
-    mutate(Milestone = "") %>%
-    setNames(c("Date", "Commit", "Author", "Description", "Milestone")) %>%
-    select(Milestone, everything()) %>%
-    add_row(.before = 1, Milestone = "Preregistration 1 Pilot Study", Date = "323434", Commit = "d3kk2", Description = "Fake commit for prereg") %>%
-    add_row(.before = 20, Milestone = "Deviation from Preregistration 1", Date = "323434", Commit = "j6jh6", Description = "Fake commit for prereg2") %>%
-    add_row(.before = 47, Milestone = "Accepted at Nature", Date = "323434", Commit = "dgaffae", Description = "Accepted Manuscript!!1!") %>%
-    mutate(
-      Commit = glue(str_c(
-        "HYPERLINK(\"",
-        str_c(repo_url, "/tree/", "{Commit}"),
-        "\", \"",
-        "{Commit}",
-        "\")"
-      ))
-    )
-  
-  
-  # Identify rows that contain Milestones (e.g., (deviations from) Preregistrations, major manuscript updates, etc.)
-  # All other rows containing intermediate commits are flagged to be collapsed in the xlsx document.
-  milestone_rows = which(gitlog$Milestone != "")
-  
-  rows_to_collapse = list()
-  
-  for (i in 1:length(milestone_rows)) {
-    
-    if (i == length(milestone_rows)) {
-      rows_to_collapse[[i]] <- seq(milestone_rows[i]+2, nrow(gitlog)+1, 1)
-    } else {
-      
[…]

### 2021-10-28 preregistrations/1_pilot/preregistration.Rmd
fix broken file paths

@@
 # Source necessary objects
-codebook = read_csv(here("data", "1_pilot_data", "clean", "pilot_self_report_codebook.csv"))
-pilot_self_report = read_csv(here("data", "1_pilot_data", "clean", "pilot_self_report.csv"))
+codebook <- read_csv(here("data", "1_pilot", "pilot_self_report_codebook.csv"))
+pilot_self_report = read_csv(here("data", "1_pilot", "pilot_self_report.csv"))
 ```
-
-*NOTE: This document serves as a time-stamped Preregistration of the pilot study.
-For each study/data collection, we will complete one preregistration.
-Each preregistration is written as a dynamic document in manuscript form.
-After data collection, the preregistration document will be extended to incorporate the analyses results and discussion.
-For each study/data collection, the document will go through a couple of milestones: 1) Preregistration; 2) Potential deviations from the preregistration; 3) Final manuscript.
-Each of these milestones will be time-stamped and tagged on [Github](https://github.com/StefanVermeent/attention_pilot) for easy referencing.*
-
-\linebreak
 
@@
 Whenever participants had to respond by use of their keyboard, the cursor was hidden from the screen to minimize distractions.
-Code for the three tasks can be found on [Github](https://github.com/StefanVermeent/attention_pilot/tree/main/tasks).
+Code for the three tasks can be found on [Github](https://github.com/StefanVermeent/attention_project/tree/main/tasks).
 

### 2021-11-03 preregistrations/1_pilot/preregistration.Rmd
update of power analysis and preregistration

@@
 # Source necessary objects
+power_linear      <- read_csv(here("data", "1_pilot", "simulation", "power_linear_model.csv")) %>% mutate(power = round(power, 0))
+power_mixed       <- read_csv(here("data", "1_pilot", "simulation", "power_mixed_model.csv")) %>% mutate(power = round(power, 0))
 codebook          <- read_csv(here("data", "1_pilot", "pilot_self_report_codebook.csv"))
-pilot_self_report = read_csv(here("data", "1_pilot", "pilot_self_report.csv"))
+pilot_self_report <- read_csv(here("data", "1_pilot", "pilot_self_report.csv"))
+
 ```
@@
 Experiencing childhood adversity can have detrimental effects on cognitive outcomes [@hackman_2010; @ursache_2016].
-However, the hidden talents approach suggests that people living in adversity might develop specific skills that help them navigate harsh and unpredictable environments.
+However, the hidden talents approach suggests that people living in adversity might develop specific skills that help them navigate harsh and unpredictable environments [@ellis_2017; @frankenhuis_2013].
 For example, recent work shows that growing up in stressful environments can enhance working memory updating, at least under certain conditions [@young_2018].
 However, the cognitive mechanisms responsible for lowered (impairments) and improved (enhancements) performance on various tests remain poorly understood.
-Some studies suggest that specific types of adversity lead to specific abilities independent of the current context [@fields_2021].
-Others only find enhancement effects when testing conditions are made more ecologically relevant [@young_2018, submitted for publication].
+Some studies suggest that specific types of adversity lead to specific abilities independent of the current context [@fields_2021; @nweze_2020].
+Others only find enhancement effects under stressful [@mittal_2015; @young_2018] or more ecologically relevant [@young_submitted] testing conditions.
 
 Further progress depends on addressing two related questions: First, to what extent are patterns of impairment and enhancement independent?
-Cognitive processes that are typically targeted in hidden talents studies (e.g., working memory, task-switching) are complex processes that share many of the same more basic processes [@conway_2021, @kovacs_2019; @verbruggen_2014].
+Cognitive processes that are typically targeted in hidden talents studies (e.g., working memory, task-switching) are complex processes that share many of the same more basic processes [@conway_2021; @kovacs_2019; @verbruggen_2014].
 This overlap means that impairment and enhancement patterns across tasks could be driven by the same underlying process.
@@
 When the effect of adversity exposure on cognitive performance is measured by looking at RTs, enhancements or impairments might be driven by any of these subprocesses.
-Formal cognitive models such as the Drift Diffusion Model [DDM; @ratcliff_2008; @ratcliff_2015] might provide inside into the exact processes that are impaired or enhanced by adversity.
-In this pilot study, we leverage the DDM to better understand the processes involved in performance differences.
+Formal cognitive models such as the Drift Diffusion Model [DDM; @ratcliff_2008; @ratcliff_2015] might provide inside into the specific processes that are impaired or enhanced by adversity.
+
+Hidden talents research makes the often implicit assumption that enhanced abilities might reflect an externally focused orientation on the present [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013].
+For example, @frankenhuis_2016 argued that living in a harsh and unpredictable environment might require a stronger present-orientation (as opposed to being focused on the future) in order to deal with unpredictable threats and benefit from fleeting rewards.
+Empirical findings seem to point in the same direction.
+Enhanced performance on attention-shifting [@fields_2021; @mittal_2015] and working memory updating [@nweze_2020; @young_2018] have been explained in terms of an ability to track contextual changes, which is thought to help cope with changing information.
+One possibility that has yet to be empirically tested is that such effects are driven by a shared present and/or externally oriented attention mechanism.
+In this pilot study, we leverage the DDM to better understand the processes involved in performance differences, specifically by focusing on basic attention skills.
 
@@
 The model assumes that the decision-making process constitutes a noisy information accumulation process that continues until one of two decision boundaries (corresponding to the response options) is reached.
-As soon as the accumulation process reaches a decision boundary, the process terminates and a motor response is initiated (e.g, pressing a a key on the keyboard).
+As soon as the accumulation process reaches a decision boundary, the process terminates and a motor response is initiated (e.g., pressing a key on the keyboard).
 The DDM accounts for the full pattern of correct RTs, incorrect RTs, and proportion of errors.
-In doing so, it recovers four parameters that map onto distinct cognitive processes ([@voss_2004]; see Figure XXX).
+In doing so, it recovers four parameters that map onto distinct cognitive processes ([@voss_2004]; see Figure 1A).
+
 The accumulation process is modeled as a drift rate (*v*), reflecting basic cognitive speed/speed of information uptake.
-large values of *v* reflect more efficient processing (faster and more accurate).
+Large values of *v* reflect more efficient processing (faster and more accurate).
 The starting point (*z*) reflects the starting position of the accumulation process relative to the two decision boundaries.
 Unless people are biased to favor one response over the other (e.g., due to a skewed reward structure), (*z*) is usually fixed to be equidistant from both decision boundaries (*a*).
-larger values of *a* indicate that the boundaries are further removed from each other, leading to more conservative responses (slower but more accurate) while smaller values of *a* reflect more liberal responses (faster but less accurate).
-Thus, *a* reflects the speed-accuracy trade-off made by an indidual.
+Larger values of *a* indicate that the boundaries are further removed from each other, leading to more conservative responses (slower but more accurate) while smaller values of *a* reflect more liberal responses (faster but less accurate).
+Thus, *a* reflects the speed-accuracy trade-off made by an individual.
 The fourth and final parameter is the non-decision time (*Ter*), which includes processes that are not related to the decision process (e.g., initial stimulus encoding and initiating the motor response).
 
+If people from adversity develop hidden talents, this should be reflected in specific DDM parameters.
+First and foremost, an enhanced cognitive ability would lead to more efficient information processing on tasks measuring that ability, which will be reflected in a higher drift rate *v* (or the other way around in case of a cognitive impairment).
+Second, enhanced performance could also be (partly) driven by the ability to quickly detect relevant stimuli before the onset of the decision-making process.
+Even if *v* is similar across levels of adversity, faster detection and encoding of relevant stimuli would allow individuals to start accumulating information sooner.
+This would be reflected in *Ter*.
+Finally, differences in performance across levels of adversity could be (partly) caused by the use of different strategies instead of by cognitive efficiency per se, for example, favoring speed over accuracy or vice versa.
+A tendency to adopt a specific strategy might be linked to individual differences in constructs like impulsivity.
+It is an open question whether performance differences driven by strategies should count as hidden talents [@young_2020].
+
 The current study aims to address these questions using an incremental preregistration approach.
-In the current preregistered pilot study, we measured various forms of adversity with a focus on unpredictability on different time scales.
-In addition, Participants completed three attention tasks that differed in the extent to which they would favor or punish a broad, externally focused attention style.
+In the current preregistered pilot study, we measured various forms of adversity with a focus on unpredictability on different time scales (e.g., seconds, days, years).
+In addition, participants completed three basic attention tasks (Flanker Task, Cued Attention Task, and Change Detection Task) that differed in the extent to which they would favor or punish a broad, externally focused attention style.
 We applied the DDM to the RT and accuracy data to decompose performance.
-If people from adversity develop specialized attention skills, this should be reflected in DDM parameters.
-First and foremost, more attention on the relevant stimuli should be reflected in a higher drift rate *v*.
-Second, enhanced initial detection of peripheral stimuli should be reflected in a lower non-decision time (*Ter*) since this would allow the decision process to initiate sooner in time.
-Beyond attention skills, people from adversity might have a smaller boundary separation *a*, reflecting more impulsive responses.
 
@@
 
-Our primary hypotheses were as follows:
+## Primary hypotheses
 
-1) People with more exposure to violence and environmental unpredictability during childhood will show enhanced or equal performance compared to people from safe environments on tasks that require quickly detecting peripheral stimuli and detecting subtle changes (i.e., the Cued Attention Task and Change Detection Task).
+1)	People with more exposure to violence during childhood will show enhanced performance compared to people from safe environments on tasks that require quickly detecting peripheral stimuli and detecting subtle changes (i.e., the Cued Attention Task and Change Detection Task).
 This effect is explained by at least one of two DDM parameters: the speed of information uptake *v* and non-decision time *Ter*.
+2)	People with more exposure to violence during childhood will perform worse on tasks that require ignoring distracting peripheral stimuli (i.e., the Flanker Task).
+This effect is at least partly explained by a wider initial attentional focus, (operationalized through the attentional width parameter of a special adaptation of the original DDM; see [data analyses](#ddm_plan) for details).
 
-2) People with more exposure to violence and environmental unpredictability during childhood will perform worse on tasks that require ignoring distracting peripheral stimuli (i.e., the Flanker Task).
-This effect is at least partly explained by a wider initial attentional focus, (operationalized through the attentional width parameter of a special adaptation of the original DDM; see [data analyses](#ddm_plan) for more details).
+## Exploratory analyses
 
-In addition, the pilot study had a number of secondary aims: First, we investigated whether the link between measures of adversity and attention would be contingent on the timescale of the adversity items.
-More specifically, we explored whether stable attention styles might be better predicted by items of momentary unpredictability (e.g., "things were often chaotic in my house") than by items of temporally extended unpredictability ("At least one of my parents changed jobs frequently").
-Second, we conducted exploratory correlation analyses between measures of adversity, attention, and measures of temporal orientation (i.e., impulsivity and future orientation).
-Third, we explored whether potential effects of adversity on task performance might be moderated by current anxiety.
-Fourth, we explored effects of hunger and sleep deprivation on performance.
-Finally, we explored the extent to which our retrospective measures of adversity correlate with current depressive symptoms, which might reflect a retrospective negativity bias driven by current psychopathological symptoms [@nivison_2021].
+1) Develop an [analysis pipeline](#ddm_plan) to estimate DDM parameters for use as dependent variables.
+2) Investigate the [factor structure](#efa) of several measures of unpredictability on different timescales through exploratory factor analysis (EFA).
+We then reran the analyses of the primary hypotheses using unpredictability as the independent variable, operationalized through composites of the original scales and through the factors resulting from the EFA.
+3) Explore the role of state anxiety, hunger, and sleep deprivation as potential moderators of the relationship between adversity and attention performance.
+Anxiety might enhance attention performance by making participants more vigilant.
+Conversely, hunger and sleep deprivation could have a negative effect on performance.
+4) Explore bivariate correlations between measures of adversity, attention, and measures of temporal orientation (i.e., impulsivity and future orientation).
+5) Explore the correlation between current depressive symptoms and retrospective measures of adversity, which might reflect a negativity bias in recalling past events driven by current depressive symptoms [@nivison_2021].
 
@@
 
-Participants were 450 US-based individuals between the ages of 18 and 30 (*M* = `r #TBD`, *SD* = `r #TBD`).
-We decided for this age cut-off to limit the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 [@salthouse_2010].
-Recruitment took place through Prolific.
-Participants were eligible for for the study if they were between 18 and 30 years old, if they were currently residing in the United States, if they did not have a history of brain injury, and if they had normal or corrected-to-normal eyesight.
+Participants were 550 US-based individuals between the ages of 18 and 30 (*M* = `r #TBD`, *SD* = `r #TBD`).
+We decided for this age cut-off to reduce the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 [@salthouse_2010].
+Recruitment took place through Prolific Academic [www.prolific.co].
+Participants were eligible for the study if they were from the United States and if they spoke fluent English.
 
-The sample size was determined based on a power analysis for detecting a standardized effect of 0.1 and 90% power. [preregistered power analysis](https://osf.io/gfpnr/))).
-[TO BE FILLED IN]
+We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the optimal number of participants to include (more information including all simulation code on [Github](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/1_pilot/scripts).
+We ran simulations for two scenarios: A linear regression model to test the effect of adversity (standardized) on attention performance (standardized) and a mixed regression model to test the adversity (standardized) X task condition (sum-coded) interaction, including a random intercept for subjects.
+We ran simulations for a standardized $\beta$ of 0.10 and 0.15.
+
+In determining the final sample size, we weighed the simulation results against our uncertainty about certain model parameters (mostly the fixed effects and sigma term for the mixed model) and the fact that this was a first pilot study.
+For the mixed model, we found that power was > .80 for the adversity X task condition interaction with *N* = 450 or more.
+For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`.
+This was significantly higher for $\beta$ = 0.10 (*N* = `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .80, alternative = "two.sided")[['n']] %>% round(0)` when power = `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .80, alternative = "two.sided")[['power']] %>% round(1)` and `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .890, alternative = "two.sided")[['n']] %>% round(0)` when power = `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .90, alternative = "two.sided")[['power']] %>% round(1)`).
+Thus, we decided on sampling 550 participants with an anticipated final sample size of around 500 due to drop-out and data exclusions.
 
@@
 We applied several exclusion criteria prior to analyzing the data.
-First, we excluded participants with incomplete data on any of the attention tasks (*N* = `r #TBD `).
+First, we excluded participants who did not complete the full study and those who had incomplete data on any of the attention tasks (*N* = `r #TBD `).
 Second, we analyzed responses to the attention checks and reversed coded items in the questionnaire part of the experiment.
-We excluded participants if they missed both attention check items or if they had suspicious response patterns (e.g., consistently endorsing high response options even when some items were reversed coded) (*N* = `r #TBD `).
+We excluded participants if they missed both attention check items or if they had suspicious response patterns (e.g., consistently endorsing high response options even when some items were reverse coded) (*N* = `r #TBD `).
 
@@
 For the Drift Diffusion analyses, it is important that each response is generated by a process of active information accumulation (i.e., a diffusion process, as opposed to guessing).
-To this end, trials with reaction times < 250ms or longer than 3500ms [@ratcliff_2015] were excluded from the analyses (*N* = `r #TBD `).
+To this end, trials with reaction times < 250 ms or > 3500 ms [@ratcliff_2015] were excluded from the analyses (*N* = `r #TBD `).
 Participants with more than 10 removed trials were excluded from the analyses (N = `r #TBD `).
 
-The exclusion criteria listed above are our best *a-priori* guesses. We expect to develop new criteria empirically after collecting the data.
+The exclusion criteria listed above are our best *a-priori* guesses. However, we expect to develop additional criteria empirically after collecting the data.
+
+## Measures {#measures}
+
+The attention tasks were programmed in JsPsych version 3.6.1 [@deLeeuw_2015].
+
+### Cued Attention Task {#cued_attention}
+
+The Cued Attention Task was an adaptation of the Posner task, which measures basic spatial attention speed [@posner_1980].
+On each trial, a left- or right-pointing arrow was presented in one of eight random locations at a distance of 300 pixels from the center of the screen (see Figure 2A).
+Participants had to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard.
+On 50% of the trials, the arrow was preceded by a cue ('\*') in the exact same location (i.e., 'cued' trials).
+On the other 50% of the trials, the cue ('\*') was presented at the center of the screen (i.e., 'neutral' trials).
+Thus, on the cued trials, the location of the cue deterministically predicted the location of the arrow, whereas on the neutral trials the arrow always appeared in a different location.
+
+Each trial started with a fixation cross presented at the center of the screen for 1000 ms.
+Then, the cue was presented for 250 ms either at the center of the screen or in the location where the arrow would appear next.
+Finally, the arrow was presented 250 ms after the onset of the cue and shown until a response was given.
+The Cued Attention Task began with eight practice trials (four cued and four neutral trials) in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
+After finishing the practice round, participants completed a single test block consisting of a total of 64 trials, consisting of two repetitions of all parameter combinations: arrow location (top center vs.
+top left vs.
+center left vs.
+bottom left vs.
+bottom center vs.
+bottom right vs.
+center right vs.
+top right) X arrow direction (left vs.
+right) X condition (cued vs.
+neutral).
+The main performance measures are RTs and accuracy for each condition.
+
+### Flanker Task {#flanker}
+
+The Flanker Task measures selective attention and response inhibition [@eriksen_1974].
+On each trial of the Flanker task, participants were presented with a set of five arrows pointing either left or right.
+Their job was to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right (see Figure 2B).
+On 50% of the trials, the flanking arrows pointed in the same direction as the central arrow (i.e., congruent trials), and on the other 50% of the trials they pointed in the opposite direction (i.e., incongruent trials).
+The arrows were randomly presented in the top-half or bottom-half of the screen.
+This was done to prevent participants from rigidly fixating on the center of the screen, which might reduce the interfering effect of the flanking arrows.
+
+Each trial started with a fixation cross presented at the center of the screen.
+After a delay of 1000ms, the arrows are presented either in the top- or bottom-half of the screen.
+The Flanker task began with eight practice trials in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
+After finishing the practice round, participants completed a single test block consisting of a total of 64 trials, consisting of eight repetitions of all parameter combinations: Arrow location (top vs.
+bottom) X central arrow direction (left vs.
+right) X condition: (congruent vs.
+incongruent).
+Participants did not receive performance feedback during the test block.
+The main performance measures were RTs and accuracy for each condition.
+
+### Change Detection Task {#change}
+
+The Change Detection Task measures the ability to detect subtle spatial changes.
+On each trial of the change detection task, participants were presented with five colored circles against a grey background, each with a radius of 15 pixels (see Figure 2C).
+Each circle was located in a semi-random location around the central fixation cross.
+The location of each circle was sampled within a pre-specified area of 50 by 50 pixels to prevent overlap.
+Participants had 1000ms to memorize the locations of the five circles.
+After 1000ms, the circles disappeared for 500ms and then reappeared again.
+On 50% of the trials, one of the circles had moved to another location with a fixed displacement of 40 pixels in a 360 degree direction.
+On the other 50% of the trials, all circles were still in the same location as the initial memory display.
+Participants had to indicate whether they thought one of the circles changed location (by pressing the left-arrow key) or whether they thought all circles were still in the same location (by pressing the right-arrow key).
+Note that the only potential difference between the memory and probe display on each trial was the displacement of **one** circle; the remaining circles were always in the same place and circles never changed color within a trial.
+
+The change detection task started with five practice trials in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
+After finishing the practice round, participants completed two test blocks consisting of 25 trials each (50 trials in total).
+The design was fully counterbalanced so that each circle moved on five trials and was a different color each time it moved *between* trials.
+Participants did not receive performance feedback during the two test blocks.
+The main performance measures are RTs and accuracy across all trials.
+
+### Current state {#state}
+
+We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [STAI-S; @spielberger_1999].
+The STAI-S contains 20 short items measuring current anxiety (e.g., "I feel tense"; See [Table S1](#appendix) for an overview of all items).
+Participants rated each item on a scale of 1 (not at all) to 4 (very much so).
+An overall state anxiety variable was computed by averaging across the 20 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+
+In addition, participants answered five questions relating to specific states: "Are you currently sick?" (rated as yes or no); "Have you eaten a full meal today?" (rated as yes or no); "How hungry do you feel right now?" (rated from 1 (not at all) to 5 (very hungry)); "How well did you sleep last night?" (rated from 1 (very poorly) to 5 (very well)); "How rested or refreshed did you feel when you woke up this morning?" (rated from 1 (not at all) to 5 (very rested)).
+We computed an overall sleep deprivation composite by standardizing and averaging across the two unweighted sleep-related items (*M* = `r #TBD `, *SD* = `r #TBD `).
+
+### Violence exposure {#violence}
+
+Violence exposure was measured using the Neighborhood Violence Scale [NVS; @frankenhuis_2018; @frankenhuis_deVries_2020] and two items assessing exposure to physical fights before age 13.
+The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up"; See [Table S2](#appendix) for an overview of all items).
+Participants rated each on a scale from 1 (never true) to 5 (very often true).
+The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
+The items of the NVS were averaged together (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+Similarly, we averaged the scores on the two fighting items together.
+Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average (*r* = `r #TBD `).
+
+### Unpredictability {#unpred}
+
+Perceived unpredictability before age 13 was measured using two different scales: A scale of perceived childhood unpredictability used in previous research [@mittal_2015; @young_2018] and an adaptation of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019].
+The perceived childhood unpredictability scale contained eight items measuring perceived unpredictability before age 13 (e.g, "My family life was generally inconsistent and unpredictable from day-to-day"; See [Table S3](#appendix) for an overview of all items).
+Participants rated each on a scale from 1 (never true) to 5 (very often true).
+
+We included the QUIC because it captures several dimensions of environmental and household unpredictability.
+The QUIC distinguishes between items capturing more short-term unpredictability (i.e., on the level of seconds to minutes) and more long-term unpredictability (i.e., on the level of days to months).
+The scale of perceived childhood unpredictability combines items on different time scales.
+Some items measure unpredictability on a relatively short-term scale (e.g., item 1) while other items measure unpredictability on a long-term scale (e.g., item 3).
+Unpredictability on different time scales might have different effects on the development of specific attention styles.
+
+The QUIC consists of 38 items across five subscales: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 5) Safety and security (See [Table S4](#appendix) for an overview of all items).
+We made two changes to the original scale as described in @glynn_2019.
+First, while the original QUIC items refer to perceived unpredictability either before age 12 or age 18, we adapted all items to refer to experiences before age 13.
+This was done to reduce cognitive load from having to go back-and-forth between different time scales.
+Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
+This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
+
+We computed several unweighted unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overall QUIC variable by averaging all 38 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `).
+See also [below](#efa) for details on a factor analysis based on the individual items across scales.
+
+### Household chaos {#chaos}
+
+We assessed household chaos before age 13 using an adaptation of the Confusion, Hubbub, and Order Scale [CHAOS; @matheny_1995].
+The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late"; See [Table S5](#appendix) for an overview of all items).
+We made two changes to the original scale as described in @matheny_1995.
+First, all items were converted from the present tense to the past tense, and were endorsed as applying to participants' lives before age 13.
+Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
+This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
+An overall household chaos variable was computed by averaging the 15 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+
+### Poverty exposure {#ses}
+
+Participants' perceived level of resource scarcity before age 13 was measured using seven items (e.g., "Your family had enough money to afford the kind of home you all needed"; See [Table S6](#appendix) for an overview of all items).
+Participants rated each item on a scale from 1 (never true) to 5 (very often true).
+Scores for the first six items were reverse coded so that higher scores indicated more perceived resource scarcity.
+The items were averaged together to create an unweighted composite scale (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+
+In addition, we measured several indicators of objective SES before age 13.
+First, participants separately indicated the highest education of their mother and father on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'.
+The mother and father education level were averaged to create an overall unweighted parental education composite (*M* = `r #TBD `, *SD* = `r #TBD `).
+Participants also indicated their family's household income before age 13 on a 6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'.
+Scores were reverse coded so that higher scores indicated higher levels of poverty.
+
+We created a composite score of poverty exposure before age 13 by averaging together the standardized scores of perceived level of resource scarcity, overall parental education, and household income.
+
+### Impulsivity {#impulsivity}
+
+We assessed impulsivity with the Motor Impulsivity subscale of the Barrett Impulsivity Scale (BIS; short form; [@patton_1995; @spinella_2007]).
+The Motor Impulsivity subscale of the BIS consists of five items (e.g., "I do things without thinking"; See [Table S7](#appendix) for an overview of all items).
+We did not include the Non-planning subscale because it overlapped substantially with the Future Orientation Scale described below.
+In addition, we did not include the Attention impulsivity subscale because it included items which we deemed to be mostly irrelevant for our target population (e.g., "I 'squirm' at plays or lectures").
+We changed the original 4-point rating scale (rarely/never to almost always) to a 5-point rating scale ranging from 1 (never true) to 5 (very often true).
+An overall impulsivity variable was computed by averaging the five unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+
+### Future Orientation {#future_orientation}
+
+We assessed future orientation with an adapted version of the Future Orientation Scale [FOS; @steinberg_2009].
+The original scale consists of 15 sets of opposing items separated by "BUT" (e.g., "Some people like to plan things out one step at a time BUT other people like to jump right into things without planning them out beforehand").
+Participants first choose the item that best matches their general preference, and then indicate whether the statement is "really true" or "somewhat true".
+We adapted this format in a couple of ways.
+First, we converted the two statements per item to a single statement by picking the statements in the original right-hand column.
+Second, we adapted the 15 statements from a third-person to a first-person format.
+These changes were made in an attempt to reduce the cognitive load of the items.
+We worried that people with less formal education or who were sitting in a noisier environment would struggle with the length of the original items.
+
+In addition, item 8 of the original scale ("[...] other people would rather spend their money right away on something fun than save it for a rainy day") was changed to "I'd rather spend money right away than save it for a rainy day" (i.e., dropping the phrase "on something fun") to make it more general with regard to the thing that money is spent on.
+For people from adversity, spending money right now instead of saving it for the future might often be born out of necessity (e.g., having just enough money for food and shelter; being in debt) instead of a failure to delay gratification.
+See [Table S8](#appendix) for an overview of all adapted items).
+Finally, the rating scale was adapted from the original 4-point scale (ranging from really true for the left-hand statement to really true for the right-hand statement) to a 5-point scale ranging from 1 (never true) to 5 (very often true).
+
+An overall future orientation variable was computed by averaging the 15 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+In addition, we calculated subscales for "Planning ahead" (items 1, 6, 7, 12 and 13), "Time perspective" (items 2, 5, 8, 11 and 14) and "Anticipation of future consequences" (items 3, 4, 9, 10 and 15).
+
+### Depressive symptoms {#depression}
+
+We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD; @radloff_1977].
+The scale consists of 20 items (e.g., "I do things without thinking"; See [Table S9](#appendix) for an overview of all items).
+Participants rate each item on a scale of 1 (rarely or none of the time (less than 1 day)) to 4 (most or all of the time (5-7 days)).
+An overall depression variable was computed by averaging the 20 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
 
@@
 
-The experiment was completed on the participants' own laptop or desktop computer and consisted of four parts: consent, attention task battery, questionnaire battery, brief demographics form, and final checks and the opportunity to give feedback on the experiment.
-[something on ethical approval].
+The experiment was completed on the participants' own laptop or desktop computer and consisted of five parts: consent, attention task battery, questionnaire battery, brief demographics form, and final checks including the opportunity to give feedback on the experiment.
+Participants were allowed to refrain from answering any of the questionnaire items, but were prompted with a warning once when moving to the next page if one of the items was not answered (which they could ignore).
 
@@
 After successfully resizing the screen, participants completed all three tasks.
-Whenever participants had to respond by use of their keyboard, the cursor was hidden from the screen to minimize distractions.
+During the task, the cursor was hidden from the screen to minimize distractions.
 Code for the three tasks can be found on [Github](https://github.com/StefanVermeent/attention_project/tree/main/tasks).
@@
 
-Finally, the demographics questions asked about the participant's age, weight, height, physical activity, sex at birth, gender, ethnicity, social class (current and during childhood), education level (one's own as well as parents' education level), occupation, and household income.
+Finally, the demographics questions asked about the participant's age, weight, height, physical activity, sex at birth, gender, ethnicity, social class (current and during childhood), education level (one's own as well as parents' education level), occupation, and household income (current and during childhood).
 At the end of the experiment, we asked participants if they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.
 
-## Measures {#measures}
-
-The attention tasks were programmed in JsPsych version 3.6.1 [@deLeeuw_2015].
-
-### Cued Attention Task {#cued_attention}
-
-The cued attention task was an adaptation of the Posner task [@posner_1980] which measures basic spatial attention speed.
-On each trial, a left- or right-pointing arrow is presented in one of eight random locations at a distance of 300 pixels from the center of the screen (see Figure 1B).
-Participants had to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard.
-On 50% of the trials, the arrow was preceded by a cue ("\*") in the exact same location (i.e., cued trials).
-On the other 50% of the trials, the cue ("\*") was presented at the center of the screen (i.e., neutral trials).
-Thus, on the cued trials, the location of the cue deterministically predicted the location of the arrow, whereas on the neutral trials the arrow always appeared in a different location.
-
-Each trial started with a fixation cross presented at the center of the screen for 1000ms.
-Then, the cue was presented for 250ms either at the center of the screen or in the location where the arrow would appear next.
-Finally, the arrow was presented 250ms after the onset of the cue and shown until a response was given.
-The cued attention task began with eight practice trials (four cued and four neutral trials) in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
-After finishing the practice round, participants completed a single test block consisting of a total of 64 trials (two repetitions of all parameter combinations: arrow location (top center vs.
-top left vs.
-center left vs.
-bottom left vs.
-bottom center vs.
-bottom right vs.
-center right vs.
-top right) X arrow direction (left vs.
-right) X condition (cued vs.
-neutral)).
-The main performance measures are RTs and accuracy for each condition.
-
-### Flanker task {#flanker}
-
-The Flanker Task measures selective attention and response inhibition.
-On each trial of the Flanker task [@eriksen_1974], participants were presented with a set of five arrows pointing either left or right.
-Their job was to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right (see Figure 1A).
-On 50% of the trials, the flanking arrows pointed in the same direction as the central arrow (i.e., congruent trials), and on the other 50% of the trials they pointed in the opposite direction (i.e., incongruent trials).
-The arrows were randomly presented in the top-half or bottom-half of the screen.
-This was done to prevent participants from rigidly fixating on the center of the screen, which would reduce the interfering effect of the flanking arrows.
-
-Each trial started with a fixation cross presented at the center of the screen.
-After a delay of 1000ms, the arrows are presented either in the top- or bottom-half of the screen.
-Participants were given 2000ms to indicate the direction of the center arrow.
-The Flanker task began with eight practice trials in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
-After finishing the practice round, participants completed a single test block consisting of a total of 64 trials (eight repetitions of all parameter combinations: arrow location (top vs.
-bottom) X central arrow direction (left vs.
-right) X condition: (congruent vs.
-incongruent)).
-Participants did not receive performance feedback during the test block.
-The main performance measures are RTs and accuracy for each condition.
-
-### Change detection task {#change}
-
-The Change Detection Task measures the ability to detect subtle spatial changes.
-On each trial of the change detection task, participants were presented with five colored circles against a grey background, each with a radius of 15 pixels (see Figure 1C).
-Each circle was located in a random location within a pre-specified area of 50 by 50 pixels to prevent overlap.
-Participants had 1000ms to memorize the locations of the five circles around the fixation cross.
-After 1000ms, the circles briefly disappeared for 500ms and then reappeared again.
-On 50% of the trials, one of the circles had moved to another location with a fixed displacement of 40 pixels in a 360 degree direction.
-On the other 50% of the trials, all circles were still in the same location as the initial memory display.
-Participants have to indicate whether they thought one of the circles changed location (by pressing the left-arrow key) or whether they thought all circles were still in the same location (by pressing the right-arrow key).
-Note that the only potential difference between the memory and probe display was the displacement of **one** circle; the remaining circles were always in the same place and circles never changed color within a trial.
-
-The change detection task started with five practice trials in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
-After finishing the practice round, participants completed two test blocks consisting of 25 trials each (50 trials in total).
-The design was fully counterbalanced so that on each "movement" trial, each of the five circles changes five times per block for each of the five colors.
-Participants did not receive performance feedback during the two test blocks.
-The main performance measures are RTs and accuracy across all trials.
-
-### Current state {#state}
-
-We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [STAI-S; @spielberger_1999].
-The STAI-S contains 20 short items measuring current anxiety (e.g., "I feel tense"; See [Table S1](#appendix) for an overview of all items).
-Participants rated each item on a scale of 1 (not at all) to 4 (very much so).
-An overall state anxiety variable was computed by averaging across the 20 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-
-In addition, participants answered five questions relating to specific states: "Are you currently sick?" (rated as yes or no); "Have you eaten a full meal today?" (rated as yes or no); "How hungry do you feel right now?" (rated from 1 (not at all) to 5 (very hungry)); "How well did you sleep last night?" (rated from 1 (very poorly) to 5 (very well)); "How rested or refreshed did you feel when you woke up this morning?" (rated from 1 (not at all) to 5 (very rested)).
-
-We computed an overall sleep deprivation composite by standardizing and averaging across the two sleep-related items (*M* = `r #TBD `, *SD* = `r #TBD `).
-The first hunger item (i.e., "have you eaten a full meal today?") was recoded as half a standard-deviation above or below the mean (standardized).
-People who had not eaten a full meal were coded as -0.5, and those who had eaten a full meal were coded as 0.5.
-A hunger composite was calculated by averaging the recoded meal item and the hunger item (*M* = `r #TBD `, *SD* = `r #TBD `).
-
-### Violence exposure {#violence}
-
-Violence exposure was measured using the Neighborhood Violence Scale [NVS; @frankenhuis_2018; @frankenhuis_deVries_2020] and two items assessing exposure to physical fights before age 13.
-The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up"; See [Table S2](#appendix) for an overview of all items).
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
-The items of the NVS were averaged together (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-Similarly, we averaged the scores on the two fighting items together.
-Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and averaging them together (*r* = `r #TBD `).
-
-### Unpredictability {#unpred}
-
-Perceived unpredictability before age 13 was measured using two different scales: A scale of perceived childhood unpredictability used in previous research [@mittal_2015; @young_2018] and an adaptation of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019].
-The perceived childhood unpredictability scale contained eight items measuring perceived unpredictability before age 13 (e.g, "My family life was generally inconsistent and unpredictable from day-to-day"; See [Table S2](#appendix) for an overview of all items).
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-
-We included the QUIC because it captures several dimensions of environmental and household unpredictability with a better (but not perfect) distinction between items capturing more short-term unpredictability (i.e., on the level of seconds to minutes) and more long-term unpredictability (i.e., on the level of days to months).
-Note that the scale of perceived childhood unpredictability combines items on a short-term scale (e.g., item 1) with items measured on a long-term scale (e.g., item 3) which might have different effects on the development of specific attention styles.
-
-The QUIC consists of 38 items across five subscales: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 5) Safety and security (See [Table S4](#appendix) for an overview of all items).
-We made two changes to the original scale as described in @glynn_2019: First, while the original QUIC items refer to perceived unpredictability either before age 12 or age 18, we adapted all items to refer to participants' experiences before age 13.
-This was done to reduce cognitive load from having to mentally switch timescales between items and different scales and because the youngest eligible participants were 18 years old.
-Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
-This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
-
-We computed several unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overal QUIC variable by averaging all 38 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `).
-
-### Household chaos {#chaos}
-
-We assessed household chaos before age 13 using an adaptation of the Confusion, Hubbub, and Order Scale [CHAOS; @matheny_1995].
-The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late"; See [Table S5](#appendix) for an overview of all items).
-We made two changes to the original scale as described in @matheny_1995: First, all items were converted from the present tense to the past tense, and were endorsed as applying to partipants' life before age 13.
-Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
-This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
-An overall household chaos variable was computed by averaging the 15 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-
-### Poverty exposure {#ses}
-
-Participants' perceived level of resource scarcity before age 13 was measured using 7 items (e.g., "Your family had enough money to afford the kind of **home** you all needed"; See [Table S6](#appendix) for an overview of all items).
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-Scores for the first six items were reversed so that higher scores indicated more perceived resource scarcity.
-The items were averaged together to create a composite scale (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-
-In addition, we measured several indicators of objective SES before age 13.
-First, participants separately indicated the highest education of their mother and father on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'.
-The mother and father education level were averaged to create an overall parental education composite (*M* = `r #TBD `, *SD* = `r #TBD `).
-
-In addition, participants indicated their family's household income before age 13 on a 6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'.
-Scores were reversed so that higher scores indicated higher levels of poverty.
-
-We created a composite score of poverty exposure before age 13 by averaging together the standardized scores of perceived level of resource scarcity, overall parental education, and household income.
-
-### Impulsivity {#impulsivity}
-
-We assessed impulsivity with the Motor Impulsivity subscale of the [Barrett Impulsivity Scale (BIS; short form); @patton_1995; @spinella_2007].
-The Motor Impulsivity subscale of the BIS (short form) consists of five items (e.g., "I do things without thinking"; See [Table S7](#appendix) for an overview of all items).
-We did not include the Non-planning subscale because it overlapped substantially with the Future Orientation Scale described below.
-In addition, we did not include the Attention impulsivity subscale because it included items which we deemed to be mostly irrelevant for our target population (e.g., "I 'squirm' at plays or lectures").
-We changed the original 4-point rating scale (rarely/never to almost always) to a 5-point rating scale ranging from 1 (never true) to 5 (very often true).
-
-An overall impulsivity variable was computed by averaging the 5 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-
-### Future Orientation {#future_orientation}
-
-We assessed future orientation with an adapted version of the Future Orientation Scale [FOS; @steinberg_2009].
-The original scale consists of 15 sets of opposing items separated by "BUT" (e.g., "Some people like to plan things out one step at a time BUT other people like to jump right into things without planning them out beforehand").
-Participants first choose the item that best matches their general preference, and then indicate whether the statement is "really true" or "somewhat true".
-We adapted this format in a couple of ways: First, we converted the two statements per item to a single statement by picking the statements in the original right-hand column.
-Second, we adapted the 15 statements from a third-person to a first-person format.
-These changes were made in an attempt to reduce the cognitive load of the items.
-We worried that people with less formal education or who were sitting in a noisier environment would struggle with the length of the original items.
-In addition, item 8 of the original scale ("[...] other people would rather spend their money right away on something fun than save it for a rainy day") was changed to "I'd rather spend money right away than save it for a rainy day" (i.e., dropping the phrase "on something fun") to make it more general with regard to the thing that money is spent on.
-For people from adversity, spending money right now instead of saving it for the future might often be born out of necessity (e.g., having just enough food for food and shelter; being in debt) instead of a failure to delay gratification.
-See [Table S8](#appendix) for an overview of all adapted items).
-Finally, the rating scale was adapted from the original 4-point scale (ranging from really true for the left-hand statement to really true for the right-hand statement) to a 5-point scale ranging from 1 (never true) to 5 (very often true).
-
-An overall future orientation variable was computed by averaging the 15 items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-In addition, we calculated subscales for "Planning ahead" (items 1, 6, 7, 12 and 13), "Time Perspective" (items 2, 5, 8, 11 and 14) and "Anticipation of Future Consequences" (items 3, 4, 9, 10 and 15).
-
-### Depressive symptoms {#depression}
-
-We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD; @radloff_1977].
-The scale consists of 20 items (e.g., "I do things without thinking"; See [Table S9](#appendix) for an overview of all items).
-Participants rate each item on a scale of 1 (rarely or none of the time (less than 1 day)) to 4 (most or all of the time (5-7 days)).
-
-An overall depression variable was computed by averaging the 20 items (*M* = `rr #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+The full experiment was expected to take approximately 35 minutes. Participants were paid £4.38 upon completing the full experiment.
 
@@
 For the change detection task, we calculated an average reaction time across all trials.
-If necessary for meeting model assumptions, reaction times were log-transformed.
+If necessary for meeting model assumptions of normally distributed residuals, reaction times were log-transformed.
 We only planned on performing analyses on the proportion of errors if the average error rate was at least 5% of trials.
@@
 For the Cued Attention Task and Flanker Task, we performed a set of linear mixed effects analyses to test adversity X condition interactions on mean RTs and accuracy (if possible).
+Condition was sum-coded (-1 and 1).
 All models included a random intercept for participants.
 For the Change Detection Task, we performed linear regression to test the main effect of adversity on mean RTs and accuracy (if possible).
-Across separate models, adversity was operationalized as the composite measures of violence exposure, SES, perceived childhood unpredictability, household chaos, and the QUIC subscales (unless they correlated >.80, in which case QUIC subscales were merged together).
+Across separate models, adversity was operationalized as the composite measures of violence exposure, SES, perceived childhood unpredictability, household chaos, and the QUIC subscales (unless they correlated > .80, in which case QUIC subscales were merged together).
 Significant interaction effects were unpacked using simple slopes analysis.
@@
 For the data of the Change Detection Task and the Cued Attention Task, the DDM was fit using Fast-dm [@voss_2007].
-We used Maximum Likelihood estimation as it has been shown to provide reliable estimates with relatively few trials [@lerche_2017]; (see also our power simulations on [Github](https://github.com/StefanVermeent/attention_pilot/tree/main/scripts), which indicated that recovered drift rate and boundary separation parameters generally correlated highly (*r* = .80-.95) with the true data-generating parameters even with 30 trials).
-*a*, *v* and *Ter* were freely estimated and *z* was fixed to 0.5 (the midpoint, indicating no response bias).
+We used Maximum Likelihood estimation as it has been shown to provide reliable estimates with relatively few trials [@lerche_2017] (see also our power simulations on [Github](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/1_pilot/scripts), which indicated that recovered drift rate and boundary separation parameters generally correlated highly (*r* = .80-.95) with the true data-generating parameters even with 30 trials).
+Parameters *a*, *v* and *Ter* were freely estimated and *z* was fixed to 0.5 (the midpoint, indicating no response bias).
 In addition, all inter-trial variability parameters were fixed to 0 to increase model parsimony.
@@
 For the Change Detection task, we had no *a-priori* expectations about performance differences between the change and no-change trials.
-Prior to fitting the DDM models, we ran paired-sample t-tests on the RTs and proportion of errors.
+Prior to fitting the DDM models, we ran paired-sample *t*-tests on the RTs and proportion of errors.
 If either model showed significant mean differences, the DDM was fit separately to data of the change and no-change trials.
@@
 
-The DDM analysis of the Flanker task was done using an adaptation of the standard DDM that was specifically developed to account for Flanker data: The Spotlight Drift Diffusion Model [SDDM; @grange_2016; @white_2018a; @white_2018b, @white_2011].
+The DDM analysis of the Flanker task was done using an adaptation of the standard DDM that was specifically developed to account for Flanker data: The Spotlight Drift Diffusion Model [SDDM; @grange_2016; @white_2018a; @white_2018b; @white_2011].
 The standard DDM model assumes a stable drift rate over time within trials (i.e., the rate of information accumulation does not change over time).
@@
 
-Previous research has shown that it is not useful to interpret both *SD~a~* and *rd* since they trade-off against each other [i.e., a wide initial spotlight combined with a large shrinking rate leads to similar patterns as a narrow initial spotlight combined with a low shrinking rate; @white_2018a; @white_2011].
+Previous research has shown that it is not useful to interpret both *SD~a~* and *rd* because they trade off with each other [i.e., a wide initial spotlight combined with a large shrinking rate leads to similar patterns as a narrow initial spotlight combined with a low shrinking rate; @white_2018a; @white_2011].
 Most previous studies have fixed *SD~a~* and only estimated *rd*, or calculated a *SD~a~*/*rd* ratio, which serves as a measure of interference.
@@
 In this pilot study, we fitted several SDDM models either estimating both attention parameters or fixing *rd* to see how it affected model fit (more details below).
-Model fit was done using the `flankr` package in R [@grange_2016].
+Model fit was done using the *flankr* package in R [@grange_2016].
 
@@
 Significant interaction effects were unpacked using simple slopes analysis.
+
+### Factor structure of unpredictability {#efa}
+
+The three included unpredictability measures contain items that vary in timescale, ranging from features of the childhood environment that might have been unpredictable on a daily basis (e.g., "things were often chaotic in my house") to sources of unpredictability that typically unfold on a timescale of weeks or months (e.g., "At least one of my parents changed jobs frequently").
+Since attention is involved in information processing on a timescale of seconds to minutes, we expect that attention styles should be more strongly related to sources of unpredictability that unfold on a similar timescale.
+However, it is unclear whether current retrospective measures of unpredictability are able to differentiate between different timescales.
+In addition, it might be the case that items of unpredictability on a longer timescale are good proxies for unpredictability on a a more daily timescale.
+We conducted an exploratory factor analysis (EFA) to address these issues.
+
+EFA was used to find common latent factors underlying the three unpredictability/household chaos measures: perceived unpredictability, QUIC, and CHAOS.
+The number of factors to retain was based on parallel analysis, with the added requirement that each factor was composed of at least five items that had their strongest loading on that particular factor.
+Factor loadings above 0.32 were considered meaningful (Tabachnick & Fidell, 2014).
+We anticipated the factors to be correlated substantially, and therefore planned to use oblimin rotation.
 

### 2021-11-03 preregistrations/1_pilot/scripts/0_power_analysis.Rmd
update of power analysis and preregistration

---
title: "0_power_analysis"
author: "Stefan Vermeent"
date: "1-11-2021"
output: pdf_document
---

```{r setup}
library(tidyverse)
library(magrittr)
library(ggpubr)
library(furrr)
library(parallel)
library(RWiener)
library(here)
library(data.table)
library(faux)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(tictoc)

# For parallel processing
cores <- parallel::detectCores()

source(here('preregistrations', '1_pilot', 'scripts', 'custom_functions', 'functions_power.R'))

```

# Introduction

This is a power analysis for the cognitive tasks in the pilot, where I calculate the required number of participants given a certain number of trials. As the DDM is fit to each individual dataset, running a power analysis with several hundreds of iterations per subject/condition would take a substantial amount of time. In order to prevent having to fit the DDM that many times, the power analysis below consists of two steps.

In part I, I calculate the correlation between simulated and recovered DDM parameters for varying numbers of trials and across two common estimation techniques: Maximum Likelihood and Kolmogorov-Smirnoff. As estimated DDM parameters are not perfectly correlated with the true, data-generating parameter values (especially with fewer trials), this correlation gives an estimate of the average "imprecision" of estimated DDM parameters. I do this for the Drift Rate and the Boundary Separation parameters, which are of main interest
to us.

In part II, I use these correlation values to simulate generate two sets of DDM parameters: the "true", data-generating parameter values, and the "recovered" parameter values which correlate to a fixed extend with the "true" parameters, as informed by the first part of the analysis. Thus, this approach allows us to run a power analysis on the DDM parameters without having to fit the DDM tens- to hundreds of thousands of times.

Estimated DDM parameters are not perfectly correlated with the true underlying parameter values, especially with fewer trials. Here, I attempt to get an estimate of the correlation between simulated DDM parameters and recovered parameters with varying number of trials and with  two different estimation techniques: Maximum Likelihood and Kolmogorov-Smirnoff. These correlations can be used in the subsequent power analysis to quickly simulate "empirical" DDM parameters, which will prevent us from having to run thousands of DDM models.

# Part I: Estimation of DDM Precision

We simulate RT data for 500 subjects and with varying numbers of trials per subject: 10, 20, 30, 40, 50 and 60 trials.

```{r}
n_subjects = 500
n_trials = c(10, 20, 30, 40, 50, 60)
```

## Create RT dataset

First, we randomly sample Drift Diffusion parameters for each subject that will be used to generate RTs. Drift rates are sampled from a uniform distribution ranging from 1 to 4.9. Boundary separation is sampled from a uniform distribution ranging from 0.6 to 1.9. Non-decision time is fixed to 0.3 and Starting-point is fixed to 0.5.

```{r}
set.seed(42)

DDM_data <- expand.grid(subject = 1:n_subjects, trials = n_trials) %>%
  mutate(
    drift_rate = runif(n(), min = 1, max = 4.9),
    boundary_sep = runif(n(), 0.6, 1.9),
    tau = 0.3,
    beta = 0.5,
    id = str_c("simulationsubj", subject, "trials", trials, sep = "_")
  )
```

Using the DDM parameters, we next generate the RTs:

```{r}
pwalk(DDM_data[c("trials", "boundary_sep", "tau", "beta", "drift_rate", "id")], generate_RTs)
```

The DDM is fit using the fast-dm software. Fast-dm runs via the command prompt. Follow the following steps to recalculate DDM parameters:

1. Open the command prompt and set the working directory to <path/to/attention_pilot>/data/1_pilot/0_simulation
2. Run the DDM model once for both estimation techniques by typing the following commands one after the other:
fast-dm.exe exp_ks.ctl
fast-dm.exe exp_ml.ctl

# Read recovered DDM parameters

```{r}
DDM_data_recovered <- bind_rows(
  read.table(here('data', "1_pilot", 'simulation', 'ddm_pars_ks.lst'), header = TRUE),
  read.table(here('data', "1_pilot", 'simulation', 'ddm_pars_ml.lst'), header = TRUE)
) %>%
  rename(id = dataset) %>%
  # Join simulated DDM parameters
  left_join(DDM_data %>% select(id, trials, drift_rate, boundary_sep)) %>%
  mutate(
    trials = as.numeric(str_extract_all(id, "[0-9]+$"))
  ) %>%
  group_by(method, trials) %>%
  # Calculate estimate errors - correlations are calculated when plotting
  mutate(
    error_drift = drift_rate - v,
    error_boundary = boundary_sep - a
  ) %>%
  rename(
    `Simulated Drift Rate` = drift_rate,
    `Simulated Boundary Separation` = boundary_sep,
    `Recovered Drift Rate` = v,
    `Recovered Boundary Separation` = a
  )
```

# Plots

## Drift Rate - Correlation

```{r fig.width = 10, fig.height = 6}
DDM_data_recovered %>%
  ggplot(aes(`Simulated Drift Rate`, `Recovered Drift Rate`, color = `Recovered Boundary Separation`)) +
  geom_point() +
  geom_smooth(method="lm") +
  facet_grid(method~trials, scales = "free") +
  theme_classic() +
  stat_cor(method="pearson") +
  labs(
    title = "Correlation Between Simulated and Recovered Drift Rate Under Varying # of Trials",
    color = "Boundary separation"
  )
```

## Boundary separation - Correlation

```{r fig.width = 10, fig.height = 6}
DDM_data_recovered %>%
  ggplot(aes(`Simulated Boundary Separation`, `Recovered Boundary Separation`, color = `Recovered Drift Rate`)) +
  geom_point() +
  geom_smooth(method="lm") +
  facet_grid(method~trials, scales = "free") +
  theme_classic() +
  stat_cor(method="pearson") +
  labs(
    title = "Correlation Between Simulated and Recovered Boundary Separation Under Varying # of Trials",
    color = "Drift Rate"
  )
```

## Drift Rate - Mean error

```{r fig.width = 10, fig.height = 6}
DDM_data_recovered %>%
  ggplot(aes(factor(trials), error_drift, fill = factor(trials))) +
  geom_violin() +
  facet_grid(method~trials, scales = "free") +
  theme_classic() +
  labs(
    title = "Absolute Error in Drift Rate Recovery Under Varying # of Trials",
    x = "Trials",
    y = "Absolute Error in Drift Rate Estimate",
    fill = "Nr. Of Trials"
  )
```

## Boundary Separation - Mean error
```{r fig.width = 10, fig.height = 6}
DDM_data_recovered %>%
  ggplot(aes(factor(trials), error_boundary, fill = factor(trials))) +
  geom_violin() +
  facet_grid(method~trials, scales = "free") +
  theme_classic() +
  labs(
    title = "Absolute Error in Boundary Separation Recovery Under Varying # of Trials",
    x = "Trials",
    y = "Absolute Error in Boundary Separation Estimate",
    fill = "Nr. Of Trials"
  )
```

# part II: Power analysis

The analyses under Part I indicate that the recovered drift rate values correlate with >=.90 with the simulated, "true" values starting at 30 trials.
For the boundary separation, the correlation is ~ .80 starting at 30 trials. Below, we calculate 80% and 90% power an effect size of $\beta$ for a number of scenarios:

1) Linear mixed effects model with main effect of adversity and interaction effect of condition*adversity
2) Correlation of recovered DDM parameters with the "true", data-generating DDM parameters of .60 and .85.
3) Different levels of random noise added to the IV-DV relationship: *SD* of 0.5 and 1.

### Set-up

```{r}
# Simulation parameters
intercept = 0        # Intercept
fixed_effect = c(0.1, 0.15)   # Fixed effect of main effects and interaction
intercept_sd = 1     # Random intercept SD for subjects
```

## Mixed Effects Model

```{r}
# Use multiple cores for simulation
plan(multisession, workers = cores - 4)

mixed_df <- function(n_subjects, DDM_recovery_correlation, sigma_sd, fixed_effect,n_sim) {
  data_mixed <- add_random(subjects = n_subjects) %>%
    add_within("subjects", condition = c("cued", "neutral")) %>%
    add_ranef("subjects", intercept_s = intercept_sd) %>%
    add_ranef(sigma = sigma_sd) %>%
    add_contrast("condition", "sum", colnames = "condition_sum") %>%
    mutate(
      adversity = scale(rnorm(n(), 0, 1)) %>% as.numeric(),
      drift_rate_true = intercept + intercept_s + (fixed_effect * condition_sum) + (fixed_effect * adversity) + (fixed_effect*(condition_sum*adversity)) + sigma
    ) %>%
    group_by(condition_sum) %>%
    mutate(
      drift_rate_recov = rnorm_pre(drift_rate_true, mu = mean(drift_rate_true), sd = sd(drift_rate_true), r = DDM_recovery_correlation, empirical = TRUE),
      n_sim=n_sim
    ) %>%
    ungroup() %>%
    select(subjects, drift_rate_true, drift_rate_recov, condition_sum, adversity)

  return(data_mixed)
}
```

### Simulate data and fit models

Note: The code below takes quite some time to process (~26 minutes on my PC using 4 processing cores).

```{r}
tic()
# Grid containing the simulation parameters to loop over
simulation_results_mixed <- expand_grid(
  n_subjects = c(400, 450, 500, 550, 600, 800, 1000),
  DDM_recovery_correlation = c(.85),
  sigma_sd = c(0.5, 1),
  fixed_effect = fixed_effect,
  n_sim = 1:500
) %>%
  # simulate data
  mutate(mixed_data = future_pmap(., mixed_df, .options = furrr_options(seed = TRUE)),
         ) %>%
  # Fit Mixed model to data
  mutate(mixed_model = future_map(mixed_data, function(x) {

    fit_true <- lmerTest::lmer(data = x, scale(drift_rate_true) ~ condition_sum*scale(adversity) + (1|subjects))
    fit_recov <- lmerTest::lmer(data = x, scale(drift_rate_recov) ~ condition_sum*scale(adversity) + (1|subjects))

      # Extract p-values and convergence
      list(
        p_mixed_main_true         = (fit_true %>% summary %>% coef() %>% as_tibble %>% pull(`Pr(>|t|)`))[3],
        p_mixed_interaction_true  = (fit_true %>% summary %>% coef() %>% as_tibble %>% pull(`Pr(>|t|)`))[4],
        convergence_true          = ifelse(is.null(fit_true@optinfo$conv$lme4$messages), TRUE, FALSE),

        p_mixed_main_recov        = (fit_recov %>% summary %>% coef() %>% as_tibble %>% pull(`Pr(>|t|)`))[3],
        p_mixed_interaction_recov = (fit_recov %>% summary %>% coef() %>% as_tibble %>% pull(`Pr(>|t|)`))[4],
        convergence_recov         = ifelse(is.null(fit_recov@optinfo$conv$lme4$messages), TRUE, FALSE)
      )
  }
  ))

toc()

plan("sequential")
```

### Calculate power

```{r}
power_mixed <- simulation_results_mixed %>%
  unnest_wider(mixed_model) %>%
  filter(DDM_recovery_correlation == 0.85) %>%
  # Only include converged models
  mutate(across(c(p_mixed_main_true, p_mixed_interaction_true), ~ifelse(convergence_true == FALSE, NA, .x))) %>%
  mutate(across(c(p_mixed_main_recov, p_mixed_interaction_recov), ~ifelse(convergence_recov == FALSE, NA, .x))) %>%
  group_by(n_subjects, fixed_effect, sigma_sd) %>%
  # Calculate power
  summarise(
    mixed_true_main_power         = (sum(p_mixed_main_true < .05) / n()) * 100,
    mixed_recov_main_power        = (sum(p_mixed_main_recov < .05) / n()) * 100,
    mixed_true_interaction_power  = (sum(p_mixed_interaction_true < .05) / n()) * 100,
    mixed_recov_interaction_power = (sum(p_mixed_interaction_recov < .05) / n()) * 100
  ) %>%
  ungroup() %>%
  pivot_longer(ends_with("power"), names_to = "effect", values_to = "power")
```

### Plot power curves

```{r, fig.width = 10, fig.height = 6}
power_mixed %>%
  mutate(
    effect = case_when(
      effect == "mixed_true_main_power" ~ "True Main Effect",
      effect == "mixed_recov_main_power" ~ "Recovered Main Effect",
      effect == "mixed_true_interaction_power" ~ "True Interaction",
      effect == "mixed_recov_interaction_power" ~ "Recovered Interaction"
    )
  ) %>%
  ggplot(aes(factor(n_subjects), power, color=factor(fixed_effect), group = factor(fixed_effect))) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = c(80, 90)) +
  #geom_text(aes(label = power)) +
  facet_grid(sigma_sd~effect) +
  theme_classic() +
  labs(
    x = "Sample Size",
    y = "Power",
    color = "DDM Recovery Correlation",
    title = "DDM Power Analysis for Mixed Effects Models",
    subtitle = str_c("Beta = ", fixed_effect)
  )
```

## Linear model

```{r}
# Use multiple cores for simulation
plan(multisession, workers = cores - 4)

linear_df <- function(n_subjects, DDM_recovery_correlation, sigma_sd, fixed_effect, n_sim) {
  faux_options(sep=".")
  data_linear <- sim_design(within = list(vars = c("drift_rate_true", "adversity")),
                            n = n_subjects,
                            mu = list(drift_rate_true = 0, adversity = 0),
                            sd = list(drift_rate_true = 1, adversity = 1),
                            r = fixed_effect, plot = FALSE) %>%
    mutate(drift_rate_recov = rnorm_pre(drift_rate_true, mu = mean(drift_rate_true), sd = sd(drift_rate_true), r = DDM_recovery_correlation, empirical = TRUE))

  return(data_linear)
}
faux_options(sep = ".")
```

### Simulate data and fit models

Note: The code below takes quite some time to process (~3.5 minutes on my PC using 4 processing cores).

```{r}
tic()
# Grid containing the simulation parameters to loop over
simulation_results_linear <- expand_grid(
  n_subjects = c(400, 450, 500, 550, 600, 800, 1000),
  DDM_recovery_correlation = c(.85),
  sigma_sd = c(0.5, 1),
  fixed_effect =fixed_effect,
  n_sim = 1:500
) %>%
  # simulate data
  mutate(linear_data = future_pmap(., linear_df, .options = furrr_options(seed = TRUE)),
  ) %>%
  # Fit Mixed model to data
  mutate(linear_model = future_map(linear_data, function(x) {

    fit_true <- lm(data  = x, scale(drift_rate_true) ~ scale(adversity))
    fit_recov <- lm(data = x, scale(drift_rate_recov) ~ scale(adversity))

    list(
      p_mixed_main_true  = (fit_true %>% summary %>% coef() %>% as_tibble %>% pull(`Pr(>|t|)`))[2],
      p_mixed_main_recov = (fit_recov %>% summary %>% coef() %>% as_tibble %>% pull(`Pr(>|t|)`))[2]
    )
  }
  ))
toc()

plan("sequential")
```
### Calculate power

```{r}
power_linear <- simulation_results_linear %>%
  unnest_wider(linear_model) %>%
  group_by(n_subjects, DDM_recovery_correlation) %>%
  # Calculate power
  summarise(
    mixed_true_main_power         = (sum(p_mixed_main_true < .05) / n()) * 100,
    mixed_recov_main_power        = (sum(p_mixed_main_recov < .05) / n()) * 100,
  ) %>%
  ungroup() %>%
  pivot_longer(ends_with("power"), names_to = "effect", values_to = "power")
```

### Plot power curves

```{r}
power_linear %>%
  mutate(
    effect = case_when(
      effect == "mixed_true_main_power" ~ "True Main Effect",
      effect == "mixed_recov_main_power" ~ "Recovered Main Effect",
    )
  ) %>%
  ggplot(aes(factor(n_subjects), power, color=factor(DDM_recovery_correlation), group = factor(DDM_recovery_correlation))) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = c(80, 90)) +
  #geom_text(aes(label = power)) +
  facet_grid(~effect) +
  theme_classic() +
  labs(
    x = "Sample Size",
    y = "Power",
    color = "DDM Recovery Correlation",
    title = "DDM Power Analysis for Linear Models",
    subtitle = str_c("Beta = ", fixed_effect)
  )
```

```{r}
write_csv(power_linear, here("data", "1_pilot", "simulation", "power_linear_model.csv"))
write_csv(power_mixed, here("data", "1_pilot", "simulation", "power_mixed_model.csv"))
```

### 2021-11-03 preregistrations/1_pilot/scripts/0_power_analysis.R

@@ -1,408 +1,0 @@
-# Author: Stefan Vermeent, Utrecht University
-# E-mail: p.c.s.vermeent@gmail.com
-
-
-# Introduction ------------------------------------------------------------
-
-# This is a power analysis for the cognitive tasks in the pilot, where I calculate the required number of participants given a certain number of trials.
-# As the DDM is fit to each individual dataset, running a power analysis with several hundreds of iterations per subject/condition would take a substantial amount of time.
-# In order to prevent having to fit the DDM that many times, the power analysis below consists of two steps.
-
-# First, I calculate the correlation between simulated and recovered DDM parameters for varying numbers of trials and across two common estimation techniques: Maximum Likelihood and Kolmogorov-Smirnoff.. 
-# As estimated DDM parameters are not perfectly correlated with the true, data-generating parameter values (especially with fewer trials), this correlation gives an
-# estimate of the average "imprecision" of estimated DDM parameters. I do this for the Drift Rate and the Boundary Separation parameters, which are of main interest
-# to us.
-
-# Next, I use these correlation values to simulate generate two sets of DDM parameters: the "true", data-generating parameter values, and the "recovered" parameter values
-# which correlate to a fixed extend with the "true" parameters, as informed by the first part of the analysis. Thus, this approach allows us to run a power analysis
-# on the DDM parameters without having to fit the DDM tens- to hundreds of thousands of times.
-
-
-# Estimated DDM parameters are not perfectly correlated with the true underlying parameter values, especially with fewer trials.
-# Here, I attempt to get an estimate of the correlation between simulated DDM parameters and recovered parameters with varying number of trials and with 
-# two different estimation techniques: Maximum Likelihood and Kolmogorov-Smirnoff.
-# These correlations can be used in the subsequent power analysis to quickly simulate "empirical" DDM parameters, which will prevent us from having to run thousands of
-# DDM models.
-
-
-
-
[…]

### 2021-11-03 preregistrations/1_pilot/scripts/custom_functions/functions_power.R

@@ -1,4 +1,4 @@
-generate_RTs <- function(trials, boundary_sep, tau, beta, drift_rate, id) { # alpha = boundary separation, tau = non-decision time, beta = starting point, delta = drift rate
+generate_RTs <- function(trials, boundary_sep, tau, beta, drift_rate, id, file_path) { # alpha = boundary separation, tau = non-decision time, beta = starting point, delta = drift rate
   
   set.seed(42)
   
@@ -11,7 +11,7 @@ generate_RTs <- function(trials, boundary_sep, tau, beta, drift_rate, id) { # al
       resp = ifelse(resp == "upper", 1, 0))
   
   
-  utils::write.table(RT_data, str_c(here("data", "0_simulation", id), ".dat"), row.names = FALSE, col.names = FALSE, sep = " ")
+  utils::write.table(RT_data, str_c(here("data", "1_pilot", "simulation"), id, ".dat"), row.names = FALSE, col.names = FALSE, sep = " ")
 
 }
 

### 2021-11-08 preregistrations/1_pilot/scripts/0_power_analysis.Rmd
final update to data reading pipeline

@@
 
-linear_df <- function(n_subjects, DDM_recovery_correlation, sigma_sd, fixed_effect, n_sim) {
+linear_df <- function(n_subjects, DDM_recovery_correlation, fixed_effect, n_sim) {
   faux_options(sep=".")
@@
   DDM_recovery_correlation = c(.85),
-  sigma_sd = c(0.5, 1),
   fixed_effect =fixed_effect,
@@
   unnest_wider(linear_model) %>%
-  group_by(n_subjects, DDM_recovery_correlation) %>%
+  group_by(n_subjects, fixed_effect) %>%
   # Calculate power
   summarise(
-    mixed_true_main_power         = (sum(p_mixed_main_true < .05) / n()) * 100,
-    mixed_recov_main_power        = (sum(p_mixed_main_recov < .05) / n()) * 100,
+    linear_true_main_power         = (sum(p_mixed_main_true < .05) / n()) * 100,
+    linear_recov_main_power        = (sum(p_mixed_main_recov < .05) / n()) * 100,
   ) %>%
@@
     effect = case_when(
-      effect == "mixed_true_main_power" ~ "True Main Effect",
-      effect == "mixed_recov_main_power" ~ "Recovered Main Effect",
+      effect == "linear_true_main_power" ~ "True Main Effect",
+      effect == "linear_recov_main_power" ~ "Recovered Main Effect",
     )
   ) %>%
-  ggplot(aes(factor(n_subjects), power, color=factor(DDM_recovery_correlation), group = factor(DDM_recovery_correlation))) +
+  ggplot(aes(factor(n_subjects), power, color=factor(fixed_effect), group = factor(fixed_effect))) +
   geom_point() +
@@
     title = "DDM Power Analysis for Linear Models",
-    subtitle = str_c("Beta = ", fixed_effect)
   )

### 2021-11-08 preregistrations/1_pilot/scripts/1_create-scales.R

@@ -5,7 +5,7 @@ library(jsonlite)
 library(here)
 
 # Functions ---------------------------------------------------------------
-source("scripts/custom_functions/create_codebook.R")
+source(here("preregistrations", "1_pilot", "scripts", "custom_functions", "create_codebook.R"))
 
 # Data --------------------------------------------------------------------
 pilot_data <- 
@@ -62,20 +62,20 @@ vars03_unp <-
     
     quic_par_predict_mean    = across(matches("quic(10|11|12|13|14|15|16|17|18|19|20|21)")) %>% psych::reverse.code(keys = c(1,-1,1,1,-1,1,-1,1,1,1,1,1), items = ., mini = 1, maxi = 5) %>% rowMeans(., na.rm = T) %>% round(1),
     quic_par_predict_missing = across(matches("quic(10|11|12|13|14|15|16|17|18|19|20|21)")) %>% is.na() %>% rowSums(., na.rm = T),
-     
-    quic_par_env_mean        = across(matches("quic(22|23|24|25|26|27|28)")) %>% psych::reverse.code(keys = c(1,1,1,1,-1,1,1), items = ., mini = 1, maxi = 5) %>% rowMeans(., na.rm = T) %>% round(1),
-    quic_par_env_missing     = across(matches("quic(22|23|24|25|26|27|28)")) %>% is.na() %>% rowSums(., na.rm = T),
     
-    quic_phys_env_mean       = across(matches("quic(29|30|31|32|33|34|35)")) %>% psych::reverse.code(keys = c(1,1,1,1-1,1,1), items = ., mini = 1, maxi = 5) %>% rowMeans(., na.rm = T) %>% round(1),
-    quic_phys_env_missing    = across(matches("quic(29|30|31|32|33|34|35)")) %>% is.na() %>% rowSums(., na.rm = T),
+    quic_par_env_mean        = across(matches("quic(22|23|24|25|26|27)")) %>% psych::reverse.code(keys = c(-1,1,1,1,1,1), items = ., mini = 0, maxi = 5) %>% rowMeans(., na.rm = T),
+    quic_par_env_missing     = across(matches("quic(22|23|24|25|26|27)")) %>% is.na() %>% rowSums(., na.rm = T),
     
-    quic_safety_mean         = across(matches("quic(36|37|38)")) %>% rowMeans(., na.rm = T),
[…]

### 2021-11-08 preregistrations/1_pilot/preregistration.Rmd
Preregistration of Pilot Study

@@
   word_document: default
-keep_md: true
 ---
@@
 library(pwr)
-
-## Custom function to restart numbering at the start of each new chapter.
-new_chapter <- function(){
-  if(!exists("chapter_count")) chapter_count <<- 0 
-  chapter_count <<- chapter_count + 1
-  }
 
@@
 The DDM accounts for the full pattern of correct RTs, incorrect RTs, and proportion of errors.
-In doing so, it recovers four parameters that map onto distinct cognitive processes ([@voss_2004]; see Figure 1A).
+In doing so, it recovers four parameters that map onto distinct cognitive processes [@voss_2004].
 
@@
 Recruitment took place through Prolific Academic [www.prolific.co].
+The sample was balanced to include roughly 50% males.
 Participants were eligible for the study if they were from the United States and if they spoke fluent English.
 
-We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the optimal number of participants to include (more information including all simulation code on [Github](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/1_pilot/scripts).
+We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the optimal number of participants to include (more information including all simulation code on [Github](https://github.com/StefanVermeent/attention_project/tree/preregistration1/preregistrations/1_pilot/scripts)).
 We ran simulations for two scenarios: A linear regression model to test the effect of adversity (standardized) on attention performance (standardized) and a mixed regression model to test the adversity (standardized) X task condition (sum-coded) interaction, including a random intercept for subjects.
 We ran simulations for a standardized $\beta$ of 0.10 and 0.15.
+In addition, we simulated the power to detect these effects with imperfectly recovered DDM parameters, assuming a recovery accuracy (i.e., correlation between data-generating parameter value and actually recovered parameter value) of *r* = 0.85 (see the [Github link](https://github.com/StefanVermeent/attention_project/tree/preregistration1/preregistrations/1_pilot/scripts) for more information).
 
-In determining the final sample size, we weighed the simulation results against our uncertainty about certain model parameters (mostly the fixed effects and sigma term for the mixed model) and the fact that this was a first pilot study.
+In determining the final sample size, we weighed the simulation results together our uncertainty about certain model parameters (mostly the fixed effects and sigma term for the mixed model) and the fact that this was a first, mostly exploratory pilot study.
 For the mixed model, we found that power was > .80 for the adversity X task condition interaction with *N* = 450 or more.
-For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`.
-This was significantly higher for $\beta$ = 0.10 (*N* = `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .80, alternative = "two.sided")[['n']] %>% round(0)` when power = `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .80, alternative = "two.sided")[['power']] %>% round(1)` and `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .890, alternative = "two.sided")[['n']] %>% round(0)` when power = `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .90, alternative = "two.sided")[['power']] %>% round(1)`).
-Thus, we decided on sampling 550 participants with an anticipated final sample size of around 500 due to drop-out and data exclusions.
+For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require *N* = `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`.
+When DDM parameter recovery accuracy was *r* = .85, power was `r (power_linear %>% filter(n_subjects == 500, fixed_effect == 0.15, effect == "linear_recov_main_power") %>% pull(power))/100` for *N* = 500 and $\beta$ = 0.15.
+Power was `r (power_linear %>% filter(n_subjects == 500, fixed_effect == 0.1, effect == "linear_recov_main_power") %>% pull(power))/100` under the same scenario when $\beta$ was 0.10.
+Ultimately, we decided on sampling 550 participants with an anticipated final sample size of around 500.
 
@@
 The Cued Attention Task was an adaptation of the Posner task, which measures basic spatial attention speed [@posner_1980].
-On each trial, a left- or right-pointing arrow was presented in one of eight random locations at a distance of 300 pixels from the center of the screen (see Figure 2A).
+On each trial, a left- or right-pointing arrow was presented in one of eight random locations at a distance of 300 pixels from the center of the screen (see Figure \@ref(fig:figure1)a).
 Participants had to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard.
@@
 On each trial of the Flanker task, participants were presented with a set of five arrows pointing either left or right.
-Their job was to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right (see Figure 2B).
+Their job was to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right (see Figure \@ref(fig:figure1)b).
 On 50% of the trials, the flanking arrows pointed in the same direction as the central arrow (i.e., congruent trials), and on the other 50% of the trials they pointed in the opposite direction (i.e., incongruent trials).
@@
 The Change Detection Task measures the ability to detect subtle spatial changes.
-On each trial of the change detection task, participants were presented with five colored circles against a grey background, each with a radius of 15 pixels (see Figure 2C).
+On each trial of the change detection task, participants were presented with five colored circles against a gray background, each with a radius of 15 pixels (see Figure \@ref(fig:figure1)c).
 Each circle was located in a semi-random location around the central fixation cross.
@@
 The main performance measures are RTs and accuracy across all trials.
+
+```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap="Overview of the three cognitive tasks."}
+knitr::include_graphics("figure1.png", error = F)
+```
 
@@
 
-Perceived unpredictability before age 13 was measured using two different scales: A scale of perceived childhood unpredictability used in previous research [@mittal_2015; @young_2018] and an adaptation of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019].
+Perceived unpredictability before age 13 was measured using two different scales: A scale of perceived childhood unpredictability used in previous research [@mittal_2015; @young_2018], an adaptation of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019], and two scales measuring change in the family and social environment.
 The perceived childhood unpredictability scale contained eight items measuring perceived unpredictability before age 13 (e.g, "My family life was generally inconsistent and unpredictable from day-to-day"; See [Table S3](#appendix) for an overview of all items).
@@
 
-The QUIC consists of 38 items across five subscales: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 5) Safety and security (See [Table S4](#appendix) for an overview of all items).
-We made two changes to the original scale as described in @glynn_2019.
-First, while the original QUIC items refer to perceived unpredictability either before age 12 or age 18, we adapted all items to refer to experiences before age 13.
+We included all five scales of the QUIC: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 3) Safety and security (See [Table S4](#appendix) for an overview of all items).
+The items of the Parental environment subscale deviated most from the original.
+
+We made three general changes to the original scale as described in @glynn_2019.
+First, we adapted all items to refer to experiences before age 13.
 This was done to reduce cognitive load from having to go back-and-forth between different time scales.
-Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
-This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
+Second, most items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
+An exception was made for four items of the parental environment scale which asked for more specific experiences (e.g., "I experienced changes in my custody arrangement"; see [Table S4](#appendix)).
+For these items, we adopted a response scale with the options "never", "only once", "a couple times", "several times", "many times".
+Third, quantifiers such as "frequently", "often", and "There was a period of time when [...]" were dropped to better match the response scale.
+We excluded the item "My parents got divorced" because it did not fit the response format and was captured by one of the items of the perceived unpredictability scale.
 
-We computed several unweighted unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overall QUIC variable by averaging all 38 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `).
+We computed several unweighted unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overall QUIC variable by averaging all 37 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `).
 See also [below](#efa) for details on a factor analysis based on the individual items across scales.
+
+One additional scales measured the stability of the family and social environment.
+On a scale of 1 (the same all the time) to 5 (constant and rapid changes), participants indicated how often the following aspects of their family and social environment changed before age 13: 1) economic status, 2) family environment, 3) childhood neighborhood environment, and 4) childhood school environment.
+
+Finally, we included four objective measures of unpredictability before age 13.
+Participants provided answers to the following items in an open response format: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "How many romantic partners did your mother have (not counting your father)?"; 4) "How many romantic partners did your father have (not counting your mother)?".
 
@@
 DDM models were fit separately to the data of each participant. 
-(see also our power simulations on [Github](https://github.com/StefanVermeent/attention_pilot/tree/main/scripts), which indicated that recovered drift rate and boundary separation parameters generally correlated highly (*r* = .80-.95) with the true data-generating parameters even with 30 trials).
+(see also our power simulations on [Github](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/1_pilot/scripts), which indicated that recovered drift rate and boundary separation parameters generally correlated highly (*r* = .80-.95) with the true data-generating parameters even with 30 trials).
 
@@
 The attentional spotlight is assumed to be normally distributed over the arrows, with relatively more attention paid to the arrows at the center and relatively less attention paid to the peripheral arrows.
-Over time, this normal distribution (*SD~a~*) narrows down to the central arrow at the rate specified by *rd*, thereby gradually decreasing the interfering effect of the flanking arrows.
-Note that the SDDM is based on a combined analysis of congruent and incongruent trials.
-See Figure 1B for a visualization of the SDDM.
+Over time, this normal distribution (*SD~a~*) narrows down to the central arrow at the rate specified by *rd*, thereby gradually decreasing the interfering effect of the flankers.
 
@@
 
-The three included unpredictability measures contain items that vary in timescale, ranging from features of the childhood environment that might have been unpredictable on a daily basis (e.g., "things were often chaotic in my house") to sources of unpredictability that typically unfold on a timescale of weeks or months (e.g., "At least one of my parents changed jobs frequently").
+The included unpredictability measures contain items that vary in timescale, ranging from features of the childhood environment that might have been unpredictable on a daily basis (e.g., "things were often chaotic in my house") to sources of unpredictability that typically unfold on a timescale of weeks or months (e.g., "At least one of my parents changed jobs frequently").
 Since attention is involved in information processing on a timescale of seconds to minutes, we expect that attention styles should be more strongly related to sources of unpredictability that unfold on a similar timescale.
@@
 
-EFA was used to find common latent factors underlying the three unpredictability/household chaos measures: perceived unpredictability, QUIC, and CHAOS.
+EFA was used to find common latent factors underlying the unpredictability/household chaos measures: perceived unpredictability, QUIC, and CHAOS, stability of the family and social environment, and the objective measures of unpredictability.
 The number of factors to retain was based on parallel analysis, with the added requirement that each factor was composed of at least five items that had their strongest loading on that particular factor.
@@
   add_row(.after = 23, "Label" = "Parental environment") %>%
-  add_row(.after = 31, "Label" = "Physical environment") %>%
-  add_row(.after = 39, "Label" = "Safety and security") %>%
-  mutate(Label = ifelse(Item %in% c(1,2,3,4,5,6,7,8,9,11,14,16,26,33), str_c(Label, "*"), Label)) %>%
+  add_row(.after = 30, "Label" = "Physical environment") %>%
+  add_row(.after = 38, "Label" = "Safety and security") %>%
+  mutate(Label = ifelse(Item %in% c(1,2,3,4,5,6,7,8,9,11,14,16,22,32), str_c(Label, "*"), Label)) %>%
   flextable(cwidth = c(0.75, .2, 5)) %>%
   set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
-  merge_h_range(i = c(1,11,24,32,40)) %>%
-  bold(i = c(1,11,24,32,40)) %>%
+  merge_h_range(i = c(1,11,24)) %>%
+  bold(i = c(1,11,24, 31, 39)) %>%
   add_footer_row(values = " ", colwidths = 3) %>%

### 2022-01-31 preregistrations/2_study1/preregistration.Rmd
setup of study1 folders

---
title: "preregistration"
author: "Stefan Vermeent"
date: "20-1-2022"
output: html_document
---

[INTRODUCTION]

# Methods

## Participants

## Materials

## Procedure

## Data analysis

There is ample research to suggest that experiencing adversity early in life has a profound effect on the way in which people attend to information. Generally, the patterns point to an attention deficit, such that adversity-exposed people take longer to point their attention towards relevant information and are more susceptible to the influence of distracting or otherwise irrelevant information [@schibli_2017]. Attention-deficit/hyperactivity disorder (ADHD). However, instead of pointing to a general attention deficit, differences in performance on tasks requiring attention control might reflect different attentional strategies that developed to navigate dangerous and unpredictable environments [e.g., increased vigilance; @frankenhuis_2016]. Understanding the attention skills of people from adversity is important because attention control has been identified as one of the key mechanisms underlying performance on higher-level executive processes such as working memory capacity, which is related to a host of real-world academic and social outcomes [@draheim_2021].

Hidden talents research makes the often implicit assumption that enhanced abilities might reflect an enhanced focus on the here-and-now [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013]. For example, @frankenhuis_2016 argued that living in a harsh and unpredictable environment might require a stronger present-orientation (as opposed to being focused on the future) in order to deal with unpredictable threats and benefit from fleeting rewards. Empirical findings seem to point in the same direction. Enhanced performance on attention-shifting [@fields_2021; @mittal_2015] and working memory updating [@nweze_2020; @young_2018] have been explained in terms of an ability to track contextual changes, which is thought to help cope with changing information.

In the current study, we focus on the Flanker Task

One possibility that has yet to be empirically tested is that such effects are driven by a shared present and/or externally oriented attention mechanism. In this pilot study, we leverage the DDM to better understand the processes involved in performance differences, specifically by focusing on basic attention skills.

### 2022-01-31 preregistrations/2_study1/materials/flanker/0_flanker_setup.js

@@ -1,0 +1,126 @@
+//------------------------- Functions
+
+var location_stim = function(up, down){
+  
+  // Present flanker stimuli either at the top or bottom of the screen
+  var html = "<style>" +
+              "divbottom{display:flex; justify-content: center; align-items: flex-end; height:600px}" +
+              "divtop{display:flex; justify-content: center; align-items: flex-start; height:600px}" +
+             ".topflanker{font-size:40px;}" +
+             ".bottomflanker{font-size:40px;}" +
+             "</style>";
+             
+  if(up != null) {
+    html += "<divtop>";
+    html += "<div class = 'topflanker'>";
+    html += up;
+    html += "</div></div>";
+  }
+  
+  if(down != null) {
+    html += "<divbottom>";
+    html += "<div class = 'bottomflanker'>";
+    html += down;
+    html += "</div></div>";
+
+  }
+  
+  return html;
+};
+  
+  
+  
+//------------------------- Stimuli
+  
+  // Flanker stimuli
+  var congruent_left1 = "&nwarr;&nwarr;&nwarr;&swarr;&swarr;";
+  var congruent_left2 = "&swarr;&swarr;&nwarr;&nwarr;&nwarr;";
+  var congruent_left3 = "&nwarr;&nwarr;&swarr;&swarr;&swarr;";
+  var congruent_left4 = "&swarr;&swarr;&swarr;&nwarr;&nwarr;";
+  
+  var congruent_left5 = "&nwarr;&swarr;&nwarr;&nwarr;&swarr;";
+  var congruent_left6 = "&swarr;&nwarr;&nwarr;&swarr;&nwarr;";
+  var congruent_left7 = "&nwarr;&swarr;&swarr;&nwarr;&swarr;";
+  var congruent_left8 = "&swarr;&nwarr;&swarr;&swarr;&nwarr;";
+  
+  
+  var congruent_right1 = "&nearr;&nearr;&nearr;&searr;&searr;";
+  var congruent_right2 = "&searr;&searr;&nearr;&nearr;&nearr;";
+  var congruent_right3 = "&nearr;&nearr;&searr;&searr;&searr;";
+  var congruent_right4 = "&searr;&searr;&searr;&nearr;&nearr;";
+  
+  var congruent_right5 = "&nearr;&searr;&nearr;&nearr;&searr;";
[…]

### 2022-01-31 preregistrations/2_study1/materials/flanker/1_flanker_instructions.js

@@ -1,0 +1,126 @@
+//-------------------- Welcome
+var flanker_welcome = {
+  type: 'instructions',
+  pages: [
+    "Welcome to the <b>Flanker</b> game!"
+  ],
+  show_clickable_nav: true,
+  allow_backward: true,
+  key_forward: -1,
+  key_backward: -1,
+  button_label_next: "continue",
+  data: {variable: 'welcome', task: "flanker_practice"}
+};
+
+//-------------------- Instructions
+var flanker_instructions = {
+  type: 'instructions',
+  pages: [
+    "<p style = 'text-align: center;'>"+ 
+      "In this game, you will see five arrows like the ones below.<br><br><br>" +
+      "<div style = 'font-size: 30px'>&larr;&larr;&larr;&larr;&larr;</div><br><br><br>" +
+      "Your job is to decide which way the <strong>middle arrow</strong> is pointing.<br><br><br>",
+      
+     "<p style = 'text-align: center;'>"+ 
+      "Sometimes, all the arrows point the <strong>same</strong> way.<br><br><br>" +
+      "<div style = 'font-size: 30px'>&larr;&larr;&larr;&larr;&larr;</div><br><br><br>",
+      
+     "<p style = 'text-align: center;'>"+ 
+      "Other times, the arrows point a <strong>different</strong> way.<br><br><br>" +
+      "<div style = 'font-size: 30px'>&larr;&larr;&rarr;&larr;&larr;</div><br><br><br>",  
+      
+      "<p style = 'text-align: center;'>"+ 
+      "You should <i>always</i> look at the <strong>middle arrow</strong> and ignore the others.<br><br>" +
+      
+      "<div style = 'float: left;'>If it points LEFT<br>press the LEFT (&larr;) key.</div>" +
+      "<div style = 'float: right;'>If it points RIGHT<br>press the RIGHT (&rarr;) key.</div><br><br><br><br>" + 
+      
+      "In the example below, the middle arrow points left,<br>" +
+      "so you would press the left key.<br><br>" +
+      "<div style = 'font-size: 30px'>&rarr;&rarr;&larr;&rarr;&rarr;</div></p><br><br><br>",
+      
+     "<p style = 'text-align: center;'>"+ 
+      "Try to respond as fast and as correctly as possible.<br><br>" +
+      "Click 'continue' to practice this game<br><br><br>"        
+  ],
+  show_clickable_nav: true,
+  allow_backward: true,
[…]

### 2022-01-31 preregistrations/2_study1/materials/flanker/2_flanker_procedure.js

@@ -1,0 +1,63 @@
+var flanker_present_arrows = {
+  type: "html-keyboard-response",
+  stimulus: jsPsych.timelineVariable('stim'),
+  choices: ['ArrowLeft', 'ArrowRight'],
+  data: {
+    variable: 'flanker_test',
+    task: 'flanker',
+    location: jsPsych.timelineVariable('location'),
+    stimtype: jsPsych.timelineVariable('stimtype'),
+    correct_response: jsPsych.timelineVariable('correct_response')
+  },
+  on_finish: function(data) { {
+    if(jsPsych.pluginAPI.compareKeys(data.response, jsPsych.timelineVariable('correct_response', true))) {
+      data.correct = true;
+    } else {
+      data.correct = false;
+    }
+  }
+  }
+};
+
+
+var flanker_test_procedure = {
+  timeline: [flanker_fixation, flanker_present_arrows],
+  timeline_variables: [
+    {location: 'top',    correct_response: 'ArrowLeft',  stimtype: 'congruent_left1',    stim: location_stim(up="&nwarr;&nwarr;&nwarr;&swarr;&swarr;", down=null)},
+    {location: 'top',    correct_response: 'ArrowRight', stimtype: 'congruent_left2',    stim: location_stim(up="&swarr;&swarr;&nwarr;&nwarr;&nwarr;", down=null)},
+    {location: 'top',    correct_response: 'ArrowLeft',  stimtype: 'congruent_left3',    stim: location_stim(up="&nwarr;&nwarr;&swarr;&swarr;&swarr;", down=null)},
+    {location: 'top',    correct_response: 'ArrowRight', stimtype: 'congruent_left4',    stim: location_stim(up="&swarr;&swarr;&swarr;&nwarr;&nwarr;", down=null)},
+    {location: 'top',    correct_response: 'ArrowLeft',  stimtype: 'congruent_right1',   stim: location_stim(up="&nwarr;&swarr;&nwarr;&nwarr;&swarr;", down=null)},
+    {location: 'top',    correct_response: 'ArrowRight', stimtype: 'congruent_right2',   stim: location_stim(up="&swarr;&nwarr;&nwarr;&swarr;&nwarr;", down=null)},
+    {location: 'top',    correct_response: 'ArrowLeft',  stimtype: 'congruent_right3',   stim: location_stim(up="&nwarr;&swarr;&swarr;&nwarr;&swarr;", down=null)},
[…]

### 2022-01-31 preregistrations/2_study1/materials/global_variables.js

@@ -1,0 +1,71 @@
+
+// These are variables that are shared across all attention tasks.
+
+
+// At start of experiment: Make sure the size of stimulus presentation is the same for all participants.
+var resize_screen = {
+  type: 'resize',
+  item_width: 3 + 3/8,
+  item_height: 2 + 1/8,
+  prompt: "<p>For this part of the experiment to work correctly, it is important that we know the resolution of your screen.<br><br>" +
+  "Please pick up a creditcard (or another card of similar size) and hold it up to the screen.<br>" +
+  "Then, click and drag the lower right corner of the box until the box is the same size as the credit card when held up to the screen." +
+  "</p>",
+  button_label: ['Continue'],
+  pixels_per_unit: 100,
+  data: {
+    task: 'resize',
+}};
+
+var fullscreenmode = {
+  type: 'fullscreen',
+  fullscreen_mode: true
+};
+
+// Remove cursor during cognitive tasks
+var cursor_off = {
+    type: 'call-function',
+    func: function() {
+        document.body.style.cursor= "none";
+    }
+};
+
+
+// Make cursor visible again in between cognitive tasks or when a button response is required.
+var cursor_on = {
+    type: 'call-function',
+    func: function() {
+        document.body.style.cursor= "auto";
+    }
+};
+
+
+// Task feedback during the practice trials.
+var feedback = {
+  type: 'html-keyboard-response',
+  stimulus: function(){
+    var last_trial_correct = jsPsych.data.get().last(1).values()[0].correct;
+    if(last_trial_correct){
+      return "<p style = 'color:green;font-size:40px'>Correct!</p>"; 
+    } else {
+      return "<p style = 'color:red;font-size:40px'>Incorrect!</p>"; 
+    }
+  },
+  trial_duration: 2000,
+  choices: jsPsych.NO_KEYS,
+  data: {
+    variable: 'feedback'
+  }
+};
+
+
+// End of Cognitive task part of the experiment.
+var cognitive_tasks_end = {
+  type: "html-button-response",
+  stimulus: 
+  "Great job!<br><br>" +
+  "You have finished the first part of the experiment.<br><br>" +
+  "Click the button below to start the second part of the experiment.<br><br>",
+  choices: ['Continue to part 2'],
+  data: {variable: "end", task: "end_global"}
+}

### 2022-02-07 preregistrations/1_pilot/scripts/old/2_exclusions.Rmd
exploratory effects of unpred. on flanker

---
title: "2_exclusions"
author: "Stefan Vermeent"
output: html_document
---

```{r setup, results=F}
library(tidyverse)
library(here)
library(magrittr)

self_report <- read_csv(here("data", "1_pilot", "pilot_self_report.csv"))
change_data <- read_csv(here("data", "1_pilot", "change_data.csv"))
flanker_data <- read_csv(here("data", "1_pilot", "flanker_data.csv"))
cueing_data <- read_csv(here("data", "1_pilot", "cueing_data.csv"))

source(here("preregistrations", "1_pilot", "scripts", "custom_functions", "functions_exclusions.R"))

# Exclusions and data fixes based on subject feedback
misc_exclusions <- readxl::read_xlsx(here("data", "1_pilot", "misc_exclusions.xlsx"))
```

# Planned Exclusions

## Self-report measures

Here, we compute exclusion variables relating to the various attention items.
```{r}
self_report_clean <- self_report %>%
  mutate(
    # Attention checks in the questionnaires - Arbitrary exclusion choices
    ex_narb_attention_checks_pass     = ifelse(attention_check_sum == 2, FALSE, TRUE),
    # Participants with all questionnaires missing - Non-arbitrary exclusion choice
    ex_narb_NA_selfreport_pass  = if_any(ends_with(c("total", "mean")), ~!is.na(.)),
  )
```

Beyond subjects who had missing data on all questionnaires, we investigate missingness patterns for the other subjects.

```{r}
self_report_clean %>%
  filter(ex_narb_NA_selfreport_pass) %>%
  select(id, ends_with("missing")) %>%
  filter(if_any(-id, ~ . > 0)) %>%
  pivot_longer(-id, names_to = "Scale", values_to = "missing") %>%
  ggplot(aes(Scale, missing, color = factor(id), group = factor(id))) +
  geom_point() +
  geom_line() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  scale_y_continuous(breaks=seq(0, 40, 2)) +
  labs(
    y = "# missing items"
  )
```
Subject 369 has missing responses on the majority of items across all questionnaires. Therefore, we exclude this participant from the analyses.

```{r}
self_report_clean %<>%
  mutate(ex_narb_NA_selfreport_pass = ifelse(id == "369", FALSE, ex_narb_NA_selfreport_pass))
```

Finally, we check for suspicious response patterns by looking at standard deviations in non-recoded items. If people consistently select the same response despite the inclusion of recoded items, this might indicate that they did not fill out the questionnaires seriously. We exclude the perceived unpredictability scale and the BIS because they do not contain recoded items, thus making an SD = 0 likely.

```{r}
low_q_SDs <- self_report_clean %>%
  filter(ex_narb_NA_selfreport_pass) %>%
  select(id, starts_with("sd_"), -sd_unp, -sd_impuls) %>%
  filter(if_any(starts_with("sd_"), ~ . == 0)) %>%
  pivot_longer(-id, names_to = "Scale", values_to = "SD") %>%
  group_by(id) %>%
  summarise(n = sum(SD == 0))

low_q_SDs %>% filter(n > 0)
```

A total of `r nrow(low_q_SDs)` subjects had an SD = 0 on at least one questionnaire. Of these, `r nrow(low_q_SDs %>% filter(n>1))` subjects have more than one SD = 0 (min = `r min(low_q_SDs$n)`, max = `r max(low_q_SDs$n)`). We did not preregister a strict cut-off to determine what constitutes a "suspicious response pattern". An SD of 0 on two or more questionnaires is arguably reason for exclusion. However, with only one SD = 0 it becomes more arbitrary, and might depend partly on the specific questionnaire in question (e.g., an SD of 0 on the QUIC with 37 items is more suspicious than an SD of 0 on the perceived SES measure with only one recoded item out of seven). Thus, we create two exclusion variables: An non-arbitrary exclusion variable for more than 2 SDs of 0, and an arbitrary exclusion variable for subjects with 1 SD of 0.

```{r}
self_report_clean %<>%
  left_join(
    low_q_SDs %>%
      mutate(
        ex_narb_suspect_responses_pass = ifelse(n > 1, FALSE, TRUE),
        ex_arb_suspect_responses = TRUE
      ) %>%
      select(-n)
    ) %>%
  # Set exclusion variables for suspect responses to TRUE for all other participants
  mutate(
    ex_narb_suspect_responses_pass = ifelse(is.na(ex_narb_suspect_responses_pass), TRUE, ex_narb_suspect_responses_pass),
    ex_arb_suspect_responses  = ifelse(is.na(ex_arb_suspect_responses), TRUE, ex_arb_suspect_responses),
  )
```

## Reaction Times

### Change Detection Task

```{r}
# Cleaning the RT data by removing extremely short and long RTs, as well as log-transformed outliers
change_data_clean <- 
  change_data %>%
  group_by(id) %>%
  mutate(
    acc_change                        = (sum(correct, na.rm=T)/n())*100,
    ex_narb_change_acc_cutoff         = ifelse(acc_change < gbinom(50, 0.50), FALSE, TRUE),
    ex_narb_change_rowcount           = n(),
    ex_narb_change_NA_trials          = ifelse(n() > 1, sum(is.na(rt)), NA), 
    ex_narb_change_log_outliers       = ifelse(n() > 1, sum(scale(log(rt)) > 3.2), NA),
    ex_narb_change_invalid_trials     = ifelse(n() > 1, sum(rt > 3500 | rt < 250, na.rm = TRUE), NA),
  ) %>%
  ungroup()
```

### Flanker Task

```{r}
# Cleaning the RT data by removing extremely short and long RTs, as well as log-transformed outliers per condition
flanker_data_clean <- 
  flanker_data %>%
  group_by(id, congruency) %>%
  mutate(acc_flanker = (sum(correct, na.rm=T)/n())*100) %>%
  group_by(id) %>%
  mutate(
    ex_narb_flanker_acc_cutoff         = ifelse(acc_flanker < gbinom(32, 0.50), FALSE, TRUE),
    ex_narb_flanker_rowcount           = n(),
    ex_narb_flanker_NA_trials          = ifelse(n() > 1, sum(is.na(rt)), NA), 
    ex_narb_flanker_log_outliers       = ifelse(n() > 1, sum(scale(log(rt)) > 3.2), NA),
    ex_narb_flanker_invalid_trials     = ifelse(n() > 1, sum(rt > 3500 | rt < 250, na.rm = TRUE), NA),
  ) %>% 
  ungroup()
```

### Cueing Task

```{r}
# Cleaning the RT data by removing extremely short and long RTs, as well as log-transformed outliers per condition
cueing_data_clean <- 
  cueing_data %>%
  group_by(id, condition) %>%
  mutate(acc_cueing = (sum(correct, na.rm=T)/n())*100) %>%
  group_by(id) %>%
  mutate(
    ex_narb_cueing_acc_cutoff         = ifelse(acc_cueing < gbinom(32, 0.50), FALSE, TRUE),
    ex_narb_cueing_rowcount           = n(),
    ex_narb_cueing_NA_trials          = ifelse(n() > 1, sum(is.na(rt)), NA), 
    ex_narb_cueing_log_outliers       = ifelse(n() > 1, sum(scale(log(rt)) > 3.2), NA),
    ex_narb_cueing_invalid_trials     = ifelse(n() > 1, sum(rt > 3500 | rt < 250, na.rm = TRUE), NA),
  ) 
```

# Overview of Non-Arbitrary Decisions

```{r}
non_arbitrary_exclusions <- 
  left_join(
    self_report_clean %>%
      select(id, starts_with("ex_narb_")),
    # Join Attention Task exclusions
    reduce(
      ls() %>% str_subset("(cueing|change|flanker)_data_clean$") %>% map(function(x) {
        eval(as.symbol(x)) %>%
          select(id, starts_with("ex_narb_")) %>%
          distinct() 
      }),
      left_join)
  ) %>%
  mutate(
    # Exclusions based on self-reported technical issues
    ex_narb_tasks_technicalissues_pass  = ifelse(id %in% unique(misc_exclusions$id), FALSE, TRUE),

    ex_narb_change_pass                 = ifelse(across(matches("ex_narb_change_(NA_trials|log_outliers|invalid_trials)")) %>% rowSums(., na.rm = TRUE) > 10 | ex_narb_change_rowcount == 1, F, T),
    ex_narb_cueing_pass                 = ifelse(across(matches("ex_narb_cueing_(NA_trials|log_outliers|invalid_trials)")) %>% rowSums(., na.rm = TRUE) > 10 | ex_narb_cueing_rowcount ==2, F, T),
    ex_narb_flanker_pass                = ifelse(across(matches("ex_narb_flanker_(NA_trials|log_outliers|invalid_trials)")) %>% rowSums(., na.rm = TRUE) > 10 | ex_narb_flanker_rowcount == 2, F, T)
  ) %>%
  mutate(
    # Total number of non-arbitrary checks passed
    n_failed = across(  ends_with("_pass")) %>% rowSums(., na.rm = T)
  )
```
```{r}
non_arbitrary_exclusions %>%
  count(n_failed)
```

A total of `r sum(non_arbitrary_exclusions$n_failed < 7)` subjects failed at least one of the non-arbitrary exclusion criteria.

# Apply data exclusions

```{r}
ids_to_retain <- non_arbitrary_exclusions %>% filter(n_failed == max(n_failed)) %>% pull(id)

change_data_clean  %<>% 
  group_by(id) %>% 
  filter(
    id %in% ids_to_retain, 
    rt > 250 & rt < 3500, 
    scale(log(rt)) < 3.2, 
    ex_narb_change_acc_cutoff==TRUE,
  ) %>% 
  ungroup()

cueing_data_clean  %<>% 
  group_by(id) %>% 
  filter(  
    rt > 250 & rt < 3500, 
    scale(log(rt)) < 3.2, 
    ex_narb_cueing_acc_cutoff==TRUE) %>% 
  # Make sure everyone has two conditions left
  filter(length(unique(condition)) == 2) %>%
  ungroup()

flanker_data_clean %<>% 
  group_by(id) %>% 
  filter(
    id %in% ids_to_retain, 
    rt > 250 & rt < 3500, 
    scale(log(rt)) < 3.2, 
    ex_narb_flanker_acc_cutoff==TRUE) %>% 
  # make sure everyone has two conditions left
  filter(length(unique(congruency)) == 2) %>%
  ungroup()

self_report_clean  %<>% group_by(id) %>% filter(id %in% ids_to_retain) %>% ungroup()

# # Sanity checks
# if(length(unique(change_data_clean$id)) != length(unique(flanker_data_clean$id))) warning("The Change data and Flanker data have a different sample size.")
# if(length(unique(change_data_clean$id)) != length(unique(cueing_data_clean$id))) warning("The Change data and Cueing data have a different sample size.")
# if(length(unique(flanker_data_clean$id)) != length(unique(cueing_data_clean$id))) warning("The Flanker data and Cueing data have a different sample size.")
# if(length(unique(change_data_clean$id)) != length(unique(self_report_clean$id))) warning("The Change data and self-report data have a different sample size.")
# if(length(unique(cueing_data_clean$id)) != length(unique(self_report_clean$id))) warning("The Cueing data and self-report data have a different sample size.")
# if(length(unique(flanker_data_clean$id)) != length(unique(self_report_clean$id))) warning("The Flanker data and self-report data have a different sample size.")
```

Sanity check: Did the correct number of trials get removed for each participant?

```{r}
if(nrow(cueing_data_clean %>% group_by(id) %>% mutate(check = ifelse(64 - (ex_narb_cueing_log_outliers + ex_narb_cueing_invalid_trials) == n(), TRUE, FALSE)) %>% filter(isFALSE(check))) > 1) {
   warning("Something went wrong with the removal of trials for the Flanker Task. Either too few or too many trials were removed for some subjects.")
}

if(nrow(change_data_clean %>% group_by(id) %>% mutate(check = ifelse(50 - (ex_narb_change_log_outliers + ex_narb_change_invalid_trials) == n(), TRUE, FALSE)) %>% filter(isFALSE(check))) > 1) {
   warning("Something went wrong with the removal of trials for the Flanker Task. Either too few or too many trials were removed for some subjects.")
}

if(nrow(flanker_data_clean %>% group_by(id) %>% mutate(check = ifelse(64 - (ex_narb_flanker_log_outliers + ex_narb_flanker_invalid_trials) == n(), TRUE, FALSE)) %>% filter(isFALSE(check))) > 1) {
   warning("Something went wrong with the removal of trials for the Flanker Task. Either too few or too many trials were removed for some subjects.")
}
```

```{r}
cueing_data_clean %>%
  group_by(id) %>%
  summarise(n=n()) %>%
  ggplot(aes(n)) +
  geom_histogram() +
  scale_x_continuous(breaks=seq(54, 64, 1)) +
  labs(title="Number of trials after exclusions on the Cueing Task")

flanker_data_clean %>%
  group_by(id) %>%
  summarise(n=n()) %>%
  ggplot(aes(n)) +
  geom_histogram() +
  scale_x_continuous(breaks=seq(54, 64, 1)) +
  labs(title="Number of trials after exclusions on the Flanker Task")

change_data_clean %>%
  group_by(id) %>%
  summarise(n=n()) %>%
  ggplot(aes(n)) +
  geom_histogram() +
  scale_x_continuous(breaks=seq(40,50, 1)) +
  labs(title="Number of trials after exclusions on the Change Task")
```

```{r}
# Create datasets with mean RTs and accuracy 
change_data_clean_mean <- change_data_clean %>%
  group_by(id, correct) %>%
  mutate(rt_change = ifelse(correct, mean(rt, na.rm = T), NA)) %>%
  group_by(id) %>%
  summarise(rt_change = mean(rt_change, na.rm = T), acc_change = (sum(correct) / n()) * 100) %>%
  ungroup() %>%
  left_join(self_report_clean %>% 
              select(id, 
                     starts_with(c("meta", "att")), 
                     matches("(total|composite|mean)$"),
                     scale_factor, fullscreenenter, fullscreenexit, event_during_change, attention_interrupt_sum))

cueing_data_clean_mean <- cueing_data_clean %>%
  group_by(id, condition, correct) %>%
  # RT for correct trials
  mutate(rt_cueing = ifelse(correct, mean(rt, na.rm = T), NA)) %>%
  group_by(id, condition) %>%
  summarise(rt_cueing = mean(rt_cueing, na.rm = T), acc_cueing = (sum(correct) / n()) * 100) %>%
  left_join(self_report_clean %>% 
              select(id, 
                     starts_with(c("meta", "att")), 
                     matches("(total|composite|mean)$"),
                     scale_factor, fullscreenenter, fullscreenexit, event_during_cueing, attention_interrupt_sum))

flanker_data_clean_mean <- flanker_data_clean %>%
 group_by(id, congruency, correct) %>%
  mutate(rt_flanker = ifelse(correct, mean(rt, na.rm = T), NA)) %>%
  group_by(id, congruency) %>%
  summarise(rt_flanker = mean(rt_flanker, na.rm = T), acc_flanker = (sum(correct) / n()) * 100) %>%
  left_join(self_report_clean %>% 
              select(id, 
                     starts_with(c("meta", "att")), 
                     matches("(total|composite|mean)$"),
                     scale_factor, fullscreenenter, fullscreenexit, event_during_flanker, attention_interrupt_sum))
```

```{r}
write_csv(change_data_clean, here("data", "1_pilot", "change_data_clean.csv"))
write_csv(cueing_data_clean, here("data", "1_pilot", "cueing_data_clean.csv"))
write_csv(flanker_data_clean, here("data", "1_pilot", "flanker_data_clean.csv"))

write_csv(cueing_data_clean_mean, here("data", "1_pilot", "cueing_data_clean_mean.csv"))
write_csv(change_data_clean_mean, here("data", "1_pilot", "change_data_clean_mean.csv"))
write_csv(flanker_data_clean_mean, here("data", "1_pilot", "flanker_data_clean_mean.csv"))

write_csv(self_report_clean, here("data", "1_pilot", "self_report_clean.csv"))

save(non_arbitrary_exclusions, file = here("data", "1_pilot", "exclusions_nonarbitrary.RData"))
```

### 2022-02-07 preregistrations/1_pilot/scripts/old/3_DDM_estimation.Rmd
exploratory effects of unpred. on flanker

---
title: "Drift Diffusion Model"
bibliography: ../references.bib
---

```{r, echo=T, results='hide', message=F, warning=F} 
library(tidyverse)
library(here)
library(RWiener)
library(mvtnorm)
library(flankr)

source(here("preregistrations", "1_pilot", "scripts", "custom_functions", "functions_exclusions.R"))

change_data_clean <- read_csv(here("data", "1_pilot", "change_data_clean.csv")) 
cueing_data_clean <- read_csv(here("data", "1_pilot", "cueing_data_clean.csv"))
flanker_data_clean <- read_csv(here("data", "1_pilot", "flanker_data_clean.csv")) 
```

# Change Detection Task

## Data Pre-treatment

First, we check whether there is a significant difference between 'same' and 'different' conditions on the Change Detection Task.

```{r}
change_DDM_setup <- change_data_clean %>%
  select(id, rt, correct, condition) %>%
  mutate(rt = rt / 1000)

change_DDM_setup %>%
  group_by(id, condition) %>%
  summarise(mean_rt = mean(log(rt), na.rm=T)) %>%
  ungroup() %>%
  pivot_wider(names_from = "condition", values_from = "mean_rt") %>%
  do(broom::tidy(t.test(.$same, .$different, data=., paired=T)))
```

```{r}
for (i in unique(change_DDM_setup$id)) {
  # 1. Filter subject i and write individual data files to data folder
  change_DDM_i <- change_DDM_setup %>%
    filter(id == i) %>%
    select(-id, -condition) %>%
    write_delim(file = here("data", "1_pilot", "DDM", str_c("change_DDM_subject", i, ".dat")), col_names = FALSE)
}

# 2. Run DDM model
path_to_files <- paste0("pushd ", here("data", "1_pilot", "DDM")) %>% str_replace_all(., pattern="/", replacement="\\\\")
run_DDM <- " && fast-dm.exe change_ml.ctl"
cmd <- paste0(path_to_files, run_DDM)

shell(cmd)

# 3. Read results
change_DDM_results <- read_delim(here("data", "1_pilot", "DDM", "ddm_results_change.lst"), delim = " ", trim_ws = TRUE) %>%
  mutate(dataset = str_replace_all(dataset, "^change_DDM_subject", "") %>% as.numeric(),
         task = "change") %>%
  rename(id = dataset)

# 4. Remove data files from folder
files_to_remove <- list.files(here("data", "1_pilot", "DDM"), pattern = ".dat$|.lst$", full.names=TRUE)
file.remove(files_to_remove)

change_DDM_results

change_DDM_results %>%
  pivot_longer(c(a,v,t0), names_to = "parameter", values_to = "value") %>%
  ggplot(aes(value)) +
  geom_histogram() +
  theme_classic() +
  facet_wrap(~parameter, scales = "free")
```

## Assessing Model Fit

```{r}
# Means
mu_v     <- mean(change_DDM_results$v, na.rm=T)
mu_a     <- mean(change_DDM_results$a, na.rm=T)
mu_t0    <- mean(change_DDM_results$t0, na.rm=T)

# SDs
sd_v     <- sd(change_DDM_results$v, na.rm=T)
sd_a     <- sd(change_DDM_results$a, na.rm=T)
sd_t0    <- sd(change_DDM_results$t0, na.rm=T)

# Correlations
cor_v_a  <- cor(change_DDM_results$v, change_DDM_results$a, use="complete.obs")
cor_v_t0 <- cor(change_DDM_results$v, change_DDM_results$t0, use="complete.obs")
cor_a_t0 <- cor(change_DDM_results$a, change_DDM_results$t0, use="complete.obs")

# Variance-Covariance Matrix
sigma <- matrix(c(sd_v^2, sd_v*sd_a*cor_v_a, sd_v*sd_t0*cor_v_t0,
                  sd_a*sd_v*cor_v_a, sd_a^2, sd_a*sd_t0*cor_a_t0,
                  sd_t0*sd_v*cor_v_t0, sd_t0*sd_a*cor_a_t0, sd_t0^2),
                ncol=3)

nsim <- 5000

# Simulate DDM parameters based on empirical data
sim_params <- rmvnorm(n=nsim, mean = c(mu_v, mu_a, mu_t0), sigma = sigma) %>%
  as_tibble() %>%
  rename(v=V1, a=V2, t0=V3) %>%
  mutate(n=50, z = 0.5, row = 1:n()) %>%
  select(n, a, t0, z, v, row) %>%
  filter(a > 0 & t0 > 0)

if(nrow(sim_params) < nsim) warning(paste0(nsim - nrow(sim_params < nsim), " simulated driftrates or non-decision times were smaller than 0 and have been dropped!"))
```

```{r echo = FALSE, results = FALSE}
# Simulate and save RTs
pmap(sim_params, function(n,a,t0,z,v, row) {
  rwiener(n,a,t0,z,v) %>%
    as_tibble() %>%
    mutate(resp = ifelse(resp == "upper", 1, 0)) %>%
    write_delim(file = here("data", "1_pilot", "DDM", str_c("par_sim", row, ".dat")), col_names = FALSE)

})
```

```{r}
# Run DDM model on simulated datasets
path_to_files <- paste0("pushd ", here("data", "1_pilot", "DDM")) %>% str_replace_all(., pattern="/", replacement="\\\\")
run_DDM <- " && fast-dm.exe change_ml.ctl"
cmd <- paste0(path_to_files, run_DDM)

shell(cmd)

# Read results
fit_vector <- read_delim(here("data", "1_pilot", "DDM", "ddm_results_change.lst"), delim = " ", trim_ws = TRUE) %>%
  select(fit) %>%
  pull()

# Remove data files from folder
files_to_remove <- list.files(here("data", "1_pilot", "DDM"), pattern = ".dat$|.lst$", full.names=TRUE)
file.remove(files_to_remove)

# Determine the 5% quantile of the distribution of fit indices to use as critical value
fit_critical_value <- quantile(fit_vector, .05)[[1]]
```

```{r}
change_DDM_results %<>%
  mutate(
    fit_critical_value = fit_critical_value,
    ex_change_bad_fit = ifelse(fit < fit_critical_value, TRUE, FALSE))

```

Using `r nsim` simulations, we found that the 5% quantile of the fit distribution corresponded to a critical value of `r round(fit_critical_value,2)`. Applying this critical value to the obtained fit statistics in the data of the Change Detection Task, we found that the data of `r sum(change_DDM_results$ex_change_bad_fit)` subjects fell below this cut-off.

# Attention Cueing Task

For the Attention Cueing Task, we have two conditions: the neutral condition and the cued condition. DDM parameters can be fixed across conditions or set to vary across conditions. It seems plausible that the manipulation across trials has an effect on the non-decision time. For the neutral trial, subjects are only able to make a saccade in the correct direction when the target is presented. Therefore, there is an offset in the time at which information can be accumulated relative the the cued trial. Second, the drift rate might be affected by the manipulation

## Model 1. Fully independent: All parameters vary across conditions

```{r}
cueing_DDM_setup <- cueing_data_clean %>%
  select(id, rt, correct, condition) %>%
  mutate(rt = rt / 1000)

for (i in unique(cueing_DDM_setup$id)) {
  # 1. Filter subject i and write individual data files to data folder
  cueing_DDM_i <- cueing_DDM_setup %>%
    filter(id == i) %>%
    select(-id) %>%
    write_delim(file = here("data", "1_pilot", "DDM", str_c("cueing_DDM_subject", i, ".dat")), col_names = FALSE)
}

# 2. Run DDM model
path_to_files <- paste0("pushd ", here("data", "1_pilot", "DDM")) %>% str_replace_all(., pattern="/", replacement="\\\\")
run_DDM <- " && fast-dm.exe cueing_full_independent_ml.ctl"
cmd <- paste0(path_to_files, run_DDM)

shell(cmd)

# 3. Read results
cueing_DDM_results1 <- read_delim(here("data", "1_pilot", "DDM", "ddm_results_cueing_full_independent.lst"), delim = " ", trim_ws = TRUE) %>%
  mutate(dataset = str_replace_all(dataset, "^cueing_DDM_subject", "") %>% as.numeric(),
         iteration  = "full_independent",
         task = "cueing") %>%
  rename(id = dataset)

# 4. Remove data files from folder
files_to_remove <- list.files(here("data", "1_pilot", "DDM"), pattern = ".dat$|.lst$", full.names=TRUE)
file.remove(files_to_remove)
```

## Model 2. Boundary separation is fixed across conditions

```{r}
for (i in unique(cueing_DDM_setup$id)) {
  # 1. Filter subject i and write individual data files to data folder
  cueing_DDM_i <- cueing_DDM_setup %>%
    filter(id == i) %>%
    select(-id) %>%
    write_delim(file = here("data", "1_pilot", "DDM", str_c("cueing_DDM_subject", i, ".dat")), col_names = FALSE)
}

# 2. Run DDM model
path_to_files <- paste0("pushd ", here("data", "1_pilot", "DDM")) %>% str_replace_all(., pattern="/", replacement="\\\\")
run_DDM <- " && fast-dm.exe cueing_v_t0_independent_ml.ctl"
cmd <- paste0(path_to_files, run_DDM)

shell(cmd)

# 3. Read results
cueing_DDM_results2 <- read_delim(here("data", "1_pilot", "DDM", "ddm_results_cueing_v_t0_independent.lst"), delim = " ", trim_ws = TRUE) %>%
  mutate(dataset = str_replace_all(dataset, "^cueing_DDM_subject", "") %>% as.numeric(),
         iteration = "a_independent",
         task = "cueing",
         a_neutral = a,
         a_cued = a) %>%
  rename(id = dataset) %>%
  select(-a)

# 4. Remove data files from folder
files_to_remove <- list.files(here("data", "1_pilot", "DDM"), pattern = ".dat$|.lst$", full.names=TRUE)
file.remove(files_to_remove)

cueing_DDM_results2

save(change_DDM_results, cueing_DDM_results1, cueing_DDM_results2, file = here("data", "1_pilot", "DDM", "DDM_objects.RData"))
```

# Comparisons between models

```{r}
# T-test on boundary separation
t.test(cueing_DDM_results1$a_cued, cueing_DDM_results1$a_neutral, paired = T)

bind_rows(cueing_DDM_results1, cueing_DDM_results2) %>%
  pivot_longer(ends_with(c("neutral", "cued")), names_to = "parameter", values_to = "value") %>%
  select(id, iteration, parameter, value) %>%
  pivot_wider(names_from = "iteration", values_from = "value") %>%
  ggplot(aes(full_independent, a_independent)) +
  geom_point() +
  facet_wrap(~parameter, scales = "free") +
  labs(
    title = "Parameter comparison across model versions"
  )

bind_rows(cueing_DDM_results1, cueing_DDM_results2) %>%
  select(id, iteration, fit) %>%
  pivot_wider(names_from = "iteration", values_from = "fit") %>%
  ggplot(aes(full_independent, a_independent)) +
  geom_point() +
  labs(
    title = "Model fit comparison across model versions"
  )

cueing_DDM_results1 %>% select(v_cued, t0_cued, a_cued, v_neutral, t0_neutral, a_neutral) %>% cor %>% corrplot(method = "number")
cueing_DDM_results2 %>% select(ends_with(c("cued", "neutral"))) %>% cor %>% corrplot(method = "number")

```

```{r}
cueing_DDM_results1 %>%
  pivot_longer(ends_with(c("neutral", "cued")), names_to = "parameter", values_to = "value") %>%
  separate(parameter, c("parameter", "condition"), sep = "_") %>%
  pivot_wider(names_from = "condition", values_from = "value") %>%
  mutate(
    parameter = case_when(
      parameter == "v" ~ "Drift rate",
      parameter == "t0" ~ "Non-decision time",
      parameter == "a" ~ "Boundary separation"
    )
  ) %>%
  ggplot(aes(neutral, cued)) +
  geom_point() +
  theme_classic() +
  geom_abline(slope = 1, intercept = 0) +
  facet_wrap(~parameter, scales = "free") +
  labs(
    title = "Model 1: Boundary separation varies across conditions"
  )

cueing_DDM_results2 %>%
  pivot_longer(ends_with(c("neutral", "cued")), names_to = "parameter", values_to = "value") %>%
  separate(parameter, c("parameter", "condition"), sep = "_") %>%
  pivot_wider(names_from = "condition", values_from = "value") %>%
  mutate(
    parameter = case_when(
      parameter == "v" ~ "Drift rate",
      parameter == "t0" ~ "Non-decision time",
      parameter == "a" ~ "Boundary separation"
    )
  ) %>%
  ggplot(aes(neutral, cued)) +
  geom_point() +
  theme_classic() +
  geom_abline(slope = 1, intercept = 0) +
  facet_wrap(~parameter, scales = "free") +
  labs(
    title = "Model 2: Boundary separation is fixed across conditions"
  )
```
## Assessing Model Fit

We assess Model fit using Monte Carlo simulations based on the empirical data, as detailed in [@voss_2015].

```{r}
# Means
mu_v_neut     <- mean(cueing_DDM_results2$v_neutral, na.rm=T)
mu_a_neut     <- mean(cueing_DDM_results2$a_neutral, na.rm=T)
mu_t0_neut    <- mean(cueing_DDM_results2$t0_neutral, na.rm=T)

mu_v_cued        <- mean(cueing_DDM_results2$v_cued, na.rm=T)
mu_a_cued        <- mean(cueing_DDM_results2$a_cued, na.rm=T)
mu_t0_cued       <- mean(cueing_DDM_results2$t0_cued, na.rm=T)

# Initiate Variance-Covariance Matrix
sigma <- matrix(nrow = 6, ncol = 6, dimnames=list(c("sd_v_neutral", "sd_a_neutral", "sd_t0_neutral", "sd_v_cued", "sd_a_cued", "sd_t0_cued"),
                                         c("sd_v_neutral", "sd_a_neutral", "sd_t0_neutral", "sd_v_cued", "sd_a_cued", "sd_t0_cued")))

# Fill cells of Var-Covar matrix 
for (col in 1:ncol(sigma)) {
  for (row in 1:nrow(sigma)) {

    col_i = colnames(sigma)[col]
    row_i = rownames(sigma)[row]

    # Variances
    if(col_i == row_i) {
      param <- str_replace(col_i, "^sd_", "")

      sigma[col_i, row_i] <- sd(cueing_DDM_results2[[param]], na.rm = T)^2
    } else {

      # Covariances
      param_col <- str_replace(col_i, "^sd_", "")
      param_row <- str_replace(row_i, "^sd_", "")

      sd_col <- sd(cueing_DDM_results2[[param_col]], na.rm = T)
      sd_row <- sd(cueing_DDM_results2[[param_row]], na.rm = T)
      r      <- cor(cueing_DDM_results2[[param_col]], cueing_DDM_results2[[param_row]])

      sigma[col_i, row_i] <- sd_col * sd_row * r
    }
  }
}

nsim <- 5000

# Simulate DDM parameters based on empirical data
sim_params <- rmvnorm(n=nsim, mean = c(mu_v_neut, mu_a_neut, mu_t0_neut, mu_v_cued, mu_a_cued, mu_t0_cued), sigma = sigma) %>%
  as_tibble() %>%
  rename(v_neut=V1, a_neut=V2, t0_neut=V3, v_cued=V4, a_cued=V5, t0_cued=V6) %>%
  mutate(n=64, z = 0.5, row = 1:n()) %>%
  select(n, a_neut, t0_neut, z, v_neut, a_cued, t0_cued, z, v_cued, row) %>%
  filter(across(starts_with(c("a_", "t0_")), ~ . > 0))

if(nrow(sim_params) < nsim) warning(paste0(nsim - nrow(sim_params < nsim), " simulated driftrates or non-decision times were smaller than 0 and have been dropped!"))
```

```{r echo = FALSE, results = FALSE}
# Simulate and save RTs
pmap(sim_params[c("n", "a_neut", "t0_neut", "z", "v_neut", "row")], function(n,a_neut,t0_neut,z,v_neut, row) {
  rwiener(n,a_neut,t0_neut,z,v_neut) %>%
    as_tibble() %>%
    mutate(resp = ifelse(resp == "upper", 1, 0)) #%>%
    #write_delim(file = here("data", "1_pilot", "DDM", str_c("par_sim", row, ".dat")), col_names = FALSE)
})

```

```{r}
cueing_DDM_results2
change_DDM_results
```

# Flanker Task

```{r}
flanker_DDM_setup <- flanker_data_clean %>%
  select(subject=id, congruency, accuracy=correct, rt) %>%
  mutate(rt = rt / 1000) 
```

```{r}
flanker_fit <- fitSSP(flanker_DDM_setup)
```

```{r}
#write_csv(change_DDM_results, here("data", "1_pilot", "DDM_results_change.csv"))
#write_csv(flanker_DDM_results, here("data", "1_pilot", "DDM_results_flanker.csv"))
#write_csv(cueing_DDM_results, here("data", "1_pilot", "DDM_results_cueing.csv"))
```

### 2022-02-07 preregistrations/1_pilot/scripts/old/3_demographics.Rmd
exploratory effects of unpred. on flanker

---
title: "3_demographics"
author: "Stefan Vermeent"
output:
  word_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(flextable)
library(here)

self_report_clean <- read_csv(here("data", "1_pilot", "self_report_clean.csv"))
```

```{r}
ethnicity <- cleaned_data %>%
  select(id, starts_with("dems")) %>%
  transmute(var = ifelse(dems_ethnicity_mixed == 1, "Mixed", dems_ethnicity)) %>%
  group_by(var) %>%
  summarise(
    percentage = round((n() / nrow(cleaned_data)) * 100, 1),
  ) %>%
  arrange(desc(percentage))

education <- cleaned_data %>%
  select(id, dems_edu) %>%
  transmute(
    var = case_when(
      dems_edu == 1 ~ "Some high school",
      dems_edu == 2 ~ "GED",
      dems_edu == 3 ~ "High school diploma",
      dems_edu == 4 ~ "Some college but no college degree",
      dems_edu == 5 ~ "Associate's degree",
      dems_edu == 6 ~ "Bachelor's or RN degree",
      dems_edu == 7 ~ "Master's degree",
      dems_edu == 8 ~ "Doctoral or law degree"
    )
  ) %>%
  mutate(var = factor(var, levels = c("Some high school", "GED", "High school diploma", "Some college but no college degree", "Associate's degree", "Bachelor's or RN degree", "Master's degree", "Doctoral or law degree"))) %>%
  group_by(var) %>%
  summarise(percentage = round((n() / nrow(cleaned_data)) * 100, 1))

gender <- cleaned_data %>%
  select(id, dems_gender) %>% 
  transmute(
    var = case_when(
      dems_gender == 1 ~ "Man",
      dems_gender == 2 ~ "Woman",
      dems_gender == 3 ~ "Non-binary",
      dems_gender == 4 ~ "Other",
      dems_gender == 5 ~ "Prefer not to say"
    )
  ) %>%
  group_by(var) %>%
  summarise(percentage = round((n() / nrow(cleaned_data)) * 100, 1)) %>%
  arrange(desc(percentage))

sex_at_birth <- cleaned_data %>%
  select(id, dems_sex) %>% 
  transmute(
    var = case_when(
      dems_sex == 0 ~ "Male",
      dems_sex == 1 ~ "Female",
      dems_sex == 2 ~ "Intersex",
      dems_sex == 3 ~ "Prefer not to say"
    )
  ) %>%
  group_by(var) %>%
  summarise(percentage = round((n() / nrow(cleaned_data)) * 100, 1)) %>%
  arrange(desc(percentage))

social_class <- cleaned_data %>%
  select(id, dems_class_current) %>% 
  transmute(
    var = case_when(
      dems_class_current == 1 ~ "Poor",
      dems_class_current == 2 ~ "Working class",
      dems_class_current == 3 ~ "Middle class",
      dems_class_current == 4 ~ "Upper-middle class",
      dems_class_current == 5 ~ "Upper class"
    ),
    var = factor(var, levels = c("Poor", "Working class", "Middle class", "Upper-middle class", "Upper class"))
  ) %>%
  group_by(var) %>%
  summarise(percentage = round((n() / nrow(cleaned_data)) * 100, 1))

```

# Create table

```{r}
table_demographics <- bind_rows(sex_at_birth, gender, ethnicity, education, social_class) %>%
  mutate(percentage = as.character(percentage)) %>%
  add_row(.before = 1, "var" = "Mean age (SD)", percentage = paste0(round(mean(self_report_clean$dems_age, na.rm=T),2), " (", round(sd(self_report_clean$dems_age, na.rm=T),2), ")")) %>%
  add_row(.before = 2, "var" = "Sex at birth (%)") %>%
  add_row(.before = 6, "var" = "Gender (%)") %>%
  add_row(.before = 12, "var" = "Ethnicity (%)") %>%
  add_row(.before = 22, "var" = "Education level (%)") %>%
  add_row(.before = 31, "var" = "Social class (%)") %>%
  rename(`  ` = var, ` ` = percentage) %>%
  flextable(cwidth = c(3, 1)) %>%
  bold(i = c(1,2,6,12,22,31), j = 1) %>%
  padding(i = c(3:5, 7:11, 13:21, 23:30, 32:36), padding.left = 20) %>%
  align(j = 2, align = "left") %>%
  padding(i = 1, j = 2, padding.left = 20)

table_demographics
```

```{r}
save(table_demographics, file = here("preregistrations", "1_pilot", "tables", "table_demographics.RData"))
```

### 2022-02-07 preregistrations/1_pilot/scripts/old/arbitrary_exclusions.Rmd
exploratory effects of unpred. on flanker

---
title: "arbitrary_exclusions"
author: "Stefan Vermeent"
date: "23-11-2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(glue)
library(magrittr)

self_report_clean <- read_csv(here("data", "1_pilot", "self_report_clean.csv"))
change_data_clean_mean <- read_csv(here("data", "1_pilot", "change_data_clean_mean.csv"))
cueing_data_clean_mean <- read_csv(here("data", "1_pilot", "cueing_data_clean_mean.csv"))
flanker_data_clean_mean <- read_csv(here("data", "1_pilot", "flanker_data_clean_mean.csv"))

source(here("preregistrations", "1_pilot", "scripts", "decision_grids_tasks.R"))

suspect_browser_interactions <- self_report_clean %>%
  select(id, blur_event, fullscreenenter, fullscreenexit, focus_event) %>%
  filter(blur_event > 0 | fullscreenexit > 0)

browser_interactions <- read_csv(here("data", "1_pilot", "browser_interactions.csv"))

theme_set(
  theme_light() +
    theme(
    #  text = element_text(family="Lato"),
      panel.grid = element_blank()
    )
)
```

# Overview of arbitrary exclusion criteria for the attention tasks

| Criteria names              | Description                                                                               |
|-------------------------------------------------------------------------------------------------------------------------|
| ex_arb_low_res              | Subjects with small screen resolutions for whom the experiment might have been too large. |
| ex_arb_no_resize            | Subjects who did not go through the resizing procedure.                                   |
| ex_arb_no_fullscreen        | Subjects who did not enter fullscreen mode at the start of the attention tasks.           |
| ex_arb_exit_fullscreen      | Subjects who exited fullscreen mode during the attention tasks.                           |
| ex_arb_event_during_change  | Subjects with blur events during the Change Detection Task.                               |
| ex_arb_event_during_cueing  | Subjects with blur events during the Attention Cueing Task.                               |
| ex_arb_event_during_flanker | SUbjects with blur events during the Flanker Task.                                        |
| ex_arb_captcha              | Subjects who had missing data on  or failed the bot detection                             | 
| ex_arb_interrupt            | Subjects who were interrupted during the experiment.                                      |
| ex_arb_noise                | Subjects who performed the cognitive tasks in a noisy environment.                        |

```{r}
create_multiverse <- function(data, grid, grid_keys) {

  multiverse <- grid %>%
    rownames_to_column("decision") %>%
    split(.$decision) %>%
    map(.f = function(x) {

      # Take all the decisions of current split and turn them into a vector
      decision_x <- x %>% select(-decision) %>% as_vector

       # Filter data based on evaluated exclusions
      final_filter <- data
      walk(decision_x, function(y) {
        final_filter <<- 
          final_filter %>% 
          filter(eval(parse(text = y)))
      })

      # Store the decisions
      decisions <- x %>%
        pivot_longer(starts_with("ex_arb"), names_to = "variable", values_to = "exp") %>%
        left_join(grid_keys, by = c("variable" = "variable", "exp" = "exp"))

      list(
        n         = nrow(final_filter),
        data      = final_filter %>% mutate(decision = x$decision),
        decisions = decisions
      )
    })
}
```

# Sample size per dataset

```{r}
multiverse_samplesize_plots <- function(multiverse_object, group_by = across()) {

  multiverse_sample_size <- 
    map_df(multiverse_object, function(x){
      # Grab the decisions flatten them out
      decisions <- x$decisions %>% 
        pivot_longer(c(exp, variable_group, name), names_to="key", values_to="value") %>%
        unite(grid_vars, variable, key) %>% 
        pivot_wider(names_from = "grid_vars", values_from = "value")
      # Add the decisions to the model table
      bind_cols(n = x$n, decisions)
    })
  # histogram of sample sizes in the multiverse
  multiverse_sample_size %>% 
    ggplot(aes(x = n)) +
    geom_histogram(color = "black", bins = 15) +
    labs(title = "Histogram of Multiverse Sample Sizes", x = "\nSample Size", y = "Number of Datasets\n")

  multiverse_sample_size %>% 
    select(-ends_with("exp")) %>% 
    pivot_longer(starts_with("ex_arb"), names_to = "variable", values_to = "exclusion") %>%
    mutate(variable = str_replace(variable, "_(name)$|_(variable_group)$", ".\\1\\2")) %>% 
    separate(variable, c("var","group"), sep = "\\.") %>% 
    pivot_wider(names_from = "group", values_from = "exclusion") %>%
    arrange(decision, variable_group) %>% 
    ggplot() +
    geom_boxplot(aes(x = name, y = n), notch = T, width = .5)  +
    scale_x_discrete("Exclusion Criteria") +
    scale_y_continuous("Sample Size (max = 495)\n") +
    ggtitle("Sample Sizes in the Multiverse") +
    facet_wrap(~variable_group, scales = "free", ncol = 2)
}
```

```{r, fig.width = 15}
multiverse_descriptives <- function(multiverse_object, vars, condition = "", plot_thinning = 0) {

  evens <- function(x, step_size) {
    if(step_size > 0) {
      subset(x, x %% step_size == 0)
    } else {
      return(x)
    }}

  multiverse_performance <- 
    map(multiverse_object, function(x) {
      data <- x$data %>%
        select(decision, id, matches(vars))

      decisions <- x$decisions %>%
        pivot_longer(c(exp, variable_group, name), names_to = "key", values_to = "value") %>%
        unite(grid_vars, variable, key) %>%
        pivot_wider(names_from = grid_vars, values_from = value)

      data %<>% left_join(decisions, by = "decision")  
    }) %>%
    bind_rows %>%
    pivot_longer(matches(vars), names_to = "key", values_to = "value") %>%
    #group_by(across(c(decision, key, starts_with("ex_arb")))) %>%
    #summarise(
    #  mean = mean(value, na.rm = T),
    #  sd   = sd(value, na.rm = T)
   # ) %>%
    group_by(across(matches("decision", "key", condition))) %>% 
    mutate(
      median = median(value),
      median = ifelse(str_detect(key, "^rt_.*$"), NA, median)) %>%
    group_by(decision) %>%
    fill(median, .direction = "updown") %>%
    group_by(key) %>%
    mutate(multiverse_set = as.numeric(fct_reorder(decision, median))) %>%
    ungroup() %>%
    mutate(value = ifelse(multiverse_set %in% evens(x = unique(.$multiverse_set), step_size = plot_thinning), value, NA))

  multiverse_plot <-   
    ggplot(multiverse_performance, aes(x = as.numeric(multiverse_set), y = value, group = multiverse_set)) +
    geom_boxplot() +
   # geom_point(size = .5) +
    # geom_errorbar(
    #   aes(x = as.numeric(multiverse_set), ymin = mean - sd, ymax = mean + sd),
    #   size = .25,
    #   width = 0,
    #   alpha = .25, 
    #   inherit.aes = F, 
    #   show.legend = T
    # ) +
    theme_classic() +
    facet_wrap(key~., scales = "free") +
    scale_y_continuous("Estimate") +
    scale_color_manual(values = c("gray","#f0506e")) +
    scale_fill_manual(values = c("gray","#f0506e")) +
    theme(
      axis.text.x = element_blank(), 
      axis.title.x = element_blank(),
      axis.ticks.x = element_blank()
    )

  multiverse_specgrid <- 
    multiverse_performance %>%
    select(-matches("exp$"), -c(id, value, median, decision)) %>%
    distinct() %>%
    pivot_longer(matches("name$|group$"), names_to = "variable", values_to = "spec") %>%
    mutate(variable = str_replace(variable, "_(name$)|_(variable_group$)",".\\1\\2")) %>% 
    separate(variable, c("variable","group"), sep = "\\.") %>% 
    pivot_wider(names_from = "group", values_from = "spec") %>%
    ggplot(aes(x = multiverse_set, y = name)) +
    geom_point(size = .75, shape = 124, show.legend = F) +
    scale_y_discrete("Specification\n") +
    scale_x_continuous("\nMultiverse Dataset") +
    scale_color_manual(values = c("gray","#f0506e")) +
    facet_grid(variable_group~key, scales = "free_y") +
    theme(strip.background.x = element_blank(), strip.text.x = element_blank(), strip.placement = "outside")

  cowplot::plot_grid(
    multiverse_plot,
    multiverse_specgrid,
    ncol = 1, 
    align = 'v', 
    axis = "lr",
    rel_heights = c(.30,.70)
  )
}
```

# Multiverse 1: Change Detection Task

```{r, fig.width = 12}
change_multiverse <- create_multiverse(data = change_data_clean_mean, grid = decision_grid_change, grid_keys = decision_grid_change_key)
multiverse_samplesize_plots(change_multiverse)
change_multiverse_plot <- multiverse_descriptives(multiverse_object = change_multiverse, vars = c("^acc_"), plot_thinning = 2)
```

# Multiverse 2: Attention Cueing Task

```{r, fig.width = 12}
cueing_multiverse <- create_multiverse(data = cueing_data_clean_mean, grid = decision_grid_cueing, grid_keys = decision_grid_cueing_key)
multiverse_samplesize_plots(cueing_multiverse)
cueing_multiverse_plot <- multiverse_descriptives(multiverse_object = cueing_multiverse, vars = c("^acc_"), plot_thinning = 2)
```

# Multiverse 3: Flanker Task

```{r, fig.width = 12}
flanker_multiverse <- create_multiverse(data = flanker_data_clean_mean, grid = decision_grid_flanker, grid_keys = decision_grid_flanker_key)
multiverse_samplesize_plots(flanker_multiverse)
flanker_multiverse_plot <- multiverse_descriptives(flanker_multiverse, c("^acc_"), plot_thinning = 2)
```

```{r, fig.width = 15, fig.height = 6}
plot_browser_interactions <- function(data, id) {

  colors = c("blur" = "orange", "focus" = "blue", "fullscreenenter" = "green", "fullscreenexit" = "red")

  for(i in id) {

    (data %>%
       filter(id == i) %>%  
       ggplot(aes(time, color = event, fill = event)) + 
       geom_rect(aes(xmin = min(time_start_change_block1), xmax = min(time_end_change_block1), ymin=0, ymax=1), fill = "lightblue", color = "black") +
       geom_rect(aes(xmin = min(time_start_change_block2), xmax = min(time_end_change_block2), ymin=0, ymax=1), fill = "lightblue", color = "black") +
       geom_rect(aes(xmin = min(time_start_cueing_data), xmax = min(time_end_cueing_data), ymin=0, ymax=1), fill = "lightpink", color = "black") +
       geom_rect(aes(xmin = min(time_start_flanker_data), xmax = min(time_end_flanker_data), ymin=0, ymax=1), fill = "lightgreen", color = "black") +
       geom_text(aes(x = (min(time_start_change_block1)+min(time_end_change_block2))/2, y = 1.05, label = "Change"), color = "black") +
       geom_text(aes(x = (min(time_start_cueing_data)+min(time_end_cueing_data))/2, y = 1.05, label = "Cueing"), color = "black") +
       geom_text(aes(x = (min(time_start_flanker_data)+min(time_end_flanker_data))/2, y = 1.05, label = "Flanker"), color = "black") +
       scale_fill_manual(values=colors) +
       scale_color_manual(values=colors) +
       geom_bar(width = 2, alpha=0.5, position="dodge") +
       theme_classic() +
       theme(
         axis.ticks.y = element_blank(),
         axis.text.y = element_blank()
       ) +
       labs(
         x = "Time",
         y = "",
         title = "Browser Interaction Events During the Cognitive Tasks",
         subtitle = "Blur = interacting with other webpages; Focus = Refocusing on the task browser."
       ) +
       guides(color="none")) %>% print
  }
}

plot_browser_interactions(data= browser_interactions, id = c(515, 494, 158, 280, 6, 189, 528))
```

## Change Detection Task

```{r}

decision_grid_change <- expand_grid(
  ex_arb_low_res_pass              = c(TRUE, FALSE),         
  ex_arb_no_resize_pass            = c(TRUE, FALSE),
  ex_arb_no_fullscreen_pass        = c(TRUE, FALSE),
  ex_arb_exit_fullscreen_pass      = c(TRUE, FALSE),
  ex_arb_event_during_change_pass  = c(TRUE, FALSE)
)

exclusion_fun <- function(ex_arb_low_res_pass, ex_arb_no_resize_pass, ex_arb_no_fullscreen_pass, ex_arb_exit_fullscreen_pass, ex_arb_event_during_change_pass) {
  data <- change_data_clean_mean %>%
      filter(
        isTRUE(ex_arb_low_res) | (isTRUE(ex_arb_low_res) & isFALSE(ex_arb_low_res_pass)) | (isFALSE(ex_arb_low_res) & isTRUE(ex_arb_low_res_pass)),
        isTRUE(ex_arb_no_resize) | (isTRUE(ex_arb_no_resize) & isFALSE(ex_arb_no_resize_pass)) | (isFALSE(ex_arb_no_resize) & isTRUE(ex_arb_no_resize_pass)),
        isTRUE(ex_arb_no_fullscreen) | (isTRUE(ex_arb_no_fullscreen) & isFALSE(ex_arb_no_fullscreen_pass)) | (isFALSE(ex_arb_no_fullscreen) & isTRUE(ex_arb_no_fullscreen_pass)),
        isTRUE(ex_arb_exit_fullscreen) | (isTRUE(ex_arb_exit_fullscreen) & isFALSE(ex_arb_exit_fullscreen_pass)) | (isFALSE(ex_arb_exit_fullscreen) & isTRUE(ex_arb_exit_fullscreen_pass)),
        isTRUE(ex_arb_event_during_change) | (isTRUE(ex_arb_event_during_change) & isFALSE(ex_arb_event_during_change_pass)) | (isFALSE(ex_arb_event_during_change) & isTRUE(ex_arb_event_during_change_pass)),
      )
}

pmap(decision_grid_change, exclusion_fun)

multiverse_change <- decision_grid_change %>%
  #rownames_to_column("decision") %>%
 # split(.$decision) %>%
  pmap(.f = function(x) {
    data <- change_data_clean_mean %>%
      filter(
        ex_arb_low_res              == x$ex_arb_low_res &
        ex_arb_no_resize            == x$ex_arb_no_resize &
        ex_arb_no_fullscreen        == x$ex_arb_no_fullscreen &
        ex_arb_exit_fullscreen      == x$ex_arb_exit_fullscreen &
        ex_arb_event_during_change  == x$ex_arb_event_during_change
      )
  })

```

### 2022-02-07 preregistrations/1_pilot/scripts/old/descriptives.Rmd
exploratory effects of unpred. on flanker

---
title: "4_descriptives"
author: "Stefan Vermeent"
output:
  html_document: default
  word_document: default
---

```{r}
library(tidyverse)
library(psych)
library(here)
library(flextable)
library(gt)
require(esyr)

source(here("preregistrations", "1_pilot", "scripts", "custom_functions", "functions_exclusions.R"))

change_data_clean_mean <- read_csv(here("data", "1_pilot", "change_data_clean_mean.csv")) 
cueing_data_clean_mean <- read_csv(here("data", "1_pilot", "cueing_data_clean_mean.csv")) 
flanker_data_clean_mean <- read_csv(here("data", "1_pilot", "flanker_data_clean_mean.csv"))

self_report_clean <- read_csv(here("data", "1_pilot", "self_report_clean.csv"))
codebook <- read_csv(here("data", "1_pilot", "pilot_self_report_codebook.csv"))
```

# Self-report

## Distributions

```{r}
create_plot <- function(data, variables, label) {

  data %>%
    pivot_longer(all_of(variables), names_to = "Scale", values_to = "value") %>%
    ggplot() +
    geom_histogram(aes(value)) +
    facet_wrap(~Scale, scales = "free") +
    theme_classic() +
    labs(
      x = "Mean score",
      y = "Frequency",
      title = label
    )

}

create_plot(data = self_report_clean, variables = c("chaos_mean", "quic_monitoring_mean", "quic_par_predict_mean", "quic_par_env_mean", "quic_phys_env_mean", "quic_safety_mean", "quic_total_mean", "unp_mean", "unp_moving", "unp_partners_mother", "unp_partners_father", "unp_household_size"), label = "Unpredictability")

create_plot(data = self_report_clean, variables = c("ses_subj_mean", "edu_parents_recoded", "income_past_recoded", "class_past_recoded", "poverty_composite"), label = "Poverty")
```

## Reliabilities

```{r}
alphas <- tibble(
  stai_s_mean           = alpha(self_report_clean %>% select(matches("stai_s\\d\\d")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  quic_total_mean       = alpha(self_report_clean %>% select(matches("quic\\d\\d")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  quic_monitoring_mean  = alpha(self_report_clean %>% select(matches("quic(01|02|03|04|05|06|07|08|09)")), check.keys = TRUE)$total$raw_alpha %>% round(2),  
  quic_par_predict_mean = alpha(self_report_clean %>% select(matches("quic(10|11|12|13|14|15|16|17|18|19|20|21)")), check.keys = TRUE)$total$raw_alpha %>% round(2),   
  quic_par_env_mean     = alpha(self_report_clean %>% select(matches("quic(22|23|24|25|26|27)")), check.keys = TRUE)$total$raw_alpha %>% round(2),    
  quic_phys_env_mean    = alpha(self_report_clean %>% select(matches("quic(28|29|30|31|32|33|34)")), check.keys = TRUE)$total$raw_alpha %>% round(2),   
  quic_safety_mean      = alpha(self_report_clean %>% select(matches("quic(35|36|37)")), check.keys = TRUE)$total$raw_alpha %>% round(2),   
  unp_mean              = alpha(self_report_clean %>% select(matches("unp\\d\\d")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  chaos_mean            = alpha(self_report_clean %>% select(matches("chaos\\d\\d")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  ses_subj_mean         = alpha(self_report_clean %>% select(matches("ses\\d\\d")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  violence_mean         = alpha(self_report_clean %>% select(matches("violence\\d\\d")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  impuls_mean           = alpha(self_report_clean %>% select(matches("impuls\\d\\d")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  fos_fo_mean           = alpha(self_report_clean %>% select(matches("fos\\d\\d")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  fos_pa_mean           = alpha(self_report_clean %>% select(matches("fos(01|06|07|12|13)")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  fos_tp_mean           = alpha(self_report_clean %>% select(matches("fos(02|05|08|11|14)")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  fos_fc_mean           = alpha(self_report_clean %>% select(matches("fos(03|04|09|10|15)")), check.keys = TRUE)$total$raw_alpha %>% round(2),
  depression_mean       = alpha(self_report_clean %>% select(matches("depression\\d\\d")), check.keys = TRUE)$total$raw_alpha %>% round(2),
) %>%
  pivot_longer(everything(), names_to = "Scale", values_to = "Reliability") %>%
  flextable(cwidth = c(3, 1)) %>%
  bold(i = c(1,2,8,9,10,11,12,13,17), j = 1) %>%
  padding(i = c(3:7, 14:16), padding.left = 20)

alphas
```

## Correlations

```{r}
correlations <- self_report_clean %>%
  select(id, ends_with(c("mean", "total", "composite", "_recoded")), sleep, hungry, rested, att_noise,
         unp_moving, unp_household_size, unp_partners_father, unp_partners_mother) %>%
  left_join(
    cueing_data_clean_mean %>% select(-acc_cueing) %>%  pivot_wider(names_from = "condition", values_from = "rt_cueing") %>% select(id, rt_cued = cued, rt_neutral = neutral)
    ) %>%
  left_join(
    flanker_data_clean_mean %>% select(-acc_flanker) %>%  pivot_wider(names_from = "congruency", values_from = "rt_flanker") %>% select(id, rt_congruent = congruent, rt_incongruent = incongruent)
  ) %>%
  left_join(change_data_clean_mean %>% select(id, rt_change)) %>%
  left_join(change_DDM_results %>% filter(!ex_change_bad_fit) %>% select(id, v, a, t0)) %>%
  left_join(cueing_DDM_results2 %>% select(id, v_neutral, a_neutral, t0_neutral, v_cued, a_cued, t0_cued))

table_cor_adversity <- correlations %>%
  select(unp_mean, quic_total_mean, chaos_mean, change_env_mean, 
         unp_moving, unp_household_size, unp_partners_father, unp_partners_mother,
         violence_mean, fighting_mean, violence_composite,
         ses_subj_mean_recoded, ses_obj_mean, poverty_composite,
         stai_s_mean, depression_mean,
         ) %>%
  corr_table(
    c.names = c("Perceived", "QUIC", "CHAOS", "Env. change", "Residential changes", "Household size", "Partners mother", "Partners father", "Neighborhood", "Fighting", "Composite", "Perceived", "Objective", "Composite", "Anxiety", "Depression"),
    numbered = T,
    flagged = T,
    stats = ""
  ) %>%
  gt(groupname_col = "stat_group") %>%
  cols_label(Variable = " ") %>% 
  tab_spanner(c("Unpredictability"), columns = 2:9) %>% 
  tab_spanner(c("Violence"), columns = 10:12) %>% 
  tab_spanner(c("Poverty"), columns = 13:15) %>%
  tab_style(
    style = cell_borders("all", color = "white"),
    locations = cells_body(columns = 1:17, rows = 2:16)
  ) %>%
  tab_options(
    table.font.size = "10px",
  )

table_cor_unpredictability <- correlations %>%
  select(unp_mean, starts_with("quic"), chaos_mean, change_env_mean,
         unp_moving, unp_household_size, unp_partners_father, unp_partners_mother,
         stai_s_mean, depression_mean) %>%
  mutate(
    unp_moving = case_when(
      unp_moving == 0 ~ 0,
      unp_moving %in% c(1,2) ~ 1,
      unp_moving %in% c(3,4) ~ 2,
      unp_moving %in% c(5,6) ~ 3,
      unp_moving %in% c(7,8) ~ 4,
      unp_moving %in% c(9,10) ~ 5,
      unp_moving > 10 ~ 6,
    ),
    unp_partners_mother = case_when(
      unp_partners_mother == 0 ~ 0,
      unp_partners_mother == 1 ~ 1,
      unp_partners_mother == 2 ~ 2,
      unp_partners_mother == 3 ~ 3,
      unp_partners_mother == 4 ~ 4,
      unp_partners_mother == 5 ~ 5,
      unp_partners_mother >= 6 ~ 6,
    ),
    unp_partners_father = case_when(
      unp_partners_father == 0 ~ 0,
      unp_partners_father == 1 ~ 1,
      unp_partners_father == 2 ~ 2,
      unp_partners_father == 3 ~ 3,
      unp_partners_father == 4 ~ 4,
      unp_partners_father == 5 ~ 5,
      unp_partners_father >= 6 ~ 6,
    )
  ) %>%
  corr_table(
    c.names = c("Perceived", "Monitoring", "Par. predictability", "Par. env.", "Phys. env.", "Safety", "Total", "CHAOS", "Env. change", 
                "Residential changes", "Household size", "Partners mother", "Partners father", "Anxiety", "Depression"),
    numbered = T,
    flagged = T,
    stats = ""
  ) %>%
  gt(groupname_col = "stat_group") %>%
  cols_label(Variable = " ") %>% 
  tab_spanner(c("QUIC"), columns = 3:8) %>% 
  tab_spanner(c("CHAOS"), columns = 9) %>% 
  tab_spanner(c("Objective"), columns = 11:14) %>% 
  tab_style(
    style = cell_borders("all", color = "white"),
    locations = cells_body(columns = 1:16, rows = 2:16)
  ) %>%
  tab_options(
    table.font.size = "10px",
  )

table_cor_all <- correlations %>%
  select(unp_mean, quic_total_mean, chaos_mean, change_env_mean, 
         violence_composite, poverty_composite, impuls_mean, 
         fos_fo_mean, fos_pa_mean, fos_tp_mean, fos_fc_mean,
         stai_s_mean, depression_mean,
         rt_change, rt_neutral, rt_cued, rt_congruent, rt_incongruent, 
         v, a, t0,
         v_neutral, a_neutral, t0_neutral, v_cued, a_cued, t0_cued) %>%
  mutate(unpredictability = across(c(unp_mean, quic_total_mean, chaos_mean, change_env_mean)) %>% rowMeans(., na.rm = T)) %>%
  mutate(across(starts_with("rt_"), ~log(.))) %>%
  select(unpredictability, everything(), -c(unp_mean, quic_total_mean, chaos_mean, change_env_mean)) %>%
  corr_table(
    c.names = c("Unpredictability", "Violence", "Poverty", "Impulsivity", "FOS - Composite", "FOS - planning", "FOS - time persp.", "FOS - Fut. conseq.", "Anxiety", "Depression",
                "Change", "Cueing - neut.", "Cueing - cued", "Flanker - congr.", "Flanker - incongr.",
                "Change - v", "Change - "),
    numbered = T,
    flagged = T,
    stats = c("")
  ) %>%
  gt() %>%
  tab_style(
    style = cell_borders("all", color = "white"),
    locations = cells_body(columns = 1:16, rows = 2:17)
  ) %>%
  tab_options(
    table.font.size = "10px",
  )

table_cor_all <- correlations %>%
  select(unp_mean, quic_total_mean, chaos_mean, change_env_mean, 
         violence_composite, poverty_composite, 
         rt_change, rt_neutral, rt_cued, rt_congruent, rt_incongruent, 
         v, a, t0,
         ) %>%
  mutate(unpredictability = across(c(unp_mean, quic_total_mean, chaos_mean, change_env_mean)) %>% rowMeans(., na.rm = T)) %>%
  mutate(across(starts_with("rt_"), ~log(.))) %>%
  select(unpredictability, everything(), -c(unp_mean, quic_total_mean, chaos_mean, change_env_mean)) %>%
  corr_table(
    c.names = c("Unpredictability", "Violence", "Poverty", 
                "Change", "Cueing - neut.", "Cueing - cued", "Flanker - congr.", "Flanker - incongr.",
                "Change - v", "Change - a", "Change - t0"),
    numbered = T,
    flagged = T,
    stats = c("")
  ) %>%
  gt() %>%
  tab_style(
    style = cell_borders("all", color = "white"),
    locations = cells_body(columns = 1:12, rows = 2:11)
  ) %>%
  tab_options(
    table.font.size = "10px",
  )
```

```{r}
table_cor_adversity
```

```{r}
table_cor_unpredictability
```

```{r}
table_cor_all
1```

### 2022-02-07 preregistrations/1_pilot/scripts/old/primary_analyses.Rmd
exploratory effects of unpred. on flanker

---
title: "primary_hypotheses"
author: "Stefan Vermeent"
date: "24-11-2021"
output:
  word_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(here)
library(broom)
library(performance)
library(lme4)
library(lmerTest)
library(GPArotation)
library(psych)
library(nFactors)
library(flextable)
library(magrittr)
library(ggeffects)

change_data_clean <- read_csv(here("data", "1_pilot", "change_data_clean.csv"))
cueing_data_clean <- read_csv(here("data", "1_pilot", "cueing_data_clean.csv"))
flanker_data_clean <- read_csv(here("data", "1_pilot", "flanker_data_clean.csv"))
self_report_clean <- read_csv(here("data", "1_pilot", "self_report_clean.csv"))

codebook <- read_csv(here("data", "1_pilot", "pilot_self_report_codebook.csv"))

# Create datasets with mean RTs and accuracy 
change_data_clean_mean <- change_data_clean %>%
  group_by(id) %>%
  summarise(rt_change = mean(rt, na.rm = T), acc_change = (sum(correct) / n()) * 100) %>%
  ungroup() %>%
  left_join(self_report_clean %>% select(id, matches("(total|composite|mean)$")))

cueing_data_clean_mean <- cueing_data_clean %>%
  group_by(id, condition) %>%
  summarise(rt_cueing = mean(rt, na.rm = T), acc_cueing = (sum(correct) / n()) * 100) %>%
  ungroup() %>%
  mutate(
    condition = ifelse(condition == "neutral", -1, 1),
    rt_cueing = scale(rt_cueing)
  ) %>%
  left_join(self_report_clean %>% select(id, matches("(total|composite|mean)$")))

flanker_data_clean_mean <- flanker_data_clean %>%
  group_by(id, congruency) %>%
  summarise(rt_flanker = mean(rt, na.rm = T), acc_flanker = (sum(correct) / n()) * 100) %>%
  ungroup() %>%
  mutate(
    congruency = ifelse(congruency == "congruent", -1, 1),
    rt_flanker = scale(rt_flanker)
  ) %>%
  left_join(self_report_clean %>% select(id, matches("(total|composite|mean)$")))
```

# 1. Primary hypotheses - Effect of violence exposure on task performance

## Reaction Times

### Change Detection Task

The mean accuracy across participants on the Change Detection Task was *M* = `r round(mean(change_data_clean_mean$acc_change),2)` (*SD* = `r round(sd(change_data_clean_mean$acc_change),2)`). Therefore, we also conducted an analysis on the mean accuracy.

```{r fig.height = 10, fig.width = 12}
model_change_rt_vio <- lm(data = change_data_clean_mean, log(rt_change) ~ violence_composite) 
summary(model_change_rt_vio)

check_model(model_change_rt_vio)
```

```{r fig.height = 10, fig.width = 12}
model_change_acc_vio <- lm(data = change_data_clean_mean, log(acc_change) ~ violence_composite) 
summary(model_change_acc_vio)

check_model(model_change_acc_vio)
```

### Attention Cueing Task

```{r fig.height = 10, fig.width = 12}
cueing_data_clean_mean %<>%
  filter(!id %in% c("269", "32", "37"))

model_cueing_rt_vio <- lmer(data = cueing_data_clean_mean, rt_cueing ~ violence_composite*condition + (1|id)) 
summary(model_cueing_rt_vio)

check_model(model_cueing_rt_vio)
```

### Flanker Task

```{r fig.height = 10, fig.width = 12}
model_flanker_rt_vio <- lmer(data = flanker_data_clean_mean, rt_flanker ~ violence_composite*congruency + (1|id)) 
summary(model_flanker_rt_vio)

ggpredict(model_flanker_rt_vio, terms = c("composite_composite [-1,1]", "congruency [-1,1]"))

check_model(model_flanker_rt_vio)
```

# 2. Primary hypotheses - Factor structure of unpredictability measures

We conducted an EFA including all items measuring unpredictability: 1) The QUIC items, 2) the perceived unpredictability items, 3) the CHAOS items, 4) the items measuring environmental change, 5) number of partners of the father and mother, 6) Number of residential changes, 7) household size.

The measures of residential changes and number of different partners of both parents were heavily positively skewed.

```{r}
self_report_clean %>%
  select(id, unp_partners_father, unp_partners_mother, unp_household_size, unp_moving) %>%
  pivot_longer(starts_with("unp_"), names_to = "var", values_to = "value") %>%
  ggplot() +
  geom_histogram(aes(value)) +
  facet_wrap(~var, scales = "free")
```

Two participants indicated 50 different partners for either their mother or father. This number corresponded with other items focusing on the family situation, such as on the QUIC ("At least one of my parents had many romantic partners") and changes in the family environment. Therefore, we saw no reason to exclude these responses. We binned the responses for these three variables to get rid of the skew. For number of residential changes, responses were recoded into 7 bins: 0 (0 times), 1 (1-2 times), 2 (3-4 times), 3 (5-6 times), 4 (7-8 times), 5 (9-10 times), and 6 (10 or more times). For the number of partners of both parents, responses were recoded into .. bins: 0 (0 partners), 1 (1 partner), 2 (2 partners), 3 (3 partners), 4 (4 partners), 5 (5 partners), and 6 (6 or more partners).

```{r}
self_report_clean %<>%
  mutate(
    unp_moving_binned = case_when(
      unp_moving == 0 ~ 0,
      unp_moving %in% c(1,2) ~ 1,
      unp_moving %in% c(3,4) ~ 2,
      unp_moving %in% c(5,6) ~ 3,
      unp_moving %in% c(7,8) ~ 4,
      unp_moving %in% c(9,10) ~ 5,
      unp_moving > 10 ~ 6,
    ),
    unp_partners_mother_binned = case_when(
      unp_partners_mother == 0 ~ 0,
      unp_partners_mother == 1 ~ 1,
      unp_partners_mother == 2 ~ 2,
      unp_partners_mother == 3 ~ 3,
      unp_partners_mother == 4 ~ 4,
      unp_partners_mother == 5 ~ 5,
      unp_partners_mother >= 6 ~ 6,
    ),
    unp_partners_father_binned = case_when(
      unp_partners_father == 0 ~ 0,
      unp_partners_father == 1 ~ 1,
      unp_partners_father == 2 ~ 2,
      unp_partners_father == 3 ~ 3,
      unp_partners_father == 4 ~ 4,
      unp_partners_father == 5 ~ 5,
      unp_partners_father >= 6 ~ 6,
    )
  )
```

```{r}
self_report_clean %>%
  select(id, unp_partners_father_binned, unp_partners_mother_binned, unp_household_size, unp_moving_binned) %>%
  pivot_longer(starts_with("unp_"), names_to = "var", values_to = "value") %>%
  ggplot() +
  geom_histogram(aes(value)) +
  facet_wrap(~var, scales = "free")
```

```{r}
efa_data <- self_report_clean %>%
  select(matches("(quic\\d\\d)|(unp\\d\\d)|(chaos\\d\\d)|(change_env\\d\\d)"), 
         unp_partners_father_binned, unp_partners_mother_binned, unp_household_size, unp_moving_binned) %>%
  drop_na() %>%
  mutate(across(matches("quic(01|02|03|04|05|06|07|08|09|11|14|16|22|32)"), ~ 6 - .)) %>%
  mutate(across(matches("chaos(01|02|04|07|12|14|15)"), ~ 6 - .))
```

First, we determine the number of factors through parallel analysis, with the added constraint that each factor should have at least 5 items that have their highest loading on that factor. Parallel analysis suggests extracting 5 factors.

```{r}
ev <- eigen(cor(efa_data)) # get eigenvalues
ap <- parallel(subject=nrow(efa_data),var=ncol(efa_data),
  rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```
```{r}
efa_model <- factanal(efa_data, factors = 5, rotation = "oblimin")

efa_model

tidy(efa_model) %>% 
  mutate(across(starts_with("fl"), ~ifelse(. < .32, NA, .))) %>% 
  left_join(codebook %>% rename(variable = Variable)) %>% 
  arrange(fl1, fl2, fl3, fl4, fl5) %>% 
  mutate(
    Label = case_when(
      variable == "unp_moving_binned" ~ "Residential changes", 
      variable == "unp_partners_father_binned" ~ "Romantic partners - father", 
      variable == "unp_partners_mother_binned" ~ "Romantic partners - mother", 
      variable == "unp_household_size" ~ "Household size",
      variable == "unp03" ~ "My parents had a difficult divorce or separation during this time.",
      TRUE ~ Label
  ),
    variable = case_when(
      str_detect(variable, "quic") ~ "QUIC - ",
      str_detect(variable, "unp\\d\\d") ~ "Perceived - ",
      str_detect(variable, "chaos") ~ "CHAOS - ",
      str_detect(variable, "change_env") ~ "Changes - ",
      TRUE ~ ""
    )
  ) %>% 
  unite(col = "Item", c(variable, Label), sep = "") %>%
  select(Item, fl1, fl2, fl3, fl4, fl5) %>% 
  mutate(across(starts_with("fl"), ~round(., 2))) %>%
  rename(
    `1` = fl1,
    `2` = fl2,
    `3` = fl3,
    `4` = fl4,
    `5` = fl5
  ) %>%
  flextable(cwidth = c(5, .6,.6,.6,.6,.6))

```

### 2022-02-07 preregistrations/1_pilot/scripts/supplemental/supp_DDM.Rmd
exploratory effects of unpred. on flanker

---
title: "supp_DDM"
author: "Stefan Vermeent"
date: "8-12-2021"
output: html_document
---

# Libraries

```{r}
library(tidyverse)
library(here)
library(magrittr)
library(glue)
```

# Load data

```{r}
load(here("data", "1_pilot", "1_task_data_clean.Rdata"))
load(here("data", "1_pilot", "2_cleaned_data.Rdata"))
```

# EZDM Estimation

Does it matter whether Mean RT and RT variance are estimated based on correct trials only or the combination of correct and incorrect trials?

```{r}
supp_change_EZ_data <- change_data_clean_average %>%
  rename(
    rt_change_correct     = rt_change,
    rt_var_change_correct = rt_var_change) %>%
  left_join(
      change_data_clean_average %>% select(change_data_long) %>%
        unnest() %>%
        mutate(rt = rt/1000) %>%
        group_by(id) %>%
        summarise(
          rt_change_all = mean(rt, na.rm = T),
          rt_var_change_all = sd(rt, na.rm = T)^2 
        )
    ) %>%
  mutate(acc_change = ifelse(acc_change == 1, 1-(1/(2*50)), acc_change))

change_EZDM_results_correcttrials <- 
  pmap(supp_change_EZ_data[c("acc_change", "rt_var_change_correct", "rt_change_correct", "id")], function(acc_change,rt_var_change_correct,rt_change_correct, id) {

    EZ_fit <- Data2EZ(Pc = acc_change, VRT = rt_var_change_correct, MRT = rt_change_correct, s = 1) %>%
      as_tibble() %>%
      mutate(id = id)
  }) %>%
  bind_rows %>%
  select(id, change_EZ_v_correct = v, change_EZ_a_correct = a, change_EZ_t0_correct = Ter)

change_EZDM_results_alltrials <- 
  pmap(supp_change_EZ_data[c("acc_change", "rt_var_change_all", "rt_change_all", "id")], function(acc_change,rt_var_change_all,rt_change_all, id) {

    EZ_fit <- Data2EZ(Pc = acc_change, VRT = rt_var_change_all, MRT = rt_change_all, s = 1) %>%
      as_tibble() %>%
      mutate(id = id)
  }) %>%
  bind_rows %>%
  select(id, change_EZ_v_all = v, change_EZ_a_all = a, change_EZ_t0_all = Ter)
```

```{r fig.height = 10, fig.width = 8}

supp_change_DDM_params <- left_join(change_EZDM_results_alltrials, change_EZDM_results_correcttrials) %>%
  left_join(cleaned_data %>% select(id, matches("change_ml_(bad_fit|v|a|t0)")))

ggplot(supp_change_DDM_params, aes(change_EZ_a_correct, change_ml_a, color = change_ml_bad_fit)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1)

ggplot(supp_change_DDM_params, aes(change_EZ_t0_correct, change_ml_t0, color = change_ml_bad_fit)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1)

ggplot(supp_change_DDM_params, aes(change_EZ_t0_correct, change_EZ_t0_all, color = change_ml_bad_fit)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1)
```

# Attention Cueing

```{r}
cueing_ddm_data <- cleaned_data %>%
  select(id, starts_with(c("rt_cueing", "acc_cueing")), starts_with("cueing"), event_during_cueing, scale_factor, counterbalance, meta_resolution_height, meta_resolution_ratio, meta_feedback, cueing_data_long, -cueing_ml_fit) 
```

```{r, fig.height = 8, fig.width = 8}
cleaned_data %>%
  select(starts_with("cueing"), -cueing_data_long, -cueing_ml_fit) %>%
  cor(use = "complete.obs") %>% 
  corrplot(method = "number")
```

```{r}
cueing_ddm_data %>%
  select(id, matches("EZ")) %>%
  pivot_longer(matches("EZ"), names_to = "parameter", values_to = "value") %>%
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~parameter, scales = "free")
```

Some subjects have a negative non-decision time, which should not be possible. These might be the same people who are in the tail of the boundary separation distribution.

```{r}
cueing_ddm_data %>%
  ggplot(aes(cueing_cued_EZ_t0, cueing_cued_EZ_a)) +
  geom_point()

cueing_ddm_data %>%
  ggplot(aes(cueing_neutral_EZ_t0, cueing_neutral_EZ_a)) +
  geom_point()
```

Indeed, the people with t0 values below or close to zero also have the highest boundary separation. Is there anything that sets these participants apart?

```{r}
cueing_ddm_data %<>%
  mutate(
    high_a = factor(ifelse(cueing_neutral_EZ_a > 2, TRUE, FALSE))
  ) %>%
  drop_na(high_a)

ggplot(cueing_ddm_data, aes(high_a, rt_cueing_cued)) +
  geom_boxplot()

ggplot(cueing_ddm_data, aes(high_a, rt_cueing_neutral)) +
  geom_boxplot()

ggplot(cueing_ddm_data, aes(high_a, acc_cueing_cued)) +
  geom_boxplot() +
  geom_jitter(width = 0.15)

ggplot(cueing_ddm_data, aes(high_a, acc_cueing_neutral)) +
  geom_boxplot() +
  geom_jitter(width = 0.15)

ggplot(cueing_ddm_data, aes(acc_cueing_cued, rt_cueing_cued, color = cueing_cued_EZ_a)) +
  geom_jitter(width = 0.005)

ggplot(cueing_ddm_data, aes(acc_cueing_neutral, rt_cueing_neutral, color = cueing_neutral_EZ_a)) +
  geom_jitter(width = 0.005)

ggplot(cueing_ddm_data, aes(acc_cueing_neutral, acc_cueing_cued, color = cueing_neutral_EZ_a)) +
  geom_jitter(width = 0.008, height = 0.008)

ggplot(cueing_ddm_data, aes(rt_cueing_neutral, rt_cueing_cued, color = cueing_neutral_EZ_a)) +
  geom_jitter(width = 0.005)
```
Subjects with extremely high boundary separations are almost exclusively subjects with high accuracy and high reaction times in both conditions.

```{r}
ggplot(cueing_ddm_data, aes(cueing_neutral_EZ_a, meta_resolution_height)) +
  geom_point()

ggplot(cueing_ddm_data, aes(cueing_neutral_EZ_a, meta_resolution_ratio)) +
  geom_point()

ggplot(cueing_ddm_data, aes(cueing_neutral_EZ_a, scale_factor)) +
  geom_point()
```
```{r}
cueing_ddm_data_long <- cueing_ddm_data %>%
  #filter(high_a == TRUE) %>%
  select(high_a, cueing_data_long) %>%
  unnest()

cueing_ddm_data_long %>%
  ggplot(aes(rt, fill = factor(id))) +
  geom_histogram() +
  facet_wrap(~id) +
  guides(fill = "none")

cueing_ddm_data_long %>%
  group_by(id, high_a) %>%
  summarise(sum(rt > 2000)) %>% View

```

### 2022-02-07 preregistrations/1_pilot/scripts/0_data_prep/7_efa.R

@@ -1,0 +1,103 @@
+# Factor structure of unpredictability measures
+
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(magrittr)
+library(broom)
+library(here)
+library(stats)
+library(GPArotation)
+library(nFactors)
+
+load(here("data", "1_pilot", "2_cleaned_data.Rdata"))
+load(here("data", "1_pilot", "0_self_report_raw.Rdata"))
+
+# We conducted an EFA including all items measuring unpredictability: 1) The QUIC items, 2) the perceived unpredictability items, 
+# 3) the CHAOS items, 4) the items measuring environmental change, 5) number of partners of the father and mother, 
+# 6) Number of residential changes, 7) household size. 
+
+# The measures of residential changes and number of different partners of both parents were heavily positively skewed.
+
+
+efa_data <- cleaned_data %>%
+  select(matches("(quic\\d\\d)|(unp\\d\\d)|(chaos\\d\\d)|(change_env\\d\\d)"), 
+         unp_partners_father_binned, unp_partners_mother_binned, unp_household_size, unp_moving_binned) %>%
+  drop_na() %>%
+  mutate(across(matches("quic(01|02|03|04|05|06|07|08|09|11|14|16|22|32)"), ~ 6 - .)) %>%
+  mutate(across(matches("chaos(01|02|04|07|12|14|15)"), ~ 6 - .))
+
+
+# Determine optimal number of factors
+ev <- eigen(cor(efa_data)) # get eigenvalues
+ap <- parallel(subject=nrow(efa_data),var=ncol(efa_data),
+               rep=100,cent=.05)
+nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
+plotnScree(nS)
+
+efa_model <- factanal(efa_data, factors = 5, rotation = "oblimin")
+
+efa_model
+
+efa_tidy <- tidy(efa_model) %>% 
+  mutate(across(starts_with("fl"), ~ifelse(. < .32, NA, .))) %>% 
+  left_join(codebook %>% rename(variable = Variable)) %>% 
+  arrange(fl1, fl2, fl3, fl4, fl5) %>% 
+  mutate(
+    Label = case_when(
+      variable == "unp_moving_binned" ~ "Residential changes", 
[…]

### 2022-02-07 preregistrations/1_pilot/scripts/1_descriptives/1_demographics.R

@@ -1,0 +1,84 @@
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(flextable)
+library(here)
+
+cleaned_data <- read_csv(here("data", "1_pilot", "2_cleaned_data.csv"))
+
+ethnicity <- cleaned_data %>%
+  select(id, starts_with("dems")) %>%
+  transmute(var = ifelse(dems_ethnicity_mixed == 1, "Mixed", dems_ethnicity)) %>%
+  group_by(var) %>%
+  summarise(
+    percentage = round((n() / nrow(cleaned_data)) * 100, 1),
+  ) %>%
+  arrange(desc(percentage))
+
+education <- cleaned_data %>%
+  select(id, dems_edu) %>%
+  transmute(
+    var = case_when(
+      dems_edu == 1 ~ "Some high school",
+      dems_edu == 2 ~ "GED",
+      dems_edu == 3 ~ "High school diploma",
+      dems_edu == 4 ~ "Some college but no college degree",
+      dems_edu == 5 ~ "Associate's degree",
+      dems_edu == 6 ~ "Bachelor's or RN degree",
+      dems_edu == 7 ~ "Master's degree",
+      dems_edu == 8 ~ "Doctoral or law degree"
+    )
+  ) %>%
+  mutate(var = factor(var, levels = c("Some high school", "GED", "High school diploma", "Some college but no college degree", "Associate's degree", "Bachelor's or RN degree", "Master's degree", "Doctoral or law degree"))) %>%
+  group_by(var) %>%
+  summarise(percentage = round((n() / nrow(cleaned_data)) * 100, 1)) 
+
+
+gender <- cleaned_data %>%
+  select(id, dems_gender) %>% 
+  transmute(
+    var = case_when(
+      dems_gender == 1 ~ "Man",
+      dems_gender == 2 ~ "Woman",
+      dems_gender == 3 ~ "Non-binary",
+      dems_gender == 4 ~ "Other",
+      dems_gender == 5 ~ "Prefer not to say"
+    )
+  ) %>%
+  group_by(var) %>%
+  summarise(percentage = round((n() / nrow(cleaned_data)) * 100, 1)) %>%
+  arrange(desc(percentage))
+
+
+sex_at_birth <- cleaned_data %>%
+  select(id, dems_sex) %>% 
+  transmute(
+    var = case_when(
+      dems_sex == 0 ~ "Male",
+      dems_sex == 1 ~ "Female",
[…]

### 2022-02-07 preregistrations/1_pilot/scripts/3_exploratory_analyses/2_unpredictability/flanker/1_create_multiverse_datasets.R

@@ -9,9 +9,12 @@ source(here("preregistrations", "1_pilot", "scripts", "3_exploratory_analyses", 
 
 # Transfrom data to long format and prepare for analyses
 multiverse_data <- cleaned_data %>%
+  mutate(unp_quic = across(matches("unp\\d\\d|quic(01|02|03|04|05|06|07|08|09|10|11|12|13|14|15|16|17|18|19|20|21|22|23|24|25|26|27|28|29|30|31|32|33|34|35|36|37)")) %>% 
+           psych::reverse.code(keys = c(1,1,1,1,1,1,1,1,-1,-1,-1,-1,-1,-1,-1,-1,-1,1,-1,1,1,-1,1,-1,1,1,1,1,1,-1,1,1,1,1,1,1,1,1,1,-1,1,1,1,1,1), items = ., mini = 1, maxi = 5) %>% 
+           rowMeans(., na.rm = T)) %>%
   select(id, scale_factor, fullscreenenter, fullscreenexit, meta_captcha, attention_interrupt_sum, att_noise, unpredictability_composite,
          contains("flanker"), -flanker_data_long, -starts_with(c("rt_var", "acc_", "event_during")), -starts_with("start"),
-         starts_with("efa")) %>%
+         starts_with("efa"), unp_quic, chaos_mean, unpredictability_obj) %>%
   rename(flanker_congruent_rt_raw = rt_flanker_congruent, flanker_incongruent_rt_raw = rt_flanker_incongruent) %>%
   pivot_longer(starts_with("flanker"),
                names_to = c("condition", ".value"),
@@ -25,7 +28,7 @@ multiverse_data <- cleaned_data %>%
     flanker_interference = ifelse(rd_flanker > 0, sda_flanker / rd_flanker, NA)
   ) %>%
   # Center IVs
-  mutate(across(c(efa_daily_unp, efa_routine, efa_spatial_unp, efa_chaos_clutter, efa_social_unp), 
+  mutate(across(c(efa_daily_unp, efa_routine, efa_spatial_unp, efa_chaos_clutter, efa_social_unp, unp_quic, chaos_mean, unpredictability_obj), 
                 ~scale(., scale = F), .names = "{.col}_c"))
 
 # arbitrary decision grid -------------------------------------------------
@@ -33,7 +36,7 @@ multiverse_data <- cleaned_data %>%
 spec_grid <- 
   expand_grid(
[…]

### 2022-02-07 preregistrations/1_pilot/scripts/3_exploratory_analyses/2_unpredictability/flanker/3_extract_effects.R

@@ -63,7 +63,7 @@ exploratory_effects_unp_flanker <-
     pval_prop      = fct_reorder(pval_prop, mod_term_num))
 
 # Medians -----------------------------------------------------------------
-exploratory_effects_medians <- 
+e %>% xploratory_effects_medians <- 
   exploratory_effects_unp_flanker %>% 
   select(dv, dv_group, contains("_term"), contains("median_")) %>% 
   distinct()

### 2022-02-07 preregistrations/1_pilot/scripts/3_exploratory_analyses/2_unpredictability/flanker/4_plot_multiverse.R

@@ -72,7 +72,7 @@ spec_curves_ssp <-
     
     # Plots
     eff_curve <- 
-      map(c("EFA - daily", "EFA - routine", "EFA - spatial", "EFA - clutter", "EFA - social" ), function(x) {
+      map(c("EFA - daily", "EFA - routine", "EFA - spatial", "EFA - clutter", "EFA - social", "Perc. + QUIC", "CHAOS", "Obj. unpredictability"), function(x) {
         effs %>% 
           filter(spec_iv_type == x) %>%
           ggplot(aes(y = mod_std_coefficient, x = spec_rank, color = mod_sig)) +
@@ -116,7 +116,7 @@ spec_curves_ssp <-
       
     
     sample_sizes <- 
-      map(c("EFA - daily", "EFA - routine", "EFA - spatial", "EFA - clutter", "EFA - social"), function(x) {
+      map(c("EFA - daily", "EFA - routine", "EFA - spatial", "EFA - clutter", "EFA - social", "Perc. + QUIC", "CHAOS", "Obj. unpredictability"), function(x) {
         effs %>% 
           filter(spec_iv_type == x) %>%
           ggplot(aes(x = spec_rank, y = n, color = mod_sig)) +
@@ -135,7 +135,7 @@ spec_curves_ssp <-
           )})
     
     spec_grid <- 
-      map(c("EFA - daily", "EFA - routine", "EFA - spatial", "EFA - clutter", "EFA - social"), function(x) {
+      map(c("EFA - daily", "EFA - routine", "EFA - spatial", "EFA - clutter", "EFA - social", "Perc. + QUIC", "CHAOS", "Obj. unpredictability"), function(x) {
         spec_grid_data %>% 
           filter(spec_iv_type == x) %>%
           ggplot(aes(x = spec_rank, y = spec_value, color = mod_sig)) +
@@ -178,7 +178,7 @@ spec_curves_ssp <-
           )})
         
     p_curve <- 
-      map(c("EFA - daily", "EFA - routine", "EFA - spatial", "EFA - clutter", "EFA - social"), function(x) {
[…]

### 2022-02-07 preregistrations/1_pilot/scripts/4_stage_objects/1_intext_stats.R.R

@@ -1,0 +1,82 @@
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(here)
+
+load(here("data", "1_pilot", "2_cleaned_data.Rdata"))
+load(here("data", "1_pilot", "efa_data.Rdata"))
+
+cleaned_data %<>%
+  left_join(efa_variables)
+
+
+# IVs ---------------------------------------------------------------------
+
+txt_ivs <- 
+  cleaned_data %>%
+  summarize(
+    across(
+      .cols = matches("unp_mean|chaos_mean|quic_.*_mean|unpredictability_composite|violence_(composite|mean)|fighting_mean|
+                      poverty_composite|ses_(subj|obj)_mean|edu_parents_recoded|income_past_recoded|class_past_recoded|
+                      impuls_mean|fos_(fo|pa|fc|tp)_mean|stai_s_mean|depression_mean"), 
+      list(mean = mean, sd = sd, min = min, max = max), na.rm=T, .names = "{.fn}.{.col}")
+  ) %>% 
+  mutate(across(everything(), ~round(.x, 2))) %>% 
+  pivot_longer(everything()) %>% 
+  separate(name, into = c("stat","var"), sep = "\\.") %>% 
+  pivot_wider(names_from = var, values_from = c(value)) %>% 
+  select(-stat) %>% 
+  map(function(x) list(mean = x[1], sd = x[2]))
+
+# DVs ---------------------------------------------------------------------
+
+txt_dvs <- 
+  cleaned_data %>%
+  summarize(
+    across(
+      .cols = matches("^rt_|_ml_|_EZ_|(a|t0|p|rd|sda)_flanker)|^efa_"), 
+      list(mean = mean, sd = sd), na.rm=T, .names = "{.fn}.{.col}")
+  ) %>% 
+  mutate(across(everything(), ~round(.x, 2))) %>% 
+  pivot_longer(everything()) %>% 
+  separate(name, into = c("stat","var"), sep = "\\.") %>% 
+  pivot_wider(names_from = var, values_from = c(value)) %>% 
+  select(-stat) %>% 
+  map(function(x) list(mean = x[1], sd = x[2]))
+
+
+# Correlations ------------------------------------------------------------
+
+txt_cors <- 
+  map(
+    c(
+      "(violence|fighting)_mean",
+      "ses_subj_mean_recoded|ses_obj_mean"
+    ), 
[…]

### 2022-02-07 preregistrations/1_pilot/scripts/4_stage_objects/2_tables.R

@@ -1,0 +1,108 @@
+library(tidyverse)
+library(here)
+library(flextable)
+
+load(here("data", "1_pilot", "2_cleaned_data.Rdata"))
+
+# Demographics - Gather data ----------------------------------------------
+
+ethnicity <- cleaned_data %>%
+  select(id, starts_with("dems")) %>%
+  transmute(var = ifelse(dems_ethnicity_mixed == 1, "Mixed", dems_ethnicity)) %>%
+  group_by(var) %>%
+  summarise(
+    percentage = round((n() / nrow(cleaned_data)) * 100, 1),
+  ) %>%
+  arrange(desc(percentage))
+
+education <- cleaned_data %>%
+  select(id, dems_edu) %>%
+  transmute(
+    var = case_when(
+      dems_edu == 1 ~ "Some high school",
+      dems_edu == 2 ~ "GED",
+      dems_edu == 3 ~ "High school diploma",
+      dems_edu == 4 ~ "Some college but no college degree",
+      dems_edu == 5 ~ "Associate's degree",
+      dems_edu == 6 ~ "Bachelor's or RN degree",
+      dems_edu == 7 ~ "Master's degree",
+      dems_edu == 8 ~ "Doctoral or law degree"
+    )
+  ) %>%
+  mutate(var = factor(var, levels = c("Some high school", "GED", "High school diploma", "Some college but no college degree", "Associate's degree", "Bachelor's or RN degree", "Master's degree", "Doctoral or law degree"))) %>%
+  group_by(var) %>%
+  summarise(percentage = round((n() / nrow(cleaned_data)) * 100, 1)) 
+
+
+gender <- cleaned_data %>%
+  select(id, dems_gender) %>% 
+  transmute(
+    var = case_when(
+      dems_gender == 1 ~ "Man",
+      dems_gender == 2 ~ "Woman",
+      dems_gender == 3 ~ "Non-binary",
+      dems_gender == 4 ~ "Other",
+      dems_gender == 5 ~ "Prefer not to say"
+    )
+  ) %>%
+  group_by(var) %>%
+  summarise(percentage = round((n() / nrow(cleaned_data)) * 100, 1)) %>%
+  arrange(desc(percentage))
+
+
+sex_at_birth <- cleaned_data %>%
+  select(id, dems_sex) %>% 
+  transmute(
+    var = case_when(
+      dems_sex == 0 ~ "Male",
+      dems_sex == 1 ~ "Female",
[…]

### 2022-02-07 preregistrations/1_pilot/scripts/old/decision_grids_tasks.R

@@ -1,0 +1,100 @@
+# Change Detection Task
+decision_grid_change <- expand_grid(
+  ex_arb_low_res              = c("meta_resolution_height > 0",            "meta_resolution_height > 700"),        
+  ex_arb_no_resize            = c("scale_factor > 0",                      "round(scale_factor, 4) != '0.3081'"),
+  ex_arb_no_fullscreen        = c("fullscreenenter %in% c(0,1)",           "fullscreenenter == 1"),
+  ex_arb_exit_fullscreen      = c("fullscreenexit %in% c(0,1)",            "fullscreenexit == 0"),
+  ex_arb_event_during_change  = c("is.logical(event_during_change)",       "event_during_change == TRUE"),
+  ex_arb_captcha              = c("meta_captcha > 0",                      "meta_captcha > 0.4"),
+  ex_arb_interrupt            = c("attention_interrupt_sum %in% c(0,1,2)", "attention_interrupt_sum < 2"),
+  ex_arb_noise                = c("att_noise %in% c(0,1,2,3,4)",           "att_noise %in% c(0,1,2)")
+)
+
+decision_grid_change_key <- tribble(
+  ~variable,                      ~variable_group,      ~exp,                                    ~name,
+  "ex_arb_low_res",               "resolution",         "meta_resolution_height > 0",            "Resolution too low",
+  "ex_arb_low_res",               "resolution",         "meta_resolution_height > 700",          "All resolutions",
+  "ex_arb_no_resize",             "resize",             "scale_factor > 0",                      "All scalings",
+  "ex_arb_no_resize",             "resize",             "round(scale_factor, 4) != '0.3081'",    "No scaling",
+  "ex_arb_no_fullscreen",         "fullscreen",         "fullscreenenter %in% c(0,1)",           "No fullscr. incl.",
+  "ex_arb_no_fullscreen",         "fullscreen",         "fullscreenenter == 1",                  "No fullscr. excl.",
+  "ex_arb_exit_fullscreen",       "fullscreen",         "fullscreenexit %in% c(0,1)",            "Exit fullscr. incl.",
+  "ex_arb_exit_fullscreen",       "fullscreen",         "fullscreenexit == 0",                   "Exit fullscr. excl.",
+  "ex_arb_event_during_change",   "blur event",         "is.logical(event_during_change)",       "Blur events incl.",
+  "ex_arb_event_during_change",   "blur event",         "event_during_change == TRUE",           "Blur events excl.",
[…]

### 2022-02-07 preregistrations/1_pilot/scripts/presentations/presentation.R

@@ -1,0 +1,80 @@
+library(officer)
+library(magrittr)
+
+primary <- read_pptx() %>%
+  # Title page
+  add_slide(layout = "Title Slide", master = "Office Theme") %>%
+  ph_with(value = "Pilot Study", location = ph_location_type(type = "ctrTitle")) %>%
+  ph_with(value = "Analyses on raw performance\n(RT and accuracy)", location = ph_location_type(type = "subTitle")) %>%
+  
+  
+  # Change Detection distributions:
+  add_slide(layout = "Title and Content", master = "Office Theme") %>%
+  ph_with("Change Detection Task", location = ph_location_type("title")) %>%
+  ph_with(supp_fig1, location = ph_location_type(type="body")) %>%
+  # Cued Attention distributions:
+  add_slide(layout = "Title and Content", master = "Office Theme") %>%
+  ph_with("Cued Attention Task", location = ph_location_type("title")) %>%
+  ph_with(supp_fig2, location = ph_location_type(type="body")) %>%
+  # Flanker distributions:
+  add_slide(layout = "Title and Content", master = "Office Theme") %>%
+  ph_with("Flanker Task", location = ph_location_type("title")) %>%
+  ph_with(supp_fig3, location = ph_location_type(type="body")) %>%
+  
+  
+  # Primary analyses: Effect of violence on raw performance
+  add_slide(layout = "Title Slide", master = "Office Theme") %>%
+  ph_with(value = "Primary analyses: Violence on Raw Performance", location = ph_location_type(type='ctrTitle')) %>%
+  
+  
+  # Covariates
+  add_slide(layout = "Title and Content", master = "Office Theme") %>%
+  ph_with(value = "Identifying potential covariates", location = ph_location_type("title")) %>%
+  ph_with(flextable::flextable(covariates, cwidth = c(1.6, rep(0.6, 18))), location = ph_location(left=0, top = 1.5)) %>%
+
+  # Change Detection Task
+  add_slide(layout = "Two Content", master = "Office Theme") %>%
+  ph_with("Change Detection Task", location = ph_location_type("title")) %>%
[…]

### 2022-02-07 preregistrations/1_pilot/scripts/stage_objects.R

@@ -1,0 +1,285 @@
+load(here("data", "1_pilot", "2_cleaned_data.Rdata"))
+load(here("data", "1_pilot", "3_primary_analyses_results.Rdata"))
+load(here("data", "1_pilot", "3_secondary_analyses_results.Rdata"))
+
+
+
+# Functions ---------------------------------------------------------------
+
+tidy_lmer_table <- function(model_tidy, std_effects, iv, iv_rename) {
+  
+  model_tidy %>%
+    left_join(std_effects %>% select(term=Parameter, Std_Coefficient)) %>%
+    filter(term != "(Intercept)", effect == "fixed") %>%
+    select(term, estimate, Std_Coefficient, std.error, statistic, p.value) %>%
+    mutate(
+      term = case_when(
+        term == str_glue("{iv}") ~ str_glue("{iv_rename}"),
+        term == "condition_sum" ~ "Task condition",
+        term == str_glue("{iv}:condition_sum") ~ str_glue("{iv_rename}*Condition"),
+        term == "event_during_task" ~ "Browser event during task",
+        term == "scale_factor" ~ "Task scaling"
+      )
+    ) %>%
+    arrange(factor(term, levels = c(str_glue("{iv_rename}"), "Task condition", str_glue("{iv_rename}*Condition"), "Browser event during task", "Task scaling"))) %>%
+    rename(
+      IV   = term,
+      b    = estimate,
+      Beta = Std_Coefficient,
+      SE   = std.error,
+      t    = statistic,
+      p    = p.value,
+    ) %>%
+    mutate(across(c(b, Beta, SE, t), ~round(.,2))) %>%
+    mutate(p = ifelse(p < .001, "< .001", round(p, 3)))
+}
+
+tidy_lm_table <- function(model_tidy, std_effects, iv, iv_rename) {
+  model_tidy %>%
+    left_join(std_effects %>% select(term=Parameter, Std_Coefficient)) %>%
+    filter(term != "(Intercept)") %>%
+    select(term, estimate, Std_Coefficient, std.error, statistic, p.value) %>%
+    mutate(
+      term = case_when(
+        term == str_glue("{iv}") ~ str_glue("{iv_rename}"),
+        term == "event_during_task" ~ "Browser event during task",
+        term == "scale_factor" ~ "Task scaling"
+      )
+    ) %>%
+    rename(
[…]

### 2022-02-07 preregistrations/1_pilot/scripts/supplemental/cueing_model_comparisons.R

@@ -1,0 +1,94 @@
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(here)
+library(RWiener)
+library(mvtnorm)
+library(flankr)
+library(corrplot)
+
+# Load data ---------------------------------------------------------------
+
+load(here("data", "1_pilot", "1_DDM_objects.Rdata"))
+
+
+
+# Explore model differences -----------------------------------------------
+
+## T-test on boundary separation ----
+t.test(cueing_DDM_results_mod1$a_cued, cueing_DDM_results_mod1$a_neutral, paired = T)
+
+## Parameter and model fit comparisons across models ----
+bind_rows(
+  cueing_DDM_results_mod1 %>% mutate(iteration = "a_dependent"), 
+  cueing_DDM_results_mod2 %>% mutate(a_neutral = a, a_cued = a, iteration = "a_independent") %>% select(-a)) %>%
+  pivot_longer(ends_with(c("neutral", "cued")), names_to = "parameter", values_to = "value") %>%
+  select(id, iteration, parameter, value) %>%
+  pivot_wider(names_from = "iteration", values_from = "value") %>%
+  ggplot(aes(a_dependent, a_independent)) +
+  geom_point() +
+  facet_wrap(~parameter, scales = "free") +
+  labs(
+    title = "Parameter comparison across model versions"
+  )
+
+bind_rows(
+  cueing_DDM_results_mod1 %>% mutate(iteration = "a_dependent"), 
+  cueing_DDM_results_mod2 %>% mutate(iteration = "a_independent")) %>%
+  select(id, iteration, fit) %>%
+  pivot_wider(names_from = "iteration", values_from = "fit") %>%
+  ggplot(aes(a_dependent, a_independent)) +
+  geom_point() +
+  geom_abline(slope = 1, intercept = 0) +
+  labs(
+    title = "Model fit comparison across model versions"
+  )
+
+## Parameter correlations across and within models ----
+cueing_DDM_results_mod1 %>% select(v_cued, t0_cued, a_cued, v_neutral, t0_neutral, a_neutral) %>% cor %>% corrplot(method = "number")
+cueing_DDM_results_mod2 %>% select(ends_with(c("cued", "neutral")), a) %>% cor %>% corrplot(method = "number")
+
+## Comparisons between parameter values across conditions
+cueing_DDM_results_mod1 %>%
[…]

### 2022-02-07 preregistrations/1_pilot/scripts/supplemental/dist_plots.R

@@ -1,0 +1,145 @@
+theme_no_legend <- theme(
+    legend.position = c(0.15, 0.85),
+    legend.background = element_rect(fill = "transparent"),
+    legend.text = element_text(color = "transparent"),
+    legend.title = element_text(color = "transparent"),
+    legend.key = element_rect(fill = "transparent")
+)
+
+theme_legend_cowplot <- theme(
+  legend.position = c(0.4, 0.80)
+)
+
+
+load(here("data", "1_pilot", "2_cleaned_data.Rdata"))
+
+
+# Change Detection Task ---------------------------------------------------
+
+supp_fig1a <- cleaned_data %>%
+  select(rt_change) %>%
+  ggplot() +
+  geom_density(aes(rt_change*1000), fill = "#345995") +
+  scale_alpha_manual(name = NULL, 
+                     values = c(1)) +
+  guides(alpha = 'none') +
+  scale_fill_manual(
+    values = c("#345995"),
+    guide = guide_legend(override.aes = list(color = "transparent", fill = "transparent"))
+  ) +
+  theme_bw() +
+  theme_no_legend + 
+  labs(
+    x = "\nReaction Time (ms)",
+    y = "Density\n",
+    title = ""
+  )
+
+supp_fig1b <- cleaned_data %>%
+  select(acc_change) %>%
+  ggplot() +
+  geom_density(aes(acc_change*100), fill = "#345995") +
+  scale_alpha_manual(name = NULL, 
+                     values = c(1)) +
+  guides(alpha = 'none') +
+  scale_fill_manual(
+    values = c("#345995"),
+    guide = guide_legend(override.aes = list(color = "transparent", fill = "transparent"))
+  ) +
+  theme_bw() +
+  theme_no_legend + 
+  labs(
+    x = "\nAccuracy (%)",
+    y = "Density\n",
+    title = ""
+  )
+
+supp_fig1 <- cowplot::plot_grid(supp_fig1a, supp_fig1b, labels = "AUTO")
+
+
+
+supp_fig2a <- cleaned_data %>%
+  select(rt_flanker_congruent, rt_flanker_incongruent) %>%
+  pivot_longer(everything(), names_to = "condition", values_to = "rt") %>%
+  ggplot() +
+  geom_density(aes(rt*1000, group = condition, fill = condition, alpha = condition)) +
+  scale_alpha_manual(name = NULL, 
[…]

### 2022-02-10 preregistrations/2_study1/preregistration.Rmd
update to prereg

@@
 ---
-title: "preregistration"
-author: "Stefan Vermeent"
-date: "20-1-2022"
-output: html_document
+bibliography: references.bib
+csl: apa.csl
+output:
+  officedown::rdocx_document:
+    page_margins:
+      bottom: 1
+      footer: 0
+      gutter: 0
+      header: 0.5
+      left: 1
+      right: 1
+      top: 1
+    plots:
+      align: center
+      caption:
+        pre: 'Figure '
+        sep: '. '
+        style: Image Caption
+    reference_docx: reference-doc.docx
+    tables:
+      caption:
+        pre: 'Table '
+        sep: '. '
+        style: Table Caption
+  pdf_document: default
+  word_document: default
 ---
+
+```{r setup, include=FALSE}
+
+# Load libraries
+library(tidyverse)
+library(officer)
+library(flextable)
+library(here)
+
+# set up chunk options
+knitr::opts_chunk$set(
+  echo = F,
+  fig.align = "center",
+  fig.pos = "!t", 
+  out.extra = "",
+  fig.show = "asis",
+  message = FALSE,
+  warning = FALSE
+)
+
+# set up flextable for tables
+set_flextable_defaults(
+  font.family = "Times", 
+  font.size = 10,
+  font.color = "black",
+  line_spacing = 1,
+  padding.bottom = 1, 
+  padding.top = 1,
+  padding.left = 1,
+  padding.right = 1
+)
+```
 
@@
 
-# Methods
+There is ample research to suggest that experiencing adversity early in life has a profound effect on the way in which people attend to information.
+Generally, the patterns point to an attention deficit, such that adversity-exposed people take longer to point their attention towards relevant information and are more susceptible to the influence of distracting or otherwise irrelevant information [@schibli_2017].
+Attention-deficit/hyperactivity disorder (ADHD).
+However, instead of pointing to a general attention deficit, differences in performance on tasks requiring attention control might reflect different attentional strategies that developed to navigate dangerous and unpredictable environments [e.g., increased vigilance; @frankenhuis_2016].
+Understanding the attention skills of people from adversity is important because attention control has been identified as one of the key mechanisms underlying performance on higher-level executive processes [@draheim_2021].
 
-## Participants
+Hidden talents research makes the often implicit assumption that enhanced abilities might reflect an enhanced focus on the here-and-now [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013].
+For example, @frankenhuis_2016 argued that living in a harsh and unpredictable environment might require a stronger present-orientation (as opposed to being focused on the future) in order to deal with unpredictable threats and benefit from fleeting rewards.
+In line with this, we initially expected people from adversity to perform better on cognitive tasks that require a broad attention scope in order to successfully detect peripheral and subtly changing information, and to perform worse on tasks requiring ignoring interfering information (see the [preregistration](https://github.com/StefanVermeent/attention_project/blob/Preregistration/preregistrations/1_pilot/preregistration.docx) of the first pilot study).
+However, the data pointed in the opposite direction.
+A Drift Diffusion analysis showed that participants with more violence exposure were slower to process information and orient their attention across all three tasks.
+At the same time, they were faster to narrow down their attention to the central target on the Flanker Task, thereby effectively limiting the amount of flanker interference that they were exposed to.
+The goal of the current study is to replicate the attention findings on the Flanker Task, and to better understand the apparent information processing deficits.
 
-## Materials
+In the current study, we focus on the Flanker Task
+
+One possibility that has yet to be empirically tested is that such effects are driven by a shared present and/or externally oriented attention mechanism.
+In this pilot study, we leverage the DDM to better understand the processes involved in performance differences, specifically by focusing on basic attention skills.
+
+# Methods {#methods}
+
+## Participants {#participants}
+
+Participants were 550 US-based individuals between the ages of 18 and 30 (*M* = `r #TBD`, *SD* = `r #TBD`).
+We decided for this age cut-off to reduce the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 [@salthouse_2010].
+Recruitment took place through Prolific Academic [www.prolific.co].
+The sample was balanced to include roughly 50% males.
+Participants were eligible for the study if they were from the United States and if they spoke fluent English.
+
+We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the optimal number of participants to include (more information including all simulation code on [Github](https://github.com/StefanVermeent/attention_project/tree/preregistration1/preregistrations/1_pilot/scripts)).
+We ran simulations for two scenarios: A linear regression model to test the effect of adversity (standardized) on attention performance (standardized) and a mixed regression model to test the adversity (standardized) X task condition (sum-coded) interaction, including a random intercept for subjects.
+We ran simulations for a standardized $\beta$ of 0.10 and 0.15.
+In addition, we simulated the power to detect these effects with imperfectly recovered DDM parameters, assuming a recovery accuracy (i.e., correlation between data-generating parameter value and actually recovered parameter value) of *r* = 0.85 (see the [Github link](https://github.com/StefanVermeent/attention_project/tree/preregistration1/preregistrations/1_pilot/scripts) for more information).
+
+In determining the final sample size, we weighed the simulation results together our uncertainty about certain model parameters (mostly the fixed effects and sigma term for the mixed model) and the fact that this was a first, mostly exploratory pilot study.
+For the mixed model, we found that power was > .80 for the adversity X task condition interaction with *N* = 450 or more.
+For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require *N* = `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`.
+When DDM parameter recovery accuracy was *r* = .85, power was `r (power_linear %>% filter(n_subjects == 500, fixed_effect == 0.15, effect == "linear_recov_main_power") %>% pull(power))/100` for *N* = 500 and $\beta$ = 0.15.
+Power was `r (power_linear %>% filter(n_subjects == 500, fixed_effect == 0.1, effect == "linear_recov_main_power") %>% pull(power))/100` under the same scenario when $\beta$ was 0.10.
+Ultimately, we decided on sampling 550 participants with an anticipated final sample size of around 500.
+
+## Exclusion criteria {#exclusion}
+
+We applied several exclusion criteria prior to analyzing the data.
+First, we excluded participants who did not complete the full study and those who had incomplete data on any of the attention tasks (*N* = `r #TBD `).
+Second, we analyzed responses to the attention checks and reversed coded items in the questionnaire part of the experiment.
+We excluded participants if they missed both attention check items or if they had suspicious response patterns (e.g., consistently endorsing high response options even when some items were reverse coded) (*N* = `r #TBD `).
+
+In addition, we screened the reaction times on each of the three attention tasks.
+For the Drift Diffusion analyses, it is important that each response is generated by a process of active information accumulation (i.e., a diffusion process, as opposed to guessing).
+To this end, trials with reaction times < 250 ms or > 3500 ms [@ratcliff_2015] were excluded from the analyses (*N* = `r #TBD `).
+Participants with more than 10 removed trials were excluded from the analyses (N = `r #TBD `).
+
+The exclusion criteria listed above are our best *a-priori* guesses. However, we expect to develop additional criteria empirically after collecting the data.
+
+## Measures {#measures}
+
+The Flanker Task was programmed in JsPsych version 3.6.1 [@deLeeuw_2015].
+
+### Flanker Task {#flanker}
+
+The Flanker Task is commonly used as a measure of selective attention and response inhibition [@eriksen_1974].
+On each trial of a typical Flanker Task, participants are presented with a set of five arrows pointing either left or right.
+Their job is to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right (see Figure \@ref(fig:figure1)b).
+On 50% of the trials, the flanking arrows point in the same direction as the central arrow (i.e., congruent trials), and on the other 50% of the trials they point in the opposite direction (i.e., incongruent trials).
+
+We programmed three conditions of the Flanker Task (See Figure \@ref(fig:figure1).
+In the standard condition, the arrows were 40 pixels in size (0.4 inches) and had zero padding between them.
+In the 'enhanced' condition, the aim was to increase the quality of visual information provided by the arrows.
+To this end, we increased the arrow size by 50% to 60 pixels (0.6 inches), and increased padding between the arrows to 20 pixels.
+In the 'degraded' condition, the aim was to decrease the quality of visual information provided by the arrows.
+The arrow size and padding were the same as in the standard version, but both flanking and target arrows were rotated 45$^\circ$.
+Therefore, they provided more noisy information about their horizontal direction.
+
+Participants completed each condition of the Flanker Task separately in different blocks.
+The presentation order of the conditions was randomized.
+Each condition consisted of 64 trials.
+For the degraded condition, participants completed four repetitions of all parameter combinations: Arrow location (top vs.
+bottom) X central arrow direction (left-up vs.
+left-down vs.
+right-up, vs right-down) X congruency: (congruent vs.
+incongruent).
+For the standard and enhanced condition, participants completed eight repetitions of all parameter combinations to match the number of trials in the degraded condition: Arrow location (top vs.
+bottom) X central arrow direction (left-up vs.
+left-down vs.
+right-up, vs right-down) X congruency: (congruent vs.
+incongruent).
+Across all three conditions, the arrows were randomly presented in the top-half or bottom-half of the screen at 200 pixels (2 inches) from the center of the screen.
+This was done to prevent participants from rigidly fixating on the center of the screen, which might reduce the interfering effect of the flanking arrows.
+Each trial started with a fixation cross presented at the center of the screen.
+After a delay of 1000ms, the arrows are presented either in the top- or bottom-half of the screen.
+
+Before the first block, participants performed eight practice trials for each condition: First standard, then enhanced, and then degraded.
+During practice, participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
+After completing the practice trials, participants completed each block with the opportunity to take a break in between.
+At the onset of each block, participants were told what the current condition was.
+No performance feedback was provided during the test blocks.
+The main performance measures were RTs and accuracy for each condition.
+
+```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap="Overview of the three cognitive tasks."}
+knitr::include_graphics("figure1.png", error = F)
+```
+
+### Current state {#state}
+
+We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [STAI-S; @spielberger_1999].
+The STAI-S contains 20 short items measuring current anxiety (e.g., "I feel tense"; See [Table S1](#appendix) for an overview of all items).
+Participants rated each item on a scale of 1 (not at all) to 4 (very much so).
+An overall state anxiety variable was computed by averaging across the 20 unweighted items (*M* = `r txt_ivs$stai_s_mean$mean`, *SD* = `r txt_ivs$stai_s_mean$sd`, $\alpha$ = `r #TBD `).
+
+In addition, participants answered five questions relating to specific states: "Are you currently sick?" (rated as yes or no); "Have you eaten a full meal today?" (rated as yes or no); "How hungry do you feel right now?" (rated from 1 (not at all) to 5 (very hungry)); "How well did you sleep last night?" (rated from 1 (very poorly) to 5 (very well)); "How rested or refreshed did you feel when you woke up this morning?" (rated from 1 (not at all) to 5 (very rested)).
+We computed an overall sleep deprivation composite by standardizing and averaging across the two unweighted sleep-related items (*M* = `r #TBD `, *SD* = `r #TBD `).
+
+### Violence exposure {#violence}
+
+Violence exposure was measured using the Neighborhood Violence Scale [NVS; @frankenhuis_2018; @frankenhuis_deVries_2020] and two items assessing exposure to physical fights before age 13.
+The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up"; See [Table S2](#appendix) for an overview of all items).
+Participants rated each on a scale from 1 (never true) to 5 (very often true).
+The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
+The items of the NVS were averaged together (*M* = `r txt_ivs$violence_mean$mean`, *SD* = `r txt_ivs$violence_mean$sd`, $\alpha$ = `r #TBD `).
+Similarly, we averaged the scores on the two fighting items together.
+Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average (*r* = `r txt_cors$vio$r`).
+
+### Unpredictability {#unpred}
+
+Perceived unpredictability before age 13 was measured using two different scales: A scale of perceived childhood unpredictability used in previous research [@mittal_2015; @young_2018], an adaptation of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019], and two scales measuring change in the family and social environment.
+The perceived childhood unpredictability scale contained eight items measuring perceived unpredictability before age 13 (e.g, "My family life was generally inconsistent and unpredictable from day-to-day"; See [Table S3](#appendix) for an overview of all items).
+Participants rated each on a scale from 1 (never true) to 5 (very often true).
+
+We included the QUIC because it captures several dimensions of environmental and household unpredictability.
+The QUIC distinguishes between items capturing more short-term unpredictability (i.e., on the level of seconds to minutes) and more long-term unpredictability (i.e., on the level of days to months).
+The scale of perceived childhood unpredictability combines items on different time scales.
+Some items measure unpredictability on a relatively short-term scale (e.g., item 1) while other items measure unpredictability on a long-term scale (e.g., item 3).
+Unpredictability on different time scales might have different effects on the development of specific attention styles.
+
+We included all five scales of the QUIC: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 3) Safety and security (See [Table S4](#appendix) for an overview of all items).
+The items of the Parental environment subscale deviated most from the original.
+
+We made three general changes to the original scale as described in @glynn_2019.
+First, we adapted all items to refer to experiences before age 13.
+This was done to reduce cognitive load from having to go back-and-forth between different time scales.
+Second, most items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
+An exception was made for four items of the parental environment scale which asked for more specific experiences (e.g., "I experienced changes in my custody arrangement"; see [Table S4](#appendix)).
+For these items, we adopted a response scale with the options "never", "only once", "a couple times", "several times", "many times".
+Third, quantifiers such as "frequently", "often", and "There was a period of time when [...]" were dropped to better match the response scale.
+We excluded the item "My parents got divorced" because it did not fit the response format and was captured by one of the items of the perceived unpredictability scale.
+
+We assessed household chaos before age 13 using an adaptation of the Confusion, Hubbub, and Order Scale [CHAOS; @matheny_1995].
+The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late"; See [Table S5](#appendix) for an overview of all items).
+We made two changes to the original scale as described in @matheny_1995.
+First, all items were converted from the present tense to the past tense, and were endorsed as applying to participants' lives before age 13.
+Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
+This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
+We treated household chaos
+
+In addition, we measured the stability of the family and social environment.
+On a scale of 1 (the same all the time) to 5 (constant and rapid changes), participants indicated how often the following aspects of their family and social environment changed before age 13: 1) economic status, 2) family environment, 3) childhood neighborhood environment, and 4) childhood school environment.
+Finally, we included four objective measures of unpredictability before age 13.
+Participants provided answers to the following items in an open response format: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "How many romantic partners did your mother have (not counting your father)?"; 4) "How many romantic partners did your father have (not counting your mother)?".
+
+We computed four main unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) *unpredictability~perceived~*: containing all items of the perceived unpredictability scale and the QUIC, given their close conceptual overlap (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD` *r* = `r #TBD` between the two scales); 2) *unpredictability~CHAOS~*: containing the items of the CHAOS (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`); 3) *unpredictability~subjective~*: containing all items of the perceived unpredictability scale, the QUIC and the CHAOS (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`); 4) *unpredictability~objective*: containing the items assessing the stability of the family- and social environement, as well as the four objective measures (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`).
+
+We computed several unweighted unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r txt_ivs$unp_mean$mean`, *SD* = = `txt_ivs$unp_mean$sd`, $\alpha$ = `r #TBD `); 2) an overall QUIC variable by averaging all 37 items (*M* = `r txt_ivs$quic_total_mean$mean`, *SD* = = `r txt_ivs$quic_total_mean$sd`, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r txt_ivs$quic_monitoring_mean$mean`, *SD* = `r txt_ivs$quic_monitoring_mean$sd`, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r txt_ivs$quic_par_predict_mean$mean`, *SD* = `r txt_ivs$quic_par_predict_mean$sd`, $\alpha$ = `r #TBD `; Parental environment: *M* = `r txt_ivs$quic_par_env_mean$mean`, *SD* = `r txt_ivs$quic_par_env_mean$sd`, $\alpha$ = `r #TBD `; Physical environment: *M* = `r txt_ivs$quic_phys_env_mean$mean`, *SD* = `r txt_ivs$quic_phys_env_mean$sd`, $\alpha$ = `r #TBD `; Safety and security: *M* = `r txt_ivs$quic_safety_mean$mean`, *SD* = `r txt_ivs$quic_safety_mean$sd`, $\alpha$ = `r #TBD `).
+See also [below](#efa) for details on a factor analysis based on the individual items across scales.
+
+### Poverty exposure {#ses}
+
+Participants' perceived level of resource scarcity before age 13 was measured using seven items (e.g., "Your family had enough money to afford the kind of home you all needed"; See [Table S6](#appendix) for an overview of all items).
+Participants rated each item on a scale from 1 (never true) to 5 (very often true).
+Scores for the first six items were reverse coded so that higher scores indicated more perceived resource scarcity.
+The items were averaged together to create an unweighted composite scale (*M* = `r txt_ivs$ses_subj_mean$mean`, *SD* = `r txt_ivs$ses_subj_mean$sd`, $\alpha$ = `r #TBD `).
+
+In addition, we measured several indicators of objective SES before age 13.
+First, participants separately indicated the highest education of their mother and father on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'.
+The mother and father education level were averaged to create an overall unweighted parental education composite (*M* = `r 8-txt_ivs$edu_parents_recoded$mean`, *SD* = `r txt_ivs$edu_parents_recoded$sd`).
+Participants also indicated their family's household income before age 13 on a 6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'.
+Scores were reverse coded so that higher scores indicated higher levels of poverty.
+
+We created a composite score of poverty exposure before age 13 by averaging together the standardized scores of perceived level of resource scarcity, overall parental education, and household income.
+
+### Impulsivity {#impulsivity}
+
+We assessed impulsivity with the Motor Impulsivity subscale of the Barrett Impulsivity Scale (BIS; short form; [@patton_1995; @spinella_2007]).
+The Motor Impulsivity subscale of the BIS consists of five items (e.g., "I do things without thinking"; See [Table S7](#appendix) for an overview of all items).
+We did not include the Non-planning subscale because it overlapped substantially with the Future Orientation Scale described below.
+In addition, we did not include the Attention impulsivity subscale because it included items which we deemed to be mostly irrelevant for our target population (e.g., "I 'squirm' at plays or lectures").
+We changed the original 4-point rating scale (rarely/never to almost always) to a 5-point rating scale ranging from 1 (never true) to 5 (very often true).
+An overall impulsivity variable was computed by averaging the five unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+
+### Future Orientation {#future_orientation}
+
+We assessed future orientation with an adapted version of the Future Orientation Scale [FOS; @steinberg_2009].
+The original scale consists of 15 sets of opposing items separated by "BUT" (e.g., "Some people like to plan things out one step at a time BUT other people like to jump right into things without planning them out beforehand").
+Participants first choose the item that best matches their general preference, and then indicate whether the statement is "really true" or "somewhat true".
+We adapted this format in a couple of ways.
+First, we converted the two statements per item to a single statement by picking the statements in the original right-hand column.
+Second, we adapted the 15 statements from a third-person to a first-person format.
+These changes were made in an attempt to reduce the cognitive load of the items.
+We worried that people with less formal education or who were sitting in a noisier environment would struggle with the length of the original items.
+
+In addition, item 8 of the original scale ("[...] other people would rather spend their money right away on something fun than save it for a rainy day") was changed to "I'd rather spend money right away than save it for a rainy day" (i.e., dropping the phrase "on something fun") to make it more general with regard to the thing that money is spent on.
+For people from adversity, spending money right now instead of saving it for the future might often be born out of necessity (e.g., having just enough money for food and shelter; being in debt) instead of a failure to delay gratification.
+See [Table S8](#appendix) for an overview of all adapted items).
+Finally, the rating scale was adapted from the original 4-point scale (ranging from really true for the left-hand statement to really true for the right-hand statement) to a 5-point scale ranging from 1 (never true) to 5 (very often true).
+
+An overall future orientation variable was computed by averaging the 15 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+In addition, we calculated subscales for "Planning ahead" (items 1, 6, 7, 12 and 13), "Time perspective" (items 2, 5, 8, 11 and 14) and "Anticipation of future consequences" (items 3, 4, 9, 10 and 15).
+
+### Depressive symptoms {#depression}
+
+We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD; @radloff_1977].
+The scale consists of 20 items (e.g., "I do things without thinking"; See [Table S9](#appendix) for an overview of all items).
+Participants rate each item on a scale of 1 (rarely or none of the time (less than 1 day)) to 4 (most or all of the time (5-7 days)).
+An overall depression variable was computed by averaging the 20 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
 
@@
 
-There is ample research to suggest that experiencing adversity early in life has a profound effect on the way in which people attend to information.
-Generally, the patterns point to an attention deficit, such that adversity-exposed people take longer to point their attention towards relevant information and are more susceptible to the influence of distracting or otherwise irrelevant information [@schibli_2017].
-Attention-deficit/hyperactivity disorder (ADHD).
-However, instead of pointing to a general attention deficit, differences in performance on tasks requiring attention control might reflect different attentional strategies that developed to navigate dangerous and unpredictable environments [e.g., increased vigilance; @frankenhuis_2016].
-Understanding the attention skills of people from adversity is important because attention control has been identified as one of the key mechanisms underlying performance on higher-level executive processes such as working memory capacity, which is related to a host of real-world academic and social outcomes [@draheim_2021].
+### DDM estimation
 
-Hidden talents research makes the often implicit assumption that enhanced abilities might reflect an enhanced focus on the here-and-now [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013].
-For example, @frankenhuis_2016 argued that living in a harsh and unpredictable environment might require a stronger present-orientation (as opposed to being focused on the future) in order to deal with unpredictable threats and benefit from fleeting rewards.
-Empirical findings seem to point in the same direction.
-Enhanced performance on attention-shifting [@fields_2021; @mittal_2015] and working memory updating [@nweze_2020; @young_2018] have been explained in terms of an ability to track contextual changes, which is thought to help cope with changing information.
+The DDM analysis of the Flanker task was done using an adaptation of the standard DDM that was specifically developed to account for Flanker data: The Shrinking Spotlight model [SSP; @grange_2016; @white_2018a; @white_2018b; @white_2011].
+The standard DDM model assumes a stable drift rate over time within trials (i.e., the rate of information accumulation does not change over time).
+However, on the Flanker Task, reaction time patterns indicate that Flankers exert their strongest effect on performance early on the trial, which then decreases over time.
+This effectively means that the drift rate increases over time, thus violating the basic assumption of the standard DDM [@white_2011].
+The SSP explains this pattern by assuming that attention on the Flanker task works like a spotlight that starts relatively broad, and then gradually narrows down to the central arrow over time.
+Each arrow provides perceptual input *p*.
+If the flanking arrows are congruent, all flankers take a positive value for *p*; if the flanking arrows are incongruent, they take a negative value for *p* while the central arrow takes a positive value.
+The drift rate (*v*) at each time point is the function of the strength of perceptual input *p* multiplied by the amount of attention focused on each arrow.
 
-In the current study, we focus on the Flanker Task
+Attention is operationalized by two additional parameters: the initial width of the attentional spotlight (*SD~a~*) and the shrinking rate of the attentional spotlight (*rd*).
+The attentional spotlight is assumed to be normally distributed over the arrows, with relatively more attention paid to the arrows at the center and relatively less attention paid to the peripheral arrows.
+Over time, this normal distribution (*SD~a~*) narrows down to the central arrow at the rate specified by *rd*, thereby gradually decreasing the interfering noise of the flankers and increasing the signal obtained from the target.
 
-One possibility that has yet to be empirically tested is that such effects are driven by a shared present and/or externally oriented attention mechanism.
-In this pilot study, we leverage the DDM to better understand the processes involved in performance differences, specifically by focusing on basic attention skills.
+Model fit was done using the *flankr* package in R [@grange_2016].
+The SSP model was fit to the data of each individual participant in two steps.
+First, we looped over 50 different sets of starting parameters with a variance of 20 to find the best starting values for each participant.
+This was done to prevent accidentally converging on a suboptimal solution [@grange_2016].
+On this first fitting step, 1000 trials were simulated on each iteration of the fit routine.
+Second, once the optimal set of starting values was found, we fitted the final model using the starting values found in step 1 and simulating 50,000 trials on each iteration.
+
+The model fit for all participants was assessed through QQ-plots comparing the empirical data with the model predictions following @grange_2020.
+Using each participant's best-fitting parameters (based on the final step above), we simulated RTs and accuracy for 50,000 trials of each congruency condition and each Flanker version.
+We calculated the total proportion accuracy and the 25th, 50th, and 75th quantile of the response time distribution (correct trials only) for both the simulated data and the empirical data.
+The outcomes for all participants were plotted against each other.
+The closer the points are to the diagonal line, the better the models fit the participants' data.
+
+For the analyses, we extracted the following parameters: 1) perceptual input (*p*); 2) boundary separation (*A*); 3) initial attention width (*sd~a~*); 4) Attention shrinking rate (*rd*); Interference effect (*sd~a~* / *rd*); 5) non-decision time (*t0*).
+
+### Multiverse analysis
+
+Online experiments come at the trade-off of having less experimental control over the way in which participants complete the experiment and over the environment in which they do so.
+It is largely unclear which factors affect performance and how strong these effects are.
+We used multiverse analysis for all main analysis to assess the robustness of the results against various environmental factors and situations during the experiment.
+We identified seven arbitrary analytic decisions, including or excluding 1) participants who had a recaptcha score below 0.5 (possibly indicating bots); 2) participants who did not rescale their screen at the start of the experiment (see the [procedure section](#procedure)); 3) participants who did not enter fullscreen mode prior to starting the Flanker Task; 4) participants who exited fullscreen mode at any point during the Flanker Task; 5) participants who indicated high levels of noise in their environment (....); indicated extreme interruptions during the experiment (....); 7) trials with RTs > 3.2 SD (within subjects).
+
+For each analysis, we report the median $\beta$, 95% confidence intervals, proportion of *p*-values < .05 across all analytic decisions.
+For the primary analyses, we used a bootstrapping technique to compute overall *p*-values to assess whether the obtained median $\beta$ is significantly larger than zero [@simonsohn_2020].
+
+### Primary analyses
+
+RT~diff~

### 2022-02-14 preregistrations/2_study1/preregistration.Rmd
intermediate update to preregistration

@@
 We applied several exclusion criteria prior to analyzing the data.
-First, we excluded participants who did not complete the full study and those who had incomplete data on any of the attention tasks (*N* = `r #TBD `).
+First, we excluded participants who did not complete the full study and those who did not complete all three Flanker conditions (*N* = `r #TBD `).
 Second, we analyzed responses to the attention checks and reversed coded items in the questionnaire part of the experiment.
@@
 
-In addition, we screened the reaction times on each of the three attention tasks.
+In addition, we screened the reaction times on the Flanker Task.
 For the Drift Diffusion analyses, it is important that each response is generated by a process of active information accumulation (i.e., a diffusion process, as opposed to guessing).
@@
 Participants with more than 10 removed trials were excluded from the analyses (N = `r #TBD `).
-
-The exclusion criteria listed above are our best *a-priori* guesses. However, we expect to develop additional criteria empirically after collecting the data.
+Finally, we logged whether participants exited full-screen mode and/or engaged with other browser tabs (i.e., blur events) at any point during the Flanker Task.
+We excluded participants for whom blur events occurred while a Flanker block was ongoing (but not while reading instructions or taking breaks in between conditions).
+Full-screen exits were included in the [multiverse analysis](#multiverse_plan).
 
@@
 
-Before the first block, participants performed eight practice trials for each condition: First standard, then enhanced, and then degraded.
-During practice, participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
+Prior to each block, participants performed eight practice trials of the current condition.
+During practice, participants received performance feedback after each trial (either "Correct!" printed in green, "Incorrect!" printed in red, or "Too slow!" printed in red if their response latency exceeded 2000 ms).
 After completing the practice trials, participants completed each block with the opportunity to take a break in between.
 At the onset of each block, participants were told what the current condition was.
-No performance feedback was provided during the test blocks.
+No performance feedback of any kind was provided during the test blocks.
 The main performance measures were RTs and accuracy for each condition.
@@
 Participants rated each item on a scale of 1 (not at all) to 4 (very much so).
-An overall state anxiety variable was computed by averaging across the 20 unweighted items (*M* = `r txt_ivs$stai_s_mean$mean`, *SD* = `r txt_ivs$stai_s_mean$sd`, $\alpha$ = `r #TBD `).
+An overall state anxiety variable was computed by averaging across the 20 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
 
@@
 The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
-The items of the NVS were averaged together (*M* = `r txt_ivs$violence_mean$mean`, *SD* = `r txt_ivs$violence_mean$sd`, $\alpha$ = `r #TBD `).
+The items of the NVS were averaged together (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
 Similarly, we averaged the scores on the two fighting items together.
-Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average (*r* = `r txt_cors$vio$r`).
+Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average (*r* = `r #TBD `).
 
@@
 
-We computed four main unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) *unpredictability~perceived~*: containing all items of the perceived unpredictability scale and the QUIC, given their close conceptual overlap (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD` *r* = `r #TBD` between the two scales); 2) *unpredictability~CHAOS~*: containing the items of the CHAOS (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`); 3) *unpredictability~subjective~*: containing all items of the perceived unpredictability scale, the QUIC and the CHAOS (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`); 4) *unpredictability~objective*: containing the items assessing the stability of the family- and social environement, as well as the four objective measures (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`).
+We computed four main unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) *unpredictability~perceived~*: containing all items of the perceived unpredictability scale and the QUIC, given their close conceptual overlap (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD` *r* = `r #TBD` between the two scales); 2) *unpredictability~CHAOS~*: containing the items of the CHAOS (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`); 3) *unpredictability~subjective~*: containing all items of the perceived unpredictability scale, the QUIC and the CHAOS (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`); 4) *unpredictability~objective*: containing the items assessing the stability of the family- and social environment , as well as the four objective measures (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`).
 
-We computed several unweighted unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r txt_ivs$unp_mean$mean`, *SD* = = `txt_ivs$unp_mean$sd`, $\alpha$ = `r #TBD `); 2) an overall QUIC variable by averaging all 37 items (*M* = `r txt_ivs$quic_total_mean$mean`, *SD* = = `r txt_ivs$quic_total_mean$sd`, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r txt_ivs$quic_monitoring_mean$mean`, *SD* = `r txt_ivs$quic_monitoring_mean$sd`, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r txt_ivs$quic_par_predict_mean$mean`, *SD* = `r txt_ivs$quic_par_predict_mean$sd`, $\alpha$ = `r #TBD `; Parental environment: *M* = `r txt_ivs$quic_par_env_mean$mean`, *SD* = `r txt_ivs$quic_par_env_mean$sd`, $\alpha$ = `r #TBD `; Physical environment: *M* = `r txt_ivs$quic_phys_env_mean$mean`, *SD* = `r txt_ivs$quic_phys_env_mean$sd`, $\alpha$ = `r #TBD `; Safety and security: *M* = `r txt_ivs$quic_safety_mean$mean`, *SD* = `r txt_ivs$quic_safety_mean$sd`, $\alpha$ = `r #TBD `).
+We computed several unweighted unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overall QUIC variable by averaging all 37 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
 See also [below](#efa) for details on a factor analysis based on the individual items across scales.
@@
 Scores for the first six items were reverse coded so that higher scores indicated more perceived resource scarcity.
-The items were averaged together to create an unweighted composite scale (*M* = `r txt_ivs$ses_subj_mean$mean`, *SD* = `r txt_ivs$ses_subj_mean$sd`, $\alpha$ = `r #TBD `).
+The items were averaged together to create an unweighted composite scale (*M* = `r  #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
 
@@
 First, participants separately indicated the highest education of their mother and father on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'.
-The mother and father education level were averaged to create an overall unweighted parental education composite (*M* = `r 8-txt_ivs$edu_parents_recoded$mean`, *SD* = `r txt_ivs$edu_parents_recoded$sd`).
+The mother and father education level were averaged to create an overall unweighted parental education composite (*M* = `r  #TBD `, *SD* = `r  #TBD `).
 Participants also indicated their family's household income before age 13 on a 6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'.
@@
 
-## Procedure
+## Procedure {#procedure}
 
-## Data analysis
+The experiment was completed on the participants' own laptop or desktop computer and consisted of five parts (in fixed order): consent, Flanker Task, questionnaire battery, brief demographics form, and final checks including the opportunity to give feedback on the experiment.
+Participants were allowed to refrain from answering any of the questionnaire items, but were prompted with a warning once when moving to the next page if one of the items was not answered (which they could ignore).
 
-### DDM estimation
+After providing consent, participants started with the Flanker Task.
+They were asked to complete the Flanker Task in a quiet room in the house where they would be least likely to be distracted by other people or outside noises.
+The order of the tasks was counterbalanced between subjects.
+At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs.
+The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deLeeuw_2015].
+Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the creditcard.
+The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants.
+After successfully resizing the screen, participants completed all three tasks.
+During the task, the cursor was hidden from the screen to minimize distractions.
+Code for the three tasks can be found on [Github](https://github.com/StefanVermeent/attention_project/tree/main/tasks).
+
+After completing the attention tasks, participants completed the questionnaire battery in the following fixed order: 1) Current state (state anxiety and separate questions relating to specific states); 2) Childhood adversity (perceived unpredictability, perceived socio-economic status, exposure to violence and physical fights, household chaos); 3) Temporal orientation (impulsivity, future orientation); 4) Depressive symptoms.
+
+Finally, the demographics questions asked about the participant's age, weight, height, physical activity, sex at birth, gender, ethnicity, social class (current and during childhood), education level (one's own as well as parents' education level), occupation, and household income (current and during childhood).
+At the end of the experiment, we asked participants if they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.
+
+The full experiment was expected to take approximately 35 minutes. Participants were paid £4.38 upon completing the full experiment.
+
+## Data analysis {#analysis_plan}
+
+### DDM estimation {#ddm_plan}
 
@@
 On this first fitting step, 1000 trials were simulated on each iteration of the fit routine.
-Second, once the optimal set of starting values was found, we fitted the final model using the starting values found in step 1 and simulating 50,000 trials on each iteration.
+Second, once the optimal set of starting values was found, we fitted the final model using the best starting values found in step 1 and simulating 50,000 trials on each iteration.
 
@@
 
-### Multiverse analysis
+### Multiverse analysis {#multiverse_plan}
 
@@
 
-### Primary analyses
+### Primary analyses {#primary_plan}
 

### 2022-02-18 preregistrations/2_study1/preregistration.Rmd
changed stimulus dimensions of enhanced flankers to be 50% wider than std condition

@@
 )
+
+load(here("data", "2_study1", "0_self_report_raw.Rdata"))
 ```
 
-[INTRODUCTION]
-
-There is ample research to suggest that experiencing adversity early in life has a profound effect on the way in which people attend to information.
-Generally, the patterns point to an attention deficit, such that adversity-exposed people take longer to point their attention towards relevant information and are more susceptible to the influence of distracting or otherwise irrelevant information [@schibli_2017].
-Attention-deficit/hyperactivity disorder (ADHD).
-However, instead of pointing to a general attention deficit, differences in performance on tasks requiring attention control might reflect different attentional strategies that developed to navigate dangerous and unpredictable environments [e.g., increased vigilance; @frankenhuis_2016].
-Understanding the attention skills of people from adversity is important because attention control has been identified as one of the key mechanisms underlying performance on higher-level executive processes [@draheim_2021].
-
-Hidden talents research makes the often implicit assumption that enhanced abilities might reflect an enhanced focus on the here-and-now [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013].
-For example, @frankenhuis_2016 argued that living in a harsh and unpredictable environment might require a stronger present-orientation (as opposed to being focused on the future) in order to deal with unpredictable threats and benefit from fleeting rewards.
-In line with this, we initially expected people from adversity to perform better on cognitive tasks that require a broad attention scope in order to successfully detect peripheral and subtly changing information, and to perform worse on tasks requiring ignoring interfering information (see the [preregistration](https://github.com/StefanVermeent/attention_project/blob/Preregistration/preregistrations/1_pilot/preregistration.docx) of the first pilot study).
+In line with previous theorizing [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013], we initially expected people from adversity to perform better on cognitive tasks that require a broad attention scope in order to successfully detect peripheral and subtly changing information, and to perform worse on tasks requiring ignoring interfering information (see the [preregistration](https://github.com/StefanVermeent/attention_project/blob/Preregistration/preregistrations/1_pilot/preregistration.docx) of the first pilot study).
 However, the data pointed in the opposite direction.
@@
 At the same time, they were faster to narrow down their attention to the central target on the Flanker Task, thereby effectively limiting the amount of flanker interference that they were exposed to.
+
+The findings in the pilot study suggest that deficit patterns that are typically found on tasks like the Flanker might not reflect problems in attention control and inhibition, even suggesting the opposite.
+Instead, people from adversity might process information more slowly, leading to longer reaction times.
 The goal of the current study is to replicate the attention findings on the Flanker Task, and to better understand the apparent information processing deficits.
+Participants completed three versions of the Flanker Task: the standard version, a version with enhanced visual information, and a version with degraded visual information.
 
-In the current study, we focus on the Flanker Task
+Figure 1 shows two possible data patterns that we might expect across the different versions at different levels of violence exposure.
+First, if the findings reflect a general information processing deficit, we would expect performance to be lower for people with more violence exposure across all versions of the task.
+Alternatively, lower performance on the standard version might reflect an adaptive trade-off towards more robust cognitive functioning, even in the face of noise or perturbations [@giudice_2018].
+In that case, we would expect more stable performance for people with more violence exposure.
+As a result, they might not benefit as much from enhanced visual information, but at the same time might be able to better maintain performance when presented with degraded information.
 
-One possibility that has yet to be empirically tested is that such effects are driven by a shared present and/or externally oriented attention mechanism.
-In this pilot study, we leverage the DDM to better understand the processes involved in performance differences, specifically by focusing on basic attention skills.
+```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap="Overview of the three cognitive tasks."}
+knitr::include_graphics("figure1.png", error = F)
+```
+
+## Primary aims
+
+1. Investigate the robustness of the primary DDM findings in the pilot study by pooling the pilot data and the data of the standard condition in the current study. 
+2.
+Extent the findings of the pilot study by investigating how Flanker performance changes across conditions as a function of violence exposure.
+We expect that the manipulations primarily have an effect on perceptual input *p*, thereby also affecting overall reaction times.
+
+# Secondary aims
+
+1.
+Investigate the extent to which the [factor structure](#efa) of the unpredictability measures corresponds to the one found in the pilot study.
+Secondly, investigate how different dimensions of unpredictability relate to Flanker performance.
+2) Explore the role of state anxiety, hunger, and sleep deprivation as potential moderators of the relationship between adversity and attention performance.
+Anxiety might enhance attention performance by making participants more vigilant.
+Conversely, hunger and sleep deprivation could have a negative effect on performance.
+3) Explore bivariate correlations between measures of adversity, attention, and measures of temporal orientation (i.e., impulsivity and future orientation).
+4) Explore the correlation between current depressive symptoms and retrospective measures of adversity, which might reflect a negativity bias in recalling past events driven by current depressive symptoms [@nivison_2021].
 
@@
 Participants were eligible for the study if they were from the United States and if they spoke fluent English.
+Finally, we used the MacArthur's ladder for perceived social-economic status (SES) as used in Prolific's pre-screening battery to ensure that 50% of the sample perceived their current SES to be low (a score of 4 or below).
 
 We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the optimal number of participants to include (more information including all simulation code on [Github](https://github.com/StefanVermeent/attention_project/tree/preregistration1/preregistrations/1_pilot/scripts)).
-We ran simulations for two scenarios: A linear regression model to test the effect of adversity (standardized) on attention performance (standardized) and a mixed regression model to test the adversity (standardized) X task condition (sum-coded) interaction, including a random intercept for subjects.
-We ran simulations for a standardized $\beta$ of 0.10 and 0.15.
-In addition, we simulated the power to detect these effects with imperfectly recovered DDM parameters, assuming a recovery accuracy (i.e., correlation between data-generating parameter value and actually recovered parameter value) of *r* = 0.85 (see the [Github link](https://github.com/StefanVermeent/attention_project/tree/preregistration1/preregistrations/1_pilot/scripts) for more information).
-
-In determining the final sample size, we weighed the simulation results together our uncertainty about certain model parameters (mostly the fixed effects and sigma term for the mixed model) and the fact that this was a first, mostly exploratory pilot study.
-For the mixed model, we found that power was > .80 for the adversity X task condition interaction with *N* = 450 or more.
-For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require *N* = `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`.
-When DDM parameter recovery accuracy was *r* = .85, power was `r (power_linear %>% filter(n_subjects == 500, fixed_effect == 0.15, effect == "linear_recov_main_power") %>% pull(power))/100` for *N* = 500 and $\beta$ = 0.15.
-Power was `r (power_linear %>% filter(n_subjects == 500, fixed_effect == 0.1, effect == "linear_recov_main_power") %>% pull(power))/100` under the same scenario when $\beta$ was 0.10.
-Ultimately, we decided on sampling 550 participants with an anticipated final sample size of around 500.
 
@@
 
-The Flanker Task was programmed in JsPsych version 3.6.1 [@deLeeuw_2015].
+Based on participant feedback in the pilot study, we changed (the wording of) a number of questionnaire items in order to make them more inclusive.
+We added an item asking about the participant's family composition.
+In addition, all mentions of 'parent(s)' across questionnaires were changed to 'caregiver(s)' (e.g., "At least one of my caregivers had punishments that were unpredictable").
+We also added a question asking about the exact family composition.
 
@@
 
+The Flanker Task was programmed in JsPsych version 3.6.1 [@deLeeuw_2015].
 We programmed three conditions of the Flanker Task (See Figure \@ref(fig:figure1).
@@
 In the 'enhanced' condition, the aim was to increase the quality of visual information provided by the arrows.
-To this end, we increased the arrow size by 50% to 60 pixels (0.6 inches), and increased padding between the arrows to 20 pixels.
+To this end, we increased the arrow size by 12.5% to 45 pixels (0.45 inches), and increased padding between the arrows to 5 pixels.
+This increased the width of the Flanker display by 50% with respect to the standard display.
 In the 'degraded' condition, the aim was to decrease the quality of visual information provided by the arrows.
@@
 Therefore, they provided more noisy information about their horizontal direction.
+We had no strong *a priori* expectations about how performance of adversity-exposed people might be affected by specific types of stimulus degradation (e.g., arrow rotation, decreasing stimulus contrast).
 
@@
 The main performance measures were RTs and accuracy for each condition.
-
-```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap="Overview of the three cognitive tasks."}
-knitr::include_graphics("figure1.png", error = F)
-```
 
@@
 This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
-We treated household chaos
 
@@
 Finally, we included four objective measures of unpredictability before age 13.
-Participants provided answers to the following items in an open response format: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "How many romantic partners did your mother have (not counting your father)?"; 4) "How many romantic partners did your father have (not counting your mother)?".
+Participants provided answers to the following items in an open response format: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "Think about the caregiver who had the most romantic partners before you were age 13.
+How many romantic partners did this person have?".
 
-We computed four main unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) *unpredictability~perceived~*: containing all items of the perceived unpredictability scale and the QUIC, given their close conceptual overlap (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD` *r* = `r #TBD` between the two scales); 2) *unpredictability~CHAOS~*: containing the items of the CHAOS (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`); 3) *unpredictability~subjective~*: containing all items of the perceived unpredictability scale, the QUIC and the CHAOS (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`); 4) *unpredictability~objective*: containing the items assessing the stability of the family- and social environment , as well as the four objective measures (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`).
+We computed four main unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) *unpredictability~perceived~*: containing all items of the perceived unpredictability scale and the QUIC, given their close conceptual overlap (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD` *r* = `r #TBD` between the two scales); 2) *unpredictability~CHAOS~*: containing the items of the CHAOS (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`); 3) *unpredictability~subjective~*: containing all items of the perceived unpredictability scale, the QUIC and the CHAOS (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`); 4) *unpredictability~objective*: containing the items assessing the stability of the family- and social environment , as well as the three objective measures (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`).
 
@@
 In addition, we measured several indicators of objective SES before age 13.
-First, participants separately indicated the highest education of their mother and father on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'.
-The mother and father education level were averaged to create an overall unweighted parental education composite (*M* = `r  #TBD `, *SD* = `r  #TBD `).
+First, participants separately indicated the highest education of their two primary caregivers (if applicable) on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'.
+The caregivers' education level were averaged to create an overall unweighted parental education composite (*M* = `r  #TBD `, *SD* = `r  #TBD `).
 Participants also indicated their family's household income before age 13 on a 6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'.
@@
 
-We created a composite score of poverty exposure before age 13 by averaging together the standardized scores of perceived level of resource scarcity, overall parental education, and household income.
+We created a composite score of poverty exposure before age 13 by averaging together the standardized scores of perceived level of resource scarcity, overall caregiver education, and household income.
 
@@
 
-The full experiment was expected to take approximately 35 minutes. Participants were paid £4.38 upon completing the full experiment.
+The full experiment was expected to take approximately 30 minutes. Participants were paid £3.75 upon completing the full experiment.
 
@@
 We used multiverse analysis for all main analysis to assess the robustness of the results against various environmental factors and situations during the experiment.
-We identified seven arbitrary analytic decisions, including or excluding 1) participants who had a recaptcha score below 0.5 (possibly indicating bots); 2) participants who did not rescale their screen at the start of the experiment (see the [procedure section](#procedure)); 3) participants who did not enter fullscreen mode prior to starting the Flanker Task; 4) participants who exited fullscreen mode at any point during the Flanker Task; 5) participants who indicated high levels of noise in their environment (....); indicated extreme interruptions during the experiment (....); 7) trials with RTs > 3.2 SD (within subjects).
+We identified seven arbitrary analytic decisions, including or excluding 1) participants who had a recaptcha score below 0.5 (possibly indicating bots); 2) participants who did not rescale their screen at the start of the experiment (see the [procedure section](#procedure)); 3) participants who did not enter fullscreen mode prior to starting the Flanker Task; 4) participants who exited fullscreen mode at any point during the Flanker Task; 5) participants who indicated high levels of noise in their environment; indicated extreme interruptions during the experiment; 7) trials with RTs > 3.2 SD (within subjects).
 
@@
 
-RT~diff~
+First, we pooled the Flanker data of the pilot study and the current study, using the standard condition of the current study.
+For the effect of violence exposure on each of the DDM parameters, we ran initial linear models including violence exposure, study number (pilot study or current study, sum-coded) and their interaction as an independent variable to check whether the two studies were sufficiently similar.
+If the interaction was non-significant, we ran a final model version including only violence exposure to estimate the main effect.
+For the analyses using raw RTs as the dependent variable, these analyses also included congruency as an independent variable, as well as the full three-way interaction.
+Similarly, we estimated a final model without study number if the interaction was non-significant.
+
+Second, we analyzed the effect of violence exposure and Flanker condition type (within the current study only) on Flanker performance using linear mixed effects models with a random intercept per subject.
+The main dependent variables were mean RTs and the SSP parameters: Perceptual input (*p*), boundary separation (*a*), non-decision time (*t0*), initial attention width (*sd~a~*), attention shrinking rate (*rd*) and the interference effect (*SD~a~*/*rd*).
+For each outcome measure, we ran two separate models: One comparing the standard condition with the enhanced condition, and one comparing the standard condition with the degraded condition.
+In both models, condition was dummy-coded using the standard condition as the reference group.
+
+### Factor structure of unpredictability {#efa}
+
+The included unpredictability measures contain items that vary in timescale, ranging from features of the childhood environment that might have been unpredictable on a daily basis (e.g., "things were often chaotic in my house") to sources of unpredictability that typically unfold on a timescale of weeks or months (e.g., "At least one of my parents changed jobs frequently").
+Since attention is involved in information processing on a timescale of seconds to minutes, we expect that attention styles should be more strongly related to sources of unpredictability that unfold on a similar timescale.
+However, it is unclear whether current retrospective measures of unpredictability are able to differentiate between different timescales.
+In addition, it might be the case that items of unpredictability on a longer timescale are good proxies for unpredictability on a a more daily timescale.
+We conducted an exploratory factor analysis (EFA) to address these issues.
+
+EFA was used to find common latent factors underlying the unpredictability/household chaos measures: perceived unpredictability, QUIC, and CHAOS, stability of the family and social environment, and the objective measures of unpredictability.
+The number of factors to retain was based on parallel analysis, with the added requirement that each factor was composed of at least five items that had their strongest loading on that particular factor.
+Factor loadings above 0.32 were considered meaningful (Tabachnick & Fidell, 2014).
+We anticipated the factors to be correlated substantially, and therefore planned to use oblimin rotation.
+
+\pagebreak
+
+# References {#refs}
+
+<div id="refs"></div>
+
+\pagebreak
+
+# Appendix
+
+Go back to [Methods](#state)
+
+```{r supp_table1, tab.id="tableS2", tab.cap.style="Table Caption", tab.cap="Items of the State-Trait Anxiety Inventory (state subscale; STAI-S)"}
+codebook %>%
+  filter(str_detect(Variable, "stai_s(\\d\\d|_\\d\\d)")) %>% 
+  mutate(Item = 1:n()) %>%
+  select(Item, Label) %>%
+  add_column(.after = 1, "empty1" = "") %>%
+  mutate(Label = ifelse(Item %in% c(1,2,5,8,10,11,15,16,19,20), str_c(Label, "*"), Label)) %>%
+  flextable(cwidth = c(0.75, .2, 5)) %>%
+  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
+  add_footer_row(values = " ", colwidths = 3) %>%
+  compose(
+    i = 1, j = 1,
+    as_paragraph(as_i("Note: "), "Reverse scored items."),
+    part = 'footer')
+```
+
+\pagebreak
+
+Go back to [Methods](#violence)
+
+```{r tableS2, tab.id="tableS2", tab.cap.style="Table Caption", tab.cap="Items of the Neighborhood Violence Scale (NVS)"}
+codebook %>%
+  filter(str_detect(Variable, "violence\\d\\d")) %>% 
+  mutate(Item = 1:n()) %>%
+  select(Item, Label) %>%
+  add_column(.after = 1, "empty1" = "") %>%
+  mutate(Label = ifelse(Item %in% c(1,3), str_c(Label, "*"), Label)) %>%
+  flextable(cwidth = c(0.75, .2, 5)) %>%
+  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
+  add_footer_row(values = " ", colwidths = 3) %>%
+  compose(
+    i = 1, j = 1,
+    as_paragraph(as_i("Note: "), "Reverse scored items."),
+    part = 'footer')
+```
+
+\pagebreak
+
+Go back to [Methods](#unpred)
+
+```{r tableS3, tab.id="tableS3", tab.cap.style="Table Caption", tab.cap="Items of the Perceived Childhood Unpredictability scale"}
+codebook %>%
+  filter(str_detect(Variable, "unp\\d\\d")) %>% 
+  mutate(Item = 1:n()) %>%
+  select(Item, Label) %>%
+  add_column(.after = 1, "empty1" = "") %>%
+  flextable(cwidth = c(0.75, .2, 5)) %>%
+  set_header_labels(Item = "Item", empty1 = "", Label = "Description")
+```
+
+\pagebreak
+
+Go back to [Methods](#unpred)
+
+```{r tableS4, tab.id="tableS4", tab.cap.style="Table Caption", tab.cap="Items of the Questionnaire of Unpredictability in Childhood (QUIC)"}
+codebook %>%
+  filter(str_detect(Variable, "quic\\d\\d")) %>% 
+  mutate(Item = 1:n()) %>%
+  select(Item, Label) %>%
+  add_column(.after = 1, "empty1" = "") %>%
+  add_row(.before = 1, "Label" = "Parental monitoring and involvement") %>%
+  add_row(.after = 10, "Label" = "Parental predictability") %>%
+  add_row(.after = 23, "Label" = "Parental environment") %>%
+  add_row(.after = 30, "Label" = "Physical environment") %>%
+  add_row(.after = 38, "Label" = "Safety and security") %>%
+  mutate(Label = ifelse(Item %in% c(1,2,3,4,5,6,7,8,9,11,14,16,22,32), str_c(Label, "*"), Label)) %>%
+  flextable(cwidth = c(0.75, .2, 5)) %>%
+  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
+  merge_h_range(i = c(1,11,24)) %>%
+  bold(i = c(1,11,24, 31, 39)) %>%
+  add_footer_row(values = " ", colwidths = 3) %>%
+  compose(
+    i = 1, j = 1,
+    as_paragraph(as_i("Note: "), "Reverse scored items."),
+    part = 'footer')
+```
+
+\pagebreak
+
+Go back to [Methods](#chaos)
+
+```{r tableS5, tab.id="tableS5", tab.cap.style="Table Caption", tab.cap="Items of the Confusion, Hubbub, and Order Scale (CHAOS)"}
+codebook %>%
+  filter(str_detect(Variable, "chaos\\d\\d")) %>% 
+  mutate(Item = 1:n()) %>%
+  select(Item, Label) %>%
+  add_column(.after = 1, "empty1" = "") %>%
+  mutate(Label = ifelse(Item %in% c(1,2,7,12,14,15), str_c(Label, "*"), Label)) %>%
+  flextable(cwidth = c(0.75, .2, 5)) %>%
+  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
+  add_footer_row(values = " ", colwidths = 3) %>%
+  compose(
+    i = 1, j = 1,
+    as_paragraph(as_i("Note: "), "Reverse scored items."),
+    part = 'footer')
+```
+
+\pagebreak
+
+Go back to [Methods](#ses)
+
+```{r tableS6, tab.id="tableS6", tab.cap.style="Table Caption", tab.cap="Items of the perceived resource scarcity scale"}
+codebook %>%
+  filter(str_detect(Variable, "ses\\d\\d")) %>% 
+  mutate(Item = 1:n()) %>%
+  select(Item, Label) %>%
+  add_column(.after = 1, "empty1" = "") %>%
+  mutate(Label = ifelse(!Item %in% c(7), str_c(Label, "*"), Label)) %>%
+  flextable(cwidth = c(0.75, .2, 5)) %>%
+  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
+  add_footer_row(values = " ", colwidths = 3) %>%
+  compose(
+    i = 1, j = 1,
+    as_paragraph(as_i("Note: "), "Reverse scored items."),
+    part = 'footer')
+```
+
+\pagebreak
+
+Go back to [Methods](#impulsivity)
+
+```{r tableS7, tab.id="tableS7", tab.cap.style="Table Caption", tab.cap="Items of the Barrett Impulsivity Scale (BIS) - motor impulsivity subscale"}
+codebook %>%
+  filter(str_detect(Variable, "impuls\\d\\d")) %>% 
+  mutate(Item = 1:n()) %>%
+  select(Item, Label) %>%
+  add_column(.after = 1, "empty1" = "") %>%
+  flextable(cwidth = c(0.75, .2, 5)) %>%
+  set_header_labels(Item = "Item", empty1 = "", Label = "Description")
+```
+
+\pagebreak
+
+Go back to [Methods](#future_orientation)
+
+```{r tableS8, tab.id="tableS8", tab.cap.style="Table Caption", tab.cap="Items of the Future Orientation Scale (FOS)"}
+codebook %>%
+  filter(str_detect(Variable, "fos\\d\\d")) %>% 
+  slice(match(c("fos01","fos06","fos07","fos12","fos13", "fos02","fos05","fos08","fos11","fos14", "fos03","fos04","fos09","fos10","fos15"), Variable)) %>%
+  mutate(Item = 1:n()) %>%
+  select(Item, Label) %>%
+  add_column(.after = 1, "empty1" = "") %>%
+  add_row(.before = 1, "Label" = "Planning ahead") %>%
+  add_row(.after = 6, "Label" = "Time perspective") %>%
+  add_row(.after = 12, "Label" = "Anticipation of future consequences") %>%
+  mutate(Label = ifelse(Item %in% c(1,2,5,8,9,11,12,15), str_c(Label, "*"), Label)) %>%
+  flextable(cwidth = c(0.75, .2, 5)) %>%
+  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
+  merge_h_range(i = c(1,7,13)) %>%
+  bold(i = c(1,7,13)) %>%
+  add_footer_row(values = " ", colwidths = 3) %>%
+  compose(
+    i = 1, j = 1,
+    as_paragraph(as_i("Note: "), "Reverse scored items."),
+    part = 'footer')
+```
+
+\pagebreak
+
+Go back to [Methods](#depression)
+
+```{r tableS9, tab.id="tableS9", tab.cap.style="Table Caption", tab.cap="Items of the Epidemiologic Studies Depression Scale (CESD)"}
+codebook %>%
+  filter(str_detect(Variable, "depression\\d\\d")) %>% 
+  mutate(Item = 1:n()) %>%
+  select(Item, Label) %>%
+  add_column(.after = 1, "empty1" = "") %>%
+  mutate(Label = ifelse(Item %in% c(4,8,12,16), str_c(Label, "*"), Label)) %>%
+  flextable(cwidth = c(0.75, .2, 5)) %>%
+  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
+  add_footer_row(values = " ", colwidths = 3) %>%
+  compose(
+    i = 1, j = 1,
+    as_paragraph(as_i("Note: "), "Reverse scored items."),
+    part = 'footer')
+```

### 2022-02-18 preregistrations/2_study1/materials/flanker/2_flanker_procedure.js

@@ -75,22 +75,22 @@ var flanker_test_procedure_degraded = {
 var flanker_test_procedure_enhanced = {
   timeline: [flanker_fixation, flanker_present_arrows],
   timeline_variables: [
-{congruency: 'congruent', condition: 'enhanced', location: 'up', correct_response: 'left', stim: set_arrows(angles = [0, 0, 0, 0, 0], loc = 'up', flankers = '&larr;', target = '&larr;', size = 60, padding = 20)},
-{congruency: 'congruent', condition: 'enhanced', location: 'down', correct_response: 'left', stim: set_arrows(angles = [0, 0, 0, 0, 0], loc = 'down', flankers = '&larr;', target = '&larr;', size = 60, padding = 20)},
-{congruency: 'incongruent', condition: 'enhanced', location: 'up', correct_response: 'left', stim: set_arrows(angles = [0, 0, 0, 0, 0], loc = 'up', flankers = '&rarr;', target = '&larr;', size = 60, padding = 20)},
-{congruency: 'incongruent', condition: 'enhanced', location: 'down', correct_response: 'left', stim: set_arrows(angles = [0, 0, 0, 0, 0], loc = 'down', flankers = '&rarr;', target = '&larr;', size = 60, padding = 20)},
-{congruency: 'congruent', condition: 'enhanced', location: 'up', correct_response: 'right', stim: set_arrows(angles = [0, 0, 0, 0, 0], loc = 'up', flankers = '&rarr;', target = '&rarr;', size = 60, padding = 20)},
-{congruency: 'congruent', condition: 'enhanced', location: 'down', correct_response: 'right', stim: set_arrows(angles = [0, 0, 0, 0, 0], loc = 'down', flankers = '&rarr;', target = '&rarr;', size = 60, padding = 20)},
-{congruency: 'incongruent', condition: 'enhanced', location: 'up', correct_response: 'right', stim: set_arrows(angles = [0, 0, 0, 0, 0], loc = 'up', flankers = '&larr;', target = '&rarr;', size = 60, padding = 20)},
-{congruency: 'incongruent', condition: 'enhanced', location: 'down', correct_response: 'right', stim: set_arrows(angles = [0, 0, 0, 0, 0], loc = 'down', flankers = '&larr;', target = '&rarr;', size = 60, padding = 20)},
[…]

### 2022-02-18 preregistrations/2_study1/materials/flanker/global_variables.js

@@ -7,9 +7,12 @@ var resize_screen = {
   type: 'resize',
   item_width: 3 + 3/8,
   item_height: 2 + 1/8,
-  prompt: "<p>For this part of the experiment to work correctly, it is important that we know the resolution of your screen.<br><br>" +
-  "Please pick up a creditcard (or another card of similar size) and hold it up to the screen.<br>" +
-  "Then, click and drag the lower right corner of the box until the box is the same size as the credit card when held up to the screen." +
+  prompt: "<p>Before we start, it is important that you follow the steps below carefully.<br>" +
+  "If you skip these steps, the experiment might not work correctly on your computer.<br><br>" +
+  "1. Pick up a creditcard (or another card of similar size) and hold it against your computer screen.<br>" +
+  "2. Next, click on the lower right corner of the blue box. You can now make it bigger or smaller.<br>" +
+  "3. Change the size of the box until it is <strong> just as big as your creditcard</strong>.<br><br><br>" +
+  "Click 'continue' when you are done" +
   "</p>",
   button_label: ['Continue'],
   pixels_per_unit: 100,

### 2022-02-23 preregistrations/2_study1/preregistration.Rmd
changes to flanker instructions

@@
 However, the data pointed in the opposite direction.
-A Drift Diffusion analysis showed that participants with more violence exposure were slower to process information and orient their attention across all three tasks.
+A Drift Diffusion analysis showed that participants with more violence exposure were generally slower to process information and orient their attention across all three tasks.
 At the same time, they were faster to narrow down their attention to the central target on the Flanker Task, thereby effectively limiting the amount of flanker interference that they were exposed to.
@@
 
-Figure 1 shows two possible data patterns that we might expect across the different versions at different levels of violence exposure.
+Figure \@ref(fig:figure1) shows two possible data patterns that we might expect across the different versions at different levels of violence exposure.
 First, if the findings reflect a general information processing deficit, we would expect performance to be lower for people with more violence exposure across all versions of the task.
@@
 
-```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap="Overview of the three cognitive tasks."}
-knitr::include_graphics("figure1.png", error = F)
+```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap="Overview of the three Flanker conditions and predicted patterns of results under different cognitive mechanisms.
+A: The different Flanker Task conditions.
+The standard version is a typical implementation of the Flanker stimuli.
+The enhanced version improves the quality of information by increasing stimulus size by 12.5% and including padding (5 pixels) between the arrows.
+The degraded cognition reduces the quality of information by rotating all arrows at a 45° angle.
+B: Two potential patterns of the effect of condition on people’s perceptual input as a function of violence exposure.
+Left plot: Under the deficit model, we would expect people with more violence exposure to perform worse across all three conditions.
+Right plot: If performance is traded off against higher robustness of the cognitive system for people with more violence exposure (Del Giudice & Crespi, 2018), we would expect cognitive performance in this group to be relatively stable across conditions, perhaps even outperforming people with less violence exposure in the degraded condition."}
+knitr::include_graphics("Fig1.png", error = F)
 ```
 
-## Primary aims
+## Primary aims {#primary}
 
@@
 
-# Secondary aims
+# Secondary  {#secondary}
 
@@
 We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the optimal number of participants to include (more information including all simulation code on [Github](https://github.com/StefanVermeent/attention_project/tree/preregistration1/preregistrations/1_pilot/scripts)).
+Assuming an effect size of $\beta$ = 0.1 and a DDM parameter recovery accuracy of *r* = .85, we estimated that we would need 500 participants to achieve at least 80% power.
+We sampled a total of 550 participants to account for necessary exclusions (based on our experiences in the pilot study).
 
@@
 We excluded participants if they missed both attention check items or if they had suspicious response patterns (e.g., consistently endorsing high response options even when some items were reverse coded) (*N* = `r #TBD `).
+Third, we excluded participants whose screen height was < 700 pixels, or whose screen height was bigger than their screen width (suggesting that they did not complete the experiment on a laptop or desktop pc).
+Finally, we screened participants' accuracy on the Flanker task within each condition.
+Using a binomial distribution, we calculated that if a participant would be purely guessing on each trial, they would have a probability of 97.5% of obtaining an overall accuracy of 59.4%.
+Therefore, we excluded participant's data on a particular condition if their accuracy on that condition was below 60%.
 
@@
 In addition, all mentions of 'parent(s)' across questionnaires were changed to 'caregiver(s)' (e.g., "At least one of my caregivers had punishments that were unpredictable").
-We also added a question asking about the exact family composition.
+We also added a question asking about the participant's exact family composition.
 
@@
 
-After completing the attention tasks, participants completed the questionnaire battery in the following fixed order: 1) Current state (state anxiety and separate questions relating to specific states); 2) Childhood adversity (perceived unpredictability, perceived socio-economic status, exposure to violence and physical fights, household chaos); 3) Temporal orientation (impulsivity, future orientation); 4) Depressive symptoms.
+After completing the Flanker task, participants completed the questionnaire battery in the following fixed order: 1) Current state (state anxiety and separate questions relating to specific states); 2) Childhood adversity (perceived unpredictability, perceived socio-economic status, exposure to violence and physical fights, household chaos); 3) Temporal orientation (impulsivity, future orientation); 4) Depressive symptoms.
 
-Finally, the demographics questions asked about the participant's age, weight, height, physical activity, sex at birth, gender, ethnicity, social class (current and during childhood), education level (one's own as well as parents' education level), occupation, and household income (current and during childhood).
+Finally, the demographics questions asked about the participant's age, weight, height, physical activity, sex at birth, gender, ethnicity, social class (current and during childhood), education level (one's own as well as caregivers' education level), occupation, and household income (current and during childhood).
 At the end of the experiment, we asked participants if they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.
@@
 
-First, we pooled the Flanker data of the pilot study and the current study, using the standard condition of the current study.
-For the effect of violence exposure on each of the DDM parameters, we ran initial linear models including violence exposure, study number (pilot study or current study, sum-coded) and their interaction as an independent variable to check whether the two studies were sufficiently similar.
+To address the [first primary aim](#primary) we pooled the Flanker data of the pilot study and the current study, using the standard condition of the current study.
+For the pooled effect of violence exposure on each of the DDM parameters, we ran initial linear models including violence exposure, study number (pilot study vs.
+current study, sum-coded) and their interaction as an independent variable to check whether the two studies were sufficiently similar.
 If the interaction was non-significant, we ran a final model version including only violence exposure to estimate the main effect.
-For the analyses using raw RTs as the dependent variable, these analyses also included congruency as an independent variable, as well as the full three-way interaction.
-Similarly, we estimated a final model without study number if the interaction was non-significant.
+The pooled effect of violence exposure on raw RTs was assessed through linear mixed models including a random intercept per participant.
+Initial models included violence exposure, congruency (congruent vs.
+incongruent, sum-coded as -1 and 1), the violence exposure X congruency interaction, study number (pilot study vs current study, sum-coded), and the violence_exposure X study number interaction.
+We estimated a final model without study number if the violence exposure X study number interaction was non-significant.
 
-Second, we analyzed the effect of violence exposure and Flanker condition type (within the current study only) on Flanker performance using linear mixed effects models with a random intercept per subject.
+To address the [second primary aim](#primary), we analyzed the effect of violence exposure and Flanker condition type (within the current study only) on Flanker performance using linear mixed effects models with a random intercept per participant.
 The main dependent variables were mean RTs and the SSP parameters: Perceptual input (*p*), boundary separation (*a*), non-decision time (*t0*), initial attention width (*sd~a~*), attention shrinking rate (*rd*) and the interference effect (*SD~a~*/*rd*).

### 2022-02-23 preregistrations/2_study1/materials/flanker/1_flanker_instructions.js

@@ -62,39 +62,39 @@ var flanker_instructions = {
      "<div class='grid-item'>" +
      "<div style = 'display: inline-grid; width: 200px; height: 80px; font-size: 40px; grid: 70px / auto auto auto auto auto;'>" +
      "<div style = 'margin: auto; padding: 0px 0px;'>" +
-     "<div style = 'margin: auto; padding: 0px 0px; transform: rotate(0deg);'><span>&larr;</span></div>" +
-     "</div>" +
-     "<div style = 'margin: auto; padding: 0px 0px;'>" +
-     "<div style = 'margin: auto; padding: 0px 0px; transform: rotate(0deg);'><span>&larr;</span></div>" +
+     "<div style = 'margin: auto; padding: 0px 0px; transform: rotate(0deg);'><span>&rarr;</span></div>" +
      "</div>" +
      "<div style = 'margin: auto; padding: 0px 0px;'>" +
      "<div style = 'margin: auto; padding: 0px 0px; transform: rotate(0deg);'><span>&rarr;</span></div>" +
      "</div>" +
      "<div style = 'margin: auto; padding: 0px 0px;'>" +
-     "<div style = 'margin: auto; padding: 0px 0px; transform: rotate(0deg);'><span>&larr;</span></div>" +
+     "<div style = 'margin: auto; padding: 0px 0px; transform: rotate(0deg);'><span>&rarr;</span></div>" +
      "</div>" +
      "<div style = 'margin: auto; padding: 0px 0px;'>" +
-     "<div style = 'margin: auto; padding: 0px 0px; transform: rotate(0deg);'><span>&larr;</span></div>" +
+     "<div style = 'margin: auto; padding: 0px 0px; transform: rotate(0deg);'><span>&rarr;</span></div>" +
+     "</div>" +
+     "<div style = 'margin: auto; padding: 0px 0px;'>" +
+     "<div style = 'margin: auto; padding: 0px 0px; transform: rotate(0deg);'><span>&rarr;</span></div>" +
      "</div>" +
      "</div></div> " +
    
      "<div class='grid-item'><strong>VERSION 2</strong></div>  " +
      "<div class='grid-item'>" +
-     "<div style = 'display: inline-grid; width: 500px; font-size: 60px; grid: 70px / auto auto auto auto auto;'>" +
+     "<div style = 'display: inline-grid; width: 280px; font-size: 45px; grid: 70px / auto auto auto auto auto;'>" +
[…]

### 2022-02-23 preregistrations/1_pilot/preregistration.Rmd
intermediate update to prereg study1

@@
 
+load(here("preregistrations", "1_pilot", "staged_objects.Rmd"))
 ```
@@
 Participants rated each item on a scale of 1 (not at all) to 4 (very much so).
-An overall state anxiety variable was computed by averaging across the 20 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+An overall state anxiety variable was computed by averaging across the 20 unweighted items (*M* = `r txt_ivs$stai_s_mean$mean`, *SD* = `r txt_ivs$stai_s_mean$sd`, $\alpha$ = `r #TBD `).
 
@@
 The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
-The items of the NVS were averaged together (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+The items of the NVS were averaged together (*M* = `r txt_ivs$violence_mean$mean`, *SD* = `r txt_ivs$violence_mean$sd`, $\alpha$ = `r #TBD `).
 Similarly, we averaged the scores on the two fighting items together.
-Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average (*r* = `r #TBD `).
+Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average (*r* = `r txt_cors$vio$r`).
 
@@
 
-We computed several unweighted unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overall QUIC variable by averaging all 37 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `).
+We computed several unweighted unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r txt_ivs$unp_mean$mean`, *SD* = = `txt_ivs$unp_mean$sd`, $\alpha$ = `r #TBD `); 2) an overall QUIC variable by averaging all 37 items (*M* = `r txt_ivs$quic_total_mean$mean`, *SD* = = `r txt_ivs$quic_total_mean$sd`, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r txt_ivs$quic_monitoring_mean$mean`, *SD* = `r txt_ivs$quic_monitoring_mean$sd`, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r txt_ivs$quic_par_predict_mean$mean`, *SD* = `r txt_ivs$quic_par_predict_mean$sd`, $\alpha$ = `r #TBD `; Parental environment: *M* = `r txt_ivs$quic_par_env_mean$mean`, *SD* = `r txt_ivs$quic_par_env_mean$sd`, $\alpha$ = `r #TBD `; Physical environment: *M* = `r txt_ivs$quic_phys_env_mean$mean`, *SD* = `r txt_ivs$quic_phys_env_mean$sd`, $\alpha$ = `r #TBD `; Safety and security: *M* = `r txt_ivs$quic_safety_mean$mean`, *SD* = `r txt_ivs$quic_safety_mean$sd`, $\alpha$ = `r #TBD `).
 See also [below](#efa) for details on a factor analysis based on the individual items across scales.
 
-One additional scales measured the stability of the family and social environment.
+One additional scale measured the stability of the family and social environment.
 On a scale of 1 (the same all the time) to 5 (constant and rapid changes), participants indicated how often the following aspects of their family and social environment changed before age 13: 1) economic status, 2) family environment, 3) childhood neighborhood environment, and 4) childhood school environment.
@@
 This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
-An overall household chaos variable was computed by averaging the 15 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+An overall household chaos variable was computed by averaging the 15 unweighted items (*M* = `r txt_ivs$chaos_mean$mean`, *SD* = `r txt_ivs$chaos_mean$sd`, $\alpha$ = `r #TBD `).
 
@@
 Scores for the first six items were reverse coded so that higher scores indicated more perceived resource scarcity.
-The items were averaged together to create an unweighted composite scale (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+The items were averaged together to create an unweighted composite scale (*M* = `r txt_ivs$ses_subj_mean$mean`, *SD* = `r txt_ivs$ses_subj_mean$sd`, $\alpha$ = `r #TBD `).
 
@@
 First, participants separately indicated the highest education of their mother and father on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'.
-The mother and father education level were averaged to create an overall unweighted parental education composite (*M* = `r #TBD `, *SD* = `r #TBD `).
+The mother and father education level were averaged to create an overall unweighted parental education composite (*M* = `r 8-txt_ivs$edu_parents_recoded$mean`, *SD* = `r txt_ivs$edu_parents_recoded$sd`).
 Participants also indicated their family's household income before age 13 on a 6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'.
@@
 We anticipated the factors to be correlated substantially, and therefore planned to use oblimin rotation.
+
+\pagebreak
+
+# Deviations from preregistration
+
+- Creation of poverty composite
+
+# Results
+
+## Exclusions
+
+## Primary analyses
+
+### Change Detection
+Violence exposure did not have an effect on the speed of change detection (see Figure 1).
+However, participants with high violence exposure were less accurate ($\beta$~median~  = `r #TBD`, `r #TBD`% of *p*s < .05).
+
+we found a negative main effect of violence exposure on the drift rate ($\beta$~median~  = `r #TBD`, `r #TBD`% of *p*s < .05), indicating that participants with more violence exposure showed slower information processing.
+
+### Attention Cueing Task
+We did not find a significant interaction effect between violence exposure and condition on raw Attention Cueing performance (see Figure 2.
+There was a significant main effect of violence exposure (($\beta$~median~  = `r #TBD`) under `r #TBD`% and `r #TBD`% of analytic decisions on raw RTs and log-transformed RTs, respectively (not shown in this figure), indicating that participants with high violence exposure generally performed slower on the task.
+
+The DDM analysis uncovered a significant interaction effect between violence exposure and task condition on the drift rate ($\beta$~median~  = `r #TBD`, `r #TBD`% of *p*s < .05).
+Simple slopes analysis suggested that on cued trials, high violence exposure participants tended to have a lower drift rate than low violence exposure participants (`r #TBD`% ps < .05).
+This difference disappeared on neutral trials, with both groups showing comparable drift rates (0% ps < .05) (See Table 2).
+
+We did not find significant interaction effects for boundary separation and non-decision time, although we did find significant main effects of violence exposure on boundary separation ($\beta$~median~  = `r #TBD`, `r #TBD`% of *p*s < .05) and non-decision time ($\beta$~median~  = `r #TBD`, `r #TBD`% of *p*s < .05), suggesting that participants with more violence exposure had more conservative decision boundaries and were slower to start the decision-making process (possibly reflecting slower eye-movements towards the targets).
+
+### Flanker Task
+We found a significant interaction effect between violence exposure and task condition on raw Flanker performance in `r #TBD`% and `r #TBD`% of analytic decisions for raw RTs and log-transformed RTs, respectively (see Figure 3).
+Simple slopes analyses showed that under `r #TBD`% of analytic decisions, participants with more violence exposure were slightly slower on congruent trials.
+This difference disappeared across all analytic decisions on incongruent trials.
+
+The DDM analyses showed a combination of parameter differences that suggest a compensatory mechanism in people with more violence exposure.
+First, people with more violence exposure extracted lower-quality perceptual information (p) from the flankers ($\beta$~median~  = `r #TBD`, `r #TBD`% of *p*s < .05), which is analogous to the lower drift rates on the other tasks.
+Thus, they needed more time to gather enough information to reach the decision boundary.
+Second, the initial width of the attention spotlight (sda) did not differ across levels of violence exposure, which is not in line with our expectations of a broader, more diffuse attention style in people from adversity.
+Third, people with more violence exposure had a higher shrinking rate rd ($\beta$~median~  = `r #TBD`, `r #TBD`% of *p*s < .05), meaning that they were faster at narrowing down their attention towards the central arrow (thereby decreasing flanker interference quicker, as shown by the sda/rd ratio).
+Judging from the interaction effect on raw RTs, this higher shrinking rate seems to offset the negative effect of lower perceptual input on incongruent trials.
+Thus, contrary to expectations, participants with more violence exposure seem to experience less interference from the flanker arrows.
+
+## Secondary analyses
+
+### Factor structure of unpredictability items
+
+We conducted an EFA including all items measuring unpredictability: 1) The QUIC items, 2) the perceived unpredictability items, 3) the CHAOS items, 4) the items measuring environmental change, 5) number of partners of the father and mother, 6) Number of residential changes, 7) household size.
+
+The measures of residential changes and number of different partners of both parents were heavily positively skewed.
+
+Two participants indicated 50 different partners for either their mother or father.
+This number corresponded with other items focusing on the family situation, such as on the QUIC ("At least one of my parents had many romantic partners") and changes in the family environment.
+Therefore, we saw no reason to exclude these responses.
+We binned the responses for these three variables to get rid of the skew.
+For number of residential changes, responses were recoded into 7 bins: 0 (0 times), 1 (1-2 times), 2 (3-4 times), 3 (5-6 times), 4 (7-8 times), 5 (9-10 times), and 6 (10 or more times).
+For the number of partners of both parents, responses were recoded into ..
+bins: 0 (0 partners), 1 (1 partner), 2 (2 partners), 3 (3 partners), 4 (4 partners), 5 (5 partners), and 6 (6 or more partners).
 

### 2022-03-18 preregistrations/2_study1/preregistration.Rmd
preregistration for study 1

@@
 
-In line with previous theorizing [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013], we initially expected people from adversity to perform better on cognitive tasks that require a broad attention scope in order to successfully detect peripheral and subtly changing information, and to perform worse on tasks requiring ignoring interfering information (see the [preregistration](https://github.com/StefanVermeent/attention_project/blob/Preregistration/preregistrations/1_pilot/preregistration.docx) of the first pilot study).
-However, the data pointed in the opposite direction.
-A Drift Diffusion analysis showed that participants with more violence exposure were generally slower to process information and orient their attention across all three tasks.
-At the same time, they were faster to narrow down their attention to the central target on the Flanker Task, thereby effectively limiting the amount of flanker interference that they were exposed to.
+In line with previous thinking (e.g., Ellis et al., 2020; Frankenhuis et al., 2016; Frankenhuis & Weerth, 2013), we initially expected people from adversity to perform better on cognitive tasks that require a broad attention scope.
+A broad attention scope might facilitate vigilance and the detection of subtle changes or peripheral information.
+However, this might come at a cost, especially for tasks that involve interference.
+To test these ideas, we ran a pilot study with a Cued Attention, Changed Detection, and Flanker Task (interference) and measured adversity exposure.
+We expected adversity-exposure would improve performance on the Cued-Attention and Change Detection tasks but hurt performance on the Flanker Task (see the preregistration of the first pilot study).
 
-The findings in the pilot study suggest that deficit patterns that are typically found on tasks like the Flanker might not reflect problems in attention control and inhibition, even suggesting the opposite.
-Instead, people from adversity might process information more slowly, leading to longer reaction times.
+In contrast to expectations, our pilot data did not find evidence for a broad adversity-related attention scope.
+In fact, our Drift Diffusion analyses showed that participants with more violence exposure were generally slower to process information – as shown by the drift rate parameters of the Cued Attention and Change Detection Task and the perceptual input parameter of the Flanker Task - and orient their attention – As shown by the non-decision time parameter - across all three tasks.
+However, on the Flanker Task — where we expected lowered performance — our analyses revealed that people exposed to violence were faster to narrow their attention to the task-relevant information.
+In other words, instead of maintaining a broad scope of attention, people exposed to violence were able to quickly focus their attention, as shown by the attention shrinking parameter.
+
+These findings are interesting for two reasons.
+First, the Flanker is a widely used task and people exposed to adversity typically show lowered performance.
+However, using the DDM to break performance into components, our pilot data suggest that lowered performance may not be caused by problems with attention control or inhibition.
+Instead, people exposed to adversity might simply extract perceptual information from the stimuli more slowly (as indicated by the perceptual input (p) parameter).
+This effectively lowers the quality of information that people can use to guide their decision, which will be reflected in lower reaction times.
+Second, these initial findings suggest that performance might be improved through different types of interventions focused on different cognitive mechanisms.
+Specifically, people with more adversity exposure might benefit from manipulations that increase the visual quality of stimuli.
+
 The goal of the current study is to replicate the attention findings on the Flanker Task, and to better understand the apparent information processing deficits.
@@
 
-# Secondary  {#secondary}
+# Secondary aims  {#secondary}
 
@@
 
-The Flanker Task was programmed in JsPsych version 3.6.1 [@deLeeuw_2015].
+The Flanker Task was programmed in JsPsych version 6.3.1 [@deLeeuw_2015].
 We programmed three conditions of the Flanker Task (See Figure \@ref(fig:figure1).
@@
 On a scale of 1 (the same all the time) to 5 (constant and rapid changes), participants indicated how often the following aspects of their family and social environment changed before age 13: 1) economic status, 2) family environment, 3) childhood neighborhood environment, and 4) childhood school environment.
-Finally, we included four objective measures of unpredictability before age 13.
+Finally, we included several objective proxy measures of unpredictability before age 13: 1) "How often did you move", 2) "Before age 13, did any other adults besides your caregivers live in your primary residence?".
+If the participant answered "yes" to this question, two additional questions asked about the number of different adult women (men) that lived in their primary residence for a period of time besides their primary caregiver.
+3) If the participant indicated more adults living in the household besides their primary caregiver, this was followed up by items asking how many of these individuals were romantically involved with their caregiver.
+
+four objective measures of unpredictability before age 13.
 Participants provided answers to the following items in an open response format: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "Think about the caregiver who had the most romantic partners before you were age 13.
@@
 
-We computed four main unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) *unpredictability~perceived~*: containing all items of the perceived unpredictability scale and the QUIC, given their close conceptual overlap (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD` *r* = `r #TBD` between the two scales); 2) *unpredictability~CHAOS~*: containing the items of the CHAOS (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`); 3) *unpredictability~subjective~*: containing all items of the perceived unpredictability scale, the QUIC and the CHAOS (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`); 4) *unpredictability~objective*: containing the items assessing the stability of the family- and social environment , as well as the three objective measures (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`).
+We computed four main unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) *unpredictability~perceived~*: containing all items of the perceived unpredictability scale and the QUIC, given their close conceptual overlap (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD` *r* = `r #TBD` between the two scales); 2) *unpredictability~CHAOS~*: containing the items of the CHAOS (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`); 3) *unpredictability~subjective~*: containing all items of the perceived unpredictability scale, the QUIC and the CHAOS (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`); 4) *unpredictability~objective*: containing the items assessing the stability of the family- and social environment, as well as the three objective measures (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`).
 

### 2022-03-23 preregistrations/2_study1/preregistration.Rmd
Amendment to Preregistration of Study 1

@@
 The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deLeeuw_2015].
-Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the creditcard.
+Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen (initial size 300 pixels) until it matched the size of the creditcard.
 The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants.
@@
 We estimated a final model without study number if the violence exposure X study number interaction was non-significant.
+
+**Amendment to preregistration prior to data analysis:** In the current study, we made a change to the screen rescaling procedure using a credit card.
+Specifically, we changed to initial size of the resize box from 100px to 300px.
+This way, the stimulus display would still be reasonably close to the intended size if participants did not engage in any resizing.
+However, this led to a change between the pilot study and the current study, which is particularly important for the pooled analysis as rescaling (yes or no) was included as an arbitrary exclusion decision in the multiverse analyses.
+To solve this issue, we decided to include this decision with four combinations: 1) exclude non-scalers in both studies; 2) include non-scalers in both studies; 3) exclude non-scalers in pilot study, include non-scalers in study 1; 4) include non-scalers in pilot study, exclude non-scalers in study 1.
 

### 2022-10-15 preregistrations/1_pilot/scripts/0_data_prep/7_HDDM_refit.Rmd
update to various scripts

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(reticulate)

use_condaenv("py37")
hddm <- reticulate::import("hddm")
reticulate::import("pandas", as = "pd")
reticulate::import("matplotlib.pyplot", as = "plt")
```

```{r}
# 2. Load data ---------------------------------------------
hddm_data <- flanker_data_clean_average %>%
  select(flanker_data_long) %>%
  mutate(
    flanker_data_long = map(flanker_data_long, function(x) {

      x %>%
        mutate(rt=rt/1000) %>%
        select(-response) %>%
        rename(subj_idx = id, response = correct) %>%
        select(subj_idx, condition, congruency, response, rt)
    }) 
  ) %>%
  unnest(flanker_data_long)

hddm_data_std <- hddm_data %>% filter(condition == "standard", subj_idx %in% 1:10)
hddm_data_enh <- hddm_data %>% filter(condition == "enhanced")
hddm_data_deg <- hddm_data %>% filter(condition == "degraded")
```

```{r}
# 3. HDDM --------------------------------------------------------------------

## 3.1 Models ----

  # a. Parameters fixed (i.e., equal) across congruency levels; standard condition
  # b. Parameters freely estimated across congruency levels; standard condition

## 3.2 Standard condition: Model a ----

### 3.2.1 Initiate and fit model
py_run_string("mod_fixed_std = r.hddm.HDDM(data = r.hddm_data_std, bias = False)")            
py_run_string("mod_fixed_std.find_starting_values()")                                 
py_run_string("hddm_fixed_std = mod_fixed_std.sample(500, burn=10)")

```

```{python}
mod_fixed_std = r.hddm.HDDM(data = r.hddm_data_std, bias = False)           
mod_fixed_std.find_starting_values()                                
hddm_fixed_std = mod_fixed_std.sample(500, burn=10)
```

### 2022-10-15 preregistrations/1_pilot/scripts/0_data_prep/3_clean_task_data.R

@@ -32,9 +32,9 @@ task_exclusions <- function(data, label, lower_rt_cutoff = 250, upper_rt_cutoff 
       ex_narb_invalid_trial      = ifelse(rt < upper_rt_cutoff & rt > lower_rt_cutoff, FALSE, TRUE),
       ex_narb_invalid_trials_n   = ifelse(n() > 1, sum(rt > upper_rt_cutoff | rt < lower_rt_cutoff, na.rm = TRUE), NA),
       
-      ex_narb_invalid_trials_neutral_n   = ifelse(n() > 1, sum((rt > upper_rt_cutoff | rt < lower_rt_cutoff) & condition == "neutral", na.rm = TRUE), NA),
+     # ex_narb_invalid_trials_neutral_n   = ifelse(n() > 1, sum((rt > upper_rt_cutoff | rt < lower_rt_cutoff) & condition == "neutral", na.rm = TRUE), NA),
       
-      ex_narb_invalid_trials_cued_n   = ifelse(n() > 1, sum((rt > upper_rt_cutoff | rt < lower_rt_cutoff) & condition == "cued", na.rm = TRUE), NA),
+     # ex_narb_invalid_trials_cued_n   = ifelse(n() > 1, sum((rt > upper_rt_cutoff | rt < lower_rt_cutoff) & condition == "cued", na.rm = TRUE), NA),
       
       
       

### 2022-10-15 preregistrations/1_pilot/scripts/0_data_prep/4_DDM_estimation.R

@@ -1,14 +1,14 @@
 
-# Libraries ---------------------------------------------------------------
+# 1. Libraries ---------------------------------------------------------------
 
 library(tidyverse)
 library(glue)
 library(here)
 library(RWiener)
-library(mvtnorm)
+#library(mvtnorm)
 library(data.table)
 
-# Load data ---------------------------------------------------------------
+# 2. Load data ---------------------------------------------------------------
 
 load(here("data", "1_pilot", "1_task_data_clean.Rdata"))
 
@@ -17,9 +17,9 @@ source(here("preregistrations", "1_pilot", "scripts", "custom_functions", "funct
 
 
 
-# Change Detection Task ---------------------------------------------------
+# 3. Change Detection Task ---------------------------------------------------
 
-# Pre-treatment
+## Preparations ----
 change_DDM_setup <- change_data_clean_average %>%
   select(change_data_long) %>%
   unnest(change_data_long) %>%
@@ -61,7 +61,7 @@ change_DDM_results_mod1 <- read_DDM(task = "change", model_version = "_mod1") %>
 change_bic_mod1 <- mean(change_DDM_results_mod1$bic, na.rm = TRUE)
 
 
-# Model 2: 5-parameter model (inter-trial variability parameters fixed to 0) ----
+## Model 2: 5-parameter model (inter-trial variability parameters fixed to 0) ----
 
 # #Set Fast-DM settings
 
@@ -130,53 +130,66 @@ change_DDM_results_mod4 <- read_DDM(task = "change", model_version = "_mod4") %>
 
 change_bic_mod4 <- mean(change_DDM_results_mod4$bic, na.rm = TRUE)
 
+change_DDM_results_mod4 %<>%
+  select(
+    id,
+    change_ml_a = a,
+    change_ml_v = v,
+    change_ml_t0 = t0
+  )
+
+
+## Model 5: KS estimation with st0 freely esimated (not preregistered) ----
+
+# Set Fast-DM settings
+
+fast_dm_settings(task = "change", 
+                 model_version = "_mod5",
+                 method = "ks",
+                 d = 0,
+                 zr = 0.5,
+                 szr = 0, sv = 0, st0 = "",
+                 format = "TIME RESPONSE")
+
[…]

### 2022-10-15 preregistrations/1_pilot/scripts/0_data_prep/7_merge_data.R

@@ -26,26 +26,20 @@ cleaned_data <-
   left_join(flanker_data_clean_average, by = "id") %>%
   # Task data: DDM
   left_join(change_DDM_results_mod4, by = "id") %>%
+  left_join(change_DDM_results_mod5, by = "id") %>%
   left_join(change_EZDM_results, by = "id") %>%
   left_join(cueing_DDM_results_mod8, by = "id") %>%
+  left_join(cueing_DDM_results_mod9, by = "id") %>%
   left_join(cueing_EZDM_results, by = "id") %>%
+  left_join(flanker_DDM_results_mod1, by = "id") %>%
   left_join(flanker_ssp_results, by = "id") %>%
   left_join(resize_screen, by = "id") %>%
   left_join(browser_interactions_summary, by = "id") %>%
   # Remove participants who have no task data
-  filter(!is.na(rt_change) | !is.na(rt_cueing_cued) | !is.na(rt_flanker_congruent)) 
+  filter(!is.na(rt_change) | !is.na(rt_cueing_cued) | !is.na(rt_flanker_congruent)) %>%
+  mutate(across(matches('meta.*duration.*_z'), as.numeric))
 
 
-cleaned_data %>% 
-  select(id, matches("rt_(change|flanker|cueing)")) %>% 
-  mutate(across(starts_with("rt_"), ~as.numeric(scale(log(.))))) %>% 
-  View
-
-
-cleaned_data %>%
-  filter(id %in% c(318, 515, 494, 158, 280, 6, 189, 528)) %>%
-  select(id, meta_feedback, contains("event"), ends_with("mean")) %>%
-  View
 
 
 # .csv file (nested columns containing trial-level data are dropped)

### 2022-10-15 preregistrations/1_pilot/scripts/1_primary_analyses/attention_cueing/4_plot_multiverse.R

@@ -1,4 +1,4 @@
-alibrary(tidyverse)
+library(tidyverse)
 library(cowplot)
 library(here)
 library(magrittr)
@@ -71,7 +71,7 @@ spec_curves_interaction <-
       ungroup()
     
     int_points <- 
-      primary_effects_points %>% 
+      primary_effects_points_cueing %>% 
       filter(dv_group == dv_which) %>%
       mutate(dv = factor(dv, levels = c("RT", "RT (log)", "Drift rate (v)", "Boundary separation (a)", "Non-decision time (t0)"))) %>%
       mutate(

### 2022-10-15 preregistrations/1_pilot/scripts/1_primary_analyses/flanker/4_plot_multiverse.R

@@ -75,7 +75,7 @@ spec_curves_flanker_raw <-
       ungroup()
     
     int_points <- 
-      primary_effects_points %>% 
+      primary_effects_points_flanker %>% 
       filter(dv_group == dv_which) %>%
       mutate(dv = factor(dv, levels = c("RT", "RT (log)", "Perceptual input (p)", "Boundary separation (a)", 
                                         "Non-decision time (t0)", "Initial attention width (sda)", "Rate of spotlight shrinking (rd)"))) %>%
@@ -469,8 +469,8 @@ primary_flanker_fig1 <-
       spec_curves_flanker_raw[[1]]$eff_curve,
       spec_curves_flanker_raw[[1]]$p_curve,
       spec_curves_flanker_raw[[1]]$sample_sizes,
-    #  spec_curves_raw[[1]]$spec_grid,
-      nrow  = 4,
+      spec_curves_flanker_raw[[1]]$spec_grid,
+      nrow  = 5,
       ncol  = 1, 
       align = "v", 
       axis  = "lr",
@@ -488,7 +488,7 @@ primary_flanker_fig2 <-
       spec_curves_flanker_ssp[[1]]$eff_curve,
       spec_curves_flanker_ssp[[1]]$p_curve,
       spec_curves_flanker_ssp[[1]]$sample_sizes,
-    #  spec_curves_ssp[[1]]$spec_grid,
+      spec_curves_ssp[[1]]$spec_grid,
       nrow  =3,
       ncol  = 1, 
       align = "v", 

### 2022-10-15 preregistrations/1_pilot/scripts/3_exploratory_analyses/1_efa.R

@@ -41,7 +41,7 @@ efa_model <- factanal(efa_data, factors = 5, rotation = "oblimin")
 efa_model
 
 efa_tidy <- tidy(efa_model) %>% 
-  mutate(across(starts_with("fl"), ~ifelse(. < .32, NA, .))) %>% 
+#  mutate(across(starts_with("fl"), ~ifelse(. < .32, NA, .))) %>% 
   left_join(codebook %>% rename(variable = Variable)) %>% 
   arrange(fl1, fl2, fl3, fl4, fl5) %>% 
   mutate(

### 2022-10-15 preregistrations/1_pilot/scripts/3_exploratory_analyses/2_unpredictability/flanker/4_plot_multiverse.R

@@ -1,7 +1,7 @@
 library(tidyverse)
 library(cowplot)
 
-load(here("data", "1_pilot", "secondary_analyses", "flanker", "3_multiverse_extracted_effects.Rdata"))
+load(here("data", "1_pilot", "3_exploratory_analyses", "2_unpredictability", "flanker", "3_multiverse_extracted_effects.Rdata"))
 
 
 # ggplot2 theme -----------------------------------------------------------

### 2022-10-15 preregistrations/1_pilot/scripts/custom_functions/functions_DDM.R

@@ -57,7 +57,7 @@ execute_fast_dm <- function(task, model_version = "") {
 
 
 read_DDM <- function(task, model_version = "") {
-  results <- read_delim(here("data", "1_pilot", "DDM", str_glue("ddm_results_{task}{model_version}.lst")), delim = " ", trim_ws = TRUE) %>%
+  results <- read_table(here("data", "1_pilot", "DDM", str_glue("ddm_results_{task}{model_version}.lst"))) %>%
     mutate(dataset = str_replace_all(dataset, str_c("^", task, "_DDM_subject"), "") %>% as.numeric(),
            task = task) %>%
     rename(id = dataset)

### 2022-10-15 preregistrations/1_pilot/scripts/pres_plot.R

@@ -1,0 +1,524 @@
+library(tidyverse)
+library(cowplot)
+library(magrittr)
+library(here)
+library(flextable)
+
+load(here("data", "1_pilot", "1_primary_analyses", "change_detection", "3_multiverse_extracted_effects.Rdata"))
+load(here("data", "1_pilot", "1_primary_analyses", "flanker", "3_multiverse_extracted_effects.Rdata"))
+load(here("data", "1_pilot", "1_primary_analyses", "attention_cueing", "3_multiverse_extracted_effects.Rdata"))
+
+# ggplot2 theme -----------------------------------------------------------
+theme_set(
+  theme_bw() +
+    theme(
+      axis.line       = element_line(),
+      axis.text       = element_text(size = rel(1)),
+      axis.title      = element_text(size = rel(1.2), margin = margin(1,0,0,0,"lines")),
+      axis.ticks      = element_line(),
+   #   axis.line.x       = element_blank(),
+   #   axis.text.x       = element_blank(),
+   #   axis.ticks.x      = element_blank(),
+     # axis.title.x      = element_blank(),
+      panel.border      = element_blank(), 
+      panel.spacing.y   = unit(0.5, "lines"),
+      plot.margin       = margin(.25,.25,.25,.25,"lines"),
+      plot.background   = element_rect(color = NA),
+      plot.title        = element_text(size = rel(.85), hjust = 0, margin = margin(0,0,.5,0, "lines")),
+      plot.subtitle     = element_blank(),
+      panel.grid        = element_line(color = NA),
+      strip.background  = element_blank(), 
+      strip.placement   = "outside",
+      strip.text        = element_text(size = rel(.85), angle = 0)
+    )
+)
+
+pval_colors <- c("pos-sig" = "#006D77", "non" = "gray70")
+my_alphas <- c(.5, 1)
+my_limits <- c(1,80)
+
+primary_effects <- 
+  bind_rows(
+    primary_effects_change %>% mutate(task = "change"),
+    primary_effects_cueing %>% mutate(task = "cueing"),
+    primary_effects_flanker %>% mutate(task = "flanker")
+  ) %>%
+  filter(dv %in% c("Drift rate (v)", "Initial width (sda)", "Perceptual input (p)", "Shrinking rate (rd)", "sda / rd (interference)")) %>%
+  mutate(
+    task = case_when(
+      task == "flanker" & dv == "Perceptual input (p)" ~ "flanker_p",
+      task == "flanker" & dv == "Initial width (sda)" ~ "flanker_sda",
[…]

### 2022-10-15 preregistrations/1_pilot/scripts/supplemental/ssp_model.R

@@ -3,15 +3,19 @@ library(here)
 library(flankr)
 library(furrr)
 library(parallel)
+library(RWiener)
 
-load(here("data", "1_pilot", "2_cleaned_data.Rdata"))
+load("data/1_pilot/2_cleaned_data.Rdata")
 
-cores <- detectCores()- 2
+cores <- detectCores()- 4
 
-plan('multisession')
+plan('multisession', workers = cores)
 
 
-predicted_quantiles <- cleaned_data %>%
+
+# Flanker Task - SSP Model ------------------------------------------------
+
+predicted_quantiles_flanker <- cleaned_data %>%
   select(a_flanker, t0_flanker, p_flanker, rd_flanker, sda_flanker, id) %>%
   drop_na() %>%
   filter(rd_flanker > 0) %>%
@@ -34,7 +38,7 @@ predicted_quantiles <- cleaned_data %>%
   unnest(sim_data)
 
 
-observed_quantiles <- cleaned_data %>%
+observed_quantiles_flanker <- cleaned_data %>%
   select(flanker_data_long) %>%
   unnest(flanker_data_long) %>%
   group_by(id, congruency) %>%
@@ -49,14 +53,352 @@ observed_quantiles <- cleaned_data %>%
     quan_rt_obs  = quan_rt_obs / 1000) 
   
 
-qq_data <- left_join(predicted_quantiles, observed_quantiles)
+qq_data_flanker <- left_join(predicted_quantiles_flanker, observed_quantiles_flanker)
 
-ggplot(qq_data) +
+qq_flanker_rt <- ggplot(qq_data_flanker) +
   geom_point(aes(quan_rt_obs, quan_rt_pred)) +
   geom_abline(slope = 1, intercept = 0) +
   facet_grid(congruency~quantile) +
   labs(
-    x = "\nObserved",
-    y = "Predicted\n"
-  )
+    x = "\nObserved RT",
+    y = "Predicted RT\n",
+    title = "Flanker Task"
+  ) +
+  theme_classic()
 
+qq_flanker_acc <- ggplot(qq_data_flanker) +
+  geom_point(aes(prop_acc_obs, prop_acc_pred)) +
+  geom_abline(slope = 1, intercept = 0) +
+  facet_grid(congruency~quantile) +
+  expand_limits(x = 0, y = 0) +
+  labs(
+    x = "\nObserved Acc",
+    y = "Predicted Acc\n"
+  ) +
[…]

### 2023-04-11 preregistrations/3_study2/preregistration.Rmd
initiate study 2 folders

--- 2022-02-23 preregistrations/2_study1/preregistration.Rmd
@@
 
-In line with previous theorizing [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013], we initially expected people from adversity to perform better on cognitive tasks that require a broad attention scope in order to successfully detect peripheral and subtly changing information, and to perform worse on tasks requiring ignoring interfering information (see the [preregistration](https://github.com/StefanVermeent/attention_project/blob/Preregistration/preregistrations/1_pilot/preregistration.docx) of the first pilot study).
-However, the data pointed in the opposite direction.
-A Drift Diffusion analysis showed that participants with more violence exposure were generally slower to process information and orient their attention across all three tasks.
-At the same time, they were faster to narrow down their attention to the central target on the Flanker Task, thereby effectively limiting the amount of flanker interference that they were exposed to.
-
-The findings in the pilot study suggest that deficit patterns that are typically found on tasks like the Flanker might not reflect problems in attention control and inhibition, even suggesting the opposite.
-Instead, people from adversity might process information more slowly, leading to longer reaction times.
-The goal of the current study is to replicate the attention findings on the Flanker Task, and to better understand the apparent information processing deficits.
-Participants completed three versions of the Flanker Task: the standard version, a version with enhanced visual information, and a version with degraded visual information.
-
-Figure \@ref(fig:figure1) shows two possible data patterns that we might expect across the different versions at different levels of violence exposure.
-First, if the findings reflect a general information processing deficit, we would expect performance to be lower for people with more violence exposure across all versions of the task.
-Alternatively, lower performance on the standard version might reflect an adaptive trade-off towards more robust cognitive functioning, even in the face of noise or perturbations [@giudice_2018].
-In that case, we would expect more stable performance for people with more violence exposure.
-As a result, they might not benefit as much from enhanced visual information, but at the same time might be able to better maintain performance when presented with degraded information.
-
-```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap="Overview of the three Flanker conditions and predicted patterns of results under different cognitive mechanisms.
-A: The different Flanker Task conditions.
-The standard version is a typical implementation of the Flanker stimuli.
-The enhanced version improves the quality of information by increasing stimulus size by 12.5% and including padding (5 pixels) between the arrows.
-The degraded cognition reduces the quality of information by rotating all arrows at a 45° angle.
-B: Two potential patterns of the effect of condition on people’s perceptual input as a function of violence exposure.
-Left plot: Under the deficit model, we would expect people with more violence exposure to perform worse across all three conditions.
-Right plot: If performance is traded off against higher robustness of the cognitive system for people with more violence exposure (Del Giudice & Crespi, 2018), we would expect cognitive performance in this group to be relatively stable across conditions, perhaps even outperforming people with less violence exposure in the degraded condition."}
-knitr::include_graphics("Fig1.png", error = F)
-```
+Generally speaking, the results of the first two studies were not in line with our initial predictions about a present-oriented attention style.
+Although we expected such a style to lead to faster speed of perceptual processing on attention tasks, we generally found the opposite pattern.
+One reason for this might be that a present-oriented attention style leads people from adversity to process information more holistically, which would lower the depth of perceptual processing of any individual stimulus.
+Another related reason might be that an external, present-oriented attention style extends beyond the computer screen to all of their immediate environment.
+Both of these are potential mechanistic explanations for a lowered quality of perceptual processing that would be in line with a specialized attention style.
+In study 2, we aimed to replicate the broader findings from study 1 (lowered perceptual input on the Flanker Task but no differences in interference) and to investigate if and how the lower quality of perceptual processing was associated with a more holistic style of attention.
 
@@
 
-1. Investigate the robustness of the primary DDM findings in the pilot study by pooling the pilot data and the data of the standard condition in the current study. 
-2.
-Extent the findings of the pilot study by investigating how Flanker performance changes across conditions as a function of violence exposure.
-We expect that the manipulations primarily have an effect on perceptual input *p*, thereby also affecting overall reaction times.
+1. Investigate how unpredictability and violence exposure are associated with perceptual input and interference on the Flanker Task by pooling the data across all three studies.
 
-# Secondary  {#secondary}
-
-1.
-Investigate the extent to which the [factor structure](#efa) of the unpredictability measures corresponds to the one found in the pilot study.
-Secondly, investigate how different dimensions of unpredictability relate to Flanker performance.
-2) Explore the role of state anxiety, hunger, and sleep deprivation as potential moderators of the relationship between adversity and attention performance.
-Anxiety might enhance attention performance by making participants more vigilant.
-Conversely, hunger and sleep deprivation could have a negative effect on performance.
-3) Explore bivariate correlations between measures of adversity, attention, and measures of temporal orientation (i.e., impulsivity and future orientation).
-4) Explore the correlation between current depressive symptoms and retrospective measures of adversity, which might reflect a negativity bias in recalling past events driven by current depressive symptoms [@nivison_2021].
+2. Investigate how unpredictability and violence exposure are associated with a preference for more holistic vs. detailed processing of information.
 
@@
 
-Participants were 550 US-based individuals between the ages of 18 and 30 (*M* = `r #TBD`, *SD* = `r #TBD`).
-We decided for this age cut-off to reduce the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 [@salthouse_2010].
-Recruitment took place through Prolific Academic [www.prolific.co].
-The sample was balanced to include roughly 50% males.
-Participants were eligible for the study if they were from the United States and if they spoke fluent English.
-Finally, we used the MacArthur's ladder for perceived social-economic status (SES) as used in Prolific's pre-screening battery to ensure that 50% of the sample perceived their current SES to be low (a score of 4 or below).
-
-We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the optimal number of participants to include (more information including all simulation code on [Github](https://github.com/StefanVermeent/attention_project/tree/preregistration1/preregistrations/1_pilot/scripts)).
-Assuming an effect size of $\beta$ = 0.1 and a DDM parameter recovery accuracy of *r* = .85, we estimated that we would need 500 participants to achieve at least 80% power.
-We sampled a total of 550 participants to account for necessary exclusions (based on our experiences in the pilot study).
+Participants will be 400 US-based individuals between the ages of 18 and 30. Recruitment will be identical to study 1. 
+We conducted a power analysis for the planned linear regressions through simulation. 
+We determined the required sample size to achieve power of > .90 for a standardized main effect of 0.05.
+This main effect is slightly lower than the effect of 0.06 that we found for perceptual input in the pooled analyses of study 1.
+Simulations revealed that we would require around 450 participants to achieve a power of .93.
+We decided to recruit 500 participants with the expectation that we will have to exclude around 50 participants.
 
@@
 
-We applied several exclusion criteria prior to analyzing the data.
-First, we excluded participants who did not complete the full study and those who did not complete all three Flanker conditions (*N* = `r #TBD `).
-Second, we analyzed responses to the attention checks and reversed coded items in the questionnaire part of the experiment.
-We excluded participants if they missed both attention check items or if they had suspicious response patterns (e.g., consistently endorsing high response options even when some items were reverse coded) (*N* = `r #TBD `).
-Third, we excluded participants whose screen height was < 700 pixels, or whose screen height was bigger than their screen width (suggesting that they did not complete the experiment on a laptop or desktop pc).
-Finally, we screened participants' accuracy on the Flanker task within each condition.
-Using a binomial distribution, we calculated that if a participant would be purely guessing on each trial, they would have a probability of 97.5% of obtaining an overall accuracy of 59.4%.
-Therefore, we excluded participant's data on a particular condition if their accuracy on that condition was below 60%.
+Participants will be excluded if they 1) do not complete the full study or both cognitive tasks, 2) miss both attention check items or if they have suspicious response patterns (e.g., consistently endorsing high response options even when some items were reverse coded), 3) have a screen height < 700 pixels or a screen height that is bigger than the screen width to ensure the tasks were completed on a laptop or desktop pc, 4) exit full-screen mode and/or engaged with other broswer tabs *during* the cognitive tasks (but not while reading instructions or while taking breaks in between blocks), 5) do not perform above chance on either the Flanker Task or the Global-Local Task (based on a binomial distribution using a probability of 97.5%).
 
-In addition, we screened the reaction times on the Flanker Task.
-For the Drift Diffusion analyses, it is important that each response is generated by a process of active information accumulation (i.e., a diffusion process, as opposed to guessing).
-To this end, trials with reaction times < 250 ms or > 3500 ms [@ratcliff_2015] were excluded from the analyses (*N* = `r #TBD `).
-Participants with more than 10 removed trials were excluded from the analyses (N = `r #TBD `).
-Finally, we logged whether participants exited full-screen mode and/or engaged with other browser tabs (i.e., blur events) at any point during the Flanker Task.
-We excluded participants for whom blur events occurred while a Flanker block was ongoing (but not while reading instructions or taking breaks in between conditions).
-Full-screen exits were included in the [multiverse analysis](#multiverse_plan).
+In addition, we will screen reaction times on both cognitive tasks. 
+We will remove trials with response times < 250 or > 3500 ms.
+Participants with more than 10 removed trials will be excluded from the analyses.
 
@@
 
-Based on participant feedback in the pilot study, we changed (the wording of) a number of questionnaire items in order to make them more inclusive.
-We added an item asking about the participant's family composition.
-In addition, all mentions of 'parent(s)' across questionnaires were changed to 'caregiver(s)' (e.g., "At least one of my caregivers had punishments that were unpredictable").
-We also added a question asking about the participant's exact family composition.
-
 ### Flanker Task {#flanker}
 
-The Flanker Task is commonly used as a measure of selective attention and response inhibition [@eriksen_1974].
-On each trial of a typical Flanker Task, participants are presented with a set of five arrows pointing either left or right.
-Their job is to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right (see Figure \@ref(fig:figure1)b).
-On 50% of the trials, the flanking arrows point in the same direction as the central arrow (i.e., congruent trials), and on the other 50% of the trials they point in the opposite direction (i.e., incongruent trials).
+The Flanker Task was identical to the standard version used in study 1. 
+It was programmed in JsPsych 7.3.2 [@deleeuw_2015]. 
+Participants first completed eight practice trials and next completed 64 test trials in a single block.
 
-The Flanker Task was programmed in JsPsych version 3.6.1 [@deLeeuw_2015].
-We programmed three conditions of the Flanker Task (See Figure \@ref(fig:figure1).
-In the standard condition, the arrows were 40 pixels in size (0.4 inches) and had zero padding between them.
-In the 'enhanced' condition, the aim was to increase the quality of visual information provided by the arrows.
-To this end, we increased the arrow size by 12.5% to 45 pixels (0.45 inches), and increased padding between the arrows to 5 pixels.
-This increased the width of the Flanker display by 50% with respect to the standard display.
-In the 'degraded' condition, the aim was to decrease the quality of visual information provided by the arrows.
-The arrow size and padding were the same as in the standard version, but both flanking and target arrows were rotated 45$^\circ$.
-Therefore, they provided more noisy information about their horizontal direction.
-We had no strong *a priori* expectations about how performance of adversity-exposed people might be affected by specific types of stimulus degradation (e.g., arrow rotation, decreasing stimulus contrast).
-
-Participants completed each condition of the Flanker Task separately in different blocks.
-The presentation order of the conditions was randomized.
-Each condition consisted of 64 trials.
-For the degraded condition, participants completed four repetitions of all parameter combinations: Arrow location (top vs.
-bottom) X central arrow direction (left-up vs.
-left-down vs.
-right-up, vs right-down) X congruency: (congruent vs.
-incongruent).
-For the standard and enhanced condition, participants completed eight repetitions of all parameter combinations to match the number of trials in the degraded condition: Arrow location (top vs.
-bottom) X central arrow direction (left-up vs.
-left-down vs.
-right-up, vs right-down) X congruency: (congruent vs.
-incongruent).
-Across all three conditions, the arrows were randomly presented in the top-half or bottom-half of the screen at 200 pixels (2 inches) from the center of the screen.
-This was done to prevent participants from rigidly fixating on the center of the screen, which might reduce the interfering effect of the flanking arrows.
-Each trial started with a fixation cross presented at the center of the screen.
-After a delay of 1000ms, the arrows are presented either in the top- or bottom-half of the screen.
-
-Prior to each block, participants performed eight practice trials of the current condition.
-During practice, participants received performance feedback after each trial (either "Correct!" printed in green, "Incorrect!" printed in red, or "Too slow!" printed in red if their response latency exceeded 2000 ms).
-After completing the practice trials, participants completed each block with the opportunity to take a break in between.
-At the onset of each block, participants were told what the current condition was.
-No performance feedback of any kind was provided during the test blocks.
-The main performance measures were RTs and accuracy for each condition.
+## Global-Local Task {#globallocal}
 
@@
 
-Perceived unpredictability before age 13 was measured using two different scales: A scale of perceived childhood unpredictability used in previous research [@mittal_2015; @young_2018], an adaptation of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019], and two scales measuring change in the family and social environment.
-The perceived childhood unpredictability scale contained eight items measuring perceived unpredictability before age 13 (e.g, "My family life was generally inconsistent and unpredictable from day-to-day"; See [Table S3](#appendix) for an overview of all items).
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-
-We included the QUIC because it captures several dimensions of environmental and household unpredictability.
-The QUIC distinguishes between items capturing more short-term unpredictability (i.e., on the level of seconds to minutes) and more long-term unpredictability (i.e., on the level of days to months).
-The scale of perceived childhood unpredictability combines items on different time scales.
-Some items measure unpredictability on a relatively short-term scale (e.g., item 1) while other items measure unpredictability on a long-term scale (e.g., item 3).
-Unpredictability on different time scales might have different effects on the development of specific attention styles.
-
-We included all five scales of the QUIC: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 3) Safety and security (See [Table S4](#appendix) for an overview of all items).
-The items of the Parental environment subscale deviated most from the original.
-
-We made three general changes to the original scale as described in @glynn_2019.
-First, we adapted all items to refer to experiences before age 13.
-This was done to reduce cognitive load from having to go back-and-forth between different time scales.
-Second, most items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
-An exception was made for four items of the parental environment scale which asked for more specific experiences (e.g., "I experienced changes in my custody arrangement"; see [Table S4](#appendix)).
-For these items, we adopted a response scale with the options "never", "only once", "a couple times", "several times", "many times".
-Third, quantifiers such as "frequently", "often", and "There was a period of time when [...]" were dropped to better match the response scale.
-We excluded the item "My parents got divorced" because it did not fit the response format and was captured by one of the items of the perceived unpredictability scale.
-
-We assessed household chaos before age 13 using an adaptation of the Confusion, Hubbub, and Order Scale [CHAOS; @matheny_1995].
-The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late"; See [Table S5](#appendix) for an overview of all items).
-We made two changes to the original scale as described in @matheny_1995.
-First, all items were converted from the present tense to the past tense, and were endorsed as applying to participants' lives before age 13.
-Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
-This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
-
-In addition, we measured the stability of the family and social environment.
-On a scale of 1 (the same all the time) to 5 (constant and rapid changes), participants indicated how often the following aspects of their family and social environment changed before age 13: 1) economic status, 2) family environment, 3) childhood neighborhood environment, and 4) childhood school environment.
-Finally, we included four objective measures of unpredictability before age 13.
-Participants provided answers to the following items in an open response format: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "Think about the caregiver who had the most romantic partners before you were age 13.
-How many romantic partners did this person have?".
-
-We computed four main unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) *unpredictability~perceived~*: containing all items of the perceived unpredictability scale and the QUIC, given their close conceptual overlap (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD` *r* = `r #TBD` between the two scales); 2) *unpredictability~CHAOS~*: containing the items of the CHAOS (*M* = `r #TBD`, *SD* = = `r #TBD`, $\alpha$ = `r #TBD`); 3) *unpredictability~subjective~*: containing all items of the perceived unpredictability scale, the QUIC and the CHAOS (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`); 4) *unpredictability~objective*: containing the items assessing the stability of the family- and social environment , as well as the three objective measures (*M* = `r #TBD`, *SD* = `r #TBD`, $\alpha$ = `r #TBD`).
-
-We computed several unweighted unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overall QUIC variable by averaging all 37 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-See also [below](#efa) for details on a factor analysis based on the individual items across scales.
+We distinguish between subjective and objective measures of environmental unpredictability.
+We distinguish between subjective and objective measures of environmental unpredictability.
+Subjective unpredictability will be measured as an unweighted average of three scales: 1) A scale of perceived childhood unpredictability used in previous research (see [Table S3]) [@mittal_2015; @young_2018]; 2) An adapted version of the Confusion, Hubbub and Order Scale [CHAOS; @matheny_1995] (see [Table S5](#appendix)); 3) An adapted version of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019] (see [Table S4](#appendix)).
+Objective unpredictability will be measured as an unweighted average of four items relating to experiences prior to age 13: 1) number of residential changes, 2) number of male and female romantic partners of a caregiver besides the other primary caregiver (measured separately; values > 6 were given a value 6 to prevent extreme outliers), 4) self-reported stability of the family and social environment across four dimensions: economic status, family environment, childhood neighborhood environment, and childhood school environment (rated between 1 (the same all the time) and 5 (constant and rapid changes)).
+The main analyses will be based on a full composite that is an unweighted standardized average of subjective and objective unpredictability.
 
@@
 
-Participants' perceived level of resource scarcity before age 13 was measured using seven items (e.g., "Your family had enough money to afford the kind of home you all needed"; See [Table S6](#appendix) for an overview of all items).
-Participants rated each item on a scale from 1 (never true) to 5 (very often true).
-Scores for the first six items were reverse coded so that higher scores indicated more perceived resource scarcity.
-The items were averaged together to create an unweighted composite scale (*M* = `r  #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+We will create a poverty composite score that is the average of the following measures (standardized) focusing on the family situation prior to age 13: 1) perceived level of resource scarcity (See [Table S6](#appendix)); 2) the unweighted average of the highest achieved education of both primary caregivers; 3) household income (6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'.
+Scores were reverse coded so that higher scores indicated higher levels of poverty.).
 
-In addition, we measured several indicators of objective SES before age 13.
-First, participants separately indicated the highest education of their two primary caregivers (if applicable) on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'.
-The caregivers' education level were averaged to create an overall unweighted parental education composite (*M* = `r  #TBD `, *SD* = `r  #TBD `).
-Participants also indicated their family's household income before age 13 on a 6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'.
-Scores were reverse coded so that higher scores indicated higher levels of poverty.
+### Attentional style
 
-We created a composite score of poverty exposure before age 13 by averaging together the standardized scores of perceived level of resource scarcity, overall caregiver education, and household income.
+We will measure attentional style using the Attentional Style Questionnaire [ASQ; @calster_2018].
+The ASQ measures self-reported attentional style, with seven items
 
@@
 
-We assessed impulsivity with the Motor Impulsivity subscale of the Barrett Impulsivity Scale (BIS; short form; [@patton_1995; @spinella_2007]).
-The Motor Impulsivity subscale of the BIS consists of five items (e.g., "I do things without thinking"; See [Table S7](#appendix) for an overview of all items).
-We did not include the Non-planning subscale because it overlapped substantially with the Future Orientation Scale described below.
-In addition, we did not include the Attention impulsivity subscale because it included items which we deemed to be mostly irrelevant for our target population (e.g., "I 'squirm' at plays or lectures").
-We changed the original 4-point rating scale (rarely/never to almost always) to a 5-point rating scale ranging from 1 (never true) to 5 (very often true).
-An overall impulsivity variable was computed by averaging the five unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+We will measure impulsivity with the Motor Impulsivity subscale of the Barrett Impulsivity Scale (BIS; short form; [@patton_1995; @spinella_2007]) (See [Table S7](#appendix)) 
+An overall impulsivity variable will be computed by averaging the five unweighted items.
 
@@
 
-We assessed future orientation with an adapted version of the Future Orientation Scale [FOS; @steinberg_2009].
-The original scale consists of 15 sets of opposing items separated by "BUT" (e.g., "Some people like to plan things out one step at a time BUT other people like to jump right into things without planning them out beforehand").
-Participants first choose the item that best matches their general preference, and then indicate whether the statement is "really true" or "somewhat true".
-We adapted this format in a couple of ways.
-First, we converted the two statements per item to a single statement by picking the statements in the original right-hand column.
-Second, we adapted the 15 statements from a third-person to a first-person format.
-These changes were made in an attempt to reduce the cognitive load of the items.
-We worried that people with less formal education or who were sitting in a noisier environment would struggle with the length of the original items.
-
-In addition, item 8 of the original scale ("[...] other people would rather spend their money right away on something fun than save it for a rainy day") was changed to "I'd rather spend money right away than save it for a rainy day" (i.e., dropping the phrase "on something fun") to make it more general with regard to the thing that money is spent on.
-For people from adversity, spending money right now instead of saving it for the future might often be born out of necessity (e.g., having just enough money for food and shelter; being in debt) instead of a failure to delay gratification.
-See [Table S8](#appendix) for an overview of all adapted items).
-Finally, the rating scale was adapted from the original 4-point scale (ranging from really true for the left-hand statement to really true for the right-hand statement) to a 5-point scale ranging from 1 (never true) to 5 (very often true).
-
-An overall future orientation variable was computed by averaging the 15 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-In addition, we calculated subscales for "Planning ahead" (items 1, 6, 7, 12 and 13), "Time perspective" (items 2, 5, 8, 11 and 14) and "Anticipation of future consequences" (items 3, 4, 9, 10 and 15).
+We will measure future orientation with an adapted version of the Future Orientation Scale [FOS; @steinberg_2009] (See [Table S8](#appendix).
+An overall future orientation variable will be computed by averaging the 15 unweighted items.
 
@@
 
-We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD; @radloff_1977].
-The scale consists of 20 items (e.g., "I do things without thinking"; See [Table S9](#appendix) for an overview of all items).
-Participants rate each item on a scale of 1 (rarely or none of the time (less than 1 day)) to 4 (most or all of the time (5-7 days)).
-An overall depression variable was computed by averaging the 20 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+We will measure depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD; @radloff_1977] (See [Table S9](#appendix). 
+An overall depression variable will be computed by averaging the 20 unweighted items.
 
@@
 
-The experiment was completed on the participants' own laptop or desktop computer and consisted of five parts (in fixed order): consent, Flanker Task, questionnaire battery, brief demographics form, and final checks including the opportunity to give feedback on the experiment.
-Participants were allowed to refrain from answering any of the questionnaire items, but were prompted with a warning once when moving to the next page if one of the items was not answered (which they could ignore).
+The experiment will be completed on the participants' own laptop or desktop computer and will of five parts (in fixed order): consent, cognitive tasks, questionnaire battery, brief demographics form, and final checks including the opportunity to give feedback on the experiment.
+Participants are allowed to refrain from answering any of the questionnaire items, but are prompted with a warning once when moving to the next page if one of the items is not answered (which they can ignore).
 
-After providing consent, participants started with the Flanker Task.
-They were asked to complete the Flanker Task in a quiet room in the house where they would be least likely to be distracted by other people or outside noises.
-The order of the tasks was counterbalanced between subjects.
-At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs.
-The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deLeeuw_2015].
-Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the creditcard.
-The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants.
-After successfully resizing the screen, participants completed all three tasks.
-During the task, the cursor was hidden from the screen to minimize distractions.
-Code for the three tasks can be found on [Github](https://github.com/StefanVermeent/attention_project/tree/main/tasks).
+After providing consent, participants start either with the Flanker Task or Global-Local Task (counterbalanced).
+They are asked to complete the tasks in a quiet room in the house where they would be least likely to be distracted by other people or outside noises.
+At the onset of the first task, the experiment switches to full-screen mode to limit distractions from other programs or browser tabs.
+The size of the task stimuli is controlled between subjects using the resize plugin in JsPsych [@deLeeuw_2015]. 
+After successfully resizing the screen, participants complete all three tasks. 
+Code for the three tasks can be found at [https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/3_study2/materials](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/3_study2/materials).
 
-After completing the Flanker task, participants completed the questionnaire battery in the following fixed order: 1) Current state (state anxiety and separate questions relating to specific states); 2) Childhood adversity (perceived unpredictability, perceived socio-economic status, exposure to violence and physical fights, household chaos); 3) Temporal orientation (impulsivity, future orientation); 4) Depressive symptoms.
+After completing the cognitive tasks, participants complete the questionnaire battery in the following fixed order: 1) Current state (state anxiety and separate questions relating to specific states); 2) Childhood adversity (perceived unpredictability, perceived socio-economic status, exposure to violence and physical fights, household chaos); 3) Temporal orientation (impulsivity, future orientation); 4) Depressive symptoms.
 
-Finally, the demographics questions asked about the participant's age, weight, height, physical activity, sex at birth, gender, ethnicity, social class (current and during childhood), education level (one's own as well as caregivers' education level), occupation, and household income (current and during childhood).
-At the end of the experiment, we asked participants if they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.
+Finally, the demographics questions asks about the participant's age, weight, height, physical activity, sex at birth, gender, ethnicity, social class (current and during childhood), education level (one's own as well as caregivers' education level), occupation, and household income (current and during childhood).
+At the end of the experiment, we ask participants if they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.
 
-The full experiment was expected to take approximately 30 minutes. Participants were paid £3.75 upon completing the full experiment.
+The full experiment is expected to take approximately 30 minutes. Participants are paid £3.75 upon completing the full experiment.
 
@@
 
-The DDM analysis of the Flanker task was done using an adaptation of the standard DDM that was specifically developed to account for Flanker data: The Shrinking Spotlight model [SSP; @grange_2016; @white_2018a; @white_2018b; @white_2011].
-The standard DDM model assumes a stable drift rate over time within trials (i.e., the rate of information accumulation does not change over time).
-However, on the Flanker Task, reaction time patterns indicate that Flankers exert their strongest effect on performance early on the trial, which then decreases over time.
-This effectively means that the drift rate increases over time, thus violating the basic assumption of the standard DDM [@white_2011].
-The SSP explains this pattern by assuming that attention on the Flanker task works like a spotlight that starts relatively broad, and then gradually narrows down to the central arrow over time.
-Each arrow provides perceptual input *p*.
-If the flanking arrows are congruent, all flankers take a positive value for *p*; if the flanking arrows are incongruent, they take a negative value for *p* while the central arrow takes a positive value.
-The drift rate (*v*) at each time point is the function of the strength of perceptual input *p* multiplied by the amount of attention focused on each arrow.
+For the Flanker Task, we will use the Shrinking Spotlight Model [SSP; @grange_2016; @white_2018a; @white_2018b; @white_2011] to fit the data.
+The SSP model will be fit to the data of each individual participant in two steps. 
+First, we loop over 50 different sets of starting parameters with a variance of 20 to find the best starting values for each participant.  
+On this first fitting step, 1000 trials will be simulated on each iteration of the fit routine. 
+Second, after finding the optimal set of starting values, we fit the final model using the best starting values found in step 1 and simulate 50,000 trials on each iteration. 
+The main parameters of interest are perceptual input (*p*) and interference (initial attention width / attention shrinking rate).
 
-Attention is operationalized by two additional parameters: the initial width of the attentional spotlight (*SD~a~*) and the shrinking rate of the attentional spotlight (*rd*).
-The attentional spotlight is assumed to be normally distributed over the arrows, with relatively more attention paid to the arrows at the center and relatively less attention paid to the peripheral arrows.
-Over time, this normal distribution (*SD~a~*) narrows down to the central arrow at the rate specified by *rd*, thereby gradually decreasing the interfering noise of the flankers and increasing the signal obtained from the target.
+For the Global-Local Task, we will use an hierarchical Bayesian DDM to fit the data using the runjags package [@denwood_2016].
+Drift rate and non-decision time will be freely estimated per task condition (global vs. local), whereas boundary separation wil be fixed to be equal across conditions.
+The starting point will be fixed to 0.5.
+Each model will be fit with three Markov Chain Monte Carlo (MCMC) chains. Each chain will contain 2,000 burn-in samples and 10,000 additional samples. 
+Of these samples, every 10th sample will be retained. 
+Posterior samples of all three chains will be combined, resulting in a posterior sample of 3,000 samples. 
+The main parameter of interest is the drift rate, more specifically, the difference between drift rates (drift rate~global~ - drift rate~local~).
 
-Model fit was done using the *flankr* package in R [@grange_2016].
-The SSP model was fit to the data of each individual participant in two steps.
-First, we looped over 50 different sets of starting parameters with a variance of 20 to find the best starting values for each participant.
-This was done to prevent accidentally converging on a suboptimal solution [@grange_2016].
-On this first fitting step, 1000 trials were simulated on each iteration of the fit routine.
-Second, once the optimal set of starting values was found, we fitted the final model using the best starting values found in step 1 and simulating 50,000 trials on each iteration.
+### Primary analyses
 
-The model fit for all participants was assessed through QQ-plots comparing the empirical data with the model predictions following @grange_2020.
-Using each participant's best-fitting parameters (based on the final step above), we simulated RTs and accuracy for 50,000 trials of each congruency condition and each Flanker version.
-We calculated the total proportion accuracy and the 25th, 50th, and 75th quantile of the response time distribution (correct trials only) for both the simulated data and the empirical data.
-The outcomes for all participants were plotted against each other.
-The closer the points are to the diagonal line, the better the models fit the participants' data.
-
-For the analyses, we extracted the following parameters: 1) perceptual input (*p*); 2) boundary separation (*A*); 3) initial attention width (*sd~a~*); 4) Attention shrinking rate (*rd*); Interference effect (*sd~a~* / *rd*); 5) non-decision time (*t0*).
+To address the [first primary aim](#primary), we will fit a linear regression model to the pooled data of all three studies (i.e., the pilot study, study 1, and study 2).
+We will fit different models for environmental unpredictability and violence exposure as predictors (using the respective composite scores) and for perceptual input and interference as dependent variables.
+Each model will additionally contain the following covariates: study number (...), whether participants rescaled their screen at the start of the cognitive tasks (yes or no, sum-coded), whether participants experienced interruptions during the tasks (yes or no, sum-coded), and whether people exited full-screen mode during the experiment (yes or no, sum-coded).
+Note that the latter three covariates were included as arbitrary decisions in the multiverse analyses for the pilot study and study 1.
+However, as we found that they substantially altered the results, we decided to reclassify them as non-arbitrary decisions and include them as covariates instead.
+To address the [second primary aim](#primary), we will fit the same model as described above for the first primary aim, but with different the difference score of the Global-Local drift rate as the dependent variable.
 
@@
 
-Online experiments come at the trade-off of having less experimental control over the way in which participants complete the experiment and over the environment in which they do so.
-It is largely unclear which factors affect performance and how strong these effects are.
-We used multiverse analysis for all main analysis to assess the robustness of the results against various environmental factors and situations during the experiment.
-We identified seven arbitrary analytic decisions, including or excluding 1) participants who had a recaptcha score below 0.5 (possibly indicating bots); 2) participants who did not rescale their screen at the start of the experiment (see the [procedure section](#procedure)); 3) participants who did not enter fullscreen mode prior to starting the Flanker Task; 4) participants who exited fullscreen mode at any point during the Flanker Task; 5) participants who indicated high levels of noise in their environment; indicated extreme interruptions during the experiment; 7) trials with RTs > 3.2 SD (within subjects).
-
+We will conduct a multiverse analysis for all primary analyses.
+We identified seven arbitrary analytic decisions, including or excluding 1) participants who had a recaptcha score below 0.5 (possibly indicating bots); 2) participants who did not enter fullscreen mode prior to starting the cognitive tasks; 3) participants who indicated high levels of noise in their environment.
 For each analysis, we report the median $\beta$, 95% confidence intervals, proportion of *p*-values < .05 across all analytic decisions.
 For the primary analyses, we used a bootstrapping technique to compute overall *p*-values to assess whether the obtained median $\beta$ is significantly larger than zero [@simonsohn_2020].
-
-### Primary analyses {#primary_plan}
-
-To address the [first primary aim](#primary) we pooled the Flanker data of the pilot study and the current study, using the standard condition of the current study.
-For the pooled effect of violence exposure on each of the DDM parameters, we ran initial linear models including violence exposure, study number (pilot study vs.
-current study, sum-coded) and their interaction as an independent variable to check whether the two studies were sufficiently similar.
-If the interaction was non-significant, we ran a final model version including only violence exposure to estimate the main effect.
-The pooled effect of violence exposure on raw RTs was assessed through linear mixed models including a random intercept per participant.
-Initial models included violence exposure, congruency (congruent vs.
-incongruent, sum-coded as -1 and 1), the violence exposure X congruency interaction, study number (pilot study vs current study, sum-coded), and the violence_exposure X study number interaction.
-We estimated a final model without study number if the violence exposure X study number interaction was non-significant.
-
-To address the [second primary aim](#primary), we analyzed the effect of violence exposure and Flanker condition type (within the current study only) on Flanker performance using linear mixed effects models with a random intercept per participant.
-The main dependent variables were mean RTs and the SSP parameters: Perceptual input (*p*), boundary separation (*a*), non-decision time (*t0*), initial attention width (*sd~a~*), attention shrinking rate (*rd*) and the interference effect (*SD~a~*/*rd*).
-For each outcome measure, we ran two separate models: One comparing the standard condition with the enhanced condition, and one comparing the standard condition with the degraded condition.
-In both models, condition was dummy-coded using the standard condition as the reference group.
-
-### Factor structure of unpredictability {#efa}
-
-The included unpredictability measures contain items that vary in timescale, ranging from features of the childhood environment that might have been unpredictable on a daily basis (e.g., "things were often chaotic in my house") to sources of unpredictability that typically unfold on a timescale of weeks or months (e.g., "At least one of my parents changed jobs frequently").
-Since attention is involved in information processing on a timescale of seconds to minutes, we expect that attention styles should be more strongly related to sources of unpredictability that unfold on a similar timescale.
-However, it is unclear whether current retrospective measures of unpredictability are able to differentiate between different timescales.
-In addition, it might be the case that items of unpredictability on a longer timescale are good proxies for unpredictability on a a more daily timescale.
-We conducted an exploratory factor analysis (EFA) to address these issues.
-
-EFA was used to find common latent factors underlying the unpredictability/household chaos measures: perceived unpredictability, QUIC, and CHAOS, stability of the family and social environment, and the objective measures of unpredictability.
-The number of factors to retain was based on parallel analysis, with the added requirement that each factor was composed of at least five items that had their strongest loading on that particular factor.
-Factor loadings above 0.32 were considered meaningful (Tabachnick & Fidell, 2014).
-We anticipated the factors to be correlated substantially, and therefore planned to use oblimin rotation.
 

### 2023-04-11 preregistrations/3_study2/materials/flanker/0_flanker_setup.js

@@ -1,0 +1,61 @@
+//------------------------- Functions
+
+var location_stim = function(up, down){
+  
+  // Present flanker stimuli either at the top or bottom of the screen
+  var html = "<style>" +
+              "divbottom{display:flex; justify-content: center; align-items: flex-end; height:300px}" +
+              "divtop{display:flex; justify-content: center; align-items: flex-start; height:300px}" +
+             ".topflanker{font-size:40px;}" +
+             ".bottomflanker{font-size:40px;}" +
+             "</style>";
+             
+  if(up != null) {
+    html += "<divtop>";
+    html += "<div class = 'topflanker'>";
+    html += up;
+    html += "</div></div>";
+  }
+  
+  if(down != null) {
+    html += "<divbottom>";
+    html += "<div class = 'bottomflanker'>";
+    html += down;
+    html += "</div></div>";
+
+  }
+  
+  return html;
+};
+  
+  
+  
+//------------------------- Stimuli
+  
+  // Flanker stimuli
+  var congruent_left = "&larr;&larr;&larr;&larr;&larr;"
+  var congruent_right = "&rarr;&rarr;&rarr;&rarr;&rarr;"
+  var incongruent_left = "&rarr;&rarr;&larr;&rarr;&rarr;"
+  var incongruent_right = "&larr;&larr;&rarr;&larr;&larr;"
+
+
+  var flanker_stimuli = [
+    {stimulus: congruent_left},
+    {stimulus: congruent_right},
+    {stimulus: incongruent_left},
+    {stimulus: incongruent_right},
+  ]
+  
+  
+  // Fixation cross
+  var flanker_fixation = {
+  type: jsPsychHtmlKeyboardResponse,
+  stimulus: '<div style="font-size:60px;">+</div>',
+  choices: 'NO_KEYS',
+  trial_duration: 1000,
+  data: {
+    variable: 'fixation'
+  }
+}
+  
+

### 2023-04-11 preregistrations/3_study2/materials/flanker/1_flanker_instructions.js

@@ -1,0 +1,132 @@
+//-------------------- Welcome
+var flanker_welcome = {
+  type: jsPsychInstructions,
+  pages: [
+    "Welcome to the <b>Flanker</b> game!"
+  ],
+  show_clickable_nav: true,
+  allow_backward: true,
+  key_forward: -1,
+  key_backward: -1,
+  button_label_next: "continue",
+  data: {variable: 'welcome', task: "flanker_practice"}
+};
+
+//-------------------- Instructions
+var flanker_instructions = {
+  type: jsPsychInstructions,
+  pages: [
+    "<p style = 'text-align: center;'>"+ 
+      "In this game, you will see five arrows like the ones below.<br><br><br>" +
+      "<div style = 'font-size: 30px'>&larr;&larr;&larr;&larr;&larr;</div><br><br><br>" +
+      "Your job is to decide which way the <strong>middle arrow</strong> is pointing.<br><br><br>",
+      
+     "<p style = 'text-align: center;'>"+ 
+      "Sometimes, all the arrows point the <strong>same</strong> way.<br><br><br>" +
+      "<div style = 'font-size: 30px'>&larr;&larr;&larr;&larr;&larr;</div><br><br><br>",
+      
+     "<p style = 'text-align: center;'>"+ 
+      "Other times, the arrows point a <strong>different</strong> way.<br><br><br>" +
+      "<div style = 'font-size: 30px'>&larr;&larr;&rarr;&larr;&larr;</div><br><br><br>",  
+      
+      "<p style = 'text-align: center;'>"+ 
+      "You should <i>always</i> look at the <strong>middle arrow</strong> and ignore the others.<br><br>" +
+      
+      "<div style = 'float: left;'>If it points LEFT<br>press the LEFT (&larr;) key.</div>" +
+      "<div style = 'float: right;'>If it points RIGHT<br>press the RIGHT (&rarr;) key.</div><br><br><br><br>" + 
+      
+      "In the example below, the middle arrow points left,<br>" +
+      "so you would press the left key.<br><br>" +
+      "<div style = 'font-size: 30px'>&rarr;&rarr;&larr;&rarr;&rarr;</div></p><br><br><br>",
+      
+     "<p style = 'text-align: center;'>"+ 
+      "Try to respond as fast and as correctly as possible.<br><br>" +
+      "Click 'continue' to practice this game<br><br><br>"        
+  ],
+  show_clickable_nav: true,
[…]

### 2023-04-11 preregistrations/3_study2/materials/flanker/2_flanker_procedure.js

@@ -1,0 +1,45 @@
+var flanker_present_arrows = {
+  type: jsPsychHtmlKeyboardResponse,
+  stimulus: function(){
+    return jsPsych.timelineVariable('stim')
+  },
+  choices: ['ArrowLeft', 'ArrowRight'],
+  data: {
+    variable: 'flanker_test',
+    task: 'flanker',
+    location: function(){
+      return jsPsych.timelineVariable('location')
+    },
+    stimtype: function(){
+      return jsPsych.timelineVariable('stimtype')
+    },
+    correct_response: function(){
+      return jsPsych.timelineVariable('correct_response')
+    }
+  },
+  on_finish: function(data) { {
+    if(jsPsych.pluginAPI.compareKeys(data.response, jsPsych.timelineVariable('correct_response', true))) {
+      data.correct = true;
+    } else {
+      data.correct = false;
+    }
+  }
+  }
+};
+
+
+var flanker_test_procedure = {
+  timeline: [flanker_fixation, flanker_present_arrows],
+  timeline_variables: [
+    {location: 'top',    correct_response: 'ArrowLeft', stimtype: 'congruent_left',    stim: location_stim(up='&larr;&larr;&larr;&larr;&larr;', down=null)},
+    {location: 'top',    correct_response: 'ArrowRight', stimtype: 'congruent_right',   stim: location_stim(up='&rarr;&rarr;&rarr;&rarr;&rarr;', down=null)},
+    {location: 'top',    correct_response: 'ArrowLeft', stimtype: 'incongruent_left',  stim: location_stim(up='&rarr;&rarr;&larr;&rarr;&rarr;', down=null)},
+    {location: 'top',    correct_response: 'ArrowRight', stimtype: 'incongruent_right', stim: location_stim(up='&larr;&larr;&rarr;&larr;&larr;', down=null)},
+    {location: 'bottom', correct_response: 'ArrowLeft', stimtype: 'congruent_left',    stim: location_stim(up=null, down='&larr;&larr;&larr;&larr;&larr;')},
+    {location: 'bottom', correct_response: 'ArrowRight', stimtype: 'congruent_right',   stim: location_stim(up=null, down='&rarr;&rarr;&rarr;&rarr;&rarr;')},
[…]

### 2023-04-11 preregistrations/3_study2/materials/global_variables.js

@@ -4,7 +4,7 @@
 
 // At start of experiment: Make sure the size of stimulus presentation is the same for all participants.
 var resize_screen = {
-  type: 'resize',
+  type: jsPsychResize,
   item_width: 3 + 3/8,
   item_height: 2 + 1/8,
   prompt: "<p>Before we start, it is important that you follow the steps below carefully.<br>" +
@@ -22,13 +22,13 @@ var resize_screen = {
 }};
 
 var fullscreenmode = {
-  type: 'fullscreen',
+  type: jsPsychFullscreen,
   fullscreen_mode: true
 };
 
 // Remove cursor during cognitive tasks
 var cursor_off = {
-    type: 'call-function',
+    type: jsPsychCallFunction,
     func: function() {
         document.body.style.cursor= "none";
     }
@@ -37,7 +37,7 @@ var cursor_off = {
 
 // Make cursor visible again in between cognitive tasks or when a button response is required.
 var cursor_on = {
-    type: 'call-function',
+    type: jsPsychCallFunction,
     func: function() {
         document.body.style.cursor= "auto";
     }
@@ -46,7 +46,7 @@ var cursor_on = {
 
 // Task feedback during the practice trials.
 var feedback = {
-  type: 'html-keyboard-response',
+  type: jsPsychHtmlKeyboardResponse,
   stimulus: function(){
     
     var last_trial_rt = jsPsych.data.getLastTrialData().values()[0].rt;
@@ -61,7 +61,7 @@ var feedback = {
         return "<p style = 'color:red;font-size:40px'>Incorrect!</p>"; 
       }}},
   trial_duration: 2000,
-  choices: jsPsych.NO_KEYS,
+  choices: "NO_KEYS",
   data: {
     variable: 'feedback'
   }
@@ -70,7 +70,7 @@ var feedback = {
 
 // End of Cognitive task part of the experiment.
 var cognitive_tasks_end = {
-  type: "html-button-response",
+  type: jsPsychHtmlButtonResponse,
   stimulus: 
   "Great job!<br><br>" +
   "You have finished the first part of the experiment.<br><br>" +

### 2023-04-11 preregistrations/3_study2/materials/globallocal/0_globallocal_setup.js

@@ -1,0 +1,53 @@
+var preload_globloc = {
+    type: jsPsychPreload,
+    images: [
+      'globallocal/img/black_e_of_f.png',
+      'globallocal/img/black_e_of_p.png',
+      'globallocal/img/black_e_of_t.png',
+      'globallocal/img/black_h_of_f.png',
+      'globallocal/img/black_h_of_p.png',
+      'globallocal/img/black_h_of_t.png',
+      'globallocal/img/black_f_of_e.png',
+      'globallocal/img/black_f_of_h.png',
+      'globallocal/img/black_p_of_e.png',
+      'globallocal/img/black_p_of_h.png',
+      'globallocal/img/black_t_of_e.png',
+      'globallocal/img/black_t_of_h.png'
+      ]
+}
+         
+var Ge_Lf  = "<img src='globallocal/img/black_e_of_f.png' height=600px>";
+var Ge_Lp  = "<img src='globallocal/img/black_e_of_p.png' height=600px>";
+var Ge_Lt  = "<img src='globallocal/img/black_e_of_t.png' height=600px>";
+var Gf_Le  = "<img src='globallocal/img/black_f_of_e.png' height=600px>";
+var Gf_Lh  = "<img src='globallocal/img/black_f_of_h.png' height=600px>";
+var Gh_Lf  = "<img src='globallocal/img/black_h_of_f.png' height=600px>";
+var Gh_Lp  = "<img src='globallocal/img/black_h_of_p.png' height=600px>";
+var Gh_Lt  = "<img src='globallocal/img/black_h_of_t.png' height=600px>";
+var Gp_Le  = "<img src='globallocal/img/black_p_of_e.png' height=600px>";
+var Gp_Lh  = "<img src='globallocal/img/black_p_of_h.png' height=600px>";
+var Gt_Le  = "<img src='globallocal/img/black_t_of_e.png' height=600px>";
+var Gt_Lh  = "<img src='globallocal/img/black_t_of_h.png' height=600px>";
+
+
+var feedback = {
+  type: jsPsychHtmlKeyboardResponse,
+  stimulus: function(){
+    
+    var last_trial_rt = jsPsych.data.getLastTrialData().values()[0].rt;
+    var last_trial_correct = jsPsych.data.get().last(1).values()[0].correct;
+    
+    if(last_trial_rt > 4000){
+      return "<p style = 'color:red;font-size:40px'>Too slow!</p>"; 
+    } else {
[…]

### 2023-04-11 preregistrations/3_study2/materials/globallocal/1_globallocal_instructions.js

@@ -1,0 +1,143 @@
+//-------------------- Welcome
+var globloc_welcome = {
+  type: jsPsychInstructions,
+  pages: [
+    "Welcome to the <strong>GLOBAL/LOCAL TASK!</strong.<br><br><br><br><br>"
+  ],
+  show_clickable_nav: true,
+  allow_backward: true,
+  key_forward: -1,
+  key_backward: -1,
+  button_label_next: "continue",
+  button_label_previous: "go back",
+  data: {variable: 'welcome', task: "globloc_practice"}
+};
+
+//-------------------- Instructions
+var globloc_instructions = {
+  type: jsPsychInstructions,
+  pages: [
+    "<p style = 'text-align: center;'>" + 
+      "In this game, you will see pictures of <strong>big letters</strong> that are made up of <strong>small letters</strong>.<br><br>" +
+      "The pictures will always contain an <strong>'H'</strong> or an <strong>'E'</strong>. These are the <strong>TARGET LETTERS</strong>.<br><br>" +
+      "For example, you might see a <strong>big 'H'</strong> that is made up of <strong>small 'P's</strong>:<br><br><br>" +
+      "<img height = 400 src = globallocal/img/black_h_of_p.png></img><br><br>",
+      
+      "Other times, you might see a <strong>big 'F'</strong> that is made up of <strong>small 'E's</strong>:<br><br><br>" +
+      "<img height = 400 src = globallocal/img/black_f_of_e.png></img><br><br>",
+      
+    "<p style = 'text-align: center;'>" + 
+      "Your job is to find the target letters (<strong>'H'</strong> or <strong>'E'</strong>) as quickly as possible<br>and indicate whether you found it as the <strong>BIG LETTER</strong> or <strong>SMALL LETTER</strong>.",
+      
+      //Page 5 
+    "<div style = 'float: left; padding-right: 150px'>If the target is BIG<br>press the 'G' key.<br><br><img height = 400 src = globallocal/img/black_e_of_t.png></img></div>" +
+    "<div style = 'float: right; padding-left: 150px'>If the target is SMALL<br>press the 'L' key.<br><br><img height = 400 src = globallocal/img/black_f_of_h.png></img></div>" +
+
+    "<p style = 'text-align: center;'>" +
+      "Remember, try to be as FAST and ACCURATE as possible."
+
[…]

### 2023-04-11 preregistrations/3_study2/materials/globallocal/2_globallocal_procedure.js

@@ -1,0 +1,101 @@
+// Fixation cross
+var fixation = {
+  type: jsPsychHtmlKeyboardResponse,
+  stimulus: '<div style="font-size:60px;">+</div>',
+  choices: "NO_KEYS",
+  trial_duration: 500,
+  data: {
+    variable: 'fixation'
+  }
+};
+
+var globloc01 = {
+  type: jsPsychCategorizeHtml,
+  choices: ['g','l'],
+  correct_text: "",
+  incorrect_text: "",
+  feedback_duration: 500,
+  show_stim_with_feedback: false,
+  stimulus: function(){return(jsPsych.timelineVariable('stimulus'))},
+  timeline: [
+{stimulus: Ge_Lp, key_answer: 'g', data: {rule: 'global', type: 'first', variable: 'globloc_01', task: 'globloc'}},
+{stimulus: Gp_Lh, key_answer: 'l', data: {rule: 'local', type: 'switch', variable: 'globloc_01', task: 'globloc'}},
+{stimulus: Gt_Lh, key_answer: 'l', data: {rule: 'local', type: 'repeat', variable: 'globloc_01', task: 'globloc'}},
+{stimulus: Gh_Lp, key_answer: 'g', data: {rule: 'global', type: 'switch', variable: 'globloc_01', task: 'globloc'}},
+{stimulus: Ge_Lf, key_answer: 'g', data: {rule: 'global', type: 'repeat', variable: 'globloc_01', task: 'globloc'}},
+{stimulus: Gh_Lt, key_answer: 'g', data: {rule: 'global', type: 'repeat', variable: 'globloc_01', task: 'globloc'}},
+{stimulus: Gt_Le, key_answer: 'l', data: {rule: 'local', type: 'switch', variable: 'globloc_01', task: 'globloc'}},
+{stimulus: Gh_Lp, key_answer: 'g', data: {rule: 'global', type: 'switch', variable: 'globloc_01', task: 'globloc'}},
+{stimulus: Gf_Le, key_answer: 'l', data: {rule: 'local', type: 'switch', variable: 'globloc_01', task: 'globloc'}},
+{stimulus: Gt_Le, key_answer: 'l', data: {rule: 'local', type: 'repeat', variable: 'globloc_01', task: 'globloc'}},
+{stimulus: Gf_Lh, key_answer: 'l', data: {rule: 'local', type: 'repeat', variable: 'globloc_01', task: 'globloc'}},
[…]

### 2023-04-11 preregistrations/3_study2/materials/globallocal/scripts/trialmaker.R

@@ -1,0 +1,144 @@
+library(tidyverse)
+library(glue)
+set.seed(486)
+
+n_block_trials <-  32
+
+stim_vector <- c('Ge_Lf', 'Ge_Lp', 'Ge_Lt', 'Gf_Le', 'Gf_Lh', 
+'Gh_Lf', 'Gh_Lp', 'Gh_Lt', 'Gp_Le', 'Gp_Lh', 'Gt_Le', 
+'Gt_Lh')
+
+# stimulus set 1
+trials01 <- tibble(
+  type     = c('first', sample(c(rep('repeat',n_block_trials/2), rep('switch',n_block_trials/2)), size = n_block_trials, replace = F)),
+  rule     = c('global', rep(NA, n_block_trials)),
+  variable = "globloc_01",
+  task     = "globloc",
+  key_answer = NA
+) 
+
+# Generate repeat or switch trials
+n = 1
+while(n<=n_block_trials){
+  trials01 <- trials01 |> 
+    mutate(
+      rule = case_when(
+        is.na(rule) & type == "repeat" & lag(rule, n=1) == 'global' ~ 'global',
+        is.na(rule) & type == "repeat" & lag(rule, n=1) == 'local' ~ 'local',
+        is.na(rule) & type == "switch" & lag(rule, n=1) == 'global' ~ 'local',
+        is.na(rule) & type == "switch" & lag(rule, n=1) == 'local' ~ 'global',
+        TRUE ~ rule
+      )
+    )
+  n = n+1
+}
+
+
+trials01 <- trials01 |> 
+  mutate(
+    stimulus = case_when(
+      rule == 'global' ~ sample(str_subset(stim_vector, "(Ge|Gh)"), size = 33, replace = T), 
+      rule == 'local' ~ sample(str_subset(stim_vector, "(Le|Lh)"), size = 33, replace = T)),
+    key_answer = case_when(
+      rule == 'global' ~ 's',
+      rule == 'local'  ~ 'l'
+      
+    )
+  )
+
+  
+
+
+# stimulus set 2
+trials02 <- tibble(
+  type     = c('first', sample(c(rep('repeat',n_block_trials/2), rep('switch',n_block_trials/2)), size = n_block_trials, replace = F)),
+  rule     = c('global', rep(NA, n_block_trials)),
+  variable = "globloc_01",
+  task     = "globloc",
+  key_answer = NA
+) 
+
+# Generate repeat or switch trials
+n = 1
+while(n<=n_block_trials){
[…]

### 2023-04-11 preregistrations/3_study2/scripts/power.R

@@ -1,0 +1,58 @@
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(future)
+library(furrr)
+
+set.seed(43876)
+
+# Simulation settings -----------------------------------------------------
+
+p_mean            <- 0.519
+p_sd              <- 0.157
+interference_mean <- 111.387
+interference_sd   <-  58.165
+
+
+# 1. Pooled Main Effects --------------------------------------------------
+
+n    <- c(300,350,400,450,500, 600, 1500, 1600)
+beta <- c(0.05, 0.1)
+
+plan(multisession, workers = 5)
+
+power <- furrr::future_map_dfr(1:500, function(x){
+  furrr::future_map_dfr(n, function(y){
+    furrr::future_map_dfr(beta, function(z){
+      
+      # Simulate data
+      sim_data <- 
+        tibble(
+          id = 1:y,
+          adversity = rnorm(n=y, mean = 0, sd = 1) |> scale() |> as.numeric(),
+          p_flanker = p_mean + (adversity * z) + rnorm(y, 0, 2*p_sd) 
+        )
+      
+      # Fit model
+      lm(data = sim_data, p_flanker ~ adversity) |> 
+        broom::tidy() |> 
+        filter(term == "adversity") |> 
+        mutate(
+          sim  = x,
+          n    = y,
+          beta = z
+        )
+    },.options = furrr_options(seed = TRUE))
+  },.options = furrr_options(seed = TRUE))
+},.options = furrr_options(seed = TRUE))
+
+
+power |> 
+  group_by(n,beta) |> 
+  summarise(
+    p = sum(p.value < .05)/n()*100,
+    eff = mean(estimate),
+    sd = sd(estimate)
+  )
+

### 2023-05-04 preregistrations/3_study2/preregistration.Rmd
intermediate version of preregistration for study 2

@@
 
-load(here("data", "2_study1", "0_self_report_raw.Rdata"))
+load(here("data", "3_study2", "0_self_report_raw.Rdata"))
 ```
 
-Generally speaking, the results of the first two studies were not in line with our initial predictions about a present-oriented attention style.
-Although we expected such a style to lead to faster speed of perceptual processing on attention tasks, we generally found the opposite pattern.
-One reason for this might be that a present-oriented attention style leads people from adversity to process information more holistically, which would lower the depth of perceptual processing of any individual stimulus.
-Another related reason might be that an external, present-oriented attention style extends beyond the computer screen to all of their immediate environment.
-Both of these are potential mechanistic explanations for a lowered quality of perceptual processing that would be in line with a specialized attention style.
-In study 2, we aimed to replicate the broader findings from study 1 (lowered perceptual input on the Flanker Task but no differences in interference) and to investigate if and how the lower quality of perceptual processing was associated with a more holistic style of attention.
+Initially we predicted that higher levels of adversity---especially violence exposure---would be associated with a present-oriented attention style.
+We expected such an attention style to be associated with faster attention to subtle changes and peripheral information, but also with lowered inhibition.
+Generally speaking, the results of the first two studies were not in line with these predictions.
+Instead, the Flanker findings suggest that both violence exposure and environmental unpredictability are associated with lowered perceptual input, but is not associated with changes in attention.
+These findings are intriguing as they suggest that performance differences are not driven by differences in interference control---which is typically assumed.
+While interesting, these findings so far leave open the question why perceptual input is negatively associated with perceptual input.
+
+First, it may indicate a deficit in processing information.
+Note that this explanation would be different from typical interpretations of lowered Flanker performance, which typically equate lower performance (i.e., longer RTs) with lowered inhibition ability.
+Instead, a deficit in processing information is a different pathway to lowered performance: it implies that people from adversity are completing the task with lower-quality information---akin to when the arrows would be more blurry.
+Alternatively, the difference in perceptual input may not be a cognitive deficit per se, but instead could be a signature of a difference in processing style.
+People from adversity  may process information more holistically, focusing more on the whole instead of individual pieces of information.
+On a task like the Flanker, this would lower the depth of perceptual processing of any individual stimulus, thus potentially explaining the pattern of results in the previous two studies.
+In study 2, our aim is to replicate the central Flanker findings of the pilot study and study 1 (lowered perceptual input but no differences in interference), and to investigate whether adversity would be associated with a stronger tendency to process information holistically on a Global-Local Task.
 
@@
 
-Participants will be excluded if they 1) do not complete the full study or both cognitive tasks, 2) miss both attention check items or if they have suspicious response patterns (e.g., consistently endorsing high response options even when some items were reverse coded), 3) have a screen height < 700 pixels or a screen height that is bigger than the screen width to ensure the tasks were completed on a laptop or desktop pc, 4) exit full-screen mode and/or engaged with other broswer tabs *during* the cognitive tasks (but not while reading instructions or while taking breaks in between blocks), 5) do not perform above chance on either the Flanker Task or the Global-Local Task (based on a binomial distribution using a probability of 97.5%).
+Participants will be excluded if they 1) do not complete the full study or both cognitive tasks, 2) miss both attention check items or if they have suspicious response patterns (e.g., consistently endorsing high response options even when some items were reverse coded), 3) have a screen height < 700 pixels or a screen height that is bigger than the screen width to ensure the tasks were completed on a laptop or desktop pc, 4) exit full-screen mode and/or engaged with other browser tabs *during* the cognitive tasks (but not while reading instructions or while taking breaks in between blocks), 5) do not perform above chance on either the Flanker Task or the Global-Local Task (based on a binomial distribution using a probability of 97.5%).
 
@@
 
+We provide brief summaries of measures that were unchanged between study 1 and the current study 2.
+See the appendix for a full overview of all questionnaires.
+
 ### Flanker Task {#flanker}
 
-The Flanker Task was identical to the standard version used in study 1. 
+The Flanker Task is identical to the standard version used in study 1. 
 It was programmed in JsPsych 7.3.2 [@deleeuw_2015]. 
-Participants first completed eight practice trials and next completed 64 test trials in a single block.
+Participants first complete eight practice trials and next completed 64 test trials in a single block.
 
@@
 
+The Global-Local Task is a measure of global-local processing [@navon_1977].
+Many different versions of the task exist in the literature.
+One key dimension is whether the tasks measures focused attention (by cueing attention towards the global or local level prior to stimulus presentation) or divided attention (by having participants search for a target on both levels) [@lee_2023].
+Here, we use a version measuring divided attention, which allows measuring a natural preference for either global or local processing [@hakim_2016; lee_2023; @mckone_2010].
+
+Participants are presented with images of big letters (the global level) that are comprised of small letters (the local level)---so-called Navon images [@navon_1977].
+On each trial, participants are instructed to find one of two target letters---an 'E' or 'H'---and indicate whether the target letter was present on the global or local letter by pressing 'g' or 'l' on their keyboard, respectively.
+Stimuli consisted of all combinations of the letters 'T', 'F', 'P', 'L', 'H', and 'E', with 'H' and 'E' present in each stimulus.
+Each stimulus was 600 pixels high and 395 pixels wide and comprised of seven local letters vertically and five local letters horizontally. 
+The global and local level never contained the same letter.
+Participants first completed eight practice trials, after which they completed an additional 64 test trials.
+The main outcome measure is mean response time and accuracy for global targets and local targets separately.
+
 ### Current state {#state}
 
-We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [STAI-S; @spielberger_1999].
-The STAI-S contains 20 short items measuring current anxiety (e.g., "I feel tense"; See [Table S1](#appendix) for an overview of all items).
-Participants rated each item on a scale of 1 (not at all) to 4 (very much so).
-An overall state anxiety variable was computed by averaging across the 20 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-
-In addition, participants answered five questions relating to specific states: "Are you currently sick?" (rated as yes or no); "Have you eaten a full meal today?" (rated as yes or no); "How hungry do you feel right now?" (rated from 1 (not at all) to 5 (very hungry)); "How well did you sleep last night?" (rated from 1 (very poorly) to 5 (very well)); "How rested or refreshed did you feel when you woke up this morning?" (rated from 1 (not at all) to 5 (very rested)).
-We computed an overall sleep deprivation composite by standardizing and averaging across the two unweighted sleep-related items (*M* = `r #TBD `, *SD* = `r #TBD `).
+We will assess state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [Stai-S; @speilberger_1999] (See [Table S1](#appendix)).
+ An overall state anxiety variable was computed by averaging across the 20 unweighted items.
 
@@
 
-Violence exposure was measured using the Neighborhood Violence Scale [NVS; @frankenhuis_2018; @frankenhuis_deVries_2020] and two items assessing exposure to physical fights before age 13.
-The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up"; See [Table S2](#appendix) for an overview of all items).
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
-The items of the NVS were averaged together (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-Similarly, we averaged the scores on the two fighting items together.
-Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average (*r* = `r #TBD `).
+Violence exposure will be measured using two measures: 1) the Neighborhood Violence Scale [NVS; @frankenhuis_2018; @frankenhuis_deVries_2020] (see [Table S2](#appendix)) and 2) two items assessing exposure to physical fights before age 13 ("Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?").
+A violence exposure composite score will be calculated as an unweighted average of the mean NVS score (standardized) and the mean of the fighting items (standardized).
 
@@
 We distinguish between subjective and objective measures of environmental unpredictability.
-We distinguish between subjective and objective measures of environmental unpredictability.
-Subjective unpredictability will be measured as an unweighted average of three scales: 1) A scale of perceived childhood unpredictability used in previous research (see [Table S3]) [@mittal_2015; @young_2018]; 2) An adapted version of the Confusion, Hubbub and Order Scale [CHAOS; @matheny_1995] (see [Table S5](#appendix)); 3) An adapted version of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019] (see [Table S4](#appendix)).
+Subjective unpredictability will be measured as an unweighted average of three scales: 1) A scale of perceived childhood unpredictability used in previous research (see [Table S3](#appendix)) [@mittal_2015; @young_2018]; 2) An adapted version of the Confusion, Hubbub and Order Scale [CHAOS; @matheny_1995] (see [Table S5](#appendix)); 3) An adapted version of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019] (see [Table S4](#appendix)).
 Objective unpredictability will be measured as an unweighted average of four items relating to experiences prior to age 13: 1) number of residential changes, 2) number of male and female romantic partners of a caregiver besides the other primary caregiver (measured separately; values > 6 were given a value 6 to prevent extreme outliers), 4) self-reported stability of the family and social environment across four dimensions: economic status, family environment, childhood neighborhood environment, and childhood school environment (rated between 1 (the same all the time) and 5 (constant and rapid changes)).
@@
 We will measure attentional style using the Attentional Style Questionnaire [ASQ; @calster_2018].
-The ASQ measures self-reported attentional style, with seven items
+The ASQ measures self-reported attentional style, with seven items asking about the participant's propensity for internally oriented attention (e.g., "During an activity, unrelated mmental images and thoughts come to my mind") and seven items about externally oriented attention (e.g., "I am easily drawn to new stimuli (for example, voices of people passing by, as sound in the house, ...) that are not relevant to a task I am doing").
+Where necessary, items were recoded in such a way that they reflected *distractibility* by internal and external stimuli, respectively, with higher scores reflecting a higher degree of distractibility.
+We will compute unweighted averages separately for internally oriented attention and externally oriented attention.
 
@@
 Posterior samples of all three chains will be combined, resulting in a posterior sample of 3,000 samples. 
-The main parameter of interest is the drift rate, more specifically, the difference between drift rates (drift rate~global~ - drift rate~local~).
+The main parameters of interest are the two drift rates of the global and local target conditions.
 
@@
 We will fit different models for environmental unpredictability and violence exposure as predictors (using the respective composite scores) and for perceptual input and interference as dependent variables.
-Each model will additionally contain the following covariates: study number (...), whether participants rescaled their screen at the start of the cognitive tasks (yes or no, sum-coded), whether participants experienced interruptions during the tasks (yes or no, sum-coded), and whether people exited full-screen mode during the experiment (yes or no, sum-coded).
+Each model will additionally contain the following covariates: (1) study number (pilot study, study 1, or study 2; sum-coded), (2) whether participants rescaled their screen at the start of the cognitive tasks (yes or no; sum-coded), (3) whether participants experienced interruptions during the tasks (yes or no; sum-coded), and (4) whether people exited full-screen mode during the experiment (yes or no; sum-coded).
 Note that the latter three covariates were included as arbitrary decisions in the multiverse analyses for the pilot study and study 1.
 However, as we found that they substantially altered the results, we decided to reclassify them as non-arbitrary decisions and include them as covariates instead.
-To address the [second primary aim](#primary), we will fit the same model as described above for the first primary aim, but with different the difference score of the Global-Local drift rate as the dependent variable.
+To address the [second primary aim](#primary), we will fit separate linear mixed effects models for environmental unpredictability and violence exposure with drift rate as the dependent variable and adversity type, task condition, and their interaction as independent variables.
+The models will contain a random intercept for participants, and contain the same covariates as described above.
 

### 2023-05-04 manuscript/manuscript.Rmd
Manuscript pilot and study 1

---
bibliography: references.bib
csl: apa.csl
output:
  officedown::rdocx_document:
    reference_docx: reference-doc.docx
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1
      header: .5
      footer: 0
      gutter: 0
    plots:
      align: center
      caption:
        style: Image Caption
        pre: 'Figure '
        sep: '. '
    tables:
      caption:
        style: Table Caption
        pre: 'Table '
        sep: '. '
---

```{r setup, include=FALSE}

# Load libraries
library(tidyverse)
library(officer)
library(flextable)
library(here)
library(pwr)
library(gt)

# set up chunk options
knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "!t", 
  out.extra = "",
  fig.show = "asis",
  message = FALSE,
  warning = FALSE
)

# set up flextable for tables
set_flextable_defaults(
  font.family = "Times", 
  font.size = 10,
  font.color = "black",
  line_spacing = 1,
  padding.bottom = 1, 
  padding.top = 1,
  padding.left = 1,
  padding.right = 1
)

# Source necessary objects
power_linear      <- read_csv("../data/1_pilot/simulation/power_linear_model.csv") %>% mutate(power = round(power, 0))
power_mixed       <- read_csv("../data/1_pilot/simulation/power_mixed_model.csv") %>% mutate(power = round(power, 0))
source("pilot_stage_objects.R") # Staged results of the pilot study
source("study1_stage_objects.R") # Staged results of study 1
source("pooled_stage_objects.R") # Pooled staged results
```

#### **Attention styles in harsh and unpredictable environments. An investigation using the Drift Diffusion Model**

<br>

#### Stefan Vermeent^1,2^, Ethan S. Young^1^, Jean-Louis van Gelder^2^, & Willem E. Frankenhuis^1,2^

#### ^1^ Department of Psychology, Utrecht University, Utrecht, The Netherlands

#### ^2^ Max Planck Institute for the Study of Crime, Security, and Law, Freiburg, Germany

\pagebreak

Experiencing childhood adversity can have detrimental effects on cognitive abilities [@hackman_2010; @ursache_2016]. 
However, the hidden talents approach suggests that people living in adversity might develop specific skills that help them navigate harsh and unpredictable environments [@ellis_2017; @frankenhuis_2013]. 
For example, recent work shows that growing up in stressful environments can enhance abilities such as working memory updating and attention shifting [@fields_2021; @mittal_2015; @nweze_2020; @young_2018; @young_2022].
However, the exact nature of lowered and improved task performance remains poorly understood.
For example, some studies suggest that specific types of adversity (e.g., threat, environmental unpredictability) are associated with specific abilities independent of the task setting or content [@fields_2021; @nweze_2020].
Others only find enhancement effects under stressful [@mittal_2015; @young_2018] or more ecologically relevant [@young_2022] testing conditions.
Despite partially mixed findings, the prediction is generally that specific types of adversity directly shape specific abilities.

Another possibility, however, is that cognitive enhancements and impairments are the result of a more general process. 
That is, adversity shapes different components of cognitive performance indirectly through an underlying cognitive style. 
For example, @frankenhuis_2016 argued that exposure to environmental unpredictability and threat might require a stronger present-orientation (as opposed to being focused on the future) in order to deal with unpredictable threats and benefit from fleeting rewards. 
A style that prioritizes information in the here-and-now could explain distinct patterns of performance, such as improved updating and shifting but lowered retrieval and attention control [@fields_2021; @mittal_2015; @nweze_2020; @young_2018].

Yet, before we can uncover an adversity-related cognitive style, we need a better understanding of the basic cognitive processes responsible for lowered (impairments) and improved (enhancements) abilities. 
Performance measures such as reaction times (RTs) or error rates are coarse indicators of performance. 
RTs on cognitive tasks are thought to reflect a number of sequentially unfolding processes.
When the effect of adversity exposure on cognitive performance is measured by looking at RTs, enhancements or impairments might be driven by any of these subprocesses. 
Formal cognitive models such as the Drift Diffusion Model [DDM\; @forstmann_2016; @ratcliff_1998; @ratcliff_2008; @ratcliff_2015; @wagenmakers_2009] may provide insight into the specific processes that are impaired or enhanced by adversity. 
The DDM accounts for the fundamental cognitive processes underlying relatively simple, binary decision-making processes. 
The model assumes that the decision-making process constitutes a noisy information accumulation process that continues until one of two decision boundaries (corresponding to the response options) is reached. 
As soon as the accumulation process reaches a decision boundary, the process terminates and a motor response is initiated (e.g., pressing a key on the keyboard). 
The DDM accounts for the full pattern of correct RTs, incorrect RTs, and proportion of errors.

The DDM models decision-making processes by estimating four parameters [@voss_2004]. 
The first is the **drift rate**, which indicates basic speed of information uptake as an information accumulation process.
Large drift rate values reflect more efficient processing (faster and more accurate).
The second is the **starting point** of the information accumulation process, which reflects a potential bias towards one of two response options.
Unless there is reason to believe there is a response bias, the starting point is usually fixed.
The third parameter is the **boundary separation**, which reflects the amount of information a person needs to make a decision.
Large decision boundaries indicate a more conservative response style (slower but more accurate), whereas smaller decision boundaries reflect more liberal responses (faster but less accurate).
The fourth and final parameter is the **non-decision time**, which captures all non-decision related cognitive processes initial stimulus encoding and initiating the motor response).

If people from adversity develop hidden talents, this should be reflected in specific DDM parameters. 
First and foremost, an enhanced cognitive ability would lead to more efficient information processing on tasks measuring that ability, which will be reflected in a higher drift rate (or the other way around in case of a cognitive impairment). 
Second, enhanced performance could also be (partly) driven by the ability to quickly detect relevant stimuli before the onset of the decision-making process. 
Even if the drift rate is similar across levels of adversity, faster detection and encoding of relevant stimuli would allow individuals to start accumulating information sooner. 
This would be reflected in the non-decision time. 
Finally, differences in performance across levels of adversity could be (partly) caused by the use of different strategies instead of by cognitive efficiency per se, for example, favoring speed over accuracy or vice versa. 
A tendency to adopt a specific strategy might be linked to individual differences in constructs like impulsivity. 
It is an open question whether performance differences driven by strategies should count as hidden talents [@young_2020].

The goal of the current work is twofold. 
First, we set out to assess how performance on basic attention tasks relates to two types of adversity: violence exposure and environmental unpredictability. 
We selected tasks that could relate to an underlying present-oriented cognitive style. 
Second, we leveraged DDM to better understand the nature of lowered and improved task performance. 
Towards these ends, we conducted three online studies (one comprehensive pilot study and two main studies) using an incremental preregistration approach (for all preregistrations, code and materials, see [https://github.com/stefanvermeent/attention_project/preregistrations](https://github.com/stefanvermeent/attention_project/preregistrations)).

The Introduction and Methods sections for each study were written as preregistrations before collecting the data. 
In a first comprehensive pilot study, we compared performance across three attention tasks (a Flanker task, a Cued Attention task, and a Change Detection task) as a function of childhood violence exposure and environmental unpredictability.
In study 1, we zoomed in further on the Flanker task to focus on some specific findings from the pilot study.
In study 2, ...
For each study we preregistered primary hypotheses and several exploratory analyses.
The main article addresses the primary hypotheses regarding the effects of violence exposure on attention performance and the exploratory hypotheses regarding the effects of environmental unpredictability on performance.
The supplemental materials provide an overview of the other exploratory analyses that were mentioned in the preregistrations.

# Pilot study

In the pilot study, we measured early-life exposure to violence and environmental unpredictability. 
In addition, participants completed three basic attention tasks (Flanker Task, Cued Attention Task, and Change Detection Task) that differed in the extent to which they measure or depend on an externally focused attention style.
The primary hypotheses focus on early-life exposure to violence. 
First, we expected that people with more exposure to violence during childhood would show enhanced performance compared to people from safe environments on tasks that required quickly detecting peripheral stimuli and detecting subtle changes (i.e., the Cued Attention Task and Change Detection Task). 
We expected that this effect would be explained by at least one of two DDM parameters: the drift rate and non-decision time.
Second, we expected that people with more exposure to violence during childhood would perform worse on tasks that required ignoring distracting peripheral stimuli (i.e., the Flanker Task). 
We expected that this effect would be at least partly explained by worse distractor inhibition, (operationalized using a Flanker-specific version of the DDM [@white_2011]; see [data analyses](#ddm_plan) for details).
Additional exploratory analyses focused on the association between environmental unpredictability and attention performance.

## Methods

### Participants {#participants}

Participants were 565 US-based individuals aged 18 between 18 and 30 recruited on Prolific Academic [https://www.prolific.co](https://www.prolific.co) (See Table \@ref(tab:table1) for demographics).
We decided on this age range to reduce the effect of age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 [@salthouse_2010]. 
The sample was balanced to include roughly 50% males. 
We used the MacArthur's ladder (included in Prolific's prescreening battery) for assessing perceived social-economic status (SES) to ensure about half of the sample came from lower SES backgrounds (a score of 4 or below).
Participants were eligible for the study if they were from the United States and if they spoke fluent English.

<br>

```{r table1, tab.id = "table1", tab.cap.style = "Table Caption", tab.cap="Demographic information for all studies."}
demographics_table
```
<br>

We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the optimal number of participants to include (more information including all simulation code on Github. 
We ran simulations for two scenarios: A linear regression model to test the effect of adversity (standardized) on attention performance (standardized) and a mixed regression model to test the interaction between adversity and task condition, including a random intercept for subjects. 
We ran simulations for a standardized $\beta$ of 0.10 and 0.15. 
In addition, we simulated the power to detect these effects with imperfectly recovered DDM parameters, assuming a recovery accuracy (i.e., correlation between data-generating parameter value and actually recovered parameter value) of *r* = 0.85.

In determining the final sample size, we weighed the simulation results together with our uncertainty about particular model parameters (mostly the fixed effects and sigma term for the mixed model) and the fact that this was a first, mostly exploratory pilot study. 
For the mixed model, we found that power was > .80 for the adversity X task condition interaction with *N* = 450 or more. 
For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require *N* = `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`. 
When DDM parameter recovery accuracy was *r* = .85, power was `r (power_linear %>% filter(n_subjects == 500, fixed_effect == 0.15, effect == "linear_recov_main_power") %>% pull(power))/100` for *N* = 500 and $\beta$ = 0.15. 
Power was `r (power_linear %>% filter(n_subjects == 500, fixed_effect == 0.1, effect == "linear_recov_main_power") %>% pull(power))/100` under the same scenario when $\beta$ was 0.10. 
Ultimately, we decided on sampling 550 participants with an anticipated final sample size of around 500.

We applied several exclusion criteria prior to analyzing the data.
First, we excluded participants who did not complete the full study and those who had incomplete data on any of the attention tasks (*N* = `r #TBD `). 
Second, we analyzed responses to the attention checks and reversed coded items in the questionnaire part of the experiment. 
We excluded participants if they missed both attention check items or if they had suspicious response patterns (e.g., consistently endorsing high response options even when some items were reverse coded) (*N* = `r #TBD `).

In addition, we screened the reaction times on each of the three attention tasks. 
For the Drift Diffusion analyses, it is important that each response is generated by a process of active information accumulation (i.e., a diffusion process, as opposed to guessing). 
To this end, trials with reaction times < 250 ms or > 3500 ms [@ratcliff_2015] were excluded from the analyses (*N* = `r #TBD `). 
Participants with more than 10 removed trials were excluded from the analyses (N = `r #TBD `).

The final sample consisted of `r nrow(pilot_data)` participants.

TODO: Describe additional non-preregistered exclusion decisions

### Cognitive measures {#cogmeasures}

The attention tasks were programmed in JsPsych version 3.6.1 [@deLeeuw_2015].

**Cued Attention Task.** The Cued Attention Task was an adaptation of the Posner task, which measures basic spatial attention speed [@posner_1980]. 
On each trial, a left- or right-pointing arrow was presented in one of eight random locations at a distance of 300 pixels from the center of the screen. 
Participants had to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard. 
On 50% of the trials, the arrow was preceded by a cue ('\*') in the exact same location (i.e., 'cued' trials). 
On the other 50% of the trials, the cue ('\*') was presented at the center of the screen (i.e., 'neutral' trials). 
Thus, on the cued trials, the location of the cue deterministically predicted the location of the arrow, whereas on the neutral trials the arrow always appeared in a different location.

Each trial started with a fixation cross presented at the center of the screen for 1000 ms. 
Then, the cue was presented for 250 ms either at the center of the screen or in the location where the arrow would appear next. 
Finally, the arrow was presented 250 ms after the onset of the cue and shown until a response was given. 
The Cued Attention Task began with eight practice trials (four cued and four neutral trials) in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red). 
After finishing the practice round, participants completed a single test block of 64 trials, consisting of two repetitions of all parameter combinations: arrow location (top center vs. top left vs. center left vs. bottom left vs. bottom center vs. bottom right vs. center right vs. top right) X arrow direction (left vs. right) X condition (cued vs. neutral). 
The main raw performance measures were RTs and accuracy for each condition (Cued: *M~RT~* = `r txt_ivs_dist_pilot$rt_cueing_cued$mean`s, *SD~RT~* = `r txt_ivs_dist_pilot$rt_cueing_cued$sd`; *M~accuracy~* = `r txt_ivs_dist_pilot$acc_cueing_cued$mean`, *SD~accuracy~* =  `r txt_ivs_dist_pilot$acc_cueing_cued$sd`; Neutral: *M~RT~* = `r txt_ivs_dist_pilot$rt_cueing_neutral$mean`s, *SD~RT~* = `r txt_ivs_dist_pilot$rt_cueing_neutral$sd`; *M~accuracy~* = `r txt_ivs_dist_pilot$acc_cueing_neutral$mean`, *SD~accuracy~* =  `r txt_ivs_dist_pilot$acc_cueing_neutral$sd`).

**Flanker Task.** The Flanker Task measures selective attention and response inhibition [@eriksen_1974]. 
On each trial of the Flanker task, participants were presented with a set of five arrows pointing either left or right. 
Their job was to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right. 
On 50% of the trials, the flanking arrows pointed in the same direction as the central arrow (i.e., congruent trials), and on the other 50% of the trials they pointed in the opposite direction (i.e., incongruent trials). 
The arrows were randomly presented in the top-half or bottom-half of the screen. 
This was done to prevent participants from rigidly fixating on the center of the screen, which might reduce the interfering effect of the flanking arrows.

Each trial started with a fixation cross presented at the center of the screen. 
After a delay of 1000ms, the arrows were presented either in the top- or bottom-half of the screen. 
The Flanker task began with eight practice trials in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red). 
After finishing the practice round, participants completed a single test block consisting of a total of 64 trials, consisting of eight repetitions of all parameter combinations: Arrow location (top vs. bottom) X central arrow direction (left vs. right) X condition: (congruent vs. incongruent). 
Participants did not receive performance feedback during the test block. 
The main raw performance measures were RTs and accuracy for each condition (Congruent: *M~RT~* = `r txt_ivs_dist_pilot$rt_flanker_congruent$mean`s, *SD~RT~* = `r txt_ivs_dist_pilot$rt_flanker_congruent$sd`; *M~accuracy~* = `r txt_ivs_dist_pilot$acc_flanker_congruent$mean`, *SD~accuracy~* =  `r txt_ivs_dist_pilot$acc_flanker_congruent$sd`; Incongruent: *M~RT~* = `r txt_ivs_dist_pilot$rt_flanker_incongruent$mean`s, *SD~RT~* = `r txt_ivs_dist_pilot$rt_flanker_incongruent$sd`; *M~accuracy~* = `r txt_ivs_dist_pilot$acc_flanker_incongruent$mean`, *SD~accuracy~* =  `r txt_ivs_dist_pilot$acc_flanker_incongruent$sd`).

**Change Detection Task.** The Change Detection Task measures the ability to detect subtle spatial changes. 
On each trial of the change detection task, participants were presented with five colored circles against a gray background, each with a radius of 15 pixels. 
Each circle was located in a semi-random location around the central fixation cross. 
The location of each circle was sampled within a pre-specified area of 50 by 50 pixels to prevent overlap. 
Participants had 1000ms to memorize the locations of the five circles. 
After 1000ms, the circles disappeared for 500ms and then reappeared again. 
On 50% of the trials, one of the circles had moved to another location with a fixed displacement of 40 pixels in a 360 degree direction. 
On the other 50% of the trials, all circles were still in the same location as the initial memory display. 
Participants had to indicate whether they thought one of the circles changed location (by pressing the left-arrow key) or whether they thought all circles were still in the same location (by pressing the right-arrow key).
Note that the only potential difference between the memory and probe display on each trial was the displacement of *one* circle; the remaining circles were always in the same place and circles never changed color within a trial.

The change detection task started with five practice trials in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red). 
After finishing the practice round, participants completed two test blocks consisting of 25 trials each (50 trials in total). 
The design was fully counterbalanced so that each circle moved on five trials and was a different color each time it moved *between* trials. 
Participants did not receive performance feedback during the two test blocks. 
The main raw performance measures were RTs and accuracy across all trials (*M~RT~* = `r txt_ivs_dist_pilot$rt_change$mean`s, *SD~RT~* = `r txt_ivs_dist_pilot$rt_change$sd`; *M~accuracy~* = `r txt_ivs_dist_pilot$acc_change$mean`, *SD~accuracy~* =  `r txt_ivs_dist_pilot$acc_change$sd`).

### Self-report measures

See Table \@ref(tab:table2) for bivariate correlations between measures of adversity across all studies.

**Violence exposure.** Violence exposure was measured using the Neighborhood Violence Scale [NVS\; @frankenhuis_2018; @frankenhuis_deVries_2020; @young_2022] and two items assessing exposure to physical fights before age 13. 
The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up"). 
Participants rated each on a scale from 1 (never true) to 5 (very often true). 
The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times). 
The items of the NVS were averaged together (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$violence`). 
Similarly, we averaged the scores on the two fighting items together. 
Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average.

**Environmental unpredictability.** We included several measures of environmental unpredictability across different temporal scales: 1) the Questionnaire of Unpredictability in Childhood [QUIC\; @glynn_2019], 2) A scale of perceived childhood unpredictability used in previous research [@mittal_2015; @young_2018], 3) the Confusion, Hubbub, and Order Scale [CHAOS\; @matheny_1995], 4) four items about the temporal stability of the family and social environment, 5) and four measures of objective unpredictability.
In the main text, we focus on exploratory analyses involving a composite measure of all z-transformed unpredictability measures.
We report additional exploratory analyses involving different subsets of measures in the supplemental materials.

The QUIC captures several dimensions of environmental and household unpredictability
The QUIC distinguishes between items capturing more short-term unpredictability (i.e., on the level of seconds to minutes) and more long-term unpredictability (i.e., on the level of days to months). 
We included all five scales of the QUIC: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 3) Safety and security. 
We made three general changes to the original scale as described in @glynn_2019. 
First, we adapted all items to refer to experiences before age 13. 
This was done to reduce cognitive load from having to go back-and-forth between different time scales. 
Second, most items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format. 
An exception was made for four items of the parental environment scale which asked for more specific experiences (e.g., "I experienced changes in my custody arrangement"). 
For these items, we adopted a response scale with the options "never", "only once", "a couple times", "several times", "many times". 
Third, quantifiers such as "frequently", "often", and "There was a period of time when [...]" were dropped to better match the response scale. 
We excluded the item "My parents got divorced" because it did not fit the response format and was captured by one of the items of the perceived unpredictability scale.
Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$quic_total`).

The perceived childhood unpredictability scale contained eight items measuring perceived unpredictability before age 13 (e.g, "My family life was generally inconsistent and unpredictable from day-to-day"). 
Participants rated each on a scale from 1 (never true) to 5 (very often true).
Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$unp`).

The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late". 
We made two changes to the original scale as described in @matheny_1995. 
First, all items were converted from the present tense to the past tense, and were endorsed as applying to participants' lives before age 13. 
Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format. 
This change was also implemented to reduce cognitive load by keeping the answer options the same between scales. 
Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$chaos`).

One additional scale measured the stability of the family and social environment. 
On a scale of 1 (the same all the time) to 5 (constant and rapid changes), participants indicated how often the following aspects of their family and social environment changed before age 13: 1) economic status, 2) family environment, 3) childhood neighborhood environment, and 4) childhood school environment.

Finally, we included four objective measures of unpredictability before age 13. 
Participants provided answers to the following items in an open response format: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "How many romantic partners did your mother have (not counting your father)?"; 4) "How many romantic partners did your father have (not counting your mother)?".

```{r table2, tab.id = "table2", tab.cap.style = "Table Caption", tab.cap="Pooled bivariate correlations and descriptive statistics of measures of childhood violence exposure and environmental unpredictability across the three studies."}
iv_cor_pooled_table
```

<br>

### Procedure {#procedure}

The experiment was completed on the participants' own laptop or desktop computer and consisted of five parts: consent, attention task battery, questionnaire battery, brief demographics form, and final checks including the opportunity to give feedback on the experiment. 
Participants were allowed to refrain from answering any of the questionnaire items, but were prompted with a warning once when moving to the next page if one of the items was not answered (which they could ignore).

After providing consent, participants started with the three attention tasks. 
They were asked to complete the attention tasks in a quiet room in the house where they would be least likely to be distracted by other people or outside noises. 
The order of the tasks was counterbalanced between subjects. At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs. 
The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deLeeuw_2015].
Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the creditcard. 
The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants. 
After successfully resizing the screen, participants completed all three tasks. 
During the task, the cursor was hidden from the screen to minimize distractions.

After completing the attention tasks, participants completed the questionnaire battery.
Finally, we asked participants if they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks. 
The full experiment took approximately 35 minutes. 
Participants were paid £4.38 upon completing the full experiment.

### Primary data analyses {#analysis_plan}

**Multiverse analysis.** Online experiments have less experimental control than lab studies.
There are many factors that might influence performance but it is ambiguous which factors affect performance and how strong these effects are. 
Although not preregistered, we decided to quantify the robustness of our findings against a set of factors that may affect online studies by using multiverse analysis (see @simonsohn_2020 for more details).
We identified seven arbitrary analytic decisions, including or excluding 1) participants who had a recaptcha score below 0.5 (possibly indicating bots); 2) participants who did not rescale their screen at the start of the experiment (see the [procedure section](#procedure)); 3) participants who did not enter fullscreen mode prior to starting the Flanker Task; 4) participants who exited fullscreen mode at any point during the Flanker Task; 5) participants who indicated high levels of noise in their environment; 6) participants who indicated extreme interruptions during the experiment.

### Reaction Times {#rt_plan}

For the Cued Attention Task and Flanker Task, average reaction times per participant were calculated separately for each condition (cued/neutral trials and incongruent/congruent trials, respectively). 
For the change detection task, we calculated an average reaction time across all trials. 
To meetmodel assumptions of normally distributed residuals, reaction times were log-transformed if they showed non-normal skew. 
We did not analyze proportion of errors because accuracy was nearly perfect on all tasks.
Note that the DDM analysis described below provides a full breakdown of performance both in terms of reaction times and accuracy.
For the Cued Attention Task and Flanker Task, we performed a set of linear mixed effects analyses to test adversity X task condition interactions on mean RTs.
Task condition was sum-coded (-1 and 1).
All models included a random intercept for participants. 
For the Change Detection Task, we performed linear regression to test the main effect of adversity on mean RTs.
Across separate models, adversity was operationalized as the composite measures of each violence exposure measure (primary analyses) and the composite measures of the unpredictability measures (exploratory analyses).
Significant interaction effects were unpacked using simple slopes analysis.

### Drift Diffusion Model {#ddm_plan}

For the Change Detection Task and the Cued Attention Task, we fit a standard DDM.
The exact estimation approach deviated from the preregistration, which was planned to be Maximum Likelihood (ML) estimation.
The reason for this change was that there were several issues with estimating DDM parameters for the Cued Attention task, which we later discovered were caused specifically by ML.
We therefore decided to switch to an hierarchical Bayesian version of the DDM (HDDM).
An important difference between HDDM and ML is that HDDM uses the group information to inform individual parameter estimates, whereas ML models are fitted to each individual separately.
This generally improves the accuracy of the estimation, especially when each participant has relatively few trials.

Following @voss_2013, we fitted several DDM models with increasingly strict constraints, comparing model fit using BIC.
For all tasks, model fit was highest when only boundary separation, drift rate and non-decision time were freely estimated (i.e., with all inter-trial variability parameters fixed to 0 and starting point fixed to 0.5, indicating no response bias).
In addition, model fit statistics for the Cued Attention task indicated that boundary separation should be fixed across conditions.
This is in line with the assumption that people cannot strategically change their decision threshold on a trial-by-trial level when conditions are presented randomly.

The DDM analysis of the Flanker task was done using a specialized DDM developed for Flanker data: The Shrinking Spotlight Model [SSP\; @grange_2016; @white_2018a; @white_2018b; @white_2011]. 
The standard DDM model assumes a stable drift rate over time within trials (i.e., the rate of information accumulation does not change over time). 
However, on the Flanker Task, reaction time patterns indicate that the drift rate increases over time, thus violating the basic assumption of the standard DDM [@white_2011]. 
The SSP accounts for this pattern by assuming that attention resembles a spotlight.
At first, attention is broad, but then gradually narrows down to the central arrow over time. 
Each arrow provides perceptual input. 
If the flanking arrows are congruent, all flankers take a positive value for perceptual input; if the flanking arrows are incongruent, they take a negative value for perceptual input.
The the central arrow always takes a positive value. 
The drift rate at each time point is a function of the strength of perceptual input multiplied by the amount of attention focused on each arrow.

Attention is operationalized by two additional parameters: the initial width of the attentional spotlight and the shrinking rate of the attentional spotlight. 
The attentional spotlight is assumed to be normally distributed over the arrows, with relatively more attention toward the center arrows and less toward the peripheral arrows. 
Over time, this normal distribution narrows down to the central arrow defined by the shrinking rate, thereby gradually decreasing the interfering effect of the flankers.
Previous studies also calculated initial attention width / shrinking rate ratio, which serves as a measure of *interference*.
We preregistered that we would analyze both the ratio and the initial attention width separately.
However, we ended up analyzing the ratio only because the attention parameters were too unstable by themselves to interpret [see also @white_2018a].
Model fit was done using the *flankr* package in R [@grange_2016].

Our dependent variables included raw RTs, the drift rate, boundary separation, and non-decision time (as well as perceptual input and interference for the Flanker Task). 
For the Flanker Task and Change Detection Task, DDM parameters were submitted to a series of linear regression models with adversity as the independent variable. 
For the Cued Attention Task, DDM parameters were submitted to linear mixed effects models to test for adversity X condition interactions. 
All models included a random intercept for participants. 
Significant interactions were unpacked using simple slopes analysis.

## Results

We first analyzed associations between raw RTs and performance across all tasks.
Participants with more violence exposure had longer RTs on the Cued Attention Task ($\beta$ = `r pilot_main_eff_rt_df |> filter(dv == "Cued Attention") |> pull(median_effect_Main)`, 95% CI = `r pilot_main_eff_rt_df |> filter(dv == "Cued Attention") |> pull(Main_CI)`, `r pilot_main_eff_rt_df |> filter(dv == "Cued Attention") |> pull(p_sum_Main)` % *p*s < .05), but we did not find significant interactions between violence exposure and task condition. 
Violence exposure did not predict RTs for the Change Detection and Flanker Tasks.

Next, we analyzed DDM parameters for each task.
For the Cued Attention Tasks, only the main effect of boundary separation was significant ($\beta$ = `r pilot_main_eff_ddm_list$cueing_a$median_effect_Main`, 95% CI = `r pilot_main_eff_ddm_list$cueing_a$Main_CI`, `r pilot_main_eff_ddm_list$cueing_a$p_sum_Main` % of *p*s < .05). 
Higher levels of violence predicted more conservative responses.
We did find a small significant task version x violence exposure interaction for the drift rate ($\beta$ = `r pilot_main_eff_ddm_list$cueing_v$median_effect_Interaction`, 95% CI = `r pilot_main_eff_ddm_list$cueing_v$Interaction_CI`, `r pilot_main_eff_ddm_list$cueing_v$p_sum_Interaction` % of *p*s < .05).
However, multiverse simple slopes analyses yielded no differences in median simple effects of violence exposure.

For the Change Detection Task, we found a main effect of violence exposure on the drift rate, indicating that higher levels of violence exposure were associated with lower drift rates, ($\beta$ = `r pilot_main_eff_ddm_list$Change_v$median_effect_Main`, 95% CI = `r pilot_main_eff_ddm_list$Change_v$Main_CI`, `r pilot_main_eff_ddm_list$Change_v$p_sum_Main` % of *p*s < .05). 
There were no significant effects of violence exposure on non-decision time and boundary separation.

Finally, for the Flanker Task, we found a main effect of violence exposure on perceptual input, indicating that higher levels of violence exposure were associated with a lower quality of perceptual input ($\beta$ = `r pilot_main_eff_ddm_list$Flanker_p$median_effect_Main`, 95% CI = `r pilot_main_eff_ddm_list$Flanker_p$Main_CI`, `r  pilot_main_eff_ddm_list$Flanker_p$p_sum_Main` % of *p*s < .05). 
Surprisingly, we additionally found a main effect of violence exposure on interference (the ratio between initial attention width and the shrinking rate) indicating that higher levels of violence exposure were associated with less interference ($\beta$ = `r pilot_main_eff_ddm_list$Flanker_interference$median_effect_Main`, 95% CI = `r pilot_main_eff_ddm_list$Flanker_interference$Main_CI`, `r pilot_main_eff_ddm_list$Flanker_interference$p_sum_Main` % of *p*s < .05).

## Discussion

In line with previous thinking [e.g., @ellis_2022; @frankenhuis_2016; @frankenhuis_2013], we initially expected people from adversity to perform better on cognitive tasks that require a broad attention scope. 
A broad attention scope might facilitate vigilance and the detection of subtle changes in peripheral information. 
However, this might come at a cost, especially for tasks that involve interference. 
Our pilot study tested these ideas by measuring performance on a Cued Attention, Changed Detection, and Flanker Task and associating it with adversity exposure. 
We expected adversity-exposure would improve performance on the Cued-Attention and Change Detection tasks but hurt performance on the Flanker Task.

In contrast to expectations, we did not find evidence for a broad adversity-related attention scope. 
In fact, the DDM analyses showed that participants with more violence exposure were generally slower to process information – as shown by the drift rate parameters of the Change Detection Task and the perceptual input parameter of the Flanker. 
However, on the Flanker Task — where we expected lowered performance — our analyses suggested that people exposed to violence experienced less interference from the flanking arrows and therefore were faster to narrow their attention to the task-relevant information.

These findings are interesting for two reasons.
First, the Flanker is a widely used task and people exposed to adversity typically show lowered performance. 
However, using the DDM decompose performance, our pilot data suggest that lowered performance may not be caused by problems with attention control or inhibition. 
Instead, people exposed to adversity might simply extract perceptual information from the stimuli more slowly (as indicated by the perceptual input parameter). 
This effectively lowers the quality of information that people can use to guide their decision, which will be reflected in lower reaction times. 
Second, these initial findings suggest that performance might be improved through different types of interventions focused on different cognitive mechanisms. 
Specifically, people with more adversity exposure might benefit from manipulations that increase the visual quality of stimuli.
In study 1, we aimed to replicated and extend these findings on the Flanker Task.

# Study 1

The goal of study 1 was to replicate the Flanker findings in the pilot study, and to better understand the possible information processing deficits for people exposed to violence. 
Participants completed three versions of the Flanker Task: the standard version (similar to the pilot study), a version with enhanced visual information, and a version with degraded visual information.

There were two possible data patterns. 
First, if violence exposure leads to deficits in perceptual processing, we would expect lower performance across all versions of the task for violence-exposed individuals.
Alternatively, lower performance on the standard version might reflect an adaptive trade-off towards more robust cognitive functioning, even in the face of noise or perturbations [@giudice_2018]. 
In that case, we would expect more stable performance for people with more violence exposure. 
As a result, they might not benefit as much from enhanced visual information, but at the same time might be able to better maintain performance when presented with degraded information.

Similarly to the pilot study, the focus of the primary aims was on childhood exposure to violence. First, we aimed to investigate the robustness of the primary findings on the Flanker Task in the pilot study by pooling the pilot data and the data of the standard condition in the current study. Second, we aimed to extent the findings of the pilot study by investigating how Flanker performance changes across task conditions as a function of violence exposure. We expected that the task manipulations would primarily have an effect on the quality of perceptual input, thereby also affecting overall response times.
Additional exploratory analyses again focused on the association between environmental unpredictability and performance on the Flanker Task.

## Methods

### Participants

Participant recruitment was identical to the pilot study.
In total, 567 US-based people between the ages of 18 and 30 participated (See Table \@ref(tab:table1)).
We applied the same exclusion criteria as reported in the pilot study.
In total, we excluded ... (TODO).
The final sample consisted of `r nrow(study1_data)` participants.

### Flanker Task

The Flanker Task was programmed in JsPsych version 6.3.1 [@deLeeuw_2015]. 
We programmed three conditions of the Flanker Task. 
In the standard condition, the arrows were 40 pixels in size (0.4 inches) and had zero padding between them.

In the 'enhanced' condition, the aim was to increase the quality of visual information provided by the arrows. 
To this end, we increased the arrow size by 12.5% to 45 pixels (0.45 inches), and increased padding between the arrows to 5 pixels. 
This increased the width of the Flanker display by 50% with respect to the standard display.

In the 'degraded' condition, the aim was to decrease the quality of visual information provided by the arrows. 
The arrow size and padding were the same as in the standard version, but both flanking and target arrows were rotated 45$^\circ$. 
Therefore, they provided more noisy information about their horizontal direction. 
We had no strong *a priori* expectations about how performance of adversity-exposed people might be affected by specific types of stimulus degradation (e.g., arrow rotation, decreasing stimulus contrast).

Participants completed each condition of the Flanker Task separately in different blocks. 
The presentation order of the conditions was randomized.
Each condition consisted of 64 trials. 
For the degraded condition, participants completed four repetitions of all parameter combinations: Arrow location (top vs. bottom) X central arrow direction (left-up vs. left-down vs. right-up, vs right-down) X congruency: (congruent vs. incongruent).
For the standard and enhanced condition, participants completed eight repetitions of all parameter combinations to match the number of trials in the degraded condition: Arrow location (top vs. bottom) X central arrow direction (left-up vs. left-down vs. right-up, vs right-down) X congruency: (congruent vs. incongruent).
Across all three conditions, the arrows were randomly presented in the top-half or bottom-half of the screen at 300 pixels from the center of the screen. 
This was done to prevent participants from rigidly fixating on the center of the screen, which might reduce the interfering effect of the flanking arrows. 
Each trial started with a fixation cross presented at the center of the screen. 
After a delay of 1000ms, the arrows are presented either in the top- or bottom-half of the screen.

Prior to each block, participants performed eight practice trials of the current condition. 
During practice, participants received performance feedback after each trial (either "Correct!" printed in green, "Incorrect!" printed in red, or "Too slow!" printed in red if their response latency exceeded 2000 ms).
After completing the practice trials, participants completed each block with the opportunity to take a break in between.
At the onset of each block, participants were told what the current condition was.
No performance feedback of any kind was provided during the test blocks.
The main performance measures were RTs and accuracy for each condition.

### Self-report measures

The self-report measures were almost identical to those used in the pilot study, with a number of small differences. 
Based on participant feedback in the pilot study, we changed all mentions of 'parent(s)' across questionnaires to 'caregiver(s)' (e.g., "At least one of my caregivers had punishments that were unpredictable). 
We also added a question asking about the participant's exact family composition.

### Procedure

The procedure was identical to the pilot study. 
The full experiment took approximately 30 minutes. 
Participants were paid £3.75 upon completing the full experiment.

### Data analyses

**Multiverse analysis.** We included the same arbitrary decisions in the multiverse analyses as in the pilot study.
For the pooled analyses, there was one minor change in the arbitrary decisions with regards to the screen rescaling procedure.
In the current study, we made a change to the screen rescaling procedure using a credit card. 
Specifically, we changed to initial size of the resize box from 100px to 300px. 
This way, the stimulus display would still be reasonably close to the intended size if participants did not engage in any resizing. 
However, this led to a change between the pilot study and the current study, which is particularly important for the pooled analysis as rescaling (yes or no) was included as an arbitrary exclusion decision in the multiverse analyses. 
To solve this issue, we decided to include this decision with four combinations: 1) exclude non-scalers in both studies; 2) include non-scalers in both studies; 3) exclude non-scalers in pilot study, include non-scalers in study 1; 4) include non-scalers in pilot study, exclude non-scalers in study 1.

For each analysis, we report the median $\beta$s, 95% confidence intervals, and the proportion of *p*-values < .05 across all analytic decisions. For the primary analyses, we used a bootstrapping technique to compute overall *p*-values to assess whether the obtained median $\beta$ is significantly larger than zero [@simonsohn_2020].

**Primary analyses.** To address the first primary aim, we pooled the Flanker data of the pilot study and the current study, using the standard condition of the current study.
For the pooled effect of violence exposure on each of the DDM parameters, we ran initial linear models including violence exposure as main predictor and study number as a covariate (effect-coded with -1 for the pilot study and 1 for study 1).
Study number was necessary as a covariate because we realized after data collection that we programmed a different vertical distance from the center of the stimuli compared to the pilot study (300px, while we used a distance of 600px in the pilot study).
The pooled effect of violence exposure on raw RTs was assessed through linear mixed models with study number included as a covariate and including a random intercept per participant.

To address the [second primary aim](#primary), we analyzed the effect of violence exposure and Flanker condition type (within the current study only) on Flanker performance using linear mixed effects models with a random intercept per participant. 
The main dependent variables were mean RTs and the SSP parameters: Perceptual input, boundary separation, non-decision time, and the interference effect (initial attention width / shrinking rate). 
For each outcome measure, we ran two separate models: One comparing the standard condition with the enhanced condition, and one comparing the standard condition with the degraded condition. 
In both models, condition was dummy-coded using the standard condition as the reference group.

## Results

### Pooled analysis

The pooled multiverse results across the two studies of the effects of violence exposure (primary analysis) and unpredictability (exploratory analysis) are summarized in Figure \@ref(fig:figure1) and Table \@ref(tab:table3).
The results for both types of adversity showed a similar pattern.
Higher levels of violence exposure were associated with a lower quality of perceptual input ($\beta$ = `r condition_pooled_results_list$p_vio$median_effect`, 95% CI = `r condition_pooled_results_list$p_vio$CI`, `r condition_pooled_results_list$p_vio$p_sum` % of *p*s < .05).
Similarly, higher levels of unpredictability were also associated with a lower quality of perceptual input ($\beta$ = `r condition_pooled_results_list$p_unp$median_effect`, 95% CI = `r condition_pooled_results_list$p_unp$CI`, `r condition_pooled_results_list$p_unp$p_sum` % of *p*s < .05).
Contrary to the results of the pilot study, more violence exposure was not associated with differences in the amount of interference ($\beta$ = `r condition_pooled_results_list$interference_vio$median_effect`, 95% CI = `r condition_pooled_results_list$interference_vio$CI`, `r condition_pooled_results_list$interference_vio$p_sum` % of *p*s < .05).
Finally, we also did not find an association between unpredictability and the amount of interference ($\beta$ = `r condition_pooled_results_list$interference_unp$median_effect`, 95% CI = `r condition_pooled_results_list$interference_unp$CI`, `r condition_pooled_results_list$interference_unp$p_sum` % of *p*s < .05).

<br>

```{r figure1, fig.id = "figure1", fig.cap.style = "Figure Caption", fig.cap="Pooled multiverse results for the associations between adversity and flanker performance. (a) visualizes the multiverse interaction effects, with the thick black lines denoting the median slope and the thin grey/blue lines denoting effects across each arbitrary decision. Grey lines indicate non-significant effects (*p* > .05) and blue lines indicate significant effects (*p* < .05). (b) plots sorted beta coefficients across each arbitrary decision. (c) plots the percentage of variance that each arbitrary decision explains in the standardized effect."}
knitr::include_graphics("figures/pooled.png")
```

<br>

```{r table3, tab.id = "table3", tab.cap.style = "Table Caption", tab.cap="Standardized effects of violence exposure and unpredictability on Flanker performance after pooling the data of the pilot study and study 1."}
condition_pooled_results_table
```

<br>

As can be seen in Figure \@ref(fig:figure1), the decision to include/exclude participants was one of the biggest sources of variance in the regression estimates.
This was despite our success in bringing the proportion of non-scalers down from `r pilot_data |> summarise(n = sum(round(scale_factor,4)==0.3081)/n()*100) |> pull() |> formatC(digits = 2, width = 3, flag = "0", format = 'f')`% to
`r study1_data |> summarise(n = sum(round(scale_factor,4)==0.9007)/n()*100) |> pull(n) |>  formatC(digits = 2, width = 3, flag = "0", format = 'f')`% in the current study.
To a lesser extent, other influential decisions were to include/exclude people who exited fullscreen at some point during the experiment and to include/exclude participants with who experienced many interruptions.

### Flanker conditions

The main effects of task condition on the quality of perceptual input were in the expected direction: Relative to the standard condition, the quality of perceptual input was higher in the enhanced condition ($\beta$ = `r study1_condition_vio_results_list$p_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$p_enhanced$condition_CI`, `r  study1_condition_vio_results_list$p_enhanced$p_sum_Condition`% of *p*s < .05) and lower in the degraded condition ($\beta$ = `r study1_condition_vio_results_list$p_degraded$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$p_degraded$condition_CI`, `r study1_condition_vio_results_list$p_degraded$p_sum_Condition`% of *p*s < .05).
The task manipulations also influenced the amount of interference. 
Relative to the standard condition, interference was lower in the enhanced condition ($\beta$ = `r study1_condition_vio_results_list$interference_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_enhanced$condition_CI`, `r study1_condition_vio_results_list$interference_enhanced$p_sum_Condition`% of *p*s < .05).
Unexpectedly, interference was also lower in the degraded condition ($\beta$ = `r study1_condition_vio_results_list$interference_degraded$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_degraded$condition_CI`, `r study1_condition_vio_results_list$interference_degraded$p_sum_Condition`% of *p*s < .05), suggesting that the angle in the flanking arrows reduced interference relative to the standard condition.

We did not find any task condition x violence exposure interactions, but a main effect for interference emerged. 
First, higher levels of violence exposure were associated with more experienced interference in the standard condition ($\beta$ = `r study1_condition_vio_results_list$interference_enhanced$median_effect_Violence`, 95% CI = `r study1_condition_vio_results_list$interference_enhanced$Violence_CI`, `r  study1_condition_vio_results_list$interference_enhanced$p_sum_Violence`% of *p*s < .05).
None of the other SSP parameters were significantly associated with violence exposure.
This pattern of results is inconsistent with the pooled results reported above, which show a negative association with perceptual input but not with interference.

We also ran exploratory analyses on the association between environmental unpredictability and Flanker performance.
We found a significant main effect of unpredictability on the quality of perceptual input, with higher levels of childhood unpredictability being associated with a lower quality of perceptual input, ($\beta$ = `r study1_condition_unp_results_list$p_enhanced$median_effect_Unpredictability`, 95% CI = `r study1_condition_unp_results_list$p_enhanced$Unpredictability_CI`, `r study1_condition_unp_results_list$p_enhanced$p_sum_Unpredictability`% of *p*s < .05).
We also found a significant main effect of unpredictability on the amount of interference, with higher levels of childhood unpredictability being associated with more interference, ($\beta$ = `r study1_condition_unp_results_list$interference_enhanced$median_effect_Unpredictability`, 95% CI = `r study1_condition_unp_results_list$interference_enhanced$Unpredictability_CI`, `r study1_condition_unp_results_list$interference_enhanced$p_sum_Unpredictability`% of *p*s < .05).
Note that the main effect of interference was not found in the pooled analyses reported above.

In addition, there was a significant task version x unpredictability interaction in the degraded task condition, ($\beta$ = `r study1_condition_unp_results_list$interference_degraded$median_effect_Interaction`, 95% CI = `r study1_condition_unp_results_list$interference_degraded$Interaction_CI`, `r study1_condition_unp_results_list$interference_degraded$p_sum_Interaction`% of *p*s < .05).
Participants with high levels of unpredictability tended to experience more distractor interference on the standard task version (*b* = `r study1_simslopes_unp_list$interference_flanker_Degraded$median_ss_Standard`, `r study1_simslopes_unp_list$interference_flanker_Degraded$p_sum_Standard`% of *p*s < .05), compared to participants with lower levels of unpredictability. However, the degraded task condition reduced this interference effect (*b* = `r study1_simslopes_unp_list$interference_flanker_Degraded$median_ss_degraded`, `r study1_simslopes_unp_list$interference_flanker_Degraded$p_sum_degraded`% of *p*s < .05).
We did not find any significant interaction effects in the enhanced condition.

## Discussion

The goal of this study was to replicate and extend the findings of the pilot study.
The findings of study 1 were inconsistent with the pilot study in a couple of ways.
First, whereas performance differences were predominantly found across levels of violence exposure and not environmental unpredictability, this pattern seemed to be reversed in the current study.
Second, we did not replicate the unexpected finding that higher levels of adversity were associated with *less* flanker interference.
Instead, adversity either led to no differences in interference .
Finally, while decreasing or increasing the perceptual quality of the arrows did affect the quality of perceptual processing across all participants, it did not reduce the interference effect difference between people with higher and lower levels of adversity.

Pooling data across the two studies, a more consistent pattern of performance emerged.
Effects were more similar across violence exposure and unpredictability.
First, participants with more adversity exposure extracted lower-quality information from the stimuli.
However, we did not find an association between adversity and the amount of interference.
Thus, the pooled analyses suggest that people with more exposure to violence *and* unpredictability process information more slowly, but are not necessarily more easily distracted by task-irrelevant information.
This is intriguing because it suggests that performance differences across levels of adversity are driven by relatively low-level perceptual differences and not by higher-level executive functions.
This interpretation of performance is quite different than previous research, which suggests that people exposed to adversity lack will-power, self-control, and are easily distracted [e.g., @farah_2006; @fields_2021; @mezzacappa_2004; @noble_2005].

Generally speaking, the results of these first two studies are not in line with our initial predictions about a present-oriented attention style.
Although we expected such a style to lead to faster speed of perceptual processing on attention tasks, we generally found the opposite pattern.
One reason for this might be that a present-oriented attention style leads people from adversity to process information more holistically, which would lower the depth of perceptual processing of any individual stimulus.
Another related reason might be that an external, present-oriented attention style extends beyond the computer screen to all of their immediate environment.
Both of these are potential mechanistic explanations for a lowered quality of perceptual processing that would be in line with a specialized attention style.
In study 2, we aimed to replicate the broader findings from study 1 (lowered perceptual input but no differences in interference) and to investigate if and how the lower quality of perceptual processing was associated with a more holistic style of attention.

# Study 2

<...>

## Methods

## Results

## Discussion

## General discussion

\pagebreak

# References {#refs}

### 2023-05-04 manuscript/pilot_stage_objects.R

@@ -1,0 +1,756 @@
+library(tidyverse)
+library(patchwork)
+library(ggsci)
+library(here)
+
+
+source(here("preregistrations/1_pilot/scripts/custom_functions/functions_corrplot.R"))
+
+
+cleaned_data = read_csv(here("data/1_pilot/2_cleaned_data.csv"))
+pilot_data <- cleaned_data # for easy referencing in the manuscript
+load(file = here("preregistrations/1_pilot/analysis_objects/primary_mult_summaries.RData"))
+load(file = here("preregistrations/1_pilot/analysis_objects/exploratory_mult_summaries.RData"))
+
+get_alphas <- function(data, string) {
+  (data |> 
+     select(matches(string)) |> 
+     psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+}
+
+
+
+# Descriptives ------------------------------------------------------------
+
+## IV distributions ----
+txt_ivs_dist_pilot <- 
+  cleaned_data |> select(matches("(mean|total|composite|edu_parents_recoded|age)$"),
+                         matches("^(acc|rt)_(flanker|cueing)"), acc_change, rt_change) |> 
+  map(function(x) {
+    list(
+      mean = round(mean(x, na.rm = T),2),
+      sd   = round(sd(x, na.rm = T),2)
+    )
+  })
+
+txt_ivs_alpha_pilot <- 
+  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
+    "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
+    "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
+    "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
+  map(function(x) {
+    (cleaned_data |> 
+       select(matches(x)) |> 
+       psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+  }) |> 
+  setNames(c("stai_s", "violence", "unp", 
+             "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
[…]

### 2023-05-04 manuscript/pooled_stage_objects.R

@@ -1,0 +1,180 @@
+library(tidyverse)
+library(here)
+library(ggsci)
+library(patchwork)
+library(flextable)
+library(specr)
+
+source(here("preregistrations/1_pilot/scripts/custom_functions/functions_corrplot.R"))
+
+pilot_data = read_csv(here("data/1_pilot/2_cleaned_data.csv")) |> mutate(study = "pilot")
+study1_data = read_csv(here("data/2_study1/2_cleaned_data.csv")) |> mutate(study = "study1")
+
+
+
+# IV correlations ---------------------------------------------------------
+
+iv_cor_pooled_table <-  bind_rows(
+    pilot_data |> 
+      mutate(id = paste0("pilot", id)) |> 
+      rename(
+        vio_comp     = violence_composite,
+        unp_obj_comp = unpredictability_obj,
+        unp_subj_comp = unpredictability_subj,
+        unp_comp     = unpredictability_composite,
+        pcunp_mean   = unp_mean,
+        nvs_mean     = violence_mean
+      ),
+    study1_data |> 
+      mutate(id = paste0("study1", id))
+  ) |> 
+select(nvs_mean, fighting_mean, vio_comp, 
+       quic_total_mean, pcunp_mean, chaos_mean, change_env_mean, unp_obj_comp, unp_subj_comp, unp_comp) |> 
+  corr_table(
+    numbered = T,
+    sample_size = F,
+    c.names = c("Neigh. violence", "Fighting", "Violence comp.", 
+                "QUIC", "Perc. unpredictability", "CHAOS", "Env. change", "Obj. unpredictability", "Subj. Unpredictability", "Unpredictability comp."),
+    stats = c("mean", "sd", "median", "min", "max", "skew", "kurtosis")
+  ) |> 
+  add_column(empty1 = "", .after = 4) |> 
+  mutate(across(
+    everything(),
+    ~ifelse(is.na(.), "", .)
+  )) |> 
+  mutate(across(
+    everything(),
+    ~formatC(.,  digits = 2, width = 3, flag = "0", format = 'f'))) |> 
+  flextable() |> 
+  width("empty1", width = .2) |> 
+  width(j = 1, width = .75) |> 
+  set_header_labels(Variable = "", empty1 = "") |> 
+  add_header_row(
+    values = c(" ", "Violence exposure", " ", "Environmental unpredictability"),
+    colwidths = c(1, 3, 1, 7)
+  ) |> 
+  border_remove() |> 
[…]

### 2023-05-04 manuscript/study1_stage_objects.R

@@ -1,0 +1,1645 @@
+library(tidyverse)
+library(here)
+library(ggsci)
+library(patchwork)
+library(flextable)
+library(specr)
+
+
+cleaned_data = read_csv(here("data/2_study1/2_cleaned_data.csv"))
+study1_data <- cleaned_data
+load(file = here("preregistrations/2_study1/analysis_objects/primary_multiverse_summaries.RData"))
+load(file = here("preregistrations/2_study1/analysis_objects/exploratory_multiverse_summaries.RData"))
+
+get_alphas <- function(data, string) {
+  (data |> 
+     select(matches(string)) |> 
+     psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+}
+
+
+
+
+# Descriptives ------------------------------------------------------------
+
+## IV distributions ----
+txt_ivs_dist_study1 <- 
+  cleaned_data |> select(matches("(mean|total|composite|edu_parents_recoded)$")) |> 
+  map(function(x) {
+    list(
+      mean = round(mean(x, na.rm = T),2),
+      sd   = round(sd(x, na.rm = T),2)
+    )
+  })
+
+txt_ivs_alpha_study1 <- 
+  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
+    "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
+    "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
+    "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
+  map(function(x) {
+    (cleaned_data |> 
+       select(matches(x)) |> 
+       psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+  }) |> 
+  setNames(c("stai_s", "violence", "unp", 
+             "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
+             "quic_total", "chaos", "ses", "impuls", "fos_pa", "fos_tp", "fos_fc", "fos_fo", "depression"))
+
+
+## Sample characteristics ----
+
+sample_pilot <- cleaned_data |> 
[…]

### 2023-05-10 preregistrations/3_study2/preregistration.Rmd
final timestamped version of preregistration for study 2

@@
 
-1. Investigate how unpredictability and violence exposure are associated with perceptual input and interference on the Flanker Task by pooling the data across all three studies.
+1. Investigate how unpredictability and violence exposure are associated with perceptual input and interference on the Flanker Task.
 
 2. Investigate how unpredictability and violence exposure are associated with a preference for more holistic vs. detailed processing of information.
+
+3. Investigate if differences in perceptual input and processing style are associated within-subjects.
 
@@
 
-Participants will be 400 US-based individuals between the ages of 18 and 30. Recruitment will be identical to study 1. 
-We conducted a power analysis for the planned linear regressions through simulation. 
-We determined the required sample size to achieve power of > .90 for a standardized main effect of 0.05.
-This main effect is slightly lower than the effect of 0.06 that we found for perceptual input in the pooled analyses of study 1.
-Simulations revealed that we would require around 450 participants to achieve a power of .93.
-We decided to recruit 500 participants with the expectation that we will have to exclude around 50 participants.
+Participants will be 600 US-based individuals between the ages of 18 and 30. 
+Recruitment will be identical to study 1. 
+We conducted a power analysis for the planned linear mixed models involving the Global Local Task through simulation. 
+We determined the required sample size to achieve power of > .80 for a standardized interaction effect of 0.06 with different levels of noise (sigma; 0.6, 0.7 and 0.8).
+This main effect is slightly lower than the main effect of 0.06 that we found for perceptual input in the pooled analyses of study 1.
+Simulations revealed that when sigma is 0.6, power is sufficient around N = 500.
+When sigma is 0.7, power is sufficient above N = 550.
+When sigma is 0.8, power is sufficient above N = 700.
+As sigma tended to be between 0.6 and 0.7 in the first two studies, we decided to recruit 600 participants with the expectation that we will have to exclude around 50 participants.
 
@@
 One key dimension is whether the tasks measures focused attention (by cueing attention towards the global or local level prior to stimulus presentation) or divided attention (by having participants search for a target on both levels) [@lee_2023].
-Here, we use a version measuring divided attention, which allows measuring a natural preference for either global or local processing [@hakim_2016; lee_2023; @mckone_2010].
+Here, we use a version measuring divided attention, which allows measuring a natural preference for either global or local processing [@hakim_2017; @lee_2023; @mckone_2010].
 
@@
 
-We will assess state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [Stai-S; @speilberger_1999] (See [Table S1](#appendix)).
+We will assess state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [Stai-S\; @spielberger_1999] (See [Table S1](#appendix)).
  An overall state anxiety variable was computed by averaging across the 20 unweighted items.
@@
 
-Violence exposure will be measured using two measures: 1) the Neighborhood Violence Scale [NVS; @frankenhuis_2018; @frankenhuis_deVries_2020] (see [Table S2](#appendix)) and 2) two items assessing exposure to physical fights before age 13 ("Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?").
+Violence exposure will be measured using two measures: 1) the Neighborhood Violence Scale [NVS\; @frankenhuis_2018; @frankenhuis_deVries_2020] (see [Table S2](#appendix)) and 2) two items assessing exposure to physical fights before age 13 ("Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?").
 A violence exposure composite score will be calculated as an unweighted average of the mean NVS score (standardized) and the mean of the fighting items (standardized).
@@
 We distinguish between subjective and objective measures of environmental unpredictability.
-Subjective unpredictability will be measured as an unweighted average of three scales: 1) A scale of perceived childhood unpredictability used in previous research (see [Table S3](#appendix)) [@mittal_2015; @young_2018]; 2) An adapted version of the Confusion, Hubbub and Order Scale [CHAOS; @matheny_1995] (see [Table S5](#appendix)); 3) An adapted version of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019] (see [Table S4](#appendix)).
+Subjective unpredictability will be measured as an unweighted average of three scales: 1) A scale of perceived childhood unpredictability used in previous research (see [Table S3](#appendix)) [@mittal_2015; @young_2018]; 2) An adapted version of the Confusion, Hubbub and Order Scale [CHAOS\; @matheny_1995] (see [Table S5](#appendix)); 3) An adapted version of the Questionnaire of Unpredictability in Childhood [QUIC\; @glynn_2019] (see [Table S4](#appendix)).
 Objective unpredictability will be measured as an unweighted average of four items relating to experiences prior to age 13: 1) number of residential changes, 2) number of male and female romantic partners of a caregiver besides the other primary caregiver (measured separately; values > 6 were given a value 6 to prevent extreme outliers), 4) self-reported stability of the family and social environment across four dimensions: economic status, family environment, childhood neighborhood environment, and childhood school environment (rated between 1 (the same all the time) and 5 (constant and rapid changes)).
@@
 
-We will measure attentional style using the Attentional Style Questionnaire [ASQ; @calster_2018].
+We will measure attentional style using the Attentional Style Questionnaire [ASQ\; @calster_2018] (See [Table S7](#appendix).
 The ASQ measures self-reported attentional style, with seven items asking about the participant's propensity for internally oriented attention (e.g., "During an activity, unrelated mmental images and thoughts come to my mind") and seven items about externally oriented attention (e.g., "I am easily drawn to new stimuli (for example, voices of people passing by, as sound in the house, ...) that are not relevant to a task I am doing").
@@
 
-We will measure impulsivity with the Motor Impulsivity subscale of the Barrett Impulsivity Scale (BIS; short form; [@patton_1995; @spinella_2007]) (See [Table S7](#appendix)) 
+We will measure impulsivity with the Motor Impulsivity subscale of the Barrett Impulsivity Scale (BIS; short form; [@patton_1995; @spinella_2007]) (See [Table S8](#appendix)) 
 An overall impulsivity variable will be computed by averaging the five unweighted items.
@@
 
-We will measure future orientation with an adapted version of the Future Orientation Scale [FOS; @steinberg_2009] (See [Table S8](#appendix).
+We will measure future orientation with an adapted version of the Future Orientation Scale [FOS\; @steinberg_2009] (See [Table S9](#appendix).
 An overall future orientation variable will be computed by averaging the 15 unweighted items.
@@
 
-We will measure depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD; @radloff_1977] (See [Table S9](#appendix). 
+We will measure depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD\; @radloff_1977] (See [Table S10](#appendix). 
 An overall depression variable will be computed by averaging the 20 unweighted items.
@@
 At the onset of the first task, the experiment switches to full-screen mode to limit distractions from other programs or browser tabs.
-The size of the task stimuli is controlled between subjects using the resize plugin in JsPsych [@deLeeuw_2015]. 
+The size of the task stimuli is controlled between subjects using the resize plugin in JsPsych [@deleeuw_2015]. 
 After successfully resizing the screen, participants complete all three tasks. 
@@
 
-For the Flanker Task, we will use the Shrinking Spotlight Model [SSP; @grange_2016; @white_2018a; @white_2018b; @white_2011] to fit the data.
+For the Flanker Task, we will use the Shrinking Spotlight Model [SSP\; @grange_2016; @white_2018a; @white_2018b; @white_2011] to fit the data.
 The SSP model will be fit to the data of each individual participant in two steps. 
@@
 
+All linear mixed effects models will contain a random intercept for participants.
+All primary models will contain the following covariates: (1) study number (pilot study, study 1, or study 2; sum-coded), (2) whether participants rescaled their screen at the start of the cognitive tasks (yes or no; sum-coded), (3) whether participants experienced interruptions during the tasks (yes or no; sum-coded), and (4) whether people exited full-screen mode during the experiment (yes or no; sum-coded).
+Note that the latter three covariates were included as arbitrary decisions in the multiverse analyses for the pilot study and study 1.
+However, as we found that they substantially altered the results, we decided to reclassify them as non-arbitrary decisions and include them as covariates instead.
+
 To address the [first primary aim](#primary), we will fit a linear regression model to the pooled data of all three studies (i.e., the pilot study, study 1, and study 2).
 We will fit different models for environmental unpredictability and violence exposure as predictors (using the respective composite scores) and for perceptual input and interference as dependent variables.
-Each model will additionally contain the following covariates: (1) study number (pilot study, study 1, or study 2; sum-coded), (2) whether participants rescaled their screen at the start of the cognitive tasks (yes or no; sum-coded), (3) whether participants experienced interruptions during the tasks (yes or no; sum-coded), and (4) whether people exited full-screen mode during the experiment (yes or no; sum-coded).
-Note that the latter three covariates were included as arbitrary decisions in the multiverse analyses for the pilot study and study 1.
-However, as we found that they substantially altered the results, we decided to reclassify them as non-arbitrary decisions and include them as covariates instead.
+
 To address the [second primary aim](#primary), we will fit separate linear mixed effects models for environmental unpredictability and violence exposure with drift rate as the dependent variable and adversity type, task condition, and their interaction as independent variables.
-The models will contain a random intercept for participants, and contain the same covariates as described above.
+
+To address the [third primary aim](#primary), we will stack the perceptual input of the Flanker Task and the drift rate of the Global-Local task.
+Before stacking the data, we will compute a difference score of Global-Local drift rates by substracting the drift rate on local trials from the drift rate on global trials (with higher scores meaning relatively faster information processing on global trials).
+In addition, perceptual input and the drift rate difference score will be separately standardized.
+We will fit separate linear mixed effects models for environmental unpredictability and violence exposure with the standardized performance measure as the dependent variable, and adversity type, task (Flanker or Global-Local, sum-coded) and their interaction as independent variables.
 
@@
 
+Go back to [Methods](#att_style)
+
+```{r tableS7, tab.id="tableS7", tab.cap.style="Table Caption", tab.cap="Items of the Attention Style Questionnaire"}
+codebook %>%
+  filter(str_detect(Variable, "att_style\\d\\d")) %>% 
+  mutate(Item = 1:n()) %>%
+  select(Item, Label) %>%
+  add_column(.after = 1, "empty1" = "") %>%
+  flextable(cwidth = c(0.75, .2, 5)) %>%
+  set_header_labels(Item = "Item", empty1 = "", Label = "Description")
+```
+
+\pagebreak
+
 Go back to [Methods](#impulsivity)
 
-```{r tableS7, tab.id="tableS7", tab.cap.style="Table Caption", tab.cap="Items of the Barrett Impulsivity Scale (BIS) - motor impulsivity subscale"}
+```{r tableS8, tab.id="tableS8", tab.cap.style="Table Caption", tab.cap="Items of the Barrett Impulsivity Scale (BIS) - motor impulsivity subscale"}
 codebook %>%
@@
 
-```{r tableS8, tab.id="tableS8", tab.cap.style="Table Caption", tab.cap="Items of the Future Orientation Scale (FOS)"}
+```{r tableS9, tab.id="tableS9", tab.cap.style="Table Caption", tab.cap="Items of the Future Orientation Scale (FOS)"}
 codebook %>%
@@
 
-```{r tableS9, tab.id="tableS9", tab.cap.style="Table Caption", tab.cap="Items of the Epidemiologic Studies Depression Scale (CESD)"}
+```{r tableS10, tab.id="tableS10", tab.cap.style="Table Caption", tab.cap="Items of the Epidemiologic Studies Depression Scale (CESD)"}
 codebook %>%

### 2023-06-06 preregistrations/3_study2/preregistration_amendment.Rmd
amendment to preregistration for study 2

---
title: "Amendment to preregistration"
output: github_document
---

Go to [this link](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2) for the original preregistration.

## Amendment to preregistration for study 2 on `r Sys.Date()`

### Global-Local performance

In the original preregistration, we specified that we would exclude participants who performed at chance on either the Flanker Task or the Global-Local Task, which was defined as an accuracy of 59.4% or lower.
However, initial inspections of the Global-Local Task data showed that a substantial part of the sample did not reach this cut-off, suggesting that the task was more difficult than anticipated.
Thus, we developed a more fine-grained approach (described below) in an attempt to distinguish between 1) participants who did not understand the task and 2) participants who understood the task, but found it difficult to perform well. 
Given the assumptions of DDM, the first group would have to be excluded because they likely did not go through a process of information accumulation.
However, the model should be able to adequately fit the data of the second group.

The amended analysis approach for the Global-Local Task looks as follows:

1) Fit the data to the cleaned data of the full sample, including participants who performed at or below chance level (i.e., after trial-level exclusions but before case-wise exclusions);
2) Based on recovered parameter estimates for each participant, simulate the same number of trials (reaction times and accuracy) using the `RWiener` package, separately for Global and Local trials.
3) For each participant, calculate the 25th, 50th and 75th quantile of both their real RTs and the simulated RTs. 
In addition, we calculate mean accuracies based on the real and simulated data.
4. Compute standardized residuals between the real and simulated data for RTs at each quantile and for accuracy.
In case of good fit, the residual should be close to zero.
5. Exclude the data of participants with any standardized residual > 3.2 SD.

### Multiverse analyses

In the preregistration, we planned to include three variables as covariates that were previously featured as arbitrary exclusion decisions in the multiverse specification: 1) whether or not participants rescaled the screen; 2) whether or not participants exited fullscreen mode at some point during the tasks; 3) Whether or not participants experienced interruptions during the tasks.
Our reasoning was that these three factors were consistently found to have a large impact on model results.
However, we realized later on that adding these factors as covariates was not a good approach from a causal inference standpoint.
That is, it is more likely that each of these factors added random noise to our estimates than that they had a causal effect on the outcome.
Therefore, we decided instead to include these factors as arbitrary decisions in the multiverse analyses, similarly as the previous two studies.
This will allow for a coherent assessment of influential factors across all three experiments.

### 2024-01-17 manuscript/manuscript5.Rmd
updates to manuscript

---
bibliography: references.bib
csl: apa.csl
output:
  officedown::rdocx_document:
    reference_docx: reference-doc.docx
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1
      header: .5
      footer: 0
      gutter: 0
    plots:
      align: center
      caption:
        style: Image Caption
        pre: 'Figure '
        sep: '. '
    tables:
      caption:
        style: Table Caption
        pre: 'Table '
        sep: '. '
---

```{r setup, include=FALSE}
# Load libraries
library(dplyr)
library(tidyr)
library(purrr)
library(furrr)
library(readr)
library(magrittr)
library(officer)
library(flextable)
library(here)
library(pwr)

# set up chunk options
knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "!t", 
  out.extra = "",
  fig.show = "asis",
  message = FALSE,
  warning = FALSE
)

# set up flextable for tables
set_flextable_defaults(
  font.family = "Times", 
  font.size = 10,
  font.color = "black",
  line_spacing = 1,
  padding.bottom = 1, 
  padding.top = 1,
  padding.left = 1,
  padding.right = 1
)

# Source necessary objects
power_linear      <- read_csv("../data/1_pilot/simulation/power_linear_model.csv") %>% mutate(power = round(power, 0))
power_mixed       <- read_csv("../data/1_pilot/simulation/power_mixed_model.csv") %>% mutate(power = round(power, 0))
source("pilot_stage_objects.R") # Staged results of the pilot study
source("study1_stage_objects.R") # Staged results of study 1
source("pooled_stage_objects.R") # Pooled staged results
source("study2_stage_objects.R")
```

####**Childhood adversity is not associated with lowered inhibition, but lower strength of perceptual input: A Drift Diffusion Model analysis**

The perceptual strength parameter, p, provides an index of the perceptual contribution of each item in the stimulus display: a large value of p indicates strong perceptual processing and relatively easy ability to identify the arrows and map them onto the correct response.
<br>

#### Stefan Vermeent^1,2^, Ethan S. Young^1^, Jean-Louis van Gelder^2^, & Willem E. Frankenhuis^1,2,3^

#### ^1^ Department of Psychology, Utrecht University, Utrecht, The Netherlands

#### ^2^ Max Planck Institute for the Study of Crime, Security, and Law, Freiburg, Germany

#### ^3^ Evolutionary and Population Biology, Institute for Biodiversity and Ecosystem Dynamics, University of Amsterdam, Amsterdam, the Netherlands

\pagebreak

The predominant view in developmental psychology is that exposure to adversity impairs cognitive abilities. 
This view is supported by decades of research showing that people living in high-adversity contexts tend to score lower on a variety of cognitive tests [@hackman_2010; @ursache_2016]. 
Recent adaptation-based perspectives, however, have argued that people from adversity may also develop intact, or enhanced, abilities for solving problems in high-adversity contexts [@ellis_2017; @frankenhuis_2013]. 
These perspectives are considered complimentary: for instance, adversity may impair some cognitive processes, yet enhance others.
Despite their compatibility, few studies have investigated the interplay of impaired and enhanced abilities shapes performance.
In this paper, across three preregistered online experiments, we used cognitive modeling to derive a process-level understanding of the association between childhood adversity and performance on the Flanker Task, a popular measure of cognitive control [@ridderinkhof_2021].

It is well-established that early-life adversity is associated with deficits in the ability to inhibit distracting, goal-irrelevant information [@hackman_2010; @ursache_2016]. 
These conclusions are often based on performance on the Flanker Task [@eriksen_1974].
On this task, participants typically see five arrows in a horizontal orientation, and are asked to indicate the direction of the central arrow.
The flanking arrows point in the opposite direction on half of the trials, leading to interference that participants must inhibit.
Slower performance on the Flanker has been documented for children and adults with lower childhood socioeconomic status [SES\; @farah_2006; @mezzacappa_2004; @noble_2005] and more environmental unpredictability [@fields_2021; @mittal_2015].
These findings are typically interpreted using a deficit lens, indicating impairment in the ability to inhibit distractions.

Notwithstanding, some recent studies suggest that growing up in adversity may be associated with improved abilities such as attention shifting [@fields_2021; @mittal_2015; @young_2022\; but see @nweze_2021].
Notably, some studies found deficit patterns on the Flanker alongside enhancements on other aspects of attention within the same participants.
For example, children with lower SES performed less well on the Flanker, but outperformed children from from higher SES on orienting their attention to salient, peripheral cues [@mezzacappa_2004]. 
Similarly, children with more caregiver switches (an indicator of unpredictability) were found to perform less well on the Flanker, but outperformed children with fewer caregiver switches on shifting their attention between different task goals [@fields_2021].
In less favorable environmental conditions, attending to peripheral cues and efficient attention shifting might promote the ability to seize fleeting rewards and detect sudden threats.
In contrast, a person who tends to inhibit distractions might be more likely to overlook such information [@mittal_2015].

The potential benefits of quickly shifting attention and detecting subtle, peripheral changes might be linked to the notion of a *present-oriented attention style* [@frankenhuis_2016; @vangelder_2023].
People with a present-oriented attention style (versus a more future-oriented attention style) are more geared towards processing information that is relevant for solving challenges and obtaining rewards in the here-and-now.
A general tendency to be more attuned to the present (while disregarding the future) is sometimes referred to as a short-term mindset [@vangelder_2023].
In environments that are both harsh and unpredictable, it might be particularly adaptive to develop a present-oriented attention style [@frankenhuis_2016].
Thus, patterns of lowered and improved performance across tasks with different attention demands could reflect two sides of the same coin: an attention style that is beneficial for one task might hurt performance on other tasks.

Although such a process-level explanation may be intuitive, we cannot yet rule out another, psychometric explanation related to limitations of the Flanker, and cognitive control tasks generally.
First, the correlations between different inhibition tasks (e.g., Flanker, Go/No-Go, Stroop) are typically moderate or even week, and these tasks often fail to form a coherent latent estimate of inhibition [@draheim_2021; @krumm_2009; @loffler_2022; @rey_mermet_2019; @rouder_2019; @stahl_2014].
This suggests that inhibition might not be a single ability that operates the same way across different contexts.
If so, the association between a present-oriented attention style and performance on inhibition tasks might be more complex than previously thought.
Second, cognitive modeling, used to separate different cognitive processes, suggests that basic processing speed is the most stable determinant of performance across inhibition tasks, not actual inhibition [@hedge_2022; @loffler_2022].
This means that lowered performance on inhibition tasks does not necessarily reflect inhibition difficulties, and therefore might not necessarily be related to a present-oriented attention style.

## Using Drift Diffusion Modeling to estimate attention and processing styles

Thus, an important issue is that several processes are involved in performance on the Flanker, and standard assessments using raw performance measures (response times, accuracy rates) mostly fail to distinguish between them.
For example, performance differences on the Flanker could indicate that someone experiences more (or less) flanker interference, generally processes less (or more) efficiently, or responds with less (or more) caution.
To understand how adversity affects performance, we need to be able to separate the difference processes that make up performance.

Formal cognitive models such as the Drift Diffusion Model [DDM\; @forstmann_2016; @ratcliff_1998; @ratcliff_2008; @ratcliff_2015; @wagenmakers_2009] provide a solution.
The DDM estimates cognitive processes at different stages of the decision-making process (See Figure 1a).
It represents decision-making on a binary decision-making task as a process in which people accumulate information until favor one response over the other.   
These two response options are represented as opposing boundaries.
One boundary corresponds to the correct response and the other to the incorrect response.
When information accumulation reaches one of the two boundaries, the corresponding response is executed.

The DDM translates trial-level RTs and accuracy into three distinct cognitive processes.
The speed of information accumulation is captured in a parameter called the *drift rate*.
Higher drift rates are associated with faster responses and higher mean accuracy.
Response caution is modeled through the *boundary separation*; that is, the width between the two boundaries.
Larger boundary separation is associated with larger RTs and higher accuracy (i.e., sacrificing speed to increase accuracy).
Finally, *non-decision time* represents the time it takes to prepare for the task at the start of the trial (before information processing) and the time it takes to execute a response (after a response boundary has been reached).
Longer non-decision times are associated with larger RTs, without influencing accuracy.

The Shrinking Spotlight (SSP) model is an extension of the standard DDM to account for attention processes on the Flanker [See Figure 1b\; @grange_2016; @white_2018a; @white_2018b; @white_2011].
The SSP model assumes that attention resembles a spotlight that is normally distributed over the Flanker arrows (with a particular starting *attentional width*).
Over time, people narrow their attention down to the central arrow (at a rate defined by the *shrinking rate*), thereby gradually decreasing interference from irrelevant information.
Prior work has defined the amount of distractor *interference* by dividing the attentional width by the shrinking rate [@white_2018a].
People may experience less interference either by starting with a narrower attentional width, and/or by more rapidly shrinking their attention down to the target arrow.
Finally, performance is also influenced by the *perceptual input* strength; that is, how well someone can process the arrows in general.
Note that typical interpretations of lowered raw Flanker performance are in terms of the amount of interference that someone experiences, and not in terms of the strength of perceptual input.
In this paper, we are interested in how childhood adversity is associated with both interference and the strength of perceptual input.

```{r}
#| label: figure1
#| fig.width: 7
#| fig.height: 9
#| dpi: 600
#| fig-cap: | 
#|   **Figure 1.** A visual overview of the Drift Diffusion Model (DDM) and the Shrinking Spotlight Model (SSP). Panel A: The DDM assumes that people go through three distinct stages when they perform cognitive tasks with two forced response options. In a first preparation phase, they visually encode the relevant stimuli. In a second decision phase, people accumulate information in favor of one decision over the other (e.g., pressing left vs. right) until the decision boundary for either the correct or incorrect response is reached. Each jagged line represents this information accumulation process on a single trial. In a third execution phase, people execute the motor response.  The model estimates four parameters that reflect distinct cognitive processes (printed in italic): (1) The drift rate represents the average rate of evidence accumulation towards the correct decision boundary and measures processing speed; (2) The non-decision time represents both the time spent encoding the stimuli and executing the response; (3) The boundary separation represents how far apart has “set” their decision boundaries, and is a measure of the person’s level of response caution; (4) The starting point represents the starting point of the decision process and measures the level of response bias (not considered here). Panel B: The SSP is an extension of the standard DDM including additional parameters to capture attentional processes involved in Flanker performance. Each stimulus arrow provides a certain strength of perceptual input (*p*). On incongruent trials, the perceptual input of flanking arrows is coded negatively (-*p*). Attention is assumed to be normally distributed over the arrows with a certain attentional width. Over time, attention is narrowed down toward the central arrow at a rate determined by the shrinking rate, thereby gradually lowering the interference caused by the flanking arrows. The drift rate in the SSP model is the sum of the perceptual input of each arrow multiplied by the attention allotted to each arrow. As attention for the flanking arrows decreases over time, the drift rate is assumed to increase over time (contrary to the standard DDM, which assumes a linear drift rate).

knitr::include_graphics("figures/fig1.png")
```

# Overview of studies
The overarching goal of our studies is to understand the attentional and processing styles that people develop in conditions of adversity.
We focus on measures of exposure to violence and environmental unpredictability. 
Previous research shows that they these two types of adversity are on the one hand associated with improved attention shifting and working memory updating [@fields_2021; @mittal_2015; @young_2018; @young_2022], yet on the other hand with lowered inhibition and working memory capacity [@fields_2021; @mittal_2015; @young_2018].
We conducted three online studies: one pilot and two follow-up studies).
Using cognitive modeling, we unpack Flanker performance 1) in comparison to other tasks that require externally focused attention (Pilot), 2) across visual processing manipulations (Study 1), and 3) in terms of tendencies for holistic versus local processing (Study 2).

We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see [https://github.com/stefanvermeent/attention_project/preregistrations](https://github.com/stefanvermeent/attention_project/preregistrations)).
For each study, we preregistered primary (i.e., hypothesis-driven) and exploratory analyses.
The main text addresses the primary analyses involving violence exposure and the exploratory analyses involving environmental unpredictability.
We describe the other exploratory analyses in the supplemental materials and involved constructs that we hypothesized might be related to a present-oriented attention style, such as impulsivity and future orientation.

# Pilot study

In the Pilot, our goal was to understand how childhood adversity relates to performance on tasks with different attentional demands.
Participants completed self-report measures of childhood adversity and three cognitive tasks.
These tasks measured inhibition, attention for peripheral cues, and attention for subtle changes.
We expected violence exposure to be positively associated with a present-oriented attention style.
Specifically, we expected participants with more violence exposure to be better at detecting peripheral stimuli and subtle changes.
This expected this would result in a higher drift rate (faster speed of information accummulation) or shorter non-decision times (faster attention orientation, among other things), but not necessarily with differences in boundary separation (response caution).
Second, we expected that participants with more violence exposure would be worse at ignoring distracting peripheral stimuli. 
We expected this would result in more experienced interference (as derived from the SSP model).

## Methods

### Participants {#participants}

Participants were 565 US-based individuals aged between 18 and 30 recruited on Prolific Academic ([https://www.prolific.co](https://www.prolific.co)) (See Table 1 for demographic data).
The sample was balanced on sex. 
We used the MacArthur's ladder, included in Prolific's prescreening battery, for assessing perceived SES to ensure about half of the sample came from lower-SES backgrounds (which we defined as a score of 4 or below).
Participants were eligible if they spoke fluent English and did not report color-blindness.

\pagebreak

```{r table1, tab.id = "table1", tab.cap.style = "Table Caption", tab.cap="Demographic information for all studies."}
demographics_table
```

<br>

We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the minimally required number of participants for standardized regression coefficients of 0.10 and 0.15 (for details and simulation code, see GitHub). 
Power was > .80 for adversity x task condition interactions with *N* = 450 or more. 
For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require *N* = `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`. 
We sampled 550 participants, anticipating a final sample of ~500 after exclusions.

Prior to analyzing the data, we applied our preregistered exclusion criteria.
First, we excluded participants who did not complete the full study; second, those who had incomplete data on any of the attention tasks; third, those who missed both attention check items; fourth, those who had suspicious response patterns (e.g., consistently endorsing high response options even though some items were reverse coded). Fifth, on a trial-level, we excluded any trials with reaction times < 250 ms or > 3500 ms [@ratcliff_2015]. 
Participants with more than 10 trials removed were completely excluded from the analyses.  
The final sample consisted of `r nrow(pilot_data)` participants.

### Procedure {#procedure}

Participants completed the experiment on their own laptop or desktop computer. Participants could refrain from answering any of the questionnaire items, and were prompted with a warning once per page in the case of missing items.

After providing consent, participants completed three attention tasks. 
They were asked to move to a quiet room in the house, where they would be unlikely to be distracted by other people or outside noises. 
The order of the tasks was counterbalanced between subjects. 
At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs. 
The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deleeuw_2015].
Participants were asked to hold a credit card (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the credit card. 
The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants. 
After successfully resizing the screen, participants completed all three tasks. 
During the task, the cursor was hidden from the screen to minimize distractions.
After completing the attention tasks, participants completed the questionnaire battery and demographic questions.
Finally, we asked participants whether they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks. 
The full experiment took ~35 minutes. 
Participants were paid £4.38 when they reached the end of the experiment.

### Cognitive measures {#cogmeasures}

The attention tasks were programmed in JsPsych version 3.6.1 [@deleeuw_2015]. 
For all materials and links to working versions of the tasks, see the Github repository.

**Flanker Task.** The Flanker measures selective attention and response inhibition [@eriksen_1974]. 
The Flanker began with eight practice trials, followed by 64 test trials.
On each trial, participants saw a set of five arrows pointing either left or right.
Participants were instructed to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right. 
All trials included black arrows against a white background.
On the *congruent* trials (50%), the flanking arrows pointed in the same direction as the central arrow. 
On the *incongruent* trials (50%), the arrows pointed in the opposite direction. 
The arrows were randomly presented in the top-half or bottom-half of the screen. 
Each trial started with a fixation cross (1000 ms), after which the arrows were visible until a response was given. 
Participants received performance feedback during the practice trials, but not during the test block.

**Cued Attention Task.** The Cued Attention Task wis an adapted version of the Posner task, which measures the speed of attention for peripheral cues [@posner_1980]. 
The Cued Attention Task began with eight practice trials, followed by 64 test trials.
On each trial, a left- or right-pointing arrow was presented in one of eight random locations at 300 pixels from the center of the screen. 
Participants were instructed to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard. 
All trials included a black cue and arrow against a white background.
On *cued* trials (50%), a cue ('\*') preceded the arrow in the exact same location.
On *neutral* trials (50%), the cue preceded the arrow, but appeared at the center of the screen (not where the arrow would appear).
Thus, the cue was perfectly predictive of the target location on cued trials, but provided no predictive information about the location of the arrow on neutral trials. 
Each trial started with a fixation cross at the center of the screen for 1000 ms. 
Then, the cue appeared for 250 ms, followed by the target arrow, until a response was given.

**Change Detection Task.** The Change Detection Task measures the ability to detect subtle spatial changes. 
The Change Detection Task started with five practice trials followed by 50 test trials.
On each trial, participants saw five colored circles (red, light-blue, dark-blue, yellow, and purple) against a gray background, each with a radius of 15 pixels. 
Each circle was located in a semi-random location around the central fixation cross. 
The location of each circle was sampled within a pre-specified area of 50-by-50 pixels to prevent overlap. 
Participants had 1000 ms to memorize the locations of the five circles. 
Then, the circles disappeared for 500 ms and then reappeared. 
On *change* trials (50%), one of the circles had moved to another location with a fixed displacement of 40 pixels in a 360 degree direction. 
On *no change* trials (50%), all circles were still in the same location. 
Participants were instructed to indicate whether all circles were still in the same location or one of the circles had changed location.
The displacement of *one* circle was the only potential difference on each trial;

**DDM/SSP parameters.** We analyzed the Flanker with the SSP model [@grange_2016; @white_2018a; @white_2018b; @white_2011], using the *flankr* package [@grange_2016].
For each participant, the SSP provided us with estimates of: (1) strength of perceptual input (general quality of information that participants get from the arrows), (2) interference (initial attention width divided by the speed at which attention is narrowed down to the central arrow), (3) non-decision time (combination of speed of initial stimulus encoding and response execution), and (4) boundary separation (response caution).
Our focus on interference as a ratio between attention width and shrinking rate was a deviation from the preregistration, as we initially planned to investigate both aspects of attention separately.
However, we discovered that both parameters in isolation were unreliable because of an inherent trade-off, while the ratio did provide a stable measure.
This was supported in a simulation study by @white_2018a showing that the ratio measure is reliable.
See the supplemental materials (section ) for a comparison between the preregistered and the updated analyses.

For the Change Detection Task and the Cued Attention Task, we used a hierarchical Bayesian implementation of the standard DDM (HDDM).
For each participant, the HDDM provided us with estimates of: 1) drift rate (speed of information accumulation; analogous to strength of perceptual input in the SSP model, except that drift rate is time-invariant), 2) non-decision time (same as SSP model), and 3) boundary separation (same as SSP model).
The hierarchical Bayesian fitting procedure was a deviation from the preregistration, in which we planned to use Maximum Likelihood (ML) estimation. 
There were several issues with estimating DDM parameters for the Cued Attention task, which we later discovered were caused specifically by ML. 
An important difference between HDDM and ML is that HDDM uses the group information to inform individual parameter estimates, whereas ML models are fitted to each individual separately. 
This generally improves the accuracy of the estimation.
See the supplemental materials for an overview of the fit procedure and model fit across all models.

### Self-report measures

See Table 2 for bivariate correlations between measures of adversity across all studies.

**Violence exposure.** We measured violence exposure using the Neighborhood Violence Scale (NVS) and two items assessing involvement in violence before age 13 [@frankenhuis_2018; @frankenhuis_deVries_2020; @young_2022]. 
The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up"). 
Participants rated each on a scale from 1 (never true) to 5 (very often true). 
The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times). 
The items of the NVS were averaged together (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$violence`). 
Similarly, we averaged the scores on the two fighting items together. 
For the main analyses, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average.

**Environmental unpredictability.** We included five measures of environmental unpredictability across different temporal scales: (1) the Questionnaire of Unpredictability in Childhood [QUIC\; @glynn_2019]; (2) the Perceived Childhood Unpredictability scale [@young_2018]; (3) the Confusion, Hubbub, and Order Scale [CHAOS\; @matheny_1995]; (4) stability of the family and social environment; and (5) objective indicators of unpredictability.
All scales were adapted to refer to experiences before age 13.
In the main text, we focus on exploratory analyses involving a composite measure of all z-transformed unpredictability measures.
We report additional exploratory analyses involving different subsets of the measures in the supplemental materials (section XXX).

The QUIC captures environmental and household unpredictability.
We made three preregistered changes to the original scale [@glynn_2019], to better align it with the other scales. 
All items were rated on a scale of 1 (never true) to 5 (very often true), except for four items referring to specific experiences (e.g., "I experienced changes in my custody arrangement"). 
For these items, we adopted a response scale with the options "never", "only once", "a couple times", "several times", "many times". 
Third, quantifiers such as "frequently", "often", and "There was a period of time when [...]" were dropped to better match the response scale. 
We excluded the item "My parents got divorced" because it did not fit the new response labels and this information was already captured by one of the items of the perceived unpredictability scale.
Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$quic_total`).

The perceived childhood unpredictability scale included eight items measuring perceived unpredictability before age 13 (e.g,. "My family life was generally inconsistent and unpredictable from day-to-day"). 
Participants rated each on a scale from 1 (never true) to 5 (very often true).
Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$unp`).

The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late"). 
All items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format. 
Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$chaos`).

We included one additional scale to measure the stability of the family and social environment. 
On a scale of 1 (the same all the time) to 5 (constant and rapid changes), participants indicated how often the following aspects of their family and social environment changed before age 13: (1) economic status; (2) family environment; (3) childhood neighborhood environment; and (4) childhood school environment.

Finally, we included four objective measures of unpredictability before age 13: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "How many romantic partners did your mother have (not counting your father)?"; 4) "How many romantic partners did your father have (not counting your mother)?".

```{r table2, tab.id = "table2", tab.cap.style = "Table Caption", tab.cap="Pooled bivariate correlations and descriptive statistics of measures of childhood violence exposure and environmental unpredictability across the three studies."}
iv_cor_pooled_table
```

<br>

### Data analyses {#analysis_plan}

**Multiverse analysis.** In an amendment to the preregistration, we quantified the robustness of our findings against six data cleaning decisions that may affect the robustness of online studies by using multiverse analysis, using the *multitool* package [@young_2023].
Multiverse analysis allows systematically evaluating the robustness of analyses across all combinations of different arbitrary data processing decisions (for details, see @giudice_2021; @simonsohn_2020; @steegen_2016).
Specifically, we looked at the influence of including or excluding 1) participants who scored below 0.5 on a build-in bot-detection measure on Prolific (potentially indicating a bot); 2) participants who did not rescale their screen at the start of the experiment; 3) participants who did not enter fullscreen mode prior to starting the tasks; 4) participants who exited fullscreen mode at any point during the tasks; 5) participants who indicated high levels of noise in their environment; 6) participants who indicated extreme interruptions during the experiment.

### Primary analyses

For the Cued Attention Task and Flanker RTs, we used linear mixed effects models to test violence exposure x task condition (sum-coded) interactions on mean RTs and each DDM parameter.
All mixed effects models included a random intercept for participants.
For the Change Detection Task and Flanker SSP parameters, we used linear regression models to test the main effect of adversity on mean RTs and each DDM/SSP parameter.
To meet model assumptions of normally distributed residuals, reaction times were log-transformed. 
Analyses involving interference (Flanker) and boundary separation (all tasks) parameters violated the assumption of normally distributed residuals.
For boundary separation, we solved this using log-transformation.
For interference, non-normality was caused by extreme outliers (>3.2SD), which we excluded from the analyses.

## Results and discussion

Table 3 summarizes the results.
More violence exposure was associated with lower strength of perceptual input under `r pilot_main_eff_ddm_list$Flanker_p$p_sum_Main`% of multiverse specifications (although the median 95% CI interval contained zero).
We additionally found a significant main effect of violence exposure on interference under `r pilot_main_eff_ddm_list$Flanker_interference$p_sum_Main`% of multiverse specifications, such that more violence exposure was associated with less interference.
This was contrary to our expectation that people exposed to adversity would have more difficulties dealing with interference from irrelevant distractors.

Participants with more exposure to childhood violence were slower on the Cued Attention Task, which was mainly related to a higher level of response caution (boundary separation).
On the Change Detection Task, more childhood violence exposure was associated with slower speed of information processing (drift rate) under `r pilot_main_eff_ddm_list$Change_v$p_sum_Main`% of multiverse specifications, but not with longer RTs.
These results were not in line with our expectation that people from adversity would perform better on cognitive tasks that require a broad, present-focused attention style.

<br>

```{r table3, tab.id = "table3", tab.cap.style = "Table Caption", tab.cap="Main and interaction effects of the effect of violence exposure on task performance."}
pilot_main_eff_ddm_table
```

<br>

The pattern of findings on the Flanker was interesting for two reasons.
First, the Flanker is a widely used task to assess the ability to inhibit irrelevant information, and people exposed to adversity typically show lowered performance. 
Our pilot results, though, suggest that lowered performance may not be caused by a reduced ability to inhibit distracting information. 
Instead, people exposed to adversity might have a lower strength of perceptual input, leading to slower and less efficient information processing.
If true, these initial findings suggest that performance might be improved through interventions that increase the visual quality of stimuli. 
In Study 1, we aimed to replicate and extend these findings.

# Study 1

The goal of Study 1 was to follow up on the Pilot by manipulating the visual quality of information on the Flanker.
Participants completed three versions: a standard version (similar to the Pilot), one with enhanced visual information, and one with degraded visual information.
We focused again on childhood exposure to violence.
Our first aim was to examine the robustness of our finding of improved interference control on the Flanker in relation to more adversity exposure in the pilot.
We did so by analyzing the data of the standard condition, as well as by pooling the data of the Pilot and Study 1.
Our second aim was to investigate whether manipulating visual information on the Flanker would influence performance for people with more violence exposure.

We preregistered two potential data patterns and associated interpretations, without a priori favoring one over the other. 
First, the strength of perceptual input might be lower for people with more exposure to violence compared to people with less exposure to violence across all conditions. 
Second, lower performance on the standard version might reflect an adaptive trade-off towards cognitive functioning that is less affected by noise or perturbations, at a cost of lower overall performance [@giudice_2018]. 
In that case, we would expect the strength of perceptual input to be influenced to a lesser extent across conditions for people with more exposure to violence than for people with less exposure to violence.
As a result, they might not benefit as much from enhanced visual information, yet might be able to better maintain performance with degraded information.

## Methods

### Participants

Participant recruitment was identical to the Pilot.
In total, 567 people from the United States between the ages of 18 and 30 participated (See Table 1).
We applied the same exclusion criteria as reported in the Pilot.
The final sample consisted of `r nrow(study1_data)` participants.

### Flanker Task

We programmed the Flanker in JsPsych version 6.3.1 [@deleeuw_2015] with three conditions. 
Each condition consisted of eight practice trials, followed b 64 test trials.
In the *standard* condition, the arrows were 40 pixels in size (0.4 inches) and had zero padding between them. 
In the *enhanced* condition, we increased the arrow size by 12.5% to 45 pixels (0.45 inches), and increased the space between the arrows to 5 pixels. 
This increased the width of the stimulus display by 50% with respect to the standard display. 
In the 'degraded' condition, sizes and space between arrows were the same as in the standard version, but all arrows were rotated 45$^\circ$ (in the same direction). 
Participants completed each condition separately in different blocks, in randomized order.

### Self-report measures

The self-report measures were identical to those used in the Pilot.

### Procedure

The procedure was identical to the pilot study. 
The full experiment took approximately 30 minutes. 
Participants were paid £3.75 when they reached the end of the experiment.

### Data analyses

**Multiverse analysis.** We included the same arbitrary decisions in the multiverse analyses as in the Pilot.
For the pooled analyses---i.e., joint analysis of the Pilot and the standard condition of Study 1---there was one minor change in in how we screen rescaling as a preprocessing decision in the multiverse. 
In Study 1, we changed the screen rescaling procedure by making the initial size of the resize box 300 pixels instead of 100 pixels.
This way, the stimulus display would still be close to the intended size if participants did not engage in any resizing. 
However, this led to one important change for the pooled analysis: rescaling (yes or no) was included as an arbitrary exclusion decision in the multiverse analyses with four combinations: (1) exclude non-scalers in both studies; (2) include non-scalers in both studies; (3) exclude non-scalers in the Pilot, include non-scalers in Study 1; (4) include non-scalers in the Pilot, exclude non-scalers in Study 1.

For each analysis, we report the median $\beta$s, 95% confidence intervals, and the proportion of *p*-values < .05 across all analytic decisions. For the primary analyses, we used bootstrapping to compute the probability of obtaining an effect size at least as extreme as observed in the real data, conditioned on a true effect size of zero [for details, see @simonsohn_2020].

**Primary analyses.** To address the first primary aim, we analyzed the data from the standard condition, as well as pooled the Flanker data of the Pilot and the current study.
We ran separate linear models for each SSP parameter as well as RT difference scores with violence exposure as main predictor and study as covariate (effect-coded).
To address the second primary aim, we analyzed the effect of violence exposure and Flanker condition type on performance using linear mixed effects models with a random intercept per participant. 
The five main dependent variables were mean RT difference and the SSP parameters: Perceptual input, boundary separation, non-decision time, and interference. 
For each outcome measure, we ran two separate models: one comparing the standard condition with the enhanced condition, and one comparing the standard condition with the degraded condition. 
In both models, condition was dummy-coded using the standard condition as the reference group.

## Results and discussion

### Standard Flanker performance

Table 4 summarizes the multiverse results for the effects of violence exposure (primary analysis) and unpredictability (exploratory analysis).
Unlike in the Pilot, we did not find any significant associations with violence exposure.
In the exploratory analysis, there was a significant negative association between unpredictability and perceptual input (median $\beta$ = `r study1_expl_results_list$p_flanker$median_effect_Main`, 95% CI = `r study1_expl_results_list$p_flanker$CI`, `r study1_expl_results_list$p_flanker$p_sum` % of *p*s <.05).

```{r table4, tab.id = "table4", tab.cap.style = "Table Caption", tab.cap="Standardized effects of violence exposure and unpredictability on Flanker performance in study 1."}
study1_results_table
```

After pooling the data of the pilot study and Study 1, there was a negative association between violence exposure and interference (median $\beta$ = `r study1_pooled_results_list$interference_vio$median_effect`, 95% CI = `r study1_pooled_results_list$interference_vio$CI`, `r study1_pooled_results_list$interference_vio$p_sum` % of *p*s <.05, bootstrapped *p* = `r study1_pooled_results_list$interference_vio$boot_p`).
Violence exposure was associated with lower strength of perceptual input under `r study1_pooled_results_list$interference_vio$p_sum`% of multiverse specifications, but the bootstrapped *p*-value was not significant (median $\beta$ = `r study1_pooled_results_list$p_vio$median_effect`, 95% CI = `r study1_pooled_results_list$p_vio$CI`, bootstrapped *p* = `r study1_pooled_results_list$p_vio$boot_p`).
We did not find other significant associations for either violence exposure or unpredictability.

### Flanker conditions

The main effects of task condition on the strength of perceptual input were in the expected direction: relative to the standard condition, the quality of perceptual input was higher in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$p_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$p_enhanced$condition_CI`, `r study1_condition_vio_results_list$p_enhanced$p_sum_Condition` % of *p*s <.05) and lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$p_degraded$median_effect_Condition`, 95% CI = `r  study1_condition_vio_results_list$p_degraded$condition_CI`, `r study1_condition_vio_results_list$p_degraded$p_sum_Condition` % of *p*s <.05). Interference was lower in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$interference_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_enhanced$condition_CI`, `r study1_condition_vio_results_list$interference_enhanced$p_sum_Condition` % of *p*s <.05). Unexpectedly, interference was also lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$interference_degraded$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_degraded$condition_CI`, `r study1_condition_vio_results_list$interference_degraded$p_sum_Condition` % of *p*s <.05), suggesting that the angle in the flanking arrows reduced interference, relative to the standard condition.
However, none of the interaction effects for either violence exposure or unpredictability were significant.

```{r table5, tab.id = "table5", tab.cap.style = "Table Caption", tab.cap="Standardized interaction effects of violence exposure (primary analysis) and unpredictability (secondary analysis) on Flanker performance across standard, enhanced, and degraded conditions."}
study1_condition_results_table
```

The results of the Pilot and Study 1 were inconsistent with regard to the association between adversity and interference, but hinted at two general patterns. 
First, violence exposure was not associated with *increased* interference; instead, we found either the opposite effect or no effect.
Second, both violence exposure and unpredictability were associated with lowered strength of perceptual input, albeit inconsistently.
These findings, if replicable, are intriguing as they would suggest that the common finding of lowered Flanker performance among people with more adversity exposure do not actually result from worse interference control---as typically inferred.
Rather, such lowered performance would result from processes other than inhibition ability, such as slower general processing.
Though interesting, our findings so far leave open the question why adversity might be negatively associated with perceptual input.
This question was the focus of Study 2.

# Study 2

Study 2 set out to compare two explanations for the finding that people exposed to adversity tended to show lower strength of perceptual input on the Flanker.
First, lowered strength of perceptual input in people exposed to adversity may indicate a difficulty in extracting relevant information (i.e., about their direction) from the arrows in general.
Second, the difference in perceptual input may not be a cognitive deficit per se, but instead could be a signature of a difference in processing style---a feature, not a bug.
People exposed to adversity may process information more holistically, focusing more on the configuration of pieces of information rather than individual pieces of information.
On the Flanker, this would lower the depth of perceptual processing of any individual stimulus, thus resulting in lowered strength of perceptual input, as we observed in the Pilot and Study 1.

We preregistered three aims focusing both on violence exposure and unpredictability.
First, we expected to replicate our earlier findings that adversity was associated with lowered perceptual input and lower interference in people exposed to adversity.
Second, we included a Global-Local Task to investigate the hypothesis---based on the findings of the Pilot and Study 1---that people with more adverse experiences would develop a more holistic style of information processing.
Third, we planned to conduct a within-subjects analysis of Flanker and Global-Local performance to assess whether people with lowered perceptual input on the Flanker Task would also show a more global processing style (rather than a local processing style) on the Global-Local Task.

## Methods

### Participants

Participants were 600 people from the United States between the ages of 18 and 30. 
Recruitment was identical to Study 1. 
We conducted a simulation-based for the planned linear mixed models with the Global Local Task (see GitHub). 
We determined that power of > .80 for a standardized interaction effect of 0.06, with sigma (noise) set to 0.7 (comparable to observed sigma's in the first two studies) would require 550 participants.
We recruited 600 participants, with the expectation to have a final sample of 550 participants after exclusions.
We applied the same exclusion criteria as reported in the Pilot and Study 1.
The final sample consisted of `r nrow(study2_data)` participants.

### Measures

The measures of childhood violence exposure and environmental unpredictability were identical to Study 1.
The Flanker was identical to the standard version used in Study 1.

*Global-Local Task*. The Global-Local Task is a measure of global-local processing [@navon_1977].
Many different versions of this task exist in the literature.
One key dimension on which they differ is whether the task measures focused attention (by cueing attention towards the global or local level prior to stimulus presentation) or divided attention (by having participants search for a target on both levels) [@lee_2023].
Here, we use a version measuring divided attention, which allows measuring whether someone tends to have a more global versus local processing style [@hakim_2017; @lee_2023; @mckone_2010].

Participants saw images of big, black letters (the global level) comprised of small letters (the local level)---so-called Navon images [@navon_1977]---against a white background.
Participants first completed eight practice trials, after which they completed an additional 64 test trials.
On each trial, participants searched for one of two target letters---an 'E' or 'H'---and indicated whether it was present on the global or local letter by pressing 'g' or 'l' on their keyboard, respectively.
Each stimulus was 600 pixels high and 395 pixels wide and comprised of seven local letters vertically and five local letters horizontally.
All stimuli consisted of combinations of the letters 'T', 'F', 'P', 'L', 'H', and 'E'.
The target letters 'H' and 'E' were both present in each stimulus, but the other letters varied. 
The global and local level never contained the same letter.

### Procedure

The procedure was identical to Study 1. 
The full experiment took ~30 minutes. 
Participants were paid £4.50 when they reached the end of the experiment.

### Data analyses

**Multiverse analysis.** We included the same decisions in the multiverse as in the previous studies.
However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, see [https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md))

**DDM estimation.** For the Flanker, we used the SSP (@grange_2016; @white_2018a; @white_2018b; @white_2011] using the same procedure as in Study 1.
For the Global-Local Task, we used a hierarchical Bayesian DDM to fit the data using the *runjags* package [@denwood_2016].
See the supplemental materials (Section 4) for more information about the procedure and model fit.

We deviated from our preregistration with regard to the preprocessing of Global-Local Task data.
Specifically, we relaxed the low performance threshold as the task was more difficult than anticipated.
These deviations are described in the amendment ([https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md)).

**Primary analyses.** We ran simple regressions for analyses involving only main effects (primary aim 1), and linear mixed effects models for analyses involving within-subject interactions (primary aim 2 and 3).
To address the third primary aim (within-subject interaction between Global-Local drift rate and Flanker strength of perceptual input), we further preprocessed the data in two steps.
First, we computed a difference score of Global-Local drift rates by subtracting the drift rate on local trials from the drift rate on global trials (with higher scores reflecting relatively faster information processing on global trials).
Second, we separately standardized the Flanker strength of perceptual input and Global-Local drift rate difference.
We fitted linear mixed effects models with the standardized performance measures as the dependent variable, and adversity type, task (Flanker or Global-Local, sum-coded) and their interaction as independent variables.

## Results and discussion

Figure 1 and 2 summarize the multiverse results for the effects of violence exposure and unpredictability within Study 2 and pooled across all studies.
In Study 2, violence exposure was negatively associated with strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.vio_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.vio_comp$boot_p`), but not associated with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.vio_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$boot_p`).
Unpredictability was not associated with either strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.unp_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.unp_comp$boot_p`), nor with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.unp_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$boot_p`).

In the pooled analysis, the results were similar for both types of adversity.
Violence exposure was associated with lower strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_list$p_flanker.vio_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.vio_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_list$interference_flanker.vio_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.vio_comp$boot_p`).
Similarly, unpredictability was associated with a lower quality of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_list$p_flanker.unp_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.unp_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_list$interference_flanker.unp_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.unp_comp$boot_p`).

```{r figure2, fig.height=9, fig.width = 7, fig.id = "figure2", fig.cap.style = "Figure Caption", fig.cap="Multiverse results for the association between violence exposure with the strength of perceptual input and interference on the Flanker across all studies. Panels A-D depict sorted standardized beta coefficients across each arbitrary decision for the Pilot study, Study 1, Study 2, and pooled across all three studies, respectively. Panel E depicts the percentage of variance that each arbitrary decision explains in the standardized effect. Panel E does not depict the influence of failing the bot-detection measure for the Pilot study and Study 1 because all participants reached the required cut-off."}
knitr::include_graphics("figures/fig2.png")
```

<br>

### Global-Local Task performance

There was a main effect of violence exposure on Global-Local drift rates, with more violence exposure being associated with slower speed of information processing ($\beta$~median~ = `r study2_aim2_results_list$Main_vio$median_effect`, `r study2_aim2_results_list$Main_vio$p_sum`% of *p*s < .05, bootstrapped *p* `r study2_aim2_results_list$Main_vio$boot_p`). 
There also was a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_vio$median_effect`, `r study2_aim2_results_list$Condition_vio$p_sum`% of *p*s < .05, bootstrapped *p* `r study2_aim2_results_list$Condition_vio$boot_p`).
Finally, there was an interaction effect between violence exposure and task condition ($\beta$~median~ = `r study2_aim2_results_list$Interaction_vio$median_effect`, `r study2_aim2_results_list$Interaction_vio$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_vio$boot_p`).
Simple slopes analyses revealed that participants with lower levels of violence exposure did not differ in speed of processing of global versus local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.Low$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.Low$p_sum`% of *p*s < .05).
In contrast, participants with higher levels of violence exposure processed global targets faster than local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.High$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.High$p_sum`% of *p*s < .05).

There was a significant main effect of unpredictability on drift rates, with more unpredictability being associated with slower speed of information processing, ($\beta$~median~ = `r study2_aim2_results_list$Main_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Main_unp$CI`, `r study2_aim2_results_list$Main_unp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim2_results_list$Main_unp$boot_p`). 
We also found a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Condition_vio$CI`, `r study2_aim2_results_list$Condition_unp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim2_results_list$Condition_unp$boot_p`).
We did not find a significant unpredictability x task condition interaction effect ($\beta$~median~ = `r study2_aim2_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Interaction_unp$CI`, `r study2_aim2_results_list$Interaction_unp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_unp$boot_p`).

### Within-subjects comparison of Flanker and Global-Local information processing

There was no significant main effects for violence exposure (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`) nor for cognitive task (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`).
There was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_vio$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_vio$CI`, `r study2_aim3_results_list$Interaction_vio$p_sum` % of *p*s < .05, bootstrapped *p* `r study2_aim3_results_list$Interaction_vio$boot_p`) (See Figure 2).
A simple slopes analysis revealed that people with higher levels of violence exposure showed lower strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$vio_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.Flanker$p_sum`% of *p*s < .05), and showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$p_sum`% of *p*s < .05).

There was no significant main effect for unpredictability (bootstrapped *p* = `r study2_aim3_results_list$Task_unp$boot_p`).
However, there was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_unp$CI`, `r study2_aim3_results_list$Interaction_unp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim3_results_list$Interaction_unp$boot_p`).
A simple slopes analysis revealed that people with higher levels of unpredictability did not differ in their strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$unp_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.Flanker$p_sum` % of *p*s < .05), but showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$p_sum`% of *p*s < .05).

```{r figure3, fig.height=9, fig.width = 7, fig.id = "figure3", fig.cap.style = "Figure Caption", fig.cap="Multiverse results for the within-subjects comparison of Flanker and Global-Local information processing. Panel A depicts the multiverse interaction effects, with the thick black lines denoting the median slope and the thin lines denoting effects for each combination of arbitrary decisions. Blue lines indicate significant effects (*p* > .05), and grey lines indicate non-significant effects (*p* > .05). Panel B depicts sorted beta coefficients across each arbitrary decision. Panel C depicts the percentage of variance that each arbitrary decision explains in the standardized effect."}

knitr::include_graphics("figures/fig3.png")
```
<br>

To sum up, Study 2 provided additional support for the basic finding that violence exposure and unpredictability were associated with lower strength of perceptual input but not with differences in interference; with the caveat that the associations for unpredictability only showed up in pooled analyses.
People with more exposure to violence and unpredictability also processed information more slowly on the Global-Local Task.
In line with our expectations, childhood exposure to violence was associated with both lowered strength of perceptual input and a more holistic processing style. 
The same processing style was observed for participants with more exposure to unpredictability, although they did not show lowered strength of perceptual input.

# General discussion

We investigated how two dimensions of childhood adversity---violence exposure and environmental unpredictability---are related to differences in how people attend to and process information.
Specifically, we hypothesized that exposure to adversity might lead to a present-oriented attention style that would facilitate rapidly detecting novel or changing information, yet which would interfere with ignoring distractors.
Across one pilot and two main studies, we tested how adversity was associated with performance on different attention tasks.
The Pilot study compared performance on a Cued Attention Task, Change Detection Task, and a Flanker.
Two follow-up studies focused on the Flanker, with Study 2 also including a Global-Local Task.
We leveraged DDM to estimate the processes underlying lowered and improved performance.
This allowed us to investigate whether performance differences were associated with abilities (i.e., attention orientation, interference control, stimulus processing), or ability-irrelevant processes (e.g., stimulus encoding, response execution, response caution).
Across all primary and exploratory analyses, we leveraged multiverse analysis to systematically assess the robustness of our findings against several uncontrollable aspects of the online assessment (e.g., distractions, fullscreen exits).

### Main insights

We found little to no support for the presence of a present-oriented attention style in people exposed to adversity.
More childhood exposure to violence was associated with slower processing of subtle changes on the Change Detection Task and lower quality of perceptual input on the Flanker Task.
It was not associated with speed of processing of peripheral information on the Cued Attention Task.
Zooming in on the Flanker, our two main studies found mixed evidence for the hypotheses that violence exposure and unpredictability were associated with lower strength of perceptual input.
This mixed evidence suggests that people with more exposure to these adversities process information less deeply, making it more difficult to make judgments about target and distractor information in equal measure.
This was corroborated by the pooled analyses across studies, which found that both exposure to violence and unpredictability were associated with lower strength of perceptual input, but not with differences in the ability to inhibit distractors.
This finding contradicts the standard deficit interpretation of lowered performance on inhibition tasks by people with more adversity exposure (discussed below).
In addition, lowered strength of perceptual input was associated with a holistic processing style.
Thus, we did not find evidence that people with more violence exposure have more difficulties with inhibiting task-irrelevant information.

Our findings of the DDM decomposition of Flanker performance challenge previous interpretations based on raw performance.
Previous studies have found that people exposed to adversity and/or low SES backgrounds have longer RTs on incongruent trials relative to congruent trials [@farah_2006; @fields_2021; @mezzacappa_2004; @mittal_2015; @noble_2005], which is commonly interpreted as an impaired ability to inhibit irrelevant information.
This fits with adaptive hypotheses, as inhibition is assumed to be useful mostly in stable and predictable environment that afford long-term goal pursuit, but can be costly in unpredictable and potentially dangerous environments [@fields_2021; @mittal_2015; @daly_2005].
Contrary to previous studies, we found little to no evidence for performance differences on the basis of raw RTs.
In addition, our DDM analyses showed that performance differences on the Flanker are not driven by differences in interference control, but by more basic processes that are not typically considered when interpreting Flanker performance.

Our findings align with a broader literature that is critical of the validity of the Flanker in particular, and that of cognitive control tasks more generally.
As noted, several studies have failed to find coherent correlations between raw performance on different cognitive control tasks [e.g., @loffler_2022; @rey_mermet_2019; @rouder_2019; @stahl_2014].
For example, previous research comparing several cognitive control tasks across different data sets using cognitive modeling found that shared variance between these tasks was mostly associated with processing speed and strategies (e.g., speed-accuracy trade-offs) [@hedge_2022].
Moreover, the modeling parameters reflecting conflict processing (similar to interference in our study) were barely correlated.
Similarly, previous work has shown that individual differences on common EF tasks---among which the Flanker Task---can be fully accounted for by general processing speed [@loffler_2022].
This literature, together with the findings reported here, underscore that researchers should be cautious when drawing inferences about cognitive control abilities in people exposed to adversity based on raw RTs and performance on individual tasks.

Finally, we showed that people exposed to adversity had a more holistic processing style, and that this style was associated with lower strength of perceptual input on the Flanker. 
This could mean that people with more adversity exposure processed the Flanker display more holistically; that is, focused less on individual arrows and more on the collection of arrows as a whole.
One (tentative) interpretation is that in the absence of threatening or otherwise salient information, people with more exposure to adversity attend to and process information in the environment globally and less deeply. 
They might only shift to local processing of a single source of information if it seems threatening or otherwise salient.
This would be consistent with research showing that growing up in a disadvantaged environment decreases the efficiency of the brain's (resting-state) salience network, which is in turn associated with lower raw performance on certain cognitive tasks [@cermakova_2023; @gellci_2019; @hilger_2017; @yuan_2012].
This research also shows that in situations of acute stress, mental resources are reallocated to this salience network, increasing vigilance and facilitating adequate responding. 
Indeed, a few studies show that cognitive abilities that may be particularly relevant in adverse contexts---such as attention shifting and working memory updating---may be enhanced in people from adversity when they experience acute stress [@mittal_2015; @young_2018].

### Strengths, limitations, and future directions

Our study has three main strengths. 
First, each study included socioeconomically diverse participants.. 
Second, the DDM allowed us to decompose performance in a more nuanced way than is possible with (typically used) raw performance scores.
Third, the multiverse analyses provided a systematic overview of the robustness of our findings under different analytical decisions. 
Our study has three main limitations.
First, all experiments were conducted online, which reduced control over people's testing environment, equipment, and behavior.
Indeed, our results were the least robust against participants who skipped the screen-scaling procedure (to ensure the stimuli were adequately sized) and interruptions during the tasks, which are factors that are largely out of our control.
Second, we deviated from our preregistrations in a number of ways in all studies, due to progressive insight.

Our findings suggest two main directions for future research.
First, future studies could replicate and expand upon our finding that lower quality of information processing in people exposed to adversity is associated with a more holistic processing style.
For example, future work could investigate whether people with more adversity exposure shift from holistic to a detail-oriented processing in situations of acute stress or otherwise salient information.
Second, our results suggest that lower strength of perceptual input is likely the result of both processing styles, as well as of slower general processing.
Future research could try to tease apart these sources using a within-subjects design simultaneously measuring inhibition, processing styles, and basic processing speed.
Third, some research suggests that inhibition is not a unitary construct, instead distinguishing between response inhibition (which involves suppressing a prepotent response) and cognitive inhibition (which involves selective attention in the presence of distractors). 
Exposure to adversity might shape these two types of inhibition in different ways.
For example, studies find that acute stress impairs performance on tasks of cognitive inhibition (of which the Flanker is an example) and enhances performance on tasks of response inhibition [for a meta-analysis, see @shields_2017].
Future work could assess inhibition more broadly, e.g., by including tasks that are hypothesized to require cognitive or response inhibition.

### General conclusion

We found that people with more childhood adversity exposure perform worse on the Flanker not because of an impairment in their ability to inhibit distracting information, but as a result of lower strength of perceptual input.
Our results suggest that people with more adversity exposure are not worse at inhibiting distractions; rather, they do not seem to process information in the environment deeply unless it proves to be a reliable and important source of information.
These findings challenge dominant interpretations, which infer an inhibition deficit from lowered performance.
This is an important difference not just for theory development, but also for future interventions aimed at closing performance gaps.
For example, when applied to school contexts, interventions based on an inhibition interpretation would focus on the learning environment, perhaps removing things from the classroom that could be distracting.
In contrast, an intervention based on an information processing interpretation might instead focus on increasing the apparent relevance of the learning materials, perhaps by providing more repetition or by making the content more ecologically relevant [@young_2022].
Thus, cognitive modeling can offer crucial insights for our understanding of cognitive abilities in adverse conditions.

\pagebreak

# References {#refs}

### 2024-01-17 manuscript/pilot_stage_objects.R

@@ -2,6 +2,7 @@ library(tidyverse)
 library(patchwork)
 library(ggsci)
 library(here)
+library(flextable)
 
 
 source(here("preregistrations/1_pilot/scripts/custom_functions/functions_corrplot.R"))
@@ -63,43 +64,6 @@ sample_pilot <- cleaned_data |>
     ))
 
 
-
-## IV correlations ----
-
-pilot_iv_cor_table <- cleaned_data |> 
-  select(violence_mean, fighting_mean, violence_composite, 
-         quic_total_mean, unp_mean, chaos_mean, change_env_mean, unpredictability_obj, unpredictability_composite) |> 
-  corr_table(
-    numbered = T,
-    c.names = c("Neigh. violence", "Fighting", "Violence comp.", 
-                "QUIC", "Perc. unpredictability", "CHAOS", "Env. change", "Obj. unpredictability", "Unpredictability comp"),
-    stats = c("mean", "sd", "median", "min", "max")
-  ) |> 
-  add_column(empty1 = "", .after = 4) |> 
-  mutate(across(
-    everything(),
-    ~ifelse(is.na(.), "", .)
-  )) |> 
-  mutate(across(
-    everything(),
-    ~formatC(.,  digits = 2, width = 3, flag = "0", format = 'f'))) |> 
-  flextable() |> 
-  width("empty1", width = .2) %>% 
-  width(j = 1, width = .75) %>% 
-  set_header_labels(Variable = "", empty1 = "") %>% 
-  add_header_row(
-    values = c(" ", "Violence exposure", " ", "Environmental unpredictability"),
-    colwidths = c(1, 3, 1, 6)
-  ) %>% 
-  border_remove() %>% 
-  border(i = 1, j = c("1","2","3","4","5","6","7","8","9"), border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
-  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 14, border.bottom = fp_border_default(), part = "body") %>% 
-  align(i = 1:14, j = 1, align = "left", part = "body") %>% 
-  bold(i = 1:2, part = "header") %>% 
-  set_table_properties(width = 1, layout = "autofit")
-
 # Main results  -----------------------------------------------------------
 
[…]

### 2024-01-17 manuscript/pooled_stage_objects.R

@@ -7,26 +7,26 @@ library(specr)
 
 source(here("preregistrations/1_pilot/scripts/custom_functions/functions_corrplot.R"))
 
+source(here("manuscript/pilot_stage_objects.R"))
+source(here("manuscript/study1_stage_objects.R"))
+source(here("manuscript/study2_stage_objects.R"))
+
 pilot_data = read_csv(here("data/1_pilot/2_cleaned_data.csv")) |> mutate(study = "pilot")
 study1_data = read_csv(here("data/2_study1/2_cleaned_data.csv")) |> mutate(study = "study1")
-
-
-
+study2_data = read_csv(here("data/3_study2/2_cleaned_data.csv")) |> mutate(study = "study2")
 # IV correlations ---------------------------------------------------------
 
 iv_cor_pooled_table <-  bind_rows(
     pilot_data |> 
       mutate(id = paste0("pilot", id)) |> 
       rename(
-        vio_comp     = violence_composite,
-        unp_obj_comp = unpredictability_obj,
-        unp_subj_comp = unpredictability_subj,
-        unp_comp     = unpredictability_composite,
         pcunp_mean   = unp_mean,
         nvs_mean     = violence_mean
       ),
     study1_data |> 
-      mutate(id = paste0("study1", id))
+      mutate(id = paste0("study1", id)),
+    study2_data |> 
+      mutate(id = paste0("study2", id)) |> select(-weight)
   ) |> 
 select(nvs_mean, fighting_mean, vio_comp, 
        quic_total_mean, pcunp_mean, chaos_mean, change_env_mean, unp_obj_comp, unp_subj_comp, unp_comp) |> 
@@ -68,17 +68,23 @@ select(nvs_mean, fighting_mean, vio_comp,
 
 
 demographics_table <- list(
-      age = map_dfr(list(pilot_data, study1_data), function(x) { 
+      n = map_dfr(list(pilot_data, study1_data, study2_data), function(x){
+        x |> 
+          summarise(stat = n() |> as.character()) |> 
+          mutate(categories = "N") |> 
+          mutate(study = x |> pull(study) |> unique())
+      }),
+      age = map_dfr(list(pilot_data, study1_data, study2_data), function(x) { 
         x |> 
         summarise(stat = paste0(paste0(round(mean(dems_age, na.rm = T),2), " (", round(sd(dems_age, na.rm = T), 2), ")"))) |> 
         mutate(categories = "Mean age (SD)") |> 
[…]

### 2024-01-17 manuscript/study1_stage_objects.R

@@ -10,6 +10,7 @@ cleaned_data = read_csv(here("data/2_study1/2_cleaned_data.csv"))
 study1_data <- cleaned_data
 load(file = here("preregistrations/2_study1/analysis_objects/primary_multiverse_summaries.RData"))
 load(file = here("preregistrations/2_study1/analysis_objects/exploratory_multiverse_summaries.RData"))
+load(file = here("preregistrations/2_study1/analysis_objects/study1_bootstrap_pvalues.RData"))
 
 get_alphas <- function(data, string) {
   (data |> 
@@ -75,11 +76,13 @@ sample_pilot <- cleaned_data |>
 theme_set(
   theme_bw() +
     theme(
-      axis.line.y       = element_line(),
-      axis.line.x       = element_line(),
-      axis.text.y       = element_text(size = rel(1)),
+      axis.line.y       = element_line(linewidth = 1),
+      axis.line.x       = element_line(linewidth = 1),
+      axis.text.y       = element_text(size = 14),
+      axis.text.x       = element_text(size = 14),
       axis.title.y      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
-      axis.ticks.y      = element_line(),
+      axis.ticks.y      = element_blank(),
+      axis.ticks.x      = element_blank(),
       
       panel.border      = element_blank(), 
       panel.spacing.y   = unit(0.5, "lines"),
@@ -102,10 +105,10 @@ pval_colors <- c("sig" = "#006D77", "non-sig" = "gray70")
 
 ## 1.1 Pooled data comparison ----
 
-study1_prim_ssp_pooled_effect_plot <- unique(prim_ssp_pooled_effects_sum$dv) |> 
+study1_prim_ssp_pooled_effect_plot <- unique(study1_prim_ssp_pooled_effects_sum$dv) |> 
   map(function(x) {
     
-    effect_data <- prim_ssp_pooled_effects_sum |> 
+    effect_data <- study1_prim_ssp_pooled_effects_sum |> 
       filter(dv == x) |> 
       select(decision, dv, term, estimate, p.value) |> 
       mutate(term = ifelse(term == "(Intercept)", "intercept", term)) |> 
[…]

### 2024-01-17 manuscript/study2_stage_objects.R

@@ -1,0 +1,1117 @@
+library(tidyverse)
+library(here)
+library(ggsci)
+library(patchwork)
+library(flextable)
+library(specr)
+
+
+cleaned_data = read_csv(here("data/3_study2/2_cleaned_data.csv"))
+study2_data <- cleaned_data
+load(file = here("preregistrations/3_study2/analysis_objects/primary_multiverse_summaries.RData"))
+load(file = here('preregistrations/3_study2/analysis_objects/study2_bootstrap_pvalues.RData'))
+
+get_alphas <- function(data, string) {
+  (data |> 
+     select(matches(string)) |> 
+     psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+}
+
+
+
+
+# Descriptives ------------------------------------------------------------
+
+## IV distributions ----
+txt_ivs_dist_study2 <- 
+  cleaned_data |> select(matches("(mean|total|composite|edu_parents_recoded)$")) |> 
+  map(function(x) {
+    list(
+      mean = round(mean(x, na.rm = T),2),
+      sd   = round(sd(x, na.rm = T),2)
+    )
+  })
+
+txt_ivs_alpha_study2 <- 
+  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
+    "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
+    "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
+    "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
+  map(function(x) {
+    (cleaned_data |> 
+       select(matches(x)) |> 
+       psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+  }) |> 
+  setNames(c("stai_s", "violence", "unp", 
+             "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
+             "quic_total", "chaos", "ses", "impuls", "fos_pa", "fos_tp", "fos_fc", "fos_fo", "depression"))
+
+
+## Sample characteristics ----
+
[…]

### 2024-01-17 preregistrations/1_pilot/materials/global_variables.js
various code updates in prep for full manuscript and supplements

@@ -18,13 +18,13 @@ var resize_screen = {
 }};
 
 var fullscreenmode = {
-  type: 'fullscreen',
+  type: jsPsychFullscreen,
   fullscreen_mode: true
 };
 
 // Remove cursor during cognitive tasks
 var cursor_off = {
-    type: 'call-function',
+    type: 'callfunction',
     func: function() {
         document.body.style.cursor= "none";
     }
@@ -33,7 +33,7 @@ var cursor_off = {
 
 // Make cursor visible again in between cognitive tasks or when a button response is required.
 var cursor_on = {
-    type: 'call-function',
+    type: 'callfunction',
     func: function() {
         document.body.style.cursor= "auto";
     }
@@ -52,7 +52,7 @@ var feedback = {
     }
   },
   trial_duration: 2000,
-  choices: jsPsych.NO_KEYS,
+  choices: "NO_KEYS",
   data: {
     variable: 'feedback'
   }
@@ -61,7 +61,7 @@ var feedback = {
 
 // End of Cognitive task part of the experiment.
 var cognitive_tasks_end = {
-  type: "html-button-response",
+  type: 'html-button-response',
   stimulus: 
   "Great job!<br><br>" +
   "You have finished the first part of the experiment.<br><br>" +

### 2024-01-17 preregistrations/1_pilot/scripts/0_data_prep/7_merge_data.R

@@ -39,7 +39,7 @@ cleaned_data <-
   # Remove participants who have no task data
   filter(!is.na(rt_change) | !is.na(rt_cueing_cued) | !is.na(rt_flanker_congruent)) |>
   mutate(across(matches('meta.*duration.*_z'), as.numeric)) |> 
-  mutate(unpredictability_subj = as.numeric(unpredictability_subj)) |>
+  mutate(unp_subj = as.numeric(unp_subj)) |>
   # Fix typos in age
   mutate(dems_age = ifelse(dems_age < 18 | dems_age > 30, NA, dems_age))
 

### 2024-01-17 preregistrations/1_pilot/scripts/3_exploratory_analyses.R

@@ -11,10 +11,29 @@ library(ggeffects)
 library(interactions)
 library(parameters)
 library(specr)
+library(flextable)
 
 
 load(here("data", "1_pilot", "2_cleaned_data.Rdata"))
 load(here("data", "1_pilot", "0_self_report_raw.Rdata"))
+load("preregistrations/1_pilot/analysis_objects/hddm_model_objects.RData")
+
+load('data/1_pilot/2_cleaned_data.RData')
+source(here("preregistrations", "1_pilot", "scripts", "custom_functions", "DBDA2E-utilities.R"))
+
+source("preregistrations/1_pilot/scripts/custom_functions/ddm_functions.R")
+
+# set up flextable for tables
+set_flextable_defaults(
+  font.family = "Times", 
+  font.size = 10,
+  font.color = "black",
+  line_spacing = 1,
+  padding.bottom = 1, 
+  padding.top = 1,
+  padding.left = 1,
+  padding.right = 1
+)
 
 
 # 1. EFA: Unpredictability ------------------------------------------------
@@ -80,495 +99,126 @@ efa_tidy <- tidy(efa_model) %>%
     `5` = fl5
   ) 
 
+
+
 # Extract new variables from EFA model
-efa_vars <- efa_tidy %>%
-  mutate(label = case_when(
-    !is.na(`1`)                                                     ~ "efa_daily_unp",
-    !is.na(`2`) & is.na(`1`)                                        ~ "efa_routine",
-    !is.na(`3`) & is.na(`1`) & is.na(`2`)                           ~ "efa_spatial_unp",
-    !is.na(`4`) & is.na(`1`) & is.na(`2`) & is.na(`3`)              ~ "efa_chaos_clutter",
-    !is.na(`5`) & is.na(`1`) & is.na(`2`) & is.na(`3`) & is.na(`4`) ~ "efa_social_unp",
-    TRUE ~ "other"
-  )) %>%
-  filter(label != "other") %>%
-  select(var, label)
+pilot_efa_table <- efa_tidy %>%
+  rename(
+    "Household\nstability/conflict" = `1`,
+    "Monitoring/neglect" = `2`,
+    "Macro unp." = `3`,
+    "Disorganization" = `4`,
+    "People in household" = `5`
+  ) |> 
+  select(-var) |> 
+  flextable() |> 
+  autofit() |> 
+  bold(i = 1:24, j = 2) |> 
[…]

### 2024-01-17 preregistrations/1_pilot/scripts/3_exploratory_analyses/hddm.R

@@ -376,7 +376,7 @@ hddm_cueing_data <- mcmc_cueing_mod1 |>
 
 
 save(
-  mcmc_flanker_mod1, hddm_flanker_data,
-  mcmc_cueing_mod1, hddm_cueing_data,
-  mcmc_change_mod1, hddm_change_data,
+  mcmc_flanker_mod1, hddm_flanker_data, flanker_id_matches,
+  mcmc_cueing_mod1, hddm_cueing_data, cueing_id_matches,
+  mcmc_change_mod1, hddm_change_data, change_id_matches,
   file = 'preregistrations/1_pilot/analysis_objects/hddm_model_objects.RData')

### 2024-01-17 preregistrations/1_pilot/scripts/custom_functions/ddm_functions.R

@@ -1,0 +1,140 @@
+
+extract_traces <- function(mcmc, chains = 3, iterations = 12000) {
+  
+  mcmc |> 
+    select(starts_with("mu")) |> 
+    mutate(
+      n = rep(1:iterations, chains),
+      chains = rep(1:chains, each = iterations))  |> 
+    rename(
+      a  = muAlpha,
+      t0 = muTau, 
+      v  = muDelta
+    ) |> 
+    pivot_longer(-c(n, chains), names_to = 'parameter', values_to = 'value')
+}
+
+
+
+extract_traces_2con <- function(mcmc, chains = 3, iterations = 1000) {
+  
+  mcmc |> 
+    select(starts_with("mu")) |> 
+    mutate(
+      n = rep(1:iterations, chains),
+      chains = rep(1:chains, each = iterations))  |> 
+    rename(
+      a   = muAlpha,
+      t01 = `muTau[1]`, 
+      t02 = `muTau[2]`,
+      v1  = `muDelta[1]`,
+      v2  = `muDelta[2]`
+    ) |> 
+    pivot_longer(-c(n, chains), names_to = 'parameter', values_to = 'value')
+}
+
+extract_traces_2con_expl <- function(mcmc, chains = 3, iterations = 1000) {
+  
+  mcmc |> 
+    select(starts_with("mu")) |> 
+    mutate(
+      n = rep(1:iterations, chains),
+      chains = rep(1:chains, each = iterations))  |> 
+    rename(
+      a1  = `muAlpha[1]`,
+      a2  = `muAlpha[2]`,
+      t01  = `muTau[1]`,
+      t02 = `muTau[2]`,
+      v1  = `muDelta[1]`,
+      v2  = `muDelta[2]`
+    ) |> 
+    pivot_longer(-c(n, chains), names_to = 'parameter', values_to = 'value')
+}
+
+
+
+extract_ddm_estimates <- function(mcmc, task_prefix, id_matches) {
+  
+  mcmc |> 
+    pivot_longer(everything(), names_to = "parameter", values_to = "estimated") |> 
+    group_by(parameter) |> 
+    summarise(estimated = mean(estimated, na.rm = T)) |> 
+    filter(str_detect(parameter, pattern = 'deviance|^mu|^prec', negate = T)) |> 
+    separate(col = parameter, into = c('parameter', 'id_num'), sep = "\\[") |> 
+    mutate(
[…]

### 2024-01-17 preregistrations/2_study1/scripts/2_primary_analyses.R

@@ -21,14 +21,19 @@ load("preregistrations/2_study1/analysis_objects/hddm_model_objects.RData")
 # Pilot study
 pilot_data <- read_csv("data/1_pilot/2_cleaned_data.csv") |> 
   select(id, scale_factor, fullscreenenter, fullscreenexit, attention_interrupt_sum, att_noise, meta_captcha,
-         vio_comp = violence_composite, rt_flanker_congruent, rt_flanker_incongruent, acc_flanker_congruent, acc_flanker_incongruent,
+         vio_comp, rt_flanker_congruent, rt_flanker_incongruent, acc_flanker_congruent, acc_flanker_incongruent,
          a_flanker = flanker_ssp_a, t0_flanker = flanker_ssp_t0, p_flanker = flanker_ssp_p, interference_flanker = flanker_ssp_interference) %>%
   mutate(
     id = str_c("pilot_", id),
     study = -1,
     counterbalance = 'pilot',
-    scale_factor = ifelse(round(scale_factor, 4) == 0.3081, 0,1)
-  )
+    scale_factor = ifelse(round(scale_factor, 4) == 0.3081, 0,1),
+    rt_diff      = rt_flanker_congruent - rt_flanker_incongruent
+  ) |> 
+  filter(!is.infinite(interference_flanker)) |> 
+  mutate(
+    a_flanker                = log(a_flanker),
+    interference_flanker     = ifelse(scale(interference_flanker) > 3.2, NA, interference_flanker))
 
 
 # Study 1
@@ -48,13 +53,14 @@ study1_data <-  read_csv("data/2_study1/2_cleaned_data.csv") |>
   mutate(
     id           = str_c("study1_", id),
     study        = 1,
-    scale_factor = ifelse(round(scale_factor, 4) == 0.9007, 0,1)
-  )
+    scale_factor = ifelse(round(scale_factor, 4) == 0.9007, 0,1),
+    rt_diff      = log(rt_flanker_congruent) - log(rt_flanker_incongruent),
+    a_flanker    = log(a_flanker),
+    interference_flanker = ifelse(scale(interference_flanker) > 3.2, NA, interference_flanker)
+  ) 
 
 # Combine data of pilot study and study 1
-prim_ssp_data_pooled <- bind_rows(pilot_data, study1_data) |> 
-  filter(is.finite(interference_flanker)) |> 
[…]

### 2024-01-17 preregistrations/2_study1/scripts/3_exploratory_analyses.R

@@ -123,14 +123,14 @@ efa_data_combined <- full_join(
   mutate(cutoff = factor(cutoff, levels = c("Both studies", "Pilot only", "Study 1 only"))) 
 
 
-efa_data_combined %>%
+study1_efa_fig <- efa_data_combined %>%
   mutate(
     Factor = case_when(
-      Factor == "f1" ~ "Factor 1 - Household stability/conflict",
-      Factor == "f2" ~ "Factor 2 - Monitoring/neglect",
-      Factor == "f3" ~ "Factor 3 - Macro unpredictability",
-      Factor == "f4" ~ "Factor 4 - Clutter/disorganization",
-      Factor == "f5" ~ "Factor 5 - People in household",
+      Factor == "f1" ~ "Household stability/conflict",
+      Factor == "f2" ~ "Monitoring/neglect",
+      Factor == "f3" ~ "Macro unp.",
+      Factor == "f4" ~ "Clutter/disorganization",
+      Factor == "f5" ~ "People in household",
     )
   ) %>%
   ggplot(aes(Loading_pilot, Loading_study1, color = cutoff)) +
@@ -146,593 +146,4 @@ efa_data_combined %>%
     color = "Loading > .32"
   )
 
-# Compute variables based on EFA for pilot data and join with study data
-pilot_efa_vars <- efa_data_combined %>%
-  select(var, Factor, Loading_pilot) %>%
-  mutate(Loading_pilot = ifelse(Loading_pilot <= .32, NA, Loading_pilot)) %>%
-  drop_na(Loading_pilot) %>%
-  pivot_wider(names_from = "Factor", values_from = "Loading_pilot") %>%
-  mutate(label = case_when(
-    !is.na(f1)                                                 ~ "efa_stability_conflict",
-    !is.na(f2) & is.na(f1)                                     ~ "efa_monitoring_neglect",
-    !is.na(f3) & is.na(f1) & is.na(f2)                         ~ "efa_spatial_unp",
-    !is.na(f4) & is.na(f1) & is.na(f2) & is.na(f3)             ~ "efa_clutter_disorganization",
-    !is.na(f5) & is.na(f1) & is.na(f2) & is.na(f3) & is.na(f4) ~ "efa_social_unpredictability",
-    TRUE ~ "other"
-  ))
-
-cleaned_data_pilot %<>%
[…]

### 2024-01-17 preregistrations/2_study1/scripts/4_bootstrap_mult.R

@@ -1,0 +1,120 @@
+
+source("preregistrations/2_study1/scripts/custom_functions/functions_analyses.R")
+cleaned_data <- read_csv("data/2_study1/2_cleaned_data.csv") 
+
+load("preregistrations/2_study1/analysis_objects/primary_mult_results.RData")
+
+# 2. Prepare data ------------------------------------------------------------
+
+# Pilot study
+pilot_data <- read_csv("data/1_pilot/2_cleaned_data.csv") |> 
+  select(id, scale_factor, fullscreenenter, fullscreenexit, attention_interrupt_sum, att_noise, meta_captcha,
+         vio_comp, rt_flanker_congruent, rt_flanker_incongruent, acc_flanker_congruent, acc_flanker_incongruent,
+         a_flanker = flanker_ssp_a, t0_flanker = flanker_ssp_t0, p_flanker = flanker_ssp_p, interference_flanker = flanker_ssp_interference) %>%
+  mutate(
+    id = str_c("pilot_", id),
+    study = -1,
+    counterbalance = 'pilot',
+    scale_factor = ifelse(round(scale_factor, 4) == 0.3081, 0,1),
+    rt_diff      = rt_flanker_congruent - rt_flanker_incongruent
+  ) |> 
+  filter(!is.infinite(interference_flanker)) |> 
+  mutate(
+    a_flanker                = log(a_flanker),
+    interference_flanker     = ifelse(scale(interference_flanker) > 3.2, NA, interference_flanker))
+
+
+# Study 1
+
+study1_data <-  read_csv("data/2_study1/2_cleaned_data.csv") |> 
+  select(id, scale_factor, fullscreenenter, fullscreenexit, attention_interrupt_sum, att_noise, meta_captcha,
+         vio_comp, rt_flanker_congruent_std, rt_flanker_incongruent_std, acc_flanker_congruent_std, acc_flanker_incongruent_std,
+         a_flanker_std, t0_flanker_std, p_flanker_std, interference_flanker_std) %>%
+  rename(rt_flanker_congruent = rt_flanker_congruent_std,
+         rt_flanker_incongruent = rt_flanker_incongruent_std,
+         acc_flanker_congruent = acc_flanker_congruent_std,
+         acc_flanker_incongruent = acc_flanker_incongruent_std,
+         a_flanker = a_flanker_std,
[…]

### 2024-01-17 preregistrations/3_study2/scripts/0_data_prep/3_clean_task_data.R

@@ -9,17 +9,18 @@ library(sjlabelled)
 
 # Load data ---------------------------------------------------------------
 
-load(here("data", "2_study1", "0_task_data_raw.Rdata"))
+load(here("data", "3_study2", "0_task_data_raw.Rdata"))
 
-source("preregistrations/2_study1/scripts/custom_functions/functions_exclusions.R")
+source("preregistrations/3_study2/scripts/custom_functions/functions_exclusions.R")
 
 # Planned exclusions ------------------------------------------------------
 
+## Flanker ----
+
 flanker_data_clean <- flanker_data %>%
-    group_by(id, condition) %>%
+    group_by(id) %>%
     mutate(
       # Is accuracy above the cut-off for performance at chance level?
-      #ex_narb_acc_below_cutoff_50 = ifelse( (sum(correct, na.rm=T)/n())*100 < gbinom(50, 0.5), TRUE, FALSE),
       ex_narb_acc_below_cutoff = ifelse( (sum(correct, na.rm=T)/n())*100 < gbinom(64, 0.5), TRUE, FALSE),
       # Do all participants have the expected number of trials? 
       ex_narb_rowcount         = n(),
@@ -43,13 +44,7 @@ flanker_data_clean <- flanker_data %>%
     ) %>%
   left_join(browser_interactions_summary %>% select(id, event_during_flanker))
 
-
-
 # Apply exclusions --------------------------------------------------------
-# Exclude participants who did not complete one or more conditions of the Flanker task
-ids_to_exclude <- c(
-  flanker_data_clean %>% group_by(id) %>% summarise(n_condition = length(unique(condition))) %>% filter(n_condition < 3) %>% select(id) %>% distinct() %>% pull
-)
 
 flanker_data_clean %<>%
   # Remove invalid trials
@@ -57,91 +52,114 @@ flanker_data_clean %<>%
   filter(!ex_narb_invalid_trial) %>%
   # Exclude participants who did not pass the quality checks
   filter(ex_narb_flanker_pass == TRUE) %>%
-  # Exclude participants who did not complete all tasks
-  filter(!id %in% ids_to_exclude) %>%
   # Exclude participants with blur events during the task
   filter(!event_during_flanker) %>%
-  # Exclude participants based on their own feedback:
-  mutate(across(c(rt, correct), ~ifelse(id == 14 & condition == "degraded", NA, .))) %>%
   select(-starts_with("ex_narb"))
-
-
-
-
[…]

### 2024-01-17 preregistrations/3_study2/scripts/0_data_prep/4_ssp_estimation.R

@@ -10,7 +10,7 @@ library(glue)
 library(flankr)
 library(tictoc)
 
-load(here("data", "2_study1", "1_task_data_clean.Rdata"))
+load(here("data", "3_study2", "1_task_data_clean.Rdata"))
 
 
 
@@ -24,7 +24,7 @@ flanker_ssp_setup <- flanker_data_clean_average %>%
       x %>%
         mutate(rt=rt/1000) %>%
         rename(subject = id, accuracy = correct) %>%
-        select(subject, condition, congruency, accuracy, rt)
+        select(subject, congruency, accuracy, rt)
     }) 
   )
 
@@ -54,12 +54,12 @@ n_final_pass <- 50000
 # Model Fit: Standard Condition -------------------------------------------
 
 # In case processing was interrupted, we check which subjects were already processed and skip them
-processed_files <- list.files(here("data", "2_study1")) %>%
-  str_subset("ssp_fit_standard") %>%
-  str_replace_all("ssp_fit_standard|.csv", "") %>%
+processed_files <- list.files(here("data", "3_study2")) %>%
+  str_subset("ssp_fit") %>%
+  str_replace_all("ssp_fit|.csv", "") %>%
   as.numeric()
 
-ssp_results_standard <- flanker_ssp_setup %>%
+ssp_results <- flanker_ssp_setup %>%
   mutate(
     flanker_data_long = map(flanker_data_long, function(x){
 
@@ -78,7 +78,7 @@ ssp_results_standard <- flanker_ssp_setup %>%
 plan(multisession, workers = cores - 2)
  
 # Find best starting parameters for each subject in the Standard Condition
-ssp_results_standard  %<>%
+ssp_results  %<>%
   mutate(
     results = future_map(flanker_data_long,
                   function(x) {
@@ -87,7 +87,6 @@ ssp_results_standard  %<>%
                     # Find best starting parameters
                     best_starting_parms <-
                       fitMultipleSSP(x, var = var_start_parms,
-                                     conditionName = "standard",
                                      nParms = n_start_parms,
                                      nTrials = n_first_pass,
                                      multipleSubjects = FALSE)
@@ -95,7 +94,7 @@ ssp_results_standard  %<>%
                     
                     # Perform final fit using best starting parameters
                     final_fit <-
-                      fitSSP(x, conditionName = "standard", 
+                      fitSSP(x, 
                              parms = best_starting_parms$bestParameters,
[…]

### 2024-01-17 preregistrations/3_study2/scripts/0_data_prep/5_hddm_estimation.R

@@ -1,0 +1,402 @@
+
+# Libraries ---------------------------------------------------------------
+library(tidyverse)
+library(multitool) #devtools::install_github("ethan-young/multitool", force = T)
+library(here)
+library(ggeffects)
+library(lmerTest)
+library(runjags)
+load("data/3_study2/1_task_data_clean.Rdata")
+load("data/3_study2/1_self_report_clean.Rdata")
+
+source("preregistrations/3_study2/scripts/custom_functions/DBDA2E-utilities.R")
+
+
+# Load data files ---------------------------------------------------------
+hddm_globloc_data <- globloc_data_clean_average |> 
+  select(globloc_data_long) |> 
+  unnest(globloc_data_long) |> 
+  select(id, rt, rule, correct) |> 
+  drop_na(rt) |> 
+  mutate(
+    rt           = rt / 1000,
+    rule = ifelse(rule == "local", 1, 2)
+  )
+  
+
+# congruency: congruent (1) vs incongruent (2)
+# condition: standard (1) vs enhanced (2) vs degraded (3)
+
+  
+mod <- "model {
+  #likelihood function
+  for (t in 1:nTrials) {
+    y[t] ~ dwiener(alpha[subject[t]], 
+                   tau[rule[t], subject[t]], 
+                   0.5, 
+                   delta[rule[t], subject[t]])
+  }
+  
+  for (s in 1:nSubjects) {
+    for (rule in 1:nRule) {
+
+      tau[rule, s] ~ dnorm(muTau[rule], precTau) T(.0001, 1)
+      delta[rule, s] ~ dnorm(muDelta[rule] , precDelta) T(-10, 10)
+      
+    }
+      alpha[s] ~ dnorm(muAlpha, precAlpha) T(.1, 5)
+  }
+  
+  #priors
+  for (rule in 1:nRule){ 
+    
+      muTau[rule] ~ dunif(.0001, 1)
+      muDelta[rule] ~ dunif(-10, 10)
+  
+  } 
+  muAlpha ~ dunif(.1, 5)
+  
+  precAlpha  ~ dgamma(.001, .001)
+  precTau ~ dgamma(.001, .001)
+  precDelta ~ dgamma(.001, .001)
+  
+}"
+
+initfunction <- function(chain){
+  return(list(
+    muAlpha = runif(1, .2, 4.9),
+    muTau = runif(2, .01, .05),
+    muDelta = runif(2, -9.9, 9.9),
[…]

### 2024-01-17 preregistrations/3_study2/scripts/0_data_prep/6_merge_data.R

@@ -8,10 +8,11 @@ library(glue)
 
 # Load data ---------------------------------------------------------------
 
-load(here("data", "2_study1", "1_self_report_clean.Rdata"))
-load(here("data", "2_study1", "1_task_data_clean.Rdata"))
-load(here("data", "2_study1", "1_SSP_objects.Rdata"))
-load('preregistrations/2_study1/analysis_objects/hddm_model_objects.RData')
+load(here("data", "3_study2", "1_self_report_clean.Rdata"))
+load(here("data", "3_study2", "1_task_data_clean.Rdata"))
+load(here("data", "3_study2", "1_SSP_objects.Rdata"))
+load('preregistrations/3_study2/analysis_objects/hddm_globloc_model_objects.RData')
+load('preregistrations/3_study2/analysis_objects/hddm_globloc_model2_objects.RData')
 
 
 # Combine data ------------------------------------------------------------
@@ -21,43 +22,26 @@ cleaned_data <-
   self_report_clean %>%
   # Task data: RTs and accuracy
   left_join(flanker_data_clean_average, by = "id") %>%
+  left_join(globloc_data_clean_average, by = "id") %>%
+  
   # Task data: DDM
   left_join(ssp_results_refit, by = "id") %>%
+  left_join(hddm_globloc_results_mod2) %>%
   left_join(resize_screen, by = "id") %>%
   left_join(browser_interactions_summary, by = "id") %>%
   # Remove participants who have no task data
-  filter(!is.na(rt_flanker_congruent_std), !is.na(rt_flanker_congruent_deg), !is.na(rt_flanker_congruent_enh)) %>%
-  # Manual exclusions
-  filter(!id %in% c(73, 99, 114, 163, 176, 304, 308, 335, 340, 483)) %>%
- # filter(!id %in% c(19, 121, 223, 8, 269, 464, 466, 491, 223)) %>%
+  filter(!is.na(rt_flanker_congruent)) %>%
   mutate(
-    interference_flanker_std = sda_flanker_std / rd_flanker_std,
-    interference_flanker_enh = sda_flanker_enh / rd_flanker_enh,
-    interference_flanker_deg = sda_flanker_deg / rd_flanker_deg,
-    # Remove age types
+    interference_flanker = sda_flanker/ rd_flanker,
+    # Remove age typ0s
     dems_age = ifelse(dems_age < 18 | dems_age > 30, NA, dems_age)
   )
 
 # .csv file (nested columns containing trial-level data are dropped)
[…]

### 2024-01-17 preregistrations/3_study2/scripts/4_exploratory_analyses.R

@@ -1,0 +1,118 @@
+
+library(tidyverse)
+library(ggsci)
+library(multitool) #devtools::install_github("ethan-young/multitool", force = T)
+library(here)
+library(ggeffects)
+library(interactions)
+library(lmerTest)
+library(parameters)
+library(specr)
+
+source("preregistrations/3_study2/scripts/custom_functions/functions_analyses.R")
+source("preregistrations/3_study2/scripts/custom_functions/functions_corrplot.R")
+
+load("data/3_study2/2_cleaned_data.rData") 
+
+load("preregistrations/3_study2/analysis_objects/hddm_globloc_model2_objects.RData")
+
+
+# 1. Bivariate correlations ------------------------------------------------------------
+
+
+# Pilot study
+pilot_data <- read_csv("data/1_pilot/2_cleaned_data.csv") |> 
+  select(id, 
+         depression_mean, impuls_mean, fos_fo_mean, ses_comp = poverty_composite,
+         a_flanker = flanker_ssp_a, t0_flanker = flanker_ssp_t0, p_flanker = flanker_ssp_p, interference_flanker = flanker_ssp_interference) %>%
+  filter(is.finite(interference_flanker)) |> 
+  mutate(
+    a_flanker           = log(a_flanker),
+    interference_flanker = ifelse(scale(interference_flanker) > 3.2, NA, interference_flanker)
+  )
+
+# Study 1
+
+study1_data <-  read_csv("data/2_study1/2_cleaned_data.csv") |> 
+  select(id, 
+         depression_mean, impuls_mean, fos_fo_mean, ses_comp,
+         a_flanker_std, t0_flanker_std, p_flanker_std, interference_flanker_std) %>%
+  rename(a_flanker = a_flanker_std,
+         t0_flanker = t0_flanker_std,
+         p_flanker = p_flanker_std,
+         interference_flanker = interference_flanker_std) %>%
+  mutate(
+    a_flanker    = log(a_flanker),
+    interference_flanker = ifelse(scale(interference_flanker) > 3.2, NA, interference_flanker)
+  ) 
+
+# Study 2
+study2_data <-  read_csv("data/3_study2/2_cleaned_data.csv") |> 
+  select(id,
+         depression_mean, impuls_mean, fos_fo_mean, ses_comp,
+         a_flanker, t0_flanker, p_flanker, interference_flanker,
+         v_globloc_local, v_globloc_global
+  ) %>%
+  mutate(
[…]

### 2024-01-17 preregistrations/3_study2/scripts/supplement/ssp_fit.R

@@ -3,10 +3,9 @@ library(here)
 library(furrr)
 library(parallel)
 library(flankr)
-library(cowplot)
 
-load(here("data", "2_study1", "1_SSP_objects.Rdata"))
-load(here("data", "2_study1", "2_cleaned_data.Rdata"))
+load(here("data", "3_study2", "1_SSP_objects.Rdata"))
+load(here("data", "3_study2", "2_cleaned_data.Rdata"))
   
   
 # Plot model fit ----------------------------------------------------------
@@ -16,16 +15,10 @@ cores <- detectCores()- 4
 plan('multisession', workers = cores)
 
 suspect_participants <- 
-  bind_rows(
-    ssp_results_refit %>% select(matches("^(a|t0|p|rd|sda|bbic|g2)_flanker_std"), id) %>% rename_with(.cols = !matches("id"), ~str_replace_all(.x, "_std", "")) %>% mutate(condition = "standard"),
-    ssp_results_refit %>% select(matches("^(a|t0|p|rd|sda|bbic|g2)_flanker_deg"), id) %>% rename_with(.cols = !matches("id"), ~str_replace_all(.x, "_deg", "")) %>% mutate(condition = "degraded"),
-    ssp_results_refit %>% select(matches("^(a|t0|p|rd|sda|bbic|g2)_flanker_enh"), id) %>% rename_with(.cols = !matches("id"), ~str_replace_all(.x, "_enh", "")) %>% mutate(condition = "enhanced")
-  ) %>%
-  #filter(id %in% c(73, 99, 176, 304, 340, 483)) %>%
+  ssp_results_refit %>% select(matches("^(a|t0|p|rd|sda|bbic|g2)_flanker"), id) %>%
   mutate(fit = pmap(., function(a_flanker, t0_flanker, p_flanker, rd_flanker, sda_flanker, g2_flanker, bbic_flanker, id, condition) {
     
     id_i = id
-    condition_i = condition
     
     plotFitSSP(
       modelFit = list(bestParameters = c(a_flanker, t0_flanker, p_flanker, rd_flanker, sda_flanker), g2 = g2_flanker, bBic = bbic_flanker),
@@ -33,7 +26,6 @@ suspect_participants <-
                     filter(id == id_i) %>% 
                     select(flanker_data_long) %>% 
                     unnest(flanker_data_long) %>% 
-                    filter(condition == condition_i) %>%
[…]

### 2024-01-17 preregistrations/4_supplemental/1_moderators.R

@@ -1,0 +1,53 @@
+library(tidyverse)
+library(lmerTest)
+library(interactions)
+library(ggeffects)
+
+
+# 1. Load data of all studies------------------------------------------------
+
+suppl_mod_pooled_data <- c("data/1_pilot/2_cleaned_data.csv", "data/2_study1/2_cleaned_data.csv", "data/3_study2/2_cleaned_data.csv") |> 
+  map_df(function(x){
+    read_csv(x) |> 
+      select(
+        id, vio_comp, unp_comp, stai_s_mean, depression_mean, 
+        matches("p_flanker|flanker_ssp_p"), matches("interference_flanker|flanker_ssp_interference"),
+        scale_factor, fullscreenexit, attention_interrupt_sum) %>% 
+      rename_with(.cols = matches("flanker_ssp_p|p_flanker_std"), .fn = ~sub(pattern = "flanker_ssp_p|p_flanker_std", "p_flanker", x = .)) |>
+      rename_with(.cols = matches("flanker_ssp_interference|interference_flanker_std"), .fn = ~sub(pattern = "flanker_ssp_interference|interference_flanker_std", "interference_flanker", x = .)) |>
+      mutate(
+        study = deparse(x) |> str_extract_all(string = _, pattern = "pilot|study\\d")
+      ) |> 
+      unnest(study)
+  }) |> 
+  select(-c(p_flanker_deg, p_flanker_enh)) |> 
+  filter(
+    study == "pilot" & round(scale_factor, 3) != 0.3081 | study %in% c("study1", "study2") & round(scale_factor, 4) != 0.9007,
+    fullscreenexit == 0, 
+    attention_interrupt_sum < 1,
+    !is.infinite(interference_flanker)
+  ) |> 
+  mutate(
+    study    = faux::contr_code_sum(study),
+    vio_comp = scale(vio_comp) |> as.numeric(),
+    unp_comp = scale(unp_comp) |> as.numeric())
+
+
+
+# 2. Main analyses --------------------------------------------------------
+
+suppl_mod_results <- multitool::run_multiverse(
+  .grid = 
+    suppl_mod_pooled_data |> 
+      multitool::add_variables("iv", vio_comp, unp_comp) |> 
+      multitool::add_variables("dv", p_flanker, interference_flanker) |> 
+      multitool::add_variables("mod", stai_s_mean, depression_mean) |> 
[…]

### 2024-01-17 supplement/supplement1_measures.Rmd
supplemental materials in progress

--- 2021-11-03 preregistrations/1_pilot/preregistration.Rmd
@@
 ---
-bibliography: references.bib
-csl: apa.csl
-output:
-  officedown::rdocx_document:
-    page_margins:
-      bottom: 1
-      footer: 0
-      gutter: 0
-      header: 0.5
-      left: 1
-      right: 1
-      top: 1
-    plots:
-      align: center
-      caption:
-        pre: 'Figure '
-        sep: '. '
-        style: Image Caption
-    reference_docx: reference-doc.docx
-    tables:
-      caption:
-        pre: 'Table '
-        sep: '. '
-        style: Table Caption
-  pdf_document: default
-  word_document: default
-keep_md: true
+title: "1_measurement_overview"
+author: "Stefan Vermeent"
+date: "2023-02-21"
+output: pdf_document
 ---
 
-```{r setup, include=FALSE}
+# 1. Descriptions of exploratory measures
 
-# Load libraries
-library(tidyverse)
-library(officer)
-library(flextable)
-library(here)
-library(pwr)
-
-## Custom function to restart numbering at the start of each new chapter.
-new_chapter <- function(){
-  if(!exists("chapter_count")) chapter_count <<- 0 
-  chapter_count <<- chapter_count + 1
-  }
-
-# set up chunk options
-knitr::opts_chunk$set(
-  echo = F,
-  fig.align = "center",
-  fig.pos = "!t", 
-  out.extra = "",
-  fig.show = "asis",
-  message = FALSE,
-  warning = FALSE
-)
-
-# set up flextable for tables
-set_flextable_defaults(
-  font.family = "Times", 
-  font.size = 10,
-  font.color = "black",
-  line_spacing = 1,
-  padding.bottom = 1, 
-  padding.top = 1,
-  padding.left = 1,
-  padding.right = 1
-)
-
-# Source necessary objects
-power_linear      <- read_csv(here("data", "1_pilot", "simulation", "power_linear_model.csv")) %>% mutate(power = round(power, 0))
-power_mixed       <- read_csv(here("data", "1_pilot", "simulation", "power_mixed_model.csv")) %>% mutate(power = round(power, 0))
-codebook          <- read_csv(here("data", "1_pilot", "pilot_self_report_codebook.csv"))
-pilot_self_report <- read_csv(here("data", "1_pilot", "pilot_self_report.csv"))
-
-```
-
-# Introduction
-
-Experiencing childhood adversity can have detrimental effects on cognitive outcomes [@hackman_2010; @ursache_2016].
-However, the hidden talents approach suggests that people living in adversity might develop specific skills that help them navigate harsh and unpredictable environments [@ellis_2017; @frankenhuis_2013].
-For example, recent work shows that growing up in stressful environments can enhance working memory updating, at least under certain conditions [@young_2018].
-However, the cognitive mechanisms responsible for lowered (impairments) and improved (enhancements) performance on various tests remain poorly understood.
-Some studies suggest that specific types of adversity lead to specific abilities independent of the current context [@fields_2021; @nweze_2020].
-Others only find enhancement effects under stressful [@mittal_2015; @young_2018] or more ecologically relevant [@young_submitted] testing conditions.
-
-Further progress depends on addressing two related questions: First, to what extent are patterns of impairment and enhancement independent?
-Cognitive processes that are typically targeted in hidden talents studies (e.g., working memory, task-switching) are complex processes that share many of the same more basic processes [@conway_2021; @kovacs_2019; @verbruggen_2014].
-This overlap means that impairment and enhancement patterns across tasks could be driven by the same underlying process.
-Second, which *cognitive* mechanisms are responsible for performance differences?
-Performance measures such as reaction times (RTs) or error rates are coarse indicators of performance.
-RTs on cognitive tasks are thought to reflect a number of sequentially unfolding processes.
-When the effect of adversity exposure on cognitive performance is measured by looking at RTs, enhancements or impairments might be driven by any of these subprocesses.
-Formal cognitive models such as the Drift Diffusion Model [DDM; @ratcliff_2008; @ratcliff_2015] might provide inside into the specific processes that are impaired or enhanced by adversity.
-
-Hidden talents research makes the often implicit assumption that enhanced abilities might reflect an externally focused orientation on the present [e.g., @ellis_2020; @frankenhuis_2016; @frankenhuis_2013].
-For example, @frankenhuis_2016 argued that living in a harsh and unpredictable environment might require a stronger present-orientation (as opposed to being focused on the future) in order to deal with unpredictable threats and benefit from fleeting rewards.
-Empirical findings seem to point in the same direction.
-Enhanced performance on attention-shifting [@fields_2021; @mittal_2015] and working memory updating [@nweze_2020; @young_2018] have been explained in terms of an ability to track contextual changes, which is thought to help cope with changing information.
-One possibility that has yet to be empirically tested is that such effects are driven by a shared present and/or externally oriented attention mechanism.
-In this pilot study, we leverage the DDM to better understand the processes involved in performance differences, specifically by focusing on basic attention skills.
-
-The DDM accounts for the fundamental cognitive processes underlying relatively simple, binary decision-making processes (2-AFC).
-The model assumes that the decision-making process constitutes a noisy information accumulation process that continues until one of two decision boundaries (corresponding to the response options) is reached.
-As soon as the accumulation process reaches a decision boundary, the process terminates and a motor response is initiated (e.g., pressing a key on the keyboard).
-The DDM accounts for the full pattern of correct RTs, incorrect RTs, and proportion of errors.
-In doing so, it recovers four parameters that map onto distinct cognitive processes ([@voss_2004]; see Figure 1A).
-
-The accumulation process is modeled as a drift rate (*v*), reflecting basic cognitive speed/speed of information uptake.
-Large values of *v* reflect more efficient processing (faster and more accurate).
-The starting point (*z*) reflects the starting position of the accumulation process relative to the two decision boundaries.
-Unless people are biased to favor one response over the other (e.g., due to a skewed reward structure), (*z*) is usually fixed to be equidistant from both decision boundaries (*a*).
-Larger values of *a* indicate that the boundaries are further removed from each other, leading to more conservative responses (slower but more accurate) while smaller values of *a* reflect more liberal responses (faster but less accurate).
-Thus, *a* reflects the speed-accuracy trade-off made by an individual.
-The fourth and final parameter is the non-decision time (*Ter*), which includes processes that are not related to the decision process (e.g., initial stimulus encoding and initiating the motor response).
-
-If people from adversity develop hidden talents, this should be reflected in specific DDM parameters.
-First and foremost, an enhanced cognitive ability would lead to more efficient information processing on tasks measuring that ability, which will be reflected in a higher drift rate *v* (or the other way around in case of a cognitive impairment).
-Second, enhanced performance could also be (partly) driven by the ability to quickly detect relevant stimuli before the onset of the decision-making process.
-Even if *v* is similar across levels of adversity, faster detection and encoding of relevant stimuli would allow individuals to start accumulating information sooner.
-This would be reflected in *Ter*.
-Finally, differences in performance across levels of adversity could be (partly) caused by the use of different strategies instead of by cognitive efficiency per se, for example, favoring speed over accuracy or vice versa.
-A tendency to adopt a specific strategy might be linked to individual differences in constructs like impulsivity.
-It is an open question whether performance differences driven by strategies should count as hidden talents [@young_2020].
-
-The current study aims to address these questions using an incremental preregistration approach.
-In the current preregistered pilot study, we measured various forms of adversity with a focus on unpredictability on different time scales (e.g., seconds, days, years).
-In addition, participants completed three basic attention tasks (Flanker Task, Cued Attention Task, and Change Detection Task) that differed in the extent to which they would favor or punish a broad, externally focused attention style.
-We applied the DDM to the RT and accuracy data to decompose performance.
-
-# Hypotheses
-
-## Primary hypotheses
-
-1)	People with more exposure to violence during childhood will show enhanced performance compared to people from safe environments on tasks that require quickly detecting peripheral stimuli and detecting subtle changes (i.e., the Cued Attention Task and Change Detection Task).
-This effect is explained by at least one of two DDM parameters: the speed of information uptake *v* and non-decision time *Ter*.
-2)	People with more exposure to violence during childhood will perform worse on tasks that require ignoring distracting peripheral stimuli (i.e., the Flanker Task).
-This effect is at least partly explained by a wider initial attentional focus, (operationalized through the attentional width parameter of a special adaptation of the original DDM; see [data analyses](#ddm_plan) for details).
-
-## Exploratory analyses
-
-1) Develop an [analysis pipeline](#ddm_plan) to estimate DDM parameters for use as dependent variables.
-2) Investigate the [factor structure](#efa) of several measures of unpredictability on different timescales through exploratory factor analysis (EFA).
-We then reran the analyses of the primary hypotheses using unpredictability as the independent variable, operationalized through composites of the original scales and through the factors resulting from the EFA.
-3) Explore the role of state anxiety, hunger, and sleep deprivation as potential moderators of the relationship between adversity and attention performance.
-Anxiety might enhance attention performance by making participants more vigilant.
-Conversely, hunger and sleep deprivation could have a negative effect on performance.
-4) Explore bivariate correlations between measures of adversity, attention, and measures of temporal orientation (i.e., impulsivity and future orientation).
-5) Explore the correlation between current depressive symptoms and retrospective measures of adversity, which might reflect a negativity bias in recalling past events driven by current depressive symptoms [@nivison_2021].
-
-# Methods {#methods}
-
-## Participants {#participants}
-
-Participants were 550 US-based individuals between the ages of 18 and 30 (*M* = `r #TBD`, *SD* = `r #TBD`).
-We decided for this age cut-off to reduce the effect of healthy age-related cognitive decline on speeded cognitive tasks, which becomes more pronounced after age 30 [@salthouse_2010].
-Recruitment took place through Prolific Academic [www.prolific.co].
-Participants were eligible for the study if they were from the United States and if they spoke fluent English.
-
-We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the optimal number of participants to include (more information including all simulation code on [Github](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/1_pilot/scripts).
-We ran simulations for two scenarios: A linear regression model to test the effect of adversity (standardized) on attention performance (standardized) and a mixed regression model to test the adversity (standardized) X task condition (sum-coded) interaction, including a random intercept for subjects.
-We ran simulations for a standardized $\beta$ of 0.10 and 0.15.
-
-In determining the final sample size, we weighed the simulation results against our uncertainty about certain model parameters (mostly the fixed effects and sigma term for the mixed model) and the fact that this was a first pilot study.
-For the mixed model, we found that power was > .80 for the adversity X task condition interaction with *N* = 450 or more.
-For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`.
-This was significantly higher for $\beta$ = 0.10 (*N* = `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .80, alternative = "two.sided")[['n']] %>% round(0)` when power = `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .80, alternative = "two.sided")[['power']] %>% round(1)` and `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .890, alternative = "two.sided")[['n']] %>% round(0)` when power = `r pwr.r.test(r = 0.1, sig.level = 0.05, power = .90, alternative = "two.sided")[['power']] %>% round(1)`).
-Thus, we decided on sampling 550 participants with an anticipated final sample size of around 500 due to drop-out and data exclusions.
-
-## Exclusion criteria {#exclusion}
-
-We applied several exclusion criteria prior to analyzing the data.
-First, we excluded participants who did not complete the full study and those who had incomplete data on any of the attention tasks (*N* = `r #TBD `).
-Second, we analyzed responses to the attention checks and reversed coded items in the questionnaire part of the experiment.
-We excluded participants if they missed both attention check items or if they had suspicious response patterns (e.g., consistently endorsing high response options even when some items were reverse coded) (*N* = `r #TBD `).
-
-In addition, we screened the reaction times on each of the three attention tasks.
-For the Drift Diffusion analyses, it is important that each response is generated by a process of active information accumulation (i.e., a diffusion process, as opposed to guessing).
-To this end, trials with reaction times < 250 ms or > 3500 ms [@ratcliff_2015] were excluded from the analyses (*N* = `r #TBD `).
-Participants with more than 10 removed trials were excluded from the analyses (N = `r #TBD `).
-
-The exclusion criteria listed above are our best *a-priori* guesses. However, we expect to develop additional criteria empirically after collecting the data.
-
-## Measures {#measures}
-
-The attention tasks were programmed in JsPsych version 3.6.1 [@deLeeuw_2015].
-
-### Cued Attention Task {#cued_attention}
-
-The Cued Attention Task was an adaptation of the Posner task, which measures basic spatial attention speed [@posner_1980].
-On each trial, a left- or right-pointing arrow was presented in one of eight random locations at a distance of 300 pixels from the center of the screen (see Figure 2A).
-Participants had to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard.
-On 50% of the trials, the arrow was preceded by a cue ('\*') in the exact same location (i.e., 'cued' trials).
-On the other 50% of the trials, the cue ('\*') was presented at the center of the screen (i.e., 'neutral' trials).
-Thus, on the cued trials, the location of the cue deterministically predicted the location of the arrow, whereas on the neutral trials the arrow always appeared in a different location.
-
-Each trial started with a fixation cross presented at the center of the screen for 1000 ms.
-Then, the cue was presented for 250 ms either at the center of the screen or in the location where the arrow would appear next.
-Finally, the arrow was presented 250 ms after the onset of the cue and shown until a response was given.
-The Cued Attention Task began with eight practice trials (four cued and four neutral trials) in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
-After finishing the practice round, participants completed a single test block consisting of a total of 64 trials, consisting of two repetitions of all parameter combinations: arrow location (top center vs.
-top left vs.
-center left vs.
-bottom left vs.
-bottom center vs.
-bottom right vs.
-center right vs.
-top right) X arrow direction (left vs.
-right) X condition (cued vs.
-neutral).
-The main performance measures are RTs and accuracy for each condition.
-
-### Flanker Task {#flanker}
-
-The Flanker Task measures selective attention and response inhibition [@eriksen_1974].
-On each trial of the Flanker task, participants were presented with a set of five arrows pointing either left or right.
-Their job was to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right (see Figure 2B).
-On 50% of the trials, the flanking arrows pointed in the same direction as the central arrow (i.e., congruent trials), and on the other 50% of the trials they pointed in the opposite direction (i.e., incongruent trials).
-The arrows were randomly presented in the top-half or bottom-half of the screen.
-This was done to prevent participants from rigidly fixating on the center of the screen, which might reduce the interfering effect of the flanking arrows.
-
-Each trial started with a fixation cross presented at the center of the screen.
-After a delay of 1000ms, the arrows are presented either in the top- or bottom-half of the screen.
-The Flanker task began with eight practice trials in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
-After finishing the practice round, participants completed a single test block consisting of a total of 64 trials, consisting of eight repetitions of all parameter combinations: Arrow location (top vs.
-bottom) X central arrow direction (left vs.
-right) X condition: (congruent vs.
-incongruent).
-Participants did not receive performance feedback during the test block.
-The main performance measures were RTs and accuracy for each condition.
-
-### Change Detection Task {#change}
-
-The Change Detection Task measures the ability to detect subtle spatial changes.
-On each trial of the change detection task, participants were presented with five colored circles against a grey background, each with a radius of 15 pixels (see Figure 2C).
-Each circle was located in a semi-random location around the central fixation cross.
-The location of each circle was sampled within a pre-specified area of 50 by 50 pixels to prevent overlap.
-Participants had 1000ms to memorize the locations of the five circles.
-After 1000ms, the circles disappeared for 500ms and then reappeared again.
-On 50% of the trials, one of the circles had moved to another location with a fixed displacement of 40 pixels in a 360 degree direction.
-On the other 50% of the trials, all circles were still in the same location as the initial memory display.
-Participants had to indicate whether they thought one of the circles changed location (by pressing the left-arrow key) or whether they thought all circles were still in the same location (by pressing the right-arrow key).
-Note that the only potential difference between the memory and probe display on each trial was the displacement of **one** circle; the remaining circles were always in the same place and circles never changed color within a trial.
-
-The change detection task started with five practice trials in which participants received performance feedback after each trial (either "Correct!" printed in green or "Incorrect!" printed in red).
-After finishing the practice round, participants completed two test blocks consisting of 25 trials each (50 trials in total).
-The design was fully counterbalanced so that each circle moved on five trials and was a different color each time it moved *between* trials.
-Participants did not receive performance feedback during the two test blocks.
-The main performance measures are RTs and accuracy across all trials.
-
-### Current state {#state}
-
-We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [STAI-S; @spielberger_1999].
-The STAI-S contains 20 short items measuring current anxiety (e.g., "I feel tense"; See [Table S1](#appendix) for an overview of all items).
+## 1.1. Current state 
+We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [STAI-S\; @spielberger_1999]. 
+The STAI-S contains 20 short items measuring current anxiety (e.g., "I feel tense"). 
 Participants rated each item on a scale of 1 (not at all) to 4 (very much so). 
-An overall state anxiety variable was computed by averaging across the 20 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+An overall state anxiety variable was computed by averaging across the 20 unweighted items (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$stai_s`).
 
 In addition, participants answered five questions relating to specific states: "Are you currently sick?" (rated as yes or no); "Have you eaten a full meal today?" (rated as yes or no); "How hungry do you feel right now?" (rated from 1 (not at all) to 5 (very hungry)); "How well did you sleep last night?" (rated from 1 (very poorly) to 5 (very well)); "How rested or refreshed did you feel when you woke up this morning?" (rated from 1 (not at all) to 5 (very rested)).
-We computed an overall sleep deprivation composite by standardizing and averaging across the two unweighted sleep-related items (*M* = `r #TBD `, *SD* = `r #TBD `).
+We computed an overall sleep deprivation composite by standardizing and averaging across the two unweighted sleep-related items.
 
-### Violence exposure {#violence}
-
-Violence exposure was measured using the Neighborhood Violence Scale [NVS; @frankenhuis_2018; @frankenhuis_deVries_2020] and two items assessing exposure to physical fights before age 13.
-The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up"; See [Table S2](#appendix) for an overview of all items).
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
-The items of the NVS were averaged together (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-Similarly, we averaged the scores on the two fighting items together.
-Finally, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average (*r* = `r #TBD `).
-
-### Unpredictability {#unpred}
-
-Perceived unpredictability before age 13 was measured using two different scales: A scale of perceived childhood unpredictability used in previous research [@mittal_2015; @young_2018] and an adaptation of the Questionnaire of Unpredictability in Childhood [QUIC; @glynn_2019].
-The perceived childhood unpredictability scale contained eight items measuring perceived unpredictability before age 13 (e.g, "My family life was generally inconsistent and unpredictable from day-to-day"; See [Table S3](#appendix) for an overview of all items).
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-
-We included the QUIC because it captures several dimensions of environmental and household unpredictability.
-The QUIC distinguishes between items capturing more short-term unpredictability (i.e., on the level of seconds to minutes) and more long-term unpredictability (i.e., on the level of days to months).
-The scale of perceived childhood unpredictability combines items on different time scales.
-Some items measure unpredictability on a relatively short-term scale (e.g., item 1) while other items measure unpredictability on a long-term scale (e.g., item 3).
-Unpredictability on different time scales might have different effects on the development of specific attention styles.
-
-The QUIC consists of 38 items across five subscales: 1) Parental monitoring and involvement, 2) Parental predictability, 3) Parental environment, 4) Physical environment, and 5) Safety and security (See [Table S4](#appendix) for an overview of all items).
-We made two changes to the original scale as described in @glynn_2019.
-First, while the original QUIC items refer to perceived unpredictability either before age 12 or age 18, we adapted all items to refer to experiences before age 13.
-This was done to reduce cognitive load from having to go back-and-forth between different time scales.
-Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
-This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
-
-We computed several unweighted unpredictability variables to be able to assess how they would relate to the dependent variables as well as to each other: 1) overall perceived unpredictability variable containing all eight items of the perceived unpredictability scale (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 2) an overall QUIC variable by averaging all 38 items (*M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `); 3) five separate QUIC subscales by averaging their sub-items (Parental monitoring and involvement: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental predictability: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Parental environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Physical environment: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `; Safety and security: *M* = `r #TBD `, *SD* = = `r #TBD `, $\alpha$ = `r #TBD `).
-See also [below](#efa) for details on a factor analysis based on the individual items across scales.
-
-### Household chaos {#chaos}
-
-We assessed household chaos before age 13 using an adaptation of the Confusion, Hubbub, and Order Scale [CHAOS; @matheny_1995].
-The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late"; See [Table S5](#appendix) for an overview of all items).
-We made two changes to the original scale as described in @matheny_1995.
-First, all items were converted from the present tense to the past tense, and were endorsed as applying to participants' lives before age 13.
-Second, all items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
-This change was also implemented to reduce cognitive load by keeping the answer options the same between scales.
-An overall household chaos variable was computed by averaging the 15 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-
-### Poverty exposure {#ses}
-
+## 1.2 Poverty exposure 
 Participants' perceived level of resource scarcity before age 13 was measured using seven items (e.g., "Your family had enough money to afford the kind of home you all needed"; See [Table S6](#appendix) for an overview of all items).
@@
 Scores for the first six items were reverse coded so that higher scores indicated more perceived resource scarcity. 
-The items were averaged together to create an unweighted composite scale (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+The items were averaged together to create an unweighted composite scale (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$ses`).
 
@@
 First, participants separately indicated the highest education of their mother and father on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'.
-The mother and father education level were averaged to create an overall unweighted parental education composite (*M* = `r #TBD `, *SD* = `r #TBD `).
+The mother and father education level were averaged to create an overall unweighted parental education composite. 
 Participants also indicated their family's household income before age 13 on a 6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'.
@@
 
-### Impulsivity {#impulsivity}
-
-We assessed impulsivity with the Motor Impulsivity subscale of the Barrett Impulsivity Scale (BIS; short form; [@patton_1995; @spinella_2007]).
-The Motor Impulsivity subscale of the BIS consists of five items (e.g., "I do things without thinking"; See [Table S7](#appendix) for an overview of all items).
+## 1.3. Impulsivity 
+We assessed impulsivity with the Motor Impulsivity subscale of the Barrett Impulsivity Scale [BIS short form\; @patton_1995; @spinella_2007]. 
+The Motor Impulsivity subscale of the BIS consists of five items (e.g., "I do things without thinking").
 We did not include the Non-planning subscale because it overlapped substantially with the Future Orientation Scale described below. 
@@
 We changed the original 4-point rating scale (rarely/never to almost always) to a 5-point rating scale ranging from 1 (never true) to 5 (very often true). 
-An overall impulsivity variable was computed by averaging the five unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
+An overall impulsivity variable was computed by averaging the five unweighted items.
+Reliability was the scale was high($\alpha$ = `r txt_ivs_alpha_pilot$impuls`).
 
-### Future Orientation {#future_orientation}
-
-We assessed future orientation with an adapted version of the Future Orientation Scale [FOS; @steinberg_2009].
+## 1.4. Future Orientation 
+We assessed future orientation with an adapted version of the Future Orientation Scale [FOS\; @steinberg_2009]. 
 The original scale consists of 15 sets of opposing items separated by "BUT" (e.g., "Some people like to plan things out one step at a time BUT other people like to jump right into things without planning them out beforehand").
@@
 For people from adversity, spending money right now instead of saving it for the future might often be born out of necessity (e.g., having just enough money for food and shelter; being in debt) instead of a failure to delay gratification.
-See [Table S8](#appendix) for an overview of all adapted items).
 Finally, the rating scale was adapted from the original 4-point scale (ranging from really true for the left-hand statement to really true for the right-hand statement) to a 5-point scale ranging from 1 (never true) to 5 (very often true).
+An overall future orientation variable was computed by averaging the 15 unweighted items.
+Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$fos_fo`).
 
-An overall future orientation variable was computed by averaging the 15 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-In addition, we calculated subscales for "Planning ahead" (items 1, 6, 7, 12 and 13), "Time perspective" (items 2, 5, 8, 11 and 14) and "Anticipation of future consequences" (items 3, 4, 9, 10 and 15).
-
-### Depressive symptoms {#depression}
-
-We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD; @radloff_1977].
-The scale consists of 20 items (e.g., "I do things without thinking"; See [Table S9](#appendix) for an overview of all items).
+# 1.5 Depressive symptoms 
+We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD\; @radloff_1977]. 
+The scale consists of 20 items (e.g., "I do things without thinking"). 
 Participants rate each item on a scale of 1 (rarely or none of the time (less than 1 day)) to 4 (most or all of the time (5-7 days)). 
-An overall depression variable was computed by averaging the 20 unweighted items (*M* = `r #TBD `, *SD* = `r #TBD `, $\alpha$ = `r #TBD `).
-
-## Procedure {#procedure}
-
-The experiment was completed on the participants' own laptop or desktop computer and consisted of five parts: consent, attention task battery, questionnaire battery, brief demographics form, and final checks including the opportunity to give feedback on the experiment.
-Participants were allowed to refrain from answering any of the questionnaire items, but were prompted with a warning once when moving to the next page if one of the items was not answered (which they could ignore).
-
-After providing consent, participants started with the three attention tasks.
-They were asked to complete the attention tasks in a quiet room in the house where they would be least likely to be distracted by other people or outside noises.
-The order of the tasks was counterbalanced between subjects.
-At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs.
-The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deLeeuw_2015].
-Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the creditcard.
-The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants.
-After successfully resizing the screen, participants completed all three tasks.
-During the task, the cursor was hidden from the screen to minimize distractions.
-Code for the three tasks can be found on [Github](https://github.com/StefanVermeent/attention_project/tree/main/tasks).
-
-After completing the attention tasks, participants completed the questionnaire battery in the following fixed order: 1) Current state (state anxiety and separate questions relating to specific states); 2) Childhood adversity (perceived unpredictability, perceived socio-economic status, exposure to violence and physical fights, household chaos); 3) Temporal orientation (impulsivity, future orientation); 4) Depressive symptoms.
-
-Finally, the demographics questions asked about the participant's age, weight, height, physical activity, sex at birth, gender, ethnicity, social class (current and during childhood), education level (one's own as well as parents' education level), occupation, and household income (current and during childhood).
-At the end of the experiment, we asked participants if they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.
-
-The full experiment was expected to take approximately 35 minutes. Participants were paid £4.38 upon completing the full experiment.
-
-## Primary data analyses {#analysis_plan}
-
-### Reaction Times {#rt_plan}
-
-For the Cued Attention Task and Flanker Task, average reaction times per participant were calculated separately for each condition (cued/neutral trials and incongruent/congruent trials, respectively).
-For the change detection task, we calculated an average reaction time across all trials.
-If necessary for meeting model assumptions of normally distributed residuals, reaction times were log-transformed.
-We only planned on performing analyses on the proportion of errors if the average error rate was at least 5% of trials.
-Note that the DDM analysis described below provides a full breakdown of performance both in terms of reaction times and accuracy.
-For the Cued Attention Task and Flanker Task, we performed a set of linear mixed effects analyses to test adversity X condition interactions on mean RTs and accuracy (if possible).
-Condition was sum-coded (-1 and 1).
-All models included a random intercept for participants.
-For the Change Detection Task, we performed linear regression to test the main effect of adversity on mean RTs and accuracy (if possible).
-Across separate models, adversity was operationalized as the composite measures of violence exposure, SES, perceived childhood unpredictability, household chaos, and the QUIC subscales (unless they correlated > .80, in which case QUIC subscales were merged together).
-Significant interaction effects were unpacked using simple slopes analysis.
-
-### Drift Diffusion Model {#ddm_plan}
-
-DDM models were fit separately to the data of each participant. 
-(see also our power simulations on [Github](https://github.com/StefanVermeent/attention_pilot/tree/main/scripts), which indicated that recovered drift rate and boundary separation parameters generally correlated highly (*r* = .80-.95) with the true data-generating parameters even with 30 trials).
-
-The DDM was fit separately to the data of each participant.
-For the data of the Change Detection Task and the Cued Attention Task, the DDM was fit using Fast-dm [@voss_2007].
-We used Maximum Likelihood estimation as it has been shown to provide reliable estimates with relatively few trials [@lerche_2017] (see also our power simulations on [Github](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/1_pilot/scripts), which indicated that recovered drift rate and boundary separation parameters generally correlated highly (*r* = .80-.95) with the true data-generating parameters even with 30 trials).
-Parameters *a*, *v* and *Ter* were freely estimated and *z* was fixed to 0.5 (the midpoint, indicating no response bias).
-In addition, all inter-trial variability parameters were fixed to 0 to increase model parsimony.
-For the Cued Attention Task, the DDM was fit separately to data of the two conditions (cued vs neutral).
-For the Change Detection task, we had no *a-priori* expectations about performance differences between the change and no-change trials.
-Prior to fitting the DDM models, we ran paired-sample *t*-tests on the RTs and proportion of errors.
-If either model showed significant mean differences, the DDM was fit separately to data of the change and no-change trials.
-If there were no differences, the DDM models were fit to all trials simultaneously.
-
-The DDM analysis of the Flanker task was done using an adaptation of the standard DDM that was specifically developed to account for Flanker data: The Spotlight Drift Diffusion Model [SDDM; @grange_2016; @white_2018a; @white_2018b; @white_2011].
-The standard DDM model assumes a stable drift rate over time within trials (i.e., the rate of information accumulation does not change over time).
-However, on the Flanker Task, reaction time patterns indicate that the drift rate increases over time, thus violating the basic assumption of the standard DDM [@white_2011].
-The SDDM explains this pattern by assuming that attention on the Flanker task works like a spotlight that starts relatively broad, and then gradually narrows down to the central arrow over time.
-Each arrow provides perceptual input *p*.
-If the flanking arrows are congruent, all flankers take a positive value for *p*; if the flanking arrows are incongruent, they take a negative value for *p* while the central arrow takes a positive value.
-The drift rate (*v*) at each time point is the function of the strength of perceptual input *p* multiplied by the amount of attention focused on each arrow.
-
-Attention is operationalized by two additional parameters: the initial width of the attentional spotlight (*SD~a~*) and the shrinking rate of the attentional spotlight (*rd*).
-The attentional spotlight is assumed to be normally distributed over the arrows, with relatively more attention paid to the arrows at the center and relatively less attention paid to the peripheral arrows.
-Over time, this normal distribution (*SD~a~*) narrows down to the central arrow at the rate specified by *rd*, thereby gradually decreasing the interfering effect of the flanking arrows.
-Note that the SDDM is based on a combined analysis of congruent and incongruent trials.
-See Figure 1B for a visualization of the SDDM.
-
-Previous research has shown that it is not useful to interpret both *SD~a~* and *rd* because they trade off with each other [i.e., a wide initial spotlight combined with a large shrinking rate leads to similar patterns as a narrow initial spotlight combined with a low shrinking rate; @white_2018a; @white_2011].
-Most previous studies have fixed *SD~a~* and only estimated *rd*, or calculated a *SD~a~*/*rd* ratio, which serves as a measure of interference.
-However, our primary interest lies in the initial width of the attentional spotlight, which we hypothesize to be wider for people from harsh and unpredictable environments compared to people from safe and predictable environments.
-In this pilot study, we fitted several SDDM models either estimating both attention parameters or fixing *rd* to see how it affected model fit (more details below).
-Model fit was done using the *flankr* package in R [@grange_2016].
-
-DDM parameters *v*, *a* and *Ter* (as well as *p*, *SD~a~* and *SD~a~*/*rd* for the Flanker Task) were used as dependent variables in the analyses for each attention task.
-For the Flanker Task and Change Detection Task, DDM parameters were submitted to a series of linear regression models with adversity as the independent variable.
-For the Cued Attention Task, DDM parameters were submitted to linear mixed effects models to test for adversity X condition interactions.
-All models included a random intercept for participants.
-Independent adversity variables were identical to the RT/accuracy analyses.
-Significant interaction effects were unpacked using simple slopes analysis.
-
-### Factor structure of unpredictability {#efa}
-
-The three included unpredictability measures contain items that vary in timescale, ranging from features of the childhood environment that might have been unpredictable on a daily basis (e.g., "things were often chaotic in my house") to sources of unpredictability that typically unfold on a timescale of weeks or months (e.g., "At least one of my parents changed jobs frequently").
-Since attention is involved in information processing on a timescale of seconds to minutes, we expect that attention styles should be more strongly related to sources of unpredictability that unfold on a similar timescale.
-However, it is unclear whether current retrospective measures of unpredictability are able to differentiate between different timescales.
-In addition, it might be the case that items of unpredictability on a longer timescale are good proxies for unpredictability on a a more daily timescale.
-We conducted an exploratory factor analysis (EFA) to address these issues.
-
-EFA was used to find common latent factors underlying the three unpredictability/household chaos measures: perceived unpredictability, QUIC, and CHAOS.
-The number of factors to retain was based on parallel analysis, with the added requirement that each factor was composed of at least five items that had their strongest loading on that particular factor.
-Factor loadings above 0.32 were considered meaningful (Tabachnick & Fidell, 2014).
-We anticipated the factors to be correlated substantially, and therefore planned to use oblimin rotation.
-
-\pagebreak
-
-# References {#refs}
-
-<div id="refs"></div>
-
-\pagebreak
-
-# Appendix
-
-Go back to [Methods](#state)
-
-```{r supp_table1, tab.id="tableS2", tab.cap.style="Table Caption", tab.cap="Items of the State-Trait Anxiety Inventory (state subscale; STAI-S)"}
-codebook %>%
-  filter(str_detect(Variable, "stai_s(\\d\\d|_\\d\\d)")) %>% 
-  mutate(Item = 1:n()) %>%
-  select(Item, Label) %>%
-  add_column(.after = 1, "empty1" = "") %>%
-  mutate(Label = ifelse(Item %in% c(1,2,5,8,10,11,15,16,19,20), str_c(Label, "*"), Label)) %>%
-  flextable(cwidth = c(0.75, .2, 5)) %>%
-  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
-  add_footer_row(values = " ", colwidths = 3) %>%
-  compose(
-    i = 1, j = 1,
-    as_paragraph(as_i("Note: "), "Reverse scored items."),
-    part = 'footer')
-```
-
-\pagebreak
-
-Go back to [Methods](#violence)
-
-```{r tableS2, tab.id="tableS2", tab.cap.style="Table Caption", tab.cap="Items of the Neighborhood Violence Scale (NVS)"}
-codebook %>%
-  filter(str_detect(Variable, "violence\\d\\d")) %>% 
-  mutate(Item = 1:n()) %>%
-  select(Item, Label) %>%
-  add_column(.after = 1, "empty1" = "") %>%
-  mutate(Label = ifelse(Item %in% c(1,3), str_c(Label, "*"), Label)) %>%
-  flextable(cwidth = c(0.75, .2, 5)) %>%
-  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
-  add_footer_row(values = " ", colwidths = 3) %>%
-  compose(
-    i = 1, j = 1,
-    as_paragraph(as_i("Note: "), "Reverse scored items."),
-    part = 'footer')
-```
-
-\pagebreak
-
-Go back to [Methods](#unpred)
-
-```{r tableS3, tab.id="tableS3", tab.cap.style="Table Caption", tab.cap="Items of the Perceived Childhood Unpredictability scale"}
-codebook %>%
-  filter(str_detect(Variable, "unp\\d\\d")) %>% 
-  mutate(Item = 1:n()) %>%
-  select(Item, Label) %>%
-  add_column(.after = 1, "empty1" = "") %>%
-  flextable(cwidth = c(0.75, .2, 5)) %>%
-  set_header_labels(Item = "Item", empty1 = "", Label = "Description")
-```
-
-\pagebreak
-
-Go back to [Methods](#unpred)
-
-```{r tableS4, tab.id="tableS4", tab.cap.style="Table Caption", tab.cap="Items of the Questionnaire of Unpredictability in Childhood (QUIC)"}
-codebook %>%
-  filter(str_detect(Variable, "quic\\d\\d")) %>% 
-  mutate(Item = 1:n()) %>%
-  select(Item, Label) %>%
-  add_column(.after = 1, "empty1" = "") %>%
-  add_row(.before = 1, "Label" = "Parental monitoring and involvement") %>%
-  add_row(.after = 10, "Label" = "Parental predictability") %>%
-  add_row(.after = 23, "Label" = "Parental environment") %>%
-  add_row(.after = 31, "Label" = "Physical environment") %>%
-  add_row(.after = 39, "Label" = "Safety and security") %>%
-  mutate(Label = ifelse(Item %in% c(1,2,3,4,5,6,7,8,9,11,14,16,26,33), str_c(Label, "*"), Label)) %>%
-  flextable(cwidth = c(0.75, .2, 5)) %>%
-  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
-  merge_h_range(i = c(1,11,24,32,40)) %>%
-  bold(i = c(1,11,24,32,40)) %>%
-  add_footer_row(values = " ", colwidths = 3) %>%
-  compose(
-    i = 1, j = 1,
-    as_paragraph(as_i("Note: "), "Reverse scored items."),
-    part = 'footer')
-```
-
-\pagebreak
-
-Go back to [Methods](#chaos)
-
-```{r tableS5, tab.id="tableS5", tab.cap.style="Table Caption", tab.cap="Items of the Confusion, Hubbub, and Order Scale (CHAOS)"}
-codebook %>%
-  filter(str_detect(Variable, "chaos\\d\\d")) %>% 
-  mutate(Item = 1:n()) %>%
-  select(Item, Label) %>%
-  add_column(.after = 1, "empty1" = "") %>%
-  mutate(Label = ifelse(Item %in% c(1,2,7,12,14,15), str_c(Label, "*"), Label)) %>%
-  flextable(cwidth = c(0.75, .2, 5)) %>%
-  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
-  add_footer_row(values = " ", colwidths = 3) %>%
-  compose(
-    i = 1, j = 1,
-    as_paragraph(as_i("Note: "), "Reverse scored items."),
-    part = 'footer')
-```
-
-\pagebreak
-
-Go back to [Methods](#ses)
-
-```{r tableS6, tab.id="tableS6", tab.cap.style="Table Caption", tab.cap="Items of the perceived resource scarcity scale"}
-codebook %>%
-  filter(str_detect(Variable, "ses\\d\\d")) %>% 
-  mutate(Item = 1:n()) %>%
-  select(Item, Label) %>%
-  add_column(.after = 1, "empty1" = "") %>%
-  mutate(Label = ifelse(!Item %in% c(7), str_c(Label, "*"), Label)) %>%
-  flextable(cwidth = c(0.75, .2, 5)) %>%
-  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
-  add_footer_row(values = " ", colwidths = 3) %>%
-  compose(
-    i = 1, j = 1,
-    as_paragraph(as_i("Note: "), "Reverse scored items."),
-    part = 'footer')
-```
-
-\pagebreak
-
-Go back to [Methods](#impulsivity)
-
-```{r tableS7, tab.id="tableS7", tab.cap.style="Table Caption", tab.cap="Items of the Barrett Impulsivity Scale (BIS) - motor impulsivity subscale"}
-codebook %>%
-  filter(str_detect(Variable, "impuls\\d\\d")) %>% 
-  mutate(Item = 1:n()) %>%
-  select(Item, Label) %>%
-  add_column(.after = 1, "empty1" = "") %>%
-  flextable(cwidth = c(0.75, .2, 5)) %>%
-  set_header_labels(Item = "Item", empty1 = "", Label = "Description")
-```
-
-\pagebreak
-
-Go back to [Methods](#future_orientation)
-
-```{r tableS8, tab.id="tableS8", tab.cap.style="Table Caption", tab.cap="Items of the Future Orientation Scale (FOS)"}
-codebook %>%
-  filter(str_detect(Variable, "fos\\d\\d")) %>% 
-  slice(match(c("fos01","fos06","fos07","fos12","fos13", "fos02","fos05","fos08","fos11","fos14", "fos03","fos04","fos09","fos10","fos15"), Variable)) %>%
-  mutate(Item = 1:n()) %>%
-  select(Item, Label) %>%
-  add_column(.after = 1, "empty1" = "") %>%
-  add_row(.before = 1, "Label" = "Planning ahead") %>%
-  add_row(.after = 6, "Label" = "Time perspective") %>%
-  add_row(.after = 12, "Label" = "Anticipation of future consequences") %>%
-  mutate(Label = ifelse(Item %in% c(1,2,5,8,9,11,12,15), str_c(Label, "*"), Label)) %>%
-  flextable(cwidth = c(0.75, .2, 5)) %>%
-  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
-  merge_h_range(i = c(1,7,13)) %>%
-  bold(i = c(1,7,13)) %>%
-  add_footer_row(values = " ", colwidths = 3) %>%
-  compose(
-    i = 1, j = 1,
-    as_paragraph(as_i("Note: "), "Reverse scored items."),
-    part = 'footer')
-```
-
-\pagebreak
-
-Go back to [Methods](#depression)
-
-```{r tableS9, tab.id="tableS9", tab.cap.style="Table Caption", tab.cap="Items of the Epidemiologic Studies Depression Scale (CESD)"}
-codebook %>%
-  filter(str_detect(Variable, "depression\\d\\d")) %>% 
-  mutate(Item = 1:n()) %>%
-  select(Item, Label) %>%
-  add_column(.after = 1, "empty1" = "") %>%
-  mutate(Label = ifelse(Item %in% c(4,8,12,16), str_c(Label, "*"), Label)) %>%
-  flextable(cwidth = c(0.75, .2, 5)) %>%
-  set_header_labels(Item = "Item", empty1 = "", Label = "Description") %>%
-  add_footer_row(values = " ", colwidths = 3) %>%
-  compose(
-    i = 1, j = 1,
-    as_paragraph(as_i("Note: "), "Reverse scored items."),
-    part = 'footer')
-```
+An overall depression variable was computed by averaging the 20 unweighted items.
+Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$depression`).

### 2024-01-17 supplement/supplements.qmd
supplemental materials in progress

---
title: "Supplements"
format: html
editor: visual
---

```{r include=FALSE}
load("../preregistrations/1_pilot/analysis_objects/supp_section2.Rdata")
load("../preregistrations/2_study1/analysis_objects/supp_section2.Rdata")
load("../preregistrations/3_study2/analysis_objects/supp_section2.Rdata")
load("../data/1_pilot/mod_fit_flanker.RData")
load("../data/3_study2/ssp_fit.RData")

source("../manuscript/pilot_stage_objects.R") # Staged results of the pilot study

library(flextable)

# set up flextable for tables
set_flextable_defaults(
  font.family = "Times", 
  font.size = 10,
  font.color = "black",
  line_spacing = 1,
  padding.bottom = 1, 
  padding.top = 1,
  padding.left = 1,
  padding.right = 1
)
```

# Section 1. Descriptions of exploratory measures

The following exploratory measures were collected in all three studies

## 1.1. Current state 
We assessed state anxiety during the experiment using the state subscale of the State-Trait Anxiety Inventory [STAI-S\; @spielberger_1999]. 
The STAI-S contains 20 short items measuring current anxiety (e.g., "I feel tense"). 
Participants rated each item on a scale of 1 (not at all) to 4 (very much so). 
An overall state anxiety variable was computed by averaging across the 20 unweighted items.

In addition, participants answered five questions relating to specific states: "Are you currently sick?" (rated as yes or no); "Have you eaten a full meal today?" (rated as yes or no); "How hungry do you feel right now?" (rated from 1 (not at all) to 5 (very hungry)); "How well did you sleep last night?" (rated from 1 (very poorly) to 5 (very well)); "How rested or refreshed did you feel when you woke up this morning?" (rated from 1 (not at all) to 5 (very rested)). We computed an overall sleep deprivation composite by standardizing and averaging across the two unweighted sleep-related items.

## 1.2. Poverty exposure 
Participants' perceived level of resource scarcity before age 13 was measured using seven items (e.g., "Your family had enough money to afford the kind of home you all needed"). 
Participants rated each item on a scale from 1 (never true) to 5 (very often true). 
Scores for the first six items were reverse coded so that higher scores indicated more perceived resource scarcity. 
The items were averaged together to create an unweighted composite scale.

In addition, we measured several indicators of objective SES before age 13. 
First, participants separately indicated the highest education of their mother and father on an 8-point scale: 'some high school', 'GED', 'high school diploma', 'some college but no college degree', associate's  degree', 'bachelor's degree', 'master's  degree', or 'doctoral or lab degree'. 
The mother and father education level were averaged to create an overall unweighted parental education composite. 
Participants also indicated their family's household income before age 13 on a 6-point scale: 'less than \$ 25k/year', '\$25k - \$49k/year, '\$50 - \$74k/year', '\$75 - \$99k/year', '\$100 - \$149k/year', 'more than \$150k/year'. 
Scores were reverse coded so that higher scores indicated higher levels of poverty.

We created a composite score of poverty exposure before age 13 by averaging together the standardized scores of perceived level of resource scarcity, overall parental education, and household income.

## 1.3. Impulsivity 
We assessed impulsivity with the Motor Impulsivity subscale of the Barrett Impulsivity Scale [BIS short form\; @patton_1995; @spinella_2007]. 
The Motor Impulsivity subscale of the BIS consists of five items (e.g., "I do things without thinking").
We did not include the Non-planning subscale because it overlapped substantially with the Future Orientation Scale described below. 
In addition, we did not include the Attention impulsivity subscale because it included items which we deemed to be mostly irrelevant for our target population (e.g., "I 'squirm' at plays or lectures"). 
We changed the original 4-point rating scale (rarely/never to almost always) to a 5-point rating scale ranging from 1 (never true) to 5 (very often true). 
An overall impulsivity variable was computed by averaging the five unweighted items.

## 1.4. Future Orientation 
We assessed future orientation with an adapted version of the Future Orientation Scale [FOS\; @steinberg_2009]. 
The original scale consists of 15 sets of opposing items separated by "BUT" (e.g., "Some people like to plan things out one step at a time BUT other people like to jump right into things without planning them out beforehand"). 
Participants first choose the item that best matches their general preference, and then indicate whether the statement is "really true" or "somewhat true". 
We adapted this format in a couple of ways. 
First, we converted the two statements per item to a single statement by picking the statements in the original right-hand column. 
Second, we adapted the 15 statements from a third-person to a first-person format. 
These changes were made in an attempt to reduce the cognitive load of the items. 
We worried that people with less formal education or who were sitting in a noisier environment would struggle with the length of the original items.

In addition, item 8 of the original scale ("[...] other people would rather spend their money right away on something fun than save it for a rainy day") was changed to "I'd rather spend money right away than save it for a rainy day" (i.e., dropping the phrase "on something fun") to make it more general with regard to the thing that money is spent on. 
For people from adversity, spending money right now instead of saving it for the future might often be born out of necessity (e.g., having just enough money for food and shelter; being in debt) instead of a failure to delay gratification. 
Finally, the rating scale was adapted from the original 4-point scale (ranging from really true for the left-hand statement to really true for the right-hand statement) to a 5-point scale ranging from 1 (never true) to 5 (very often true).
An overall future orientation variable was computed by averaging the 15 unweighted items.

## 1.5. Depressive symptoms 
We assessed depressive symptoms during the past week using the Center for Epidemiologic Studies Depression Scale [CESD\; @radloff_1977]. 
The scale consists of 20 items (e.g., "I do things without thinking"). 
Participants rate each item on a scale of 1 (rarely or none of the time (less than 1 day)) to 4 (most or all of the time (5-7 days)). 
An overall depression variable was computed by averaging the 20 unweighted items.

# Section 2. Exploratory analyses

## 2.1. Consistency in unpredictability measures

### 2.1.1. Pilot

The EFA yielded five factors based on parallel analysis (see Table SX).
Based on their contents, we labelled these factors (1) Daily unpredictability; (2) Household routine; (3) Spatial unpredictability; (4) Chaos/clutter; (5) Social unpredictability.

```{r}
pilot_efa_table
```

### 2.1.2 Study 1

Similar to the Pilot, the EFA yielded five factors based on parallel analysis.
We plotted the factor loadings of each factor in the Pilot against those in Study 1 to investigate their correspondence (See Figure SX).
In general, individual items largely loaded on the same factors, and the sizes of their loadings were also comparable.
The items from the CHAOS were found to be most unstable, with many showing a loading < .32 in one of the two studies.

```{r}
study1_efa_fig
```
## 2.2. Bivariate correlations between future orientation and impulsivity with attention tasks

Table SX shows bivariate correlations between self-reported depression, impulsivity, future orientation, and SES with each of the Flanker SSP parameters and the Global-Local drift rate difference.
Participants who reported more depressive symptoms had a lower strength of perceptual input.
Participants who reported more impulsivity had a lower strength of perceptual input, higher interference, as well as a more holistic processing style.
Participants who were more future oriented had a higher strength of perceptual input and a more detail-oriented processing style, without an association with interference.

```{r}
supp_cor_table
```

# Section 3. Deviations from preregistrations

## 3.1. Pilot

## 3.2. Study 1

## 3.3. Study 2

# Section 4. Model fit

## 4.1. Pilot

## 4.1.1 Cueing and Change Detection Task

In our initial, preregistered approach, DDM models for the Cueing and Change Detection Task were fit with the fast-dm-30 software [@voss_2015] using maximum likelihood (ML) estimation.
For both tasks, we started out with a model that freely estimated all parameters, and then fit additional models with an increasing number of constrained parameters.
We compared model fit using the Bayesian information criterion (BIC), for which smaller values indicate better fit.
For the Change Detection Task, the most simple model provided the best fit.
This model freely estimated the drift rate, non-decision time, and boundary separation, and fixed all other parameters.

For the Cued Attention Task, three models provided comparable model fit.
However, all three models showed estimation problems, especially with regard to the boundary separation.
Specifically, boundary separation estimates for several participants ended up at an upper boundary of 10, indicating that they were not recovered well.
Based on subsequent external input, we fit an additional model using Kolmogorov-Smirnov (KS) estimation instead of ML estimation, additionally estimating the inter-trial variability parameter of the non-decision time.
This improved parameter estimation (see Figure SX).

```{r}
cueing_DDM_results_mod9 |> 
  select(starts_with("cueing"), -cueing_ks_fit) |> 
  rename(
    "a" = cueing_ks_a,
    "v - cued" = cueing_cued_ks_v,
    "v - neutral" = cueing_neutral_ks_v,
    "t - cued" = cueing_cued_ks_t0,
    "t - neutral" = cueing_neutral_ks_t0,
  ) |> 
  pivot_longer(everything(), names_to = "parameter", values_to = "Estimate") |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~parameter, scales = 'free')
```
Finally, we switched to estimation using Hierarchical Bayesian DDM (HDDM) for our final analyses.
The main reason for this step was that although KS estimation seemed to work well, we had fewer trials than is typically recommended for this estimation technique [@lerche_2017].
An advantage of HDDM is that it uses group-level estimates to inform and constrain individual-level estimates.
This is especially useful in cases such as ours, where we have a large sample size but relatively few trials per participant.

The HDDM models were fit using the *runjags* package [@denwood_2016], using code from @johnson_2017.
All models were fit using three Markov Chain Monte Carlo (MCMC) chains.
Each of these chains started with 2,000 burn-in samples, followed by 10,000 additional samples.
To decrease the total size of the model, every 10th sample was retained, resulting in a posterior sample of 3,000 samples.

Model convergence was assessed (1) by visually inspecting the traces, which should not contain any drifts or large jumps; (2) through simulation. Specifically, we used each participant's DDM estimates to simulate 100 RT and accuracy estimates (per condition). The distributions of the participant's true RTs and their simulated RTs were assessed through bivariate correlations at the 25th, 50th and 75th percentile.
We made the same comparison for mean accuracy levels.

## 4.1.2 Flanker

To fit the SSP model to the Flanker data, we followed recommendations by @grange_2016.
First, we searched for the optimal set of starting values.
For each participant, we used 50 sets of starting parameters with a variance of 20 for each, simulating 1,000 trials.
After finding the optimal starting values, we fit the final model based on 50,000 simulated trials.
Model fit was assessed through simulation.
For each participant, we simulated 50,000 trials.
We then calculated correlations between observed and simulated RTs at the 25th, 50th, and 75th percentile, as well as between observed and simulated mean accuracy.
As can be seen in Figure SX and Figure SX, we observed high agreement between observed and simulated RTs and accuracy rates.

<br>

```{r}
qq_data_flanker <- left_join(predicted_quantiles_flanker, observed_quantiles_flanker)

qq_flanker_rt <- ggplot(qq_data_flanker) +
  geom_point(aes(quan_rt_obs, quan_rt_pred)) +
  geom_abline(slope = 1, intercept = 0) +
  facet_grid(congruency~quantile) +
  labs(
    x = "\nObserved RT",
    y = "Predicted RT\n",
    title = "Flanker Task"
  ) +
  theme_classic()
```

<br>

```{r}
qq_flanker_acc <- ggplot(qq_data_flanker) +
  geom_point(aes(prop_acc_obs, prop_acc_pred)) +
  geom_abline(slope = 1, intercept = 0) +
  facet_grid(congruency~quantile) +
  expand_limits(x = 0, y = 0) +
  labs(
    x = "\nObserved Acc",
    y = "Predicted Acc\n"
  ) +
  theme_classic()
```

## 4.2. Study 1

Model fit of the Flanker was done the same as in the Pilot.
Figure SX and Figure SX show the model fit based on simulated data.
We found good model fit across all three conditions, both for RTs as well as accuracy rates.

<br>

```{r}
study1_ssp_fit_rt
```

<br>

```{r}
study1_ssp_fit_acc
```

<br>

## 4.3. Study 2

### 4.3.1 Flanker

Model fit of the Flanker was done the same as in the Pilot and Study 1.
Figure SX and Figure SX show the model fit based on simulated data.
We found good model fit, both for RTs as well as accuracy rates.

```{r}
study2_ssp_fit_rt
```

<br>

```{r}
study2_ssp_fit_acc
```

### 4.3.2 Global-Local Task

# Section 5. Multiverse analysis.

### 2024-03-26 manuscript/scripts/create_ssp_viz.R
move manuscript staging files to scripts folder

@@ -1,0 +1,60 @@
+library(bayestestR)  
+library(ggforce)
+library(ggtext)
+library(bruceR)
+
+
+ssp_plot_data1 <- distribution_normal(n = 1000, mean = 0, sd = 1.5)
+
+ssp_plot_data1 %>% 
+  density() %>%  
+  as.data.frame() %>% 
+  ggplot(aes(x=x, y=y)) +
+  geom_line(linewidth = 1) +
+  geom_segment(aes(x = -4, xend = -4, y = 0, yend = 0.008), linetype = "longdash") +
+  geom_segment(aes(x = 4, xend = 4, y = 0, yend = 0.008), linetype = "longdash") +
+  geom_segment(aes(x = -2, xend = -2, y = 0, yend = 0.11), linetype = "longdash") +
+  geom_segment(aes(x = 2, xend = 2, y = 0, yend = 0.11), linetype = "longdash") +
+  geom_segment(aes(x = 0, xend = 0, y = 0, yend = 0.26), linetype = "longdash") +
+  scale_x_continuous(breaks = c(-4,-2,0,2,4), labels=c("\u2190<br>|<br>*p*","\u2190<br>|<br>*p*","\u2192<br>|<br>*p*","\u2190<br>|<br>*p*","\u2190<br>|<br>*p*")) +
+  theme(
+    panel.background = element_rect(fill='transparent'),
+    plot.background = element_rect(fill='transparent', color=NA),
+    axis.text.x = element_markdown(color = 'black', size = 25),
+    axis.title = element_blank(),
+    axis.text.y = element_blank(),
+    axis.line.y = element_blank(),
+    axis.ticks = element_blank()
+  ) +
+  labs(
+    y = ""
+  ) 
+  
+
+
+ssp_plot_data2 <- distribution_normal(n = 1000, mean = 0, sd = 1)
+
+ssp_plot_data2 %>% 
+  density() %>%  
+  as.data.frame() %>% 
+  ggplot(aes(x=x, y=y)) +
+  geom_line(linewidth = 1) +
+  geom_segment(aes(x = -2, xend = -2, y = 0, yend = 0.06), linetype = "longdash") +
+  geom_segment(aes(x = 2, xend = 2, y = 0, yend = 0.06), linetype = "longdash") +
+  geom_segment(aes(x = 0, xend = 0, y = 0, yend = 0.39), linetype = "longdash") +
[…]

### 2024-03-26 manuscript/scripts/pilot_stage_objects.R

@@ -1,0 +1,1026 @@
+library(tidyverse)
+library(patchwork)
+library(ggsci)
+library(here)
+library(flextable)
+
+
+source(here("preregistrations/1_pilot/scripts/custom_functions/functions_corrplot.R"))
+
+
+cleaned_data = read_csv(here("data/1_pilot/2_cleaned_data.csv"))
+pilot_data <- cleaned_data # for easy referencing in the manuscript
+load(file = here("preregistrations/1_pilot/analysis_objects/primary_mult_summaries.RData"))
+load(file = here("preregistrations/1_pilot/analysis_objects/exploratory_mult_summaries.RData"))
+
+get_alphas <- function(data, string) {
+  (data |> 
+     select(matches(string)) |> 
+     psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+}
+
+
+
+# Descriptives ------------------------------------------------------------
+
+## IV distributions ----
+txt_ivs_dist_pilot <- 
+  cleaned_data |> select(matches("(mean|total|composite|edu_parents_recoded|age)$"),
+                         matches("^(acc|rt)_(flanker|cueing)"), acc_change, rt_change) |> 
+  map(function(x) {
+    list(
+      mean = round(mean(x, na.rm = T),2),
+      sd   = round(sd(x, na.rm = T),2)
+    )
+  })
+
+txt_ivs_alpha_pilot <- 
+  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
+    "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
+    "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
+    "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
+  map(function(x) {
+    (cleaned_data |> 
+       select(matches(x)) |> 
+       psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+  }) |> 
+  setNames(c("stai_s", "violence", "unp", 
+             "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
[…]

### 2024-03-26 manuscript/scripts/pooled_stage_objects.R

@@ -1,0 +1,346 @@
+library(tidyverse)
+library(here)
+library(ggsci)
+library(patchwork)
+library(flextable)
+library(specr)
+
+source(here("preregistrations/1_pilot/scripts/custom_functions/functions_corrplot.R"))
+
+load(file = "preregistrations/1_pilot/analysis_objects/primary_mult_summaries.RData")
+load(file = "preregistrations/1_pilot/analysis_objects/exploratory_mult_summaries.RData")
+
+load(file = here("preregistrations/2_study1/analysis_objects/primary_multiverse_summaries.RData"))
+load(file = here("preregistrations/2_study1/analysis_objects/exploratory_multiverse_summaries.RData"))
+
+load(file = here("preregistrations/3_study2/analysis_objects/primary_multiverse_summaries.RData"))
+load(file = here('preregistrations/3_study2/analysis_objects/study2_bootstrap_pvalues.RData'))
+
+
+load('manuscript/pilot_staged_results.RData')
+load('manuscript/study1_staged_results.RData')
+load('manuscript/study2_staged_results.RData')
+
+
+pilot_data = read_csv(here("data/1_pilot/2_cleaned_data.csv")) |> mutate(study = "pilot")
+study1_data = read_csv(here("data/2_study1/2_cleaned_data.csv")) |> mutate(study = "study1")
+study2_data = read_csv(here("data/3_study2/2_cleaned_data.csv")) |> mutate(study = "study2")
+# IV correlations ---------------------------------------------------------
+
+iv_cor_pooled_table <-  bind_rows(
+    pilot_data |> 
+      mutate(id = paste0("pilot", id)) |> 
+      rename(
+        pcunp_mean   = unp_mean,
+        nvs_mean     = violence_mean
+      ),
+    study1_data |> 
+      mutate(id = paste0("study1", id)),
+    study2_data |> 
+      mutate(id = paste0("study2", id)) |> select(-weight)
+  ) |> 
+select(nvs_mean, fighting_mean, vio_comp, 
+       quic_total_mean, pcunp_mean, chaos_mean, change_env_mean, unp_obj_comp, unp_subj_comp, unp_comp) |> 
+  corr_table(
+    numbered = T,
+    sample_size = F,
+    c.names = c("Neigh. violence", "Fighting", "Violence comp.", 
+                "QUIC", "Perc. unpredictability", "CHAOS", "Env. change", "Obj. unpredictability", "Subj. Unpredictability", "Unpredictability comp."),
[…]

### 2024-03-26 manuscript/scripts/study1_stage_objects.R

@@ -1,0 +1,1996 @@
+library(tidyverse)
+library(here)
+library(ggsci)
+library(patchwork)
+library(flextable)
+library(specr)
+
+
+cleaned_data = read_csv(here("data/2_study1/2_cleaned_data.csv"))
+study1_data <- cleaned_data
+load(file = here("preregistrations/2_study1/analysis_objects/primary_multiverse_summaries.RData"))
+load(file = here("preregistrations/2_study1/analysis_objects/exploratory_multiverse_summaries.RData"))
+load(file = here("preregistrations/2_study1/analysis_objects/study1_bootstrap_pvalues.RData"))
+
+get_alphas <- function(data, string) {
+  (data |> 
+     select(matches(string)) |> 
+     psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+}
+
+
+
+
+# Descriptives ------------------------------------------------------------
+
+## IV distributions ----
+txt_ivs_dist_study1 <- 
+  cleaned_data |> select(matches("(mean|total|composite|edu_parents_recoded)$")) |> 
+  map(function(x) {
+    list(
+      mean = round(mean(x, na.rm = T),2),
+      sd   = round(sd(x, na.rm = T),2)
+    )
+  })
+
+txt_ivs_alpha_study1 <- 
+  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
+    "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
+    "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
+    "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
+  map(function(x) {
+    (cleaned_data |> 
+       select(matches(x)) |> 
+       psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+  }) |> 
+  setNames(c("stai_s", "violence", "unp", 
+             "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
[…]

### 2024-03-26 manuscript/scripts/study2_stage_objects.R

@@ -1,0 +1,1128 @@
+library(tidyverse)
+library(here)
+library(ggsci)
+library(patchwork)
+library(flextable)
+library(specr)
+
+
+cleaned_data = read_csv(here("data/3_study2/2_cleaned_data.csv"))
+study2_data <- cleaned_data
+load(file = here("preregistrations/3_study2/analysis_objects/primary_multiverse_summaries.RData"))
+load(file = here('preregistrations/3_study2/analysis_objects/study2_bootstrap_pvalues.RData'))
+
+get_alphas <- function(data, string) {
+  (data |> 
+     select(matches(string)) |> 
+     psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+}
+
+
+
+
+# Descriptives ------------------------------------------------------------
+
+## IV distributions ----
+txt_ivs_dist_study2 <- 
+  cleaned_data |> select(matches("(mean|total|composite|edu_parents_recoded)$")) |> 
+  map(function(x) {
+    list(
+      mean = round(mean(x, na.rm = T),2),
+      sd   = round(sd(x, na.rm = T),2)
+    )
+  })
+
+txt_ivs_alpha_study2 <- 
+  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
+    "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
+    "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
+    "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
+  map(function(x) {
+    (cleaned_data |> 
+       select(matches(x)) |> 
+       psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
+  }) |> 
+  setNames(c("stai_s", "violence", "unp", 
+             "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
+             "quic_total", "chaos", "ses", "impuls", "fos_pa", "fos_tp", "fos_fc", "fos_fo", "depression"))
+
+
+## Sample characteristics ----
+
[…]

### 2024-03-26 manuscript/manuscript.qmd
new changes to manuscript

--- 2024-01-17 manuscript/manuscript5.Rmd
@@
 csl: apa.csl
+format:
+  docx:
+    reference-doc: reference-doc.docx
 output:
   officedown::rdocx_document:
-    reference_docx: reference-doc.docx
     page_margins:
       bottom: 1
-      top: 1
-      right: 1
-      left: 1
-      header: .5
       footer: 0
       gutter: 0
+      header: 0.5
+      left: 1
+      right: 1
+      top: 1
     plots:
@@
       caption:
-        style: Image Caption
         pre: 'Figure '
         sep: '. '
+        style: Image Caption
     tables:
       caption:
-        style: Table Caption
         pre: 'Table '
         sep: '. '
+        style: Table Caption
+  pdf_document: default
+  word_document: default
+editor: 
+  markdown: 
+    wrap: sentence
 ---
@@
 power_mixed       <- read_csv("../data/1_pilot/simulation/power_mixed_model.csv") %>% mutate(power = round(power, 0))
-source("pilot_stage_objects.R") # Staged results of the pilot study
-source("study1_stage_objects.R") # Staged results of study 1
-source("pooled_stage_objects.R") # Pooled staged results
-source("study2_stage_objects.R")
+
+load("pilot_staged_results.RData")
+load("study1_staged_results.RData")
+load("study2_staged_results.RData")
+load("pooled_staged_results.Rdata")
 ```
 
-####**Childhood adversity is not associated with lowered inhibition, but lower strength of perceptual input: A Drift Diffusion Model analysis**
-
-The perceptual strength parameter, p, provides an index of the perceptual contribution of each item in the stimulus display: a large value of p indicates strong perceptual processing and relatively easy ability to identify the arrows and map them onto the correct response.
-<br>
+#### **Childhood adversity is not associated with lowered inhibition, but lower perceptual processing: A Drift Diffusion Model analysis**
 
@@
 
+# Childhood adversity is not associated with lowered inhibition, but lower perceptual processing: A Drift Diffusion Model analysis
+
 The predominant view in developmental psychology is that exposure to adversity impairs cognitive abilities.
@@
 Recent adaptation-based perspectives, however, have argued that people from adversity may also develop intact, or enhanced, abilities for solving problems in high-adversity contexts [@ellis_2017; @frankenhuis_2013].
-These perspectives are considered complimentary: for instance, adversity may impair some cognitive processes, yet enhance others.
-Despite their compatibility, few studies have investigated the interplay of impaired and enhanced abilities shapes performance.
+Adaptation- and deficit-based perspectives are considered complimentary: for instance, adversity may impair some cognitive processes, yet enhance others.
+Despite their compatibility, few studies have investigated how the interplay of impaired and enhanced abilities shapes performance.
 In this paper, across three preregistered online experiments, we used cognitive modeling to derive a process-level understanding of the association between childhood adversity and performance on the Flanker Task, a popular measure of cognitive control [@ridderinkhof_2021].
 
+## Attention in adverse conditions
+
 It is well-established that early-life adversity is associated with deficits in the ability to inhibit distracting, goal-irrelevant information [@hackman_2010; @ursache_2016].
-These conclusions are often based on performance on the Flanker Task [@eriksen_1974].
+One of the leading paradigms in this literature is the Flanker Task [@eriksen_1974].
 On this task, participants typically see five arrows in a horizontal orientation, and are asked to indicate the direction of the central arrow.
@@
 Slower performance on the Flanker has been documented for children and adults with lower childhood socioeconomic status [SES\; @farah_2006; @mezzacappa_2004; @noble_2005] and more environmental unpredictability [@fields_2021; @mittal_2015].
-These findings are typically interpreted using a deficit lens, indicating impairment in the ability to inhibit distractions.
+These findings are typically interpreted as indicating a deficit in the ability to inhibit distractions.
 
-Notwithstanding, some recent studies suggest that growing up in adversity may be associated with improved abilities such as attention shifting [@fields_2021; @mittal_2015; @young_2022\; but see @nweze_2021].
-Notably, some studies found deficit patterns on the Flanker alongside enhancements on other aspects of attention within the same participants.
-For example, children with lower SES performed less well on the Flanker, but outperformed children from from higher SES on orienting their attention to salient, peripheral cues [@mezzacappa_2004]. 
+Nonetheless, some recent studies suggest that growing up in adversity may also be associated with improved abilities such as attention shifting [@fields_2021; @mittal_2015; @young_2022; but see @nweze_2021].
+Some studies found deficit patterns on the Flanker alongside enhancements on other aspects of attention within the same participants.
+For example, in one study, children with lower SES performed less well on the Flanker, but outperformed children from higher SES on orienting their attention to salient cues and, peripheral cues [@mezzacappa_2004].
 Similarly, children with more caregiver switches (an indicator of unpredictability) were found to perform less well on the Flanker, but outperformed children with fewer caregiver switches on shifting their attention between different task goals [@fields_2021].
-In less favorable environmental conditions, attending to peripheral cues and efficient attention shifting might promote the ability to seize fleeting rewards and detect sudden threats.
-In contrast, a person who tends to inhibit distractions might be more likely to overlook such information [@mittal_2015].
 
-The potential benefits of quickly shifting attention and detecting subtle, peripheral changes might be linked to the notion of a *present-oriented attention style* [@frankenhuis_2016; @vangelder_2023].
-People with a present-oriented attention style (versus a more future-oriented attention style) are more geared towards processing information that is relevant for solving challenges and obtaining rewards in the here-and-now.
-A general tendency to be more attuned to the present (while disregarding the future) is sometimes referred to as a short-term mindset [@vangelder_2023].
-In environments that are both harsh and unpredictable, it might be particularly adaptive to develop a present-oriented attention style [@frankenhuis_2016].
-Thus, patterns of lowered and improved performance across tasks with different attention demands could reflect two sides of the same coin: an attention style that is beneficial for one task might hurt performance on other tasks.
+Performance on attention tasks could reflect developmental adaptation to adverse environments [@blair_2012; @dangiulli_2012; @frankenhuis_2020; @mittal_2015].
+In unpredictable or threatening conditions, the ability to detect salient peripheral information (e.g., distant noises or approaching individuals) could help to more quickly detect and act on potential threats.
+Over time, cognitive adaptations to such conditions could result in a general tendency to use a more diffuse scope of attention, leading to an enhanced ability to keep track of the broader environment.
+In line with this hypothesis, people with lower SES respond more strongly to auditory distractors [@giuliano_2018; @stevens_2009; @hao_2022] and are faster to orient their attention to peripheral visual information [@mezzacappa_2004].
+While potentially adaptive, a more diffuse scope of attention could come at the cost of lowered ability to ignore irrelevant distractors.
+This could compromise more long-term goal-directed behavior, especially in chaotic environments (e.g., a noisy classroom or a busy street).
 
-Although such a process-level explanation may be intuitive, we cannot yet rule out another, psychometric explanation related to limitations of the Flanker, and cognitive control tasks generally.
-First, the correlations between different inhibition tasks (e.g., Flanker, Go/No-Go, Stroop) are typically moderate or even week, and these tasks often fail to form a coherent latent estimate of inhibition [@draheim_2021; @krumm_2009; @loffler_2022; @rey_mermet_2019; @rouder_2019; @stahl_2014].
-This suggests that inhibition might not be a single ability that operates the same way across different contexts.
-If so, the association between a present-oriented attention style and performance on inhibition tasks might be more complex than previously thought.
-Second, cognitive modeling, used to separate different cognitive processes, suggests that basic processing speed is the most stable determinant of performance across inhibition tasks, not actual inhibition [@hedge_2022; @loffler_2022].
-This means that lowered performance on inhibition tasks does not necessarily reflect inhibition difficulties, and therefore might not necessarily be related to a present-oriented attention style.
+Thus, lowered performance on tasks like the Flanker could reflect either a cognitive impairment or a difference in attentional strategies.
+Distinguishing between these two possibilities is challenging for two reasons.
+First, few studies in the adversity literature have measured performance differences on different attention tasks within the same individual.
+Thus, it is unclear whether lowered inhibition is related to enhanced processing of peripheral information in people from from adverse backgrounds.
+Second, performance on inhibition tasks is---beyond the ability to inhibit distractors---also influenced by other factors, such as a person's general processing speed and response caution [@hedge_2022; @loffler_2022].
+This multifinality means that lowered performance on inhibition tasks does not necessarily reflect inhibition difficulties.
+In other words, we should consider cognitive processes other than ability when drawing inferences based on inhibition tasks.
 
@@
 
-Thus, an important issue is that several processes are involved in performance on the Flanker, and standard assessments using raw performance measures (response times, accuracy rates) mostly fail to distinguish between them.
+An important issue, therefore, is that several processes are involved in performance on the Flanker, and standard assessments using raw performance measures (response times, accuracy rates) mostly fail to distinguish between them.
 For example, performance differences on the Flanker could indicate that someone experiences more (or less) flanker interference, generally processes less (or more) efficiently, or responds with less (or more) caution.
@@
 
-Formal cognitive models such as the Drift Diffusion Model [DDM\; @forstmann_2016; @ratcliff_1998; @ratcliff_2008; @ratcliff_2015; @wagenmakers_2009] provide a solution.
+Formal cognitive models such as the Drift Diffusion Model [DDM\; @forstmann_2016; @ratcliff_1998; @ratcliff_2008; @ratcliff_2015; @wagenmakers_2009] provide a potential solution.
 The DDM estimates cognitive processes at different stages of the decision-making process (See Figure 1a).
-It represents decision-making on a binary decision-making task as a process in which people accumulate information until favor one response over the other.   
+It represents decision-making on binary decision-making tasks as a process in which people accumulate information until one response is sufficiently favored over the other.
 These two response options are represented as opposing boundaries.
@@
 
-The DDM translates trial-level RTs and accuracy into three distinct cognitive processes.
+The DDM translates trial-level response times (RTs) and accuracy into three distinct cognitive processes.
 The speed of information accumulation is captured in a parameter called the *drift rate*.
@@
 
-The Shrinking Spotlight (SSP) model is an extension of the standard DDM to account for attention processes on the Flanker [See Figure 1b\; @grange_2016; @white_2018a; @white_2018b; @white_2011].
+The Shrinking Spotlight (SSP) model is an extension of the standard DDM to account for attention processes on the Flanker [@grange_2016; @white_2018a; @white_2018b; @white_2011].
 The SSP model assumes that attention resembles a spotlight that is normally distributed over the Flanker arrows (with a particular starting *attentional width*).
-Over time, people narrow their attention down to the central arrow (at a rate defined by the *shrinking rate*), thereby gradually decreasing interference from irrelevant information.
+Over time, people narrow their attention down to the central arrow (at a rate defined by the *shrinking rate*), thereby gradually decreasing interference from irrelevant information (See Figure 1b).
 Prior work has defined the amount of distractor *interference* by dividing the attentional width by the shrinking rate [@white_2018a].
@@
 Note that typical interpretations of lowered raw Flanker performance are in terms of the amount of interference that someone experiences, and not in terms of the strength of perceptual input.
-In this paper, we are interested in how childhood adversity is associated with both interference and the strength of perceptual input.
+Here, we are interested in how childhood adversity is associated with both interference and the strength of perceptual input.
+
+<br>
 
@@
 # Overview of studies
+
 The overarching goal of our studies is to understand the attentional and processing styles that people develop in conditions of adversity.
 We focus on measures of exposure to violence and environmental unpredictability.
-Previous research shows that they these two types of adversity are on the one hand associated with improved attention shifting and working memory updating [@fields_2021; @mittal_2015; @young_2018; @young_2022], yet on the other hand with lowered inhibition and working memory capacity [@fields_2021; @mittal_2015; @young_2018].
+Previous research shows that these two types of adversity are on the one hand associated with improved attention shifting and working memory updating [@fields_2021; @mittal_2015; @young_2018; @young_2022], and on the other hand with lowered inhibition and working memory capacity [@fields_2021; @mittal_2015; @young_2018].
 We conducted three online studies: one pilot and two follow-up studies).
-Using cognitive modeling, we unpack Flanker performance 1) in comparison to other tasks that require externally focused attention (Pilot), 2) across visual processing manipulations (Study 1), and 3) in terms of tendencies for holistic versus local processing (Study 2).
+Using cognitive modeling, we unpack Flanker performance in comparison to other tasks that require externally focused attention (Pilot), across visual processing manipulations (Study 1), and in terms of tendencies for holistic versus local processing (Study 2).
 
-We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see [https://github.com/stefanvermeent/attention_project/preregistrations](https://github.com/stefanvermeent/attention_project/preregistrations)).
+We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see <https://github.com/stefanvermeent/attention_project/preregistrations>).
 For each study, we preregistered primary (i.e., hypothesis-driven) and exploratory analyses.
@@
 Specifically, we expected participants with more violence exposure to be better at detecting peripheral stimuli and subtle changes.
-This expected this would result in a higher drift rate (faster speed of information accummulation) or shorter non-decision times (faster attention orientation, among other things), but not necessarily with differences in boundary separation (response caution).
+We expected this would result in a higher drift rate (faster speed of information accumulation) or shorter non-decision times (faster attention orientation, among other things), but not necessarily with differences in boundary separation (response caution).
 Second, we expected that participants with more violence exposure would be worse at ignoring distracting peripheral stimuli.
@@
 
-```{r table1, tab.id = "table1", tab.cap.style = "Table Caption", tab.cap="Demographic information for all studies."}
+```{r}
+#| tab.id: table1
+#| results: markup
 demographics_table
@@
 
-We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the minimally required number of participants for standardized regression coefficients of 0.10 and 0.15 (for details and simulation code, see GitHub).
-Power was > .80 for adversity x task condition interactions with *N* = 450 or more. 
+We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the minimally required number of participants for standardized regression coefficients of 0.10 and 0.15 (for details and simulation code, see ([https://github.com/stefanvermeent/attention_project/preregistrations](https://github.com/stefanvermeent/attention_project/preregistrations)).
+Power was \> .80 for adversity x task condition interactions with *N* = 450 or more.
 For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require *N* = `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`.
-We sampled 550 participants, anticipating a final sample of ~500 after exclusions.
+We sampled 550 participants, anticipating a final sample of \~500 after exclusions.
 
@@
 First, we excluded participants who did not complete the full study; second, those who had incomplete data on any of the attention tasks; third, those who missed both attention check items; fourth, those who had suspicious response patterns (e.g., consistently endorsing high response options even though some items were reverse coded).
-Fifth, on a trial-level, we excluded any trials with reaction times < 250 ms or > 3500 ms [@ratcliff_2015].
-Participants with more than 10 trials removed were completely excluded from the analyses.  
+Fifth, on a trial-level, we excluded any trials with reaction times \< 250 ms or \> 3500 ms [@ratcliff_2015].
+Participants with more than 10 trials removed were completely excluded from the analyses.\
 The final sample consisted of `r nrow(pilot_data)` participants.
@@
 Participants completed the experiment on their own laptop or desktop computer.
-Participants could refrain from answering any of the questionnaire items, and were prompted with a warning once per page in the case of missing items.
+Participants could refrain from answering any of the questionnaire items and were prompted with a warning once per page in case of missing items.
 
@@
 Finally, we asked participants whether they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.
-The full experiment took ~35 minutes. 
+The full experiment took \~35 minutes.
 Participants were paid £4.38 when they reached the end of the experiment.
@@
 
-**Cued Attention Task.** The Cued Attention Task wis an adapted version of the Posner task, which measures the speed of attention for peripheral cues [@posner_1980]. 
+**Cued Attention Task.** The Cued Attention Task was an adapted version of the Posner task, which measures the speed of attention for peripheral cues [@posner_1980].
 The Cued Attention Task began with eight practice trials, followed by 64 test trials.
@@
 Thus, the cue was perfectly predictive of the target location on cued trials, but provided no predictive information about the location of the arrow on neutral trials.
-Each trial started with a fixation cross at the center of the screen for 1000 ms. 
-Then, the cue appeared for 250 ms, followed by the target arrow, until a response was given.
+Each trial started with a fixation cross at the center of the screen for 1000 ms. Then, the cue appeared for 250 ms, followed by the target arrow, until a response was given.
 
@@
 This was supported in a simulation study by @white_2018a showing that the ratio measure is reliable.
-See the supplemental materials (section ) for a comparison between the preregistered and the updated analyses.
+See the supplemental materials (section 3) for a comparison between the preregistered and the updated analyses.
 
 For the Change Detection Task and the Cued Attention Task, we used a hierarchical Bayesian implementation of the standard DDM (HDDM).
-For each participant, the HDDM provided us with estimates of: 1) drift rate (speed of information accumulation; analogous to strength of perceptual input in the SSP model, except that drift rate is time-invariant), 2) non-decision time (same as SSP model), and 3) boundary separation (same as SSP model).
+For each participant, the HDDM provided us with estimates of: (1) drift rate (speed of information accumulation; analogous to strength of perceptual input in the SSP model, except that drift rate is time-invariant), (2) non-decision time (same as SSP model), and (3) boundary separation (same as SSP model).
 The hierarchical Bayesian fitting procedure was a deviation from the preregistration, in which we planned to use Maximum Likelihood (ML) estimation.
@@
 All scales were adapted to refer to experiences before age 13.
-In the main text, we focus on exploratory analyses involving a composite measure of all z-transformed unpredictability measures.
-We report additional exploratory analyses involving different subsets of the measures in the supplemental materials (section XXX).
+We computed a composite measure of all z-transformed unpredictability measures.
+See section 2 of the supplemental materials for an exploration of the factor structure of these measures.
 
@@
 We made three preregistered changes to the original scale [@glynn_2019], to better align it with the other scales.
-All items were rated on a scale of 1 (never true) to 5 (very often true), except for four items referring to specific experiences (e.g., "I experienced changes in my custody arrangement"). 
+First, all items were rated on a scale of 1 (never true) to 5 (very often true), except for four items referring to specific experiences (e.g., "I experienced changes in my custody arrangement").
 For these items, we adopted a response scale with the options "never", "only once", "a couple times", "several times", "many times".
-Third, quantifiers such as "frequently", "often", and "There was a period of time when [...]" were dropped to better match the response scale. 
-We excluded the item "My parents got divorced" because it did not fit the new response labels and this information was already captured by one of the items of the perceived unpredictability scale.
+Second, quantifiers such as "frequently", "often", and "There was a period of time when [...]" were dropped to better match the response scale.
+Third, we excluded the item "My parents got divorced" because it did not fit the new response labels and this information was already captured by one of the items of the perceived unpredictability scale.
 Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$quic_total`).
 
-The perceived childhood unpredictability scale included eight items measuring perceived unpredictability before age 13 (e.g,.
-"My family life was generally inconsistent and unpredictable from day-to-day").
+The perceived childhood unpredictability scale included eight items measuring perceived unpredictability before age 13 (e.g., "My family life was generally inconsistent and unpredictable from day-to-day").
 Participants rated each on a scale from 1 (never true) to 5 (very often true).
@@
 
-```{r table2, tab.id = "table2", tab.cap.style = "Table Caption", tab.cap="Pooled bivariate correlations and descriptive statistics of measures of childhood violence exposure and environmental unpredictability across the three studies."}
+```{r}
+#| tab.id: table2
+#| results: markup
 iv_cor_pooled_table
@@
 **Multiverse analysis.** In an amendment to the preregistration, we quantified the robustness of our findings against six data cleaning decisions that may affect the robustness of online studies by using multiverse analysis, using the *multitool* package [@young_2023].
-Multiverse analysis allows systematically evaluating the robustness of analyses across all combinations of different arbitrary data processing decisions (for details, see @giudice_2021; @simonsohn_2020; @steegen_2016).
+Multiverse analysis allows for systematically evaluating the robustness of analyses across all combinations of different arbitrary data processing decisions [for details, see @giudice_2021; @simonsohn_2020; @steegen_2016].
 Specifically, we looked at the influence of including or excluding 1) participants who scored below 0.5 on a build-in bot-detection measure on Prolific (potentially indicating a bot); 2) participants who did not rescale their screen at the start of the experiment; 3) participants who did not enter fullscreen mode prior to starting the tasks; 4) participants who exited fullscreen mode at any point during the tasks; 5) participants who indicated high levels of noise in their environment; 6) participants who indicated extreme interruptions during the experiment.
@@
 For boundary separation, we solved this using log-transformation.
-For interference, non-normality was caused by extreme outliers (>3.2SD), which we excluded from the analyses.
+For interference, non-normality was caused by extreme outliers (\>3.2SD), which we excluded from the analyses.
 
@@
 
-```{r table3, tab.id = "table3", tab.cap.style = "Table Caption", tab.cap="Main and interaction effects of the effect of violence exposure on task performance."}
+```{r}
+#| tab.id: table3
+#| results: markup
 pilot_main_eff_ddm_table
@@
 Participants completed three versions: a standard version (similar to the Pilot), one with enhanced visual information, and one with degraded visual information.
-We focused again on childhood exposure to violence.
+We again focused on childhood exposure to violence.
 Our first aim was to examine the robustness of our finding of improved interference control on the Flanker in relation to more adversity exposure in the pilot.
@@
 We programmed the Flanker in JsPsych version 6.3.1 [@deleeuw_2015] with three conditions.
-Each condition consisted of eight practice trials, followed b 64 test trials.
+Each condition consisted of eight practice trials, followed by 64 test trials.
 In the *standard* condition, the arrows were 40 pixels in size (0.4 inches) and had zero padding between them.
@@
 This increased the width of the stimulus display by 50% with respect to the standard display.
-In the 'degraded' condition, sizes and space between arrows were the same as in the standard version, but all arrows were rotated 45$^\circ$ (in the same direction). 
+In the 'degraded' condition, sizes and space between arrows were the same as in the standard version, but all arrows were rotated 45$^\circ$ (in the same direction; that is, if the left flanker arrows pointed upwards, the right flanker arrows pointed downward).
 Participants completed each condition separately in different blocks, in randomized order.
@@
 The full experiment took approximately 30 minutes.
-Participants were paid £3.75 when they reached the end of the experiment.
+Participants were paid £3.75 after they completed the full study.
 
@@
 **Multiverse analysis.** We included the same arbitrary decisions in the multiverse analyses as in the Pilot.
-For the pooled analyses---i.e., joint analysis of the Pilot and the standard condition of Study 1---there was one minor change in in how we screen rescaling as a preprocessing decision in the multiverse.
-In Study 1, we changed the screen rescaling procedure by making the initial size of the resize box 300 pixels instead of 100 pixels.
+For the pooled analyses---i.e., joint analysis of the Pilot and the standard condition of Study 1---there was one minor change in how we included screen rescaling as a preprocessing decision in the multiverse.
+In Study 1, we changed the screen rescaling procedure by converting the initial size of the resize box to 300 pixels instead of 100 pixels.
 This way, the stimulus display would still be close to the intended size if participants did not engage in any resizing.
@@
 
-For each analysis, we report the median $\beta$s, 95% confidence intervals, and the proportion of *p*-values < .05 across all analytic decisions.
+For each analysis, we report the median $\beta$s, 95% confidence intervals, and the proportion of *p*-values \< .05 across all analytic decisions.
 For the primary analyses, we used bootstrapping to compute the probability of obtaining an effect size at least as extreme as observed in the real data, conditioned on a true effect size of zero [for details, see @simonsohn_2020].
 
-**Primary analyses.** To address the first primary aim, we analyzed the data from the standard condition, as well as pooled the Flanker data of the Pilot and the current study.
+**Primary analyses.** To address the first aim, we analyzed the data from the standard condition, as well as pooled the Flanker data of the Pilot and the current study.
 We ran separate linear models for each SSP parameter as well as RT difference scores with violence exposure as main predictor and study as covariate (effect-coded).
-To address the second primary aim, we analyzed the effect of violence exposure and Flanker condition type on performance using linear mixed effects models with a random intercept per participant. 
+To address the second aim, we analyzed the effect of violence exposure and Flanker condition type on performance using linear mixed effects models with a random intercept per participant.
 The five main dependent variables were mean RT difference and the SSP parameters: Perceptual input, boundary separation, non-decision time, and interference.
@@
 Unlike in the Pilot, we did not find any significant associations with violence exposure.
-In the exploratory analysis, there was a significant negative association between unpredictability and perceptual input (median $\beta$ = `r study1_expl_results_list$p_flanker$median_effect_Main`, 95% CI = `r study1_expl_results_list$p_flanker$CI`, `r study1_expl_results_list$p_flanker$p_sum` % of *p*s <.05).
+In the exploratory analysis, there was a significant negative association between unpredictability and perceptual input (median $\beta$ = `r study1_expl_results_list$p_flanker$median_effect_Main`, 95% CI = `r study1_expl_results_list$p_flanker$CI`, `r study1_expl_results_list$p_flanker$p_sum` % of *p*s \<.05).
 
-```{r table4, tab.id = "table4", tab.cap.style = "Table Caption", tab.cap="Standardized effects of violence exposure and unpredictability on Flanker performance in study 1."}
+```{r}
+#| tab.id: table4
+#| results: markup
 study1_results_table
@@
 
-After pooling the data of the pilot study and Study 1, there was a negative association between violence exposure and interference (median $\beta$ = `r study1_pooled_results_list$interference_vio$median_effect`, 95% CI = `r study1_pooled_results_list$interference_vio$CI`, `r study1_pooled_results_list$interference_vio$p_sum` % of *p*s <.05, bootstrapped *p* = `r study1_pooled_results_list$interference_vio$boot_p`).
+After pooling the data of the pilot study and Study 1, there was a negative association between violence exposure and interference (median $\beta$ = `r study1_pooled_results_list$interference_vio$median_effect`, 95% CI = `r study1_pooled_results_list$interference_vio$CI`, `r study1_pooled_results_list$interference_vio$p_sum` % of *p*s \<.05, bootstrapped *p* = `r study1_pooled_results_list$interference_vio$boot_p`).
 Violence exposure was associated with lower strength of perceptual input under `r study1_pooled_results_list$interference_vio$p_sum`% of multiverse specifications, but the bootstrapped *p*-value was not significant (median $\beta$ = `r study1_pooled_results_list$p_vio$median_effect`, 95% CI = `r study1_pooled_results_list$p_vio$CI`, bootstrapped *p* = `r study1_pooled_results_list$p_vio$boot_p`).
@@
 
-The main effects of task condition on the strength of perceptual input were in the expected direction: relative to the standard condition, the quality of perceptual input was higher in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$p_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$p_enhanced$condition_CI`, `r study1_condition_vio_results_list$p_enhanced$p_sum_Condition` % of *p*s <.05) and lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$p_degraded$median_effect_Condition`, 95% CI = `r  study1_condition_vio_results_list$p_degraded$condition_CI`, `r study1_condition_vio_results_list$p_degraded$p_sum_Condition` % of *p*s <.05).
-Interference was lower in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$interference_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_enhanced$condition_CI`, `r study1_condition_vio_results_list$interference_enhanced$p_sum_Condition` % of *p*s <.05).
-Unexpectedly, interference was also lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$interference_degraded$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_degraded$condition_CI`, `r study1_condition_vio_results_list$interference_degraded$p_sum_Condition` % of *p*s <.05), suggesting that the angle in the flanking arrows reduced interference, relative to the standard condition.
+The main effects of task condition on the strength of perceptual input were in the expected direction: relative to the standard condition, the quality of perceptual input was higher in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$p_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$p_enhanced$condition_CI`, `r study1_condition_vio_results_list$p_enhanced$p_sum_Condition` % of *p*s \<.05) and lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$p_degraded$median_effect_Condition`, 95% CI = `r  study1_condition_vio_results_list$p_degraded$condition_CI`, `r study1_condition_vio_results_list$p_degraded$p_sum_Condition` % of *p*s \<.05).
+Interference was lower in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$interference_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_enhanced$condition_CI`, `r study1_condition_vio_results_list$interference_enhanced$p_sum_Condition` % of *p*s \<.05).
+Unexpectedly, interference was also lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$interference_degraded$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_degraded$condition_CI`, `r study1_condition_vio_results_list$interference_degraded$p_sum_Condition` % of *p*s \<.05), suggesting that the angle in the flanking arrows reduced interference, relative to the standard condition.
 However, none of the interaction effects for either violence exposure or unpredictability were significant.
 
-```{r table5, tab.id = "table5", tab.cap.style = "Table Caption", tab.cap="Standardized interaction effects of violence exposure (primary analysis) and unpredictability (secondary analysis) on Flanker performance across standard, enhanced, and degraded conditions."}
+```{r}
+#| tab.id: table5
+#| results: markup
 study1_condition_results_table
@@
 First, lowered strength of perceptual input in people exposed to adversity may indicate a difficulty in extracting relevant information (i.e., about their direction) from the arrows in general.
-Second, the difference in perceptual input may not be a cognitive deficit per se, but instead could be a signature of a difference in processing style---a feature, not a bug.
+Second, the difference in perceptual input may not be a cognitive deficit per se, but instead could be a signature of a difference in processing style---that is, a feature, and not a bug.
 People exposed to adversity may process information more holistically, focusing more on the configuration of pieces of information rather than individual pieces of information.
@@
 Recruitment was identical to Study 1.
-We conducted a simulation-based for the planned linear mixed models with the Global Local Task (see GitHub). 
-We determined that power of > .80 for a standardized interaction effect of 0.06, with sigma (noise) set to 0.7 (comparable to observed sigma's in the first two studies) would require 550 participants.
+We conducted a simulation-based power analysis for the planned linear mixed models with the Global Local Task (see GitHub).
+We determined that power of \> .80 for a standardized interaction effect of 0.06, with sigma (noise) set to 0.7 (comparable to observed sigmas in the first two studies) would require 550 participants.
 We recruited 600 participants, with the expectation to have a final sample of 550 participants after exclusions.
@@
 
-*Global-Local Task*. The Global-Local Task is a measure of global-local processing [@navon_1977].
+*Global-Local Task*.
+The Global-Local Task is a measure of global-local processing [@navon_1977].
 Many different versions of this task exist in the literature.
@@
 The procedure was identical to Study 1.
-The full experiment took ~30 minutes. 
+The full experiment took \~30 minutes.
 Participants were paid £4.50 when they reached the end of the experiment.
@@
 **Multiverse analysis.** We included the same decisions in the multiverse as in the previous studies.
-However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, see [https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md))
+However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, see <https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md>)
 
-**DDM estimation.** For the Flanker, we used the SSP (@grange_2016; @white_2018a; @white_2018b; @white_2011] using the same procedure as in Study 1.
+**DDM estimation.** For the Flanker, we used the SSP (@grange_2016; @white_2018a; @white_2018b; @white_2011\] using the same procedure as in Study 1.
 For the Global-Local Task, we used a hierarchical Bayesian DDM to fit the data using the *runjags* package [@denwood_2016].
@@
 
-We deviated from our preregistration with regard to the preprocessing of Global-Local Task data.
+We deviated from our preregistration regarding the preprocessing of Global-Local Task data.
 Specifically, we relaxed the low performance threshold as the task was more difficult than anticipated.
-These deviations are described in the amendment ([https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md)).
+These deviations are described in the amendment (<https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md>).
 
@@
 
-Figure 1 and 2 summarize the multiverse results for the effects of violence exposure and unpredictability within Study 2 and pooled across all studies.
-In Study 2, violence exposure was negatively associated with strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.vio_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.vio_comp$boot_p`), but not associated with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.vio_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$boot_p`).
-Unpredictability was not associated with either strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.unp_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.unp_comp$boot_p`), nor with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.unp_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$boot_p`).
+Figure 2 and 3 summarize the multiverse results for the effects of violence exposure and unpredictability within Study 2 and pooled across all studies.
+In Study 2, violence exposure was negatively associated with strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.vio_comp$boot_p`), but not associated with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$boot_p`).
+Unpredictability was not associated with either strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.unp_comp$boot_p`), nor with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$boot_p`).
 
 In the pooled analysis, the results were similar for both types of adversity.
-Violence exposure was associated with lower strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_list$p_flanker.vio_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.vio_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_list$interference_flanker.vio_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.vio_comp$boot_p`).
-Similarly, unpredictability was associated with a lower quality of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_list$p_flanker.unp_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.unp_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_list$interference_flanker.unp_comp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.unp_comp$boot_p`).
+Violence exposure was associated with lower strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.vio_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.vio_comp$boot_p`).
+Similarly, unpredictability was associated with a lower quality of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_list$p_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.unp_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_list$interference_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.unp_comp$boot_p`).
 
-```{r figure2, fig.height=9, fig.width = 7, fig.id = "figure2", fig.cap.style = "Figure Caption", fig.cap="Multiverse results for the association between violence exposure with the strength of perceptual input and interference on the Flanker across all studies.
-Panels A-D depict sorted standardized beta coefficients across each arbitrary decision for the Pilot study, Study 1, Study 2, and pooled across all three studies, respectively.
-Panel E depicts the percentage of variance that each arbitrary decision explains in the standardized effect.
-Panel E does not depict the influence of failing the bot-detection measure for the Pilot study and Study 1 because all participants reached the required cut-off."}
+```{r}
+#| label: figure2
+#| fig.width: 7
+#| fig.height: 9
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure 2.** Multiverse results for the association between violence exposure with the strength of perceptual input and interference on the Flanker across all studies.
+Each panel depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
+The top row depicts effect curves in the Pilot.
+The second row depicts effect curves in Study 1.
+The third row depicts effect curves in Study 2.
+The Fourth row depicts effect curves of the pooled analyses across all studies.
 knitr::include_graphics("figures/fig2.png")
+```
+
+<br>
+
+```{r}
+#| label: figure3
+#| fig.width: 7
+#| fig.height: 9
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure 3.** Multiverse results for the association between unpredictability with the strength of perceptual input and interference on the Flanker across all studies.
+Each panel depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
+The top row depicts effect curves in the Pilot.
+The second row depicts effect curves in Study 1.
+The third row depicts effect curves in Study 2.
+The Fourth row depicts effect curves of the pooled analyses across all studies.
+knitr::include_graphics("figures/fig3.png")
 ```
@@
 
-There was a main effect of violence exposure on Global-Local drift rates, with more violence exposure being associated with slower speed of information processing ($\beta$~median~ = `r study2_aim2_results_list$Main_vio$median_effect`, `r study2_aim2_results_list$Main_vio$p_sum`% of *p*s < .05, bootstrapped *p* `r study2_aim2_results_list$Main_vio$boot_p`).
-There also was a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_vio$median_effect`, `r study2_aim2_results_list$Condition_vio$p_sum`% of *p*s < .05, bootstrapped *p* `r study2_aim2_results_list$Condition_vio$boot_p`).
-Finally, there was an interaction effect between violence exposure and task condition ($\beta$~median~ = `r study2_aim2_results_list$Interaction_vio$median_effect`, `r study2_aim2_results_list$Interaction_vio$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_vio$boot_p`).
-Simple slopes analyses revealed that participants with lower levels of violence exposure did not differ in speed of processing of global versus local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.Low$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.Low$p_sum`% of *p*s < .05).
-In contrast, participants with higher levels of violence exposure processed global targets faster than local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.High$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.High$p_sum`% of *p*s < .05).
+There was a main effect of violence exposure on Global-Local drift rates, with more violence exposure being associated with slower speed of information processing ($\beta$~median~ = `r study2_aim2_results_list$Main_vio$median_effect`, `r study2_aim2_results_list$Main_vio$p_sum`% of *p*s \< .05, bootstrapped *p* `r study2_aim2_results_list$Main_vio$boot_p`).
+There also was a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_vio$median_effect`, `r study2_aim2_results_list$Condition_vio$p_sum`% of *p*s \< .05, bootstrapped *p* `r study2_aim2_results_list$Condition_vio$boot_p`).
+Finally, there was an interaction effect between violence exposure and task condition ($\beta$~median~ = `r study2_aim2_results_list$Interaction_vio$median_effect`, `r study2_aim2_results_list$Interaction_vio$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_vio$boot_p`).
+Simple slopes analyses revealed that participants with lower levels of violence exposure did not differ in speed of processing of global versus local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.Low$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.Low$p_sum`% of *p*s \< .05).
+In contrast, participants with higher levels of violence exposure processed global targets faster than local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.High$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.High$p_sum`% of *p*s \< .05).
 
-There was a significant main effect of unpredictability on drift rates, with more unpredictability being associated with slower speed of information processing, ($\beta$~median~ = `r study2_aim2_results_list$Main_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Main_unp$CI`, `r study2_aim2_results_list$Main_unp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim2_results_list$Main_unp$boot_p`).
-We also found a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Condition_vio$CI`, `r study2_aim2_results_list$Condition_unp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim2_results_list$Condition_unp$boot_p`).
-We did not find a significant unpredictability x task condition interaction effect ($\beta$~median~ = `r study2_aim2_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Interaction_unp$CI`, `r study2_aim2_results_list$Interaction_unp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_unp$boot_p`).
+There was a significant main effect of unpredictability on drift rates, with more unpredictability being associated with slower speed of information processing, ($\beta$~median~ = `r study2_aim2_results_list$Main_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Main_unp$CI`, `r study2_aim2_results_list$Main_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Main_unp$boot_p`).
+We also found a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Condition_vio$CI`, `r study2_aim2_results_list$Condition_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Condition_unp$boot_p`).
+We did not find a significant unpredictability x task condition interaction effect ($\beta$~median~ = `r study2_aim2_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Interaction_unp$CI`, `r study2_aim2_results_list$Interaction_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_unp$boot_p`).
 
@@
 There was no significant main effects for violence exposure (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`) nor for cognitive task (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`).
-There was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_vio$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_vio$CI`, `r study2_aim3_results_list$Interaction_vio$p_sum` % of *p*s < .05, bootstrapped *p* `r study2_aim3_results_list$Interaction_vio$boot_p`) (See Figure 2).
-A simple slopes analysis revealed that people with higher levels of violence exposure showed lower strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$vio_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.Flanker$p_sum`% of *p*s < .05), and showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$p_sum`% of *p*s < .05).
+There was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_vio$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_vio$CI`, `r study2_aim3_results_list$Interaction_vio$p_sum` % of *p*s \< .05, bootstrapped *p* `r study2_aim3_results_list$Interaction_vio$boot_p`) (See Figure 2).
+A simple slopes analysis revealed that people with higher levels of violence exposure showed lower strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$vio_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.Flanker$p_sum`% of *p*s \< .05), and showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$p_sum`% of *p*s \< .05).
 
 There was no significant main effect for unpredictability (bootstrapped *p* = `r study2_aim3_results_list$Task_unp$boot_p`).
-However, there was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_unp$CI`, `r study2_aim3_results_list$Interaction_unp$p_sum` % of *p*s < .05, bootstrapped *p* = `r study2_aim3_results_list$Interaction_unp$boot_p`).
-A simple slopes analysis revealed that people with higher levels of unpredictability did not differ in their strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$unp_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.Flanker$p_sum` % of *p*s < .05), but showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$p_sum`% of *p*s < .05).
+However, there was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_unp$CI`, `r study2_aim3_results_list$Interaction_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim3_results_list$Interaction_unp$boot_p`).
+A simple slopes analysis revealed that people with higher levels of unpredictability did not differ in their strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$unp_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.Flanker$p_sum` % of *p*s \< .05), but showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$p_sum`% of *p*s \< .05).
 
-```{r figure3, fig.height=9, fig.width = 7, fig.id = "figure3", fig.cap.style = "Figure Caption", fig.cap="Multiverse results for the within-subjects comparison of Flanker and Global-Local information processing.
+```{r}
+#| label: figure4
+#| fig.width: 7
+#| fig.height: 9
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure 4.** Multiverse results for the within-subjects comparison of Flanker and Global-Local information processing.
 Panel A depicts the multiverse interaction effects, with the thick black lines denoting the median slope and the thin lines denoting effects for each combination of arbitrary decisions.
-Blue lines indicate significant effects (*p* > .05), and grey lines indicate non-significant effects (*p* > .05).
-Panel B depicts sorted beta coefficients across each arbitrary decision.
-Panel C depicts the percentage of variance that each arbitrary decision explains in the standardized effect."}
+Blue thin lines indicate significant effects (*p* > .05), and grey thin lines indicate non-significant effects (*p* > .05).
+Panel B depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
+See the main text for more information about the multiverse analyses.
+knitr::include_graphics("figures/fig4.png")
+```
 
-knitr::include_graphics("figures/fig3.png")
-```
 <br>
@@
 The same processing style was observed for participants with more exposure to unpredictability, although they did not show lowered strength of perceptual input.
+
+# Exploratory analyses
+
+We hypothesized that the potential adaptive benefits of a more diffuse scope of attention in adverse conditions might be linked to the notion of a *present-oriented attention style* [@frankenhuis_2016; @vangelder_2023].
+People with a present-oriented attention style (versus a more future-oriented attention style) are more geared towards processing information that is relevant for solving challenges and obtaining rewards in the here-and-now.
+A general tendency to be more attuned to the present (while disregarding the future) is sometimes referred to as a short-term mindset [@kubel_2023; @vangelder_2023], which also includes tendencies to be more impulsive, to more steeply discount future rewards, and to be more sensation-seeking.
+Although short-term mindsets are associated with exposure to adversity [@ganschow_2023], it is unclear how they are associated with performance on attention tasks.
+We explored bivariate correlations between two indicators of short-term mindsets (impulsivity and future orientation) and SSP parameters of the Flanker (for more information on the measures, see section 1 of the supplemental materials).
+
+See Table SX for an overview of the correlations.
+Impulsivity was negatively associated with the strength of perceptual input (*r* = -.07, *p* = .004) and positively associated with interference (*r* = .09, *p* = .005). 
+In addition, impulsivity was also associated with a more holistic information processing style (*r* = .11, *p* = .020). 
+Thus, more impulsive participants processed information less deeply and were more easily drawn to distractions, but this might partly be explained by a holistic information processing style.
+Similarly, future-orientation was positively associated with perceptual input (*r* = .09 *p* < .001)—--but not with interference (*p* = .112) —--on the Flanker Task, and was also associated with a more detail-oriented processing style (*r* = -.12, *p* = .011).
+Thus, more future-oriented participants processed information more deeply, which might partly be explained by a detail-oriented processing style.
 
@@
 One (tentative) interpretation is that in the absence of threatening or otherwise salient information, people with more exposure to adversity attend to and process information in the environment globally and less deeply.
-They might only shift to local processing of a single source of information if it seems threatening or otherwise salient.
+They might only shift to local processing of a single source of information if it seems threatening or otherwise salient [@shields_2015; @schwabe_2013].
 This would be consistent with research showing that growing up in a disadvantaged environment decreases the efficiency of the brain's (resting-state) salience network, which is in turn associated with lower raw performance on certain cognitive tasks [@cermakova_2023; @gellci_2019; @hilger_2017; @yuan_2012].
@@
 Our study has three main strengths.
-First, each study included socioeconomically diverse participants.. 
+First, each study included socioeconomically diverse participants.
 Second, the DDM allowed us to decompose performance in a more nuanced way than is possible with (typically used) raw performance scores.
@@
 Indeed, our results were the least robust against participants who skipped the screen-scaling procedure (to ensure the stimuli were adequately sized) and interruptions during the tasks, which are factors that are largely out of our control.
-Second, we deviated from our preregistrations in a number of ways in all studies, due to progressive insight.
+Second, we deviated from our preregistrations in several ways in all studies, due to progressive insight.
+This decreased the severity of our statistical tests, and so this work would benefit from preregistered replications [@lakens_2023].
 
@@
 Exposure to adversity might shape these two types of inhibition in different ways.
-For example, studies find that acute stress impairs performance on tasks of cognitive inhibition (of which the Flanker is an example) and enhances performance on tasks of response inhibition [for a meta-analysis, see @shields_2017].
+For example, acute stress might impair performance on tasks of cognitive inhibition (of which the Flanker is an example) and enhances performance on tasks of response inhibition [for a meta-analysis, see @shields_2016; but see @dang_2017].
 Future work could assess inhibition more broadly, e.g., by including tasks that are hypothesized to require cognitive or response inhibition.
@@
 
-We found that people with more childhood adversity exposure perform worse on the Flanker not because of an impairment in their ability to inhibit distracting information, but as a result of lower strength of perceptual input.
+We found that people with more childhood adversity exposure perform worse on the Flanker not because of an impairment in their ability to inhibit distracting information, but because of lower strength of perceptual input.
 Our results suggest that people with more adversity exposure are not worse at inhibiting distractions; rather, they do not seem to process information in the environment deeply unless it proves to be a reliable and important source of information.

### 2024-03-26 manuscript/create_ssp_viz.R

@@ -1,60 +1,0 @@
-library(bayestestR)  
-library(ggforce)
-library(ggtext)
-library(bruceR)
-
-
-ssp_plot_data1 <- distribution_normal(n = 1000, mean = 0, sd = 1.5)
-
-ssp_plot_data1 %>% 
-  density() %>%  
-  as.data.frame() %>% 
-  ggplot(aes(x=x, y=y)) +
-  geom_line(linewidth = 1) +
-  geom_segment(aes(x = -4, xend = -4, y = 0, yend = 0.008), linetype = "longdash") +
-  geom_segment(aes(x = 4, xend = 4, y = 0, yend = 0.008), linetype = "longdash") +
-  geom_segment(aes(x = -2, xend = -2, y = 0, yend = 0.11), linetype = "longdash") +
-  geom_segment(aes(x = 2, xend = 2, y = 0, yend = 0.11), linetype = "longdash") +
-  geom_segment(aes(x = 0, xend = 0, y = 0, yend = 0.26), linetype = "longdash") +
-  scale_x_continuous(breaks = c(-4,-2,0,2,4), labels=c("\u2190<br>|<br>*p*","\u2190<br>|<br>*p*","\u2192<br>|<br>*p*","\u2190<br>|<br>*p*","\u2190<br>|<br>*p*")) +
-  theme(
-    panel.background = element_rect(fill='transparent'),
-    plot.background = element_rect(fill='transparent', color=NA),
-    axis.text.x = element_markdown(color = 'black', size = 25),
-    axis.title = element_blank(),
-    axis.text.y = element_blank(),
-    axis.line.y = element_blank(),
-    axis.ticks = element_blank()
-  ) +
-  labs(
-    y = ""
-  ) 
-  
-
-
-ssp_plot_data2 <- distribution_normal(n = 1000, mean = 0, sd = 1)
-
-ssp_plot_data2 %>% 
-  density() %>%  
-  as.data.frame() %>% 
-  ggplot(aes(x=x, y=y)) +
-  geom_line(linewidth = 1) +
-  geom_segment(aes(x = -2, xend = -2, y = 0, yend = 0.06), linetype = "longdash") +
-  geom_segment(aes(x = 2, xend = 2, y = 0, yend = 0.06), linetype = "longdash") +
-  geom_segment(aes(x = 0, xend = 0, y = 0, yend = 0.39), linetype = "longdash") +
[…]

### 2024-03-26 manuscript/pilot_stage_objects.R

@@ -1,713 +1,0 @@
-library(tidyverse)
-library(patchwork)
-library(ggsci)
-library(here)
-library(flextable)
-
-
-source(here("preregistrations/1_pilot/scripts/custom_functions/functions_corrplot.R"))
-
-
-cleaned_data = read_csv(here("data/1_pilot/2_cleaned_data.csv"))
-pilot_data <- cleaned_data # for easy referencing in the manuscript
-load(file = here("preregistrations/1_pilot/analysis_objects/primary_mult_summaries.RData"))
-load(file = here("preregistrations/1_pilot/analysis_objects/exploratory_mult_summaries.RData"))
-
-get_alphas <- function(data, string) {
-  (data |> 
-     select(matches(string)) |> 
-     psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
-}
-
-
-
-# Descriptives ------------------------------------------------------------
-
-## IV distributions ----
-txt_ivs_dist_pilot <- 
-  cleaned_data |> select(matches("(mean|total|composite|edu_parents_recoded|age)$"),
-                         matches("^(acc|rt)_(flanker|cueing)"), acc_change, rt_change) |> 
-  map(function(x) {
-    list(
-      mean = round(mean(x, na.rm = T),2),
-      sd   = round(sd(x, na.rm = T),2)
-    )
-  })
-
-txt_ivs_alpha_pilot <- 
-  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
-    "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
-    "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
-    "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
-  map(function(x) {
-    (cleaned_data |> 
-       select(matches(x)) |> 
-       psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
-  }) |> 
-  setNames(c("stai_s", "violence", "unp", 
-             "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
[…]

### 2024-03-26 manuscript/pooled_stage_objects.R

@@ -1,312 +1,0 @@
-library(tidyverse)
-library(here)
-library(ggsci)
-library(patchwork)
-library(flextable)
-library(specr)
-
-source(here("preregistrations/1_pilot/scripts/custom_functions/functions_corrplot.R"))
-
-source(here("manuscript/pilot_stage_objects.R"))
-source(here("manuscript/study1_stage_objects.R"))
-source(here("manuscript/study2_stage_objects.R"))
-
-pilot_data = read_csv(here("data/1_pilot/2_cleaned_data.csv")) |> mutate(study = "pilot")
-study1_data = read_csv(here("data/2_study1/2_cleaned_data.csv")) |> mutate(study = "study1")
-study2_data = read_csv(here("data/3_study2/2_cleaned_data.csv")) |> mutate(study = "study2")
-# IV correlations ---------------------------------------------------------
-
-iv_cor_pooled_table <-  bind_rows(
-    pilot_data |> 
-      mutate(id = paste0("pilot", id)) |> 
-      rename(
-        pcunp_mean   = unp_mean,
-        nvs_mean     = violence_mean
-      ),
-    study1_data |> 
-      mutate(id = paste0("study1", id)),
-    study2_data |> 
-      mutate(id = paste0("study2", id)) |> select(-weight)
-  ) |> 
-select(nvs_mean, fighting_mean, vio_comp, 
-       quic_total_mean, pcunp_mean, chaos_mean, change_env_mean, unp_obj_comp, unp_subj_comp, unp_comp) |> 
-  corr_table(
-    numbered = T,
-    sample_size = F,
-    c.names = c("Neigh. violence", "Fighting", "Violence comp.", 
-                "QUIC", "Perc. unpredictability", "CHAOS", "Env. change", "Obj. unpredictability", "Subj. Unpredictability", "Unpredictability comp."),
-    stats = c("mean", "sd", "median", "min", "max", "skew", "kurtosis")
-  ) |> 
-  add_column(empty1 = "", .after = 4) |> 
-  mutate(across(
-    everything(),
-    ~ifelse(is.na(.), "", .)
-  )) |> 
-  mutate(across(
-    everything(),
-    ~formatC(.,  digits = 2, width = 3, flag = "0", format = 'f'))) |> 
-  flextable() |> 
-  width("empty1", width = .2) |> 
-  width(j = 1, width = .75) |> 
-  set_header_labels(Variable = "", empty1 = "") |> 
[…]

### 2024-03-26 manuscript/study1_stage_objects.R

@@ -1,1801 +1,0 @@
-library(tidyverse)
-library(here)
-library(ggsci)
-library(patchwork)
-library(flextable)
-library(specr)
-
-
-cleaned_data = read_csv(here("data/2_study1/2_cleaned_data.csv"))
-study1_data <- cleaned_data
-load(file = here("preregistrations/2_study1/analysis_objects/primary_multiverse_summaries.RData"))
-load(file = here("preregistrations/2_study1/analysis_objects/exploratory_multiverse_summaries.RData"))
-load(file = here("preregistrations/2_study1/analysis_objects/study1_bootstrap_pvalues.RData"))
-
-get_alphas <- function(data, string) {
-  (data |> 
-     select(matches(string)) |> 
-     psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
-}
-
-
-
-
-# Descriptives ------------------------------------------------------------
-
-## IV distributions ----
-txt_ivs_dist_study1 <- 
-  cleaned_data |> select(matches("(mean|total|composite|edu_parents_recoded)$")) |> 
-  map(function(x) {
-    list(
-      mean = round(mean(x, na.rm = T),2),
-      sd   = round(sd(x, na.rm = T),2)
-    )
-  })
-
-txt_ivs_alpha_study1 <- 
-  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
-    "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
-    "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
-    "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
-  map(function(x) {
-    (cleaned_data |> 
-       select(matches(x)) |> 
-       psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
-  }) |> 
-  setNames(c("stai_s", "violence", "unp", 
-             "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
[…]

### 2024-03-26 manuscript/study2_stage_objects.R

@@ -1,1117 +1,0 @@
-library(tidyverse)
-library(here)
-library(ggsci)
-library(patchwork)
-library(flextable)
-library(specr)
-
-
-cleaned_data = read_csv(here("data/3_study2/2_cleaned_data.csv"))
-study2_data <- cleaned_data
-load(file = here("preregistrations/3_study2/analysis_objects/primary_multiverse_summaries.RData"))
-load(file = here('preregistrations/3_study2/analysis_objects/study2_bootstrap_pvalues.RData'))
-
-get_alphas <- function(data, string) {
-  (data |> 
-     select(matches(string)) |> 
-     psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
-}
-
-
-
-
-# Descriptives ------------------------------------------------------------
-
-## IV distributions ----
-txt_ivs_dist_study2 <- 
-  cleaned_data |> select(matches("(mean|total|composite|edu_parents_recoded)$")) |> 
-  map(function(x) {
-    list(
-      mean = round(mean(x, na.rm = T),2),
-      sd   = round(sd(x, na.rm = T),2)
-    )
-  })
-
-txt_ivs_alpha_study2 <- 
-  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
-    "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
-    "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
-    "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
-  map(function(x) {
-    (cleaned_data |> 
-       select(matches(x)) |> 
-       psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
-  }) |> 
-  setNames(c("stai_s", "violence", "unp", 
-             "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
-             "quic_total", "chaos", "ses", "impuls", "fos_pa", "fos_tp", "fos_fc", "fos_fo", "depression"))
-
-
-## Sample characteristics ----
-
[…]

### 2024-03-26 supplement/supplements.qmd
full version of supplemental materials

@@
 ---
-title: "Supplements"
-format: html
-editor: visual
+bibliography: ../manuscript/references.bib
+csl: ../manuscript/apa.csl
+format: 
+  docx:
+    reference-doc: ../manuscript/reference-doc.docx
+    toc: true
+    toc-location: left
+    toc-title: Table of Contents
+output:
+  officedown::rdocx_document:
+    page_margins:
+      bottom: 1
+      footer: 0
+      gutter: 0
+      header: 0.5
+      left: 1
+      right: 1
+      top: 1
+    plots:
+      align: center
+      caption:
+        pre: 'Figure '
+        sep: '. '
+        style: Image Caption
+    tables:
+      caption:
+        pre: 'Table '
+        sep: '. '
+        style: Table Caption
+  pdf_document: default
+  word_document: default
+editor: 
+  markdown: 
+    wrap: sentence
 ---
-
 ```{r include=FALSE}
@@
 load("../data/1_pilot/mod_fit_flanker.RData")
+load("../data/2_study1/ssp_fit.RData")
 load("../data/3_study2/ssp_fit.RData")
+load("../preregistrations/1_pilot/analysis_objects/DDM_objects.Rdata")
+load("../preregistrations/1_pilot/analysis_objects/hddm_recovery_plots.RData")
 
-source("../manuscript/pilot_stage_objects.R") # Staged results of the pilot study
+load("../manuscript/pilot_staged_results.RData")
+load("../manuscript/study1_staged_results.RData")
+load("../manuscript/study2_staged_results.RData")
+load("../manuscript/pooled_staged_results.RData")
 
 library(flextable)
+library(tidyverse)
+library(patchwork)
 
@@
 )
+
+knitr::opts_chunk$set(
+  echo = F,
+  fig.align = "center",
+  fig.pos = "!t", 
+  out.extra = "",
+  fig.show = "asis",
+  message = FALSE,
+  tab.topcaption = T,
+  warning = FALSE
+)
 ```
@@
 
-The following exploratory measures were collected in all three studies
+The exploratory measures described in section 1.1 - 1.5 were collected in all three studies.
+The exploratory measure described in section 1.6 was collected on Study 2 only.
+
+The following exploratory measures were collected in all three studies.
 
@@
 
+## 1.6. Attentional style
+
+We measured attentional style using the Attentional Style Questionnaire [ASQ\; @calster_2018] (See [Table S7](#appendix).
+The ASQ measures self-reported attentional style, with seven items asking about the participant's propensity for internally oriented attention (e.g., "During an activity, unrelated mmental images and thoughts come to my mind") and seven items about externally oriented attention (e.g., "I am easily drawn to new stimuli (for example, voices of people passing by, as sound in the house, ...) that are not relevant to a task I am doing").
+Where necessary, items were recoded in such a way that they reflected *distractibility* by internal and external stimuli, respectively, with higher scores reflecting a higher degree of distractibility.
+We computed unweighted averages separately for internally oriented attention and externally oriented attention.
+
 # Section 2. Exploratory analyses
@@
 
-The EFA yielded five factors based on parallel analysis (see Table SX).
+The EFA yielded five factors based on parallel analysis (see Table S1).
 Based on their contents, we labelled these factors (1) Daily unpredictability; (2) Household routine; (3) Spatial unpredictability; (4) Chaos/clutter; (5) Social unpredictability.
@@
 ```{r}
+#| tab.id: tableS1
+#| results: markup
 pilot_efa_table 
@@
 ```{r}
+#| label: figureS1
+#| dpi: 600
+#| fig.width: 7
+#| fig.height: 7
+#| fig-cap: | 
+#|   **Figure S1.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
 study1_efa_fig 
@@
 
-Table SX shows bivariate correlations between self-reported depression, impulsivity, future orientation, and SES with each of the Flanker SSP parameters and the Global-Local drift rate difference.
+Table S2 shows bivariate correlations between self-reported depression, impulsivity, future orientation, and SES with each of the Flanker SSP parameters and the Global-Local drift rate difference.
 Participants who reported more depressive symptoms had a lower strength of perceptual input.
@@
 ```{r}
-supp_cor_table
+#| tab.id: tableS3
+#| results: markup
+supp_cor_table |> 
+  autofit()
 ```
 
-# Section 3. Deviations from preregistrations
+# Section 3. Model fit
 
@@
 
-## 3.2. Study 1
-
-## 3.3. Study 2
-
-# Section 4. Model fit
-
-## 4.1. Pilot
-
-## 4.1.1 Cueing and Change Detection Task
+## 3.1.1 Cueing and Change Detection Task
 
@@
 ```{r}
+#| label: figureS2
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S2.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
 cueing_DDM_results_mod9 |> 
@@
   pivot_longer(everything(), names_to = "parameter", values_to = "Estimate") |> 
-  ggplot(aes(value)) +
+  ggplot(aes(Estimate)) +
   geom_histogram() +
-  facet_wrap(~parameter, scales = 'free')
+  facet_wrap(~parameter, scales = 'free') +
+  theme_classic()
 ```
@@
 
-Model convergence was assessed (1) by visually inspecting the traces, which should not contain any drifts or large jumps; (2) through simulation.
+Model convergence was assessed (1) by visually inspecting the traces, which should not contain any drifts or large jumps (see Figure SX and SX); (2) through simulation.
 Specifically, we used each participant's DDM estimates to simulate 100 RT and accuracy estimates (per condition).
-The distributions of the participant's true RTs and their simulated RTs were assessed through bivariate correlations at the 25th, 50th and 75th percentile.
-We made the same comparison for mean accuracy levels.
+The distributions of the participant's true RTs and their simulated RTs were assessed through bivariate correlations at the 25th, 50th and 75th percentile (See Figure SX and SX).
+We made the same comparison for mean accuracy levels (See Figure SX and SX).
 
-## 4.1.2 Flanker
+<br>
+
+```{r}
+#| label: figureS3
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S3.
+** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+pilot_traces_cueing
+```
+
+<br>
+
+```{r}
+#| label: figureS4
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S4.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+pilot_recov_rt_cueing
+```
+
+<br>
+
+```{r}
+#| label: figureS5
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S5.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+pilot_recov_acc_cueing
+```
+
+<br>
+
+```{r}
+#| label: figureS6
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S6.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+pilot_traces_change
+```
+
+<br>
+
+```{r}
+#| label: figureS7
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S7.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+pilot_recov_rt_change
+```
+
+<br>
+
+```{r}
+#| label: figureS8
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S8.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+pilot_recov_rt_cueing
+```
+
+<br>
+
+## 3.1.2 Flanker
 
@@
 ```{r}
+#| label: figureS9
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S9.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
 qq_data_flanker <- left_join(predicted_quantiles_flanker, observed_quantiles_flanker)
@@
   theme_classic()
+
+qq_flanker_rt
 ```
@@
 ```{r}
+#| label: figureS10
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S10.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
 qq_flanker_acc <- ggplot(qq_data_flanker) +
@@
 
-## 4.2. Study 1
+## 3.2. Study 1
 
@@
 ```{r}
+#| label: figureS11
+#| dpi: 600
+#| fig.width: 7
+#| fig.height: 7
+#| fig-cap: | 
+#|   **Figure S11.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
 study1_ssp_fit_rt
@@
 ```{r}
+#| label: figureS12
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S12.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
 study1_ssp_fit_acc
@@
 
-## 4.3. Study 2
+## 3.3. Study 2
 
-### 4.3.1 Flanker
+### 3.3.1 Flanker
 
@@
 ```{r}
+#| label: figureS13
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S13.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
 study2_ssp_fit_rt
@@
 ```{r}
+#| label: figureS14
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S14.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
 study2_ssp_fit_acc
@@
 
-### 4.3.2 Global-Local Task
+### 3.3.2 Global-Local Task
+
+# Section 4. Deviations from preregistrations
+
+In this section, we provide a numbered overview of the deviations from the preregistration in each study.
+
+## 4.1. Pilot
+
+1. *DDM estimation using Hierarchical Bayesian DDM instead of Maximum Likelihood estimation.* The rational for this change is explained in more detail in section 3.1.1.
+
+2.
+*Focus on Flanker Interference instead of separate attention parameters.* The SSP model provides two parameters representing attentional processes: (1) the initial attention width, and (2) the rate at which attention shrinks towards the central target.
+We had initially planned to analyze both parameters separately.
+However, after analyzing the data from Study 1, we realized that the estimates of these two parameters separately were very unstable.
+We noticed this when plotting the within-person estimates between conditions (standard, enhanced, and degraded) against each other.
+Figure SX provides an overview of these correlations for attentional width, shrinking rate, interference, and, for illustrative purposes, the RT difference score.
+We consider the comparison between the standard and enhanced condition the most informative, as the stimuli in these conditions were most similar.
+The within-person correlations between conditions of attentional width and shrinking were very low.
+However, the correlations were substantially higher for interference (which even outperformed the standard RT difference scores, as typically used in traditional assessments).
+Thus, we decided to use the Interference estimate in our analyses across all studies.
+
+```{r}
+#| label: figureS15
+#| fig-width: 7
+#| fig-height: 8
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S15. **Within-person bivarate correlations between Flanker conditions in Study 2 for RT differences, attentional width, shrinking rate, and interference.
+study1_ssp_cor_plot
+```
+
+3.
+
+## 4.2. Study 1
+
+1.
+In our preregistration of Study 1, we preregistered four exploratory (hypothesis-generating) aims, which were unrelated to the primary (hypothesis-driven) aims described in the main manuscript.
+These were: (1) Investigating the factor structure of unpredictability measures and comparing it to the structure found in the Pilot; (2) Exploring the role of state anxiety, hunger, and sleep deprivation as potential moderators of the relationship between adversity and attention performance; (3) Exploring bivariate correlations between measures of adversity, attention, and measures of temporal orientation; (4) Explore the correlation between current depressive symptoms and retrospective measures of adversity.
+The results of aim 1 are described in Section 2.1.2.
+The
+
+## 4.3. Study 2
+
+2.
+*Global-Local performance.* In the original preregistration, we specified that we would exclude participants who performed at chance on either the Flanker Task or the Global-Local Task, which was defined as an accuracy of 59.4% or lower.
+However, initial inspections of the Global-Local Task data showed that a substantial part of the sample did not reach this cut-off, suggesting that the task was more difficult than anticipated.
+Thus, we developed a more fine-grained approach (described below) in an attempt to distinguish between 1) participants who did not understand the task and 2) participants who understood the task, but found it difficult to perform well.
+Given the assumptions of DDM, the first group would have to be excluded because they likely did not go through a process of information accumulation.
+However, the model should be able to adequately fit the data of the second group.
+
+The amended analysis approach for the Global-Local Task looked as follows: (1) Fit the data to the cleaned data of the full sample, including participants who performed at or below chance level (i.e., after trial-level exclusions but before case-wise exclusions); (2) Based on recovered parameter estimates for each participant, simulate the same number of trials (reaction times and accuracy) using the `RWiener` package, separately for Global and Local trials.
+(3) For each participant, calculate the 25th, 50th and 75th quantile of both their real RTs and the simulated RTs.
+In addition, we calculate mean accuracies based on the real and simulated data. (4) Compute standardized residuals between the real and simulated data for RTs at each quantile and for accuracy.
+In case of good fit, the residual should be close to zero. (5) Exclude the data of participants with any standardized residual > 3.2 SD.
+
+3.
+*Multiverse analysis.* In the preregistration, we planned to include three variables as covariates that were previously featured as arbitrary exclusion decisions in the multiverse specification: 1) whether or not participants rescaled the screen; 2) whether or not participants exited fullscreen mode at some point during the tasks; 3) Whether or not participants experienced interruptions during the tasks.
+Our reasoning was that these three factors were consistently found to have a large impact on model results.
+However, we realized later on that adding these factors as covariates was not a good approach from a causal inference standpoint.
+That is, it is more likely that each of these factors added random noise to our estimates than that they had a causal effect on the outcome.
+Therefore, we decided instead to include these factors as arbitrary decisions in the multiverse analyses, similarly as the previous two studies.
+This allowed for a coherent assessment of influential factors across all three experiments.
 
 # Section 5. Multiverse analysis.
+
+In this section, we provide additional results of the multiverse analyses.
+Specifically, we report (1) the distributions of *p*-values across the multiverses and (2) influential data cleaning decisions.
+
+## 5.1. Pilot
+
+Figure XX and Figure XX present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 3 in the main text.
+
+```{r}
+#| label: figureS16
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S16.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+Panel A: Cued Attention Task.
+Panel B: Change Detection Task.
+Panel C: Flanker Task.
+(
+  (pilot_prim_lmer_pvalues_plot$cueing_rt + labs(title = "Raw response time", tag = "A", y = "") + theme_classic()) + 
+    (pilot_prim_lmer_pvalues_plot$cueing_hddm_v + labs(title = "Drift rate", y = "") + theme_classic()) + 
+    (pilot_prim_lm_pvalues_plot$cueing_fixed_hddm_a + labs(title = "Boundary separation", y = "") + theme_classic()) + 
+    (pilot_prim_lmer_pvalues_plot$cueing_hddm_t + labs(title = "Non-decision time", y = "") + theme_classic())
+) /
+  (
+    (pilot_prim_lm_pvalues_plot$rt_change + labs(title = "Raw response time", tag = "B", y = "") + theme_classic()) + 
+      (pilot_prim_lm_pvalues_plot$change_hddm_v + labs(title = "Drift rate", y = "") + theme_classic()) + 
+      (pilot_prim_lm_pvalues_plot$change_hddm_a + labs(title = "Boundary separation", y = "") + theme_classic()) + 
+      (pilot_prim_lm_pvalues_plot$change_hddm_t + labs(title = "Non-decision time", y = "") + theme_classic())
+  ) /
+  (
+    (pilot_prim_lmer_pvalues_plot$flanker_rt + labs(title = "Raw response time", tag = "C", y = "") + theme_classic()) + 
+      (pilot_prim_lm_pvalues_plot$flanker_ssp_p + labs(title = "Perceptual input", y = "") + theme_classic()) + 
+      (pilot_prim_lm_pvalues_plot$flanker_ssp_interference + labs(title = "Interference", y = "") + theme_classic()) + 
+      (pilot_prim_lm_pvalues_plot$flanker_ssp_a + labs(title = "Boundary separation", y = "") + theme_classic()) +
+      (pilot_prim_lm_pvalues_plot$flanker_ssp_t + labs(title = "Non-decision time", y = "") + theme_classic())
+  ) 
+```
+
+```{r}
+#| include: false
+#| echo: false
+f17_p1 <- pilot_prim_lmer_variance_plot$cueing_rt + labs(title = "Raw response time", tag = "A", y = "", fill = "")
+f17_p2 <- pilot_prim_lmer_variance_plot$cueing_hddm_v + labs(title = "Drift rate", y = "") + guides(fill = "none")
+f17_p3 <- pilot_prim_lm_variance_plot$cueing_fixed_hddm_a + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f17_p4 <- pilot_prim_lmer_variance_plot$cueing_hddm_t + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+
+f17_p5 <- pilot_prim_lm_variance_plot$rt_change + labs(title = "Raw response time", tag = "B", y = "") + guides(fill = "none") 
+f17_p6 <- pilot_prim_lm_variance_plot$change_hddm_v + labs(title = "Drift rate", y = "") + guides(fill = "none") 
+f17_p7 <- pilot_prim_lm_variance_plot$change_hddm_a + labs(title = "Boundary separation", y = "") + guides(fill = "none")
+f17_p8 <- pilot_prim_lm_variance_plot$change_hddm_t + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+
+f17_p9 <- pilot_prim_lmer_variance_plot$flanker_rt + labs(title = "Raw response time", tag = "C", y = "") + guides(fill = "none")
+f17_p10 <- pilot_prim_lm_variance_plot$flanker_ssp_p + labs(title = "Perceptual input", y = "") + guides(fill = "none") 
+f17_p11 <- pilot_prim_lm_variance_plot$flanker_ssp_interference + labs(title = "Interference", y = "") + guides(fill = "none") 
+f17_p12 <- pilot_prim_lm_variance_plot$flanker_ssp_a + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f17_p13 <- pilot_prim_lm_variance_plot$flanker_ssp_t + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+
+align_patches(f17_p1,f17_p2,f17_p3,f17_p4,f17_p5,f17_p6,f17_p7,f17_p8,f17_p9,f17_p10,f17_p11,f17_p12,f17_p13)
+```
+
+```{r}
+#| label: figureS17
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S17.** Multiverse explained variance of each data cleaning decision belonging to the analyses reported in Table 3 in the main text.
+Panel A: Cued Attention Task.
+Panel B: Change Detection Task.
+Panel C: Flanker Task.
+final_plot_S17 <- 
+  (f17_p1+f17_p2+f17_p3+f17_p4 + plot_layout(ncol = 3)) /
+  (f17_p5+f17_p6+f17_p7+f17_p8 + plot_layout(ncol = 3)) /
+  (f17_p9+f17_p10+f17_p11+f17_p12+f17_p13 + plot_layout(ncol = 3)) + 
+  plot_layout(guides = "collect") & theme(legend.position='bottom')
+
+final_plot_S17
+
+```
+
+## 5.2 Study 1
+
+Figure XX and Figure XX present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 4 in the main text.
+
+```{r}
+#| label: figureS18
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S18.** Multiverse p-value distributions belonging to the analyses reported in Table 4 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+Panel A: Analyses involving violence exposure (hypothesis-driven).
+Panel B: Analyses involving unpredictability (exploratory).
+(
+  (study1_prim_ssp_pvalues_plot_study1$rt_diff + labs(title = "RT difference", tag = "A", y = "") + theme_classic()) + 
+    (study1_prim_ssp_pvalues_plot_study1$p_flanker + labs(title = "Perceptual input", y = "") + theme_classic()) + 
+    (study1_prim_ssp_pvalues_plot_study1$interference_flanker + labs(title = "Interference", y = "") + theme_classic()) + 
+    (study1_prim_ssp_pvalues_plot_study1$a_flanker + labs(title = "Boundary separation", y = "") + theme_classic()) +
+    (study1_prim_ssp_pvalues_plot_study1$t0_flanker + labs(title = "Non-decision time", y = "") + theme_classic())
+) /
+  (
+    (study1_expl_ssp_pvalues_plot_study1$rt_diff + labs(title = "RT difference", tag = "B", y = "") + theme_classic()) + 
+      (study1_expl_ssp_pvalues_plot_study1$p_flanker + labs(title = "Perceptual input", y = "") + theme_classic()) + 
+      (study1_expl_ssp_pvalues_plot_study1$interference_flanker + labs(title = "Interference", y = "") + theme_classic()) + 
+      (study1_expl_ssp_pvalues_plot_study1$a_flanker + labs(title = "Boundary separation", y = "") + theme_classic()) +
+      (study1_expl_ssp_pvalues_plot_study1$t0_flanker + labs(title = "Non-decision time", y = "") + theme_classic())
+  )
+```
+
+```{r}
+#| include: false
+#| echo: false
+f19_p1 <- study1_prim_ssp_variance_plot_study1$rt_diff + labs(title = "RT difference", tag = "A", y = "", fill = "")
+f19_p2 <- study1_prim_ssp_variance_plot_study1$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none") 
+f19_p3 <- study1_prim_ssp_variance_plot_study1$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
+f19_p4 <- study1_prim_ssp_variance_plot_study1$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f19_p5 <- study1_prim_ssp_variance_plot_study1$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+
+f19_p6 <- study1_expl_ssp_variance_plot_study1$rt_diff + labs(title = "RT difference", tag = "B", y = "") + guides(fill = "none") 
+f19_p7 <- study1_expl_ssp_variance_plot_study1$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
+f19_p8 <- study1_expl_ssp_variance_plot_study1$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none")
+f19_p9 <- study1_expl_ssp_variance_plot_study1$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f19_p10 <- study1_expl_ssp_variance_plot_study1$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+
+align_patches(f19_p1,f19_p2,f19_p3,f19_p4,f19_p5,f19_p6,f19_p7,f19_p8,f19_p9,f19_p10)
+```
+
+```{r}
+#| label: figureS19
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S19.** Multiverse explained variance of each data cleaning decision belonging to the analyses reported in Table 4 in the main text.
+Panel A: Analyses involving violence exposure (hypothesis-driven).
+Panel B: Analyses involving unpredictability (exploratory).
+final_plot_S19 <- 
+  (f19_p1+f19_p2+f19_p3+f19_p4+f19_p5 + plot_layout(ncol = 3)) /
+  (f19_p6+f19_p7+f19_p8+f19_p9+f19_p10 + plot_layout(ncol = 3)) +
+  plot_layout(guides = "collect") & theme(legend.position='bottom')
+
+final_plot_S19
+
+```
+
+```{r}
+#| label: figureS20
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S20.** Multiverse p-value distributions belonging to the interaction effects involving violence exposure reported in Table 5 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+Panel A: Analyses comparing the enhanced condition to the standard condition.
+Panel B: Analyses comparing the degraded condition to the standard condition.
+(
+  (study1_prim_ssp_enh_pvalues_plot$rt_diff + labs(title = "RT difference", tag = "A", x = "p", y = "") + theme_classic()) + 
+    (study1_prim_ssp_enh_pvalues_plot$p_flanker + labs(title = "Perceptual input", x = "p", y = "") + theme_classic()) + 
+    (study1_prim_ssp_enh_pvalues_plot$interference_flanker + labs(title = "Interference", x = "p", y = "") + theme_classic()) + 
+    (study1_prim_ssp_enh_pvalues_plot$a_flanker + labs(title = "Boundary separation", x = "p", y = "") + theme_classic()) +
+    (study1_prim_ssp_enh_pvalues_plot$t0_flanker + labs(title = "Non-decision time", x = "p", y = "") + theme_classic())
+) /
+  (
+    (study1_prim_ssp_deg_pvalues_plot$rt_diff + labs(title = "RT difference", tag = "B", x = "p", y = "") + theme_classic()) + 
+    (study1_prim_ssp_deg_pvalues_plot$p_flanker + labs(title = "Perceptual input", x = "p", y = "") + theme_classic()) + 
+    (study1_prim_ssp_deg_pvalues_plot$interference_flanker + labs(title = "Interference", x = "p", y = "") + theme_classic()) + 
+    (study1_prim_ssp_deg_pvalues_plot$a_flanker + labs(title = "Boundary separation", x = "p", y = "") + theme_classic()) +
+    (study1_prim_ssp_deg_pvalues_plot$t0_flanker + labs(title = "Non-decision time", x = "p", y = "") + theme_classic())
+  )
+```
+
+```{r}
+#| include: false
+#| echo: false
+f21_p1 <- study1_prim_ssp_enh_variance_plot$rt_diff + labs(title = "RT difference", tag = "A", y = "", fill = "")
+f21_p2 <- study1_prim_ssp_enh_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none") 
+f21_p3 <- study1_prim_ssp_enh_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
+f21_p4 <- study1_prim_ssp_enh_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f21_p5 <- study1_prim_ssp_enh_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+
+f21_p6 <- study1_prim_ssp_deg_variance_plot$rt_diff + labs(title = "RT difference", tag = "B", y = "") + guides(fill = "none") 
+f21_p7 <- study1_prim_ssp_deg_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
+f21_p8 <- study1_prim_ssp_deg_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
+f21_p9 <- study1_prim_ssp_deg_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f21_p10 <- study1_prim_ssp_deg_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+
+align_patches(f21_p1,f21_p2,f21_p3,f21_p4,f21_p5,f21_p6,f21_p7,f21_p8,f21_p9,f21_p10)
+```
+
+```{r}
+#| label: figureS21
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S21.** Multiverse explained variance of each data cleaning decision belonging to the interaction effects involving violence exposure reported in Table 5 in the main text.
+Panel A: Analyses comparing the enhanced condition to the standard condition.
+Panel B: Analyses comparing the degraded condition to the standard condition.
+final_plot_S21 <- 
+  (f21_p1+f21_p2+f21_p3+f21_p4+f21_p5 + plot_layout(ncol = 3)) /
+  (f21_p6+f21_p7+f21_p8+f21_p9+f21_p10 + plot_layout(ncol = 3)) /
+  plot_layout(guides = "collect") & theme(legend.position='bottom')
+
+final_plot_S21
+
+```
+
+```{r}
+#| label: figureS22
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S22.** Multiverse p-value distributions belonging to the interaction effects involving unpredictability reported in Table 5 in the main text.
+The dashed vertical line depicts the cut-off of .05.
+The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+Panel A: Analyses comparing the enhanced condition to the standard condition.
+Panel B: Analyses comparing the degraded condition to the standard condition.
+(
+  (study1_expl_ssp_enh_pvalues_plot$rt_diff + labs(title = "RT difference", tag = "A", x = "p", y = "")) + theme_classic() + 
+    (study1_expl_ssp_enh_pvalues_plot$p_flanker + labs(title = "Perceptual input", x = "p", y = "") + theme_classic()) + 
+    (study1_expl_ssp_enh_pvalues_plot$interference_flanker + labs(title = "Interference", x = "p", y = "") + theme_classic()) + 
+    (study1_expl_ssp_enh_pvalues_plot$a_flanker + labs(title = "Boundary separation", x = "p", y = "") + theme_classic()) +
+    (study1_expl_ssp_enh_pvalues_plot$t0_flanker + labs(title = "Non-decision time", x = "p", y = "") + theme_classic())
+) /
+  (
+    (study1_expl_ssp_deg_pvalues_plot$rt_diff + labs(title = "RT difference", tag = "B", x = "p", y = "") + theme_classic()) + 
+    (study1_expl_ssp_deg_pvalues_plot$p_flanker + labs(title = "Perceptual input", x = "p", y = "") + theme_classic()) + 
+    (study1_expl_ssp_deg_pvalues_plot$interference_flanker + labs(title = "Interference", x = "p", y = "") + theme_classic()) + 
+    (study1_expl_ssp_deg_pvalues_plot$a_flanker + labs(title = "Boundary separation", x = "p", y = "") + theme_classic()) +
+    (study1_expl_ssp_deg_pvalues_plot$t0_flanker + labs(title = "Non-decision time", x = "p", y = "") + theme_classic())
+  )
+```
+
+```{r}
+#| include: false
+#| echo: false
+f23_p1 <- study1_expl_ssp_enh_variance_plot$rt_diff + labs(title = "RT difference", tag = "A", y = "", fill = "") 
+f23_p2 <- study1_expl_ssp_enh_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
+f23_p3 <- study1_expl_ssp_enh_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none")
+f23_p4 <- study1_expl_ssp_enh_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none")
+f23_p5 <- study1_expl_ssp_enh_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+
+f23_p6 <- study1_expl_ssp_deg_variance_plot$rt_diff + labs(title = "RT difference", tag = "B", y = "") + guides(fill = "none") 
+f23_p7 <- study1_expl_ssp_deg_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
+f23_p8 <- study1_expl_ssp_deg_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
+f23_p9 <- study1_expl_ssp_deg_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f23_p10 <- study1_expl_ssp_deg_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+
+align_patches(f23_p1,f23_p2,f23_p3,f23_p4,f23_p5,f23_p6,f23_p7,f23_p8,f23_p9,f23_p10)
+```
+
+```{r}
+#| label: figureS23
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S23.** Multiverse explained variance of each data cleaning decision belonging to the interaction effects involving unpredictability reported in Table 5 in the main text.
+Panel A: Analyses comparing the enhanced condition to the standard condition.
+Panel B: Analyses comparing the degraded condition to the standard condition.
+final_plot_S23 <- 
+  (f23_p1+f23_p2+f23_p3+f23_p4+f23_p5 + plot_layout(ncol = 3)) /
+  (f23_p6+f23_p7+f23_p8+f23_p9+f23_p10 + plot_layout(ncol = 3)) /
+  plot_layout(guides = "collect") & theme(legend.position='bottom')
+
+final_plot_S23
+
+```
+
+## 5.3 Study 2
+
+```{r}
+#| label: figureS24
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S24.** Multiverse p-value distributions belonging to the associations between violence exposure with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 2 in the main text.
+(
+  (pilot_prim_lm_pvalues_plot$flanker_ssp_p + labs(title = "Perceptual input", tag = "Pilot", y = "", x = "p") + theme_classic()) + 
+    (pilot_prim_lm_pvalues_plot$flanker_ssp_interference + labs(title = "Interference", y = "", x = "p") + theme_classic()) 
+) /
+  (
+    (study1_prim_ssp_pvalues_plot_study1$p_flanker + labs(title = "Perceptual input", tag = "Study 1", y = "", x = "p") + theme_classic()) + 
+    (study1_prim_ssp_pvalues_plot_study1$interference_flanker + labs(title = "Interference", y = "", x = "p") + theme_classic()) 
+  ) /
+  (
+    (study2_prim_aim1_pvalues_plot_study2$p_flanker.vio_comp + labs(title = "Perceptual input", tag = "Study 2", y = "") + theme_classic()) + 
+    (study2_prim_aim1_pvalues_plot_study2$interference_flanker.vio_comp + labs(title = "Interference", y = "") + theme_classic()) 
+  ) /
+  (
+    (study2_aim1_ssp_pooled_pvalues_plot$vio_comp_p_flanker + labs(title = "Perceptual input", tag = "Pooled", y = "") + theme_classic()) + 
+    (study2_aim1_ssp_pooled_pvalues_plot$vio_comp_interference_flanker + labs(title = "Interference", y = "") + theme_classic()) 
+  )
+```
+
+```{r}
+#| label: figureS25
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S25.** Multiverse explained variance of each data cleaning decision belonging to the associations between violence exposure with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 2 in the main text.
+(
+  (pilot_prim_lm_variance_plot$flanker_ssp_p + labs(title = "Perceptual input", tag = "Pilot", fill = "", y = "")) + 
+    (pilot_prim_lm_variance_plot$flanker_ssp_interference + labs(title = "Interference", y = "") + guides(fill = "none")) 
+) /
+  (
+    (study1_prim_ssp_variance_plot_study1$p_flanker + labs(title = "Perceptual input", tag = "Study 1", y = "") + guides(fill = "none")) + 
+    (study1_prim_ssp_variance_plot_study1$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none")) 
+  ) /
+  (
+    (study2_prim_aim1_variance_plot_study2$p_flanker.vio_comp + labs(title = "Perceptual input", tag = "Study 2", y = "") + guides(fill = "none")) + 
+    (study2_prim_aim1_variance_plot_study2$interference_flanker.vio_comp + labs(title = "Interference", y = "") + guides(fill = "none")) 
+  ) /
+  (
+    (study2_prim_aim1_variance_plot$p_flanker.vio_comp + labs(title = "Perceptual input", tag = "Pooled", y = "") + guides(fill = "none")) + 
+    (study2_prim_aim1_variance_plot$interference_flanker.vio_comp + labs(title = "Interference", y = "") + guides(fill = "none")) 
+  ) + plot_layout(guides = "collect") & theme(legend.position='bottom')
+```
+
+```{r}
+#| label: figureS26
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S26.** Multiverse p-value distributions belonging to the associations between unpredictability with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 3 in the main text.
+(
+  (pilot_expl_lm_pvalues_plot$flanker_ssp_p + labs(title = "Perceptual input", tag = "Pilot", y = "", x = "p") + theme_classic()) + 
+    (pilot_expl_lm_pvalues_plot$flanker_ssp_interference + labs(title = "Interference", y = "", x = "p") + theme_classic()) 
+) /
+  (
+    (study1_expl_ssp_pvalues_plot_study1$p_flanker + labs(title = "Perceptual input", tag = "Study 1", y = "", x = "p") + theme_classic()) + 
+    (study1_expl_ssp_pvalues_plot_study1$interference_flanker + labs(title = "Interference", y = "", x = "p") + theme_classic()) 
+  ) /
+  (
+    (study2_prim_aim1_pvalues_plot_study2$p_flanker.unp_comp + labs(title = "Perceptual input", tag = "Study 2", y = "") + theme_classic()) + 
+    (study2_prim_aim1_pvalues_plot_study2$interference_flanker.unp_comp + labs(title = "Interference", y = "") + theme_classic()) 
+  ) /
+  (
+    (study2_prim_aim1_pvalues_plot$p_flanker.unp_comp + labs(title = "Perceptual input", tag = "Pooled", y = "") + theme_classic()) + 
+    (study2_prim_aim1_pvalues_plot$interference_flanker.unp_comp + labs(title = "Interference", y = "") + theme_classic()) 
+  )
+```
+
+```{r}
+#| label: figureS27
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S27.** Multiverse explained variance of each data cleaning decision belonging to the associations between unpredictability with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 3 in the main text.
+(
+  (pilot_expl_lm_variance_plot$flanker_ssp_p + labs(title = "Perceptual input", fill = "", tag = "Pilot", y = "")) + 
+    (pilot_expl_lm_variance_plot$flanker_ssp_interference + labs(title = "Interference", y = "") + guides(fill = "none")) 
+) /
+  (
+    (study1_expl_ssp_variance_plot_study1$p_flanker + labs(title = "Perceptual input", tag = "Study 1", y = "") + guides(fill = "none")) + 
+    (study1_expl_ssp_variance_plot_study1$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none")) 
+  ) /
+  (
+    (study2_prim_aim1_variance_plot_study2$p_flanker.unp_comp + labs(title = "Perceptual input", tag = "Study 2", y = "") + guides(fill = "none")) + 
+    (study2_prim_aim1_variance_plot_study2$interference_flanker.unp_comp + labs(title = "Interference", y = "") + guides(fill = "none")) 
+  ) /
+  (
+    (study2_prim_aim1_variance_plot$p_flanker.unp_comp + labs(title = "Perceptual input", tag = "Pooled", y = "") + guides(fill = "none")) + 
+    (study2_prim_aim1_variance_plot$interference_flanker.unp_comp + labs(title = "Interference", y = "") + guides(fill = "none")) 
+  ) + plot_layout(guides = "collect") & theme(legend.position='bottom')
+```

### 2024-03-26 supplement/supplements.qmd
Make supplement single spaced and update Table titles

@@
   docx:
-    reference-doc: ../manuscript/reference-doc.docx
+    reference-doc: reference-doc.docx
     toc: true
@@
 The following exploratory measures were collected in all three studies.
+<br>
 
@@
 We computed an overall sleep deprivation composite by standardizing and averaging across the two unweighted sleep-related items.
+<br>
 
@@
 We created a composite score of poverty exposure before age 13 by averaging together the standardized scores of perceived level of resource scarcity, overall parental education, and household income.
+<br>
 
@@
 An overall impulsivity variable was computed by averaging the five unweighted items.
+<br>
 
@@
 An overall future orientation variable was computed by averaging the 15 unweighted items.
+<br>
 
@@
 An overall depression variable was computed by averaging the 20 unweighted items.
+<br>
 
@@
 
-We measured attentional style using the Attentional Style Questionnaire [ASQ\; @calster_2018] (See [Table S7](#appendix).
+We measured attentional style using the Attentional Style Questionnaire [ASQ\; @calster_2018].
 The ASQ measures self-reported attentional style, with seven items asking about the participant's propensity for internally oriented attention (e.g., "During an activity, unrelated mmental images and thoughts come to my mind") and seven items about externally oriented attention (e.g., "I am easily drawn to new stimuli (for example, voices of people passing by, as sound in the house, ...) that are not relevant to a task I am doing").
@@
 We computed unweighted averages separately for internally oriented attention and externally oriented attention.
+<br>
 
 # Section 2. Exploratory analyses
+<br>
 
 ## 2.1. Consistency in unpredictability measures
+<br>
 
@@
 
+<br>
+
 ### 2.1.2 Study 1
@@
 Similar to the Pilot, the EFA yielded five factors based on parallel analysis.
-We plotted the factor loadings of each factor in the Pilot against those in Study 1 to investigate their correspondence (See Figure SX).
+We plotted the factor loadings of each factor in the Pilot against those in Study 1 to investigate their correspondence (See Figure S1).
 In general, individual items largely loaded on the same factors, and the sizes of their loadings were also comparable.
@@
 #| fig-cap: | 
-#|   **Figure S1.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S1.** Comparison of factor loadings of unpredictability items in the Pilot and Study 1. 
 study1_efa_fig 
 ```
+<br>
+
 ## 2.2. Bivariate correlations between future orientation and impulsivity with attention tasks
@@
 ```{r}
-#| tab.id: tableS3
+#| tab.id: tableS2
 #| results: markup
-supp_cor_table |> 
-  autofit()
+supp_cor_table 
 ```
 
+<br>
+
 # Section 3. Model fit
+<br>
 
 ## 3.1. Pilot 
+<br>
 
@@
 Based on subsequent external input, we fit an additional model using Kolmogorov-Smirnov (KS) estimation instead of ML estimation, additionally estimating the inter-trial variability parameter of the non-decision time.
-This improved parameter estimation (see Figure SX).
+This improved parameter estimation (see Figure S3-5).
 
@@
 #| fig-cap: | 
-#|   **Figure S2.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S2.** Distributions of Drift Diffusion Model parameters for the Cued Attention Task using Kolmogorov-Smirnov estimation.
 cueing_DDM_results_mod9 |> 
@@
 
-Model convergence was assessed (1) by visually inspecting the traces, which should not contain any drifts or large jumps (see Figure SX and SX); (2) through simulation.
+Model convergence was assessed (1) by visually inspecting the traces, which should not contain any drifts or large jumps (see Figure S3 and Figure S6); (2) through simulation.
 Specifically, we used each participant's DDM estimates to simulate 100 RT and accuracy estimates (per condition).
-The distributions of the participant's true RTs and their simulated RTs were assessed through bivariate correlations at the 25th, 50th and 75th percentile (See Figure SX and SX).
-We made the same comparison for mean accuracy levels (See Figure SX and SX).
+The distributions of the participant's true RTs and their simulated RTs were assessed through bivariate correlations at the 25th, 50th and 75th percentile (See Figure S4 and Figure S7).
+We made the same comparison for mean accuracy levels (See Figure S5 and Figure S8).
 
@@
 #| fig-cap: | 
-#|   **Figure S3.
-** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S3. ** Chain convergence for the Hierarchical Bayesion Drift Diffusion Model for the Cued Attention Task. Plots should resemble a 'fat, hairy catterpillar'.
 pilot_traces_cueing
@@
 #| fig-cap: | 
-#|   **Figure S4.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S4.** Drift Diffusion parameter recovery for the Cued Attention Task comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
 pilot_recov_rt_cueing
@@
 #| fig-cap: | 
-#|   **Figure S5.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S5.** Drift Diffusion parameter recovery for the Cued Attention Task comparing simulated and recovered accuracy rates.
 pilot_recov_acc_cueing
@@
 #| fig-cap: | 
-#|   **Figure S6.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S6.** Chain convergence for the Hierarchical Bayesion Drift Diffusion Model for the Change Detection Task. Plots should resemble a 'fat, hairy catterpillar'.
 pilot_traces_change
@@
 #| fig-cap: | 
-#|   **Figure S7.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S7.** Drift Diffusion parameter recovery for the Change Detection Task comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
 pilot_recov_rt_change
@@
 #| fig-cap: | 
-#|   **Figure S8.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
-pilot_recov_rt_cueing
+#|   **Figure S8.** Drift Diffusion parameter recovery for the Change Detection Task comparing simulated and recovered accuracy rates.
+pilot_recov_acc_change
 ```
@@
 We then calculated correlations between observed and simulated RTs at the 25th, 50th, and 75th percentile, as well as between observed and simulated mean accuracy.
-As can be seen in Figure SX and Figure SX, we observed high agreement between observed and simulated RTs and accuracy rates.
+As can be seen in Figure S9 and Figure S10, we observed high agreement between observed and simulated RTs and accuracy rates.
 
@@
 #| fig-cap: | 
-#|   **Figure S9.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S9.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
 qq_data_flanker <- left_join(predicted_quantiles_flanker, observed_quantiles_flanker)
@@
 #| fig-cap: | 
-#|   **Figure S10.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S10.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered accuracy rates.
 qq_flanker_acc <- ggplot(qq_data_flanker) +
@@
 
+<br>
+
 ## 3.2. Study 1
@@
 Model fit of the Flanker was done the same as in the Pilot.
-Figure SX and Figure SX show the model fit based on simulated data.
+Figure S11 and Figure S12 show the model fit based on simulated data.
 We found good model fit across all three conditions, both for RTs as well as accuracy rates.
@@
 #| fig-cap: | 
-#|   **Figure S11.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S11.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times across the standard, enhanced, and degraded condition.
 study1_ssp_fit_rt
@@
 #| fig-cap: | 
-#|   **Figure S12.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S12.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered accuracy rates across the standard, enhanced, and degraded condition.
 study1_ssp_fit_acc
@@
 
+<br>
+
 ### 3.3.1 Flanker
@@
 Model fit of the Flanker was done the same as in the Pilot and Study 1.
-Figure SX and Figure SX show the model fit based on simulated data.
+Figure S13 and Figure S14 show the model fit based on simulated data.
 We found good model fit, both for RTs as well as accuracy rates.
@@
 #| fig-cap: | 
-#|   **Figure S13.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S13.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
 study2_ssp_fit_rt
@@
 #| fig-cap: | 
-#|   **Figure S14.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
-The dashed vertical line depicts the cut-off of .05.
-The percentages in the upper-right corners are the percentage of statistically significant analyses in multiverse.
+#|   **Figure S14.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered accuracy rates.
 study2_ssp_fit_acc
@@
 
+<br>
+
 ### 3.3.2 Global-Local Task
+
+<br>
 
@@
 In this section, we provide a numbered overview of the deviations from the preregistration in each study.
+<br>
 
@@
 We noticed this when plotting the within-person estimates between conditions (standard, enhanced, and degraded) against each other.
-Figure SX provides an overview of these correlations for attentional width, shrinking rate, interference, and, for illustrative purposes, the RT difference score.
+Figure S15 provides an overview of these correlations for attentional width, shrinking rate, interference, and, for illustrative purposes, the RT difference score.
 We consider the comparison between the standard and enhanced condition the most informative, as the stimuli in these conditions were most similar.
@@
 
-3.
+<br>
 
@@
 The results of aim 1 are described in Section 2.1.2.
-The
+Results of aim 2-4 are described in Section 2.2.
+
+<br>
 
@@
 
+<br>
+
 # Section 5. Multiverse analysis.
@@
 
+<br>
+
 ## 5.1. Pilot
 
-Figure XX and Figure XX present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 3 in the main text.
+Figure S16 and Figure S17 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 3 in the main text.
 
@@
 ```
+<br>
 
@@
 
-Figure XX and Figure XX present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 4 in the main text.
+Figure S18 and Figure S19 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 4 in the main text.
 
@@
 
+<br>
+
+Figure S20-S23 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 5 in the main text.
+
 ```{r}
@@
 ```
+
+<br>
 
@@
 
+<br>
+
 ## 5.3 Study 2
+
+Figure S24 and Figure S25 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Figure 2 in the main text.
 
@@
 ```
+<br>
+
+Figure S26 and Figure S27 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Figure 3 in the main text.
 

### 2024-03-26 preregistrations/1_pilot/scripts/0_data_prep/1_create_scales.R
fix scripts

@@ -446,7 +446,7 @@ self_report <-
     by = "id"
    ) |> 
   select(
-    id, meta_start, meta_captcha, meta_resolution_ratio, meta_resolution_height, matches("^(chaos|unp|change|quic|unp_comp|violence|vio_comp|fighting|ses|fos|dems_age|dems_sex|dems_gender|att_check01|att_check02|att_getup|att_interrupted|att_noise|attention)")
+    id, meta_start, meta_captcha, meta_resolution_ratio, meta_resolution_height, dems_edu, dems_class_current, matches("^(chaos|unp|pcunp|change|quic|unp_comp|violence|vio_comp|fighting|ses|fos|depression|impuls|dems_age|dems_sex|dems_gender|att_check01|att_check02|att_getup|att_interrupted|att_noise|attention)")
   )
 
 codebook <- create_codebook(self_report) %>%

### 2024-03-26 preregistrations/1_pilot/scripts/3_exploratory_analyses.R

@@ -105,14 +105,14 @@ efa_tidy <- tidy(efa_model) %>%
 pilot_efa_table <- efa_tidy %>%
   rename(
     "Household\nstability/conflict" = `1`,
-    "Monitoring/neglect" = `2`,
+    "Monitoring/\nneglect" = `2`,
     "Macro unp." = `3`,
     "Disorganization" = `4`,
-    "People in household" = `5`
+    "People in\nhousehold" = `5`
   ) |> 
   select(-var) |> 
   flextable() |> 
-  autofit() |> 
+
   bold(i = 1:24, j = 2) |> 
   bold(i = 25:37, j = 3) |>
   bold(i = 38:44, j = 4) |>
@@ -127,9 +127,10 @@ pilot_efa_table <- efa_tidy %>%
   ) |> # Add a new header row on top. We can use this new row to add the title
   flextable::compose(
     i = 1, j = 1,
-    as_paragraph(as_b("Table SX. "), "Exploratory Factor Analysis on unpredictability items in the Pilot."),
+    as_paragraph(as_b("Table S1. "), "Exploratory Factor Analysis on unpredictability items in the Pilot."),
     part = "header"
-  )
+  ) |> 
+  width(width = c(4,0.75,0.75,0.75,0.75,0.75))
   
 save(pilot_efa_table, file = "preregistrations/1_pilot/analysis_objects/supp_section2.Rdata")
 

### 2024-03-26 preregistrations/2_study1/scripts/1_data_prep/1_create_scales.R

@@ -521,7 +521,7 @@ self_report <-
     by = "id"
   ) |> 
   select(
-    id, meta_start, meta_captcha, meta_resolution_ratio, meta_resolution_height, matches("^(chaos|unp|change|quic|unp_comp|violence|vio_comp|fighting|ses|fos|dems_age|dems_sex|dems_gender|att_check01|att_check02|att_getup|att_interrupted|att_noise|attention)")
+    id, meta_start, meta_captcha, meta_resolution_ratio, meta_resolution_height, dems_edu, dems_class_current, matches("^(chaos|unp|change|quic|unp_comp|violence|vio_comp|fighting|ses|fos|depression|impuls|dems_age|dems_sex|dems_gender|att_check01|att_check02|att_getup|att_interrupted|att_noise|attention)")
   )
 
 codebook <- create_codebook(self_report) %>%

### 2024-03-26 preregistrations/3_study2/scripts/4_exploratory_analyses.R

@@ -25,7 +25,7 @@ load("preregistrations/3_study2/analysis_objects/hddm_globloc_model2_objects.RDa
 # Pilot study
 pilot_data <- read_csv("data/1_pilot/2_cleaned_data.csv") |> 
   select(id, 
-         depression_mean, impuls_mean, fos_fo_mean, ses_comp = poverty_composite,
+         depression_mean, impuls_mean, fos_fo_mean,
          a_flanker = flanker_ssp_a, t0_flanker = flanker_ssp_t0, p_flanker = flanker_ssp_p, interference_flanker = flanker_ssp_interference) %>%
   filter(is.finite(interference_flanker)) |> 
   mutate(
@@ -37,7 +37,7 @@ pilot_data <- read_csv("data/1_pilot/2_cleaned_data.csv") |>
 
 study1_data <-  read_csv("data/2_study1/2_cleaned_data.csv") |> 
   select(id, 
-         depression_mean, impuls_mean, fos_fo_mean, ses_comp,
+         depression_mean, impuls_mean, fos_fo_mean,
          a_flanker_std, t0_flanker_std, p_flanker_std, interference_flanker_std) %>%
   rename(a_flanker = a_flanker_std,
          t0_flanker = t0_flanker_std,
@@ -51,7 +51,7 @@ study1_data <-  read_csv("data/2_study1/2_cleaned_data.csv") |>
 # Study 2
 study2_data <-  read_csv("data/3_study2/2_cleaned_data.csv") |> 
   select(id,
-         depression_mean, impuls_mean, fos_fo_mean, ses_comp, att_style_int, att_style_ext,
+         depression_mean, impuls_mean, fos_fo_mean, att_style_int, att_style_ext,
          a_flanker, t0_flanker, p_flanker, interference_flanker,
          hddm_v_local, hddm_v_global
   ) %>%
@@ -69,7 +69,7 @@ study2_data <-  read_csv("data/3_study2/2_cleaned_data.csv") |>
 supp_cor_table <- bind_rows(pilot_data, study1_data, study2_data) |> 
   filter(is.finite(interference_flanker)) |> 
   select(
-    depression_mean, impuls_mean, fos_fo_mean, ses_comp,
+    depression_mean, impuls_mean, fos_fo_mean, 
     att_style_int, att_style_ext, p_flanker, interference_flanker,
     a_flanker, t0_flanker, v_globloc_diff
   ) |>
[…]

### 2024-03-26 manuscript/manuscript.qmd
fix Table formatting

@@
 
-#### **Childhood adversity is not associated with lowered inhibition, but lower perceptual processing: A Drift Diffusion Model analysis**
+#### **Childhood adversity is not associated with lowered inhibition, but slower perceptual processing: A Drift Diffusion Model analysis**
 
@@
 #| results: markup
-pilot_main_eff_ddm_table
+pilot_main_eff_ddm_table |> 
+  border(i = 1, border.bottom = fp_border_default(), part = "header") 
 ```
@@
 #| results: markup
-study1_results_table
+study1_results_table |> 
+  border(i = 1, border.bottom = fp_border_default(), part = "header") 
 ```
@@
 
+\pagebreak
+
 ```{r}
@@
 #| results: markup
-study1_condition_results_table
+study1_condition_results_table |> 
+  border(i = 1, border.bottom = fp_border_default(), part = "header") 
 ```

### 2024-03-26 manuscript/scripts/pooled_stage_objects.R

@@ -56,7 +56,7 @@ select(nvs_mean, fighting_mean, vio_comp,
     ~ifelse(is.na(.), "", .)
   )) |> 
   mutate(across(
-    everything(),
+    -Variable,
     ~formatC(.,  digits = 2, width = 3, flag = "0", format = 'f'))) |> 
   flextable() |> 
   width("empty1", width = .2) |> 
@@ -99,12 +99,12 @@ select(nvs_mean, fighting_mean, vio_comp,
   border(i = 2, border.top = fp_border_default(), part = "header") |> 
   border(i = 3, border.bottom = fp_border_default(), part = "header") |> 
   border(i = 17, border.bottom = fp_border_default(), part = "body") |> 
-  align(i = 1:12, j = 1, align = "left", part = "body") |> 
   bold(i = 2:3, part = "header") |> 
-  align(i = 2:3, align = c("center"), part = "header") |> 
-  align(i = 1, align = c("left"), part = "body") |> 
-  padding(j=1, padding.left=0) |> 
-  autofit() 
+  align(j = 2:3, align = c("center"), part = "header") |> 
+  align(j = 2:12, align = c("center"), part = "body") |> 
+  align(i = 1:17, j = 1, align = c("left"), part = "body") |> 
+  border(i = 1, border.bottom = fp_border_default(), part = "header") |> 
+  width(width = c(1.5, rep(0.6, 3), 0.1, rep(0.6, 7)))
 
 
 
@@ -213,12 +213,13 @@ demographics_table <- list(
   ) |>
   border_remove() |> 
   border(i = 2, border.top = fp_border_default(), part = "header") |> 
-  border(i = 1, border.top = fp_border_default(), part = "body") |> 
   border(i = 24, border.bottom = fp_border_default(), part = "body") |> 
-  set_table_properties(width = 1, layout = "autofit") |> 
   bold(i = c(1, 2, 3, 8, 18), j = 1) |> 
   bold(i = 1, j = 2:4, part = "header") |> 
-  padding(i=c(4:7, 9:17, 19:24), j=1, padding.left=20)
+  padding(i=c(4:7, 9:17, 19:24), j=1, padding.left=20) |> 
+  border(i = 1, border.bottom = fp_border_default(), part = "header") |> 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") |> 
+  autofit()
 
 
 

### 2024-03-26 manuscript/manuscript.qmd
small edits in manuscript

@@
 Recent adaptation-based perspectives, however, have argued that people from adversity may also develop intact, or enhanced, abilities for solving problems in high-adversity contexts [@ellis_2017; @frankenhuis_2013].
-Adaptation- and deficit-based perspectives are considered complimentary: for instance, adversity may impair some cognitive processes, yet enhance others.
+Adaptation- and deficit-based perspectives are considered complimentary.
+For instance, adversity may impair some cognitive processes, yet enhance others.
 Despite their compatibility, few studies have investigated how the interplay of impaired and enhanced abilities shapes performance.
@@
 Distinguishing between these two possibilities is challenging for two reasons.
-First, few studies in the adversity literature have measured performance differences on different attention tasks within the same individual.
+First, few studies in the adversity literature have measured performance differences on different attention tasks within the same individual [@mezzacappa_2004; @mittal_2015].
 Thus, it is unclear whether lowered inhibition is related to enhanced processing of peripheral information in people from from adverse backgrounds.
 Second, performance on inhibition tasks is---beyond the ability to inhibit distractors---also influenced by other factors, such as a person's general processing speed and response caution [@hedge_2022; @loffler_2022].
-This multifinality means that lowered performance on inhibition tasks does not necessarily reflect inhibition difficulties.
+This means that lowered performance on inhibition tasks does not necessarily reflect inhibition difficulties.
 In other words, we should consider cognitive processes other than ability when drawing inferences based on inhibition tasks.
@@
 Previous research shows that these two types of adversity are on the one hand associated with improved attention shifting and working memory updating [@fields_2021; @mittal_2015; @young_2018; @young_2022], and on the other hand with lowered inhibition and working memory capacity [@fields_2021; @mittal_2015; @young_2018].
-We conducted three online studies: one pilot and two follow-up studies).
+We conducted three online studies: one pilot and two follow-up studies.
 Using cognitive modeling, we unpack Flanker performance in comparison to other tasks that require externally focused attention (Pilot), across visual processing manipulations (Study 1), and in terms of tendencies for holistic versus local processing (Study 2).
@@
 The main text addresses the primary analyses involving violence exposure and the exploratory analyses involving environmental unpredictability.
-We describe the other exploratory analyses in the supplemental materials and involved constructs that we hypothesized might be related to a present-oriented attention style, such as impulsivity and future orientation.
+We describe the other exploratory analyses in the supplemental materials (section 2).
+For an overview of all deviations from the preregistrations, see section 4 of the supplemental materials.
 
-# Pilot study
+# Pilot
 
@@
 This generally improves the accuracy of the estimation.
-See the supplemental materials for an overview of the fit procedure and model fit across all models.
+See the supplemental materials (section 3) for an overview of the fit procedure and model fit across all models.
 
@@
 Specifically, we looked at the influence of including or excluding 1) participants who scored below 0.5 on a build-in bot-detection measure on Prolific (potentially indicating a bot); 2) participants who did not rescale their screen at the start of the experiment; 3) participants who did not enter fullscreen mode prior to starting the tasks; 4) participants who exited fullscreen mode at any point during the tasks; 5) participants who indicated high levels of noise in their environment; 6) participants who indicated extreme interruptions during the experiment.
+See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
 
@@
 
-We preregistered two potential data patterns and associated interpretations, without a priori favoring one over the other.
+We preregistered two potential data patterns and associated interpretations, without favoring one over the other *a priori*.
 First, the strength of perceptual input might be lower for people with more exposure to violence compared to people with less exposure to violence across all conditions.
@@
 For the primary analyses, we used bootstrapping to compute the probability of obtaining an effect size at least as extreme as observed in the real data, conditioned on a true effect size of zero [for details, see @simonsohn_2020].
+See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
 
@@
 **Multiverse analysis.** We included the same decisions in the multiverse as in the previous studies.
-However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, see <https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md>)
+However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, see <https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md>).
+See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
 
-**DDM estimation.** For the Flanker, we used the SSP (@grange_2016; @white_2018a; @white_2018b; @white_2011\] using the same procedure as in Study 1.
+**DDM estimation.** For the Flanker, we used the SSP [@grange_2016; @white_2018a; @white_2018b; @white_2011] using the same procedure as in Study 1.
 For the Global-Local Task, we used a hierarchical Bayesian DDM to fit the data using the *runjags* package [@denwood_2016].
-See the supplemental materials (Section 4) for more information about the procedure and model fit.
+See the supplemental materials (Section 3) for more information about the procedure and model fit.
 
@@
 Specifically, we relaxed the low performance threshold as the task was more difficult than anticipated.
-These deviations are described in the amendment (<https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md>).
+These deviations are described in the supplemental materials (section 4).
 
-**Primary analyses.** We ran simple regressions for analyses involving only main effects (primary aim 1), and linear mixed effects models for analyses involving within-subject interactions (primary aim 2 and 3).
-To address the third primary aim (within-subject interaction between Global-Local drift rate and Flanker strength of perceptual input), we further preprocessed the data in two steps.
+**Primary analyses.** We ran simple regressions for analyses involving only main effects (aim 1), and linear mixed effects models for analyses involving within-subject interactions (aim 2 and 3).
+To address aim 3 (within-subject interaction between Global-Local drift rate and Flanker strength of perceptual input), we further preprocessed the data in two steps.
 First, we computed a difference score of Global-Local drift rates by subtracting the drift rate on local trials from the drift rate on global trials (with higher scores reflecting relatively faster information processing on global trials).

### 2024-03-26 manuscript/scripts/study1_stage_objects.R

@@ -34,7 +34,7 @@ txt_ivs_dist_study1 <-
   })
 
 txt_ivs_alpha_study1 <- 
-  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
+  c("violence\\d\\d", "unp\\d\\d", 
     "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
     "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
     "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
@@ -43,7 +43,7 @@ txt_ivs_alpha_study1 <-
        select(matches(x)) |> 
        psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
   }) |> 
-  setNames(c("stai_s", "violence", "unp", 
+  setNames(c("violence", "unp", 
              "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
              "quic_total", "chaos", "ses", "impuls", "fos_pa", "fos_tp", "fos_fc", "fos_fo", "depression"))
 
@@ -839,7 +839,7 @@ study1_expl_ssp_eff_curve_plot_study1 <- unique(study1_expl_ssp_effects_sum_stud
         inherit.aes = F
       )  +
       geom_text(
-        aes(x = 32, y = 0.28, label = paste0(round(sum(p.value < .05)/n*10, 1), " % of p-values < .05")),
+        aes(x = 32, y = 0.28, label = paste0(round(sum(p.value < .05)/n*100, 1), " % of p-values < .05")),
         size = 5,
         show.legend = F,
         inherit.aes = F

### 2024-03-26 supplement/supplements.qmd
add Figure with DDM ML distributions

@@
 However, all three models showed estimation problems, especially with regard to the boundary separation.
-Specifically, boundary separation estimates for several participants ended up at an upper boundary of 10, indicating that they were not recovered well.
+Specifically, boundary separation estimates for several participants ended up at an upper boundary of 10, indicating that they were not recovered well (see Figure S2).
 Based on subsequent external input, we fit an additional model using Kolmogorov-Smirnov (KS) estimation instead of ML estimation, additionally estimating the inter-trial variability parameter of the non-decision time.
-This improved parameter estimation (see Figure S3-5).
+This improved parameter estimation (see Figure S4).
 
@@
 #| fig-cap: | 
-#|   **Figure S2.** Distributions of Drift Diffusion Model parameters for the Cued Attention Task using Kolmogorov-Smirnov estimation.
+#|   **Figure S2.** Distributions of Drift Diffusion Model parameters for the Cued Attention Task using Maximum likelihood estimation.
+cueing_DDM_results_mod8 |> select(starts_with("cueing"), -cueing_ml_fit) |> 
+     rename(
+         "a" = cueing_ml_a,
+         "v - cued" = cueing_cued_ml_v,
+         "v - neutral" = cueing_neutral_ml_v,
+         "t - cued" = cueing_cued_ml_t0,
+         "t - neutral" = cueing_neutral_ml_t0,
+     ) |> 
+     pivot_longer(everything(), names_to = "parameter", values_to = "Estimate") |> 
+     ggplot(aes(Estimate)) +
+     geom_histogram() +
+     facet_wrap(~parameter, scales = 'free') +
+     theme_classic()
+```
+
+<br>
+
+```{r}
+#| label: figureS3
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S3.** Distributions of Drift Diffusion Model parameters for the Cued Attention Task using Kolmogorov-Smirnov estimation.
 cueing_DDM_results_mod9 |> 
@@
 ```
+<br>
+
 Finally, we switched to estimation using Hierarchical Bayesian DDM (HDDM) for our final analyses.
@@
 
-Model convergence was assessed (1) by visually inspecting the traces, which should not contain any drifts or large jumps (see Figure S3 and Figure S6); (2) through simulation.
+Model convergence was assessed (1) by visually inspecting the traces, which should not contain any drifts or large jumps (see Figure S4 and Figure S7); (2) through simulation.
 Specifically, we used each participant's DDM estimates to simulate 100 RT and accuracy estimates (per condition).
-The distributions of the participant's true RTs and their simulated RTs were assessed through bivariate correlations at the 25th, 50th and 75th percentile (See Figure S4 and Figure S7).
-We made the same comparison for mean accuracy levels (See Figure S5 and Figure S8).
-
-<br>
-
-```{r}
-#| label: figureS3
-#| dpi: 600
-#| fig.width: 7
-#| fig-cap: | 
-#|   **Figure S3. ** Chain convergence for the Hierarchical Bayesion Drift Diffusion Model for the Cued Attention Task. Plots should resemble a 'fat, hairy catterpillar'.
-pilot_traces_cueing
-```
+The distributions of the participant's true RTs and their simulated RTs were assessed through bivariate correlations at the 25th, 50th and 75th percentile (See Figure S5 and Figure S8).
+We made the same comparison for mean accuracy levels (See Figure S6 and Figure S9).
 
@@
 #| fig-cap: | 
-#|   **Figure S4.** Drift Diffusion parameter recovery for the Cued Attention Task comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
-pilot_recov_rt_cueing
+#|   **Figure S4. ** Chain convergence for the Hierarchical Bayesion Drift Diffusion Model for the Cued Attention Task. Plots should resemble a 'fat, hairy catterpillar'.
+pilot_traces_cueing
 ```
@@
 #| fig-cap: | 
-#|   **Figure S5.** Drift Diffusion parameter recovery for the Cued Attention Task comparing simulated and recovered accuracy rates.
-pilot_recov_acc_cueing
+#|   **Figure S5.** Drift Diffusion parameter recovery for the Cued Attention Task comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
+pilot_recov_rt_cueing
 ```
@@
 #| fig-cap: | 
-#|   **Figure S6.** Chain convergence for the Hierarchical Bayesion Drift Diffusion Model for the Change Detection Task. Plots should resemble a 'fat, hairy catterpillar'.
-pilot_traces_change
+#|   **Figure S6.** Drift Diffusion parameter recovery for the Cued Attention Task comparing simulated and recovered accuracy rates.
+pilot_recov_acc_cueing
 ```
@@
 #| fig-cap: | 
-#|   **Figure S7.** Drift Diffusion parameter recovery for the Change Detection Task comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
-pilot_recov_rt_change
+#|   **Figure S7.** Chain convergence for the Hierarchical Bayesion Drift Diffusion Model for the Change Detection Task. Plots should resemble a 'fat, hairy catterpillar'.
+pilot_traces_change
 ```
@@
 #| fig-cap: | 
-#|   **Figure S8.** Drift Diffusion parameter recovery for the Change Detection Task comparing simulated and recovered accuracy rates.
+#|   **Figure S8.** Drift Diffusion parameter recovery for the Change Detection Task comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
+pilot_recov_rt_change
+```
+
+<br>
+
+```{r}
+#| label: figureS9
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S9.** Drift Diffusion parameter recovery for the Change Detection Task comparing simulated and recovered accuracy rates.
 pilot_recov_acc_change
@@
 We then calculated correlations between observed and simulated RTs at the 25th, 50th, and 75th percentile, as well as between observed and simulated mean accuracy.
-As can be seen in Figure S9 and Figure S10, we observed high agreement between observed and simulated RTs and accuracy rates.
+As can be seen in Figure S10 and Figure S11, we observed high agreement between observed and simulated RTs and accuracy rates.
 
@@
 ```{r}
-#| label: figureS9
+#| label: figureS10
 #| dpi: 600
@@
 #| fig-cap: | 
-#|   **Figure S9.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
+#|   **Figure S10.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
 qq_data_flanker <- left_join(predicted_quantiles_flanker, observed_quantiles_flanker)
@@
 ```{r}
-#| label: figureS10
+#| label: figureS11
 #| dpi: 600
@@
 #| fig-cap: | 
-#|   **Figure S10.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered accuracy rates.
+#|   **Figure S11.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered accuracy rates.
 qq_flanker_acc <- ggplot(qq_data_flanker) +
@@
 Model fit of the Flanker was done the same as in the Pilot.
-Figure S11 and Figure S12 show the model fit based on simulated data.
+Figure S12 and Figure S13 show the model fit based on simulated data.
 We found good model fit across all three conditions, both for RTs as well as accuracy rates.
-
-<br>
-
-```{r}
-#| label: figureS11
-#| dpi: 600
-#| fig.width: 7
-#| fig.height: 7
-#| fig-cap: | 
-#|   **Figure S11.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times across the standard, enhanced, and degraded condition.
-study1_ssp_fit_rt
-```
 
@@
 #| fig.width: 7
+#| fig.height: 7
 #| fig-cap: | 
-#|   **Figure S12.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered accuracy rates across the standard, enhanced, and degraded condition.
+#|   **Figure S12.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times across the standard, enhanced, and degraded condition.
+study1_ssp_fit_rt
+```
+
+<br>
+
+```{r}
+#| label: figureS13
+#| dpi: 600
+#| fig.width: 7
+#| fig-cap: | 
+#|   **Figure S13.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered accuracy rates across the standard, enhanced, and degraded condition.
 study1_ssp_fit_acc
@@
 Model fit of the Flanker was done the same as in the Pilot and Study 1.
-Figure S13 and Figure S14 show the model fit based on simulated data.
+Figure S14 and Figure S15 show the model fit based on simulated data.
 We found good model fit, both for RTs as well as accuracy rates.
@@
 ```{r}
-#| label: figureS13
+#| label: figureS14
 #| dpi: 600
@@
 #| fig-cap: | 
-#|   **Figure S13.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
+#|   **Figure S14.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered response times at the 25th, 50th and 75th percentile of response times.
 study2_ssp_fit_rt
@@
 ```{r}
-#| label: figureS14
+#| label: figureS15
 #| dpi: 600
@@
 #| fig-cap: | 
-#|   **Figure S14.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered accuracy rates.
+#|   **Figure S15.** Drift Diffusion parameter recovery for the Flanker comparing simulated and recovered accuracy rates.
 study2_ssp_fit_acc
@@
 We noticed this when plotting the within-person estimates between conditions (standard, enhanced, and degraded) against each other.
-Figure S15 provides an overview of these correlations for attentional width, shrinking rate, interference, and, for illustrative purposes, the RT difference score.
+Figure S16 provides an overview of these correlations for attentional width, shrinking rate, interference, and, for illustrative purposes, the RT difference score.
 We consider the comparison between the standard and enhanced condition the most informative, as the stimuli in these conditions were most similar.
@@
 ```{r}
-#| label: figureS15
+#| label: figureS16
 #| fig-width: 7
@@
 #| fig-cap: | 
-#|   **Figure S15. **Within-person bivarate correlations between Flanker conditions in Study 2 for RT differences, attentional width, shrinking rate, and interference.
+#|   **Figure S16. **Within-person bivarate correlations between Flanker conditions in Study 2 for RT differences, attentional width, shrinking rate, and interference.
 study1_ssp_cor_plot
@@
 
-Figure S16 and Figure S17 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 3 in the main text.
+Figure S17 and Figure S18 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 3 in the main text.
 
 ```{r}
-#| label: figureS16
+#| label: figureS17
 #| fig.width: 7
@@
 #| fig-cap: | 
-#|   **Figure S16.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
+#|   **Figure S17.** Multiverse p-value distributions belonging to the analyses reported in Table 3 in the main text.
 The dashed vertical line depicts the cut-off of .05.
@@
 #| echo: false
-f17_p1 <- pilot_prim_lmer_variance_plot$cueing_rt + labs(title = "Raw response time", tag = "A", y = "", fill = "")
-f17_p2 <- pilot_prim_lmer_variance_plot$cueing_hddm_v + labs(title = "Drift rate", y = "") + guides(fill = "none")
-f17_p3 <- pilot_prim_lm_variance_plot$cueing_fixed_hddm_a + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
-f17_p4 <- pilot_prim_lmer_variance_plot$cueing_hddm_t + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+f18_p1 <- pilot_prim_lmer_variance_plot$cueing_rt + labs(title = "Raw response time", tag = "A", y = "", fill = "")
+f18_p2 <- pilot_prim_lmer_variance_plot$cueing_hddm_v + labs(title = "Drift rate", y = "") + guides(fill = "none")
+f18_p3 <- pilot_prim_lm_variance_plot$cueing_fixed_hddm_a + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f18_p4 <- pilot_prim_lmer_variance_plot$cueing_hddm_t + labs(title = "Non-decision time", y = "") + guides(fill = "none")
 
-f17_p5 <- pilot_prim_lm_variance_plot$rt_change + labs(title = "Raw response time", tag = "B", y = "") + guides(fill = "none") 
-f17_p6 <- pilot_prim_lm_variance_plot$change_hddm_v + labs(title = "Drift rate", y = "") + guides(fill = "none") 
-f17_p7 <- pilot_prim_lm_variance_plot$change_hddm_a + labs(title = "Boundary separation", y = "") + guides(fill = "none")
-f17_p8 <- pilot_prim_lm_variance_plot$change_hddm_t + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+f18_p5 <- pilot_prim_lm_variance_plot$rt_change + labs(title = "Raw response time", tag = "B", y = "") + guides(fill = "none") 
+f18_p6 <- pilot_prim_lm_variance_plot$change_hddm_v + labs(title = "Drift rate", y = "") + guides(fill = "none") 
+f18_p7 <- pilot_prim_lm_variance_plot$change_hddm_a + labs(title = "Boundary separation", y = "") + guides(fill = "none")
+f18_p8 <- pilot_prim_lm_variance_plot$change_hddm_t + labs(title = "Non-decision time", y = "") + guides(fill = "none")
 
-f17_p9 <- pilot_prim_lmer_variance_plot$flanker_rt + labs(title = "Raw response time", tag = "C", y = "") + guides(fill = "none")
-f17_p10 <- pilot_prim_lm_variance_plot$flanker_ssp_p + labs(title = "Perceptual input", y = "") + guides(fill = "none") 
-f17_p11 <- pilot_prim_lm_variance_plot$flanker_ssp_interference + labs(title = "Interference", y = "") + guides(fill = "none") 
-f17_p12 <- pilot_prim_lm_variance_plot$flanker_ssp_a + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
-f17_p13 <- pilot_prim_lm_variance_plot$flanker_ssp_t + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+f18_p9 <- pilot_prim_lmer_variance_plot$flanker_rt + labs(title = "Raw response time", tag = "C", y = "") + guides(fill = "none")
+f18_p10 <- pilot_prim_lm_variance_plot$flanker_ssp_p + labs(title = "Perceptual input", y = "") + guides(fill = "none") 
+f18_p11 <- pilot_prim_lm_variance_plot$flanker_ssp_interference + labs(title = "Interference", y = "") + guides(fill = "none") 
+f18_p12 <- pilot_prim_lm_variance_plot$flanker_ssp_a + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f18_p13 <- pilot_prim_lm_variance_plot$flanker_ssp_t + labs(title = "Non-decision time", y = "") + guides(fill = "none")
 
-align_patches(f17_p1,f17_p2,f17_p3,f17_p4,f17_p5,f17_p6,f17_p7,f17_p8,f17_p9,f17_p10,f17_p11,f17_p12,f17_p13)
+align_patches(f18_p1,f18_p2,f18_p3,f18_p4,f18_p5,f18_p6,f18_p7,f18_p8,f18_p9,f18_p10,f18_p11,f18_p12,f18_p13)
 ```
-
-```{r}
-#| label: figureS17
-#| fig.width: 7
-#| fig.height: 10
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure S17.** Multiverse explained variance of each data cleaning decision belonging to the analyses reported in Table 3 in the main text.
-Panel A: Cued Attention Task.
-Panel B: Change Detection Task.
-Panel C: Flanker Task.
-final_plot_S17 <- 
-  (f17_p1+f17_p2+f17_p3+f17_p4 + plot_layout(ncol = 3)) /
-  (f17_p5+f17_p6+f17_p7+f17_p8 + plot_layout(ncol = 3)) /
-  (f17_p9+f17_p10+f17_p11+f17_p12+f17_p13 + plot_layout(ncol = 3)) + 
-  plot_layout(guides = "collect") & theme(legend.position='bottom')
-
-final_plot_S17
-
-```
-<br>
-
-## 5.2 Study 1
-
-Figure S18 and Figure S19 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 4 in the main text.
 
@@
 #| fig-cap: | 
-#|   **Figure S18.** Multiverse p-value distributions belonging to the analyses reported in Table 4 in the main text.
+#|   **Figure S18.** Multiverse explained variance of each data cleaning decision belonging to the analyses reported in Table 3 in the main text.
+Panel A: Cued Attention Task.
+Panel B: Change Detection Task.
+Panel C: Flanker Task.
+final_plot_S18 <- 
+  (f18_p1+f18_p2+f18_p3+f18_p4 + plot_layout(ncol = 3)) /
+  (f18_p5+f18_p6+f18_p7+f18_p8 + plot_layout(ncol = 3)) /
+  (f18_p9+f18_p10+f18_p11+f18_p12+f18_p13 + plot_layout(ncol = 3)) + 
+  plot_layout(guides = "collect") & theme(legend.position='bottom')
+
+final_plot_S18
+
+```
+<br>
+
+## 5.2 Study 1
+
+Figure S19 and Figure S20 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 4 in the main text.
+
+```{r}
+#| label: figureS19
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S19.** Multiverse p-value distributions belonging to the analyses reported in Table 4 in the main text.
 The dashed vertical line depicts the cut-off of .05.
@@
 #| echo: false
-f19_p1 <- study1_prim_ssp_variance_plot_study1$rt_diff + labs(title = "RT difference", tag = "A", y = "", fill = "")
-f19_p2 <- study1_prim_ssp_variance_plot_study1$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none") 
-f19_p3 <- study1_prim_ssp_variance_plot_study1$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
-f19_p4 <- study1_prim_ssp_variance_plot_study1$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
-f19_p5 <- study1_prim_ssp_variance_plot_study1$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+f20_p1 <- study1_prim_ssp_variance_plot_study1$rt_diff + labs(title = "RT difference", tag = "A", y = "", fill = "")
+f20_p2 <- study1_prim_ssp_variance_plot_study1$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none") 
+f20_p3 <- study1_prim_ssp_variance_plot_study1$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
+f20_p4 <- study1_prim_ssp_variance_plot_study1$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f20_p5 <- study1_prim_ssp_variance_plot_study1$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
 
-f19_p6 <- study1_expl_ssp_variance_plot_study1$rt_diff + labs(title = "RT difference", tag = "B", y = "") + guides(fill = "none") 
-f19_p7 <- study1_expl_ssp_variance_plot_study1$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
-f19_p8 <- study1_expl_ssp_variance_plot_study1$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none")
-f19_p9 <- study1_expl_ssp_variance_plot_study1$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
-f19_p10 <- study1_expl_ssp_variance_plot_study1$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+f20_p6 <- study1_expl_ssp_variance_plot_study1$rt_diff + labs(title = "RT difference", tag = "B", y = "") + guides(fill = "none") 
+f20_p7 <- study1_expl_ssp_variance_plot_study1$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
+f20_p8 <- study1_expl_ssp_variance_plot_study1$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none")
+f20_p9 <- study1_expl_ssp_variance_plot_study1$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f20_p10 <- study1_expl_ssp_variance_plot_study1$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
 
-align_patches(f19_p1,f19_p2,f19_p3,f19_p4,f19_p5,f19_p6,f19_p7,f19_p8,f19_p9,f19_p10)
+align_patches(f20_p1,f20_p2,f20_p3,f20_p4,f20_p5,f20_p6,f20_p7,f20_p8,f20_p9,f20_p10)
 ```
-
-```{r}
-#| label: figureS19
-#| fig.width: 7
-#| fig.height: 10
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure S19.** Multiverse explained variance of each data cleaning decision belonging to the analyses reported in Table 4 in the main text.
-Panel A: Analyses involving violence exposure (hypothesis-driven).
-Panel B: Analyses involving unpredictability (exploratory).
-final_plot_S19 <- 
-  (f19_p1+f19_p2+f19_p3+f19_p4+f19_p5 + plot_layout(ncol = 3)) /
-  (f19_p6+f19_p7+f19_p8+f19_p9+f19_p10 + plot_layout(ncol = 3)) +
-  plot_layout(guides = "collect") & theme(legend.position='bottom')
-
-final_plot_S19
-
-```
-
-<br>
-
-Figure S20-S23 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 5 in the main text.
 
@@
 #| fig-cap: | 
-#|   **Figure S20.** Multiverse p-value distributions belonging to the interaction effects involving violence exposure reported in Table 5 in the main text.
+#|   **Figure S20.** Multiverse explained variance of each data cleaning decision belonging to the analyses reported in Table 4 in the main text.
+Panel A: Analyses involving violence exposure (hypothesis-driven).
+Panel B: Analyses involving unpredictability (exploratory).
+final_plot_S20 <- 
+  (f20_p1+f20_p2+f20_p3+f20_p4+f20_p5 + plot_layout(ncol = 3)) /
+  (f20_p6+f20_p7+f20_p8+f20_p9+f20_p10 + plot_layout(ncol = 3)) +
+  plot_layout(guides = "collect") & theme(legend.position='bottom')
+
+final_plot_S20
+
+```
+
+<br>
+
+Figure S21-S24 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Table 5 in the main text.
+
+```{r}
+#| label: figureS21
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S21.** Multiverse p-value distributions belonging to the interaction effects involving violence exposure reported in Table 5 in the main text.
 The dashed vertical line depicts the cut-off of .05.
@@
 #| echo: false
-f21_p1 <- study1_prim_ssp_enh_variance_plot$rt_diff + labs(title = "RT difference", tag = "A", y = "", fill = "")
-f21_p2 <- study1_prim_ssp_enh_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none") 
-f21_p3 <- study1_prim_ssp_enh_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
-f21_p4 <- study1_prim_ssp_enh_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
-f21_p5 <- study1_prim_ssp_enh_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+f22_p1 <- study1_prim_ssp_enh_variance_plot$rt_diff + labs(title = "RT difference", tag = "A", y = "", fill = "")
+f22_p2 <- study1_prim_ssp_enh_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none") 
+f22_p3 <- study1_prim_ssp_enh_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
+f22_p4 <- study1_prim_ssp_enh_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f22_p5 <- study1_prim_ssp_enh_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
 
-f21_p6 <- study1_prim_ssp_deg_variance_plot$rt_diff + labs(title = "RT difference", tag = "B", y = "") + guides(fill = "none") 
-f21_p7 <- study1_prim_ssp_deg_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
-f21_p8 <- study1_prim_ssp_deg_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
-f21_p9 <- study1_prim_ssp_deg_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
-f21_p10 <- study1_prim_ssp_deg_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+f22_p6 <- study1_prim_ssp_deg_variance_plot$rt_diff + labs(title = "RT difference", tag = "B", y = "") + guides(fill = "none") 
+f22_p7 <- study1_prim_ssp_deg_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
+f22_p8 <- study1_prim_ssp_deg_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
+f22_p9 <- study1_prim_ssp_deg_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f22_p10 <- study1_prim_ssp_deg_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
 
-align_patches(f21_p1,f21_p2,f21_p3,f21_p4,f21_p5,f21_p6,f21_p7,f21_p8,f21_p9,f21_p10)
-```
-
-```{r}
-#| label: figureS21
-#| fig.width: 7
-#| fig.height: 10
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure S21.** Multiverse explained variance of each data cleaning decision belonging to the interaction effects involving violence exposure reported in Table 5 in the main text.
-Panel A: Analyses comparing the enhanced condition to the standard condition.
-Panel B: Analyses comparing the degraded condition to the standard condition.
-final_plot_S21 <- 
-  (f21_p1+f21_p2+f21_p3+f21_p4+f21_p5 + plot_layout(ncol = 3)) /
-  (f21_p6+f21_p7+f21_p8+f21_p9+f21_p10 + plot_layout(ncol = 3)) /
-  plot_layout(guides = "collect") & theme(legend.position='bottom')
-
-final_plot_S21
-
+align_patches(f22_p1,f22_p2,f22_p3,f22_p4,f22_p5,f22_p6,f22_p7,f22_p8,f22_p9,f22_p10)
 ```
@@
 #| fig-cap: | 
-#|   **Figure S22.** Multiverse p-value distributions belonging to the interaction effects involving unpredictability reported in Table 5 in the main text.
+#|   **Figure S22.** Multiverse explained variance of each data cleaning decision belonging to the interaction effects involving violence exposure reported in Table 5 in the main text.
+Panel A: Analyses comparing the enhanced condition to the standard condition.
+Panel B: Analyses comparing the degraded condition to the standard condition.
+final_plot_S22 <- 
+  (f22_p1+f22_p2+f22_p3+f22_p4+f22_p5 + plot_layout(ncol = 3)) /
+  (f22_p6+f22_p7+f22_p8+f22_p9+f22_p10 + plot_layout(ncol = 3)) /
+  plot_layout(guides = "collect") & theme(legend.position='bottom')
+
+final_plot_S22
+
+```
+
+```{r}
+#| label: figureS23
+#| fig.width: 7
+#| fig.height: 10
+#| dpi: 600
+#| fig-cap: | 
+#|   **Figure S23.** Multiverse p-value distributions belonging to the interaction effects involving unpredictability reported in Table 5 in the main text.
 The dashed vertical line depicts the cut-off of .05.
@@
 #| echo: false
-f23_p1 <- study1_expl_ssp_enh_variance_plot$rt_diff + labs(title = "RT difference", tag = "A", y = "", fill = "") 
-f23_p2 <- study1_expl_ssp_enh_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
-f23_p3 <- study1_expl_ssp_enh_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none")
-f23_p4 <- study1_expl_ssp_enh_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none")
-f23_p5 <- study1_expl_ssp_enh_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+f24_p1 <- study1_expl_ssp_enh_variance_plot$rt_diff + labs(title = "RT difference", tag = "A", y = "", fill = "") 
+f24_p2 <- study1_expl_ssp_enh_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
+f24_p3 <- study1_expl_ssp_enh_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none")
+f24_p4 <- study1_expl_ssp_enh_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none")
+f24_p5 <- study1_expl_ssp_enh_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
 
-f23_p6 <- study1_expl_ssp_deg_variance_plot$rt_diff + labs(title = "RT difference", tag = "B", y = "") + guides(fill = "none") 
-f23_p7 <- study1_expl_ssp_deg_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
-f23_p8 <- study1_expl_ssp_deg_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
-f23_p9 <- study1_expl_ssp_deg_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
-f23_p10 <- study1_expl_ssp_deg_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
+f24_p6 <- study1_expl_ssp_deg_variance_plot$rt_diff + labs(title = "RT difference", tag = "B", y = "") + guides(fill = "none") 
+f24_p7 <- study1_expl_ssp_deg_variance_plot$p_flanker + labs(title = "Perceptual input", y = "") + guides(fill = "none")
+f24_p8 <- study1_expl_ssp_deg_variance_plot$interference_flanker + labs(title = "Interference", y = "") + guides(fill = "none") 
+f24_p9 <- study1_expl_ssp_deg_variance_plot$a_flanker + labs(title = "Boundary separation", y = "") + guides(fill = "none") 
+f24_p10 <- study1_expl_ssp_deg_variance_plot$t0_flanker + labs(title = "Non-decision time", y = "") + guides(fill = "none")
 
-align_patches(f23_p1,f23_p2,f23_p3,f23_p4,f23_p5,f23_p6,f23_p7,f23_p8,f23_p9,f23_p10)
+align_patches(f24_p1,f24_p2,f24_p3,f24_p4,f24_p5,f24_p6,f24_p7,f24_p8,f24_p9,f24_p10)
 ```
@@
 ```{r}
-#| label: figureS23
+#| label: figureS24
 #| fig.width: 7
@@
 #| fig-cap: | 
-#|   **Figure S23.** Multiverse explained variance of each data cleaning decision belonging to the interaction effects involving unpredictability reported in Table 5 in the main text.
+#|   **Figure S24.** Multiverse explained variance of each data cleaning decision belonging to the interaction effects involving unpredictability reported in Table 5 in the main text.
 Panel A: Analyses comparing the enhanced condition to the standard condition.
 Panel B: Analyses comparing the degraded condition to the standard condition.
-final_plot_S23 <- 
-  (f23_p1+f23_p2+f23_p3+f23_p4+f23_p5 + plot_layout(ncol = 3)) /
-  (f23_p6+f23_p7+f23_p8+f23_p9+f23_p10 + plot_layout(ncol = 3)) /
+final_plot_S24 <- 
+  (f24_p1+f24_p2+f24_p3+f24_p4+f24_p5 + plot_layout(ncol = 3)) /
+  (f24_p6+f24_p7+f24_p8+f24_p9+f24_p10 + plot_layout(ncol = 3)) /
   plot_layout(guides = "collect") & theme(legend.position='bottom')
 
-final_plot_S23
+final_plot_S24
 
@@
 
-Figure S24 and Figure S25 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Figure 2 in the main text.
+Figure S25 and Figure S26 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Figure 2 in the main text.
 
 ```{r}
-#| label: figureS24
+#| label: figureS25
 #| fig.width: 7
@@
 #| fig-cap: | 
-#|   **Figure S24.** Multiverse p-value distributions belonging to the associations between violence exposure with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 2 in the main text.
+#|   **Figure S25.** Multiverse p-value distributions belonging to the associations between violence exposure with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 2 in the main text.
 (
@@
 ```{r}
-#| label: figureS25
+#| label: figureS26
 #| fig.width: 7
@@
 #| fig-cap: | 
-#|   **Figure S25.** Multiverse explained variance of each data cleaning decision belonging to the associations between violence exposure with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 2 in the main text.
+#|   **Figure S26.** Multiverse explained variance of each data cleaning decision belonging to the associations between violence exposure with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 2 in the main text.
 (
@@
 
-Figure S26 and Figure S27 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Figure 3 in the main text.
+Figure S27 and Figure S28 present *p*-distributions and the explained variance of each data cleaning decision in the variation in effect sizes for the results presented in Figure 3 in the main text.
 
 ```{r}
-#| label: figureS26
+#| label: figureS27
 #| fig.width: 7
@@
 #| fig-cap: | 
-#|   **Figure S26.** Multiverse p-value distributions belonging to the associations between unpredictability with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 3 in the main text.
+#|   **Figure S27.** Multiverse p-value distributions belonging to the associations between unpredictability with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 3 in the main text.
 (
@@
 ```{r}
-#| label: figureS27
+#| label: figureS28
 #| fig.width: 7
@@
 #| fig-cap: | 
-#|   **Figure S27.** Multiverse explained variance of each data cleaning decision belonging to the associations between unpredictability with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 3 in the main text.
+#|   **Figure S28.** Multiverse explained variance of each data cleaning decision belonging to the associations between unpredictability with perceptual input and interference in the Pilot, Study 1, Study 2, and pooled across all studies, as reported in Figure 3 in the main text.
 (

### 2024-03-26 manuscript/manuscript.qmd
Align manuscript with journal requirements

@@
 
-#### Stefan Vermeent^1,2^, Ethan S. Young^1^, Jean-Louis van Gelder^2^, & Willem E. Frankenhuis^1,2,3^
+#### Stefan Vermeent^a,b^, Ethan S. Young^a^, Jean-Louis van Gelder^b^, & Willem E. Frankenhuis^a,b,c^
 
-#### ^1^ Department of Psychology, Utrecht University, Utrecht, The Netherlands
+#### ^a^ Department of Psychology, Utrecht University, Utrecht, The Netherlands
 
-#### ^2^ Max Planck Institute for the Study of Crime, Security, and Law, Freiburg, Germany
+#### ^b^ Max Planck Institute for the Study of Crime, Security, and Law, Freiburg, Germany
 
-#### ^3^ Evolutionary and Population Biology, Institute for Biodiversity and Ecosystem Dynamics, University of Amsterdam, Amsterdam, the Netherlands
+#### ^c^ Evolutionary and Population Biology, Institute for Biodiversity and Ecosystem Dynamics, University of Amsterdam, Amsterdam, the Netherlands
+
+<br>
+
+# Corresponding author
+
+Correspondence concerning this article should be addressed to Stefan Vermeent, Department of Psychology, Utrecht University, Heidelberglaan 1, 3584 CS Utrecht, The Netherlands.
+Email: p.c.s.vermeent@gmail.com / p.c.s.vermeent@uu.nl.
+
+# Data Statement
+
+All scripts, materials, and data supporting the results presented here are available on the article's GitHub repository [(https://stefanvermeent.github.io/attention_project/)](https://stefanvermeent.github.io/attention_project/).
+
+# Funding Statement
+WEF’s contributions have been supported by the Dutch Research Council (V1.Vidi.195.130) and the James S. McDonnell Foundation (https://doi.org/10.37717/220020502).
+
+# Author contributions
+
+**Stefan Vermeent:** Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Project administration, Data curation, Visualization, Writing - original draft, Writing - review & editing.
+**Ethan S. Young:** Conceptualization, Methodology, Supervision, Writing - review & editing.
+**Jean-Louis van Gelder:** Conceptualization, Funding acquisition, Methodology, Supervision, Writing - review & editing.
+**Willem E. Frankenhuis:** Conceptualization, Funding acquisition, Methodology, Supervision, Writing - review & editing.
+
+\pagebreak
+
+# Abstract
+
+Previous research has shown that people who grew up in adverse conditions tend to perform worse on cognitive tasks like the Flanker, which suggests that they have more difficulty inhibiting distractions.
+Across an online Pilot and two online follow-up studies, we used Drift Diffusion Modeling to better understand performance differences on the Flanker in association with childhood adversity. 
+Neither exposure to violence nor unpredictability were associated with inhibition.
+In contrast, although mixed, results suggested that exposure to violence and unpredictability were associated with lower strength of perceptual input; that is, how well someone can process the arrows in general.
+Finally, people exposed to adversity had a more holistic processing style, and this style was associated with lower strength of perceptual input.
+Taken together, our findings underscore that researchers should be cautious when drawing inferences about inhibition abilities in people exposed to adversity based on response times alone.
+
+*Key-words:* childhood adversity, inhibition, Flanker, Drift Diffusion Modeling
 
@@
 Although short-term mindsets are associated with exposure to adversity [@ganschow_2023], it is unclear how they are associated with performance on attention tasks.
-We explored bivariate correlations between two indicators of short-term mindsets (impulsivity and future orientation) and SSP parameters of the Flanker (for more information on the measures, see section 1 of the supplemental materials).
+We explored bivariate correlations pooled across all studies between two indicators of short-term mindsets (impulsivity and future orientation) and SSP parameters of the Flanker (for more information on the measures, see section 1 of the supplemental materials).
 
-See Table SX for an overview of the correlations.
+See Table S2 for an overview of the correlations.
 Impulsivity was negatively associated with the strength of perceptual input (*r* = -.07, *p* = .004) and positively associated with interference (*r* = .09, *p* = .005). 
@@
 Across one pilot and two main studies, we tested how adversity was associated with performance on different attention tasks.
-The Pilot study compared performance on a Cued Attention Task, Change Detection Task, and a Flanker.
+The Pilot compared performance on a Cued Attention Task, Change Detection Task, and a Flanker.
 Two follow-up studies focused on the Flanker, with Study 2 also including a Global-Local Task.
@@
 
+# Glossary
+
+**Adversity:** prolonged exposures to intense stress; for instance, resulting from abuse, neglect, and poverty.
+
+<br>
+<br>
+
+**Boundary separation:** Parameter from the Drift Diffusion Model and Shrinking Spotlight Model. Provides a measure of a person's level of response caution on binary decision-making tasks.
+
+<br>
+<br>
+
+**Developmental adaptation:** A process that tailors people to the demands of their environments based on their experiences.
+
+<br>
+<br>
+
+**Drift Diffusion Model:** A formal cognitive model that estimates cognitive processes at different stages of the decision-making process for speeded binary decision-making tasks.
+It represents decision-making on binary decision-making tasks as a process in which people accumulate information until one response is sufficiently favored over the other.
+
+<br>
+<br>
+
+**Drift rate:** Parameter from the Drift Diffusion Model. Provides a measure of a person's speed of information accumulation on binary
+
+<br>
+<br>
+
+**Inhibition:** A person's ability to ignore task-irrelevant distractors in favor of task-relevant information.
+Operationalized in the Shrinking Spotlight Model as the initial attention width over all stimuli (i.e., target and distractors) divided by the rate at which attention is narrowed down to the central target.
+
+<br>
+<br>
+
+**Multiverse analysis:** An analysis technique that systematically and transparently assesses the influence of arbitrary data cleaning decisions on analysis results.
+
+<br>
+<br>
+
+**Non-decision time:** Parameter from the Drift Diffusion Model and Shrinking Spotlight Model.
+Provides a measure of the time it takes a person to prepare for the task at the start of the trial (before information processing) and the time it takes to execute a response (after a response boundary has been reached) on binary decision-making tasks.
+
+<br>
+<br>
+
+**Perceptual input:** Parameter from the Shrinking Spotlight Model of Flanker performance. Provides a measure of how well a person can process the Flanker stimuli in general.
+
+<br>
+<br>
+
+**Shrinking Spotlight Model:** An extension of the standard Drift Diffusion Model to account for attention processes on the Flanker.
+
+\pagebreak
+
 # References {#refs}

### 2024-03-26 preregistrations/2_study1/scripts/1_data_prep/1_create_scales.R

@@ -521,7 +521,7 @@ self_report <-
     by = "id"
   ) |> 
   select(
-    id, meta_start, meta_captcha, meta_resolution_ratio, meta_resolution_height, dems_edu, dems_class_current, matches("^(chaos|unp|change|quic|unp_comp|violence|vio_comp|fighting|ses|fos|depression|impuls|dems_age|dems_sex|dems_gender|att_check01|att_check02|att_getup|att_interrupted|att_noise|attention)")
+    id, meta_start, meta_captcha, meta_resolution_ratio, meta_resolution_height, dems_edu, dems_class_current, matches("^(chaos|unp|change|quic|unp_comp|violence|vio_comp|fighting|ses|fos|depression|impuls|dems_age|dems_sex|dems_gender|dems_ethnicity|dems_ethnicity_mixed|att_check01|att_check02|att_getup|att_interrupted|att_noise|attention)")
   )
 
 codebook <- create_codebook(self_report) %>%

### 2024-03-27 manuscript/manuscript.qmd
Create anonymized version of manuscript for peer review

@@
 
-All scripts, materials, and data supporting the results presented here are available on the article's GitHub repository [(https://stefanvermeent.github.io/attention_project/)](https://stefanvermeent.github.io/attention_project/).
+All scripts, materials, and data supporting the results presented here are available on the article's GitHub repository [ANONYMIZED FOR REVIEW].
 
@@
 
-Previous research has shown that people who grew up in adverse conditions tend to perform worse on cognitive tasks like the Flanker, which suggests that they have more difficulty inhibiting distractions.
-Across an online Pilot and two online follow-up studies, we used Drift Diffusion Modeling to better understand performance differences on the Flanker in association with childhood adversity. 
+Previous research has shown that people who grew up in adverse conditions tend to be slower on the Flanker Task, suggesting difficulty inhibiting distractions.
+However, this pattern might result from slower general cognitive processes (e.g., reduced general processing speed), rather than the specific ability of inhibition.
+We used Drift Diffusion Modeling in three studies---one pilot and two confirmatory studies---to better understand associations of adversity exposures with Flanker performance. 
 Neither exposure to violence nor unpredictability were associated with inhibition.
-In contrast, although mixed, results suggested that exposure to violence and unpredictability were associated with lower strength of perceptual input; that is, how well someone can process the arrows in general.
-Finally, people exposed to adversity had a more holistic processing style, and this style was associated with lower strength of perceptual input.
-Taken together, our findings underscore that researchers should be cautious when drawing inferences about inhibition abilities in people exposed to adversity based on response times alone.
+In contrast, although mixed, exposure to violence and unpredictability were associated with lower strength of perceptual input; that is, how well someone can process the arrows in general.
+Finally, lower strength of perceptual input was linked to a tendency to process information more holistically, focusing less on individual details.
+Thus, researchers should be cautious when drawing inferences about inhibition abilities in people exposed to adversity based on response times alone.
 
@@
 
-We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see <https://github.com/stefanvermeent/attention_project/preregistrations>).
+We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see [ANONYMIZED FOR REVIEW].
 For each study, we preregistered primary (i.e., hypothesis-driven) and exploratory analyses.
@@
 
-We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the minimally required number of participants for standardized regression coefficients of 0.10 and 0.15 (for details and simulation code, see ([https://github.com/stefanvermeent/attention_project/preregistrations](https://github.com/stefanvermeent/attention_project/preregistrations)).
+We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the minimally required number of participants for standardized regression coefficients of 0.10 and 0.15 (for details and simulation code, see [ANONYMIZED FOR REVIEW]).
 Power was \> .80 for adversity x task condition interactions with *N* = 450 or more.
@@
 **Multiverse analysis.** We included the same decisions in the multiverse as in the previous studies.
-However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, see <https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md>).
+However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, [ANONYMIZED FOR REVIEW]).
 See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
@@
 
-**Adversity:** prolonged exposures to intense stress; for instance, resulting from abuse, neglect, and poverty.
+**Adversity:** Prolonged exposures to intense stress; for instance, resulting from abuse, neglect, and poverty.
 
@@
 
-**Boundary separation:** Parameter from the Drift Diffusion Model and Shrinking Spotlight Model. Provides a measure of a person's level of response caution on binary decision-making tasks.
+**Boundary separation:** Parameter of the Drift Diffusion Model and Shrinking Spotlight Model.
+Measures the amount of information a person requires before making a decision, determining the speed-accuracy trade-off (e.g., sacrificing speed in favor of higher accuracy).
 
@@
 **Drift Diffusion Model:** A formal cognitive model that estimates cognitive processes at different stages of the decision-making process for speeded binary decision-making tasks.
-It represents decision-making on binary decision-making tasks as a process in which people accumulate information until one response is sufficiently favored over the other.
+It represents decision-making as a process in which people accumulate information until one response is sufficiently favored over the other.
 
@@
 
-**Drift rate:** Parameter from the Drift Diffusion Model. Provides a measure of a person's speed of information accumulation on binary
+**Drift rate:** Parameter of the Drift Diffusion Model. Measures a person's speed of information accumulation on binary decision-making tasks.
 
@@
 **Inhibition:** A person's ability to ignore task-irrelevant distractors in favor of task-relevant information.
-Operationalized in the Shrinking Spotlight Model as the initial attention width over all stimuli (i.e., target and distractors) divided by the rate at which attention is narrowed down to the central target.
+Operationalized in the Shrinking Spotlight Model as the initial attention width over all stimuli (i.e., target and distractors), divided by the rate at which attention is narrowed down to the central target.
 
@@
 
-**Multiverse analysis:** An analysis technique that systematically and transparently assesses the influence of arbitrary data cleaning decisions on analysis results.
+**Multiverse analysis:** An analysis technique that systematically and transparently evaluates the influence of arbitrary data-cleaning decisions on statistical outcomes.
 
@@
 
-**Non-decision time:** Parameter from the Drift Diffusion Model and Shrinking Spotlight Model.
-Provides a measure of the time it takes a person to prepare for the task at the start of the trial (before information processing) and the time it takes to execute a response (after a response boundary has been reached) on binary decision-making tasks.
+**Non-decision time:** Parameter of the Drift Diffusion Model and Shrinking Spotlight Model.
+Measures the time it takes a person to prepare for the task at the start of the trial (before information processing) and the time it takes to execute a response (after a response boundary has been reached) on binary decision-making tasks.
 
@@
 
-**Perceptual input:** Parameter from the Shrinking Spotlight Model of Flanker performance. Provides a measure of how well a person can process the Flanker stimuli in general.
+**Perceptual input:** Parameter from the Shrinking Spotlight Model of Flanker performance. Measures how well a person can process the Flanker stimuli in general.
 

### 2024-03-28 manuscript/manuscript_blinded.qmd
anonymize GitHub links

--- 2024-03-27 manuscript/manuscript.qmd
@@
 
-#### **Childhood adversity is not associated with lowered inhibition, but slower perceptual processing: A Drift Diffusion Model analysis**
-
-#### Stefan Vermeent^a,b^, Ethan S. Young^a^, Jean-Louis van Gelder^b^, & Willem E. Frankenhuis^a,b,c^
-
-#### ^a^ Department of Psychology, Utrecht University, Utrecht, The Netherlands
-
-#### ^b^ Max Planck Institute for the Study of Crime, Security, and Law, Freiburg, Germany
-
-#### ^c^ Evolutionary and Population Biology, Institute for Biodiversity and Ecosystem Dynamics, University of Amsterdam, Amsterdam, the Netherlands
-
-<br>
-
-# Corresponding author
-
-Correspondence concerning this article should be addressed to Stefan Vermeent, Department of Psychology, Utrecht University, Heidelberglaan 1, 3584 CS Utrecht, The Netherlands.
-Email: p.c.s.vermeent@gmail.com / p.c.s.vermeent@uu.nl.
-
-# Data Statement
-
-All scripts, materials, and data supporting the results presented here are available on the article's GitHub repository [ANONYMIZED FOR REVIEW].
-
-# Funding Statement
-WEF’s contributions have been supported by the Dutch Research Council (V1.Vidi.195.130) and the James S. McDonnell Foundation (https://doi.org/10.37717/220020502).
-
-# Author contributions
-
-**Stefan Vermeent:** Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Project administration, Data curation, Visualization, Writing - original draft, Writing - review & editing.
-**Ethan S. Young:** Conceptualization, Methodology, Supervision, Writing - review & editing.
-**Jean-Louis van Gelder:** Conceptualization, Funding acquisition, Methodology, Supervision, Writing - review & editing.
-**Willem E. Frankenhuis:** Conceptualization, Funding acquisition, Methodology, Supervision, Writing - review & editing.
-
-\pagebreak
-
 # Abstract
 
-Previous research has shown that people who grew up in adverse conditions tend to be slower on the Flanker Task, suggesting difficulty inhibiting distractions.
-However, this pattern might result from slower general cognitive processes (e.g., reduced general processing speed), rather than the specific ability of inhibition.
-We used Drift Diffusion Modeling in three studies---one pilot and two confirmatory studies---to better understand associations of adversity exposures with Flanker performance. 
-Neither exposure to violence nor unpredictability were associated with inhibition.
-In contrast, although mixed, exposure to violence and unpredictability were associated with lower strength of perceptual input; that is, how well someone can process the arrows in general.
-Finally, lower strength of perceptual input was linked to a tendency to process information more holistically, focusing less on individual details.
-Thus, researchers should be cautious when drawing inferences about inhibition abilities in people exposed to adversity based on response times alone.
+It is well-established that individuals who grew up in adverse conditions tend to be slower on the Flanker Task. 
+This finding is typically interpreted to reflect difficulty inhibiting distractions. 
+However, it might result from slower general cognitive processes (e.g., reduced general processing speed), rather than the specific ability of inhibition. 
+We used Drift Diffusion Modeling in three online studies (total N = 1560) with young adults to understand associations of adversity with Flanker performance. 
+We find no associations between exposure to violence and unpredictability with inhibition. 
+Yet, although mixed, violence and unpredictability exposure were associated with lower strength of perceptual input--—how well someone can process target and distractor information alike. 
+Finally, people with lower strength of perceptual input processed information more holistically, focusing less on details. 
+Thus, lowered Flanker performance does not necessarily imply lowered inhibition ability. 
+Cognitive modeling might reveal a different picture of abilities in adverse conditions.
 
@@
 
-We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see [ANONYMIZED FOR REVIEW].
+We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see <https://anonymous.4open.science/r/CogDev_AnonLink>).
 For each study, we preregistered primary (i.e., hypothesis-driven) and exploratory analyses.
@@
 
-Participants were 565 US-based individuals aged between 18 and 30 recruited on Prolific Academic ([https://www.prolific.co](https://www.prolific.co)) (See Table 1 for demographic data).
+Participants were 565 people from the United States aged between 18 and 30 recruited on Prolific Academic ([https://www.prolific.co](https://www.prolific.co)) (See Table 1 for demographic data).
 The sample was balanced on sex.
@@
 
-We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the minimally required number of participants for standardized regression coefficients of 0.10 and 0.15 (for details and simulation code, see [ANONYMIZED FOR REVIEW]).
+We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the minimally required number of participants for standardized regression coefficients of 0.10 and 0.15 (for details and simulation code, see <https://anonymous.4open.science/r/CogDev_AnonLink/preregistrations/1_pilot/scripts>).
 Power was \> .80 for adversity x task condition interactions with *N* = 450 or more.
@@
 **Multiverse analysis.** We included the same decisions in the multiverse as in the previous studies.
-However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, [ANONYMIZED FOR REVIEW]).
+However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, <https://anonymous.4open.science/r/CogDev_AnonLink/preregistrations/3_study2>).
 See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
@@
 
-**Boundary separation:** Parameter of the Drift Diffusion Model and Shrinking Spotlight Model.
-Measures the amount of information a person requires before making a decision, determining the speed-accuracy trade-off (e.g., sacrificing speed in favor of higher accuracy).
+**Boundary separation:** Parameter of the Drift Diffusion Model and Shrinking Spotlight Model. Measures the amount of information a person requires before making a decision (i.e., response caution).
 

### 2024-03-28 manuscript/titlepage.qmd
anonymize GitHub links

--- 2024-03-26 manuscript/manuscript.qmd
@@
 
-```{r setup, include=FALSE}
-# Load libraries
-library(dplyr)
-library(tidyr)
-library(purrr)
-library(furrr)
-library(readr)
-library(magrittr)
-library(officer)
-library(flextable)
-library(here)
-library(pwr)
-
-# set up chunk options
-knitr::opts_chunk$set(
-  echo = F,
-  fig.align = "center",
-  fig.pos = "!t", 
-  out.extra = "",
-  fig.show = "asis",
-  message = FALSE,
-  warning = FALSE
-)
-
-# set up flextable for tables
-set_flextable_defaults(
-  font.family = "Times", 
-  font.size = 10,
-  font.color = "black",
-  line_spacing = 1,
-  padding.bottom = 1, 
-  padding.top = 1,
-  padding.left = 1,
-  padding.right = 1
-)
-
-# Source necessary objects
-power_linear      <- read_csv("../data/1_pilot/simulation/power_linear_model.csv") %>% mutate(power = round(power, 0))
-power_mixed       <- read_csv("../data/1_pilot/simulation/power_mixed_model.csv") %>% mutate(power = round(power, 0))
-
-load("pilot_staged_results.RData")
-load("study1_staged_results.RData")
-load("study2_staged_results.RData")
-load("pooled_staged_results.Rdata")
-```
-
 #### **Childhood adversity is not associated with lowered inhibition, but slower perceptual processing: A Drift Diffusion Model analysis**
 
-#### Stefan Vermeent^1,2^, Ethan S. Young^1^, Jean-Louis van Gelder^2^, & Willem E. Frankenhuis^1,2,3^
+#### Stefan Vermeent^a,b^, Ethan S. Young^a^, Jean-Louis van Gelder^b^, & Willem E. Frankenhuis^a,b,c^
 
-#### ^1^ Department of Psychology, Utrecht University, Utrecht, The Netherlands
+#### ^a^ Department of Psychology, Utrecht University, Utrecht, The Netherlands
 
-#### ^2^ Max Planck Institute for the Study of Crime, Security, and Law, Freiburg, Germany
+#### ^b^ Max Planck Institute for the Study of Crime, Security, and Law, Freiburg, Germany
 
-#### ^3^ Evolutionary and Population Biology, Institute for Biodiversity and Ecosystem Dynamics, University of Amsterdam, Amsterdam, the Netherlands
-
-\pagebreak
-
-# Childhood adversity is not associated with lowered inhibition, but lower perceptual processing: A Drift Diffusion Model analysis
-
-The predominant view in developmental psychology is that exposure to adversity impairs cognitive abilities.
-This view is supported by decades of research showing that people living in high-adversity contexts tend to score lower on a variety of cognitive tests [@hackman_2010; @ursache_2016].
-Recent adaptation-based perspectives, however, have argued that people from adversity may also develop intact, or enhanced, abilities for solving problems in high-adversity contexts [@ellis_2017; @frankenhuis_2013].
-Adaptation- and deficit-based perspectives are considered complimentary.
-For instance, adversity may impair some cognitive processes, yet enhance others.
-Despite their compatibility, few studies have investigated how the interplay of impaired and enhanced abilities shapes performance.
-In this paper, across three preregistered online experiments, we used cognitive modeling to derive a process-level understanding of the association between childhood adversity and performance on the Flanker Task, a popular measure of cognitive control [@ridderinkhof_2021].
-
-## Attention in adverse conditions
-
-It is well-established that early-life adversity is associated with deficits in the ability to inhibit distracting, goal-irrelevant information [@hackman_2010; @ursache_2016].
-One of the leading paradigms in this literature is the Flanker Task [@eriksen_1974].
-On this task, participants typically see five arrows in a horizontal orientation, and are asked to indicate the direction of the central arrow.
-The flanking arrows point in the opposite direction on half of the trials, leading to interference that participants must inhibit.
-Slower performance on the Flanker has been documented for children and adults with lower childhood socioeconomic status [SES\; @farah_2006; @mezzacappa_2004; @noble_2005] and more environmental unpredictability [@fields_2021; @mittal_2015].
-These findings are typically interpreted as indicating a deficit in the ability to inhibit distractions.
-
-Nonetheless, some recent studies suggest that growing up in adversity may also be associated with improved abilities such as attention shifting [@fields_2021; @mittal_2015; @young_2022; but see @nweze_2021].
-Some studies found deficit patterns on the Flanker alongside enhancements on other aspects of attention within the same participants.
-For example, in one study, children with lower SES performed less well on the Flanker, but outperformed children from higher SES on orienting their attention to salient cues and, peripheral cues [@mezzacappa_2004].
-Similarly, children with more caregiver switches (an indicator of unpredictability) were found to perform less well on the Flanker, but outperformed children with fewer caregiver switches on shifting their attention between different task goals [@fields_2021].
-
-Performance on attention tasks could reflect developmental adaptation to adverse environments [@blair_2012; @dangiulli_2012; @frankenhuis_2020; @mittal_2015].
-In unpredictable or threatening conditions, the ability to detect salient peripheral information (e.g., distant noises or approaching individuals) could help to more quickly detect and act on potential threats.
-Over time, cognitive adaptations to such conditions could result in a general tendency to use a more diffuse scope of attention, leading to an enhanced ability to keep track of the broader environment.
-In line with this hypothesis, people with lower SES respond more strongly to auditory distractors [@giuliano_2018; @stevens_2009; @hao_2022] and are faster to orient their attention to peripheral visual information [@mezzacappa_2004].
-While potentially adaptive, a more diffuse scope of attention could come at the cost of lowered ability to ignore irrelevant distractors.
-This could compromise more long-term goal-directed behavior, especially in chaotic environments (e.g., a noisy classroom or a busy street).
-
-Thus, lowered performance on tasks like the Flanker could reflect either a cognitive impairment or a difference in attentional strategies.
-Distinguishing between these two possibilities is challenging for two reasons.
-First, few studies in the adversity literature have measured performance differences on different attention tasks within the same individual [@mezzacappa_2004; @mittal_2015].
-Thus, it is unclear whether lowered inhibition is related to enhanced processing of peripheral information in people from from adverse backgrounds.
-Second, performance on inhibition tasks is---beyond the ability to inhibit distractors---also influenced by other factors, such as a person's general processing speed and response caution [@hedge_2022; @loffler_2022].
-This means that lowered performance on inhibition tasks does not necessarily reflect inhibition difficulties.
-In other words, we should consider cognitive processes other than ability when drawing inferences based on inhibition tasks.
-
-## Using Drift Diffusion Modeling to estimate attention and processing styles
-
-An important issue, therefore, is that several processes are involved in performance on the Flanker, and standard assessments using raw performance measures (response times, accuracy rates) mostly fail to distinguish between them.
-For example, performance differences on the Flanker could indicate that someone experiences more (or less) flanker interference, generally processes less (or more) efficiently, or responds with less (or more) caution.
-To understand how adversity affects performance, we need to be able to separate the difference processes that make up performance.
-
-Formal cognitive models such as the Drift Diffusion Model [DDM\; @forstmann_2016; @ratcliff_1998; @ratcliff_2008; @ratcliff_2015; @wagenmakers_2009] provide a potential solution.
-The DDM estimates cognitive processes at different stages of the decision-making process (See Figure 1a).
-It represents decision-making on binary decision-making tasks as a process in which people accumulate information until one response is sufficiently favored over the other.
-These two response options are represented as opposing boundaries.
-One boundary corresponds to the correct response and the other to the incorrect response.
-When information accumulation reaches one of the two boundaries, the corresponding response is executed.
-
-The DDM translates trial-level response times (RTs) and accuracy into three distinct cognitive processes.
-The speed of information accumulation is captured in a parameter called the *drift rate*.
-Higher drift rates are associated with faster responses and higher mean accuracy.
-Response caution is modeled through the *boundary separation*; that is, the width between the two boundaries.
-Larger boundary separation is associated with larger RTs and higher accuracy (i.e., sacrificing speed to increase accuracy).
-Finally, *non-decision time* represents the time it takes to prepare for the task at the start of the trial (before information processing) and the time it takes to execute a response (after a response boundary has been reached).
-Longer non-decision times are associated with larger RTs, without influencing accuracy.
-
-The Shrinking Spotlight (SSP) model is an extension of the standard DDM to account for attention processes on the Flanker [@grange_2016; @white_2018a; @white_2018b; @white_2011].
-The SSP model assumes that attention resembles a spotlight that is normally distributed over the Flanker arrows (with a particular starting *attentional width*).
-Over time, people narrow their attention down to the central arrow (at a rate defined by the *shrinking rate*), thereby gradually decreasing interference from irrelevant information (See Figure 1b).
-Prior work has defined the amount of distractor *interference* by dividing the attentional width by the shrinking rate [@white_2018a].
-People may experience less interference either by starting with a narrower attentional width, and/or by more rapidly shrinking their attention down to the target arrow.
-Finally, performance is also influenced by the *perceptual input* strength; that is, how well someone can process the arrows in general.
-Note that typical interpretations of lowered raw Flanker performance are in terms of the amount of interference that someone experiences, and not in terms of the strength of perceptual input.
-Here, we are interested in how childhood adversity is associated with both interference and the strength of perceptual input.
+#### ^c^ Evolutionary and Population Biology, Institute for Biodiversity and Ecosystem Dynamics, University of Amsterdam, Amsterdam, the Netherlands
 
@@
 
-```{r}
-#| label: figure1
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 1.** A visual overview of the Drift Diffusion Model (DDM) and the Shrinking Spotlight Model (SSP).
-Panel A: The DDM assumes that people go through three distinct stages when they perform cognitive tasks with two forced response options.
-In a first preparation phase, they visually encode the relevant stimuli.
-In a second decision phase, people accumulate information in favor of one decision over the other (e.g., pressing left vs.
-right) until the decision boundary for either the correct or incorrect response is reached.
-Each jagged line represents this information accumulation process on a single trial.
-In a third execution phase, people execute the motor response.
-The model estimates four parameters that reflect distinct cognitive processes (printed in italic): (1) The drift rate represents the average rate of evidence accumulation towards the correct decision boundary and measures processing speed; (2) The non-decision time represents both the time spent encoding the stimuli and executing the response; (3) The boundary separation represents how far apart has “set” their decision boundaries, and is a measure of the person’s level of response caution; (4) The starting point represents the starting point of the decision process and measures the level of response bias (not considered here).
-Panel B: The SSP is an extension of the standard DDM including additional parameters to capture attentional processes involved in Flanker performance.
-Each stimulus arrow provides a certain strength of perceptual input (*p*).
-On incongruent trials, the perceptual input of flanking arrows is coded negatively (-*p*).
-Attention is assumed to be normally distributed over the arrows with a certain attentional width.
-Over time, attention is narrowed down toward the central arrow at a rate determined by the shrinking rate, thereby gradually lowering the interference caused by the flanking arrows.
-The drift rate in the SSP model is the sum of the perceptual input of each arrow multiplied by the attention allotted to each arrow.
-As attention for the flanking arrows decreases over time, the drift rate is assumed to increase over time (contrary to the standard DDM, which assumes a linear drift rate).
+# Corresponding author
 
-knitr::include_graphics("figures/fig1.png")
-```
+Correspondence concerning this article should be addressed to Stefan Vermeent, Department of Psychology, Utrecht University, Heidelberglaan 1, 3584 CS Utrecht, The Netherlands.
+Email: p.c.s.vermeent@gmail.com / p.c.s.vermeent@uu.nl.
 
-# Overview of studies
+# Data Statement
 
-The overarching goal of our studies is to understand the attentional and processing styles that people develop in conditions of adversity.
-We focus on measures of exposure to violence and environmental unpredictability.
-Previous research shows that these two types of adversity are on the one hand associated with improved attention shifting and working memory updating [@fields_2021; @mittal_2015; @young_2018; @young_2022], and on the other hand with lowered inhibition and working memory capacity [@fields_2021; @mittal_2015; @young_2018].
-We conducted three online studies: one pilot and two follow-up studies.
-Using cognitive modeling, we unpack Flanker performance in comparison to other tasks that require externally focused attention (Pilot), across visual processing manipulations (Study 1), and in terms of tendencies for holistic versus local processing (Study 2).
+All scripts, materials, and data supporting the results presented here are available on the article's GitHub repository [ANONYMIZED FOR REVIEW].
 
-We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see <https://github.com/stefanvermeent/attention_project/preregistrations>).
-For each study, we preregistered primary (i.e., hypothesis-driven) and exploratory analyses.
-The main text addresses the primary analyses involving violence exposure and the exploratory analyses involving environmental unpredictability.
-We describe the other exploratory analyses in the supplemental materials (section 2).
-For an overview of all deviations from the preregistrations, see section 4 of the supplemental materials.
+# Funding Statement
+WEF’s contributions have been supported by the Dutch Research Council (V1.Vidi.195.130) and the James S. McDonnell Foundation (https://doi.org/10.37717/220020502).
 
-# Pilot
+# Author contributions
 
-In the Pilot, our goal was to understand how childhood adversity relates to performance on tasks with different attentional demands.
-Participants completed self-report measures of childhood adversity and three cognitive tasks.
-These tasks measured inhibition, attention for peripheral cues, and attention for subtle changes.
-We expected violence exposure to be positively associated with a present-oriented attention style.
-Specifically, we expected participants with more violence exposure to be better at detecting peripheral stimuli and subtle changes.
-We expected this would result in a higher drift rate (faster speed of information accumulation) or shorter non-decision times (faster attention orientation, among other things), but not necessarily with differences in boundary separation (response caution).
-Second, we expected that participants with more violence exposure would be worse at ignoring distracting peripheral stimuli.
-We expected this would result in more experienced interference (as derived from the SSP model).
-
-## Methods
-
-### Participants {#participants}
-
-Participants were 565 US-based individuals aged between 18 and 30 recruited on Prolific Academic ([https://www.prolific.co](https://www.prolific.co)) (See Table 1 for demographic data).
-The sample was balanced on sex.
-We used the MacArthur's ladder, included in Prolific's prescreening battery, for assessing perceived SES to ensure about half of the sample came from lower-SES backgrounds (which we defined as a score of 4 or below).
-Participants were eligible if they spoke fluent English and did not report color-blindness.
-
-\pagebreak
-
-```{r}
-#| tab.id: table1
-#| results: markup
-demographics_table
-```
-
-<br>
-
-We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the minimally required number of participants for standardized regression coefficients of 0.10 and 0.15 (for details and simulation code, see ([https://github.com/stefanvermeent/attention_project/preregistrations](https://github.com/stefanvermeent/attention_project/preregistrations)).
-Power was \> .80 for adversity x task condition interactions with *N* = 450 or more.
-For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require *N* = `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`.
-We sampled 550 participants, anticipating a final sample of \~500 after exclusions.
-
-Prior to analyzing the data, we applied our preregistered exclusion criteria.
-First, we excluded participants who did not complete the full study; second, those who had incomplete data on any of the attention tasks; third, those who missed both attention check items; fourth, those who had suspicious response patterns (e.g., consistently endorsing high response options even though some items were reverse coded).
-Fifth, on a trial-level, we excluded any trials with reaction times \< 250 ms or \> 3500 ms [@ratcliff_2015].
-Participants with more than 10 trials removed were completely excluded from the analyses.\
-The final sample consisted of `r nrow(pilot_data)` participants.
-
-### Procedure {#procedure}
-
-Participants completed the experiment on their own laptop or desktop computer.
-Participants could refrain from answering any of the questionnaire items and were prompted with a warning once per page in case of missing items.
-
-After providing consent, participants completed three attention tasks.
-They were asked to move to a quiet room in the house, where they would be unlikely to be distracted by other people or outside noises.
-The order of the tasks was counterbalanced between subjects.
-At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs.
-The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deleeuw_2015].
-Participants were asked to hold a credit card (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the credit card.
-The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants.
-After successfully resizing the screen, participants completed all three tasks.
-During the task, the cursor was hidden from the screen to minimize distractions.
-After completing the attention tasks, participants completed the questionnaire battery and demographic questions.
-Finally, we asked participants whether they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.
-The full experiment took \~35 minutes.
-Participants were paid £4.38 when they reached the end of the experiment.
-
-### Cognitive measures {#cogmeasures}
-
-The attention tasks were programmed in JsPsych version 3.6.1 [@deleeuw_2015].
-For all materials and links to working versions of the tasks, see the Github repository.
-
-**Flanker Task.** The Flanker measures selective attention and response inhibition [@eriksen_1974].
-The Flanker began with eight practice trials, followed by 64 test trials.
-On each trial, participants saw a set of five arrows pointing either left or right.
-Participants were instructed to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right.
-All trials included black arrows against a white background.
-On the *congruent* trials (50%), the flanking arrows pointed in the same direction as the central arrow.
-On the *incongruent* trials (50%), the arrows pointed in the opposite direction.
-The arrows were randomly presented in the top-half or bottom-half of the screen.
-Each trial started with a fixation cross (1000 ms), after which the arrows were visible until a response was given.
-Participants received performance feedback during the practice trials, but not during the test block.
-
-**Cued Attention Task.** The Cued Attention Task was an adapted version of the Posner task, which measures the speed of attention for peripheral cues [@posner_1980].
-The Cued Attention Task began with eight practice trials, followed by 64 test trials.
-On each trial, a left- or right-pointing arrow was presented in one of eight random locations at 300 pixels from the center of the screen.
-Participants were instructed to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard.
-All trials included a black cue and arrow against a white background.
-On *cued* trials (50%), a cue ('\*') preceded the arrow in the exact same location.
-On *neutral* trials (50%), the cue preceded the arrow, but appeared at the center of the screen (not where the arrow would appear).
-Thus, the cue was perfectly predictive of the target location on cued trials, but provided no predictive information about the location of the arrow on neutral trials.
-Each trial started with a fixation cross at the center of the screen for 1000 ms. Then, the cue appeared for 250 ms, followed by the target arrow, until a response was given.
-
-**Change Detection Task.** The Change Detection Task measures the ability to detect subtle spatial changes.
-The Change Detection Task started with five practice trials followed by 50 test trials.
-On each trial, participants saw five colored circles (red, light-blue, dark-blue, yellow, and purple) against a gray background, each with a radius of 15 pixels.
-Each circle was located in a semi-random location around the central fixation cross.
-The location of each circle was sampled within a pre-specified area of 50-by-50 pixels to prevent overlap.
-Participants had 1000 ms to memorize the locations of the five circles.
-Then, the circles disappeared for 500 ms and then reappeared.
-On *change* trials (50%), one of the circles had moved to another location with a fixed displacement of 40 pixels in a 360 degree direction.
-On *no change* trials (50%), all circles were still in the same location.
-Participants were instructed to indicate whether all circles were still in the same location or one of the circles had changed location.
-The displacement of *one* circle was the only potential difference on each trial;
-
-**DDM/SSP parameters.** We analyzed the Flanker with the SSP model [@grange_2016; @white_2018a; @white_2018b; @white_2011], using the *flankr* package [@grange_2016].
-For each participant, the SSP provided us with estimates of: (1) strength of perceptual input (general quality of information that participants get from the arrows), (2) interference (initial attention width divided by the speed at which attention is narrowed down to the central arrow), (3) non-decision time (combination of speed of initial stimulus encoding and response execution), and (4) boundary separation (response caution).
-Our focus on interference as a ratio between attention width and shrinking rate was a deviation from the preregistration, as we initially planned to investigate both aspects of attention separately.
-However, we discovered that both parameters in isolation were unreliable because of an inherent trade-off, while the ratio did provide a stable measure.
-This was supported in a simulation study by @white_2018a showing that the ratio measure is reliable.
-See the supplemental materials (section 3) for a comparison between the preregistered and the updated analyses.
-
-For the Change Detection Task and the Cued Attention Task, we used a hierarchical Bayesian implementation of the standard DDM (HDDM).
-For each participant, the HDDM provided us with estimates of: (1) drift rate (speed of information accumulation; analogous to strength of perceptual input in the SSP model, except that drift rate is time-invariant), (2) non-decision time (same as SSP model), and (3) boundary separation (same as SSP model).
-The hierarchical Bayesian fitting procedure was a deviation from the preregistration, in which we planned to use Maximum Likelihood (ML) estimation.
-There were several issues with estimating DDM parameters for the Cued Attention task, which we later discovered were caused specifically by ML.
-An important difference between HDDM and ML is that HDDM uses the group information to inform individual parameter estimates, whereas ML models are fitted to each individual separately.
-This generally improves the accuracy of the estimation.
-See the supplemental materials (section 3) for an overview of the fit procedure and model fit across all models.
-
-### Self-report measures
-
-See Table 2 for bivariate correlations between measures of adversity across all studies.
-
-**Violence exposure.** We measured violence exposure using the Neighborhood Violence Scale (NVS) and two items assessing involvement in violence before age 13 [@frankenhuis_2018; @frankenhuis_deVries_2020; @young_2022].
-The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up").
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
-The items of the NVS were averaged together (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$violence`).
-Similarly, we averaged the scores on the two fighting items together.
-For the main analyses, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average.
-
-**Environmental unpredictability.** We included five measures of environmental unpredictability across different temporal scales: (1) the Questionnaire of Unpredictability in Childhood [QUIC\; @glynn_2019]; (2) the Perceived Childhood Unpredictability scale [@young_2018]; (3) the Confusion, Hubbub, and Order Scale [CHAOS\; @matheny_1995]; (4) stability of the family and social environment; and (5) objective indicators of unpredictability.
-All scales were adapted to refer to experiences before age 13.
-We computed a composite measure of all z-transformed unpredictability measures.
-See section 2 of the supplemental materials for an exploration of the factor structure of these measures.
-
-The QUIC captures environmental and household unpredictability.
-We made three preregistered changes to the original scale [@glynn_2019], to better align it with the other scales.
-First, all items were rated on a scale of 1 (never true) to 5 (very often true), except for four items referring to specific experiences (e.g., "I experienced changes in my custody arrangement").
-For these items, we adopted a response scale with the options "never", "only once", "a couple times", "several times", "many times".
-Second, quantifiers such as "frequently", "often", and "There was a period of time when [...]" were dropped to better match the response scale.
-Third, we excluded the item "My parents got divorced" because it did not fit the new response labels and this information was already captured by one of the items of the perceived unpredictability scale.
-Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$quic_total`).
-
-The perceived childhood unpredictability scale included eight items measuring perceived unpredictability before age 13 (e.g., "My family life was generally inconsistent and unpredictable from day-to-day").
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$unp`).
-
-The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late").
-All items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
-Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$chaos`).
-
-We included one additional scale to measure the stability of the family and social environment.
-On a scale of 1 (the same all the time) to 5 (constant and rapid changes), participants indicated how often the following aspects of their family and social environment changed before age 13: (1) economic status; (2) family environment; (3) childhood neighborhood environment; and (4) childhood school environment.
-
-Finally, we included four objective measures of unpredictability before age 13: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "How many romantic partners did your mother have (not counting your father)?"; 4) "How many romantic partners did your father have (not counting your mother)?".
-
-```{r}
-#| tab.id: table2
-#| results: markup
-iv_cor_pooled_table
-```
-
-<br>
-
-### Data analyses {#analysis_plan}
-
-**Multiverse analysis.** In an amendment to the preregistration, we quantified the robustness of our findings against six data cleaning decisions that may affect the robustness of online studies by using multiverse analysis, using the *multitool* package [@young_2023].
-Multiverse analysis allows for systematically evaluating the robustness of analyses across all combinations of different arbitrary data processing decisions [for details, see @giudice_2021; @simonsohn_2020; @steegen_2016].
-Specifically, we looked at the influence of including or excluding 1) participants who scored below 0.5 on a build-in bot-detection measure on Prolific (potentially indicating a bot); 2) participants who did not rescale their screen at the start of the experiment; 3) participants who did not enter fullscreen mode prior to starting the tasks; 4) participants who exited fullscreen mode at any point during the tasks; 5) participants who indicated high levels of noise in their environment; 6) participants who indicated extreme interruptions during the experiment.
-See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
-
-### Primary analyses
-
-For the Cued Attention Task and Flanker RTs, we used linear mixed effects models to test violence exposure x task condition (sum-coded) interactions on mean RTs and each DDM parameter.
-All mixed effects models included a random intercept for participants.
-For the Change Detection Task and Flanker SSP parameters, we used linear regression models to test the main effect of adversity on mean RTs and each DDM/SSP parameter.
-To meet model assumptions of normally distributed residuals, reaction times were log-transformed.
-Analyses involving interference (Flanker) and boundary separation (all tasks) parameters violated the assumption of normally distributed residuals.
-For boundary separation, we solved this using log-transformation.
-For interference, non-normality was caused by extreme outliers (\>3.2SD), which we excluded from the analyses.
-
-## Results and discussion
-
-Table 3 summarizes the results.
-More violence exposure was associated with lower strength of perceptual input under `r pilot_main_eff_ddm_list$Flanker_p$p_sum_Main`% of multiverse specifications (although the median 95% CI interval contained zero).
-We additionally found a significant main effect of violence exposure on interference under `r pilot_main_eff_ddm_list$Flanker_interference$p_sum_Main`% of multiverse specifications, such that more violence exposure was associated with less interference.
-This was contrary to our expectation that people exposed to adversity would have more difficulties dealing with interference from irrelevant distractors.
-
-Participants with more exposure to childhood violence were slower on the Cued Attention Task, which was mainly related to a higher level of response caution (boundary separation).
-On the Change Detection Task, more childhood violence exposure was associated with slower speed of information processing (drift rate) under `r pilot_main_eff_ddm_list$Change_v$p_sum_Main`% of multiverse specifications, but not with longer RTs.
-These results were not in line with our expectation that people from adversity would perform better on cognitive tasks that require a broad, present-focused attention style.
-
-<br>
-
-```{r}
-#| tab.id: table3
-#| results: markup
-pilot_main_eff_ddm_table |> 
-  border(i = 1, border.bottom = fp_border_default(), part = "header") 
-```
-
-<br>
-
-The pattern of findings on the Flanker was interesting for two reasons.
-First, the Flanker is a widely used task to assess the ability to inhibit irrelevant information, and people exposed to adversity typically show lowered performance.
-Our pilot results, though, suggest that lowered performance may not be caused by a reduced ability to inhibit distracting information.
-Instead, people exposed to adversity might have a lower strength of perceptual input, leading to slower and less efficient information processing.
-If true, these initial findings suggest that performance might be improved through interventions that increase the visual quality of stimuli.
-In Study 1, we aimed to replicate and extend these findings.
-
-# Study 1
-
-The goal of Study 1 was to follow up on the Pilot by manipulating the visual quality of information on the Flanker.
-Participants completed three versions: a standard version (similar to the Pilot), one with enhanced visual information, and one with degraded visual information.
-We again focused on childhood exposure to violence.
-Our first aim was to examine the robustness of our finding of improved interference control on the Flanker in relation to more adversity exposure in the pilot.
-We did so by analyzing the data of the standard condition, as well as by pooling the data of the Pilot and Study 1.
-Our second aim was to investigate whether manipulating visual information on the Flanker would influence performance for people with more violence exposure.
-
-We preregistered two potential data patterns and associated interpretations, without favoring one over the other *a priori*.
-First, the strength of perceptual input might be lower for people with more exposure to violence compared to people with less exposure to violence across all conditions.
-Second, lower performance on the standard version might reflect an adaptive trade-off towards cognitive functioning that is less affected by noise or perturbations, at a cost of lower overall performance [@giudice_2018].
-In that case, we would expect the strength of perceptual input to be influenced to a lesser extent across conditions for people with more exposure to violence than for people with less exposure to violence.
-As a result, they might not benefit as much from enhanced visual information, yet might be able to better maintain performance with degraded information.
-
-## Methods
-
-### Participants
-
-Participant recruitment was identical to the Pilot.
-In total, 567 people from the United States between the ages of 18 and 30 participated (See Table 1).
-We applied the same exclusion criteria as reported in the Pilot.
-The final sample consisted of `r nrow(study1_data)` participants.
-
-### Flanker Task
-
-We programmed the Flanker in JsPsych version 6.3.1 [@deleeuw_2015] with three conditions.
-Each condition consisted of eight practice trials, followed by 64 test trials.
-In the *standard* condition, the arrows were 40 pixels in size (0.4 inches) and had zero padding between them.
-In the *enhanced* condition, we increased the arrow size by 12.5% to 45 pixels (0.45 inches), and increased the space between the arrows to 5 pixels.
-This increased the width of the stimulus display by 50% with respect to the standard display.
-In the 'degraded' condition, sizes and space between arrows were the same as in the standard version, but all arrows were rotated 45$^\circ$ (in the same direction; that is, if the left flanker arrows pointed upwards, the right flanker arrows pointed downward).
-Participants completed each condition separately in different blocks, in randomized order.
-
-### Self-report measures
-
-The self-report measures were identical to those used in the Pilot.
-
-### Procedure
-
-The procedure was identical to the pilot study.
-The full experiment took approximately 30 minutes.
-Participants were paid £3.75 after they completed the full study.
-
-### Data analyses
-
-**Multiverse analysis.** We included the same arbitrary decisions in the multiverse analyses as in the Pilot.
-For the pooled analyses---i.e., joint analysis of the Pilot and the standard condition of Study 1---there was one minor change in how we included screen rescaling as a preprocessing decision in the multiverse.
-In Study 1, we changed the screen rescaling procedure by converting the initial size of the resize box to 300 pixels instead of 100 pixels.
-This way, the stimulus display would still be close to the intended size if participants did not engage in any resizing.
-However, this led to one important change for the pooled analysis: rescaling (yes or no) was included as an arbitrary exclusion decision in the multiverse analyses with four combinations: (1) exclude non-scalers in both studies; (2) include non-scalers in both studies; (3) exclude non-scalers in the Pilot, include non-scalers in Study 1; (4) include non-scalers in the Pilot, exclude non-scalers in Study 1.
-
-For each analysis, we report the median $\beta$s, 95% confidence intervals, and the proportion of *p*-values \< .05 across all analytic decisions.
-For the primary analyses, we used bootstrapping to compute the probability of obtaining an effect size at least as extreme as observed in the real data, conditioned on a true effect size of zero [for details, see @simonsohn_2020].
-See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
-
-**Primary analyses.** To address the first aim, we analyzed the data from the standard condition, as well as pooled the Flanker data of the Pilot and the current study.
-We ran separate linear models for each SSP parameter as well as RT difference scores with violence exposure as main predictor and study as covariate (effect-coded).
-To address the second aim, we analyzed the effect of violence exposure and Flanker condition type on performance using linear mixed effects models with a random intercept per participant.
-The five main dependent variables were mean RT difference and the SSP parameters: Perceptual input, boundary separation, non-decision time, and interference.
-For each outcome measure, we ran two separate models: one comparing the standard condition with the enhanced condition, and one comparing the standard condition with the degraded condition.
-In both models, condition was dummy-coded using the standard condition as the reference group.
-
-## Results and discussion
-
-### Standard Flanker performance
-
-Table 4 summarizes the multiverse results for the effects of violence exposure (primary analysis) and unpredictability (exploratory analysis).
-Unlike in the Pilot, we did not find any significant associations with violence exposure.
-In the exploratory analysis, there was a significant negative association between unpredictability and perceptual input (median $\beta$ = `r study1_expl_results_list$p_flanker$median_effect_Main`, 95% CI = `r study1_expl_results_list$p_flanker$CI`, `r study1_expl_results_list$p_flanker$p_sum` % of *p*s \<.05).
-
-```{r}
-#| tab.id: table4
-#| results: markup
-study1_results_table |> 
-  border(i = 1, border.bottom = fp_border_default(), part = "header") 
-```
-
-After pooling the data of the pilot study and Study 1, there was a negative association between violence exposure and interference (median $\beta$ = `r study1_pooled_results_list$interference_vio$median_effect`, 95% CI = `r study1_pooled_results_list$interference_vio$CI`, `r study1_pooled_results_list$interference_vio$p_sum` % of *p*s \<.05, bootstrapped *p* = `r study1_pooled_results_list$interference_vio$boot_p`).
-Violence exposure was associated with lower strength of perceptual input under `r study1_pooled_results_list$interference_vio$p_sum`% of multiverse specifications, but the bootstrapped *p*-value was not significant (median $\beta$ = `r study1_pooled_results_list$p_vio$median_effect`, 95% CI = `r study1_pooled_results_list$p_vio$CI`, bootstrapped *p* = `r study1_pooled_results_list$p_vio$boot_p`).
-We did not find other significant associations for either violence exposure or unpredictability.
-
-### Flanker conditions
-
-The main effects of task condition on the strength of perceptual input were in the expected direction: relative to the standard condition, the quality of perceptual input was higher in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$p_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$p_enhanced$condition_CI`, `r study1_condition_vio_results_list$p_enhanced$p_sum_Condition` % of *p*s \<.05) and lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$p_degraded$median_effect_Condition`, 95% CI = `r  study1_condition_vio_results_list$p_degraded$condition_CI`, `r study1_condition_vio_results_list$p_degraded$p_sum_Condition` % of *p*s \<.05).
-Interference was lower in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$interference_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_enhanced$condition_CI`, `r study1_condition_vio_results_list$interference_enhanced$p_sum_Condition` % of *p*s \<.05).
-Unexpectedly, interference was also lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$interference_degraded$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_degraded$condition_CI`, `r study1_condition_vio_results_list$interference_degraded$p_sum_Condition` % of *p*s \<.05), suggesting that the angle in the flanking arrows reduced interference, relative to the standard condition.
-However, none of the interaction effects for either violence exposure or unpredictability were significant.
-
-\pagebreak
-
-```{r}
-#| tab.id: table5
-#| results: markup
-study1_condition_results_table |> 
-  border(i = 1, border.bottom = fp_border_default(), part = "header") 
-```
-
-The results of the Pilot and Study 1 were inconsistent with regard to the association between adversity and interference, but hinted at two general patterns.
-First, violence exposure was not associated with *increased* interference; instead, we found either the opposite effect or no effect.
-Second, both violence exposure and unpredictability were associated with lowered strength of perceptual input, albeit inconsistently.
-These findings, if replicable, are intriguing as they would suggest that the common finding of lowered Flanker performance among people with more adversity exposure do not actually result from worse interference control---as typically inferred.
-Rather, such lowered performance would result from processes other than inhibition ability, such as slower general processing.
-Though interesting, our findings so far leave open the question why adversity might be negatively associated with perceptual input.
-This question was the focus of Study 2.
-
-# Study 2
-
-Study 2 set out to compare two explanations for the finding that people exposed to adversity tended to show lower strength of perceptual input on the Flanker.
-First, lowered strength of perceptual input in people exposed to adversity may indicate a difficulty in extracting relevant information (i.e., about their direction) from the arrows in general.
-Second, the difference in perceptual input may not be a cognitive deficit per se, but instead could be a signature of a difference in processing style---that is, a feature, and not a bug.
-People exposed to adversity may process information more holistically, focusing more on the configuration of pieces of information rather than individual pieces of information.
-On the Flanker, this would lower the depth of perceptual processing of any individual stimulus, thus resulting in lowered strength of perceptual input, as we observed in the Pilot and Study 1.
-
-We preregistered three aims focusing both on violence exposure and unpredictability.
-First, we expected to replicate our earlier findings that adversity was associated with lowered perceptual input and lower interference in people exposed to adversity.
-Second, we included a Global-Local Task to investigate the hypothesis---based on the findings of the Pilot and Study 1---that people with more adverse experiences would develop a more holistic style of information processing.
-Third, we planned to conduct a within-subjects analysis of Flanker and Global-Local performance to assess whether people with lowered perceptual input on the Flanker Task would also show a more global processing style (rather than a local processing style) on the Global-Local Task.
-
-## Methods
-
-### Participants
-
-Participants were 600 people from the United States between the ages of 18 and 30.
-Recruitment was identical to Study 1.
-We conducted a simulation-based power analysis for the planned linear mixed models with the Global Local Task (see GitHub).
-We determined that power of \> .80 for a standardized interaction effect of 0.06, with sigma (noise) set to 0.7 (comparable to observed sigmas in the first two studies) would require 550 participants.
-We recruited 600 participants, with the expectation to have a final sample of 550 participants after exclusions.
-We applied the same exclusion criteria as reported in the Pilot and Study 1.
-The final sample consisted of `r nrow(study2_data)` participants.
-
-### Measures
-
-The measures of childhood violence exposure and environmental unpredictability were identical to Study 1.
-The Flanker was identical to the standard version used in Study 1.
-
-*Global-Local Task*.
-The Global-Local Task is a measure of global-local processing [@navon_1977].
-Many different versions of this task exist in the literature.
-One key dimension on which they differ is whether the task measures focused attention (by cueing attention towards the global or local level prior to stimulus presentation) or divided attention (by having participants search for a target on both levels) [@lee_2023].
-Here, we use a version measuring divided attention, which allows measuring whether someone tends to have a more global versus local processing style [@hakim_2017; @lee_2023; @mckone_2010].
-
-Participants saw images of big, black letters (the global level) comprised of small letters (the local level)---so-called Navon images [@navon_1977]---against a white background.
-Participants first completed eight practice trials, after which they completed an additional 64 test trials.
-On each trial, participants searched for one of two target letters---an 'E' or 'H'---and indicated whether it was present on the global or local letter by pressing 'g' or 'l' on their keyboard, respectively.
-Each stimulus was 600 pixels high and 395 pixels wide and comprised of seven local letters vertically and five local letters horizontally.
-All stimuli consisted of combinations of the letters 'T', 'F', 'P', 'L', 'H', and 'E'.
-The target letters 'H' and 'E' were both present in each stimulus, but the other letters varied.
-The global and local level never contained the same letter.
-
-### Procedure
-
-The procedure was identical to Study 1.
-The full experiment took \~30 minutes.
-Participants were paid £4.50 when they reached the end of the experiment.
-
-### Data analyses
-
-**Multiverse analysis.** We included the same decisions in the multiverse as in the previous studies.
-However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, see <https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/preregistration_amendment.md>).
-See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
-
-**DDM estimation.** For the Flanker, we used the SSP [@grange_2016; @white_2018a; @white_2018b; @white_2011] using the same procedure as in Study 1.
-For the Global-Local Task, we used a hierarchical Bayesian DDM to fit the data using the *runjags* package [@denwood_2016].
-See the supplemental materials (Section 3) for more information about the procedure and model fit.
-
-We deviated from our preregistration regarding the preprocessing of Global-Local Task data.
-Specifically, we relaxed the low performance threshold as the task was more difficult than anticipated.
-These deviations are described in the supplemental materials (section 4).
-
-**Primary analyses.** We ran simple regressions for analyses involving only main effects (aim 1), and linear mixed effects models for analyses involving within-subject interactions (aim 2 and 3).
-To address aim 3 (within-subject interaction between Global-Local drift rate and Flanker strength of perceptual input), we further preprocessed the data in two steps.
-First, we computed a difference score of Global-Local drift rates by subtracting the drift rate on local trials from the drift rate on global trials (with higher scores reflecting relatively faster information processing on global trials).
-Second, we separately standardized the Flanker strength of perceptual input and Global-Local drift rate difference.
-We fitted linear mixed effects models with the standardized performance measures as the dependent variable, and adversity type, task (Flanker or Global-Local, sum-coded) and their interaction as independent variables.
-
-## Results and discussion
-
-Figure 2 and 3 summarize the multiverse results for the effects of violence exposure and unpredictability within Study 2 and pooled across all studies.
-In Study 2, violence exposure was negatively associated with strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.vio_comp$boot_p`), but not associated with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$boot_p`).
-Unpredictability was not associated with either strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.unp_comp$boot_p`), nor with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$boot_p`).
-
-In the pooled analysis, the results were similar for both types of adversity.
-Violence exposure was associated with lower strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.vio_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.vio_comp$boot_p`).
-Similarly, unpredictability was associated with a lower quality of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_list$p_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.unp_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_list$interference_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.unp_comp$boot_p`).
-
-```{r}
-#| label: figure2
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 2.** Multiverse results for the association between violence exposure with the strength of perceptual input and interference on the Flanker across all studies.
-Each panel depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-The top row depicts effect curves in the Pilot.
-The second row depicts effect curves in Study 1.
-The third row depicts effect curves in Study 2.
-The Fourth row depicts effect curves of the pooled analyses across all studies.
-knitr::include_graphics("figures/fig2.png")
-```
-
-<br>
-
-```{r}
-#| label: figure3
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 3.** Multiverse results for the association between unpredictability with the strength of perceptual input and interference on the Flanker across all studies.
-Each panel depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-The top row depicts effect curves in the Pilot.
-The second row depicts effect curves in Study 1.
-The third row depicts effect curves in Study 2.
-The Fourth row depicts effect curves of the pooled analyses across all studies.
-knitr::include_graphics("figures/fig3.png")
-```
-
-<br>
-
-### Global-Local Task performance
-
-There was a main effect of violence exposure on Global-Local drift rates, with more violence exposure being associated with slower speed of information processing ($\beta$~median~ = `r study2_aim2_results_list$Main_vio$median_effect`, `r study2_aim2_results_list$Main_vio$p_sum`% of *p*s \< .05, bootstrapped *p* `r study2_aim2_results_list$Main_vio$boot_p`).
-There also was a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_vio$median_effect`, `r study2_aim2_results_list$Condition_vio$p_sum`% of *p*s \< .05, bootstrapped *p* `r study2_aim2_results_list$Condition_vio$boot_p`).
-Finally, there was an interaction effect between violence exposure and task condition ($\beta$~median~ = `r study2_aim2_results_list$Interaction_vio$median_effect`, `r study2_aim2_results_list$Interaction_vio$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_vio$boot_p`).
-Simple slopes analyses revealed that participants with lower levels of violence exposure did not differ in speed of processing of global versus local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.Low$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.Low$p_sum`% of *p*s \< .05).
-In contrast, participants with higher levels of violence exposure processed global targets faster than local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.High$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.High$p_sum`% of *p*s \< .05).
-
-There was a significant main effect of unpredictability on drift rates, with more unpredictability being associated with slower speed of information processing, ($\beta$~median~ = `r study2_aim2_results_list$Main_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Main_unp$CI`, `r study2_aim2_results_list$Main_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Main_unp$boot_p`).
-We also found a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Condition_vio$CI`, `r study2_aim2_results_list$Condition_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Condition_unp$boot_p`).
-We did not find a significant unpredictability x task condition interaction effect ($\beta$~median~ = `r study2_aim2_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Interaction_unp$CI`, `r study2_aim2_results_list$Interaction_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_unp$boot_p`).
-
-### Within-subjects comparison of Flanker and Global-Local information processing
-
-There was no significant main effects for violence exposure (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`) nor for cognitive task (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`).
-There was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_vio$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_vio$CI`, `r study2_aim3_results_list$Interaction_vio$p_sum` % of *p*s \< .05, bootstrapped *p* `r study2_aim3_results_list$Interaction_vio$boot_p`) (See Figure 2).
-A simple slopes analysis revealed that people with higher levels of violence exposure showed lower strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$vio_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.Flanker$p_sum`% of *p*s \< .05), and showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$p_sum`% of *p*s \< .05).
-
-There was no significant main effect for unpredictability (bootstrapped *p* = `r study2_aim3_results_list$Task_unp$boot_p`).
-However, there was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_unp$CI`, `r study2_aim3_results_list$Interaction_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim3_results_list$Interaction_unp$boot_p`).
-A simple slopes analysis revealed that people with higher levels of unpredictability did not differ in their strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$unp_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.Flanker$p_sum` % of *p*s \< .05), but showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$p_sum`% of *p*s \< .05).
-
-```{r}
-#| label: figure4
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 4.** Multiverse results for the within-subjects comparison of Flanker and Global-Local information processing.
-Panel A depicts the multiverse interaction effects, with the thick black lines denoting the median slope and the thin lines denoting effects for each combination of arbitrary decisions.
-Blue thin lines indicate significant effects (*p* > .05), and grey thin lines indicate non-significant effects (*p* > .05).
-Panel B depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-See the main text for more information about the multiverse analyses.
-knitr::include_graphics("figures/fig4.png")
-```
-
-<br>
-
-To sum up, Study 2 provided additional support for the basic finding that violence exposure and unpredictability were associated with lower strength of perceptual input but not with differences in interference; with the caveat that the associations for unpredictability only showed up in pooled analyses.
-People with more exposure to violence and unpredictability also processed information more slowly on the Global-Local Task.
-In line with our expectations, childhood exposure to violence was associated with both lowered strength of perceptual input and a more holistic processing style.
-The same processing style was observed for participants with more exposure to unpredictability, although they did not show lowered strength of perceptual input.
-
-# Exploratory analyses
-
-We hypothesized that the potential adaptive benefits of a more diffuse scope of attention in adverse conditions might be linked to the notion of a *present-oriented attention style* [@frankenhuis_2016; @vangelder_2023].
-People with a present-oriented attention style (versus a more future-oriented attention style) are more geared towards processing information that is relevant for solving challenges and obtaining rewards in the here-and-now.
-A general tendency to be more attuned to the present (while disregarding the future) is sometimes referred to as a short-term mindset [@kubel_2023; @vangelder_2023], which also includes tendencies to be more impulsive, to more steeply discount future rewards, and to be more sensation-seeking.
-Although short-term mindsets are associated with exposure to adversity [@ganschow_2023], it is unclear how they are associated with performance on attention tasks.
-We explored bivariate correlations between two indicators of short-term mindsets (impulsivity and future orientation) and SSP parameters of the Flanker (for more information on the measures, see section 1 of the supplemental materials).
-
-See Table SX for an overview of the correlations.
-Impulsivity was negatively associated with the strength of perceptual input (*r* = -.07, *p* = .004) and positively associated with interference (*r* = .09, *p* = .005). 
-In addition, impulsivity was also associated with a more holistic information processing style (*r* = .11, *p* = .020). 
-Thus, more impulsive participants processed information less deeply and were more easily drawn to distractions, but this might partly be explained by a holistic information processing style.
-Similarly, future-orientation was positively associated with perceptual input (*r* = .09 *p* < .001)—--but not with interference (*p* = .112) —--on the Flanker Task, and was also associated with a more detail-oriented processing style (*r* = -.12, *p* = .011).
-Thus, more future-oriented participants processed information more deeply, which might partly be explained by a detail-oriented processing style.
-
-# General discussion
-
-We investigated how two dimensions of childhood adversity---violence exposure and environmental unpredictability---are related to differences in how people attend to and process information.
-Specifically, we hypothesized that exposure to adversity might lead to a present-oriented attention style that would facilitate rapidly detecting novel or changing information, yet which would interfere with ignoring distractors.
-Across one pilot and two main studies, we tested how adversity was associated with performance on different attention tasks.
-The Pilot study compared performance on a Cued Attention Task, Change Detection Task, and a Flanker.
-Two follow-up studies focused on the Flanker, with Study 2 also including a Global-Local Task.
-We leveraged DDM to estimate the processes underlying lowered and improved performance.
-This allowed us to investigate whether performance differences were associated with abilities (i.e., attention orientation, interference control, stimulus processing), or ability-irrelevant processes (e.g., stimulus encoding, response execution, response caution).
-Across all primary and exploratory analyses, we leveraged multiverse analysis to systematically assess the robustness of our findings against several uncontrollable aspects of the online assessment (e.g., distractions, fullscreen exits).
-
-### Main insights
-
-We found little to no support for the presence of a present-oriented attention style in people exposed to adversity.
-More childhood exposure to violence was associated with slower processing of subtle changes on the Change Detection Task and lower quality of perceptual input on the Flanker Task.
-It was not associated with speed of processing of peripheral information on the Cued Attention Task.
-Zooming in on the Flanker, our two main studies found mixed evidence for the hypotheses that violence exposure and unpredictability were associated with lower strength of perceptual input.
-This mixed evidence suggests that people with more exposure to these adversities process information less deeply, making it more difficult to make judgments about target and distractor information in equal measure.
-This was corroborated by the pooled analyses across studies, which found that both exposure to violence and unpredictability were associated with lower strength of perceptual input, but not with differences in the ability to inhibit distractors.
-This finding contradicts the standard deficit interpretation of lowered performance on inhibition tasks by people with more adversity exposure (discussed below).
-In addition, lowered strength of perceptual input was associated with a holistic processing style.
-Thus, we did not find evidence that people with more violence exposure have more difficulties with inhibiting task-irrelevant information.
-
-Our findings of the DDM decomposition of Flanker performance challenge previous interpretations based on raw performance.
-Previous studies have found that people exposed to adversity and/or low SES backgrounds have longer RTs on incongruent trials relative to congruent trials [@farah_2006; @fields_2021; @mezzacappa_2004; @mittal_2015; @noble_2005], which is commonly interpreted as an impaired ability to inhibit irrelevant information.
-This fits with adaptive hypotheses, as inhibition is assumed to be useful mostly in stable and predictable environment that afford long-term goal pursuit, but can be costly in unpredictable and potentially dangerous environments [@fields_2021; @mittal_2015; @daly_2005].
-Contrary to previous studies, we found little to no evidence for performance differences on the basis of raw RTs.
-In addition, our DDM analyses showed that performance differences on the Flanker are not driven by differences in interference control, but by more basic processes that are not typically considered when interpreting Flanker performance.
-
-Our findings align with a broader literature that is critical of the validity of the Flanker in particular, and that of cognitive control tasks more generally.
-As noted, several studies have failed to find coherent correlations between raw performance on different cognitive control tasks [e.g., @loffler_2022; @rey_mermet_2019; @rouder_2019; @stahl_2014].
-For example, previous research comparing several cognitive control tasks across different data sets using cognitive modeling found that shared variance between these tasks was mostly associated with processing speed and strategies (e.g., speed-accuracy trade-offs) [@hedge_2022].
-Moreover, the modeling parameters reflecting conflict processing (similar to interference in our study) were barely correlated.
-Similarly, previous work has shown that individual differences on common EF tasks---among which the Flanker Task---can be fully accounted for by general processing speed [@loffler_2022].
-This literature, together with the findings reported here, underscore that researchers should be cautious when drawing inferences about cognitive control abilities in people exposed to adversity based on raw RTs and performance on individual tasks.
-
-Finally, we showed that people exposed to adversity had a more holistic processing style, and that this style was associated with lower strength of perceptual input on the Flanker.
-This could mean that people with more adversity exposure processed the Flanker display more holistically; that is, focused less on individual arrows and more on the collection of arrows as a whole.
-One (tentative) interpretation is that in the absence of threatening or otherwise salient information, people with more exposure to adversity attend to and process information in the environment globally and less deeply.
-They might only shift to local processing of a single source of information if it seems threatening or otherwise salient [@shields_2015; @schwabe_2013].
-This would be consistent with research showing that growing up in a disadvantaged environment decreases the efficiency of the brain's (resting-state) salience network, which is in turn associated with lower raw performance on certain cognitive tasks [@cermakova_2023; @gellci_2019; @hilger_2017; @yuan_2012].
-This research also shows that in situations of acute stress, mental resources are reallocated to this salience network, increasing vigilance and facilitating adequate responding.
-Indeed, a few studies show that cognitive abilities that may be particularly relevant in adverse contexts---such as attention shifting and working memory updating---may be enhanced in people from adversity when they experience acute stress [@mittal_2015; @young_2018].
-
-### Strengths, limitations, and future directions
-
-Our study has three main strengths.
-First, each study included socioeconomically diverse participants.
-Second, the DDM allowed us to decompose performance in a more nuanced way than is possible with (typically used) raw performance scores.
-Third, the multiverse analyses provided a systematic overview of the robustness of our findings under different analytical decisions.
-Our study has three main limitations.
-First, all experiments were conducted online, which reduced control over people's testing environment, equipment, and behavior.
-Indeed, our results were the least robust against participants who skipped the screen-scaling procedure (to ensure the stimuli were adequately sized) and interruptions during the tasks, which are factors that are largely out of our control.
-Second, we deviated from our preregistrations in several ways in all studies, due to progressive insight.
-This decreased the severity of our statistical tests, and so this work would benefit from preregistered replications [@lakens_2023].
-
-Our findings suggest two main directions for future research.
-First, future studies could replicate and expand upon our finding that lower quality of information processing in people exposed to adversity is associated with a more holistic processing style.
-For example, future work could investigate whether people with more adversity exposure shift from holistic to a detail-oriented processing in situations of acute stress or otherwise salient information.
-Second, our results suggest that lower strength of perceptual input is likely the result of both processing styles, as well as of slower general processing.
-Future research could try to tease apart these sources using a within-subjects design simultaneously measuring inhibition, processing styles, and basic processing speed.
-Third, some research suggests that inhibition is not a unitary construct, instead distinguishing between response inhibition (which involves suppressing a prepotent response) and cognitive inhibition (which involves selective attention in the presence of distractors).
-Exposure to adversity might shape these two types of inhibition in different ways.
-For example, acute stress might impair performance on tasks of cognitive inhibition (of which the Flanker is an example) and enhances performance on tasks of response inhibition [for a meta-analysis, see @shields_2016; but see @dang_2017].
-Future work could assess inhibition more broadly, e.g., by including tasks that are hypothesized to require cognitive or response inhibition.
-
-### General conclusion
-
-We found that people with more childhood adversity exposure perform worse on the Flanker not because of an impairment in their ability to inhibit distracting information, but because of lower strength of perceptual input.
-Our results suggest that people with more adversity exposure are not worse at inhibiting distractions; rather, they do not seem to process information in the environment deeply unless it proves to be a reliable and important source of information.
-These findings challenge dominant interpretations, which infer an inhibition deficit from lowered performance.
-This is an important difference not just for theory development, but also for future interventions aimed at closing performance gaps.
-For example, when applied to school contexts, interventions based on an inhibition interpretation would focus on the learning environment, perhaps removing things from the classroom that could be distracting.
-In contrast, an intervention based on an information processing interpretation might instead focus on increasing the apparent relevance of the learning materials, perhaps by providing more repetition or by making the content more ecologically relevant [@young_2022].
-Thus, cognitive modeling can offer crucial insights for our understanding of cognitive abilities in adverse conditions.
-
-\pagebreak
-
-# References {#refs}
+**Stefan Vermeent:** Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Project administration, Data curation, Visualization, Writing - original draft, Writing - review & editing.
+**Ethan S. Young:** Conceptualization, Methodology, Supervision, Writing - review & editing.
+**Jean-Louis van Gelder:** Conceptualization, Funding acquisition, Methodology, Supervision, Writing - review & editing.
+**Willem E. Frankenhuis:** Conceptualization, Funding acquisition, Methodology, Supervision, Writing - review & editing.

### 2024-04-02 manuscript/abstract.qmd
final tweaks to manuscript files for submission

--- 2024-03-28 manuscript/manuscript_blinded.qmd
@@
 
-```{r setup, include=FALSE}
-# Load libraries
-library(dplyr)
-library(tidyr)
-library(purrr)
-library(furrr)
-library(readr)
-library(magrittr)
-library(officer)
-library(flextable)
-library(here)
-library(pwr)
-
-# set up chunk options
-knitr::opts_chunk$set(
-  echo = F,
-  fig.align = "center",
-  fig.pos = "!t", 
-  out.extra = "",
-  fig.show = "asis",
-  message = FALSE,
-  warning = FALSE
-)
-
-# set up flextable for tables
-set_flextable_defaults(
-  font.family = "Times", 
-  font.size = 10,
-  font.color = "black",
-  line_spacing = 1,
-  padding.bottom = 1, 
-  padding.top = 1,
-  padding.left = 1,
-  padding.right = 1
-)
-
-# Source necessary objects
-power_linear      <- read_csv("../data/1_pilot/simulation/power_linear_model.csv") %>% mutate(power = round(power, 0))
-power_mixed       <- read_csv("../data/1_pilot/simulation/power_mixed_model.csv") %>% mutate(power = round(power, 0))
-
-load("pilot_staged_results.RData")
-load("study1_staged_results.RData")
-load("study2_staged_results.RData")
-load("pooled_staged_results.Rdata")
-```
-
 # Abstract
@@
 *Key-words:* childhood adversity, inhibition, Flanker, Drift Diffusion Modeling
-
-\pagebreak
-
-# Childhood adversity is not associated with lowered inhibition, but lower perceptual processing: A Drift Diffusion Model analysis
-
-The predominant view in developmental psychology is that exposure to adversity impairs cognitive abilities.
-This view is supported by decades of research showing that people living in high-adversity contexts tend to score lower on a variety of cognitive tests [@hackman_2010; @ursache_2016].
-Recent adaptation-based perspectives, however, have argued that people from adversity may also develop intact, or enhanced, abilities for solving problems in high-adversity contexts [@ellis_2017; @frankenhuis_2013].
-Adaptation- and deficit-based perspectives are considered complimentary.
-For instance, adversity may impair some cognitive processes, yet enhance others.
-Despite their compatibility, few studies have investigated how the interplay of impaired and enhanced abilities shapes performance.
-In this paper, across three preregistered online experiments, we used cognitive modeling to derive a process-level understanding of the association between childhood adversity and performance on the Flanker Task, a popular measure of cognitive control [@ridderinkhof_2021].
-
-## Attention in adverse conditions
-
-It is well-established that early-life adversity is associated with deficits in the ability to inhibit distracting, goal-irrelevant information [@hackman_2010; @ursache_2016].
-One of the leading paradigms in this literature is the Flanker Task [@eriksen_1974].
-On this task, participants typically see five arrows in a horizontal orientation, and are asked to indicate the direction of the central arrow.
-The flanking arrows point in the opposite direction on half of the trials, leading to interference that participants must inhibit.
-Slower performance on the Flanker has been documented for children and adults with lower childhood socioeconomic status [SES\; @farah_2006; @mezzacappa_2004; @noble_2005] and more environmental unpredictability [@fields_2021; @mittal_2015].
-These findings are typically interpreted as indicating a deficit in the ability to inhibit distractions.
-
-Nonetheless, some recent studies suggest that growing up in adversity may also be associated with improved abilities such as attention shifting [@fields_2021; @mittal_2015; @young_2022; but see @nweze_2021].
-Some studies found deficit patterns on the Flanker alongside enhancements on other aspects of attention within the same participants.
-For example, in one study, children with lower SES performed less well on the Flanker, but outperformed children from higher SES on orienting their attention to salient cues and, peripheral cues [@mezzacappa_2004].
-Similarly, children with more caregiver switches (an indicator of unpredictability) were found to perform less well on the Flanker, but outperformed children with fewer caregiver switches on shifting their attention between different task goals [@fields_2021].
-
-Performance on attention tasks could reflect developmental adaptation to adverse environments [@blair_2012; @dangiulli_2012; @frankenhuis_2020; @mittal_2015].
-In unpredictable or threatening conditions, the ability to detect salient peripheral information (e.g., distant noises or approaching individuals) could help to more quickly detect and act on potential threats.
-Over time, cognitive adaptations to such conditions could result in a general tendency to use a more diffuse scope of attention, leading to an enhanced ability to keep track of the broader environment.
-In line with this hypothesis, people with lower SES respond more strongly to auditory distractors [@giuliano_2018; @stevens_2009; @hao_2022] and are faster to orient their attention to peripheral visual information [@mezzacappa_2004].
-While potentially adaptive, a more diffuse scope of attention could come at the cost of lowered ability to ignore irrelevant distractors.
-This could compromise more long-term goal-directed behavior, especially in chaotic environments (e.g., a noisy classroom or a busy street).
-
-Thus, lowered performance on tasks like the Flanker could reflect either a cognitive impairment or a difference in attentional strategies.
-Distinguishing between these two possibilities is challenging for two reasons.
-First, few studies in the adversity literature have measured performance differences on different attention tasks within the same individual [@mezzacappa_2004; @mittal_2015].
-Thus, it is unclear whether lowered inhibition is related to enhanced processing of peripheral information in people from from adverse backgrounds.
-Second, performance on inhibition tasks is---beyond the ability to inhibit distractors---also influenced by other factors, such as a person's general processing speed and response caution [@hedge_2022; @loffler_2022].
-This means that lowered performance on inhibition tasks does not necessarily reflect inhibition difficulties.
-In other words, we should consider cognitive processes other than ability when drawing inferences based on inhibition tasks.
-
-## Using Drift Diffusion Modeling to estimate attention and processing styles
-
-An important issue, therefore, is that several processes are involved in performance on the Flanker, and standard assessments using raw performance measures (response times, accuracy rates) mostly fail to distinguish between them.
-For example, performance differences on the Flanker could indicate that someone experiences more (or less) flanker interference, generally processes less (or more) efficiently, or responds with less (or more) caution.
-To understand how adversity affects performance, we need to be able to separate the difference processes that make up performance.
-
-Formal cognitive models such as the Drift Diffusion Model [DDM\; @forstmann_2016; @ratcliff_1998; @ratcliff_2008; @ratcliff_2015; @wagenmakers_2009] provide a potential solution.
-The DDM estimates cognitive processes at different stages of the decision-making process (See Figure 1a).
-It represents decision-making on binary decision-making tasks as a process in which people accumulate information until one response is sufficiently favored over the other.
-These two response options are represented as opposing boundaries.
-One boundary corresponds to the correct response and the other to the incorrect response.
-When information accumulation reaches one of the two boundaries, the corresponding response is executed.
-
-The DDM translates trial-level response times (RTs) and accuracy into three distinct cognitive processes.
-The speed of information accumulation is captured in a parameter called the *drift rate*.
-Higher drift rates are associated with faster responses and higher mean accuracy.
-Response caution is modeled through the *boundary separation*; that is, the width between the two boundaries.
-Larger boundary separation is associated with larger RTs and higher accuracy (i.e., sacrificing speed to increase accuracy).
-Finally, *non-decision time* represents the time it takes to prepare for the task at the start of the trial (before information processing) and the time it takes to execute a response (after a response boundary has been reached).
-Longer non-decision times are associated with larger RTs, without influencing accuracy.
-
-The Shrinking Spotlight (SSP) model is an extension of the standard DDM to account for attention processes on the Flanker [@grange_2016; @white_2018a; @white_2018b; @white_2011].
-The SSP model assumes that attention resembles a spotlight that is normally distributed over the Flanker arrows (with a particular starting *attentional width*).
-Over time, people narrow their attention down to the central arrow (at a rate defined by the *shrinking rate*), thereby gradually decreasing interference from irrelevant information (See Figure 1b).
-Prior work has defined the amount of distractor *interference* by dividing the attentional width by the shrinking rate [@white_2018a].
-People may experience less interference either by starting with a narrower attentional width, and/or by more rapidly shrinking their attention down to the target arrow.
-Finally, performance is also influenced by the *perceptual input* strength; that is, how well someone can process the arrows in general.
-Note that typical interpretations of lowered raw Flanker performance are in terms of the amount of interference that someone experiences, and not in terms of the strength of perceptual input.
-Here, we are interested in how childhood adversity is associated with both interference and the strength of perceptual input.
-
-<br>
-
-```{r}
-#| label: figure1
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 1.** A visual overview of the Drift Diffusion Model (DDM) and the Shrinking Spotlight Model (SSP).
-Panel A: The DDM assumes that people go through three distinct stages when they perform cognitive tasks with two forced response options.
-In a first preparation phase, they visually encode the relevant stimuli.
-In a second decision phase, people accumulate information in favor of one decision over the other (e.g., pressing left vs.
-right) until the decision boundary for either the correct or incorrect response is reached.
-Each jagged line represents this information accumulation process on a single trial.
-In a third execution phase, people execute the motor response.
-The model estimates four parameters that reflect distinct cognitive processes (printed in italic): (1) The drift rate represents the average rate of evidence accumulation towards the correct decision boundary and measures processing speed; (2) The non-decision time represents both the time spent encoding the stimuli and executing the response; (3) The boundary separation represents how far apart has “set” their decision boundaries, and is a measure of the person’s level of response caution; (4) The starting point represents the starting point of the decision process and measures the level of response bias (not considered here).
-Panel B: The SSP is an extension of the standard DDM including additional parameters to capture attentional processes involved in Flanker performance.
-Each stimulus arrow provides a certain strength of perceptual input (*p*).
-On incongruent trials, the perceptual input of flanking arrows is coded negatively (-*p*).
-Attention is assumed to be normally distributed over the arrows with a certain attentional width.
-Over time, attention is narrowed down toward the central arrow at a rate determined by the shrinking rate, thereby gradually lowering the interference caused by the flanking arrows.
-The drift rate in the SSP model is the sum of the perceptual input of each arrow multiplied by the attention allotted to each arrow.
-As attention for the flanking arrows decreases over time, the drift rate is assumed to increase over time (contrary to the standard DDM, which assumes a linear drift rate).
-
-knitr::include_graphics("figures/fig1.png")
-```
-
-# Overview of studies
-
-The overarching goal of our studies is to understand the attentional and processing styles that people develop in conditions of adversity.
-We focus on measures of exposure to violence and environmental unpredictability.
-Previous research shows that these two types of adversity are on the one hand associated with improved attention shifting and working memory updating [@fields_2021; @mittal_2015; @young_2018; @young_2022], and on the other hand with lowered inhibition and working memory capacity [@fields_2021; @mittal_2015; @young_2018].
-We conducted three online studies: one pilot and two follow-up studies.
-Using cognitive modeling, we unpack Flanker performance in comparison to other tasks that require externally focused attention (Pilot), across visual processing manipulations (Study 1), and in terms of tendencies for holistic versus local processing (Study 2).
-
-We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see <https://anonymous.4open.science/r/CogDev_AnonLink>).
-For each study, we preregistered primary (i.e., hypothesis-driven) and exploratory analyses.
-The main text addresses the primary analyses involving violence exposure and the exploratory analyses involving environmental unpredictability.
-We describe the other exploratory analyses in the supplemental materials (section 2).
-For an overview of all deviations from the preregistrations, see section 4 of the supplemental materials.
-
-# Pilot
-
-In the Pilot, our goal was to understand how childhood adversity relates to performance on tasks with different attentional demands.
-Participants completed self-report measures of childhood adversity and three cognitive tasks.
-These tasks measured inhibition, attention for peripheral cues, and attention for subtle changes.
-We expected violence exposure to be positively associated with a present-oriented attention style.
-Specifically, we expected participants with more violence exposure to be better at detecting peripheral stimuli and subtle changes.
-We expected this would result in a higher drift rate (faster speed of information accumulation) or shorter non-decision times (faster attention orientation, among other things), but not necessarily with differences in boundary separation (response caution).
-Second, we expected that participants with more violence exposure would be worse at ignoring distracting peripheral stimuli.
-We expected this would result in more experienced interference (as derived from the SSP model).
-
-## Methods
-
-### Participants {#participants}
-
-Participants were 565 people from the United States aged between 18 and 30 recruited on Prolific Academic ([https://www.prolific.co](https://www.prolific.co)) (See Table 1 for demographic data).
-The sample was balanced on sex.
-We used the MacArthur's ladder, included in Prolific's prescreening battery, for assessing perceived SES to ensure about half of the sample came from lower-SES backgrounds (which we defined as a score of 4 or below).
-Participants were eligible if they spoke fluent English and did not report color-blindness.
-
-\pagebreak
-
-```{r}
-#| tab.id: table1
-#| results: markup
-demographics_table
-```
-
-<br>
-
-We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the minimally required number of participants for standardized regression coefficients of 0.10 and 0.15 (for details and simulation code, see <https://anonymous.4open.science/r/CogDev_AnonLink/preregistrations/1_pilot/scripts>).
-Power was \> .80 for adversity x task condition interactions with *N* = 450 or more.
-For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require *N* = `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`.
-We sampled 550 participants, anticipating a final sample of \~500 after exclusions.
-
-Prior to analyzing the data, we applied our preregistered exclusion criteria.
-First, we excluded participants who did not complete the full study; second, those who had incomplete data on any of the attention tasks; third, those who missed both attention check items; fourth, those who had suspicious response patterns (e.g., consistently endorsing high response options even though some items were reverse coded).
-Fifth, on a trial-level, we excluded any trials with reaction times \< 250 ms or \> 3500 ms [@ratcliff_2015].
-Participants with more than 10 trials removed were completely excluded from the analyses.\
-The final sample consisted of `r nrow(pilot_data)` participants.
-
-### Procedure {#procedure}
-
-Participants completed the experiment on their own laptop or desktop computer.
-Participants could refrain from answering any of the questionnaire items and were prompted with a warning once per page in case of missing items.
-
-After providing consent, participants completed three attention tasks.
-They were asked to move to a quiet room in the house, where they would be unlikely to be distracted by other people or outside noises.
-The order of the tasks was counterbalanced between subjects.
-At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs.
-The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deleeuw_2015].
-Participants were asked to hold a credit card (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the credit card.
-The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants.
-After successfully resizing the screen, participants completed all three tasks.
-During the task, the cursor was hidden from the screen to minimize distractions.
-After completing the attention tasks, participants completed the questionnaire battery and demographic questions.
-Finally, we asked participants whether they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.
-The full experiment took \~35 minutes.
-Participants were paid £4.38 when they reached the end of the experiment.
-
-### Cognitive measures {#cogmeasures}
-
-The attention tasks were programmed in JsPsych version 3.6.1 [@deleeuw_2015].
-For all materials and links to working versions of the tasks, see the Github repository.
-
-**Flanker Task.** The Flanker measures selective attention and response inhibition [@eriksen_1974].
-The Flanker began with eight practice trials, followed by 64 test trials.
-On each trial, participants saw a set of five arrows pointing either left or right.
-Participants were instructed to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right.
-All trials included black arrows against a white background.
-On the *congruent* trials (50%), the flanking arrows pointed in the same direction as the central arrow.
-On the *incongruent* trials (50%), the arrows pointed in the opposite direction.
-The arrows were randomly presented in the top-half or bottom-half of the screen.
-Each trial started with a fixation cross (1000 ms), after which the arrows were visible until a response was given.
-Participants received performance feedback during the practice trials, but not during the test block.
-
-**Cued Attention Task.** The Cued Attention Task was an adapted version of the Posner task, which measures the speed of attention for peripheral cues [@posner_1980].
-The Cued Attention Task began with eight practice trials, followed by 64 test trials.
-On each trial, a left- or right-pointing arrow was presented in one of eight random locations at 300 pixels from the center of the screen.
-Participants were instructed to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard.
-All trials included a black cue and arrow against a white background.
-On *cued* trials (50%), a cue ('\*') preceded the arrow in the exact same location.
-On *neutral* trials (50%), the cue preceded the arrow, but appeared at the center of the screen (not where the arrow would appear).
-Thus, the cue was perfectly predictive of the target location on cued trials, but provided no predictive information about the location of the arrow on neutral trials.
-Each trial started with a fixation cross at the center of the screen for 1000 ms. Then, the cue appeared for 250 ms, followed by the target arrow, until a response was given.
-
-**Change Detection Task.** The Change Detection Task measures the ability to detect subtle spatial changes.
-The Change Detection Task started with five practice trials followed by 50 test trials.
-On each trial, participants saw five colored circles (red, light-blue, dark-blue, yellow, and purple) against a gray background, each with a radius of 15 pixels.
-Each circle was located in a semi-random location around the central fixation cross.
-The location of each circle was sampled within a pre-specified area of 50-by-50 pixels to prevent overlap.
-Participants had 1000 ms to memorize the locations of the five circles.
-Then, the circles disappeared for 500 ms and then reappeared.
-On *change* trials (50%), one of the circles had moved to another location with a fixed displacement of 40 pixels in a 360 degree direction.
-On *no change* trials (50%), all circles were still in the same location.
-Participants were instructed to indicate whether all circles were still in the same location or one of the circles had changed location.
-The displacement of *one* circle was the only potential difference on each trial;
-
-**DDM/SSP parameters.** We analyzed the Flanker with the SSP model [@grange_2016; @white_2018a; @white_2018b; @white_2011], using the *flankr* package [@grange_2016].
-For each participant, the SSP provided us with estimates of: (1) strength of perceptual input (general quality of information that participants get from the arrows), (2) interference (initial attention width divided by the speed at which attention is narrowed down to the central arrow), (3) non-decision time (combination of speed of initial stimulus encoding and response execution), and (4) boundary separation (response caution).
-Our focus on interference as a ratio between attention width and shrinking rate was a deviation from the preregistration, as we initially planned to investigate both aspects of attention separately.
-However, we discovered that both parameters in isolation were unreliable because of an inherent trade-off, while the ratio did provide a stable measure.
-This was supported in a simulation study by @white_2018a showing that the ratio measure is reliable.
-See the supplemental materials (section 3) for a comparison between the preregistered and the updated analyses.
-
-For the Change Detection Task and the Cued Attention Task, we used a hierarchical Bayesian implementation of the standard DDM (HDDM).
-For each participant, the HDDM provided us with estimates of: (1) drift rate (speed of information accumulation; analogous to strength of perceptual input in the SSP model, except that drift rate is time-invariant), (2) non-decision time (same as SSP model), and (3) boundary separation (same as SSP model).
-The hierarchical Bayesian fitting procedure was a deviation from the preregistration, in which we planned to use Maximum Likelihood (ML) estimation.
-There were several issues with estimating DDM parameters for the Cued Attention task, which we later discovered were caused specifically by ML.
-An important difference between HDDM and ML is that HDDM uses the group information to inform individual parameter estimates, whereas ML models are fitted to each individual separately.
-This generally improves the accuracy of the estimation.
-See the supplemental materials (section 3) for an overview of the fit procedure and model fit across all models.
-
-### Self-report measures
-
-See Table 2 for bivariate correlations between measures of adversity across all studies.
-
-**Violence exposure.** We measured violence exposure using the Neighborhood Violence Scale (NVS) and two items assessing involvement in violence before age 13 [@frankenhuis_2018; @frankenhuis_deVries_2020; @young_2022].
-The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up").
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
-The items of the NVS were averaged together (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$violence`).
-Similarly, we averaged the scores on the two fighting items together.
-For the main analyses, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average.
-
-**Environmental unpredictability.** We included five measures of environmental unpredictability across different temporal scales: (1) the Questionnaire of Unpredictability in Childhood [QUIC\; @glynn_2019]; (2) the Perceived Childhood Unpredictability scale [@young_2018]; (3) the Confusion, Hubbub, and Order Scale [CHAOS\; @matheny_1995]; (4) stability of the family and social environment; and (5) objective indicators of unpredictability.
-All scales were adapted to refer to experiences before age 13.
-We computed a composite measure of all z-transformed unpredictability measures.
-See section 2 of the supplemental materials for an exploration of the factor structure of these measures.
-
-The QUIC captures environmental and household unpredictability.
-We made three preregistered changes to the original scale [@glynn_2019], to better align it with the other scales.
-First, all items were rated on a scale of 1 (never true) to 5 (very often true), except for four items referring to specific experiences (e.g., "I experienced changes in my custody arrangement").
-For these items, we adopted a response scale with the options "never", "only once", "a couple times", "several times", "many times".
-Second, quantifiers such as "frequently", "often", and "There was a period of time when [...]" were dropped to better match the response scale.
-Third, we excluded the item "My parents got divorced" because it did not fit the new response labels and this information was already captured by one of the items of the perceived unpredictability scale.
-Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$quic_total`).
-
-The perceived childhood unpredictability scale included eight items measuring perceived unpredictability before age 13 (e.g., "My family life was generally inconsistent and unpredictable from day-to-day").
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$unp`).
-
-The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late").
-All items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
-Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$chaos`).
-
-We included one additional scale to measure the stability of the family and social environment.
-On a scale of 1 (the same all the time) to 5 (constant and rapid changes), participants indicated how often the following aspects of their family and social environment changed before age 13: (1) economic status; (2) family environment; (3) childhood neighborhood environment; and (4) childhood school environment.
-
-Finally, we included four objective measures of unpredictability before age 13: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "How many romantic partners did your mother have (not counting your father)?"; 4) "How many romantic partners did your father have (not counting your mother)?".
-
-```{r}
-#| tab.id: table2
-#| results: markup
-iv_cor_pooled_table
-```
-
-<br>
-
-### Data analyses {#analysis_plan}
-
-**Multiverse analysis.** In an amendment to the preregistration, we quantified the robustness of our findings against six data cleaning decisions that may affect the robustness of online studies by using multiverse analysis, using the *multitool* package [@young_2023].
-Multiverse analysis allows for systematically evaluating the robustness of analyses across all combinations of different arbitrary data processing decisions [for details, see @giudice_2021; @simonsohn_2020; @steegen_2016].
-Specifically, we looked at the influence of including or excluding 1) participants who scored below 0.5 on a build-in bot-detection measure on Prolific (potentially indicating a bot); 2) participants who did not rescale their screen at the start of the experiment; 3) participants who did not enter fullscreen mode prior to starting the tasks; 4) participants who exited fullscreen mode at any point during the tasks; 5) participants who indicated high levels of noise in their environment; 6) participants who indicated extreme interruptions during the experiment.
-See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
-
-### Primary analyses
-
-For the Cued Attention Task and Flanker RTs, we used linear mixed effects models to test violence exposure x task condition (sum-coded) interactions on mean RTs and each DDM parameter.
-All mixed effects models included a random intercept for participants.
-For the Change Detection Task and Flanker SSP parameters, we used linear regression models to test the main effect of adversity on mean RTs and each DDM/SSP parameter.
-To meet model assumptions of normally distributed residuals, reaction times were log-transformed.
-Analyses involving interference (Flanker) and boundary separation (all tasks) parameters violated the assumption of normally distributed residuals.
-For boundary separation, we solved this using log-transformation.
-For interference, non-normality was caused by extreme outliers (\>3.2SD), which we excluded from the analyses.
-
-## Results and discussion
-
-Table 3 summarizes the results.
-More violence exposure was associated with lower strength of perceptual input under `r pilot_main_eff_ddm_list$Flanker_p$p_sum_Main`% of multiverse specifications (although the median 95% CI interval contained zero).
-We additionally found a significant main effect of violence exposure on interference under `r pilot_main_eff_ddm_list$Flanker_interference$p_sum_Main`% of multiverse specifications, such that more violence exposure was associated with less interference.
-This was contrary to our expectation that people exposed to adversity would have more difficulties dealing with interference from irrelevant distractors.
-
-Participants with more exposure to childhood violence were slower on the Cued Attention Task, which was mainly related to a higher level of response caution (boundary separation).
-On the Change Detection Task, more childhood violence exposure was associated with slower speed of information processing (drift rate) under `r pilot_main_eff_ddm_list$Change_v$p_sum_Main`% of multiverse specifications, but not with longer RTs.
-These results were not in line with our expectation that people from adversity would perform better on cognitive tasks that require a broad, present-focused attention style.
-
-<br>
-
-```{r}
-#| tab.id: table3
-#| results: markup
-pilot_main_eff_ddm_table |> 
-  border(i = 1, border.bottom = fp_border_default(), part = "header") 
-```
-
-<br>
-
-The pattern of findings on the Flanker was interesting for two reasons.
-First, the Flanker is a widely used task to assess the ability to inhibit irrelevant information, and people exposed to adversity typically show lowered performance.
-Our pilot results, though, suggest that lowered performance may not be caused by a reduced ability to inhibit distracting information.
-Instead, people exposed to adversity might have a lower strength of perceptual input, leading to slower and less efficient information processing.
-If true, these initial findings suggest that performance might be improved through interventions that increase the visual quality of stimuli.
-In Study 1, we aimed to replicate and extend these findings.
-
-# Study 1
-
-The goal of Study 1 was to follow up on the Pilot by manipulating the visual quality of information on the Flanker.
-Participants completed three versions: a standard version (similar to the Pilot), one with enhanced visual information, and one with degraded visual information.
-We again focused on childhood exposure to violence.
-Our first aim was to examine the robustness of our finding of improved interference control on the Flanker in relation to more adversity exposure in the pilot.
-We did so by analyzing the data of the standard condition, as well as by pooling the data of the Pilot and Study 1.
-Our second aim was to investigate whether manipulating visual information on the Flanker would influence performance for people with more violence exposure.
-
-We preregistered two potential data patterns and associated interpretations, without favoring one over the other *a priori*.
-First, the strength of perceptual input might be lower for people with more exposure to violence compared to people with less exposure to violence across all conditions.
-Second, lower performance on the standard version might reflect an adaptive trade-off towards cognitive functioning that is less affected by noise or perturbations, at a cost of lower overall performance [@giudice_2018].
-In that case, we would expect the strength of perceptual input to be influenced to a lesser extent across conditions for people with more exposure to violence than for people with less exposure to violence.
-As a result, they might not benefit as much from enhanced visual information, yet might be able to better maintain performance with degraded information.
-
-## Methods
-
-### Participants
-
-Participant recruitment was identical to the Pilot.
-In total, 567 people from the United States between the ages of 18 and 30 participated (See Table 1).
-We applied the same exclusion criteria as reported in the Pilot.
-The final sample consisted of `r nrow(study1_data)` participants.
-
-### Flanker Task
-
-We programmed the Flanker in JsPsych version 6.3.1 [@deleeuw_2015] with three conditions.
-Each condition consisted of eight practice trials, followed by 64 test trials.
-In the *standard* condition, the arrows were 40 pixels in size (0.4 inches) and had zero padding between them.
-In the *enhanced* condition, we increased the arrow size by 12.5% to 45 pixels (0.45 inches), and increased the space between the arrows to 5 pixels.
-This increased the width of the stimulus display by 50% with respect to the standard display.
-In the 'degraded' condition, sizes and space between arrows were the same as in the standard version, but all arrows were rotated 45$^\circ$ (in the same direction; that is, if the left flanker arrows pointed upwards, the right flanker arrows pointed downward).
-Participants completed each condition separately in different blocks, in randomized order.
-
-### Self-report measures
-
-The self-report measures were identical to those used in the Pilot.
-
-### Procedure
-
-The procedure was identical to the pilot study.
-The full experiment took approximately 30 minutes.
-Participants were paid £3.75 after they completed the full study.
-
-### Data analyses
-
-**Multiverse analysis.** We included the same arbitrary decisions in the multiverse analyses as in the Pilot.
-For the pooled analyses---i.e., joint analysis of the Pilot and the standard condition of Study 1---there was one minor change in how we included screen rescaling as a preprocessing decision in the multiverse.
-In Study 1, we changed the screen rescaling procedure by converting the initial size of the resize box to 300 pixels instead of 100 pixels.
-This way, the stimulus display would still be close to the intended size if participants did not engage in any resizing.
-However, this led to one important change for the pooled analysis: rescaling (yes or no) was included as an arbitrary exclusion decision in the multiverse analyses with four combinations: (1) exclude non-scalers in both studies; (2) include non-scalers in both studies; (3) exclude non-scalers in the Pilot, include non-scalers in Study 1; (4) include non-scalers in the Pilot, exclude non-scalers in Study 1.
-
-For each analysis, we report the median $\beta$s, 95% confidence intervals, and the proportion of *p*-values \< .05 across all analytic decisions.
-For the primary analyses, we used bootstrapping to compute the probability of obtaining an effect size at least as extreme as observed in the real data, conditioned on a true effect size of zero [for details, see @simonsohn_2020].
-See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
-
-**Primary analyses.** To address the first aim, we analyzed the data from the standard condition, as well as pooled the Flanker data of the Pilot and the current study.
-We ran separate linear models for each SSP parameter as well as RT difference scores with violence exposure as main predictor and study as covariate (effect-coded).
-To address the second aim, we analyzed the effect of violence exposure and Flanker condition type on performance using linear mixed effects models with a random intercept per participant.
-The five main dependent variables were mean RT difference and the SSP parameters: Perceptual input, boundary separation, non-decision time, and interference.
-For each outcome measure, we ran two separate models: one comparing the standard condition with the enhanced condition, and one comparing the standard condition with the degraded condition.
-In both models, condition was dummy-coded using the standard condition as the reference group.
-
-## Results and discussion
-
-### Standard Flanker performance
-
-Table 4 summarizes the multiverse results for the effects of violence exposure (primary analysis) and unpredictability (exploratory analysis).
-Unlike in the Pilot, we did not find any significant associations with violence exposure.
-In the exploratory analysis, there was a significant negative association between unpredictability and perceptual input (median $\beta$ = `r study1_expl_results_list$p_flanker$median_effect_Main`, 95% CI = `r study1_expl_results_list$p_flanker$CI`, `r study1_expl_results_list$p_flanker$p_sum` % of *p*s \<.05).
-
-```{r}
-#| tab.id: table4
-#| results: markup
-study1_results_table |> 
-  border(i = 1, border.bottom = fp_border_default(), part = "header") 
-```
-
-After pooling the data of the pilot study and Study 1, there was a negative association between violence exposure and interference (median $\beta$ = `r study1_pooled_results_list$interference_vio$median_effect`, 95% CI = `r study1_pooled_results_list$interference_vio$CI`, `r study1_pooled_results_list$interference_vio$p_sum` % of *p*s \<.05, bootstrapped *p* = `r study1_pooled_results_list$interference_vio$boot_p`).
-Violence exposure was associated with lower strength of perceptual input under `r study1_pooled_results_list$interference_vio$p_sum`% of multiverse specifications, but the bootstrapped *p*-value was not significant (median $\beta$ = `r study1_pooled_results_list$p_vio$median_effect`, 95% CI = `r study1_pooled_results_list$p_vio$CI`, bootstrapped *p* = `r study1_pooled_results_list$p_vio$boot_p`).
-We did not find other significant associations for either violence exposure or unpredictability.
-
-### Flanker conditions
-
-The main effects of task condition on the strength of perceptual input were in the expected direction: relative to the standard condition, the quality of perceptual input was higher in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$p_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$p_enhanced$condition_CI`, `r study1_condition_vio_results_list$p_enhanced$p_sum_Condition` % of *p*s \<.05) and lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$p_degraded$median_effect_Condition`, 95% CI = `r  study1_condition_vio_results_list$p_degraded$condition_CI`, `r study1_condition_vio_results_list$p_degraded$p_sum_Condition` % of *p*s \<.05).
-Interference was lower in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$interference_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_enhanced$condition_CI`, `r study1_condition_vio_results_list$interference_enhanced$p_sum_Condition` % of *p*s \<.05).
-Unexpectedly, interference was also lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$interference_degraded$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_degraded$condition_CI`, `r study1_condition_vio_results_list$interference_degraded$p_sum_Condition` % of *p*s \<.05), suggesting that the angle in the flanking arrows reduced interference, relative to the standard condition.
-However, none of the interaction effects for either violence exposure or unpredictability were significant.
-
-\pagebreak
-
-```{r}
-#| tab.id: table5
-#| results: markup
-study1_condition_results_table |> 
-  border(i = 1, border.bottom = fp_border_default(), part = "header") 
-```
-
-The results of the Pilot and Study 1 were inconsistent with regard to the association between adversity and interference, but hinted at two general patterns.
-First, violence exposure was not associated with *increased* interference; instead, we found either the opposite effect or no effect.
-Second, both violence exposure and unpredictability were associated with lowered strength of perceptual input, albeit inconsistently.
-These findings, if replicable, are intriguing as they would suggest that the common finding of lowered Flanker performance among people with more adversity exposure do not actually result from worse interference control---as typically inferred.
-Rather, such lowered performance would result from processes other than inhibition ability, such as slower general processing.
-Though interesting, our findings so far leave open the question why adversity might be negatively associated with perceptual input.
-This question was the focus of Study 2.
-
-# Study 2
-
-Study 2 set out to compare two explanations for the finding that people exposed to adversity tended to show lower strength of perceptual input on the Flanker.
-First, lowered strength of perceptual input in people exposed to adversity may indicate a difficulty in extracting relevant information (i.e., about their direction) from the arrows in general.
-Second, the difference in perceptual input may not be a cognitive deficit per se, but instead could be a signature of a difference in processing style---that is, a feature, and not a bug.
-People exposed to adversity may process information more holistically, focusing more on the configuration of pieces of information rather than individual pieces of information.
-On the Flanker, this would lower the depth of perceptual processing of any individual stimulus, thus resulting in lowered strength of perceptual input, as we observed in the Pilot and Study 1.
-
-We preregistered three aims focusing both on violence exposure and unpredictability.
-First, we expected to replicate our earlier findings that adversity was associated with lowered perceptual input and lower interference in people exposed to adversity.
-Second, we included a Global-Local Task to investigate the hypothesis---based on the findings of the Pilot and Study 1---that people with more adverse experiences would develop a more holistic style of information processing.
-Third, we planned to conduct a within-subjects analysis of Flanker and Global-Local performance to assess whether people with lowered perceptual input on the Flanker Task would also show a more global processing style (rather than a local processing style) on the Global-Local Task.
-
-## Methods
-
-### Participants
-
-Participants were 600 people from the United States between the ages of 18 and 30.
-Recruitment was identical to Study 1.
-We conducted a simulation-based power analysis for the planned linear mixed models with the Global Local Task (see GitHub).
-We determined that power of \> .80 for a standardized interaction effect of 0.06, with sigma (noise) set to 0.7 (comparable to observed sigmas in the first two studies) would require 550 participants.
-We recruited 600 participants, with the expectation to have a final sample of 550 participants after exclusions.
-We applied the same exclusion criteria as reported in the Pilot and Study 1.
-The final sample consisted of `r nrow(study2_data)` participants.
-
-### Measures
-
-The measures of childhood violence exposure and environmental unpredictability were identical to Study 1.
-The Flanker was identical to the standard version used in Study 1.
-
-*Global-Local Task*.
-The Global-Local Task is a measure of global-local processing [@navon_1977].
-Many different versions of this task exist in the literature.
-One key dimension on which they differ is whether the task measures focused attention (by cueing attention towards the global or local level prior to stimulus presentation) or divided attention (by having participants search for a target on both levels) [@lee_2023].
-Here, we use a version measuring divided attention, which allows measuring whether someone tends to have a more global versus local processing style [@hakim_2017; @lee_2023; @mckone_2010].
-
-Participants saw images of big, black letters (the global level) comprised of small letters (the local level)---so-called Navon images [@navon_1977]---against a white background.
-Participants first completed eight practice trials, after which they completed an additional 64 test trials.
-On each trial, participants searched for one of two target letters---an 'E' or 'H'---and indicated whether it was present on the global or local letter by pressing 'g' or 'l' on their keyboard, respectively.
-Each stimulus was 600 pixels high and 395 pixels wide and comprised of seven local letters vertically and five local letters horizontally.
-All stimuli consisted of combinations of the letters 'T', 'F', 'P', 'L', 'H', and 'E'.
-The target letters 'H' and 'E' were both present in each stimulus, but the other letters varied.
-The global and local level never contained the same letter.
-
-### Procedure
-
-The procedure was identical to Study 1.
-The full experiment took \~30 minutes.
-Participants were paid £4.50 when they reached the end of the experiment.
-
-### Data analyses
-
-**Multiverse analysis.** We included the same decisions in the multiverse as in the previous studies.
-However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, <https://anonymous.4open.science/r/CogDev_AnonLink/preregistrations/3_study2>).
-See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
-
-**DDM estimation.** For the Flanker, we used the SSP [@grange_2016; @white_2018a; @white_2018b; @white_2011] using the same procedure as in Study 1.
-For the Global-Local Task, we used a hierarchical Bayesian DDM to fit the data using the *runjags* package [@denwood_2016].
-See the supplemental materials (Section 3) for more information about the procedure and model fit.
-
-We deviated from our preregistration regarding the preprocessing of Global-Local Task data.
-Specifically, we relaxed the low performance threshold as the task was more difficult than anticipated.
-These deviations are described in the supplemental materials (section 4).
-
-**Primary analyses.** We ran simple regressions for analyses involving only main effects (aim 1), and linear mixed effects models for analyses involving within-subject interactions (aim 2 and 3).
-To address aim 3 (within-subject interaction between Global-Local drift rate and Flanker strength of perceptual input), we further preprocessed the data in two steps.
-First, we computed a difference score of Global-Local drift rates by subtracting the drift rate on local trials from the drift rate on global trials (with higher scores reflecting relatively faster information processing on global trials).
-Second, we separately standardized the Flanker strength of perceptual input and Global-Local drift rate difference.
-We fitted linear mixed effects models with the standardized performance measures as the dependent variable, and adversity type, task (Flanker or Global-Local, sum-coded) and their interaction as independent variables.
-
-## Results and discussion
-
-Figure 2 and 3 summarize the multiverse results for the effects of violence exposure and unpredictability within Study 2 and pooled across all studies.
-In Study 2, violence exposure was negatively associated with strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.vio_comp$boot_p`), but not associated with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$boot_p`).
-Unpredictability was not associated with either strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.unp_comp$boot_p`), nor with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$boot_p`).
-
-In the pooled analysis, the results were similar for both types of adversity.
-Violence exposure was associated with lower strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.vio_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.vio_comp$boot_p`).
-Similarly, unpredictability was associated with a lower quality of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_list$p_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.unp_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_list$interference_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.unp_comp$boot_p`).
-
-```{r}
-#| label: figure2
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 2.** Multiverse results for the association between violence exposure with the strength of perceptual input and interference on the Flanker across all studies.
-Each panel depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-The top row depicts effect curves in the Pilot.
-The second row depicts effect curves in Study 1.
-The third row depicts effect curves in Study 2.
-The Fourth row depicts effect curves of the pooled analyses across all studies.
-knitr::include_graphics("figures/fig2.png")
-```
-
-<br>
-
-```{r}
-#| label: figure3
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 3.** Multiverse results for the association between unpredictability with the strength of perceptual input and interference on the Flanker across all studies.
-Each panel depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-The top row depicts effect curves in the Pilot.
-The second row depicts effect curves in Study 1.
-The third row depicts effect curves in Study 2.
-The Fourth row depicts effect curves of the pooled analyses across all studies.
-knitr::include_graphics("figures/fig3.png")
-```
-
-<br>
-
-### Global-Local Task performance
-
-There was a main effect of violence exposure on Global-Local drift rates, with more violence exposure being associated with slower speed of information processing ($\beta$~median~ = `r study2_aim2_results_list$Main_vio$median_effect`, `r study2_aim2_results_list$Main_vio$p_sum`% of *p*s \< .05, bootstrapped *p* `r study2_aim2_results_list$Main_vio$boot_p`).
-There also was a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_vio$median_effect`, `r study2_aim2_results_list$Condition_vio$p_sum`% of *p*s \< .05, bootstrapped *p* `r study2_aim2_results_list$Condition_vio$boot_p`).
-Finally, there was an interaction effect between violence exposure and task condition ($\beta$~median~ = `r study2_aim2_results_list$Interaction_vio$median_effect`, `r study2_aim2_results_list$Interaction_vio$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_vio$boot_p`).
-Simple slopes analyses revealed that participants with lower levels of violence exposure did not differ in speed of processing of global versus local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.Low$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.Low$p_sum`% of *p*s \< .05).
-In contrast, participants with higher levels of violence exposure processed global targets faster than local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.High$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.High$p_sum`% of *p*s \< .05).
-
-There was a significant main effect of unpredictability on drift rates, with more unpredictability being associated with slower speed of information processing, ($\beta$~median~ = `r study2_aim2_results_list$Main_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Main_unp$CI`, `r study2_aim2_results_list$Main_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Main_unp$boot_p`).
-We also found a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Condition_vio$CI`, `r study2_aim2_results_list$Condition_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Condition_unp$boot_p`).
-We did not find a significant unpredictability x task condition interaction effect ($\beta$~median~ = `r study2_aim2_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Interaction_unp$CI`, `r study2_aim2_results_list$Interaction_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_unp$boot_p`).
-
-### Within-subjects comparison of Flanker and Global-Local information processing
-
-There was no significant main effects for violence exposure (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`) nor for cognitive task (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`).
-There was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_vio$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_vio$CI`, `r study2_aim3_results_list$Interaction_vio$p_sum` % of *p*s \< .05, bootstrapped *p* `r study2_aim3_results_list$Interaction_vio$boot_p`) (See Figure 2).
-A simple slopes analysis revealed that people with higher levels of violence exposure showed lower strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$vio_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.Flanker$p_sum`% of *p*s \< .05), and showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$p_sum`% of *p*s \< .05).
-
-There was no significant main effect for unpredictability (bootstrapped *p* = `r study2_aim3_results_list$Task_unp$boot_p`).
-However, there was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_unp$CI`, `r study2_aim3_results_list$Interaction_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim3_results_list$Interaction_unp$boot_p`).
-A simple slopes analysis revealed that people with higher levels of unpredictability did not differ in their strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$unp_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.Flanker$p_sum` % of *p*s \< .05), but showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$p_sum`% of *p*s \< .05).
-
-```{r}
-#| label: figure4
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 4.** Multiverse results for the within-subjects comparison of Flanker and Global-Local information processing.
-Panel A depicts the multiverse interaction effects, with the thick black lines denoting the median slope and the thin lines denoting effects for each combination of arbitrary decisions.
-Blue thin lines indicate significant effects (*p* > .05), and grey thin lines indicate non-significant effects (*p* > .05).
-Panel B depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-See the main text for more information about the multiverse analyses.
-knitr::include_graphics("figures/fig4.png")
-```
-
-<br>
-
-To sum up, Study 2 provided additional support for the basic finding that violence exposure and unpredictability were associated with lower strength of perceptual input but not with differences in interference; with the caveat that the associations for unpredictability only showed up in pooled analyses.
-People with more exposure to violence and unpredictability also processed information more slowly on the Global-Local Task.
-In line with our expectations, childhood exposure to violence was associated with both lowered strength of perceptual input and a more holistic processing style.
-The same processing style was observed for participants with more exposure to unpredictability, although they did not show lowered strength of perceptual input.
-
-# Exploratory analyses
-
-We hypothesized that the potential adaptive benefits of a more diffuse scope of attention in adverse conditions might be linked to the notion of a *present-oriented attention style* [@frankenhuis_2016; @vangelder_2023].
-People with a present-oriented attention style (versus a more future-oriented attention style) are more geared towards processing information that is relevant for solving challenges and obtaining rewards in the here-and-now.
-A general tendency to be more attuned to the present (while disregarding the future) is sometimes referred to as a short-term mindset [@kubel_2023; @vangelder_2023], which also includes tendencies to be more impulsive, to more steeply discount future rewards, and to be more sensation-seeking.
-Although short-term mindsets are associated with exposure to adversity [@ganschow_2023], it is unclear how they are associated with performance on attention tasks.
-We explored bivariate correlations pooled across all studies between two indicators of short-term mindsets (impulsivity and future orientation) and SSP parameters of the Flanker (for more information on the measures, see section 1 of the supplemental materials).
-
-See Table S2 for an overview of the correlations.
-Impulsivity was negatively associated with the strength of perceptual input (*r* = -.07, *p* = .004) and positively associated with interference (*r* = .09, *p* = .005). 
-In addition, impulsivity was also associated with a more holistic information processing style (*r* = .11, *p* = .020). 
-Thus, more impulsive participants processed information less deeply and were more easily drawn to distractions, but this might partly be explained by a holistic information processing style.
-Similarly, future-orientation was positively associated with perceptual input (*r* = .09 *p* < .001)—--but not with interference (*p* = .112) —--on the Flanker Task, and was also associated with a more detail-oriented processing style (*r* = -.12, *p* = .011).
-Thus, more future-oriented participants processed information more deeply, which might partly be explained by a detail-oriented processing style.
-
-# General discussion
-
-We investigated how two dimensions of childhood adversity---violence exposure and environmental unpredictability---are related to differences in how people attend to and process information.
-Specifically, we hypothesized that exposure to adversity might lead to a present-oriented attention style that would facilitate rapidly detecting novel or changing information, yet which would interfere with ignoring distractors.
-Across one pilot and two main studies, we tested how adversity was associated with performance on different attention tasks.
-The Pilot compared performance on a Cued Attention Task, Change Detection Task, and a Flanker.
-Two follow-up studies focused on the Flanker, with Study 2 also including a Global-Local Task.
-We leveraged DDM to estimate the processes underlying lowered and improved performance.
-This allowed us to investigate whether performance differences were associated with abilities (i.e., attention orientation, interference control, stimulus processing), or ability-irrelevant processes (e.g., stimulus encoding, response execution, response caution).
-Across all primary and exploratory analyses, we leveraged multiverse analysis to systematically assess the robustness of our findings against several uncontrollable aspects of the online assessment (e.g., distractions, fullscreen exits).
-
-### Main insights
-
-We found little to no support for the presence of a present-oriented attention style in people exposed to adversity.
-More childhood exposure to violence was associated with slower processing of subtle changes on the Change Detection Task and lower quality of perceptual input on the Flanker Task.
-It was not associated with speed of processing of peripheral information on the Cued Attention Task.
-Zooming in on the Flanker, our two main studies found mixed evidence for the hypotheses that violence exposure and unpredictability were associated with lower strength of perceptual input.
-This mixed evidence suggests that people with more exposure to these adversities process information less deeply, making it more difficult to make judgments about target and distractor information in equal measure.
-This was corroborated by the pooled analyses across studies, which found that both exposure to violence and unpredictability were associated with lower strength of perceptual input, but not with differences in the ability to inhibit distractors.
-This finding contradicts the standard deficit interpretation of lowered performance on inhibition tasks by people with more adversity exposure (discussed below).
-In addition, lowered strength of perceptual input was associated with a holistic processing style.
-Thus, we did not find evidence that people with more violence exposure have more difficulties with inhibiting task-irrelevant information.
-
-Our findings of the DDM decomposition of Flanker performance challenge previous interpretations based on raw performance.
-Previous studies have found that people exposed to adversity and/or low SES backgrounds have longer RTs on incongruent trials relative to congruent trials [@farah_2006; @fields_2021; @mezzacappa_2004; @mittal_2015; @noble_2005], which is commonly interpreted as an impaired ability to inhibit irrelevant information.
-This fits with adaptive hypotheses, as inhibition is assumed to be useful mostly in stable and predictable environment that afford long-term goal pursuit, but can be costly in unpredictable and potentially dangerous environments [@fields_2021; @mittal_2015; @daly_2005].
-Contrary to previous studies, we found little to no evidence for performance differences on the basis of raw RTs.
-In addition, our DDM analyses showed that performance differences on the Flanker are not driven by differences in interference control, but by more basic processes that are not typically considered when interpreting Flanker performance.
-
-Our findings align with a broader literature that is critical of the validity of the Flanker in particular, and that of cognitive control tasks more generally.
-As noted, several studies have failed to find coherent correlations between raw performance on different cognitive control tasks [e.g., @loffler_2022; @rey_mermet_2019; @rouder_2019; @stahl_2014].
-For example, previous research comparing several cognitive control tasks across different data sets using cognitive modeling found that shared variance between these tasks was mostly associated with processing speed and strategies (e.g., speed-accuracy trade-offs) [@hedge_2022].
-Moreover, the modeling parameters reflecting conflict processing (similar to interference in our study) were barely correlated.
-Similarly, previous work has shown that individual differences on common EF tasks---among which the Flanker Task---can be fully accounted for by general processing speed [@loffler_2022].
-This literature, together with the findings reported here, underscore that researchers should be cautious when drawing inferences about cognitive control abilities in people exposed to adversity based on raw RTs and performance on individual tasks.
-
-Finally, we showed that people exposed to adversity had a more holistic processing style, and that this style was associated with lower strength of perceptual input on the Flanker.
-This could mean that people with more adversity exposure processed the Flanker display more holistically; that is, focused less on individual arrows and more on the collection of arrows as a whole.
-One (tentative) interpretation is that in the absence of threatening or otherwise salient information, people with more exposure to adversity attend to and process information in the environment globally and less deeply.
-They might only shift to local processing of a single source of information if it seems threatening or otherwise salient [@shields_2015; @schwabe_2013].
-This would be consistent with research showing that growing up in a disadvantaged environment decreases the efficiency of the brain's (resting-state) salience network, which is in turn associated with lower raw performance on certain cognitive tasks [@cermakova_2023; @gellci_2019; @hilger_2017; @yuan_2012].
-This research also shows that in situations of acute stress, mental resources are reallocated to this salience network, increasing vigilance and facilitating adequate responding.
-Indeed, a few studies show that cognitive abilities that may be particularly relevant in adverse contexts---such as attention shifting and working memory updating---may be enhanced in people from adversity when they experience acute stress [@mittal_2015; @young_2018].
-
-### Strengths, limitations, and future directions
-
-Our study has three main strengths.
-First, each study included socioeconomically diverse participants.
-Second, the DDM allowed us to decompose performance in a more nuanced way than is possible with (typically used) raw performance scores.
-Third, the multiverse analyses provided a systematic overview of the robustness of our findings under different analytical decisions.
-Our study has three main limitations.
-First, all experiments were conducted online, which reduced control over people's testing environment, equipment, and behavior.
-Indeed, our results were the least robust against participants who skipped the screen-scaling procedure (to ensure the stimuli were adequately sized) and interruptions during the tasks, which are factors that are largely out of our control.
-Second, we deviated from our preregistrations in several ways in all studies, due to progressive insight.
-This decreased the severity of our statistical tests, and so this work would benefit from preregistered replications [@lakens_2023].
-
-Our findings suggest two main directions for future research.
-First, future studies could replicate and expand upon our finding that lower quality of information processing in people exposed to adversity is associated with a more holistic processing style.
-For example, future work could investigate whether people with more adversity exposure shift from holistic to a detail-oriented processing in situations of acute stress or otherwise salient information.
-Second, our results suggest that lower strength of perceptual input is likely the result of both processing styles, as well as of slower general processing.
-Future research could try to tease apart these sources using a within-subjects design simultaneously measuring inhibition, processing styles, and basic processing speed.
-Third, some research suggests that inhibition is not a unitary construct, instead distinguishing between response inhibition (which involves suppressing a prepotent response) and cognitive inhibition (which involves selective attention in the presence of distractors).
-Exposure to adversity might shape these two types of inhibition in different ways.
-For example, acute stress might impair performance on tasks of cognitive inhibition (of which the Flanker is an example) and enhances performance on tasks of response inhibition [for a meta-analysis, see @shields_2016; but see @dang_2017].
-Future work could assess inhibition more broadly, e.g., by including tasks that are hypothesized to require cognitive or response inhibition.
-
-### General conclusion
-
-We found that people with more childhood adversity exposure perform worse on the Flanker not because of an impairment in their ability to inhibit distracting information, but because of lower strength of perceptual input.
-Our results suggest that people with more adversity exposure are not worse at inhibiting distractions; rather, they do not seem to process information in the environment deeply unless it proves to be a reliable and important source of information.
-These findings challenge dominant interpretations, which infer an inhibition deficit from lowered performance.
-This is an important difference not just for theory development, but also for future interventions aimed at closing performance gaps.
-For example, when applied to school contexts, interventions based on an inhibition interpretation would focus on the learning environment, perhaps removing things from the classroom that could be distracting.
-In contrast, an intervention based on an information processing interpretation might instead focus on increasing the apparent relevance of the learning materials, perhaps by providing more repetition or by making the content more ecologically relevant [@young_2022].
-Thus, cognitive modeling can offer crucial insights for our understanding of cognitive abilities in adverse conditions.
-
-\pagebreak
-
-# Glossary
-
-**Adversity:** Prolonged exposures to intense stress; for instance, resulting from abuse, neglect, and poverty.
-
-<br>
-<br>
-
-**Boundary separation:** Parameter of the Drift Diffusion Model and Shrinking Spotlight Model. Measures the amount of information a person requires before making a decision (i.e., response caution).
-
-<br>
-<br>
-
-**Developmental adaptation:** A process that tailors people to the demands of their environments based on their experiences.
-
-<br>
-<br>
-
-**Drift Diffusion Model:** A formal cognitive model that estimates cognitive processes at different stages of the decision-making process for speeded binary decision-making tasks.
-It represents decision-making as a process in which people accumulate information until one response is sufficiently favored over the other.
-
-<br>
-<br>
-
-**Drift rate:** Parameter of the Drift Diffusion Model. Measures a person's speed of information accumulation on binary decision-making tasks.
-
-<br>
-<br>
-
-**Inhibition:** A person's ability to ignore task-irrelevant distractors in favor of task-relevant information.
-Operationalized in the Shrinking Spotlight Model as the initial attention width over all stimuli (i.e., target and distractors), divided by the rate at which attention is narrowed down to the central target.
-
-<br>
-<br>
-
-**Multiverse analysis:** An analysis technique that systematically and transparently evaluates the influence of arbitrary data-cleaning decisions on statistical outcomes.
-
-<br>
-<br>
-
-**Non-decision time:** Parameter of the Drift Diffusion Model and Shrinking Spotlight Model.
-Measures the time it takes a person to prepare for the task at the start of the trial (before information processing) and the time it takes to execute a response (after a response boundary has been reached) on binary decision-making tasks.
-
-<br>
-<br>
-
-**Perceptual input:** Parameter from the Shrinking Spotlight Model of Flanker performance. Measures how well a person can process the Flanker stimuli in general.
-
-<br>
-<br>
-
-**Shrinking Spotlight Model:** An extension of the standard Drift Diffusion Model to account for attention processes on the Flanker.
-
-\pagebreak
-
-# References {#refs}

### 2024-04-02 manuscript/manuscript_blinded.qmd
final tweaks to manuscript files for submission

@@
 ```
-
-# Abstract
-
-It is well-established that individuals who grew up in adverse conditions tend to be slower on the Flanker Task. 
-This finding is typically interpreted to reflect difficulty inhibiting distractions. 
-However, it might result from slower general cognitive processes (e.g., reduced general processing speed), rather than the specific ability of inhibition. 
-We used Drift Diffusion Modeling in three online studies (total N = 1560) with young adults to understand associations of adversity with Flanker performance. 
-We find no associations between exposure to violence and unpredictability with inhibition. 
-Yet, although mixed, violence and unpredictability exposure were associated with lower strength of perceptual input--—how well someone can process target and distractor information alike. 
-Finally, people with lower strength of perceptual input processed information more holistically, focusing less on details. 
-Thus, lowered Flanker performance does not necessarily imply lowered inhibition ability. 
-Cognitive modeling might reveal a different picture of abilities in adverse conditions.
-
-*Key-words:* childhood adversity, inhibition, Flanker, Drift Diffusion Modeling
-
-\pagebreak
 

### 2024-05-28 data/README.Rmd
clean old data files

---
title: ""
output: 
  html_document:
    template: ../assets/template.html
    css: ../assets/style.css
editor_options: 
  markdown: 
    wrap: sentence
---

## Data {#data}

All scripts to reproduce our analyses can be found under `preregistrations`, grouped per study.
Each study sub-folder contains an `analysis objects` folder, which contains both the raw and cleaned data files.
It is therefore possible to immediately run the primary analyses scripts (e.g., `1_primary_analyses.R`) without preprocessing the data first.
However, if you'd like to go through the analysis pipeline start-to-finish, you should take the following steps:

### 1. Loading Dependencies

1.  [`dependencies.R`](https://github.com/stefanvermeent/attention_project/blob/main/scripts/dependencies): Loads (and installs if necessary) all the necessary R packages as they were on 2024-01-01 using the [`Groundhog`](https://groundhogr.com/) package. 
This ensures that scripts will continue functioning as intended even after packages have been updated. 
`Groundhog` is a more lightweight, easy-to-use alternative to package dependency managers such as `renv`.

### 2. Data Preparation

Each study `script` folder contains a subfolder names `0_data_prep`. 
This subfolder contains all the scripts necessary to get from the (minimally) preprocessed data to the cleaned data.
The scripts are numbered, and should be run in that order.
Importantly, the `1_create_scales.R` script will not work, as it requires access to the raw data.
We do not share these raw data files as they contain variables that are not necessary for the analyses, as well as identifying information (e.g., Prolific IDs).
So, data preprocessing should start at `2_clean_self_report.R`.

**A note on running DDM models**. Please note that rerunning the DDM models takes a substantial amount of time, in particular the Hierarchical Bayesian DDM models and the SSP models.
The SSP model in particular, takes around 20-30 minutes per participant to complete.
Even in parallel, this will take multiple hours.
Thus, in most cases, it might be better to use the DDM result objects in each study's `analysis_objects` folder as a starting point.

Direct links to:

1.  [Pilot preprocessing scripts](https://github.com/stefanvermeent/attention_project/blob/main/1_pilot/scripts/0_data_prep).
2.  [Study 1 preprocessing scripts](https://github.com/stefanvermeent/attention_project/blob/main/2_study1/scripts/0_data_prep).
3.  [Study 2 preprocessing scripts](https://github.com/stefanvermeent/attention_project/blob/main/3_study2/scripts/0_data_prep).

### 3. Primary Analyses

The script for the primary analyses for each study can be found under `preregistrations/<study>/scripts`. 
This script reads in the cleaned data, runs all the analyses, and stores the main results as an .RData file under `preregistrations/<study>/analysis_objects`.

### 4. Manuscript

1.  [`manuscript/scripts/staging.R`](https://github.com/stefanvermeent/attention_project/blob/main/manuscript/scripts): This folder contains four scripts: one for each separate study, and one for the pooled analyses. These scripts load the .RData files stored in the `analysis_objects` folder, and states the statistics that are reported in the manuscript (e.g., creating Figures and Tables, and formatting descriptive statistics). The results per study are stored in a single .RData file under [`manuscript`](https://github.com/stefanvermeent/attention_project/blob/main/manuscript) (e.g., `study1_staged_results.RData`).
2.  [`manuscript/manuscript.qmd`](https://github.com/stefanvermeent/abcd_ddm/blob/main/manuscript/manuscript.qmd): loads the staged results and knits together the manuscript and all statistics, tables, and figures computed in previous scripts.

### 5. Supplement

1.  [`supplement/supplements.qmd`](https://github.com/stefanvermeent/attention_project/blob/main/supplement/supplements.qmd): loads the staged results list and knits together the written supplement and all tables and figures computed by the staging scripts.

### 6. Issues with dependencies? {#using_docker}

Even if you use the `dependencies.R` file to reinstate the correct versions of packages, the code might break over time as a result of changing operation systems or incompatibilities with future R versions.
To solve, this, we supply a Docker image that instantiates an Rstudio cloud environment with all the required dependencies.

In short, Docker provides a 'container'---similar to a virtual machine---with all the project dependencies (R packages, software, operating systems) pre-loaded in their (historic) versions as they were used when the project was created.
Thus, Docker ensures that scripts will still function as intended even into the future.
**Note: It is not necessary to use Docker to reproduce our results**.
If you're cloning the repository within a couple of years of publication and installing the proper dependencies (see step 1 below) you should be able to run all scripts without issues.
However, some of our scripts might stop to function properly over time as other dependencies get updated and/or deprecated (e.g., future versions of RStudio)
If that case, Docker is the solution.

Below is the exact order these scripts should be ran (irrespective of whether you are working with or without Docker):

If you want to create a Docker container in which to run the scripts, you will have to follow the following steps:

1.  Download and install docker at <https://docs.docker.com/get-docker/>.
2.  If on Windows, open the PowerShell. If on Mac, open the terminal through 'Applications \> Utilities \> Terminal'.
3.  On the command line, type: `docker run --rm -d -e PASSWORD=my_password -p 8787:8787 stefanvermeent/attention_project`
4.  Open a browser window and enter: `localhost:8787` as the URL.
5.  You will be redirected to an Rstudio cloud login page. As the username, type *rstudio*. As the password, type *my_password*, unless you changed it under step 3.
6.  You should now see an RStudio environment with the required dependencies pre-installed and loaded.

### 2024-05-28 README.Rmd
New top-level README file

--- 2024-05-28 data/README.Rmd
@@
   html_document:
-    template: ../assets/template.html
-    css: ../assets/style.css
+    template: assets/template.html
+    css: assets/style.css
+    keep_md: true
 editor_options: 
@@
 
-## Data {#data}
+```{r setup, include=F, echo=F}
+library(tidyverse)
+library(glue)
+devtools::load_all("D:/repositories/projectlog")
+#source('scripts/dependencies.R')
+
+knitr::opts_chunk$set("ft.shadow" = FALSE, echo = F, message = F, warning = F)
+
+```
+<br>
+This repository contains data, code, and output for a project entitled "Childhood adversity is not associated with lowered inhibition, but lower perceptual processing: A Drift Diffusion Model analysis".
+The manuscript is currently under review at *Cognitive Development*.
+
+Do you want to download or clone the materials for this project? Go to [https://github.com/stefanvermeent/attention_project](https://github.com/stefanvermeent/attention_project).
+
+## Directory Structure {#structure}
+
+The names of each folder are intended to be self-explanatory.
+There are eight top-level folders to organize the inputs and outputs of this project:
+
+1.  [`Manuscript`](https://stefanvermeent.github.io/attention_project/manuscript/README.html): The Registered Report written in Quarto.
+2.  [`Supplement`](https://stefanvermeent.github.io/attention_project/supplement/README.html): a supplemental text (to be submitted with the manuscript) documenting all secondary analyses in detail.
+3.
+[`Preregistrations`](https://stefanvermeent.github.io/attention_project/preregistrations/README.html): Contains a sub-folder for each study, which in turn contain all scripts, materials, analysis objects, and preregistration documents for that study (see below for more information).
+4.
+[`Data`](https://stefanvermeent.github.io/attention_project/data/README.html): Contains a sub-folder for each study, which in turn contain all raw and processed data files needed to reproduce the results.
+
+Click on each of the folders to get more details.
+
+## Overview of project milestones
+
+Below is an overview of all the project milestones, such as first-time data access, submissions, and revisions.
+Data access events were automatically captured using custom code, which over the course of this project was collected in the R package `projectlog` [https://stefanvermeent.github.io/projectlog/](https://stefanvermeent.github.io/projectlog/).
+For more information about how tracking worked, Go to the [Open science workflow tab](https://stefanvermeent.github.io/abcd_ddm/opensci_workflow/README.html).
+
+```{r results ='asis', echo = FALSE}
+milestones <- gert::git_tag_list() |> 
+  mutate(
+    tags = pmap(list(name = name, ref = ref, commit = commit), function(name, ref, commit) {
+      gert::git_commit_info(commit) |> 
+        as_tibble() |> 
+        select(commit = id, author, time, message) 
+    })
+  ) |> 
+  select(-commit, -ref) |> 
+  unnest(tags) |> 
+  separate(message, into = c("description", "hash", "code"), sep = "\\n") |> 
+  mutate(
+    name = map_chr(name, function(name) {
+      name |> 
+        str_remove("\\[\\[") |>
+        str_remove("\\d*$") |> 
+        str_replace("_", " ") |> 
+        str_to_title()
+    })
+  ) |> 
+  mutate(
+    code = str_remove_all(code, "^code\\s") |> str_replace_all(string = _, "\\|\\>", "\\|\\>\\\n"),
+    link_to_git = paste0(
+       gert::git_remote_list()$url |> str_remove(string = _, pattern = "\\.git$"), "/tree/", commit)
+    ) |>
+  arrange(desc(time))
+
+# Write scripts including code to .projectlog folder
+milestones |> 
+  pwalk(function(name,commit,author,time,description,hash,code,link_to_git){
+
+    if(name == "Data Access"){
+      code <- code |> 
+        str_replace_all(string = _, "\\|> ", "\\|>\n") |> 
+        str_remove(string = _, "^code ")
+
+      url <- gert::git_remote_list()$url |> 
+        str_remove(string = _, "\\.git$") |> 
+        paste0(paste0("/commit/", commit))
+
+      #  url <- "<anonymized repository>"
+
+      script <-
+        glue(
+          "
+          ### Date: {time}\n
+          ### Description: {description}\n\n
+          ### For more information on this commit, see the README file, or go to {url}\n
+          ### Below is the full code that was used to access the data:\n\n
+          {code}"
+        )
+
+      writeLines(script, con = paste0(".projectlog/", commit, ".R"))
+    }
+  })
+
+branch <- gert::git_branch_list() |> filter(local == TRUE) |> pull(name)
+
+# Print milestones
+glue_data(milestones, "  - **[{time}]({link_to_git}): {description}**
+        - **Milestone:** {name}
+        - **Data MD5 hash**: {hash}
+        - [Link to code snippet](https://github.com/StefanVermeent/liss_wm_profiles_2023/blob/{branch}/.projectlog/{commit}.R)
+        \n
+    ")
+
+```
+
+## How to reproduce this repository {#reproduce}
 
@@
 6.  You should now see an RStudio environment with the required dependencies pre-installed and loaded.
+
+### Contact
+
+For questions or comments, feel free to contact me at p.c.s.vermeent@gmail.com.

### 2024-05-28 preregistrations/README.Rmd
README file for preregistrations folder

---
title: ""
output: 
  html_document:
    template: ../assets/template.html
    css: ../assets/style.css
editor_options: 
  markdown: 
    wrap: sentence
---

# Links to analyses scripts

1.  [Pilot study](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/1_pilot/scripts)
2.  [Study 1](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/2_study1/scripts)
3.  [Study 2](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/3_study2/scripts)

# Links to Cognitive task materials

1.  [Pilot study](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/1_pilot/materials)
2.  [Study 1](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/2_study1/materials)
3.  [Study 2](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/3_study2/materials)

# Links to preregistrations

1.  [Pilot study](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/1_pilot)
2.  [Study 1](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/2_study1)
3.  [Study 2](https://github.com/StefanVermeent/attention_project/tree/main/preregistrations/3_study2)

### 2024-05-28 preregistrations/1_pilot/scripts/0_data_prep/1_create_scales.R

@@ -446,7 +446,7 @@ self_report <-
     by = "id"
    ) |> 
   select(
-    id, meta_start, meta_captcha, meta_resolution_ratio, meta_resolution_height, dems_edu, dems_class_current, matches("^(chaos|unp|pcunp|change|quic|unp_comp|violence|vio_comp|fighting|ses|fos|depression|impuls|dems_age|dems_sex|dems_gender|att_check01|att_check02|att_getup|att_interrupted|att_noise|attention)")
+    id, meta_start, meta_captcha, meta_resolution_ratio, meta_resolution_height, dems_edu, dems_class_current, matches("^(chaos|unp|pcunp|change|quic|unp_comp|violence|vio_comp|fighting|ses|fos|depression|impuls|dems_age|dems_sex|dems_gender|dems_ethnicity|dems_ethnicity_mixed|att_check01|att_check02|att_getup|att_interrupted|att_noise|attention)")
   )
 
 codebook <- create_codebook(self_report) %>%

### 2024-05-28 manuscript/manuscript_blinded_revised.qmd
Intermediate commit of revised manuscript files

--- 2024-04-02 manuscript/manuscript_blinded.qmd
@@
 
-The predominant view in developmental psychology is that exposure to adversity impairs cognitive abilities.
+The predominant view in developmental psychology is that exposure to adversity---defined as prolonged exposure to intense stress---impairs cognitive abilities.
 This view is supported by decades of research showing that people living in high-adversity contexts tend to score lower on a variety of cognitive tests [@hackman_2010; @ursache_2016].
 Recent adaptation-based perspectives, however, have argued that people from adversity may also develop intact, or enhanced, abilities for solving problems in high-adversity contexts [@ellis_2017; @frankenhuis_2013].
-Adaptation- and deficit-based perspectives are considered complimentary.
+Adaptation- and deficit-based perspectives are considered complementary.
 For instance, adversity may impair some cognitive processes, yet enhance others.
 Despite their compatibility, few studies have investigated how the interplay of impaired and enhanced abilities shapes performance.
-In this paper, across three preregistered online experiments, we used cognitive modeling to derive a process-level understanding of the association between childhood adversity and performance on the Flanker Task, a popular measure of cognitive control [@ridderinkhof_2021].
+Across three preregistered online experiments, we used cognitive modeling to derive a process-level understanding of the association between childhood adversity and performance in the Flanker task, a popular measure of cognitive control [@ridderinkhof_2021].
 
@@
 It is well-established that early-life adversity is associated with deficits in the ability to inhibit distracting, goal-irrelevant information [@hackman_2010; @ursache_2016].
-One of the leading paradigms in this literature is the Flanker Task [@eriksen_1974].
+One of the leading paradigms in this literature is the Flanker task [@eriksen_1974].
 On this task, participants typically see five arrows in a horizontal orientation, and are asked to indicate the direction of the central arrow.
 The flanking arrows point in the opposite direction on half of the trials, leading to interference that participants must inhibit.
-Slower performance on the Flanker has been documented for children and adults with lower childhood socioeconomic status [SES\; @farah_2006; @mezzacappa_2004; @noble_2005] and more environmental unpredictability [@fields_2021; @mittal_2015].
+Slower performance in the Flanker task has been documented for children and adults with more environmental unpredictability [@fields_2021; @mittal_2015].
 These findings are typically interpreted as indicating a deficit in the ability to inhibit distractions.
 
-Nonetheless, some recent studies suggest that growing up in adversity may also be associated with improved abilities such as attention shifting [@fields_2021; @mittal_2015; @young_2022; but see @nweze_2021].
-Some studies found deficit patterns on the Flanker alongside enhancements on other aspects of attention within the same participants.
-For example, in one study, children with lower SES performed less well on the Flanker, but outperformed children from higher SES on orienting their attention to salient cues and, peripheral cues [@mezzacappa_2004].
-Similarly, children with more caregiver switches (an indicator of unpredictability) were found to perform less well on the Flanker, but outperformed children with fewer caregiver switches on shifting their attention between different task goals [@fields_2021].
+Similar associations have been documented for factors that increase the risk of adversity exposure, such as lower socioeconomic status [SES\; @farah_2006; @mezzacappa_2004; @noble_2005].
+Although people living in low-SES conditions experience more adversity, on average, we do not regard low SES itself as a form of adversity. 
+First, SES and adversity can affect cognitive abilities through different mechanisms (e.g., education versus physiological stress). 
+Second, people with low SES have diverse experiences, both positive and negative, even if adversity is more common in this group.
+
+Some recent studies suggest that growing up in adversity may also be associated with improved abilities such as attention shifting [@fields_2021; @mittal_2015; @young_2022; but see @mezzacappa_2004; @nweze_2021].
+Some studies found deficit patterns on inhibition tasks alongside enhancements on other aspects of attention within the same participants.
+For example, one study found that young adults with more childhood unpredictability committed more errors on an Antisaccade task (a measure of inhibition), but more efficiently switched their attention between tasks on an attention shifting task [@mittal_2015].
+Similarly, children with more caregiver switches (an indicator of unpredictability) experienced more interference in the Flanker task (based on RTs), but outperformed children with fewer caregiver switches on shifting their attention between different task goals [@fields_2021].
 
@@
 While potentially adaptive, a more diffuse scope of attention could come at the cost of lowered ability to ignore irrelevant distractors.
-This could compromise more long-term goal-directed behavior, especially in chaotic environments (e.g., a noisy classroom or a busy street).
+This could compromise longer-term goal-directed behavior, especially in chaotic environments (e.g., a noisy classroom or a busy street).
 
-Thus, lowered performance on tasks like the Flanker could reflect either a cognitive impairment or a difference in attentional strategies.
+Thus, lowered performance on tasks like the Flanker task could reflect either a cognitive impairment or a difference in attentional strategies.
 Distinguishing between these two possibilities is challenging for two reasons.
@@
 Thus, it is unclear whether lowered inhibition is related to enhanced processing of peripheral information in people from from adverse backgrounds.
-Second, performance on inhibition tasks is---beyond the ability to inhibit distractors---also influenced by other factors, such as a person's general processing speed and response caution [@hedge_2022; @loffler_2022].
+Second, performance on inhibition tasks is---beyond the ability to inhibit distractors---also influenced by other factors, such as a person's general processing speed and response caution [@hedge_2022; @loffler_2024].
 This means that lowered performance on inhibition tasks does not necessarily reflect inhibition difficulties.
@@
 
-An important issue, therefore, is that several processes are involved in performance on the Flanker, and standard assessments using raw performance measures (response times, accuracy rates) mostly fail to distinguish between them.
-For example, performance differences on the Flanker could indicate that someone experiences more (or less) flanker interference, generally processes less (or more) efficiently, or responds with less (or more) caution.
+An important issue, therefore, is that several processes are involved in performance in the Flanker task, and standard assessments using raw performance measures (response times, accuracy rates) mostly fail to distinguish between them.
+For example, performance differences in the Flanker task could indicate that someone experiences more (or less) distractor interference, generally processes less (or more) efficiently, or responds with less (or more) caution.
 To understand how adversity affects performance, we need to be able to separate the difference processes that make up performance.
@@
 Formal cognitive models such as the Drift Diffusion Model [DDM\; @forstmann_2016; @ratcliff_1998; @ratcliff_2008; @ratcliff_2015; @wagenmakers_2009] provide a potential solution.
-The DDM estimates cognitive processes at different stages of the decision-making process (See Figure 1a).
+The DDM estimates explicitly models the cognitive processes underlying the decision-making (See Figure 1a).
 It represents decision-making on binary decision-making tasks as a process in which people accumulate information until one response is sufficiently favored over the other.
 These two response options are represented as opposing boundaries.
-One boundary corresponds to the correct response and the other to the incorrect response.
-When information accumulation reaches one of the two boundaries, the corresponding response is executed.
+One boundary corresponds to the correct response and the other to the incorrect response (note that in some research designs, the boundaries may be coded as the two choice options instead, for example, when the question is whether people classify a certain class of stimuli (e.g., angry faces) more efficiently than another class of stimuli (e.g., happy faces)).
+When the accumulated information reaches one of the two boundaries, the corresponding response is executed.
 
@@
 Larger boundary separation is associated with larger RTs and higher accuracy (i.e., sacrificing speed to increase accuracy).
-Finally, *non-decision time* represents the time it takes to prepare for the task at the start of the trial (before information processing) and the time it takes to execute a response (after a response boundary has been reached).
+*Non-decision time* represents the time it takes to prepare for the task at the start of the trial (before information accumulation starts) and the time it takes to execute a response (after a response boundary has been reached).
 Longer non-decision times are associated with larger RTs, without influencing accuracy.
+Finally, the *starting point* represents a potential bias towards one of two responses, with a biased decision-making process starting closer to one boundary relative to the other boundary.
 
-The Shrinking Spotlight (SSP) model is an extension of the standard DDM to account for attention processes on the Flanker [@grange_2016; @white_2018a; @white_2018b; @white_2011].
-The SSP model assumes that attention resembles a spotlight that is normally distributed over the Flanker arrows (with a particular starting *attentional width*).
-Over time, people narrow their attention down to the central arrow (at a rate defined by the *shrinking rate*), thereby gradually decreasing interference from irrelevant information (See Figure 1b).
+The Shrinking Spotlight (SSP) model is an extension of the standard DDM to account for attention processes in the Flanker task [@grange_2016; @white_2018a; @white_2018b; @white_2011].
+The SSP model assumes that attention resembles a spotlight that is normally distributed over the Flanker task arrows (with a particular starting *attentional width*).
+Over time, people narrow their attention down to the central arrow (at a rate defined by the *shrinking rate*), thereby gradually decreasing interference from irrelevant information [cf\.
+@eriksen_1986\; see Figure 1b).
 Prior work has defined the amount of distractor *interference* by dividing the attentional width by the shrinking rate [@white_2018a].
@@
 Finally, performance is also influenced by the *perceptual input* strength; that is, how well someone can process the arrows in general.
-Note that typical interpretations of lowered raw Flanker performance are in terms of the amount of interference that someone experiences, and not in terms of the strength of perceptual input.
-Here, we are interested in how childhood adversity is associated with both interference and the strength of perceptual input.
+Note that typical interpretations of lowered raw Flanker task performance are in terms of the amount of interference that someone experiences, and not in terms of the strength of perceptual input.
+
+The DDM and SSP model share many assumptions. 
+Both provide identical estimates of boundary separation and non-decision time. 
+The main difference is the decision-making phase. 
+The DDM assumes that the quality of the information is the same across the entire trial. 
+In contrast, the SSP model assumes that the quality of the information improves across the trial, as attention becomes gradually focused more on the central arrow. 
+The simpler assumption of the DDM makes the model broadly applicable, but less precise for conflict tasks. 
+The SSP model is more precise, but applicable only to the Flanker task. 
+Previous studies have successfully applied the DDM to Flanker task data [e.g., @loffler_2024; @vermeent_2024a].
+However, unlike the DDM, the SSP model affords testing hypotheses about the association between adversity and attentional interference in the Flanker task.
+Specifically, we are interested in how childhood adversity is associated with both interference and the strength of perceptual input.
+Finally, the SSP model is one of several completing diffusion models developed to explain performance on conflict tasks [@hubner_2010; @ulrich_2015].
+We focus exclusively on the SSP model because it performs well with relatively few trials per participant relative to other conflict diffusion models [@white_2018a].
 
@@
 In a third execution phase, people execute the motor response.
-The model estimates four parameters that reflect distinct cognitive processes (printed in italic): (1) The drift rate represents the average rate of evidence accumulation towards the correct decision boundary and measures processing speed; (2) The non-decision time represents both the time spent encoding the stimuli and executing the response; (3) The boundary separation represents how far apart has “set” their decision boundaries, and is a measure of the person’s level of response caution; (4) The starting point represents the starting point of the decision process and measures the level of response bias (not considered here).
-Panel B: The SSP is an extension of the standard DDM including additional parameters to capture attentional processes involved in Flanker performance.
+The model estimates four parameters that reflect distinct cognitive processes (printed in italic): (1) The drift rate represents the average rate of evidence accumulation towards the correct decision boundary and measures processing speed; (2) The non-decision time represents both the time spent encoding the stimuli and executing the response; (3) The boundary separation represents how far apart a person has “set” their decision boundaries, and is a measure of the person’s level of response caution; (4) The starting point (not considered here) represents a potential bias towards one of two responses, with a biased decision-making process starting closer to one boundary relative to the other boundary.
+Panel B: The SSP is an extension of the standard DDM including additional parameters to capture attentional processes involved in Flanker task performance.
 Each stimulus arrow provides a certain strength of perceptual input (*p*).
@@
 
+<br>
+
 # Overview of studies
@@
 Previous research shows that these two types of adversity are on the one hand associated with improved attention shifting and working memory updating [@fields_2021; @mittal_2015; @young_2018; @young_2022], and on the other hand with lowered inhibition and working memory capacity [@fields_2021; @mittal_2015; @young_2018].
-We conducted three online studies: one pilot and two follow-up studies.
-Using cognitive modeling, we unpack Flanker performance in comparison to other tasks that require externally focused attention (Pilot), across visual processing manipulations (Study 1), and in terms of tendencies for holistic versus local processing (Study 2).
+We conducted three online studies: one pilot study and two follow-up studies.
+Using cognitive modeling, we unpack Flanker task performance in comparison to other tasks that require externally focused attention (Pilot study), across visual processing manipulations (Study 1), and in terms of tendencies for holistic versus local processing (Study 2).
 
-We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see <https://anonymous.4open.science/r/CogDev_AnonLink>).
-For each study, we preregistered primary (i.e., hypothesis-driven) and exploratory analyses.
-The main text addresses the primary analyses involving violence exposure and the exploratory analyses involving environmental unpredictability.
+We used an incremental preregistration approach across studies (for all preregistrations, data, code and materials, see <https://anonymous.4open.science/r/CogDev_AnonLink>).
+For each study, we preregistered confirmatory (i.e., hypothesis-driven) and exploratory analyses.
+The main text addresses the confirmatory analyses involving violence exposure and the exploratory analyses involving environmental unpredictability.
 We describe the other exploratory analyses in the supplemental materials (section 2).
@@
 
-# Pilot
+# Pilot study
 
-In the Pilot, our goal was to understand how childhood adversity relates to performance on tasks with different attentional demands.
-Participants completed self-report measures of childhood adversity and three cognitive tasks.
+In the Pilot study, our goal was to understand how childhood adversity relates to performance on tasks with different attentional demands.
+Participants completed self-report measures of childhood adversity and three cognitive tasks (Flanker task, Cued Attention task, and Change Detection task).
 These tasks measured inhibition, attention for peripheral cues, and attention for subtle changes.
-We expected violence exposure to be positively associated with a present-oriented attention style.
-Specifically, we expected participants with more violence exposure to be better at detecting peripheral stimuli and subtle changes.
+In line with the idea that exposure to adversity may lead to a more diffuse scope of attention, we expected people with more violence exposure to be better at detecting peripheral stimuli and subtle changes.
 We expected this would result in a higher drift rate (faster speed of information accumulation) or shorter non-decision times (faster attention orientation, among other things), but not necessarily with differences in boundary separation (response caution).
-Second, we expected that participants with more violence exposure would be worse at ignoring distracting peripheral stimuli.
+In contrast, we expected that participants with more violence exposure would be worse at ignoring distracting peripheral stimuli.
 We expected this would result in more experienced interference (as derived from the SSP model).
@@
 Participants were eligible if they spoke fluent English and did not report color-blindness.
+We obtained ethical approval from the first author's institute (anonymized for peer review).
 
@@
 Fifth, on a trial-level, we excluded any trials with reaction times \< 250 ms or \> 3500 ms [@ratcliff_2015].
-Participants with more than 10 trials removed were completely excluded from the analyses.\
+Participants with more than 10 trials removed were completely excluded from the analyses.
 The final sample consisted of `r nrow(pilot_data)` participants.
@@
 
-**Flanker Task.** The Flanker measures selective attention and response inhibition [@eriksen_1974].
-The Flanker began with eight practice trials, followed by 64 test trials.
+**Flanker task.** The Flanker task measures selective attention and response inhibition [@eriksen_1974].
+The Flanker task began with eight practice trials, followed by 64 test trials.
 On each trial, participants saw a set of five arrows pointing either left or right.
-Participants were instructed to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right.
+Participants were instructed to indicate the direction of the central arrow by pressing the respective arrow keys, while ignoring the flanking arrows to the left and right.
 All trials included black arrows against a white background.
-On the *congruent* trials (50%), the flanking arrows pointed in the same direction as the central arrow.
-On the *incongruent* trials (50%), the arrows pointed in the opposite direction.
+in the *congruent* trials (50%), the flanking arrows pointed in the same direction as the central arrow.
+in the *incongruent* trials (50%), the arrows pointed in the opposite direction.
 The arrows were randomly presented in the top-half or bottom-half of the screen.
@@
 
-**Cued Attention Task.** The Cued Attention Task was an adapted version of the Posner task, which measures the speed of attention for peripheral cues [@posner_1980].
-The Cued Attention Task began with eight practice trials, followed by 64 test trials.
+**Cued Attention task.** The Cued Attention task was an adapted version of the Posner task, which measures the speed of attention for peripheral cues [@posner_1980].
+The Cued Attention task began with eight practice trials, followed by 64 test trials.
 On each trial, a left- or right-pointing arrow was presented in one of eight random locations at 300 pixels from the center of the screen.
@@
 
-**Change Detection Task.** The Change Detection Task measures the ability to detect subtle spatial changes.
-The Change Detection Task started with five practice trials followed by 50 test trials.
+**Change Detection task.** The Change Detection task measures the ability to detect subtle spatial changes.
+The Change Detection task started with five practice trials followed by 50 test trials.
 On each trial, participants saw five colored circles (red, light-blue, dark-blue, yellow, and purple) against a gray background, each with a radius of 15 pixels.
@@
 On *no change* trials (50%), all circles were still in the same location.
-Participants were instructed to indicate whether all circles were still in the same location or one of the circles had changed location.
+Participants were instructed to indicate whether all circles were still in the same location or one of the circles had changed location by pressing the left- or right-arrow key.
 The displacement of *one* circle was the only potential difference on each trial;
 
-**DDM/SSP parameters.** We analyzed the Flanker with the SSP model [@grange_2016; @white_2018a; @white_2018b; @white_2011], using the *flankr* package [@grange_2016].
+**DDM/SSP parameters.** We analyzed Flanker task performance with the SSP model [@grange_2016; @white_2018a; @white_2018b; @white_2011], using the *flankr* package [@grange_2016].
 For each participant, the SSP provided us with estimates of: (1) strength of perceptual input (general quality of information that participants get from the arrows), (2) interference (initial attention width divided by the speed at which attention is narrowed down to the central arrow), (3) non-decision time (combination of speed of initial stimulus encoding and response execution), and (4) boundary separation (response caution).
-Our focus on interference as a ratio between attention width and shrinking rate was a deviation from the preregistration, as we initially planned to investigate both aspects of attention separately.
+We always fixed the starting-point to the midpoint between the two boundaries, as modeling bias makes little sense when the boundaries correspond to correct and incorrect responses (as is the case here), rather than the distinct response options.
+Our focus on interference as a ratio between attention width and shrinking rate deviated from the preregistration, as we initially planned to investigate both aspects of attention separately.
 However, we discovered that both parameters in isolation were unreliable because of an inherent trade-off, while the ratio did provide a stable measure.
@@
 
-For the Change Detection Task and the Cued Attention Task, we used a hierarchical Bayesian implementation of the standard DDM (HDDM).
-For each participant, the HDDM provided us with estimates of: (1) drift rate (speed of information accumulation; analogous to strength of perceptual input in the SSP model, except that drift rate is time-invariant), (2) non-decision time (same as SSP model), and (3) boundary separation (same as SSP model).
+For the Change Detection task and the Cued Attention task, we used a hierarchical Bayesian implementation of the standard DDM (HDDM).
+For each participant, the HDDM provided us with estimates of: (1) drift rate (speed of information accumulation; analogous to strength of perceptual input in the SSP model, except that drift rate is time-invariant), (2) non-decision time (same as in the SSP model), and (3) boundary separation (same as in the SSP model).
 The hierarchical Bayesian fitting procedure was a deviation from the preregistration, in which we planned to use Maximum Likelihood (ML) estimation.
@@
 An important difference between HDDM and ML is that HDDM uses the group information to inform individual parameter estimates, whereas ML models are fitted to each individual separately.
-This generally improves the accuracy of the estimation.
-See the supplemental materials (section 3) for an overview of the fit procedure and model fit across all models.
+The hierarchical approach generally improves generally improves the accuracy of the estimation.
+See the supplemental materials (section 3) for an overview of the fit procedure and model fit across all studies.
 
@@
 Finally, we included four objective measures of unpredictability before age 13: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "How many romantic partners did your mother have (not counting your father)?"; 4) "How many romantic partners did your father have (not counting your mother)?".
+Previous studies have found associations between (subsets of) these measures and subjective measures of adversity as well as with developmental outcomes [@belsky_2012; @ellis_2009; @young_2022].
+
+\pagebreak
 
@@
 
-### Primary analyses
-
-For the Cued Attention Task and Flanker RTs, we used linear mixed effects models to test violence exposure x task condition (sum-coded) interactions on mean RTs and each DDM parameter.
+**Confirmatory analyses.** For the Cued Attention and Flanker task RTs, we used linear mixed effects models to test violence exposure x task condition (sum-coded) interactions on mean RTs (calculated separately for each condition) and each DDM parameter.
 All mixed effects models included a random intercept for participants.
-For the Change Detection Task and Flanker SSP parameters, we used linear regression models to test the main effect of adversity on mean RTs and each DDM/SSP parameter.
-To meet model assumptions of normally distributed residuals, reaction times were log-transformed.
-Analyses involving interference (Flanker) and boundary separation (all tasks) parameters violated the assumption of normally distributed residuals.
+For the Change Detection and Flanker task SSP parameters, we used linear regression models to test the main effect of adversity on mean RTs and each DDM/SSP parameter.
+We did not analyze accuracy rates as these were close to ceiling for the Flanker and Cued Attention task.
+To meet model assumptions of normally distributed residuals, mean reaction time were log-transformed, separately for the congruent and incongruent condition.
+Analyses involving interference (Flanker task) and boundary separation (all tasks) parameters violated the assumption of normally distributed residuals.
 For boundary separation, we solved this using log-transformation.
@@
 Table 3 summarizes the results.
-More violence exposure was associated with lower strength of perceptual input under `r pilot_main_eff_ddm_list$Flanker_p$p_sum_Main`% of multiverse specifications (although the median 95% CI interval contained zero).
+In the flanker task, More violence exposure was associated with lower strength of perceptual input under `r pilot_main_eff_ddm_list$Flanker_p$p_sum_Main`% of multiverse specifications (although the median 95% CI interval contained zero).
 We additionally found a significant main effect of violence exposure on interference under `r pilot_main_eff_ddm_list$Flanker_interference$p_sum_Main`% of multiverse specifications, such that more violence exposure was associated with less interference.
@@
 
-Participants with more exposure to childhood violence were slower on the Cued Attention Task, which was mainly related to a higher level of response caution (boundary separation).
-On the Change Detection Task, more childhood violence exposure was associated with slower speed of information processing (drift rate) under `r pilot_main_eff_ddm_list$Change_v$p_sum_Main`% of multiverse specifications, but not with longer RTs.
+Participants with more exposure to childhood violence were slower in the Cued Attention task, which was mainly related to a higher level of response caution (boundary separation).
+in the Change Detection task, more childhood violence exposure was associated with slower speed of information processing (drift rate) under `r pilot_main_eff_ddm_list$Change_v$p_sum_Main`% of multiverse specifications, but not with longer RTs.
 These results were not in line with our expectation that people from adversity would perform better on cognitive tasks that require a broad, present-focused attention style.
 
-<br>
+Exploratory analyses did not show any significant associations with Flanker task performance.
+Participants with more exposure to childhood unpredictability were slower in the Cued Attention task (main effect) (median $\beta$ = `r pilot_expl_eff_ddm_list$cueing_rt$median_effect_Main`, 95% CI = `r pilot_expl_eff_ddm_list$cueing_rt$Main_CI`, `r pilot_expl_eff_ddm_list$cueing_rt$p_sum_Main` % of *p*s \<.05), which was related to slower non-decision time (median $\beta$ = `r pilot_expl_eff_ddm_list$cueing_t0$median_effect_Main`, 95% CI = `r pilot_expl_eff_ddm_list$cueing_t0$Main_CI`, `r pilot_expl_eff_ddm_list$cueing_t0$p_sum_Main` % of *p*s \<.05).
+We did not find a significant association between exposure to childhood unpredictability and mean RTs on the Change Detection task, although more unpredictability was negatively associated with drift rates (median $\beta$ = `r pilot_expl_eff_ddm_list$Change_v$median_effect_Main`, 95% CI = `r pilot_expl_eff_ddm_list$Change_v$Main_CI`, `r pilot_expl_eff_ddm_list$Change_v$p_sum_Main` % of *p*s \<.05).
+
+\pagebreak
 
@@
 
-The pattern of findings on the Flanker was interesting for two reasons.
-First, the Flanker is a widely used task to assess the ability to inhibit irrelevant information, and people exposed to adversity typically show lowered performance.
+The pattern of findings in the Flanker task was interesting for two reasons.
+First, the Flanker task is a widely used task to assess the ability to inhibit irrelevant information, and people exposed to adversity typically show lowered performance.
 Our pilot results, though, suggest that lowered performance may not be caused by a reduced ability to inhibit distracting information.
@@
 
-The goal of Study 1 was to follow up on the Pilot by manipulating the visual quality of information on the Flanker.
-Participants completed three versions: a standard version (similar to the Pilot), one with enhanced visual information, and one with degraded visual information.
+The goal of Study 1 was to follow up on the Pilot study by manipulating the visual quality of information in the Flanker task.
+Participants completed three versions: a standard version (similar to the Pilot study), one with enhanced visual information, and one with degraded visual information.
 We again focused on childhood exposure to violence.
-Our first aim was to examine the robustness of our finding of improved interference control on the Flanker in relation to more adversity exposure in the pilot.
-We did so by analyzing the data of the standard condition, as well as by pooling the data of the Pilot and Study 1.
-Our second aim was to investigate whether manipulating visual information on the Flanker would influence performance for people with more violence exposure.
+Our first aim was to examine the robustness of our finding of improved interference control in the Flanker task in relation to more adversity exposure in the Pilot study.
+We did so by analyzing the data of the standard condition, as well as by pooling the data of the Pilot study and Study 1.
+Our second aim was to investigate whether manipulating visual information in the Flanker task would influence performance for people with more violence exposure.
 
@@
 First, the strength of perceptual input might be lower for people with more exposure to violence compared to people with less exposure to violence across all conditions.
-Second, lower performance on the standard version might reflect an adaptive trade-off towards cognitive functioning that is less affected by noise or perturbations, at a cost of lower overall performance [@giudice_2018].
+Second, lower performance in the standard version might reflect an adaptive trade-off towards cognitive functioning that is less affected by noise or perturbations, at a cost of lower overall performance [@giudice_2018].
 In that case, we would expect the strength of perceptual input to be influenced to a lesser extent across conditions for people with more exposure to violence than for people with less exposure to violence.
@@
 
-Participant recruitment was identical to the Pilot.
+Participant recruitment was identical to the Pilot study.
 In total, 567 people from the United States between the ages of 18 and 30 participated (See Table 1).
-We applied the same exclusion criteria as reported in the Pilot.
+We obtained ethical approval from the first author's institute (anonymized for peer review).
+We applied the same exclusion criteria as reported in the Pilot study.
 The final sample consisted of `r nrow(study1_data)` participants.
 
-### Flanker Task
+### Flanker task
 
-We programmed the Flanker in JsPsych version 6.3.1 [@deleeuw_2015] with three conditions.
+We programmed the Flanker task in JsPsych version 6.3.1 [@deleeuw_2015] with three conditions.
 Each condition consisted of eight practice trials, followed by 64 test trials.
@@
 This increased the width of the stimulus display by 50% with respect to the standard display.
-In the 'degraded' condition, sizes and space between arrows were the same as in the standard version, but all arrows were rotated 45$^\circ$ (in the same direction; that is, if the left flanker arrows pointed upwards, the right flanker arrows pointed downward).
+In the *degraded* condition, sizes and space between arrows were the same as in the standard version, but all arrows were rotated 45$^\circ$.
+The lines of the arrows always had the same 45$^\circ$ angle.
+For example, if the flanking arrows pointed to the upper-left on an incongruent trial, the central arrow pointed to the lower-right.
+On congruent trials, all arrows pointed in the same direction (e.g., upper-right).
 Participants completed each condition separately in different blocks, in randomized order.
@@
 
-The self-report measures were identical to those used in the Pilot.
+The self-report measures were identical to those used in the Pilot study.
 
@@
 
-The procedure was identical to the pilot study.
+The procedure was identical to the Pilot study.
 The full experiment took approximately 30 minutes.
@@
 
-**Multiverse analysis.** We included the same arbitrary decisions in the multiverse analyses as in the Pilot.
-For the pooled analyses---i.e., joint analysis of the Pilot and the standard condition of Study 1---there was one minor change in how we included screen rescaling as a preprocessing decision in the multiverse.
+**Multiverse analysis.** We included the same arbitrary decisions in the multiverse analyses as in the Pilot study.
+For the pooled analyses---i.e., joint analysis of the Pilot study and the standard condition of Study 1---there was one minor change in how we included screen rescaling as a preprocessing decision in the multiverse.
 In Study 1, we changed the screen rescaling procedure by converting the initial size of the resize box to 300 pixels instead of 100 pixels.
 This way, the stimulus display would still be close to the intended size if participants did not engage in any resizing.
-However, this led to one important change for the pooled analysis: rescaling (yes or no) was included as an arbitrary exclusion decision in the multiverse analyses with four combinations: (1) exclude non-scalers in both studies; (2) include non-scalers in both studies; (3) exclude non-scalers in the Pilot, include non-scalers in Study 1; (4) include non-scalers in the Pilot, exclude non-scalers in Study 1.
+However, this led to one important change for the pooled analysis: rescaling (yes or no) was included as an arbitrary exclusion decision in the multiverse analyses with four combinations: (1) exclude non-scalers in both studies; (2) include non-scalers in both studies; (3) exclude non-scalers in the Pilot study, include non-scalers in Study 1; (4) include non-scalers in the Pilot study, exclude non-scalers in Study 1.
 
 For each analysis, we report the median $\beta$s, 95% confidence intervals, and the proportion of *p*-values \< .05 across all analytic decisions.
-For the primary analyses, we used bootstrapping to compute the probability of obtaining an effect size at least as extreme as observed in the real data, conditioned on a true effect size of zero [for details, see @simonsohn_2020].
+For the confirmatory analyses, we used bootstrapping to compute the probability of obtaining an effect size at least as extreme as observed in the real data, conditioned on a true effect size of zero [for details, see @simonsohn_2020].
 See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
 
-**Primary analyses.** To address the first aim, we analyzed the data from the standard condition, as well as pooled the Flanker data of the Pilot and the current study.
-We ran separate linear models for each SSP parameter as well as RT difference scores with violence exposure as main predictor and study as covariate (effect-coded).
-To address the second aim, we analyzed the effect of violence exposure and Flanker condition type on performance using linear mixed effects models with a random intercept per participant.
-The five main dependent variables were mean RT difference and the SSP parameters: Perceptual input, boundary separation, non-decision time, and interference.
+**Confirmatory analyses.** To address the first aim, we analyzed the data from the standard condition, as well as pooled the Flanker task data of the Pilot study and the current study.
+We ran separate linear models for each SSP parameter as well as RT difference scores (based on log-transformed mean RTs of each condition) with violence exposure as main predictor and study as covariate (effect-coded).
+To address the second aim, we analyzed the effect of violence exposure and Flanker task condition type on performance using linear mixed effects models with a random intercept per participant.
+The five main dependent variables were mean RT difference (based on log-transformed mean RTs of each condition) and the SSP parameters: Perceptual input, boundary separation, non-decision time, and interference.
 For each outcome measure, we ran two separate models: one comparing the standard condition with the enhanced condition, and one comparing the standard condition with the degraded condition.
 In both models, condition was dummy-coded using the standard condition as the reference group.
+
+The use of RT difference scores differed from the Pilot study, where we included task condition as a moderator.
+We opted for RT difference scores here (as well as in Study 2) to prevent the use of three-way interactions, for which we did not have enough power.
 
@@
 
-Table 4 summarizes the multiverse results for the effects of violence exposure (primary analysis) and unpredictability (exploratory analysis).
-Unlike in the Pilot, we did not find any significant associations with violence exposure.
+Table 4 summarizes the multiverse results for the effects of violence exposure (confirmatory analysis) and unpredictability (exploratory analysis).
+Unlike in the Pilot study, we did not find any significant associations with violence exposure.
 In the exploratory analysis, there was a significant negative association between unpredictability and perceptual input (median $\beta$ = `r study1_expl_results_list$p_flanker$median_effect_Main`, 95% CI = `r study1_expl_results_list$p_flanker$CI`, `r study1_expl_results_list$p_flanker$p_sum` % of *p*s \<.05).
+
+\pagebreak
 
@@
 
-After pooling the data of the pilot study and Study 1, there was a negative association between violence exposure and interference (median $\beta$ = `r study1_pooled_results_list$interference_vio$median_effect`, 95% CI = `r study1_pooled_results_list$interference_vio$CI`, `r study1_pooled_results_list$interference_vio$p_sum` % of *p*s \<.05, bootstrapped *p* = `r study1_pooled_results_list$interference_vio$boot_p`).
+After pooling the data of the Pilot study and Study 1, there was a negative association between violence exposure and interference (median $\beta$ = `r study1_pooled_results_list$interference_vio$median_effect`, 95% CI = `r study1_pooled_results_list$interference_vio$CI`, `r study1_pooled_results_list$interference_vio$p_sum` % of *p*s \<.05, bootstrapped *p* = `r study1_pooled_results_list$interference_vio$boot_p`).
 Violence exposure was associated with lower strength of perceptual input under `r study1_pooled_results_list$interference_vio$p_sum`% of multiverse specifications, but the bootstrapped *p*-value was not significant (median $\beta$ = `r study1_pooled_results_list$p_vio$median_effect`, 95% CI = `r study1_pooled_results_list$p_vio$CI`, bootstrapped *p* = `r study1_pooled_results_list$p_vio$boot_p`).
@@
 
-### Flanker conditions
+### Flanker task conditions
 
@@
 
-\pagebreak
+<br>
 
@@
 
-The results of the Pilot and Study 1 were inconsistent with regard to the association between adversity and interference, but hinted at two general patterns.
+<br>
+
+The results of the Pilot study and Study 1 were inconsistent with regard to the association between adversity and interference, but hinted at two general patterns.
 First, violence exposure was not associated with *increased* interference; instead, we found either the opposite effect or no effect.
 Second, both violence exposure and unpredictability were associated with lowered strength of perceptual input, albeit inconsistently.
-These findings, if replicable, are intriguing as they would suggest that the common finding of lowered Flanker performance among people with more adversity exposure do not actually result from worse interference control---as typically inferred.
+These findings, if replicable, are intriguing as they would suggest that the common finding of lowered Flanker task performance among people with more adversity exposure do not actually result from worse interference control---as typically inferred.
 Rather, such lowered performance would result from processes other than inhibition ability, such as slower general processing.
@@
 
-Study 2 set out to compare two explanations for the finding that people exposed to adversity tended to show lower strength of perceptual input on the Flanker.
+Study 2 set out to compare two explanations for the finding that people exposed to adversity tended to show lower strength of perceptual input in the Flanker task.
 First, lowered strength of perceptual input in people exposed to adversity may indicate a difficulty in extracting relevant information (i.e., about their direction) from the arrows in general.
@@
 People exposed to adversity may process information more holistically, focusing more on the configuration of pieces of information rather than individual pieces of information.
-On the Flanker, this would lower the depth of perceptual processing of any individual stimulus, thus resulting in lowered strength of perceptual input, as we observed in the Pilot and Study 1.
+in the Flanker task, this would lower the depth of perceptual processing of any individual stimulus, thus resulting in lowered strength of perceptual input, as we observed in the Pilot study and Study 1.
 
@@
 First, we expected to replicate our earlier findings that adversity was associated with lowered perceptual input and lower interference in people exposed to adversity.
-Second, we included a Global-Local Task to investigate the hypothesis---based on the findings of the Pilot and Study 1---that people with more adverse experiences would develop a more holistic style of information processing.
-Third, we planned to conduct a within-subjects analysis of Flanker and Global-Local performance to assess whether people with lowered perceptual input on the Flanker Task would also show a more global processing style (rather than a local processing style) on the Global-Local Task.
+Second, we included a Global-Local task to investigate the hypothesis---based on the findings of the Pilot study and Study 1---that people with more adverse experiences would develop a more holistic style of information processing.
+Third, we planned to conduct a within-subjects analysis of Flanker and Global-Local task performance to assess whether people with lowered perceptual input in the Flanker task would also show a more global processing style (rather than a local processing style) in the Global-Local task.
 
@@
 Recruitment was identical to Study 1.
-We conducted a simulation-based power analysis for the planned linear mixed models with the Global Local Task (see GitHub).
+We obtained ethical approval from the first author's institute (anonymized for peer review).
+We conducted a simulation-based power analysis for the planned linear mixed models with the Global Local task (see GitHub).
 We determined that power of \> .80 for a standardized interaction effect of 0.06, with sigma (noise) set to 0.7 (comparable to observed sigmas in the first two studies) would require 550 participants.
 We recruited 600 participants, with the expectation to have a final sample of 550 participants after exclusions.
-We applied the same exclusion criteria as reported in the Pilot and Study 1.
+We applied the same exclusion criteria as reported in the Pilot study and Study 1.
 The final sample consisted of `r nrow(study2_data)` participants.
@@
 The measures of childhood violence exposure and environmental unpredictability were identical to Study 1.
-The Flanker was identical to the standard version used in Study 1.
+The Flanker task was identical to the standard version used in Study 1.
 
-*Global-Local Task*.
-The Global-Local Task is a measure of global-local processing [@navon_1977].
+*Global-Local task*.
+The Global-Local task is a measure of global-local processing [@navon_1977].
 Many different versions of this task exist in the literature.
@@
 
-Participants saw images of big, black letters (the global level) comprised of small letters (the local level)---so-called Navon images [@navon_1977]---against a white background.
+Participants saw images of big, black letters (the global level) comprising small letters (the local level)---so-called Navon images [@navon_1977]---against a white background.
 Participants first completed eight practice trials, after which they completed an additional 64 test trials.
-On each trial, participants searched for one of two target letters---an 'E' or 'H'---and indicated whether it was present on the global or local letter by pressing 'g' or 'l' on their keyboard, respectively.
-Each stimulus was 600 pixels high and 395 pixels wide and comprised of seven local letters vertically and five local letters horizontally.
-All stimuli consisted of combinations of the letters 'T', 'F', 'P', 'L', 'H', and 'E'.
-The target letters 'H' and 'E' were both present in each stimulus, but the other letters varied.
-The global and local level never contained the same letter.
+On each trial, participants searched for one of two target letters---an 'E' or 'H'---and indicated whether it was present on the global or local level by pressing 'g' or 'l' on their keyboard, respectively.
+Each stimulus was 600 pixels high and 395 pixels wide and comprised seven local letters vertically and five local letters horizontally.
+The stimuli consisted of combinations of the letters 'T', 'F', 'P', 'L', 'H', and 'E'.
+All stimuli always contained one (and only one) of the target letters 'H' and 'E' on either the local or global level.
+The other letters were randomly varied, and the global and local level never contained the same letter.
+Thus, the global-local task did not contain a congruent and incongruent condition as did the Flanker task.
 
@@
 **Multiverse analysis.** We included the same decisions in the multiverse as in the previous studies.
-However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, <https://anonymous.4open.science/r/CogDev_AnonLink/preregistrations/3_study2>).
+However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot study and Study 1, instead of a subset, as we preregistered (for details, <https://anonymous.4open.science/r/CogDev_AnonLink/preregistrations/3_study2>).
 See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
 
-**DDM estimation.** For the Flanker, we used the SSP [@grange_2016; @white_2018a; @white_2018b; @white_2011] using the same procedure as in Study 1.
-For the Global-Local Task, we used a hierarchical Bayesian DDM to fit the data using the *runjags* package [@denwood_2016].
+**DDM estimation.** For the Flanker task, we used the SSP [@grange_2016; @white_2018a; @white_2018b; @white_2011] using the same procedure as in Study 1.
+For the Global-Local task, we used a hierarchical Bayesian DDM to fit the data using the *runjags* package [@denwood_2016].
 See the supplemental materials (Section 3) for more information about the procedure and model fit.
 
-We deviated from our preregistration regarding the preprocessing of Global-Local Task data.
+We deviated from our preregistration regarding the preprocessing of Global-Local task data.
 Specifically, we relaxed the low performance threshold as the task was more difficult than anticipated.
@@
 
-**Primary analyses.** We ran simple regressions for analyses involving only main effects (aim 1), and linear mixed effects models for analyses involving within-subject interactions (aim 2 and 3).
-To address aim 3 (within-subject interaction between Global-Local drift rate and Flanker strength of perceptual input), we further preprocessed the data in two steps.
+**Confirmatory analyses.** We ran simple regressions for analyses involving only main effects (aim 1), and linear mixed effects models for analyses involving within-subject interactions (aim 2 and 3).
+To address aim 3 (within-subject interaction between Global-Local task drift rate and Flanker task strength of perceptual input), we further preprocessed the data in two steps.
 First, we computed a difference score of Global-Local drift rates by subtracting the drift rate on local trials from the drift rate on global trials (with higher scores reflecting relatively faster information processing on global trials).
-Second, we separately standardized the Flanker strength of perceptual input and Global-Local drift rate difference.
-We fitted linear mixed effects models with the standardized performance measures as the dependent variable, and adversity type, task (Flanker or Global-Local, sum-coded) and their interaction as independent variables.
+Second, we separately standardized the Flanker task strength of perceptual input and Global-Local task drift rate difference.
+We fitted linear mixed effects models with the standardized performance measures as the dependent variable, and adversity type, task (Flanker task or Global-Local task, sum-coded) and their interaction as independent variables.
 
@@
 Figure 2 and 3 summarize the multiverse results for the effects of violence exposure and unpredictability within Study 2 and pooled across all studies.
-In Study 2, violence exposure was negatively associated with strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.vio_comp$boot_p`), but not associated with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$boot_p`).
+In Study 2, violence exposure was negatively associated with strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* `r study2_aim1_results_study2_list$p_flanker.vio_comp$boot_p`), but not associated with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$boot_p`).
 Unpredictability was not associated with either strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.unp_comp$boot_p`), nor with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$boot_p`).
@@
 In the pooled analysis, the results were similar for both types of adversity.
-Violence exposure was associated with lower strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.vio_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.vio_comp$boot_p`).
+Violence exposure was associated with lower strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* `r study2_aim1_results_list$p_flanker.vio_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.vio_comp$boot_p`).
 Similarly, unpredictability was associated with a lower quality of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_list$p_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.unp_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_list$interference_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.unp_comp$boot_p`).
@@
 #| fig-cap: | 
-#|   **Figure 2.** Multiverse results for the association between violence exposure with the strength of perceptual input and interference on the Flanker across all studies.
+#|   **Figure 2.** Multiverse results for the association between violence exposure with the strength of perceptual input and interference in the Flanker across all studies.
 Each panel depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-The top row depicts effect curves in the Pilot.
+The top row depicts effect curves in the Pilot study.
 The second row depicts effect curves in Study 1.
@@
 #| fig-cap: | 
-#|   **Figure 3.** Multiverse results for the association between unpredictability with the strength of perceptual input and interference on the Flanker across all studies.
+#|   **Figure 3.** Multiverse results for the association between unpredictability with the strength of perceptual input and interference in the Flanker task across all studies.
 Each panel depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-The top row depicts effect curves in the Pilot.
+The top row depicts effect curves in the Pilot study.
 The second row depicts effect curves in Study 1.
@@
 
-### Global-Local Task performance
+### Global-Local task performance
 
@@
 There was a significant main effect of unpredictability on drift rates, with more unpredictability being associated with slower speed of information processing, ($\beta$~median~ = `r study2_aim2_results_list$Main_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Main_unp$CI`, `r study2_aim2_results_list$Main_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Main_unp$boot_p`).
-We also found a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Condition_vio$CI`, `r study2_aim2_results_list$Condition_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Condition_unp$boot_p`).
+We also found a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Condition_vio$CI`, `r study2_aim2_results_list$Condition_unp$p_sum` % of *p*s \< .05, bootstrapped *p* `r study2_aim2_results_list$Condition_unp$boot_p`).
 We did not find a significant unpredictability x task condition interaction effect ($\beta$~median~ = `r study2_aim2_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Interaction_unp$CI`, `r study2_aim2_results_list$Interaction_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_unp$boot_p`).
 
-### Within-subjects comparison of Flanker and Global-Local information processing
+### Within-subjects comparison of Flanker and Global-Local task information processing
 
-There was no significant main effects for violence exposure (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`) nor for cognitive task (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`).
+There were no significant main effects for violence exposure (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`) nor for cognitive task (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`).
 There was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_vio$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_vio$CI`, `r study2_aim3_results_list$Interaction_vio$p_sum` % of *p*s \< .05, bootstrapped *p* `r study2_aim3_results_list$Interaction_vio$boot_p`) (See Figure 2).
-A simple slopes analysis revealed that people with higher levels of violence exposure showed lower strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$vio_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.Flanker$p_sum`% of *p*s \< .05), and showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$p_sum`% of *p*s \< .05).
+A simple slopes analysis revealed that people with higher levels of violence exposure showed lower strength of perceptual input in the Flanker task (b = `r study2_aim3_simslopes1_list$vio_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.Flanker$p_sum`% of *p*s \< .05), and showed a more global versus local processing style in the Global-Local task (b = `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$p_sum`% of *p*s \< .05).
 
@@
 However, there was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_unp$CI`, `r study2_aim3_results_list$Interaction_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim3_results_list$Interaction_unp$boot_p`).
-A simple slopes analysis revealed that people with higher levels of unpredictability did not differ in their strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$unp_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.Flanker$p_sum` % of *p*s \< .05), but showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$p_sum`% of *p*s \< .05).
+A simple slopes analysis revealed that people with higher levels of unpredictability did not differ in their strength of perceptual input in the Flanker task (b = `r study2_aim3_simslopes1_list$unp_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.Flanker$p_sum` % of *p*s \< .05), but showed a more global versus local processing style in the Global-Local task (b = `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$p_sum`% of *p*s \< .05).
 
@@
 #| fig-cap: | 
-#|   **Figure 4.** Multiverse results for the within-subjects comparison of Flanker and Global-Local information processing.
+#|   **Figure 4.** Multiverse results for the within-subjects comparison of Flanker and Global-Local task information processing.
 Panel A depicts the multiverse interaction effects, with the thick black lines denoting the median slope and the thin lines denoting effects for each combination of arbitrary decisions.
@@
 To sum up, Study 2 provided additional support for the basic finding that violence exposure and unpredictability were associated with lower strength of perceptual input but not with differences in interference; with the caveat that the associations for unpredictability only showed up in pooled analyses.
-People with more exposure to violence and unpredictability also processed information more slowly on the Global-Local Task.
+People with more exposure to violence and unpredictability also processed information more slowly in the Global-Local task.
 In line with our expectations, childhood exposure to violence was associated with both lowered strength of perceptual input and a more holistic processing style.
@@
 Although short-term mindsets are associated with exposure to adversity [@ganschow_2023], it is unclear how they are associated with performance on attention tasks.
-We explored bivariate correlations pooled across all studies between two indicators of short-term mindsets (impulsivity and future orientation) and SSP parameters of the Flanker (for more information on the measures, see section 1 of the supplemental materials).
+We explored bivariate correlations pooled across all studies between two indicators of short-term mindsets (impulsivity and future orientation) and SSP parameters of the Flanker task (for more information on the measures, see section 1 of the supplemental materials).
 
@@
 Thus, more impulsive participants processed information less deeply and were more easily drawn to distractions, but this might partly be explained by a holistic information processing style.
-Similarly, future-orientation was positively associated with perceptual input (*r* = .09 *p* < .001)—--but not with interference (*p* = .112) —--on the Flanker Task, and was also associated with a more detail-oriented processing style (*r* = -.12, *p* = .011).
+Similarly, future-orientation was positively associated with perceptual input (*r* = .09 *p* < .001)—--but not with interference (*p* = .112) —--in the Flanker task, and was also associated with a more detail-oriented processing style (*r* = -.12, *p* = .011).
 Thus, more future-oriented participants processed information more deeply, which might partly be explained by a detail-oriented processing style.
@@
 Specifically, we hypothesized that exposure to adversity might lead to a present-oriented attention style that would facilitate rapidly detecting novel or changing information, yet which would interfere with ignoring distractors.
-Across one pilot and two main studies, we tested how adversity was associated with performance on different attention tasks.
-The Pilot compared performance on a Cued Attention Task, Change Detection Task, and a Flanker.
-Two follow-up studies focused on the Flanker, with Study 2 also including a Global-Local Task.
+Across one Pilot study and two main studies, we tested how adversity was associated with performance on different attention tasks.
+The Pilot study compared performance on a Cued Attention task, Change Detection task, and a Flanker task.
+Two follow-up studies focused in the Flanker task, with Study 2 also including a Global-Local task.
 We leveraged DDM to estimate the processes underlying lowered and improved performance.
-This allowed us to investigate whether performance differences were associated with abilities (i.e., attention orientation, interference control, stimulus processing), or ability-irrelevant processes (e.g., stimulus encoding, response execution, response caution).
-Across all primary and exploratory analyses, we leveraged multiverse analysis to systematically assess the robustness of our findings against several uncontrollable aspects of the online assessment (e.g., distractions, fullscreen exits).
+This allowed us to investigate whether performance differences were associated with abilities that are typically the main focus when using these tasks (i.e., attention orientation, interference control, information accumulation), or with other processes (e.g., stimulus encoding, response execution, response caution).
+Across all confirmatory and exploratory analyses, we leveraged multiverse analysis to systematically assess the robustness of our findings against several uncontrollable aspects of the online assessment (e.g., distractions, fullscreen exits).
 
@@
 We found little to no support for the presence of a present-oriented attention style in people exposed to adversity.
-More childhood exposure to violence was associated with slower processing of subtle changes on the Change Detection Task and lower quality of perceptual input on the Flanker Task.
-It was not associated with speed of processing of peripheral information on the Cued Attention Task.
-Zooming in on the Flanker, our two main studies found mixed evidence for the hypotheses that violence exposure and unpredictability were associated with lower strength of perceptual input.
-This mixed evidence suggests that people with more exposure to these adversities process information less deeply, making it more difficult to make judgments about target and distractor information in equal measure.
+More childhood exposure to violence was associated with slower processing of subtle changes in the Change Detection task and lower quality of perceptual input in the Flanker task.
+It was not associated with speed of processing of peripheral information in the Cued Attention task.
+Zooming in in the Flanker task, our two main studies found mixed evidence for the hypotheses that violence exposure and unpredictability were associated with lower strength of perceptual input.
+This mixed evidence suggests that people with more exposure to these adversities process information less deeply, leading to slower responses on congruent and incongruent trials in equal measure.
+
+which would affect both the processing of distractor and target information. making it more difficult to make judgments about target and distractor information in equal measure.
 This was corroborated by the pooled analyses across studies, which found that both exposure to violence and unpredictability were associated with lower strength of perceptual input, but not with differences in the ability to inhibit distractors.
@@
 
-Our findings of the DDM decomposition of Flanker performance challenge previous interpretations based on raw performance.
+Our findings of the DDM decomposition of Flanker task performance challenge previous interpretations based on raw performance.
 Previous studies have found that people exposed to adversity and/or low SES backgrounds have longer RTs on incongruent trials relative to congruent trials [@farah_2006; @fields_2021; @mezzacappa_2004; @mittal_2015; @noble_2005], which is commonly interpreted as an impaired ability to inhibit irrelevant information.
@@
 Contrary to previous studies, we found little to no evidence for performance differences on the basis of raw RTs.
-In addition, our DDM analyses showed that performance differences on the Flanker are not driven by differences in interference control, but by more basic processes that are not typically considered when interpreting Flanker performance.
+In addition, our DDM analyses showed that performance differences in the Flanker task are not driven by differences in interference control, but by more basic processes that are not typically considered when interpreting Flanker task performance.
+Although we are not aware of similar findings in the literature on adversity, comparable conclusions have recently been drawn in research on cognitive functioning related to depression and autism [@grange_2022; @merkt_2013; @poole_2024].
 
-Our findings align with a broader literature that is critical of the validity of the Flanker in particular, and that of cognitive control tasks more generally.
-As noted, several studies have failed to find coherent correlations between raw performance on different cognitive control tasks [e.g., @loffler_2022; @rey_mermet_2019; @rouder_2019; @stahl_2014].
+Our findings align with a broader literature that is critical of the validity of the Flanker task in particular, and that of cognitive control tasks more generally.
+As noted, several studies have failed to find coherent correlations between raw performance on different cognitive control tasks [e.g., @loffler_2024; @rey_mermet_2019; @rouder_2019; @stahl_2014].
 For example, previous research comparing several cognitive control tasks across different data sets using cognitive modeling found that shared variance between these tasks was mostly associated with processing speed and strategies (e.g., speed-accuracy trade-offs) [@hedge_2022].
 Moreover, the modeling parameters reflecting conflict processing (similar to interference in our study) were barely correlated.
-Similarly, previous work has shown that individual differences on common EF tasks---among which the Flanker Task---can be fully accounted for by general processing speed [@loffler_2022].
+Similarly, previous work has shown that individual differences on common EF tasks---among which the Flanker task---can be fully accounted for by general processing speed [@loffler_2024].
 This literature, together with the findings reported here, underscore that researchers should be cautious when drawing inferences about cognitive control abilities in people exposed to adversity based on raw RTs and performance on individual tasks.
 
-Finally, we showed that people exposed to adversity had a more holistic processing style, and that this style was associated with lower strength of perceptual input on the Flanker.
-This could mean that people with more adversity exposure processed the Flanker display more holistically; that is, focused less on individual arrows and more on the collection of arrows as a whole.
+Finally, we showed that people exposed to adversity had a more holistic processing style, and that this style was associated with lower strength of perceptual input in the Flanker task.
+This could mean that people with more adversity exposure processed the Flanker task display more holistically; that is, focused less on individual arrows and more on the collection of arrows as a whole.
 One (tentative) interpretation is that in the absence of threatening or otherwise salient information, people with more exposure to adversity attend to and process information in the environment globally and less deeply.
@@
 Indeed, a few studies show that cognitive abilities that may be particularly relevant in adverse contexts---such as attention shifting and working memory updating---may be enhanced in people from adversity when they experience acute stress [@mittal_2015; @young_2018].
+
+We did not control for (potentially) confounding variables in our models, even though variables like education, intelligence, and current adversity exposure generally correlate with both childhood adversity exposure and performance on the Flanker task.
+Our reason for not including them as covariates was that all these factors can be reasonably seen as mediators of the association between childhood adversity and cognitive performance. 
+However, they are unlikely (or even impossible) causes of childhood adversity. 
+Therefore, adjusting for these variables could have introduced bias to our estimation of the total effect of childhood adversity on performance (which was our estimand) [@rohrer_2018]. 
+That said, one way in which our analyses may have been confounded is by using retrospective measures of adversity.
+For example, some work suggests that current psychopathology may bias retrospective reports of childhood adversity, although the causal pathways are still mostly unclear [@francis_2023; @goltermann_2023; @patten_2015].
+Systematic investigations into potential confounders will ultimately improve our understanding of the effects of early adversity [@ning_2023].
 
@@
 Exposure to adversity might shape these two types of inhibition in different ways.
-For example, acute stress might impair performance on tasks of cognitive inhibition (of which the Flanker is an example) and enhances performance on tasks of response inhibition [for a meta-analysis, see @shields_2016; but see @dang_2017].
+For example, acute stress might impair performance on tasks of cognitive inhibition (of which the Flanker task is an example) and enhances performance on tasks of response inhibition [for a meta-analysis, see @shields_2016; but see @dang_2017].
 Future work could assess inhibition more broadly, e.g., by including tasks that are hypothesized to require cognitive or response inhibition.
@@
 
-We found that people with more childhood adversity exposure perform worse on the Flanker not because of an impairment in their ability to inhibit distracting information, but because of lower strength of perceptual input.
+We found that people with more childhood adversity exposure perform worse in the Flanker task not because of an impairment in their ability to inhibit distracting information, but because of lower strength of perceptual input.
 Our results suggest that people with more adversity exposure are not worse at inhibiting distractions; rather, they do not seem to process information in the environment deeply unless it proves to be a reliable and important source of information.
@@
 
-**Drift Diffusion Model:** A formal cognitive model that estimates cognitive processes at different stages of the decision-making process for speeded binary decision-making tasks.
+**Drift Diffusion Model:** A formal cognitive model that explicitly models the cognitive processes underlying decision-making on speeded binary decision-making tasks.
 It represents decision-making as a process in which people accumulate information until one response is sufficiently favored over the other.
@@
 
-**Perceptual input:** Parameter from the Shrinking Spotlight Model of Flanker performance. Measures how well a person can process the Flanker stimuli in general.
+**Perceptual input:** Parameter of the Shrinking Spotlight Model of Flanker task performance. Measures how well a person can process the Flanker task stimuli in general.
 
@@
 
-**Shrinking Spotlight Model:** An extension of the standard Drift Diffusion Model to account for attention processes on the Flanker.
+**Shrinking Spotlight Model:** An extension of the standard Drift Diffusion Model to account for attention processes in the Flanker task.
 

### 2024-05-28 manuscript/scripts/pilot_stage_objects.R

@@ -19,7 +19,17 @@ get_alphas <- function(data, string) {
      psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
 }
 
-
+# set up flextable for tables
+set_flextable_defaults(
+  font.family = "Times", 
+  font.size = 10,
+  font.color = "black",
+  line_spacing = 1,
+  padding.bottom = 1, 
+  padding.top = 1,
+  padding.left = 1,
+  padding.right = 1
+)
 
 # Descriptives ------------------------------------------------------------
 
@@ -35,7 +45,7 @@ txt_ivs_dist_pilot <-
   })
 
 txt_ivs_alpha_pilot <- 
-  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
+  c("violence\\d\\d", "unp\\d\\d", 
     "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
     "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
     "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
@@ -44,7 +54,7 @@ txt_ivs_alpha_pilot <-
        select(matches(x)) |> 
        psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
   }) |> 
-  setNames(c("stai_s", "violence", "unp", 
+  setNames(c("violence", "unp", 
              "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
              "quic_total", "chaos", "ses", "impuls", "fos_pa", "fos_tp", "fos_fc", "fos_fo", "depression"))
 
@@ -1014,6 +1024,72 @@ pilot_expl_lmer_variance_plot <- names(pilot_expl_lmer_variance_sum) |>
   setNames(names(pilot_expl_lmer_variance_sum))
 
 
+pilot_expl_eff_ddm_df <- pilot_expl_lmer_effects_sum |> 
+  filter(dv %in% c("cueing_rt", "cueing_hddm_v", "flanker_rt", "cueing_hddm_t")) |> 
+  filter(str_detect(parameter, "unp_comp|:")) |> 
+  group_by(dv, parameter) |> 
[…]

### 2024-05-28 manuscript/scripts/pooled_stage_objects.R

@@ -25,6 +25,19 @@ load('manuscript/study2_staged_results.RData')
 pilot_data = read_csv(here("data/1_pilot/2_cleaned_data.csv")) |> mutate(study = "pilot")
 study1_data = read_csv(here("data/2_study1/2_cleaned_data.csv")) |> mutate(study = "study1")
 study2_data = read_csv(here("data/3_study2/2_cleaned_data.csv")) |> mutate(study = "study2")
+
+# set up flextable for tables
+set_flextable_defaults(
+  font.family = "Times", 
+  font.size = 10,
+  font.color = "black",
+  line_spacing = 1,
+  padding.bottom = 1, 
+  padding.top = 1,
+  padding.left = 1,
+  padding.right = 1
+)
+
 # IV correlations ---------------------------------------------------------
 
 iv_cor_pooled_table <-  bind_rows(
@@ -72,7 +85,7 @@ select(nvs_mean, fighting_mean, vio_comp,
   ) |> # Add a new header row on top. We can use this new row to add the title
   flextable::compose(
     i = 1, j = 1,
-    as_paragraph(as_b("Table 1. "), "Pooled bivariate correlations and descriptive statistics of measures of childhood violence exposure and environmental unpredictability across the three studies."),
+    as_paragraph(as_b("Table 2. "), "Pooled bivariate correlations and descriptive statistics of measures of childhood violence exposure and environmental unpredictability across the three studies."),
     part = "header"
   ) |>
   add_footer_row(
@@ -81,7 +94,7 @@ select(nvs_mean, fighting_mean, vio_comp,
   ) |> 
   flextable::compose(
     i = 1, j = 1,
-    as_paragraph("Note: * = ", as_i("p"), " < .05, ** = ", as_i("p"), " < .01, *** = ", as_i("p"), "< .001. ",
+    as_paragraph("Note: * = ", as_i("p"), " < .05, ** = ", as_i("p"), " < .01, *** = ", as_i("p"), " < .001. ",
                  "CHAOS = Chaos, Hubbub, and Order Scale; ",
                  "Env. change = environmental change; ",
                  "Obj. unpredictability = objective unpredictability; ",
@@ -208,7 +221,7 @@ demographics_table <- list(
   ) |> # Add a new header row on top. We can use this new row to add the title
   flextable::compose(
[…]

### 2024-05-28 manuscript/scripts/study1_stage_objects.R

@@ -18,7 +18,17 @@ get_alphas <- function(data, string) {
      psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
 }
 
-
+# set up flextable for tables
+set_flextable_defaults(
+  font.family = "Times", 
+  font.size = 10,
+  font.color = "black",
+  line_spacing = 1,
+  padding.bottom = 1, 
+  padding.top = 1,
+  padding.left = 1,
+  padding.right = 1
+)
 
 
 # Descriptives ------------------------------------------------------------
@@ -1435,7 +1445,7 @@ study1_results_list <- study1_results_df |>
 
 study1_results_table <- study1_results_df |> 
   select(dv, median_effect, CI, p_sum, boot_p) |> 
-  add_row(.before = 1, dv = "Violence exposure (primary)") |> 
+  add_row(.before = 1, dv = "Violence exposure (confirmatory)") |> 
   add_row(.after = 6, dv = "Unpredictability (exploratory)") |> 
   mutate(across(everything(), ~ifelse(is.na(.), "", .))) |> 
   mutate(
@@ -1593,7 +1603,7 @@ study1_pooled_results_list <- study1_pooled_results_df |>
 
 study1_pooled_results_table <- study1_pooled_results_df |> 
   select(dv, median_effect, CI, p_sum, boot_p) |> 
-  add_row(.before = 1, dv = "Violence exposure (primary)") |> 
+  add_row(.before = 1, dv = "Violence exposure (confirmatory)") |> 
   add_row(.after = 6, dv = "Unpredictability (exploratory)") |> 
   mutate(across(everything(), ~ifelse(is.na(.), "", .))) |> 
   mutate(
@@ -1960,7 +1970,7 @@ study1_condition_results_table <- study1_condition_vio_results_df |>
   ) |> # Add a new header row on top. We can use this new row to add the title
   flextable::compose(
     i = 1, j = 1,
-    as_paragraph(as_b("Table 5. "), "Standardized interaction effects of violence exposure (primary analysis) and unpredictability (secondary analysis) on Flanker performance across standard, enhanced, and degraded conditions."),
+    as_paragraph(as_b("Table 5. "), "Standardized interaction effects of violence exposure (confirmatory analysis) and unpredictability (secondary analysis) on Flanker performance across standard, enhanced, and degraded conditions."),
     part = "header"
   ) |>
   align(i = 2:3, align = "center", part = "header") |> 

### 2024-05-28 manuscript/scripts/study2_stage_objects.R

@@ -17,7 +17,17 @@ get_alphas <- function(data, string) {
      psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
 }
 
-
+# set up flextable for tables
+set_flextable_defaults(
+  font.family = "Times", 
+  font.size = 10,
+  font.color = "black",
+  line_spacing = 1,
+  padding.bottom = 1, 
+  padding.top = 1,
+  padding.left = 1,
+  padding.right = 1
+)
 
 
 # Descriptives ------------------------------------------------------------
@@ -33,7 +43,7 @@ txt_ivs_dist_study2 <-
   })
 
 txt_ivs_alpha_study2 <- 
-  c("stai_s\\d\\d", "violence\\d\\d", "unp\\d\\d", 
+  c("violence\\d\\d", "unp\\d\\d", 
     "quic(01|02|03|04|05|06|07|08|09)", "quic(10|11|12|13|14|15|16|17|18|19|20|21)", "quic(22|23|24|25|26|27)", "quic(28|29|30|31|32|33|34)", "quic(35|36|37)",
     "quic.*\\d\\d", "chaos\\d\\d", "ses\\d\\d", "impuls\\d\\d", 
     "fos(01|06|07|12|13)", "fos(02|05|08|11|14)", "fos(03|04|09|10|15)", "fos.*\\d\\d", "depression\\d\\d") |> 
@@ -42,7 +52,7 @@ txt_ivs_alpha_study2 <-
        select(matches(x)) |> 
        psych::alpha(check.keys = TRUE))$total[[1]] |> round(2)
   }) |> 
-  setNames(c("stai_s", "violence", "unp", 
+  setNames(c("violence", "unp", 
              "quic_monitoring", "quic_par_predict", "quic_par_env", "quic_phys_env", "quic_safety",
              "quic_total", "chaos", "ses", "impuls", "fos_pa", "fos_tp", "fos_fc", "fos_fo", "depression"))
 

### 2024-05-31 manuscript/CD_submission1/abstract.qmd
cleaning up manuscript folder

--- 2024-04-02 manuscript/abstract.qmd
@@
 ---
-bibliography: references.bib
+bibliography: ../references.bib
 csl: apa.csl
@@
   docx:
-    reference-doc: reference-doc.docx
+    reference-doc: ../reference-doc.docx
 output:
@@
 Thus, lowered Flanker performance does not necessarily imply lowered inhibition ability. 
-Cognitive modeling might reveal a different picture of abilities in adverse conditions.
+Cognitive modeling reveals a different picture of abilities in adverse conditions as opposed to analyses based on raw performance.
 

### 2024-05-31 manuscript/CD_submission1/manuscript.qmd
cleaning up manuscript folder

--- 2024-03-27 manuscript/manuscript.qmd
@@
 # Source necessary objects
-power_linear      <- read_csv("../data/1_pilot/simulation/power_linear_model.csv") %>% mutate(power = round(power, 0))
-power_mixed       <- read_csv("../data/1_pilot/simulation/power_mixed_model.csv") %>% mutate(power = round(power, 0))
+power_linear      <- read_csv("../../data/1_pilot/simulation/power_linear_model.csv") %>% mutate(power = round(power, 0))
+power_mixed       <- read_csv("../../data/1_pilot/simulation/power_mixed_model.csv") %>% mutate(power = round(power, 0))
 
-load("pilot_staged_results.RData")
-load("study1_staged_results.RData")
-load("study2_staged_results.RData")
-load("pooled_staged_results.Rdata")
+load("../pilot_staged_results.RData")
+load("../study1_staged_results.RData")
+load("../study2_staged_results.RData")
+load("../pooled_staged_results.Rdata")
 ```
@@
 
-All scripts, materials, and data supporting the results presented here are available on the article's GitHub repository [ANONYMIZED FOR REVIEW].
+All scripts, materials, and data supporting the results presented here are available on the article's GitHub repository (<https://anonymous.4open.science/r/CogDev_AnonLink>).
 
@@
 
-Previous research has shown that people who grew up in adverse conditions tend to be slower on the Flanker Task, suggesting difficulty inhibiting distractions.
-However, this pattern might result from slower general cognitive processes (e.g., reduced general processing speed), rather than the specific ability of inhibition.
-We used Drift Diffusion Modeling in three studies---one pilot and two confirmatory studies---to better understand associations of adversity exposures with Flanker performance. 
-Neither exposure to violence nor unpredictability were associated with inhibition.
-In contrast, although mixed, exposure to violence and unpredictability were associated with lower strength of perceptual input; that is, how well someone can process the arrows in general.
-Finally, lower strength of perceptual input was linked to a tendency to process information more holistically, focusing less on individual details.
-Thus, researchers should be cautious when drawing inferences about inhibition abilities in people exposed to adversity based on response times alone.
+It is well-established that individuals who grew up in adverse conditions tend to be slower on the Flanker Task. 
+This finding is typically interpreted to reflect difficulty inhibiting distractions. 
+However, it might result from slower general cognitive processes (e.g., reduced general processing speed), rather than the specific ability of inhibition. 
+We used Drift Diffusion Modeling in three online studies (total N = 1560) with young adults to understand associations of adversity with Flanker performance. 
+We find no associations between exposure to violence and unpredictability with inhibition. 
+Yet, although mixed, violence and unpredictability exposure were associated with lower strength of perceptual input--—how well someone can process target and distractor information alike. 
+Finally, people with lower strength of perceptual input processed information more holistically, focusing less on details. 
+Thus, lowered Flanker performance does not necessarily imply lowered inhibition ability. 
+Cognitive modeling might reveal a different picture of abilities in adverse conditions.
 
@@
 Distinguishing between these two possibilities is challenging for two reasons.
-First, few studies in the adversity literature have measured performance differences on different attention tasks within the same individual [@mezzacappa_2004; @mittal_2015].
-Thus, it is unclear whether lowered inhibition is related to enhanced processing of peripheral information in people from from adverse backgrounds.
+First, few studies in the adversity literature have measured performance differences on different attention tasks within the same individual [@fields_2021; @mezzacappa_2004; @mittal_2015].
+Thus, it is unclear whether lowered inhibition is related to enhanced processing of peripheral information in people from adverse backgrounds.
 Second, performance on inhibition tasks is---beyond the ability to inhibit distractors---also influenced by other factors, such as a person's general processing speed and response caution [@hedge_2022; @loffler_2022].
@@
 
-knitr::include_graphics("figures/fig1.png")
+knitr::include_graphics("../figures/fig1.png")
 ```
@@
 These tasks measured inhibition, attention for peripheral cues, and attention for subtle changes.
-We expected violence exposure to be positively associated with a present-oriented attention style.
-Specifically, we expected participants with more violence exposure to be better at detecting peripheral stimuli and subtle changes.
+We expected people with more violence exposure to be better at detecting peripheral stimuli and subtle changes, as a result of a more diffuse scope of attention.
 We expected this would result in a higher drift rate (faster speed of information accumulation) or shorter non-decision times (faster attention orientation, among other things), but not necessarily with differences in boundary separation (response caution).
@@
 The Fourth row depicts effect curves of the pooled analyses across all studies.
-knitr::include_graphics("figures/fig2.png")
+knitr::include_graphics("../figures/fig2.png")
 ```
@@
 The Fourth row depicts effect curves of the pooled analyses across all studies.
-knitr::include_graphics("figures/fig3.png")
+knitr::include_graphics("../figures/fig3.png")
 ```
@@
 See the main text for more information about the multiverse analyses.
-knitr::include_graphics("figures/fig4.png")
+knitr::include_graphics("../figures/fig4.png")
 ```

### 2024-05-31 manuscript/CD_submission1/manuscript_blinded.qmd
cleaning up manuscript folder

--- 2024-05-31 manuscript/CD_submission1/manuscript.qmd
@@
 
-#### **Childhood adversity is not associated with lowered inhibition, but slower perceptual processing: A Drift Diffusion Model analysis**
-
-#### Stefan Vermeent^a,b^, Ethan S. Young^a^, Jean-Louis van Gelder^b^, & Willem E. Frankenhuis^a,b,c^
-
-#### ^a^ Department of Psychology, Utrecht University, Utrecht, The Netherlands
-
-#### ^b^ Max Planck Institute for the Study of Crime, Security, and Law, Freiburg, Germany
-
-#### ^c^ Evolutionary and Population Biology, Institute for Biodiversity and Ecosystem Dynamics, University of Amsterdam, Amsterdam, the Netherlands
-
-<br>
-
-# Corresponding author
-
-Correspondence concerning this article should be addressed to Stefan Vermeent, Department of Psychology, Utrecht University, Heidelberglaan 1, 3584 CS Utrecht, The Netherlands.
-Email: p.c.s.vermeent@gmail.com / p.c.s.vermeent@uu.nl.
-
-# Data Statement
-
-All scripts, materials, and data supporting the results presented here are available on the article's GitHub repository (<https://anonymous.4open.science/r/CogDev_AnonLink>).
-
-# Funding Statement
-WEF’s contributions have been supported by the Dutch Research Council (V1.Vidi.195.130) and the James S. McDonnell Foundation (https://doi.org/10.37717/220020502).
-
-# Author contributions
-
-**Stefan Vermeent:** Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Project administration, Data curation, Visualization, Writing - original draft, Writing - review & editing.
-**Ethan S. Young:** Conceptualization, Methodology, Supervision, Writing - review & editing.
-**Jean-Louis van Gelder:** Conceptualization, Funding acquisition, Methodology, Supervision, Writing - review & editing.
-**Willem E. Frankenhuis:** Conceptualization, Funding acquisition, Methodology, Supervision, Writing - review & editing.
-
-\pagebreak
-
-# Abstract
-
-It is well-established that individuals who grew up in adverse conditions tend to be slower on the Flanker Task. 
-This finding is typically interpreted to reflect difficulty inhibiting distractions. 
-However, it might result from slower general cognitive processes (e.g., reduced general processing speed), rather than the specific ability of inhibition. 
-We used Drift Diffusion Modeling in three online studies (total N = 1560) with young adults to understand associations of adversity with Flanker performance. 
-We find no associations between exposure to violence and unpredictability with inhibition. 
-Yet, although mixed, violence and unpredictability exposure were associated with lower strength of perceptual input--—how well someone can process target and distractor information alike. 
-Finally, people with lower strength of perceptual input processed information more holistically, focusing less on details. 
-Thus, lowered Flanker performance does not necessarily imply lowered inhibition ability. 
-Cognitive modeling might reveal a different picture of abilities in adverse conditions.
-
-*Key-words:* childhood adversity, inhibition, Flanker, Drift Diffusion Modeling
-
-\pagebreak
-
 # Childhood adversity is not associated with lowered inhibition, but lower perceptual processing: A Drift Diffusion Model analysis
@@
 Distinguishing between these two possibilities is challenging for two reasons.
-First, few studies in the adversity literature have measured performance differences on different attention tasks within the same individual [@fields_2021; @mezzacappa_2004; @mittal_2015].
-Thus, it is unclear whether lowered inhibition is related to enhanced processing of peripheral information in people from adverse backgrounds.
+First, few studies in the adversity literature have measured performance differences on different attention tasks within the same individual [@mezzacappa_2004; @mittal_2015].
+Thus, it is unclear whether lowered inhibition is related to enhanced processing of peripheral information in people from from adverse backgrounds.
 Second, performance on inhibition tasks is---beyond the ability to inhibit distractors---also influenced by other factors, such as a person's general processing speed and response caution [@hedge_2022; @loffler_2022].
@@
 These tasks measured inhibition, attention for peripheral cues, and attention for subtle changes.
-We expected people with more violence exposure to be better at detecting peripheral stimuli and subtle changes, as a result of a more diffuse scope of attention.
+We expected violence exposure to be positively associated with a present-oriented attention style.
+Specifically, we expected participants with more violence exposure to be better at detecting peripheral stimuli and subtle changes.
 We expected this would result in a higher drift rate (faster speed of information accumulation) or shorter non-decision times (faster attention orientation, among other things), but not necessarily with differences in boundary separation (response caution).

### 2024-05-31 manuscript/CD_submission1/titlepage.qmd
cleaning up manuscript folder

--- 2024-05-31 manuscript/CD_submission1/manuscript.qmd
@@
 
-```{r setup, include=FALSE}
-# Load libraries
-library(dplyr)
-library(tidyr)
-library(purrr)
-library(furrr)
-library(readr)
-library(magrittr)
-library(officer)
-library(flextable)
-library(here)
-library(pwr)
-
-# set up chunk options
-knitr::opts_chunk$set(
-  echo = F,
-  fig.align = "center",
-  fig.pos = "!t", 
-  out.extra = "",
-  fig.show = "asis",
-  message = FALSE,
-  warning = FALSE
-)
-
-# set up flextable for tables
-set_flextable_defaults(
-  font.family = "Times", 
-  font.size = 10,
-  font.color = "black",
-  line_spacing = 1,
-  padding.bottom = 1, 
-  padding.top = 1,
-  padding.left = 1,
-  padding.right = 1
-)
-
-# Source necessary objects
-power_linear      <- read_csv("../../data/1_pilot/simulation/power_linear_model.csv") %>% mutate(power = round(power, 0))
-power_mixed       <- read_csv("../../data/1_pilot/simulation/power_mixed_model.csv") %>% mutate(power = round(power, 0))
-
-load("../pilot_staged_results.RData")
-load("../study1_staged_results.RData")
-load("../study2_staged_results.RData")
-load("../pooled_staged_results.Rdata")
-```
-
 #### **Childhood adversity is not associated with lowered inhibition, but slower perceptual processing: A Drift Diffusion Model analysis**
@@
 
-All scripts, materials, and data supporting the results presented here are available on the article's GitHub repository (<https://anonymous.4open.science/r/CogDev_AnonLink>).
+All scripts, materials, and data supporting the results presented here are available on the article's GitHub repository [ANONYMIZED FOR REVIEW].
 
@@
 **Willem E. Frankenhuis:** Conceptualization, Funding acquisition, Methodology, Supervision, Writing - review & editing.
-
-\pagebreak
-
-# Abstract
-
-It is well-established that individuals who grew up in adverse conditions tend to be slower on the Flanker Task. 
-This finding is typically interpreted to reflect difficulty inhibiting distractions. 
-However, it might result from slower general cognitive processes (e.g., reduced general processing speed), rather than the specific ability of inhibition. 
-We used Drift Diffusion Modeling in three online studies (total N = 1560) with young adults to understand associations of adversity with Flanker performance. 
-We find no associations between exposure to violence and unpredictability with inhibition. 
-Yet, although mixed, violence and unpredictability exposure were associated with lower strength of perceptual input--—how well someone can process target and distractor information alike. 
-Finally, people with lower strength of perceptual input processed information more holistically, focusing less on details. 
-Thus, lowered Flanker performance does not necessarily imply lowered inhibition ability. 
-Cognitive modeling might reveal a different picture of abilities in adverse conditions.
-
-*Key-words:* childhood adversity, inhibition, Flanker, Drift Diffusion Modeling
-
-\pagebreak
-
-# Childhood adversity is not associated with lowered inhibition, but lower perceptual processing: A Drift Diffusion Model analysis
-
-The predominant view in developmental psychology is that exposure to adversity impairs cognitive abilities.
-This view is supported by decades of research showing that people living in high-adversity contexts tend to score lower on a variety of cognitive tests [@hackman_2010; @ursache_2016].
-Recent adaptation-based perspectives, however, have argued that people from adversity may also develop intact, or enhanced, abilities for solving problems in high-adversity contexts [@ellis_2017; @frankenhuis_2013].
-Adaptation- and deficit-based perspectives are considered complimentary.
-For instance, adversity may impair some cognitive processes, yet enhance others.
-Despite their compatibility, few studies have investigated how the interplay of impaired and enhanced abilities shapes performance.
-In this paper, across three preregistered online experiments, we used cognitive modeling to derive a process-level understanding of the association between childhood adversity and performance on the Flanker Task, a popular measure of cognitive control [@ridderinkhof_2021].
-
-## Attention in adverse conditions
-
-It is well-established that early-life adversity is associated with deficits in the ability to inhibit distracting, goal-irrelevant information [@hackman_2010; @ursache_2016].
-One of the leading paradigms in this literature is the Flanker Task [@eriksen_1974].
-On this task, participants typically see five arrows in a horizontal orientation, and are asked to indicate the direction of the central arrow.
-The flanking arrows point in the opposite direction on half of the trials, leading to interference that participants must inhibit.
-Slower performance on the Flanker has been documented for children and adults with lower childhood socioeconomic status [SES\; @farah_2006; @mezzacappa_2004; @noble_2005] and more environmental unpredictability [@fields_2021; @mittal_2015].
-These findings are typically interpreted as indicating a deficit in the ability to inhibit distractions.
-
-Nonetheless, some recent studies suggest that growing up in adversity may also be associated with improved abilities such as attention shifting [@fields_2021; @mittal_2015; @young_2022; but see @nweze_2021].
-Some studies found deficit patterns on the Flanker alongside enhancements on other aspects of attention within the same participants.
-For example, in one study, children with lower SES performed less well on the Flanker, but outperformed children from higher SES on orienting their attention to salient cues and, peripheral cues [@mezzacappa_2004].
-Similarly, children with more caregiver switches (an indicator of unpredictability) were found to perform less well on the Flanker, but outperformed children with fewer caregiver switches on shifting their attention between different task goals [@fields_2021].
-
-Performance on attention tasks could reflect developmental adaptation to adverse environments [@blair_2012; @dangiulli_2012; @frankenhuis_2020; @mittal_2015].
-In unpredictable or threatening conditions, the ability to detect salient peripheral information (e.g., distant noises or approaching individuals) could help to more quickly detect and act on potential threats.
-Over time, cognitive adaptations to such conditions could result in a general tendency to use a more diffuse scope of attention, leading to an enhanced ability to keep track of the broader environment.
-In line with this hypothesis, people with lower SES respond more strongly to auditory distractors [@giuliano_2018; @stevens_2009; @hao_2022] and are faster to orient their attention to peripheral visual information [@mezzacappa_2004].
-While potentially adaptive, a more diffuse scope of attention could come at the cost of lowered ability to ignore irrelevant distractors.
-This could compromise more long-term goal-directed behavior, especially in chaotic environments (e.g., a noisy classroom or a busy street).
-
-Thus, lowered performance on tasks like the Flanker could reflect either a cognitive impairment or a difference in attentional strategies.
-Distinguishing between these two possibilities is challenging for two reasons.
-First, few studies in the adversity literature have measured performance differences on different attention tasks within the same individual [@fields_2021; @mezzacappa_2004; @mittal_2015].
-Thus, it is unclear whether lowered inhibition is related to enhanced processing of peripheral information in people from adverse backgrounds.
-Second, performance on inhibition tasks is---beyond the ability to inhibit distractors---also influenced by other factors, such as a person's general processing speed and response caution [@hedge_2022; @loffler_2022].
-This means that lowered performance on inhibition tasks does not necessarily reflect inhibition difficulties.
-In other words, we should consider cognitive processes other than ability when drawing inferences based on inhibition tasks.
-
-## Using Drift Diffusion Modeling to estimate attention and processing styles
-
-An important issue, therefore, is that several processes are involved in performance on the Flanker, and standard assessments using raw performance measures (response times, accuracy rates) mostly fail to distinguish between them.
-For example, performance differences on the Flanker could indicate that someone experiences more (or less) flanker interference, generally processes less (or more) efficiently, or responds with less (or more) caution.
-To understand how adversity affects performance, we need to be able to separate the difference processes that make up performance.
-
-Formal cognitive models such as the Drift Diffusion Model [DDM\; @forstmann_2016; @ratcliff_1998; @ratcliff_2008; @ratcliff_2015; @wagenmakers_2009] provide a potential solution.
-The DDM estimates cognitive processes at different stages of the decision-making process (See Figure 1a).
-It represents decision-making on binary decision-making tasks as a process in which people accumulate information until one response is sufficiently favored over the other.
-These two response options are represented as opposing boundaries.
-One boundary corresponds to the correct response and the other to the incorrect response.
-When information accumulation reaches one of the two boundaries, the corresponding response is executed.
-
-The DDM translates trial-level response times (RTs) and accuracy into three distinct cognitive processes.
-The speed of information accumulation is captured in a parameter called the *drift rate*.
-Higher drift rates are associated with faster responses and higher mean accuracy.
-Response caution is modeled through the *boundary separation*; that is, the width between the two boundaries.
-Larger boundary separation is associated with larger RTs and higher accuracy (i.e., sacrificing speed to increase accuracy).
-Finally, *non-decision time* represents the time it takes to prepare for the task at the start of the trial (before information processing) and the time it takes to execute a response (after a response boundary has been reached).
-Longer non-decision times are associated with larger RTs, without influencing accuracy.
-
-The Shrinking Spotlight (SSP) model is an extension of the standard DDM to account for attention processes on the Flanker [@grange_2016; @white_2018a; @white_2018b; @white_2011].
-The SSP model assumes that attention resembles a spotlight that is normally distributed over the Flanker arrows (with a particular starting *attentional width*).
-Over time, people narrow their attention down to the central arrow (at a rate defined by the *shrinking rate*), thereby gradually decreasing interference from irrelevant information (See Figure 1b).
-Prior work has defined the amount of distractor *interference* by dividing the attentional width by the shrinking rate [@white_2018a].
-People may experience less interference either by starting with a narrower attentional width, and/or by more rapidly shrinking their attention down to the target arrow.
-Finally, performance is also influenced by the *perceptual input* strength; that is, how well someone can process the arrows in general.
-Note that typical interpretations of lowered raw Flanker performance are in terms of the amount of interference that someone experiences, and not in terms of the strength of perceptual input.
-Here, we are interested in how childhood adversity is associated with both interference and the strength of perceptual input.
-
-<br>
-
-```{r}
-#| label: figure1
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 1.** A visual overview of the Drift Diffusion Model (DDM) and the Shrinking Spotlight Model (SSP).
-Panel A: The DDM assumes that people go through three distinct stages when they perform cognitive tasks with two forced response options.
-In a first preparation phase, they visually encode the relevant stimuli.
-In a second decision phase, people accumulate information in favor of one decision over the other (e.g., pressing left vs.
-right) until the decision boundary for either the correct or incorrect response is reached.
-Each jagged line represents this information accumulation process on a single trial.
-In a third execution phase, people execute the motor response.
-The model estimates four parameters that reflect distinct cognitive processes (printed in italic): (1) The drift rate represents the average rate of evidence accumulation towards the correct decision boundary and measures processing speed; (2) The non-decision time represents both the time spent encoding the stimuli and executing the response; (3) The boundary separation represents how far apart has “set” their decision boundaries, and is a measure of the person’s level of response caution; (4) The starting point represents the starting point of the decision process and measures the level of response bias (not considered here).
-Panel B: The SSP is an extension of the standard DDM including additional parameters to capture attentional processes involved in Flanker performance.
-Each stimulus arrow provides a certain strength of perceptual input (*p*).
-On incongruent trials, the perceptual input of flanking arrows is coded negatively (-*p*).
-Attention is assumed to be normally distributed over the arrows with a certain attentional width.
-Over time, attention is narrowed down toward the central arrow at a rate determined by the shrinking rate, thereby gradually lowering the interference caused by the flanking arrows.
-The drift rate in the SSP model is the sum of the perceptual input of each arrow multiplied by the attention allotted to each arrow.
-As attention for the flanking arrows decreases over time, the drift rate is assumed to increase over time (contrary to the standard DDM, which assumes a linear drift rate).
-
-knitr::include_graphics("../figures/fig1.png")
-```
-
-# Overview of studies
-
-The overarching goal of our studies is to understand the attentional and processing styles that people develop in conditions of adversity.
-We focus on measures of exposure to violence and environmental unpredictability.
-Previous research shows that these two types of adversity are on the one hand associated with improved attention shifting and working memory updating [@fields_2021; @mittal_2015; @young_2018; @young_2022], and on the other hand with lowered inhibition and working memory capacity [@fields_2021; @mittal_2015; @young_2018].
-We conducted three online studies: one pilot and two follow-up studies.
-Using cognitive modeling, we unpack Flanker performance in comparison to other tasks that require externally focused attention (Pilot), across visual processing manipulations (Study 1), and in terms of tendencies for holistic versus local processing (Study 2).
-
-We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see <https://anonymous.4open.science/r/CogDev_AnonLink>).
-For each study, we preregistered primary (i.e., hypothesis-driven) and exploratory analyses.
-The main text addresses the primary analyses involving violence exposure and the exploratory analyses involving environmental unpredictability.
-We describe the other exploratory analyses in the supplemental materials (section 2).
-For an overview of all deviations from the preregistrations, see section 4 of the supplemental materials.
-
-# Pilot
-
-In the Pilot, our goal was to understand how childhood adversity relates to performance on tasks with different attentional demands.
-Participants completed self-report measures of childhood adversity and three cognitive tasks.
-These tasks measured inhibition, attention for peripheral cues, and attention for subtle changes.
-We expected people with more violence exposure to be better at detecting peripheral stimuli and subtle changes, as a result of a more diffuse scope of attention.
-We expected this would result in a higher drift rate (faster speed of information accumulation) or shorter non-decision times (faster attention orientation, among other things), but not necessarily with differences in boundary separation (response caution).
-Second, we expected that participants with more violence exposure would be worse at ignoring distracting peripheral stimuli.
-We expected this would result in more experienced interference (as derived from the SSP model).
-
-## Methods
-
-### Participants {#participants}
-
-Participants were 565 people from the United States aged between 18 and 30 recruited on Prolific Academic ([https://www.prolific.co](https://www.prolific.co)) (See Table 1 for demographic data).
-The sample was balanced on sex.
-We used the MacArthur's ladder, included in Prolific's prescreening battery, for assessing perceived SES to ensure about half of the sample came from lower-SES backgrounds (which we defined as a score of 4 or below).
-Participants were eligible if they spoke fluent English and did not report color-blindness.
-
-\pagebreak
-
-```{r}
-#| tab.id: table1
-#| results: markup
-demographics_table
-```
-
-<br>
-
-We conducted a power simulation using the *faux* package in R [@debruine_2021] to determine the minimally required number of participants for standardized regression coefficients of 0.10 and 0.15 (for details and simulation code, see <https://anonymous.4open.science/r/CogDev_AnonLink/preregistrations/1_pilot/scripts>).
-Power was \> .80 for adversity x task condition interactions with *N* = 450 or more.
-For a linear main effect, detecting an effect of $\beta$ = 0.15 with .90 power would require *N* = `r pwr.r.test(r = 0.15, sig.level = 0.05, power = .90, alternative = "two.sided")[['n']] %>% round(0)`.
-We sampled 550 participants, anticipating a final sample of \~500 after exclusions.
-
-Prior to analyzing the data, we applied our preregistered exclusion criteria.
-First, we excluded participants who did not complete the full study; second, those who had incomplete data on any of the attention tasks; third, those who missed both attention check items; fourth, those who had suspicious response patterns (e.g., consistently endorsing high response options even though some items were reverse coded).
-Fifth, on a trial-level, we excluded any trials with reaction times \< 250 ms or \> 3500 ms [@ratcliff_2015].
-Participants with more than 10 trials removed were completely excluded from the analyses.\
-The final sample consisted of `r nrow(pilot_data)` participants.
-
-### Procedure {#procedure}
-
-Participants completed the experiment on their own laptop or desktop computer.
-Participants could refrain from answering any of the questionnaire items and were prompted with a warning once per page in case of missing items.
-
-After providing consent, participants completed three attention tasks.
-They were asked to move to a quiet room in the house, where they would be unlikely to be distracted by other people or outside noises.
-The order of the tasks was counterbalanced between subjects.
-At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs.
-The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deleeuw_2015].
-Participants were asked to hold a credit card (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the credit card.
-The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants.
-After successfully resizing the screen, participants completed all three tasks.
-During the task, the cursor was hidden from the screen to minimize distractions.
-After completing the attention tasks, participants completed the questionnaire battery and demographic questions.
-Finally, we asked participants whether they ever got up or were interrupted during the study, and how noisy their environment was during the attention tasks.
-The full experiment took \~35 minutes.
-Participants were paid £4.38 when they reached the end of the experiment.
-
-### Cognitive measures {#cogmeasures}
-
-The attention tasks were programmed in JsPsych version 3.6.1 [@deleeuw_2015].
-For all materials and links to working versions of the tasks, see the Github repository.
-
-**Flanker Task.** The Flanker measures selective attention and response inhibition [@eriksen_1974].
-The Flanker began with eight practice trials, followed by 64 test trials.
-On each trial, participants saw a set of five arrows pointing either left or right.
-Participants were instructed to indicate the direction of the central arrow while ignoring the flanking arrows to the left and right.
-All trials included black arrows against a white background.
-On the *congruent* trials (50%), the flanking arrows pointed in the same direction as the central arrow.
-On the *incongruent* trials (50%), the arrows pointed in the opposite direction.
-The arrows were randomly presented in the top-half or bottom-half of the screen.
-Each trial started with a fixation cross (1000 ms), after which the arrows were visible until a response was given.
-Participants received performance feedback during the practice trials, but not during the test block.
-
-**Cued Attention Task.** The Cued Attention Task was an adapted version of the Posner task, which measures the speed of attention for peripheral cues [@posner_1980].
-The Cued Attention Task began with eight practice trials, followed by 64 test trials.
-On each trial, a left- or right-pointing arrow was presented in one of eight random locations at 300 pixels from the center of the screen.
-Participants were instructed to indicate the direction of the arrow by pressing either the left- or right arrow key on their keyboard.
-All trials included a black cue and arrow against a white background.
-On *cued* trials (50%), a cue ('\*') preceded the arrow in the exact same location.
-On *neutral* trials (50%), the cue preceded the arrow, but appeared at the center of the screen (not where the arrow would appear).
-Thus, the cue was perfectly predictive of the target location on cued trials, but provided no predictive information about the location of the arrow on neutral trials.
-Each trial started with a fixation cross at the center of the screen for 1000 ms. Then, the cue appeared for 250 ms, followed by the target arrow, until a response was given.
-
-**Change Detection Task.** The Change Detection Task measures the ability to detect subtle spatial changes.
-The Change Detection Task started with five practice trials followed by 50 test trials.
-On each trial, participants saw five colored circles (red, light-blue, dark-blue, yellow, and purple) against a gray background, each with a radius of 15 pixels.
-Each circle was located in a semi-random location around the central fixation cross.
-The location of each circle was sampled within a pre-specified area of 50-by-50 pixels to prevent overlap.
-Participants had 1000 ms to memorize the locations of the five circles.
-Then, the circles disappeared for 500 ms and then reappeared.
-On *change* trials (50%), one of the circles had moved to another location with a fixed displacement of 40 pixels in a 360 degree direction.
-On *no change* trials (50%), all circles were still in the same location.
-Participants were instructed to indicate whether all circles were still in the same location or one of the circles had changed location.
-The displacement of *one* circle was the only potential difference on each trial;
-
-**DDM/SSP parameters.** We analyzed the Flanker with the SSP model [@grange_2016; @white_2018a; @white_2018b; @white_2011], using the *flankr* package [@grange_2016].
-For each participant, the SSP provided us with estimates of: (1) strength of perceptual input (general quality of information that participants get from the arrows), (2) interference (initial attention width divided by the speed at which attention is narrowed down to the central arrow), (3) non-decision time (combination of speed of initial stimulus encoding and response execution), and (4) boundary separation (response caution).
-Our focus on interference as a ratio between attention width and shrinking rate was a deviation from the preregistration, as we initially planned to investigate both aspects of attention separately.
-However, we discovered that both parameters in isolation were unreliable because of an inherent trade-off, while the ratio did provide a stable measure.
-This was supported in a simulation study by @white_2018a showing that the ratio measure is reliable.
-See the supplemental materials (section 3) for a comparison between the preregistered and the updated analyses.
-
-For the Change Detection Task and the Cued Attention Task, we used a hierarchical Bayesian implementation of the standard DDM (HDDM).
-For each participant, the HDDM provided us with estimates of: (1) drift rate (speed of information accumulation; analogous to strength of perceptual input in the SSP model, except that drift rate is time-invariant), (2) non-decision time (same as SSP model), and (3) boundary separation (same as SSP model).
-The hierarchical Bayesian fitting procedure was a deviation from the preregistration, in which we planned to use Maximum Likelihood (ML) estimation.
-There were several issues with estimating DDM parameters for the Cued Attention task, which we later discovered were caused specifically by ML.
-An important difference between HDDM and ML is that HDDM uses the group information to inform individual parameter estimates, whereas ML models are fitted to each individual separately.
-This generally improves the accuracy of the estimation.
-See the supplemental materials (section 3) for an overview of the fit procedure and model fit across all models.
-
-### Self-report measures
-
-See Table 2 for bivariate correlations between measures of adversity across all studies.
-
-**Violence exposure.** We measured violence exposure using the Neighborhood Violence Scale (NVS) and two items assessing involvement in violence before age 13 [@frankenhuis_2018; @frankenhuis_deVries_2020; @young_2022].
-The NVS contains seven items measuring perceived exposure to violence before age 13 (e.g., "Crime was common in the neighborhood where I grew up").
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-The physical fighting items assessed the number of times participants witnessed fights before age 13: "Based on your experiences, how many times did you see or hear someone being beaten up in real life, before age 13?" and "How many times were you in a physical fight, before age 13?" Answers to both items ranged from 1 (0 times) to 8 (12 or more times).
-The items of the NVS were averaged together (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$violence`).
-Similarly, we averaged the scores on the two fighting items together.
-For the main analyses, we created a perceived violence exposure composite by standardizing the NVS and fighting composites and calculating an unweighted average.
-
-**Environmental unpredictability.** We included five measures of environmental unpredictability across different temporal scales: (1) the Questionnaire of Unpredictability in Childhood [QUIC\; @glynn_2019]; (2) the Perceived Childhood Unpredictability scale [@young_2018]; (3) the Confusion, Hubbub, and Order Scale [CHAOS\; @matheny_1995]; (4) stability of the family and social environment; and (5) objective indicators of unpredictability.
-All scales were adapted to refer to experiences before age 13.
-We computed a composite measure of all z-transformed unpredictability measures.
-See section 2 of the supplemental materials for an exploration of the factor structure of these measures.
-
-The QUIC captures environmental and household unpredictability.
-We made three preregistered changes to the original scale [@glynn_2019], to better align it with the other scales.
-First, all items were rated on a scale of 1 (never true) to 5 (very often true), except for four items referring to specific experiences (e.g., "I experienced changes in my custody arrangement").
-For these items, we adopted a response scale with the options "never", "only once", "a couple times", "several times", "many times".
-Second, quantifiers such as "frequently", "often", and "There was a period of time when [...]" were dropped to better match the response scale.
-Third, we excluded the item "My parents got divorced" because it did not fit the new response labels and this information was already captured by one of the items of the perceived unpredictability scale.
-Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$quic_total`).
-
-The perceived childhood unpredictability scale included eight items measuring perceived unpredictability before age 13 (e.g., "My family life was generally inconsistent and unpredictable from day-to-day").
-Participants rated each on a scale from 1 (never true) to 5 (very often true).
-Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$unp`).
-
-The CHAOS consists of 15 items measuring the level of chaos in the household (e.g., "No matter how hard we tried, we always seemed to be running late").
-All items were rated on a scale of 1 (never true) to 5 (very often true) instead of the original yes/no answer format.
-Reliability of the scale was high (Cronbach's $\alpha$ = `r txt_ivs_alpha_pilot$chaos`).
-
-We included one additional scale to measure the stability of the family and social environment.
-On a scale of 1 (the same all the time) to 5 (constant and rapid changes), participants indicated how often the following aspects of their family and social environment changed before age 13: (1) economic status; (2) family environment; (3) childhood neighborhood environment; and (4) childhood school environment.
-
-Finally, we included four objective measures of unpredictability before age 13: 1) "How often did you move?"; 2) "How many adults lived in your home on average?"; 3) "How many romantic partners did your mother have (not counting your father)?"; 4) "How many romantic partners did your father have (not counting your mother)?".
-
-```{r}
-#| tab.id: table2
-#| results: markup
-iv_cor_pooled_table
-```
-
-<br>
-
-### Data analyses {#analysis_plan}
-
-**Multiverse analysis.** In an amendment to the preregistration, we quantified the robustness of our findings against six data cleaning decisions that may affect the robustness of online studies by using multiverse analysis, using the *multitool* package [@young_2023].
-Multiverse analysis allows for systematically evaluating the robustness of analyses across all combinations of different arbitrary data processing decisions [for details, see @giudice_2021; @simonsohn_2020; @steegen_2016].
-Specifically, we looked at the influence of including or excluding 1) participants who scored below 0.5 on a build-in bot-detection measure on Prolific (potentially indicating a bot); 2) participants who did not rescale their screen at the start of the experiment; 3) participants who did not enter fullscreen mode prior to starting the tasks; 4) participants who exited fullscreen mode at any point during the tasks; 5) participants who indicated high levels of noise in their environment; 6) participants who indicated extreme interruptions during the experiment.
-See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
-
-### Primary analyses
-
-For the Cued Attention Task and Flanker RTs, we used linear mixed effects models to test violence exposure x task condition (sum-coded) interactions on mean RTs and each DDM parameter.
-All mixed effects models included a random intercept for participants.
-For the Change Detection Task and Flanker SSP parameters, we used linear regression models to test the main effect of adversity on mean RTs and each DDM/SSP parameter.
-To meet model assumptions of normally distributed residuals, reaction times were log-transformed.
-Analyses involving interference (Flanker) and boundary separation (all tasks) parameters violated the assumption of normally distributed residuals.
-For boundary separation, we solved this using log-transformation.
-For interference, non-normality was caused by extreme outliers (\>3.2SD), which we excluded from the analyses.
-
-## Results and discussion
-
-Table 3 summarizes the results.
-More violence exposure was associated with lower strength of perceptual input under `r pilot_main_eff_ddm_list$Flanker_p$p_sum_Main`% of multiverse specifications (although the median 95% CI interval contained zero).
-We additionally found a significant main effect of violence exposure on interference under `r pilot_main_eff_ddm_list$Flanker_interference$p_sum_Main`% of multiverse specifications, such that more violence exposure was associated with less interference.
-This was contrary to our expectation that people exposed to adversity would have more difficulties dealing with interference from irrelevant distractors.
-
-Participants with more exposure to childhood violence were slower on the Cued Attention Task, which was mainly related to a higher level of response caution (boundary separation).
-On the Change Detection Task, more childhood violence exposure was associated with slower speed of information processing (drift rate) under `r pilot_main_eff_ddm_list$Change_v$p_sum_Main`% of multiverse specifications, but not with longer RTs.
-These results were not in line with our expectation that people from adversity would perform better on cognitive tasks that require a broad, present-focused attention style.
-
-<br>
-
-```{r}
-#| tab.id: table3
-#| results: markup
-pilot_main_eff_ddm_table |> 
-  border(i = 1, border.bottom = fp_border_default(), part = "header") 
-```
-
-<br>
-
-The pattern of findings on the Flanker was interesting for two reasons.
-First, the Flanker is a widely used task to assess the ability to inhibit irrelevant information, and people exposed to adversity typically show lowered performance.
-Our pilot results, though, suggest that lowered performance may not be caused by a reduced ability to inhibit distracting information.
-Instead, people exposed to adversity might have a lower strength of perceptual input, leading to slower and less efficient information processing.
-If true, these initial findings suggest that performance might be improved through interventions that increase the visual quality of stimuli.
-In Study 1, we aimed to replicate and extend these findings.
-
-# Study 1
-
-The goal of Study 1 was to follow up on the Pilot by manipulating the visual quality of information on the Flanker.
-Participants completed three versions: a standard version (similar to the Pilot), one with enhanced visual information, and one with degraded visual information.
-We again focused on childhood exposure to violence.
-Our first aim was to examine the robustness of our finding of improved interference control on the Flanker in relation to more adversity exposure in the pilot.
-We did so by analyzing the data of the standard condition, as well as by pooling the data of the Pilot and Study 1.
-Our second aim was to investigate whether manipulating visual information on the Flanker would influence performance for people with more violence exposure.
-
-We preregistered two potential data patterns and associated interpretations, without favoring one over the other *a priori*.
-First, the strength of perceptual input might be lower for people with more exposure to violence compared to people with less exposure to violence across all conditions.
-Second, lower performance on the standard version might reflect an adaptive trade-off towards cognitive functioning that is less affected by noise or perturbations, at a cost of lower overall performance [@giudice_2018].
-In that case, we would expect the strength of perceptual input to be influenced to a lesser extent across conditions for people with more exposure to violence than for people with less exposure to violence.
-As a result, they might not benefit as much from enhanced visual information, yet might be able to better maintain performance with degraded information.
-
-## Methods
-
-### Participants
-
-Participant recruitment was identical to the Pilot.
-In total, 567 people from the United States between the ages of 18 and 30 participated (See Table 1).
-We applied the same exclusion criteria as reported in the Pilot.
-The final sample consisted of `r nrow(study1_data)` participants.
-
-### Flanker Task
-
-We programmed the Flanker in JsPsych version 6.3.1 [@deleeuw_2015] with three conditions.
-Each condition consisted of eight practice trials, followed by 64 test trials.
-In the *standard* condition, the arrows were 40 pixels in size (0.4 inches) and had zero padding between them.
-In the *enhanced* condition, we increased the arrow size by 12.5% to 45 pixels (0.45 inches), and increased the space between the arrows to 5 pixels.
-This increased the width of the stimulus display by 50% with respect to the standard display.
-In the 'degraded' condition, sizes and space between arrows were the same as in the standard version, but all arrows were rotated 45$^\circ$ (in the same direction; that is, if the left flanker arrows pointed upwards, the right flanker arrows pointed downward).
-Participants completed each condition separately in different blocks, in randomized order.
-
-### Self-report measures
-
-The self-report measures were identical to those used in the Pilot.
-
-### Procedure
-
-The procedure was identical to the pilot study.
-The full experiment took approximately 30 minutes.
-Participants were paid £3.75 after they completed the full study.
-
-### Data analyses
-
-**Multiverse analysis.** We included the same arbitrary decisions in the multiverse analyses as in the Pilot.
-For the pooled analyses---i.e., joint analysis of the Pilot and the standard condition of Study 1---there was one minor change in how we included screen rescaling as a preprocessing decision in the multiverse.
-In Study 1, we changed the screen rescaling procedure by converting the initial size of the resize box to 300 pixels instead of 100 pixels.
-This way, the stimulus display would still be close to the intended size if participants did not engage in any resizing.
-However, this led to one important change for the pooled analysis: rescaling (yes or no) was included as an arbitrary exclusion decision in the multiverse analyses with four combinations: (1) exclude non-scalers in both studies; (2) include non-scalers in both studies; (3) exclude non-scalers in the Pilot, include non-scalers in Study 1; (4) include non-scalers in the Pilot, exclude non-scalers in Study 1.
-
-For each analysis, we report the median $\beta$s, 95% confidence intervals, and the proportion of *p*-values \< .05 across all analytic decisions.
-For the primary analyses, we used bootstrapping to compute the probability of obtaining an effect size at least as extreme as observed in the real data, conditioned on a true effect size of zero [for details, see @simonsohn_2020].
-See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
-
-**Primary analyses.** To address the first aim, we analyzed the data from the standard condition, as well as pooled the Flanker data of the Pilot and the current study.
-We ran separate linear models for each SSP parameter as well as RT difference scores with violence exposure as main predictor and study as covariate (effect-coded).
-To address the second aim, we analyzed the effect of violence exposure and Flanker condition type on performance using linear mixed effects models with a random intercept per participant.
-The five main dependent variables were mean RT difference and the SSP parameters: Perceptual input, boundary separation, non-decision time, and interference.
-For each outcome measure, we ran two separate models: one comparing the standard condition with the enhanced condition, and one comparing the standard condition with the degraded condition.
-In both models, condition was dummy-coded using the standard condition as the reference group.
-
-## Results and discussion
-
-### Standard Flanker performance
-
-Table 4 summarizes the multiverse results for the effects of violence exposure (primary analysis) and unpredictability (exploratory analysis).
-Unlike in the Pilot, we did not find any significant associations with violence exposure.
-In the exploratory analysis, there was a significant negative association between unpredictability and perceptual input (median $\beta$ = `r study1_expl_results_list$p_flanker$median_effect_Main`, 95% CI = `r study1_expl_results_list$p_flanker$CI`, `r study1_expl_results_list$p_flanker$p_sum` % of *p*s \<.05).
-
-```{r}
-#| tab.id: table4
-#| results: markup
-study1_results_table |> 
-  border(i = 1, border.bottom = fp_border_default(), part = "header") 
-```
-
-After pooling the data of the pilot study and Study 1, there was a negative association between violence exposure and interference (median $\beta$ = `r study1_pooled_results_list$interference_vio$median_effect`, 95% CI = `r study1_pooled_results_list$interference_vio$CI`, `r study1_pooled_results_list$interference_vio$p_sum` % of *p*s \<.05, bootstrapped *p* = `r study1_pooled_results_list$interference_vio$boot_p`).
-Violence exposure was associated with lower strength of perceptual input under `r study1_pooled_results_list$interference_vio$p_sum`% of multiverse specifications, but the bootstrapped *p*-value was not significant (median $\beta$ = `r study1_pooled_results_list$p_vio$median_effect`, 95% CI = `r study1_pooled_results_list$p_vio$CI`, bootstrapped *p* = `r study1_pooled_results_list$p_vio$boot_p`).
-We did not find other significant associations for either violence exposure or unpredictability.
-
-### Flanker conditions
-
-The main effects of task condition on the strength of perceptual input were in the expected direction: relative to the standard condition, the quality of perceptual input was higher in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$p_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$p_enhanced$condition_CI`, `r study1_condition_vio_results_list$p_enhanced$p_sum_Condition` % of *p*s \<.05) and lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$p_degraded$median_effect_Condition`, 95% CI = `r  study1_condition_vio_results_list$p_degraded$condition_CI`, `r study1_condition_vio_results_list$p_degraded$p_sum_Condition` % of *p*s \<.05).
-Interference was lower in the enhanced condition (median $\beta$ = `r study1_condition_vio_results_list$interference_enhanced$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_enhanced$condition_CI`, `r study1_condition_vio_results_list$interference_enhanced$p_sum_Condition` % of *p*s \<.05).
-Unexpectedly, interference was also lower in the degraded condition (median $\beta$ = `r study1_condition_vio_results_list$interference_degraded$median_effect_Condition`, 95% CI = `r study1_condition_vio_results_list$interference_degraded$condition_CI`, `r study1_condition_vio_results_list$interference_degraded$p_sum_Condition` % of *p*s \<.05), suggesting that the angle in the flanking arrows reduced interference, relative to the standard condition.
-However, none of the interaction effects for either violence exposure or unpredictability were significant.
-
-\pagebreak
-
-```{r}
-#| tab.id: table5
-#| results: markup
-study1_condition_results_table |> 
-  border(i = 1, border.bottom = fp_border_default(), part = "header") 
-```
-
-The results of the Pilot and Study 1 were inconsistent with regard to the association between adversity and interference, but hinted at two general patterns.
-First, violence exposure was not associated with *increased* interference; instead, we found either the opposite effect or no effect.
-Second, both violence exposure and unpredictability were associated with lowered strength of perceptual input, albeit inconsistently.
-These findings, if replicable, are intriguing as they would suggest that the common finding of lowered Flanker performance among people with more adversity exposure do not actually result from worse interference control---as typically inferred.
-Rather, such lowered performance would result from processes other than inhibition ability, such as slower general processing.
-Though interesting, our findings so far leave open the question why adversity might be negatively associated with perceptual input.
-This question was the focus of Study 2.
-
-# Study 2
-
-Study 2 set out to compare two explanations for the finding that people exposed to adversity tended to show lower strength of perceptual input on the Flanker.
-First, lowered strength of perceptual input in people exposed to adversity may indicate a difficulty in extracting relevant information (i.e., about their direction) from the arrows in general.
-Second, the difference in perceptual input may not be a cognitive deficit per se, but instead could be a signature of a difference in processing style---that is, a feature, and not a bug.
-People exposed to adversity may process information more holistically, focusing more on the configuration of pieces of information rather than individual pieces of information.
-On the Flanker, this would lower the depth of perceptual processing of any individual stimulus, thus resulting in lowered strength of perceptual input, as we observed in the Pilot and Study 1.
-
-We preregistered three aims focusing both on violence exposure and unpredictability.
-First, we expected to replicate our earlier findings that adversity was associated with lowered perceptual input and lower interference in people exposed to adversity.
-Second, we included a Global-Local Task to investigate the hypothesis---based on the findings of the Pilot and Study 1---that people with more adverse experiences would develop a more holistic style of information processing.
-Third, we planned to conduct a within-subjects analysis of Flanker and Global-Local performance to assess whether people with lowered perceptual input on the Flanker Task would also show a more global processing style (rather than a local processing style) on the Global-Local Task.
-
-## Methods
-
-### Participants
-
-Participants were 600 people from the United States between the ages of 18 and 30.
-Recruitment was identical to Study 1.
-We conducted a simulation-based power analysis for the planned linear mixed models with the Global Local Task (see GitHub).
-We determined that power of \> .80 for a standardized interaction effect of 0.06, with sigma (noise) set to 0.7 (comparable to observed sigmas in the first two studies) would require 550 participants.
-We recruited 600 participants, with the expectation to have a final sample of 550 participants after exclusions.
-We applied the same exclusion criteria as reported in the Pilot and Study 1.
-The final sample consisted of `r nrow(study2_data)` participants.
-
-### Measures
-
-The measures of childhood violence exposure and environmental unpredictability were identical to Study 1.
-The Flanker was identical to the standard version used in Study 1.
-
-*Global-Local Task*.
-The Global-Local Task is a measure of global-local processing [@navon_1977].
-Many different versions of this task exist in the literature.
-One key dimension on which they differ is whether the task measures focused attention (by cueing attention towards the global or local level prior to stimulus presentation) or divided attention (by having participants search for a target on both levels) [@lee_2023].
-Here, we use a version measuring divided attention, which allows measuring whether someone tends to have a more global versus local processing style [@hakim_2017; @lee_2023; @mckone_2010].
-
-Participants saw images of big, black letters (the global level) comprised of small letters (the local level)---so-called Navon images [@navon_1977]---against a white background.
-Participants first completed eight practice trials, after which they completed an additional 64 test trials.
-On each trial, participants searched for one of two target letters---an 'E' or 'H'---and indicated whether it was present on the global or local letter by pressing 'g' or 'l' on their keyboard, respectively.
-Each stimulus was 600 pixels high and 395 pixels wide and comprised of seven local letters vertically and five local letters horizontally.
-All stimuli consisted of combinations of the letters 'T', 'F', 'P', 'L', 'H', and 'E'.
-The target letters 'H' and 'E' were both present in each stimulus, but the other letters varied.
-The global and local level never contained the same letter.
-
-### Procedure
-
-The procedure was identical to Study 1.
-The full experiment took \~30 minutes.
-Participants were paid £4.50 when they reached the end of the experiment.
-
-### Data analyses
-
-**Multiverse analysis.** We included the same decisions in the multiverse as in the previous studies.
-However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, <https://anonymous.4open.science/r/CogDev_AnonLink/preregistrations/3_study2>).
-See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
-
-**DDM estimation.** For the Flanker, we used the SSP [@grange_2016; @white_2018a; @white_2018b; @white_2011] using the same procedure as in Study 1.
-For the Global-Local Task, we used a hierarchical Bayesian DDM to fit the data using the *runjags* package [@denwood_2016].
-See the supplemental materials (Section 3) for more information about the procedure and model fit.
-
-We deviated from our preregistration regarding the preprocessing of Global-Local Task data.
-Specifically, we relaxed the low performance threshold as the task was more difficult than anticipated.
-These deviations are described in the supplemental materials (section 4).
-
-**Primary analyses.** We ran simple regressions for analyses involving only main effects (aim 1), and linear mixed effects models for analyses involving within-subject interactions (aim 2 and 3).
-To address aim 3 (within-subject interaction between Global-Local drift rate and Flanker strength of perceptual input), we further preprocessed the data in two steps.
-First, we computed a difference score of Global-Local drift rates by subtracting the drift rate on local trials from the drift rate on global trials (with higher scores reflecting relatively faster information processing on global trials).
-Second, we separately standardized the Flanker strength of perceptual input and Global-Local drift rate difference.
-We fitted linear mixed effects models with the standardized performance measures as the dependent variable, and adversity type, task (Flanker or Global-Local, sum-coded) and their interaction as independent variables.
-
-## Results and discussion
-
-Figure 2 and 3 summarize the multiverse results for the effects of violence exposure and unpredictability within Study 2 and pooled across all studies.
-In Study 2, violence exposure was negatively associated with strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.vio_comp$boot_p`), but not associated with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.vio_comp$boot_p`).
-Unpredictability was not associated with either strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_study2_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$p_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$p_flanker.unp_comp$boot_p`), nor with interference ($\beta$~median~ = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_study2_list$interference_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_study2_list$interference_flanker.unp_comp$boot_p`).
-
-In the pooled analysis, the results were similar for both types of adversity.
-Violence exposure was associated with lower strength of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.vio_comp$CI`, `r study2_aim1_results_list$p_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.vio_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.vio_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.vio_comp$CI`, `r study2_aim1_results_list$interference_flanker.vio_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.vio_comp$boot_p`).
-Similarly, unpredictability was associated with a lower quality of perceptual input ($\beta$~median~ = `r study2_aim1_results_list$p_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$p_flanker.unp_comp$CI`, `r study2_aim1_results_list$p_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$p_flanker.unp_comp$boot_p`), but not with interference ($\beta$~median~ = `r study2_aim1_results_list$interference_flanker.unp_comp$median_effect_Main`, 95% CI = `r study2_aim1_results_list$interference_flanker.unp_comp$CI`, `r study2_aim1_results_list$interference_flanker.unp_comp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim1_results_list$interference_flanker.unp_comp$boot_p`).
-
-```{r}
-#| label: figure2
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 2.** Multiverse results for the association between violence exposure with the strength of perceptual input and interference on the Flanker across all studies.
-Each panel depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-The top row depicts effect curves in the Pilot.
-The second row depicts effect curves in Study 1.
-The third row depicts effect curves in Study 2.
-The Fourth row depicts effect curves of the pooled analyses across all studies.
-knitr::include_graphics("../figures/fig2.png")
-```
-
-<br>
-
-```{r}
-#| label: figure3
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 3.** Multiverse results for the association between unpredictability with the strength of perceptual input and interference on the Flanker across all studies.
-Each panel depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-The top row depicts effect curves in the Pilot.
-The second row depicts effect curves in Study 1.
-The third row depicts effect curves in Study 2.
-The Fourth row depicts effect curves of the pooled analyses across all studies.
-knitr::include_graphics("../figures/fig3.png")
-```
-
-<br>
-
-### Global-Local Task performance
-
-There was a main effect of violence exposure on Global-Local drift rates, with more violence exposure being associated with slower speed of information processing ($\beta$~median~ = `r study2_aim2_results_list$Main_vio$median_effect`, `r study2_aim2_results_list$Main_vio$p_sum`% of *p*s \< .05, bootstrapped *p* `r study2_aim2_results_list$Main_vio$boot_p`).
-There also was a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_vio$median_effect`, `r study2_aim2_results_list$Condition_vio$p_sum`% of *p*s \< .05, bootstrapped *p* `r study2_aim2_results_list$Condition_vio$boot_p`).
-Finally, there was an interaction effect between violence exposure and task condition ($\beta$~median~ = `r study2_aim2_results_list$Interaction_vio$median_effect`, `r study2_aim2_results_list$Interaction_vio$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_vio$boot_p`).
-Simple slopes analyses revealed that participants with lower levels of violence exposure did not differ in speed of processing of global versus local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.Low$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.Low$p_sum`% of *p*s \< .05).
-In contrast, participants with higher levels of violence exposure processed global targets faster than local targets (b~median~ = `r study2_aim2_simslopes2_list$vio_comp.High$median_ss`, `r study2_aim2_simslopes2_list$vio_comp.High$p_sum`% of *p*s \< .05).
-
-There was a significant main effect of unpredictability on drift rates, with more unpredictability being associated with slower speed of information processing, ($\beta$~median~ = `r study2_aim2_results_list$Main_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Main_unp$CI`, `r study2_aim2_results_list$Main_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Main_unp$boot_p`).
-We also found a main effect of task condition on drift rates, with people processing information faster when the target was present at the global level compared to the local level, ($\beta$~median~ = `r study2_aim2_results_list$Condition_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Condition_vio$CI`, `r study2_aim2_results_list$Condition_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Condition_unp$boot_p`).
-We did not find a significant unpredictability x task condition interaction effect ($\beta$~median~ = `r study2_aim2_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim2_results_list$Interaction_unp$CI`, `r study2_aim2_results_list$Interaction_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim2_results_list$Interaction_unp$boot_p`).
-
-### Within-subjects comparison of Flanker and Global-Local information processing
-
-There was no significant main effects for violence exposure (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`) nor for cognitive task (bootstrapped *p* = `r study2_aim3_results_list$Task_vio$boot_p`).
-There was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_vio$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_vio$CI`, `r study2_aim3_results_list$Interaction_vio$p_sum` % of *p*s \< .05, bootstrapped *p* `r study2_aim3_results_list$Interaction_vio$boot_p`) (See Figure 2).
-A simple slopes analysis revealed that people with higher levels of violence exposure showed lower strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$vio_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.Flanker$p_sum`% of *p*s \< .05), and showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$vio_comp.GlobalLocal$p_sum`% of *p*s \< .05).
-
-There was no significant main effect for unpredictability (bootstrapped *p* = `r study2_aim3_results_list$Task_unp$boot_p`).
-However, there was a significant interaction effect ($\beta$~median~ = `r study2_aim3_results_list$Interaction_unp$median_effect`, 95% CI = `r study2_aim3_results_list$Interaction_unp$CI`, `r study2_aim3_results_list$Interaction_unp$p_sum` % of *p*s \< .05, bootstrapped *p* = `r study2_aim3_results_list$Interaction_unp$boot_p`).
-A simple slopes analysis revealed that people with higher levels of unpredictability did not differ in their strength of perceptual input on the Flanker (b = `r study2_aim3_simslopes1_list$unp_comp.Flanker$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.Flanker$p_sum` % of *p*s \< .05), but showed a more global versus local processing style on the Global-Local Task (b = `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$median_ss`, `r study2_aim3_simslopes1_list$unp_comp.GlobalLocal$p_sum`% of *p*s \< .05).
-
-```{r}
-#| label: figure4
-#| fig.width: 7
-#| fig.height: 9
-#| dpi: 600
-#| fig-cap: | 
-#|   **Figure 4.** Multiverse results for the within-subjects comparison of Flanker and Global-Local information processing.
-Panel A depicts the multiverse interaction effects, with the thick black lines denoting the median slope and the thin lines denoting effects for each combination of arbitrary decisions.
-Blue thin lines indicate significant effects (*p* > .05), and grey thin lines indicate non-significant effects (*p* > .05).
-Panel B depicts sorted beta coefficients across all combinations of arbitrary decisions (i.e., the effect curve across the whole multiverse).
-See the main text for more information about the multiverse analyses.
-knitr::include_graphics("../figures/fig4.png")
-```
-
-<br>
-
-To sum up, Study 2 provided additional support for the basic finding that violence exposure and unpredictability were associated with lower strength of perceptual input but not with differences in interference; with the caveat that the associations for unpredictability only showed up in pooled analyses.
-People with more exposure to violence and unpredictability also processed information more slowly on the Global-Local Task.
-In line with our expectations, childhood exposure to violence was associated with both lowered strength of perceptual input and a more holistic processing style.
-The same processing style was observed for participants with more exposure to unpredictability, although they did not show lowered strength of perceptual input.
-
-# Exploratory analyses
-
-We hypothesized that the potential adaptive benefits of a more diffuse scope of attention in adverse conditions might be linked to the notion of a *present-oriented attention style* [@frankenhuis_2016; @vangelder_2023].
-People with a present-oriented attention style (versus a more future-oriented attention style) are more geared towards processing information that is relevant for solving challenges and obtaining rewards in the here-and-now.
-A general tendency to be more attuned to the present (while disregarding the future) is sometimes referred to as a short-term mindset [@kubel_2023; @vangelder_2023], which also includes tendencies to be more impulsive, to more steeply discount future rewards, and to be more sensation-seeking.
-Although short-term mindsets are associated with exposure to adversity [@ganschow_2023], it is unclear how they are associated with performance on attention tasks.
-We explored bivariate correlations pooled across all studies between two indicators of short-term mindsets (impulsivity and future orientation) and SSP parameters of the Flanker (for more information on the measures, see section 1 of the supplemental materials).
-
-See Table S2 for an overview of the correlations.
-Impulsivity was negatively associated with the strength of perceptual input (*r* = -.07, *p* = .004) and positively associated with interference (*r* = .09, *p* = .005). 
-In addition, impulsivity was also associated with a more holistic information processing style (*r* = .11, *p* = .020). 
-Thus, more impulsive participants processed information less deeply and were more easily drawn to distractions, but this might partly be explained by a holistic information processing style.
-Similarly, future-orientation was positively associated with perceptual input (*r* = .09 *p* < .001)—--but not with interference (*p* = .112) —--on the Flanker Task, and was also associated with a more detail-oriented processing style (*r* = -.12, *p* = .011).
-Thus, more future-oriented participants processed information more deeply, which might partly be explained by a detail-oriented processing style.
-
-# General discussion
-
-We investigated how two dimensions of childhood adversity---violence exposure and environmental unpredictability---are related to differences in how people attend to and process information.
-Specifically, we hypothesized that exposure to adversity might lead to a present-oriented attention style that would facilitate rapidly detecting novel or changing information, yet which would interfere with ignoring distractors.
-Across one pilot and two main studies, we tested how adversity was associated with performance on different attention tasks.
-The Pilot compared performance on a Cued Attention Task, Change Detection Task, and a Flanker.
-Two follow-up studies focused on the Flanker, with Study 2 also including a Global-Local Task.
-We leveraged DDM to estimate the processes underlying lowered and improved performance.
-This allowed us to investigate whether performance differences were associated with abilities (i.e., attention orientation, interference control, stimulus processing), or ability-irrelevant processes (e.g., stimulus encoding, response execution, response caution).
-Across all primary and exploratory analyses, we leveraged multiverse analysis to systematically assess the robustness of our findings against several uncontrollable aspects of the online assessment (e.g., distractions, fullscreen exits).
-
-### Main insights
-
-We found little to no support for the presence of a present-oriented attention style in people exposed to adversity.
-More childhood exposure to violence was associated with slower processing of subtle changes on the Change Detection Task and lower quality of perceptual input on the Flanker Task.
-It was not associated with speed of processing of peripheral information on the Cued Attention Task.
-Zooming in on the Flanker, our two main studies found mixed evidence for the hypotheses that violence exposure and unpredictability were associated with lower strength of perceptual input.
-This mixed evidence suggests that people with more exposure to these adversities process information less deeply, making it more difficult to make judgments about target and distractor information in equal measure.
-This was corroborated by the pooled analyses across studies, which found that both exposure to violence and unpredictability were associated with lower strength of perceptual input, but not with differences in the ability to inhibit distractors.
-This finding contradicts the standard deficit interpretation of lowered performance on inhibition tasks by people with more adversity exposure (discussed below).
-In addition, lowered strength of perceptual input was associated with a holistic processing style.
-Thus, we did not find evidence that people with more violence exposure have more difficulties with inhibiting task-irrelevant information.
-
-Our findings of the DDM decomposition of Flanker performance challenge previous interpretations based on raw performance.
-Previous studies have found that people exposed to adversity and/or low SES backgrounds have longer RTs on incongruent trials relative to congruent trials [@farah_2006; @fields_2021; @mezzacappa_2004; @mittal_2015; @noble_2005], which is commonly interpreted as an impaired ability to inhibit irrelevant information.
-This fits with adaptive hypotheses, as inhibition is assumed to be useful mostly in stable and predictable environment that afford long-term goal pursuit, but can be costly in unpredictable and potentially dangerous environments [@fields_2021; @mittal_2015; @daly_2005].
-Contrary to previous studies, we found little to no evidence for performance differences on the basis of raw RTs.
-In addition, our DDM analyses showed that performance differences on the Flanker are not driven by differences in interference control, but by more basic processes that are not typically considered when interpreting Flanker performance.
-
-Our findings align with a broader literature that is critical of the validity of the Flanker in particular, and that of cognitive control tasks more generally.
-As noted, several studies have failed to find coherent correlations between raw performance on different cognitive control tasks [e.g., @loffler_2022; @rey_mermet_2019; @rouder_2019; @stahl_2014].
-For example, previous research comparing several cognitive control tasks across different data sets using cognitive modeling found that shared variance between these tasks was mostly associated with processing speed and strategies (e.g., speed-accuracy trade-offs) [@hedge_2022].
-Moreover, the modeling parameters reflecting conflict processing (similar to interference in our study) were barely correlated.
-Similarly, previous work has shown that individual differences on common EF tasks---among which the Flanker Task---can be fully accounted for by general processing speed [@loffler_2022].
-This literature, together with the findings reported here, underscore that researchers should be cautious when drawing inferences about cognitive control abilities in people exposed to adversity based on raw RTs and performance on individual tasks.
-
-Finally, we showed that people exposed to adversity had a more holistic processing style, and that this style was associated with lower strength of perceptual input on the Flanker.
-This could mean that people with more adversity exposure processed the Flanker display more holistically; that is, focused less on individual arrows and more on the collection of arrows as a whole.
-One (tentative) interpretation is that in the absence of threatening or otherwise salient information, people with more exposure to adversity attend to and process information in the environment globally and less deeply.
-They might only shift to local processing of a single source of information if it seems threatening or otherwise salient [@shields_2015; @schwabe_2013].
-This would be consistent with research showing that growing up in a disadvantaged environment decreases the efficiency of the brain's (resting-state) salience network, which is in turn associated with lower raw performance on certain cognitive tasks [@cermakova_2023; @gellci_2019; @hilger_2017; @yuan_2012].
-This research also shows that in situations of acute stress, mental resources are reallocated to this salience network, increasing vigilance and facilitating adequate responding.
-Indeed, a few studies show that cognitive abilities that may be particularly relevant in adverse contexts---such as attention shifting and working memory updating---may be enhanced in people from adversity when they experience acute stress [@mittal_2015; @young_2018].
-
-### Strengths, limitations, and future directions
-
-Our study has three main strengths.
-First, each study included socioeconomically diverse participants.
-Second, the DDM allowed us to decompose performance in a more nuanced way than is possible with (typically used) raw performance scores.
-Third, the multiverse analyses provided a systematic overview of the robustness of our findings under different analytical decisions.
-Our study has three main limitations.
-First, all experiments were conducted online, which reduced control over people's testing environment, equipment, and behavior.
-Indeed, our results were the least robust against participants who skipped the screen-scaling procedure (to ensure the stimuli were adequately sized) and interruptions during the tasks, which are factors that are largely out of our control.
-Second, we deviated from our preregistrations in several ways in all studies, due to progressive insight.
-This decreased the severity of our statistical tests, and so this work would benefit from preregistered replications [@lakens_2023].
-
-Our findings suggest two main directions for future research.
-First, future studies could replicate and expand upon our finding that lower quality of information processing in people exposed to adversity is associated with a more holistic processing style.
-For example, future work could investigate whether people with more adversity exposure shift from holistic to a detail-oriented processing in situations of acute stress or otherwise salient information.
-Second, our results suggest that lower strength of perceptual input is likely the result of both processing styles, as well as of slower general processing.
-Future research could try to tease apart these sources using a within-subjects design simultaneously measuring inhibition, processing styles, and basic processing speed.
-Third, some research suggests that inhibition is not a unitary construct, instead distinguishing between response inhibition (which involves suppressing a prepotent response) and cognitive inhibition (which involves selective attention in the presence of distractors).
-Exposure to adversity might shape these two types of inhibition in different ways.
-For example, acute stress might impair performance on tasks of cognitive inhibition (of which the Flanker is an example) and enhances performance on tasks of response inhibition [for a meta-analysis, see @shields_2016; but see @dang_2017].
-Future work could assess inhibition more broadly, e.g., by including tasks that are hypothesized to require cognitive or response inhibition.
-
-### General conclusion
-
-We found that people with more childhood adversity exposure perform worse on the Flanker not because of an impairment in their ability to inhibit distracting information, but because of lower strength of perceptual input.
-Our results suggest that people with more adversity exposure are not worse at inhibiting distractions; rather, they do not seem to process information in the environment deeply unless it proves to be a reliable and important source of information.
-These findings challenge dominant interpretations, which infer an inhibition deficit from lowered performance.
-This is an important difference not just for theory development, but also for future interventions aimed at closing performance gaps.
-For example, when applied to school contexts, interventions based on an inhibition interpretation would focus on the learning environment, perhaps removing things from the classroom that could be distracting.
-In contrast, an intervention based on an information processing interpretation might instead focus on increasing the apparent relevance of the learning materials, perhaps by providing more repetition or by making the content more ecologically relevant [@young_2022].
-Thus, cognitive modeling can offer crucial insights for our understanding of cognitive abilities in adverse conditions.
-
-\pagebreak
-
-# Glossary
-
-**Adversity:** Prolonged exposures to intense stress; for instance, resulting from abuse, neglect, and poverty.
-
-<br>
-<br>
-
-**Boundary separation:** Parameter of the Drift Diffusion Model and Shrinking Spotlight Model. Measures the amount of information a person requires before making a decision (i.e., response caution).
-
-<br>
-<br>
-
-**Developmental adaptation:** A process that tailors people to the demands of their environments based on their experiences.
-
-<br>
-<br>
-
-**Drift Diffusion Model:** A formal cognitive model that estimates cognitive processes at different stages of the decision-making process for speeded binary decision-making tasks.
-It represents decision-making as a process in which people accumulate information until one response is sufficiently favored over the other.
-
-<br>
-<br>
-
-**Drift rate:** Parameter of the Drift Diffusion Model. Measures a person's speed of information accumulation on binary decision-making tasks.
-
-<br>
-<br>
-
-**Inhibition:** A person's ability to ignore task-irrelevant distractors in favor of task-relevant information.
-Operationalized in the Shrinking Spotlight Model as the initial attention width over all stimuli (i.e., target and distractors), divided by the rate at which attention is narrowed down to the central target.
-
-<br>
-<br>
-
-**Multiverse analysis:** An analysis technique that systematically and transparently evaluates the influence of arbitrary data-cleaning decisions on statistical outcomes.
-
-<br>
-<br>
-
-**Non-decision time:** Parameter of the Drift Diffusion Model and Shrinking Spotlight Model.
-Measures the time it takes a person to prepare for the task at the start of the trial (before information processing) and the time it takes to execute a response (after a response boundary has been reached) on binary decision-making tasks.
-
-<br>
-<br>
-
-**Perceptual input:** Parameter from the Shrinking Spotlight Model of Flanker performance. Measures how well a person can process the Flanker stimuli in general.
-
-<br>
-<br>
-
-**Shrinking Spotlight Model:** An extension of the standard Drift Diffusion Model to account for attention processes on the Flanker.
-
-\pagebreak
-
-# References {#refs}

### 2024-05-31 manuscript/manuscript.qmd
cleaning up manuscript folder

@@
 
-Previous research has shown that people who grew up in adverse conditions tend to be slower on the Flanker Task, suggesting difficulty inhibiting distractions.
-However, this pattern might result from slower general cognitive processes (e.g., reduced general processing speed), rather than the specific ability of inhibition.
-We used Drift Diffusion Modeling in three studies---one pilot and two confirmatory studies---to better understand associations of adversity exposures with Flanker performance. 
-Neither exposure to violence nor unpredictability were associated with inhibition.
-In contrast, although mixed, exposure to violence and unpredictability were associated with lower strength of perceptual input; that is, how well someone can process the arrows in general.
-Finally, lower strength of perceptual input was linked to a tendency to process information more holistically, focusing less on individual details.
-Thus, researchers should be cautious when drawing inferences about inhibition abilities in people exposed to adversity based on response times alone.
+It is well-established that individuals who grew up in adverse conditions tend to be slower on the Flanker Task. 
+This finding is typically interpreted to reflect difficulty inhibiting distractions. 
+However, it might result from slower general cognitive processes (e.g., reduced general processing speed), rather than the specific ability of inhibition. 
+We used Drift Diffusion Modeling in three online studies (total N = 1560) with young adults to understand associations of adversity with Flanker performance. 
+We find no associations between exposure to violence and unpredictability with inhibition. 
+Yet, although mixed, violence and unpredictability exposure were associated with lower strength of perceptual input--—how well someone can process target and distractor information alike. 
+Finally, people with lower strength of perceptual input processed information more holistically, focusing less on details. 
+Thus, lowered Flanker performance does not necessarily imply lowered inhibition ability. 
+Cognitive modeling reveals a different picture of abilities in adverse conditions as opposed to analyses based on raw performance.
 
@@
 Previous research shows that these two types of adversity are on the one hand associated with improved attention shifting and working memory updating [@fields_2021; @mittal_2015; @young_2018; @young_2022], and on the other hand with lowered inhibition and working memory capacity [@fields_2021; @mittal_2015; @young_2018].
-We conducted three online studies: one pilot and two follow-up studies.
-Using cognitive modeling, we unpack Flanker performance in comparison to other tasks that require externally focused attention (Pilot), across visual processing manipulations (Study 1), and in terms of tendencies for holistic versus local processing (Study 2).
+We conducted three online studies: one pilot study and two follow-up studies.
+Using cognitive modeling, we unpack Flanker task performance in comparison to other tasks that require externally focused attention (Pilot study), across visual processing manipulations (Study 1), and in terms of tendencies for holistic versus local processing (Study 2).
 
-We used an incremental preregistration approach across studies (for all preregistrations, code and materials, see [ANONYMIZED FOR REVIEW].
-For each study, we preregistered primary (i.e., hypothesis-driven) and exploratory analyses.
-The main text addresses the primary analyses involving violence exposure and the exploratory analyses involving environmental unpredictability.
+We used an incremental preregistration approach across studies (for all preregistrations, data, code and materials, see <https://anonymous.4open.science/r/CogDev_AnonLink>).
+For each study, we preregistered confirmatory (i.e., hypothesis-driven) and exploratory analyses.
+The main text addresses the confirmatory analyses involving violence exposure and the exploratory analyses involving environmental unpredictability.
 We describe the other exploratory analyses in the supplemental materials (section 2).
@@
 **Multiverse analysis.** We included the same decisions in the multiverse as in the previous studies.
-However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot and Study 1, instead of a subset, as we preregistered (for details, [ANONYMIZED FOR REVIEW]).
+However, there was one deviation from the preregistration: the multiverse analysis contained the same arbitrary decisions as the Pilot study and Study 1, instead of a subset, as we preregistered (for details, <https://anonymous.4open.science/r/CogDev_AnonLink/preregistrations/3_study2>).
 See the supplemental materials (section 5) for figures summarizing *p*-distributions and the explained variance in the regression coefficients of each data cleaning decision.
 
-**DDM estimation.** For the Flanker, we used the SSP [@grange_2016; @white_2018a; @white_2018b; @white_2011] using the same procedure as in Study 1.
-For the Global-Local Task, we used a hierarchical Bayesian DDM to fit the data using the *runjags* package [@denwood_2016].
+**DDM estimation.** For the Flanker task, we used the SSP [@grange_2016; @white_2018a; @white_2018b; @white_2011] using the same procedure as in Study 1.
+For the Global-Local task, we used a hierarchical Bayesian DDM to fit the data using the *runjags* package [@denwood_2016].
 See the supplemental materials (Section 3) for more information about the procedure and model fit.
 
-We deviated from our preregistration regarding the preprocessing of Global-Local Task data.
+We deviated from our preregistration regarding the preprocessing of Global-Local task data.
 Specifically, we relaxed the low performance threshold as the task was more difficult than anticipated.
@@
 Indeed, a few studies show that cognitive abilities that may be particularly relevant in adverse contexts---such as attention shifting and working memory updating---may be enhanced in people from adversity when they experience acute stress [@mittal_2015; @young_2018].
+
+We did not control for (potentially) confounding variables in our models, even though variables like education, intelligence, and current adversity exposure generally correlate with both childhood adversity exposure and performance on the Flanker task.
+Our reason for not including them as covariates was that all these factors can be reasonably seen as mediators of the association between childhood adversity and cognitive performance. 
+However, they are unlikely (or even impossible) causes of childhood adversity. 
+Therefore, adjusting for these variables could have introduced bias to our estimation of the total effect of childhood adversity on performance (which was our estimand) [@rohrer_2018]. 
+That said, one way in which our analyses may have been confounded is by using retrospective measures of adversity.
+For example, some work suggests that current psychopathology may bias retrospective reports of childhood adversity, although the causal pathways are still mostly unclear [@francis_2023; @goltermann_2023; @nivison_2021; @patten_2015].
+Systematic investigations into potential confounders will ultimately improve our understanding of the effects of early adversity [@ning_2023].
 

### 2024-05-31 manuscript/scripts/pooled_stage_objects.R

@@ -132,7 +132,7 @@ demographics_table <- list(
   }),
   age = map_dfr(list(pilot_data, study1_data, study2_data), function(x) { 
     x |> 
-      summarise(stat = paste0(paste0(round(mean(dems_age, na.rm = T),2), " (", round(sd(dems_age, na.rm = T), 2), ")"))) |> 
+      summarise(stat = paste0(paste0(round(mean(dems_age, na.rm = T),0), " (", round(sd(dems_age, na.rm = T), 0), ")"))) |> 
       mutate(categories = "Mean age (SD)") |> 
       mutate(study = x |> pull(study) |> unique())
   }),
@@ -281,7 +281,7 @@ study2_aim1_ssp_pooled_pvalues_plot <- unique(study2_aim1_ssp_pooled_pvalues$iv_
     
     
     pvalues |> 
-      ggplot(aes(p.value)) +
+      ggplot(aes(p)) +
       geom_histogram(color = "black", size = .2, bins = 100) +
       geom_vline(aes(xintercept = .05), linetype = "dashed") +
       annotate(

### 2024-05-31 README.Rmd
fix broken links in top-level README

@@
 
-Below is an overview of all the project milestones, such as first-time data access, submissions, and revisions.
+Below is an overview of all the project milestones (e.g., timestamped versions of the preregistrations).
 Data access events were automatically captured using custom code, which over the course of this project was collected in the R package `projectlog` [https://stefanvermeent.github.io/projectlog/](https://stefanvermeent.github.io/projectlog/).
-For more information about how tracking worked, Go to the [Open science workflow tab](https://stefanvermeent.github.io/abcd_ddm/opensci_workflow/README.html).
+Clicking the link of a specific milestone will take you to the historic version of the repository (i.e., as it was when the milestone was timestamped).
 
@@
         - **Milestone:** {name}
-        - **Data MD5 hash**: {hash}
-        - [Link to code snippet](https://github.com/StefanVermeent/liss_wm_profiles_2023/blob/{branch}/.projectlog/{commit}.R)
         \n
@@
 
-1.  [Pilot preprocessing scripts](https://github.com/stefanvermeent/attention_project/blob/main/1_pilot/scripts/0_data_prep).
-2.  [Study 1 preprocessing scripts](https://github.com/stefanvermeent/attention_project/blob/main/2_study1/scripts/0_data_prep).
-3.  [Study 2 preprocessing scripts](https://github.com/stefanvermeent/attention_project/blob/main/3_study2/scripts/0_data_prep).
+1.  [Pilot preprocessing scripts](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/1_pilot/scripts/0_data_prep).
+2.  [Study 1 preprocessing scripts](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/2_study1/scripts/0_data_prep).
+3.  [Study 2 preprocessing scripts](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/scripts/0_data_prep).
 
